### 2023-02-01 paper.Rmd
Initial commit

---
title: "Lorem ipsum dolor sit amet"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
author:
- name: Duke A Caboom
  affiliation: University of Tuktoyaktuk
  email: dtholmes@mail.ubc.ca
  number: 1
- name: Justin d'Ottawa
  affiliation: University of Ottawa
  number: 2
- name: Pedro Torres
  number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua. Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    number_sections: false
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/library.bib     # bibliografia en bibtex
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2cm,right=2cm,top=3cm,bottom=3cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = FALSE,    # cache de los chunks,usar analisis pesados
                      out.width = '85%',# largo de imagen en %
                      fig.pos= "H",     # posicion figuras H = HERE
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''

table_format = if(is_html_output()) { # Usar en argumento "format=" de kable
  "html"
} else if(is_latex_output()) {
  "latex"
}

fwidth = if(is_html_output()) { #Usar en argumento "full_width" de kableExtra
  T
} else if(is_latex_output()) {
  F
}
```

# Introducción

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.

Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

## Hipótesis

$H_{1}$: Individuos con mayor percepción de Estatus Social para su familia de origen tenderían a percibir más meritocracia

$H_{2}$: Una posición superior en la distribución de ingresos se asocia positivamente con la percepción de meritocracia.

$H_{3}$: Pertenecer a grupos con mayor logro educativo, se asocia con una mayor percepción de meritocracia

## Datos

* Descripción de la muestra

## Variables

* Variable(s) dependiente(s)
* Variables independientes

* Descriptivos
* Bivariados

## Métodos

# Resultados

> Para referencias una imagen generada en ggplot2 debemos fijar un label en el chunk: ` ```{r biscuits}` Luego, en el texto, usamos el tag `\@ref(fig:label)` como en el ejemplo:

```{r biscuits, echo=FALSE, fig.cap = "Relación entre biscuits y tea", fig.align='center',fig.width=10,fig.height=8,out.width='50%'}
tea <- rnorm(100)
biscuits <- tea + rnorm(100, 0, 1.3)
data <- data.frame(tea, biscuits) 
p <- ggplot(data, aes(x = tea, y = biscuits)) +
    geom_point() + 
    geom_smooth(method = "lm") + 
    labs(x = "Tea", y = "Biscuits") + theme_bw() 
print(p)
```

Como podemos ver la correlación en la Figura \@ref(fig:biscuits)

> Para referencias una tabla generada en `knitr::kable()` debemos fijar un label en las opciones del chunk : ` ```{r modelo1}`. Luego, en el texto, usamos el tag `\@ref(tab:label)` como en el ejemplo:

```{r modelo01, echo=FALSE}
data(efc) # Cargar datos
efc <- to_factor(efc, c161sex, e42dep, c172code) # convertir variables a factor
m   <- lm(neg_c_7 ~ pos_v_4 + c12hour + e42dep + c172code, data = efc)# Modelo 1
m2   <- lm(neg_c_7 ~ pos_v_4 + c12hour + e42dep , data = efc)         # Modelo 2
broom::tidy(m) %>%                      # resumen de modelo en formato tidy
  kable(format = table_format,          # formato de tabla ("html" o "latex")
        caption = "Tabla de regresión", # Título de tabla
        digits = 2,                     # decimales
        booktabs= TRUE,                 # lineas horizontales de tabla
        col.names = c("Variable","Coef.","SE","t","p")) %>% # etiquetas columnas
  kable_styling(full_width = fwidth,                        # ancho de tabla
                latex_options = c("HOLD_position")          # opciones de tabla pdf
                )   
```

La Tabla \@ref(tab:modelo01) muestra los resultados del modelo de regresión. @Brady2014 lo enuncia.

> En tablas que **NO SON** generadas con `knitr::kable()` debemos usar otro método:
En este caso usamos: `paste("(\\#tab:model2)",cap)`, donde previamente definimos el objeto `cap` y luego usamos `paste0()` para unir ambos vectores de caracteres lo cual se debería ver así: `"(\\#tab:model2) Modelos de regresión para autos y sus partes."`

```{r results='asis'}
cap <- "Modelos de regresión para autos y sus partes." # Titulo de tabla
custom.coef.names = c( # Custom names para coeficientes:                                                     
  "Intercept",
  "Positive value with 4 items",
  "average number of hours of care per week",
  "slightly dependent", "moderately dependent", "severely dependent",
  "intermediate level of education","high level of education"
  )
# Custom footnote de tabla: 
custom.note = "$^{***}$p < 0,001;$^{**}$p < 0,01;$^{*}$p < 0,05. Errores estándar robustos entre paréntesis (HC2)"
# texreg::knitreg() decide si usar formato tabla html o latex según corresponda. 
knitreg(list(m,m2),                            # Modelos 1 y 2
       caption = paste("(\\#tab:model2)",cap), # Label para crossref + titulo  
       caption.above = T,                      # Titulo de tabla arriba
       custom.coef.names=custom.coef.names,    # Definir custom names para coeficientes
       custom.note = custom.note,              # Definir footnote de tabla
       booktabs = TRUE,                        # Usar líneas horizontales en tabla
       scalebox = 0.75,                         # tamaño de tabla a .75
       float.pos = "hp!"
       )                        
```

Table \@ref(tab:model2) contrasta el Modelo 1 saturado, versus el Modelo 2 simplificado.

# Conclusiones

# References

<div id="refs"> </div>  <!-- Aunque <div> es tag HTML, este método funciona para otros formatos de salida como el PDF. -->

# (APPENDIX) Appendix {-}

`r if (knitr::is_latex_output()){ '\\appendix'}`          <!-- Si documento es latex, se genera sección de Anexos -->
`r if (knitr::is_latex_output()){ '\\section{Appendix}'}` <!-- Si documento es latex, se genera titulo de Anexos -->

|                     | Sample  |   CEP  |
|---------------------|:-------:|:------:|
| __Gender__          |         |        |
| Men                 | 49,82%  | 50,52% |
| Women               | 50.18%  | 49,47% |
| __Age__             |         |        |
| 18 - 24             | 18,55%  | 18,17% |
| 25 - 34             | 18,86%  | 17,48% |
| 35 - 44             | 19.09%  | 19,98% |
| 45 - 54             | 17,96%  | 19,23% |
| 55 - or more        | 25,54%  | 25.11% |
| __Education__       |         |        |
| Primary  or less    | 2,93%   | 15,88% |
| High school          | 43,23%  | 37,04% |
| Non university      | 32,63%  | 28,93% |
| university or more  | 21,21%  | 18,13% |
Table: `r as.character(paste("(\\#tab:rep-samp)", "Representativeness of the sample"))`. <!-- Label+titulo de tabla en syntax Markdown pura -->

### 2023-02-01 procesamiento/prod_analysis.Rmd
Initial commit

---
title: "Análisis de datos"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }

#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

## Librerías

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,       # Manipulacion de datos 
               haven,       # importar datos en .dta o .sav
               sjmisc,      # descriptivos y frecuencias
               sjPlot,      # tablas, plots y descriptivos
               summarytools,# resumen de dataframe
               texreg,      # tablas de regresion
               knitr,       # tablas kable
               kableExtra,  # tablas kable personalizadas
               ggplot2,     # plots
               corrplot     # plot correlacion
               )
```

## Datos
```{r}
load(file = "../input/data/proc/df_final.Rdata" )
```

# Análisis

## Descriptivos univariados

## Descriptivos bivariadas

## Estimaciones - modelos

### 2023-02-01 procesamiento/prod_prep.Rmd
Initial commit

---
title: "Preparación de datos"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica
```

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

## Librerías

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos 
               haven,       # importar datos en .dta o .sav
               car,         # recodificar variables
               sjlabelled,  # etiquetado de variables
               sjmisc,      # descriptivos y frecuencias
               sjPlot,      # tablas, plots y descriptivos
               summarytools,# resumen de dataframe
               )
```

## Datos

Para este ejemplo se va utilizar una base de datos proveniente del paquete `carData`:

> The Chile data frame has 2700 rows and 8 columns. The data are from a national survey conducted in April and May of 1988 by FLACSO/Chile. There are some missing data.

```{r echo=TRUE}
df<- carData::Chile
df1 <- df %>% select(zona=region,
                     poblacion=population,
                     sexo=sex,
                     edad=age,
                     educ=education,
                     statusquo)
```

# Preparación

En esta sección se realizará la preparación de datos. Se sugiere seguir los siguientes pasos para cada variable:

| Paso                      | Función                         |
|---------------------------|---------------------------------|
| 1. Descriptivo inicial    | sjmisc::frq() o sjmisc::descr() |
| 2. Recodificación         | car::recode()                   |
| 3. Etiquetado de valores  | sjlabelled::set_labels()        |
| 4. Etiquetado de variable | sjlabelled::set_label()         |
| 5. Descriptivo final      | sjmisc::frq o sjmisc::descr()   |

## Variables individuales

### Edad 
```{r edad}
sjmisc::descr(df1$edad)
df1$edadcat <- car::recode(var = df1$edad,
                           recodes = "18:24=1;25:44=2;45:64=3;65:70=4",
                           as.factor = T) 
df1$edadcat <- set_labels(x = df1$edadcat,
                          labels = c("18 a 24 años" = 1,
                                     "25 a 44 años" = 2,
                                     "45 a 65 años" = 3,
                                     "65 años o más" = 4))
df1$edadcat <- set_label(df1$edadcat,label = "Tramos de edad")
sjmisc::frq(df1$edadcat,out = "txt")
```

### Sexo 
```{r sexo}
sjmisc::frq(df1$sexo)
df1$mujer <- car::recode(var = df1$sexo,
                           recodes = "'F'=1;'M'=0",
                           as.factor = T)

df1$mujer <- set_labels(x = df1$mujer,
                          labels = c("Hombre" = 0,
                                     "Mujer" = 1))
df1$mujer <- set_label(df1$mujer,label = "Sexo entrevistado")
sjmisc::frq(df1$mujer,out = "txt")
```

### Nivel educacional

```{r}
sjmisc::frq(df1$educ)
df1$educ <- car::recode(df1$educ,
                        recodes = "'P'=1;'S'=2;'PS'=3",
                        as.factor = T)

df1$educ <- set_labels(df1$educ,labels = c("Primaria"=1,
                                           "Secundaria"=2,
                                           "Post-secundaria"=3))
df1$educ <- set_label(df1$educ,label = "Nivel educacional")
sjmisc::frq(df1$educ)
```

### Apoyo statusquo

```{r}
sjmisc::descr(df1$statusquo)
df1$statusquo <- set_label(df1$statusquo,label = "Escala de apoyo al status-quo")
sjmisc::descr(df1$statusquo)
```

## Variables contextuales

### Zona

```{r zona}
sjmisc::frq(df1$zona)
df1$zona <- set_labels(x = df1$zona,
                          labels = c("Centro" = "C",
                                     "Metropolitana Santiago" = "M",
                                     "Norte"="N",
                                     "Sur"="S",
                                     "Santiago ciudad"='SA'))
df1$zona <- set_label(df1$zona,label = "Zona geográfica")
sjmisc::frq(df1$zona,out = "txt")
```

### Proporcion de mujeres x zona
```{r}
tab_xtab(var.row = df1$zona, # Filas= zona
         var.col = df1$mujer,# columna= sexo 
         show.obs = FALSE,   
         show.row.prc = T)
df1 %>% group_by(zona) %>% summarise(propmuj=mean(as.numeric(mujer))-1)

prop.muj<- df1 %>%
  group_by(zona, mujer) %>%
  summarise(n = n()) %>%
  mutate(propmuj = n / sum(n)) %>%
  filter(mujer==1) %>% 
  ungroup() %>% 
  select(zona,propmuj)

df1 <- left_join(df1,prop.muj,by="zona")
df1$propmuj <- set_label(df1$propmuj,label = "Proporción de mujeres por zona geográfica")
sjmisc::descr(df1$propmuj)
```

### Población por zona

```{r poblacion}
sjmisc::frq(df1$poblacion)
df1$poblacion <- set_label(df1$poblacion,label = "Población por zona geofráfica")
sjmisc::frq(df1$poblacion,out = "txt")
```

# Seleccionar variables

```{r}
df_final<- df1 %>%
  select(zona,
         poblacion,
         mujer,
         edadcat,
         educ,
         statusquo)
```

# Resumen

```{r,results='asis', echo=FALSE}
st_css() # esto configura el css de dfsummary
print(dfSummary(df_final),
      method = "render")
view_df(df_final)
```

# Guardar datos

```{r}
save(df_final,file = "../input/data/proc/df_final.Rdata")
```

### 2023-06-21 procesamiento/prod_analysis.Rmd
update1

@@
 
-```{css, echo=FALSE}
-# /* expandir el espacio del documento*/
-body .main-container {
-      max-width: 1600px !important;
-      width: 1600px !important;
-    }
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
 
-#/* expandir width de la TOC*/
-div.tocify {
-    width: 22% !important;
-    max-width: 331px !important;
-    max-height: 102% !important;
-}
+df1$country2 <- sjlabelled::to_character(df1$country) 
+percentage_data <- df1 %>%
+  group_by(country2, class5) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,class5,percentage)
+
+percentage_data$class5 <- forcats::fct_rev(percentage_data$class5)
+
+order <- 
+percentage_data %>% 
+  filter(class5=="Non-skilled manual workers (VIIa+b)") %>% 
+  arrange(percentage) %>% 
+  select(country2)
+
+order$orden <- 1:30
+ggplot(percentage_data, aes(x=country2,y=percentage,fill=class5,group=class5))+
+  geom_bar(stat = 'identity')+
+  # geom_text(aes(label=number_of_errors),position = position_stack(0.5))+
+  scale_y_continuous(labels = NULL) +
+  scale_x_discrete(limits=order$country2) +  
+  scale_fill_ordinal() +
+  theme_classic() +
+  theme(legend.position = 'bottom')  +
+  coord_flip()
 ```
-
-## Librerías
 
@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,       # Manipulacion de datos 
-               haven,       # importar datos en .dta o .sav
-               sjmisc,      # descriptivos y frecuencias
-               sjPlot,      # tablas, plots y descriptivos
-               summarytools,# resumen de dataframe
-               texreg,      # tablas de regresion
-               knitr,       # tablas kable
-               kableExtra,  # tablas kable personalizadas
-               ggplot2,     # plots
-               corrplot     # plot correlacion
-               )
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+
+df1$country2 <- sjlabelled::to_character(df1$country) 
+percentage_data <- df1 %>%
+  group_by(country2, class3) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,class3,percentage)
+
+percentage_data$class3 <- forcats::fct_rev(percentage_data$class3)
+
+order <- 
+percentage_data %>% 
+  filter(class3=="Intermediate class (III+IV)") %>% 
+  arrange(percentage) %>% 
+  select(country2)
+
+order$orden <- 1:30
+ggplot(percentage_data, aes(x=country2,y=percentage,fill=class3,group=class3))+
+  geom_bar(stat = 'identity')+
+  # geom_text(aes(label=number_of_errors),position = position_stack(0.5))+
+  scale_y_continuous(labels = NULL) +
+  scale_x_discrete(limits=order$country2) +  
+  scale_fill_ordinal() +
+  theme_classic() +
+  theme(legend.position = 'bottom')  +
+  coord_flip()
 ```
-
-## Datos
-```{r}
-load(file = "../input/data/proc/df_final.Rdata" )
-```
-
-# Análisis
-
-## Descriptivos univariados
-
-## Descriptivos bivariadas
-
-## Estimaciones - modelos

### 2023-06-21 procesamiento/prod_prep.Rmd
update1

@@
 ---
-title: "Preparación de datos"
+title: "Data preparation"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
 
-```{css, echo=FALSE}
-# /* expandir el espacio del documento*/
-body .main-container {
-      max-width: 1600px !important;
-      width: 1600px !important;
-    }
-#/* expandir width de la TOC*/
-div.tocify {
-    width: 22% !important;
-    max-width: 331px !important;
-    max-height: 102% !important;
-}
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally)
+df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
 ```
 
-## Librerías
+```{r generador}
+ocupations <- names(dplyr::select(df1,v1:v10))
 
-```{r}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-                            # cargar librerias
-pacman::p_load(dplyr,       # Manipulacion de datos 
-               haven,       # importar datos en .dta o .sav
-               car,         # recodificar variables
-               sjlabelled,  # etiquetado de variables
-               sjmisc,      # descriptivos y frecuencias
-               sjPlot,      # tablas, plots y descriptivos
-               summarytools,# resumen de dataframe
+for (i in ocupations) {
+  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
+  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
+}
+
+frq(df1$v1)
+df1$busdriver <- as.numeric(car::recode(df1$v1,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$busdriver) <- "Know: bus/lorry driver" 
+frq(df1$busdriver)
+
+frq(df1$v2)
+df1$ceo <- as.numeric(car::recode(df1$v2,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$ceo) <- "Know: CEO large company" 
+frq(df1$ceo)
+
+frq(df1$v3)
+df1$cleaner <- as.numeric(car::recode(df1$v3,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$cleaner) <- "Know: home or office cleaner" 
+frq(df1$cleaner)
+
+frq(df1$v4)
+df1$hairbarber <- as.numeric(car::recode(df1$v4,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hairbarber) <- "Know: hairdresser/barber" 
+frq(df1$hairbarber)
+
+frq(df1$v5)
+df1$hrmanager <- as.numeric(car::recode(df1$v5,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hrmanager) <- "Know: human resource manager" 
+frq(df1$hrmanager)
+
+frq(df1$v6)
+df1$lawyer <- as.numeric(car::recode(df1$v6,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$lawyer) <- "Know: lawyer" 
+frq(df1$lawyer)
+
+frq(df1$v7)
+df1$mechanic <- as.numeric(car::recode(df1$v7,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$mechanic) <- "Know: car mechanic" 
+frq(df1$mechanic)
+
+frq(df1$v8)
+df1$nurse <- as.numeric(car::recode(df1$v8,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$nurse) <- "Know: nurse" 
+frq(df1$mechanic)
+
+frq(df1$v9)
+df1$police <- as.numeric(car::recode(df1$v9,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$police) <- "Know: police officer" 
+frq(df1$police)
+
+frq(df1$v10)
+df1$teacher <- as.numeric(car::recode(df1$v10,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$teacher) <- "Know: school teacher" 
+frq(df1$teacher)
+
+# Total of known occupations
+isei_ocupnames<- names(select(df1,busdriver:teacher))
+df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+summary(df1$know_total)
+sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
+sjPlot::plot_frq(df1$know_total,type = 'density')
+```
+
+```{r isei-generador}
+df1$isei_busdriver <- as.numeric(ifelse(df1$busdriver ==1,37,NA)) 
+sjlabelled::set_label(df1$isei_busdriver) <- "ISEI: bus/lorry driver" 
+frq(df1$isei_busdriver)
+
+df1$isei_ceo <- as.numeric(ifelse(df1$ceo==1,70,NA)) 
+sjlabelled::set_label(df1$isei_ceo) <- "ISEI: CEO large company" 
+frq(df1$isei_ceo)
+
+df1$isei_cleaner <- as.numeric(ifelse(df1$cleaner==1,17,NA)) 
+sjlabelled::set_label(df1$isei_cleaner) <- "ISEI: home or office cleaner" 
+frq(df1$isei_cleaner)
+
+df1$isei_hairbarber <- as.numeric(ifelse(df1$hairbarber==1,32,NA)) 
+sjlabelled::set_label(df1$isei_hairbarber) <- "ISEI: hairdresser/barber" 
+frq(df1$isei_hairbarber)
+
+df1$isei_hrmanager <- as.numeric(ifelse(df1$hrmanager==1,68,NA)) 
+sjlabelled::set_label(df1$isei_hrmanager) <- "ISEI: human resource manager" 
+frq(df1$isei_hrmanager)
+
+df1$isei_lawyer <- as.numeric(ifelse(df1$lawyer==1,85,NA)) 
+sjlabelled::set_label(df1$isei_lawyer) <- "ISEI: lawyer" 
+frq(df1$isei_lawyer)
+
+df1$isei_mechanic <- as.numeric(ifelse(df1$mechanic==1,38,NA)) 
+sjlabelled::set_label(df1$isei_mechanic) <- "ISEI: car mechanic" 
+frq(df1$isei_mechanic)
+
+df1$isei_nurse <- as.numeric(ifelse(df1$nurse==1,48,NA)) 
+sjlabelled::set_label(df1$isei_nurse) <- "ISEI: nurse" 
+frq(df1$isei_nurse)
+
+df1$isei_police <- as.numeric(ifelse(df1$police==1,53,NA)) 
+sjlabelled::set_label(df1$isei_police) <- "ISEI: police officer" 
+frq(df1$isei_police)
+
+df1$isei_teacher <- as.numeric(ifelse(df1$teacher==1,63,NA)) 
+sjlabelled::set_label(df1$isei_teacher) <- "ISEI: school teacher" 
+frq(df1$isei_teacher)
+```
+
+```{r social-capital}
+# Social capital measures
+isei_ocupnames<- names(select(df1,starts_with("isei_")))
+
+# number of high status contacts
+df1$n_high <- 
+  rowSums(x = select(df1,c("lawyer","hrmanager","ceo")),na.rm = T)
+sjlabelled::set_label(df1$n_high) <- 'Number of high status contacts'
+sjPlot::plot_frq(df1$n_high,type = 'density')
+
+# percentage of high status contacts
+
+df1$pct_high <- (df1$n_high/df1$know_total)*100
+sjlabelled::set_label(df1$df1$pct_high ) <- 'Percentage of high status contacts'
+sjPlot::plot_frq(df1$pct_high,type = 'density')
+
+# number of middle status contacts
+df1$n_middle <-
+  rowSums(x = select(df1,c("teacher","police","nurse")),na.rm = T)
+sjlabelled::set_label(df1$n_middle) <- 'Number of middle status contacts'
+sjPlot::plot_frq(df1$n_middle,type = 'density')
+
+# percentage of middle status contacts
+df1$pct_middle <- (df1$n_middle/df1$know_total)*100
+sjlabelled::set_label(df1$pct_middle) <- 'Percentage of middle status contacts'
+sjPlot::plot_frq(df1$pct_middle,type = 'density')
+
+# number of low status contacts
+# df1$n_low <- 
+#   rowSums(x = select(df1,c("n_waiter","n_carmech","n_taxi","n_stvend","n_cleaner")),na.rm = T)
+df1$n_low <- 
+  rowSums(x = select(df1,c("mechanic","busdriver","hairbarber","cleaner")),na.rm = T)
+sjlabelled::set_label(df1$n_low) <- 'Number of low status contacts'
+sjPlot::plot_frq(df1$n_low,type = 'density')
+
+# percentage of low status contacts
+df1$pct_low <- (df1$n_low/df1$know_total)*100
+sjlabelled::set_label(df1$pct_low) <- 'Percentage of low status contacts'
+sjPlot::plot_frq(df1$pct_low,type = 'density')
+
+# Average ISEI 
+df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) #REVISAR NO DEBERIA CONTENER 0
+sjlabelled::set_label(df1$isei_avg) <- 'Average contact prestige'
+summary(df1$isei_avg)
+
+sjPlot::plot_frq(df1$isei_avg,type = 'density')
+
+# Total ISEI 
+df1$isei_tot <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+sjlabelled::set_label(df1$isei_tot) <- 'Total contact prestige'
+summary(df1$isei_tot)
+sjPlot::plot_frq(df1$isei_tot,type = 'density')
+
+# skimr::skim(df1$isei_tot/df1$n_total)
+# skimr::skim(df1$isei_tot/df1$know_total)
+# skimr::skim(df1$isei_avg)
+
+# max ISEI 
+df1 <- df1 %>% 
+mutate(isei_max = do.call(pmax, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_max) <- 'Maximum contact prestige'
+sjmisc::frq(df1$isei_max)
+sjPlot::plot_frq(df1$isei_max)
+
+# min ISEI
+df1 <- df1 %>% 
+mutate(isei_min = do.call(pmin, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_min) <- 'Minimum contact prestige'
+sjmisc::frq(df1$isei_min)
+sjPlot::plot_frq(df1$isei_min)
+
+# range ISEI
+table(df1$know_total>=2)
+df1$isei_range <- ifelse(df1$know_total>=2,(df1$isei_max - df1$isei_min),no = NA)
+
+sjlabelled::set_label(df1$isei_range) <- 'Range contact prestige'
+sjmisc::frq(df1$isei_range)
+# sjPlot::plot_frq(df1$isei_range)
+# df1 %>% select(starts_with("isei_")) %>%View
+
+# ggpairs(df1[,c("isei_avg","isei_max","isei_range",
+#                  "know_total","n_high","n_middle","n_low",
+#                  "pct_high","pct_middle","pct_low")],
+#         title="Social capital measures")
+
+```
+
+# Occupational status
+
+```{r isei}
+df1$ISCO08[df1$ISCO08 %in% c(9998,9999)] <- NA
+df1$isei08 <- occupar::isco08toISEI08(isco08 = df1$ISCO08,display.nas = T)
+summary(df1$isei08)
+
+frq(df1$SPISCO08)
+df1$SPISCO08[df1$SPISCO08 %in% c(9998,9999)] <- NA
+df1$isei08sp <- occupar::isco08toISEI08(isco08 = df1$SPISCO08,display.nas = T)
+summary(df1$isei08sp)
+```
+
+# Class scheme
+
+```{r class}
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+frq(df1$SPISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
+sjmisc::frq(df1$isco88spo)
+
+#Relación de Empleo encuestado
+sjmisc::frq(df1$SPEMPREL)
+
+df1$sempspo <- df1$SPEMPREL
+df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
+sjmisc::frq(df1$sempspo)
+
+df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
+sjmisc::frq(df1$sempspo)
+
+# superivison
+sjmisc::frq(df1$SPWRKSUP) #supervision spouse
+df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
+sjmisc::frq(df1$supvisspo)
+
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+frq(df1$ISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88r <- occupar::isco08to88(df1$ISCO08)
+sjmisc::frq(df1$isco88r)
+
+#Note: the package generate identical recodes as my own manual recoding
+
+#Employment relation encuestado
+sjmisc::frq(df1$EMPREL)
+sjmisc::frq(df1$WORK)
+df1$semp <- df1$EMPREL
+df1$semp <- as.numeric(car::recode(df1$semp, "c(2,3,4)=1;c(1)=2;c(0,8,9)=NA"))
+sjmisc::frq(df1$semp)
+df1$semp <- sjlabelled::set_labels(x = df1$semp,labels=c('Self-employed','Employee'))
+sjmisc::frq(df1$semp)
+
+# superivison
+sjmisc::frq(df1$NEMPLOY) #supervision respondent
+df1$supvis <- as.numeric(car::recode(df1$NEMPLOY,"c(9998,9999)=NA"))
+sjmisc::frq(df1$supvis)
+# save the occupational variables for using them in stata-----------------------
+df1$id <- NULL
+df1 <- tibble::rowid_to_column(df1, "id")
+haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
+                              "isco88spo","sempspo","supvisspo")],
+                 path = "input/data/proc/ocup_respondent-spouse.dta")
+
+# Load the data created in stata------------------------------------------------
+df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
+df1 <- left_join(df1,df_class,by='id')
+
+df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$class10 <- sjlabelled::set_labels(df1$class10, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$class10) <- "Social Class - respondent"
+
+frq(df1$class10)
+
+df1$class10spo <- car::recode(df1$class10spo, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$class10spo <- sjlabelled::set_labels(df1$class10spo, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$class10spo) <- "Social Class - spouse"
+
+frq(df1$class10spo)
+
+#if NA in class of respondent, replace with household
+
+sjmisc::frq(df1$class10)
+sjmisc::frq(df1$class10spo)
+
+df1$class11 <- ifelse(is.na(df1$class10),df1$class10spo,df1$class10)
+sjmisc::frq(df1$class11)
+
+# if NA in respondents it is assumed to be lower than spouse
+# know, with the cases in we have information for respondent and spouse
+# we replace the value by the highest one, just for those
+
+# Replace the highest class by dominance criteria 
+# Keep the highest of two values:
+df1$class11d <- pmax(df1$class11, #social class respondent + spouse vs:
+                       df1$class10spo,#social class spouse
+                       na.rm = T) # if NA, do nothing
+
+df1$class11d <- 
+  sjlabelled::set_labels(df1$class11d,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                         labels =  c("I", "II", "IIIa", "IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
+sjmisc::frq(df1$class11d)
+sjlabelled::set_label(df1$class11d) <- "Social Class"
+
+# Class Scheme 3 classes
+df1$class3 <- car::recode(df1$class11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3) <- "Social Class"
+
+sjmisc::frq(df1$class3)
+
+# Class Scheme 5 classes
+df1$class5 <- car::recode(
+  df1$class11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$class5) <- "Social Class"
+sjmisc::frq(df1$class5)
+
+# Class Scheme 6 classes
+df1$class6 <- car::recode(
+  df1$class11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
 )
@@
 
-## Datos
-
-Para este ejemplo se va utilizar una base de datos proveniente del paquete `carData`:
-
-> The Chile data frame has 2700 rows and 8 columns. The data are from a national survey conducted in April and May of 1988 by FLACSO/Chile. There are some missing data.
-
-```{r echo=TRUE}
-df<- carData::Chile
-df1 <- df %>% select(zona=region,
-                     poblacion=population,
-                     sexo=sex,
-                     edad=age,
-                     educ=education,
-                     statusquo)
+```{r}
+save(df1,file = here::here("input/data/proc/study1.RData"))
 ```
-
-# Preparación
-
-En esta sección se realizará la preparación de datos. Se sugiere seguir los siguientes pasos para cada variable:
-
-| Paso                      | Función                         |
-|---------------------------|---------------------------------|
-| 1. Descriptivo inicial    | sjmisc::frq() o sjmisc::descr() |
-| 2. Recodificación         | car::recode()                   |
-| 3. Etiquetado de valores  | sjlabelled::set_labels()        |
-| 4. Etiquetado de variable | sjlabelled::set_label()         |
-| 5. Descriptivo final      | sjmisc::frq o sjmisc::descr()   |
-
-## Variables individuales
-
-### Edad 
-```{r edad}
-sjmisc::descr(df1$edad)
-df1$edadcat <- car::recode(var = df1$edad,
-                           recodes = "18:24=1;25:44=2;45:64=3;65:70=4",
-                           as.factor = T) 
-df1$edadcat <- set_labels(x = df1$edadcat,
-                          labels = c("18 a 24 años" = 1,
-                                     "25 a 44 años" = 2,
-                                     "45 a 65 años" = 3,
-                                     "65 años o más" = 4))
-df1$edadcat <- set_label(df1$edadcat,label = "Tramos de edad")
-sjmisc::frq(df1$edadcat,out = "txt")
-```
-
-### Sexo 
-```{r sexo}
-sjmisc::frq(df1$sexo)
-df1$mujer <- car::recode(var = df1$sexo,
-                           recodes = "'F'=1;'M'=0",
-                           as.factor = T)
-
-df1$mujer <- set_labels(x = df1$mujer,
-                          labels = c("Hombre" = 0,
-                                     "Mujer" = 1))
-df1$mujer <- set_label(df1$mujer,label = "Sexo entrevistado")
-sjmisc::frq(df1$mujer,out = "txt")
-```
-
-### Nivel educacional
-
-```{r}
-sjmisc::frq(df1$educ)
-df1$educ <- car::recode(df1$educ,
-                        recodes = "'P'=1;'S'=2;'PS'=3",
-                        as.factor = T)
-
-df1$educ <- set_labels(df1$educ,labels = c("Primaria"=1,
-                                           "Secundaria"=2,
-                                           "Post-secundaria"=3))
-df1$educ <- set_label(df1$educ,label = "Nivel educacional")
-sjmisc::frq(df1$educ)
-```
-
-### Apoyo statusquo
-
-```{r}
-sjmisc::descr(df1$statusquo)
-df1$statusquo <- set_label(df1$statusquo,label = "Escala de apoyo al status-quo")
-sjmisc::descr(df1$statusquo)
-```
-
-## Variables contextuales
-
-### Zona
-
-```{r zona}
-sjmisc::frq(df1$zona)
-df1$zona <- set_labels(x = df1$zona,
-                          labels = c("Centro" = "C",
-                                     "Metropolitana Santiago" = "M",
-                                     "Norte"="N",
-                                     "Sur"="S",
-                                     "Santiago ciudad"='SA'))
-df1$zona <- set_label(df1$zona,label = "Zona geográfica")
-sjmisc::frq(df1$zona,out = "txt")
-```
-
-### Proporcion de mujeres x zona
-```{r}
-tab_xtab(var.row = df1$zona, # Filas= zona
-         var.col = df1$mujer,# columna= sexo 
-         show.obs = FALSE,   
-         show.row.prc = T)
-df1 %>% group_by(zona) %>% summarise(propmuj=mean(as.numeric(mujer))-1)
-
-prop.muj<- df1 %>%
-  group_by(zona, mujer) %>%
-  summarise(n = n()) %>%
-  mutate(propmuj = n / sum(n)) %>%
-  filter(mujer==1) %>% 
-  ungroup() %>% 
-  select(zona,propmuj)
-
-df1 <- left_join(df1,prop.muj,by="zona")
-df1$propmuj <- set_label(df1$propmuj,label = "Proporción de mujeres por zona geográfica")
-sjmisc::descr(df1$propmuj)
-```
-
-### Población por zona
-
-```{r poblacion}
-sjmisc::frq(df1$poblacion)
-df1$poblacion <- set_label(df1$poblacion,label = "Población por zona geofráfica")
-sjmisc::frq(df1$poblacion,out = "txt")
-```
-
-# Seleccionar variables
-
-```{r}
-df_final<- df1 %>%
-  select(zona,
-         poblacion,
-         mujer,
-         edadcat,
-         educ,
-         statusquo)
-```
-
-# Resumen
-
-```{r,results='asis', echo=FALSE}
-st_css() # esto configura el css de dfsummary
-print(dfSummary(df_final),
-      method = "render")
-view_df(df_final)
-```
-
-# Guardar datos
-
-```{r}
-save(df_final,file = "../input/data/proc/df_final.Rdata")
-```

### 2023-06-21 procesamiento/prod_egp-household.R

@@ -1,0 +1,695 @@
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+frq(df1$SPISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
+sjmisc::frq(df1$isco88spo)
+
+#Relación de Empleo encuestado
+sjmisc::frq(df1$SPEMPREL)
+
+df1$sempspo <- df1$SPEMPREL
+df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
+sjmisc::frq(df1$sempspo)
+
+df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
+sjmisc::frq(df1$sempspo)
+
+# superivison
+sjmisc::frq(df1$SPWRKSUP) #supervision spouse
+df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
+sjmisc::frq(df1$supvisspo)
+
+# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
+df1$tmpisco88 <- df1$isco88
+
+# Replace values in `tmpdf1$isco88` based on specified conditions
+df1$tempisco <- ifelse((df1$isco88spo >= 6100 & df1$isco88spo <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88spo)
+df1$tempisco <- ifelse((df1$isco88spo >= 9200 & df1$isco88spo <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88spo)
+df1$tempisco <- ifelse(df1$isco88spo == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88spo)
+df1$tempisco <- ifelse(df1$isco88spo == 1312 & df1$supvis > 10 & !is.na(df1$supvis), 1222, df1$isco88spo)
+df1$tempisco <- ifelse(df1$isco88spo == 1313 & df1$supvis > 10 & !is.na(df1$supvis), 1223, df1$isco88spo)
[…]

### 2023-06-21 procesamiento/prod_egp-respondent.R

@@ -1,0 +1,706 @@
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+frq(df1$ISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88r <- occupar::isco08to88(df1$ISCO08)
+sjmisc::frq(df1$isco88r)
+
+#Note: the package generate identical recodes as my own manual recoding
+
+#Employment relation encuestado
+sjmisc::frq(df1$EMPREL)
+sjmisc::frq(df1$WORK)
+df1$semp <- df1$EMPREL
+df1$semp <- as.numeric(car::recode(df1$semp, "c(2,3,4)=1;c(1)=2;c(0,8,9)=NA"))
+sjmisc::frq(df1$semp)
+df1$semp <- sjlabelled::set_labels(x = df1$semp,labels=c('Self-employed','Employee'))
+sjmisc::frq(df1$semp)
+
+# superivison
+sjmisc::frq(df1$NEMPLOY) #supervision respondent
+df1$supvis <- as.numeric(car::recode(df1$NEMPLOY,"c(9998,9999)=NA"))
+sjmisc::frq(df1$supvis)
+
+# head(df1[,c('ISCO08','cod_m22',"isco88",'m06','m25',"supvis")],50)
+# View(df1[,c('ISCO08','cod_m22',"isco88",'m06','m25',"supvis")])
+
+# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
+df1$tmpisco88 <- df1$isco88r
+summary(df1$tmpisco88)
+# Replace values in `tmpdf1$isco88` based on specified conditions
+df1$tempisco <- ifelse((df1$isco88r >= 6100 & df1$isco88r <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88r)
+df1$tempisco <- ifelse((df1$isco88r >= 9200 & df1$isco88r <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88r)
+df1$tempisco <- ifelse(df1$isco88r == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88r)
[…]

### 2023-06-21 procesamiento/prod_egp-spouse.R

@@ -1,0 +1,701 @@
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+frq(df1$SPISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
+sjmisc::frq(df1$isco88spo)
+
+#Relación de Empleo encuestado
+sjmisc::frq(df1$SPEMPREL)
+
+df1$sempspo <- df1$SPEMPREL
+df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
+sjmisc::frq(df1$sempspo)
+
+df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
+sjmisc::frq(df1$sempspo)
+
+# superivison
+sjmisc::frq(df1$SPWRKSUP) #supervision spouse
+df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
+sjmisc::frq(df1$supvisspo)
+
+df1$id <- NULL
+df1 <- tibble::rowid_to_column(df1, "id")
+haven::write_dta(data = df1[c("id","isco88spo","sempspo","supvisspo")],
+                 path = "input/data/proc/ocup_spouse.dta")
+df1$id <- NULL
+
+# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
+df1$tmpisco88 <- df1$isco88
+
+# Replace values in `tmpdf1$isco88` based on specified conditions
+df1$tempisco <- ifelse((df1$isco88spo >= 6100 & df1$isco88spo <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88spo)
+df1$tempisco <- ifelse((df1$isco88spo >= 9200 & df1$isco88spo <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88spo)
+df1$tempisco <- ifelse(df1$isco88spo == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88spo)
[…]

### 2023-06-26 procesamiento/prod_analysis.Rmd
update resultados

@@
 load(here::here("input/data/proc/study1.RData"))
+  # Declare ggplot2 features
+ggplot2::theme_set(
+  ggplot2::theme(
+    panel.background = ggplot2::element_rect(fill = "gray85",
+                                             colour = "gray85"),
+    panel.border = ggplot2::element_blank(),
+    axis.text.y = ggplot2::element_text(size = 13,
+                                        hjust = 1),
+    title = ggplot2::element_text(size = 13,
+                                  face = "bold"),
+    legend.text = ggplot2::element_text(size = 12),
+    plot.caption = ggplot2::element_text(size = 10,
+                                         face = "plain",
+                                         hjust = 1)
+  )
+)
 
-df1$country2 <- sjlabelled::to_character(df1$country) 
+df1 %>%
+    dplyr::select(perineq,prefineq,pertransfer,redist) %>%
+    na.omit() %>% 
+    sjPlot::plot_likert(geom.colors = "PuBu",
+                        grid.range  =  c (1.2 , 1),
+                        # title = "a. Perception meritocratic",
+                          geom.size = c(0.62),
+                          catcount = 4,
+                          expand.grid = T,
+                          values  =  "sum.outside",
+                          reverse.colors = T,
+                          reverse.scale = T,
+                          show.n = FALSE,cat.neutral = 3,
+                        show.prc.sign = T,
+                        title = '') +
+    ggplot2::theme(legend.position = "bottom")
+```
+
+```{r welfare}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+df1 %>%
+    dplyr::select(whealth,wcarelder) %>%
+    na.omit() %>% 
+    sjPlot::plot_likert(geom.colors = "PuBu",
+                        grid.range  =  c (0.9 , 0.5),
+                        # title = "a. Perception meritocratic",
+                          geom.size = c(0.62),
+                          catcount = 5,
+                          expand.grid = T,
+                          # values  =  "sum.outside",
+                          reverse.colors = T,
+                          reverse.scale = T,
+                          show.n = FALSE,show.prc.sign = T,
+                        title = 'Who do you think should primarily provide...') +
+    ggplot2::theme(legend.position = "bottom")
+```
+
+```{r redistribution}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+df1$redistF <- factor(df1$redist,levels = 1:5,labels = sjlabelled::get_labels(df1$redist))
+percentage_data <- df1 %>%
+  group_by(country2, redistF) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,redistF,percentage) %>% 
+  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
+  mutate(pct_lab=ifelse(!redistF %in% c("Strongly agree"),NA,pct_lab))
+
+order <- 
+percentage_data %>% 
+  filter(redistF=="Strongly agree") %>% 
+  arrange(percentage) %>% 
+  select(country2)
+
+order$orden <- 1:31
+ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=redistF,group=redistF,label = pct_lab))+
+  geom_bar(stat = 'identity') +
+  # geom_text(position = position_fill(vjust =100)) +
+  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
+  scale_x_discrete(limits=order$country2,name=NULL) +  
+  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
+  theme_classic() +
+  ggtitle(label= "Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes.") + 
+  theme(legend.position = 'bottom',legend.title = element_blank())  +
+  coord_flip()
+
+ggsave(plot = last_plot(),filename = "wredist_cn.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+```{r ealth}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+
+df1$whealthF <- factor(df1$whealth,levels = 1:5,labels = sjlabelled::get_labels(df1$whealth))
+
+percentage_data <- df1 %>%
+  group_by(country2, whealthF) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,whealthF,percentage) %>% 
+  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
+  mutate(pct_lab=ifelse(!whealthF %in% c("Government"),NA,pct_lab))
+
+order <- 
+percentage_data %>% 
+  filter(whealthF=="Government") %>% 
+  arrange(percentage) %>% 
+  select(country2)
+
+order$orden <- 1:32
+ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=whealthF,group=whealthF,label = pct_lab))+
+  geom_bar(stat = 'identity') +
+  geom_text(position = position_fill(vjust = 90)) + 
+  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
+  scale_x_discrete(limits=order$country2,name=NULL) +  
+  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
+  theme_classic() +
+  ggtitle(label= "Who do you think should primarily provide: health") + 
+  theme(legend.position = 'bottom',legend.title = element_blank())  +
+  coord_flip()
+
+ggsave(plot = last_plot(),filename = "whealth_cn.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+```{r elderlycare}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+df1$wcarelderF <- factor(df1$wcarelder,levels = 1:5,labels = sjlabelled::get_labels(df1$wcarelder))
+percentage_data <- df1 %>%
+  group_by(country2, wcarelderF) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,wcarelderF,percentage) %>% 
+  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
+  mutate(pct_lab=ifelse(!wcarelderF %in% c("Government"),NA,pct_lab))
+
+order <- 
+percentage_data %>% 
+  filter(wcarelderF=="Government") %>% 
+  arrange(percentage) %>% 
+  select(country2)
+
+order$orden <- 1:32
+ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=wcarelderF,group=wcarelderF,label = pct_lab))+
+  geom_bar(stat = 'identity') +
+  geom_text(position = position_fill(vjust = 95)) + 
+  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
+  scale_x_discrete(limits=order$country2,name=NULL) +  
+  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
+  theme_classic() +
+  ggtitle(label= "Who do you think should primarily provide: elderly care") + 
+  theme(legend.position = 'bottom',legend.title = element_blank())  +
+  coord_flip()
+
+ggsave(plot = last_plot(),filename = "wcareelder_cn.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
 percentage_data <- df1 %>%
@@
 percentage_data %>% 
-  filter(class5=="Non-skilled manual workers (VIIa+b)") %>% 
+  filter(class5=="Service class (I+II)") %>% 
   arrange(percentage) %>% 
@@
 
-order$orden <- 1:30
-ggplot(percentage_data, aes(x=country2,y=percentage,fill=class5,group=class5))+
+order$orden <- 1:32
+ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=class5,group=class5))+
   geom_bar(stat = 'identity')+
-  # geom_text(aes(label=number_of_errors),position = position_stack(0.5))+
-  scale_y_continuous(labels = NULL) +
-  scale_x_discrete(limits=order$country2) +  
-  scale_fill_ordinal() +
+  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
+  scale_x_discrete(limits=order$country2,name=NULL) +  
+  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
   theme_classic() +
-  theme(legend.position = 'bottom')  +
+  ggtitle(label= "Social class by country") + 
+  theme(legend.position = 'bottom',legend.title = element_blank())  +
   coord_flip()
+
+ggsave(plot = last_plot(),filename = "class5_cn.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
 percentage_data %>% 
-  filter(class3=="Intermediate class (III+IV)") %>% 
+  filter(class3=="Working Class (V+VI+VII)") %>% 
   arrange(percentage) %>% 
@@
 
-order$orden <- 1:30
+order$orden <- 1:32
 ggplot(percentage_data, aes(x=country2,y=percentage,fill=class3,group=class3))+
@@
 ```
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+
+df1 %>% 
+  group_by(class6) %>% 
+  summarise(mean(eindex,na.rm = T))
+
+sjPlot::plot_grpfrq(var.cnt = (df1$eindex),
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+sjPlot::plot_grpfrq(var.cnt = df1$hindex_sta,
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+sjPlot::plot_grpfrq(var.cnt = df1$hindex_10,
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+sjPlot::plot_grpfrq(var.cnt = df1$homclass,
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+sjPlot::plot_grpfrq(var.cnt = df1$socdist,
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+sjPlot::plot_grpfrq(var.cnt = df1$socdist_tot,
+                    var.grp = df1$class6,
+                    type = "boxplot")
+
+df1 %>% 
+  group_by(class6) %>% 
+  summarise(df1$socdist_tot)
+
+df1 %>% 
+  select('redist',"eindex","hindex_sta","hindex_10","homclass","socdist","class6") %>% 
+  group_by(class6) %>% 
+  summarise(mean(homclass,na.rm = T))
+
+# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
+cormat1 <- 
+df1 %>% 
+    select('redist',wcarelder,whealth,isei_tot,isei_max,isei_range,"class6") %>% 
+  na.omit() %>% 
+  polycor::hetcor(parallel = T)
+
+  corrplot::corrplot(cormat1$correlations,
+    method = "color",
+    addCoef.col = "#000390",
+    type = "upper",
+    tl.col = "black",
+    col=colorRampPalette(c("white","#0068DC"))(12),
+    bg = "white",
+    na.label = "-")
+  text(4.7, 0.6, paste0("Source: Authors calculation based on ISSP 2017",
+                             " (N = ",")"),   
+       cex = 0.75)
+
+df1 %>% 
+  select("eindex","hindex_sta","hindex_10","homclass","socdist","class6",class5) %>% 
+  group_by(class5) %>% 
+  summarise(mean(eindex,na.rm = T))
+
+sjPlot::tab_corr((df1[,c("eindex","hindex_sta","hindex_10","homclass","socdist")]),
+                 triangle = "lower") 
+```
+
+```{r}
+df1$country2 <- sjlabelled::to_character(df1$country)
+library(scales)
+
+df1 %>% 
+  filter(!is.na(class5)) %>%
+ggplot(aes(x = class5, y = isei_avg))+
+  geom_boxplot(outlier.shape = NA)+
+  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red")+
+  ylim(25, 75) +
+  facet_wrap(.~country2, scales = "free")+ 
+  scale_x_discrete(labels=c("I+II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
+  ggtitle(sjlabelled::get_label(df1$isei_avg))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+df1 %>% 
+  # filter(!is.na(class5)) %>% 
+ggplot(aes(x = class5, y = hindex_10))+
+  geom_boxplot(outlier.shape = NA)+
+  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red")+
+  ylim(0, 1) +
+  facet_wrap(.~country2, scales = "free")+ 
+  scale_x_discrete(labels=c("I+II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
+  ggtitle(sjlabelled::get_label(df1$hindex_10))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+df1 %>% 
+  filter(!is.na(class6)) %>% 
+ggplot(aes(x = class6, y = hindex_10))+
+  geom_boxplot(outlier.shape = NA)+
+  facet_wrap(.~country2, scales = "free")+ 
+  scale_x_discrete(labels=c("I","II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
+  ggtitle(sjlabelled::get_label(df1$hindex_10))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+levels(df1$class5)
+```
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
+load(here::here("input/data/proc/study1.RData"))
+
+df1$class3 <- forcats::fct_rev(df1$class3)
+df1$class5 <- forcats::fct_rev(df1$class5)
+df1$class6 <- forcats::fct_rev(df1$class6)
+
+dfreg <- df1 %>% select(redist,
+                        isei08,
+                        class3,
+                        eindex,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        ednum,female,agenum,country) %>% na.omit()
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+scapital <- lmer(redist~1 + female+agenum + eindex + (1|country),data=dfreg)
+class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + eindex+isei08+ (1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + eindex*isei08+ (1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + eindex*isei08+ (1+eindex|country),data=dfreg)
+models <- list(scapital,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+texreg::plotreg(full,omit.coef = "(Intercept)")
+
+interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
+  ylab("Network diversity coefficient")+
+  xlab("SES Respondent")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+# en la medida que aumenta el status, el efecto de la diversidad de la red se vuelve positivo.
+# en personas de estatus bajo la diversidad hace que demanden menos redistribucion
+# en personas de estatus alto la diversidad hace que demanden más redistribucion
+```

### 2023-06-26 procesamiento/prod_prep.Rmd
update resultados

@@
 df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
+dfTR <- haven::read_dta(here::here("input/data/original/ZA5521_v1-0-0.dta"))
+dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))
+dfES$c_alphan <- NULL
+dfTR$c_alphan <- NULL
+df2 <- bind_rows(dfES,dfTR)
+df1<- bind_rows(df1,df2)
+
+frq(df1$country)
 ```
 
-```{r generador}
-ocupations <- names(dplyr::select(df1,v1:v10))
+# Welfare attitudes
 
-for (i in ocupations) {
-  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
-  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
+```{r}
+frq(df1$v13)
+df1$redist <- car::recode(df1$v13,recodes = "c(0,8,9)=NA")
+df1$redist <- set_na(df1$redist,na = c(0,8,9))
+df1$redist <- sjmisc::rec(x = df1$redist,rec = "rev")
+sjlabelled::set_label(df1$redist) <- "Preferences goverment redistribution"
+frq(df1$redist)
+
+frq(df1$v15)
+df1$whealth <- car::recode(df1$v15,recodes = "c(0,8,9)=NA")
+df1$whealth <- set_na(df1$whealth,na = c(0,8,9))
+df1$whealth <- sjmisc::rec(x = df1$whealth,rec = "rev")
+sjlabelled::set_label(df1$whealth) <- "Welfare provision: health"
+frq(df1$whealth)
+
+frq(df1$v16)
+df1$wcarelder <- car::recode(df1$v16,recodes = "c(0,8,9)=NA")
+df1$wcarelder <- set_na(df1$wcarelder,na = c(0,8,9))
+df1$wcarelder <- sjmisc::rec(x = df1$wcarelder,rec = "rev")
+sjlabelled::set_label(df1$wcarelder) <- "Welfare provision: elderly care"
+frq(df1$wcarelder)
+# cor(df1[,c("redist","whealth","wcarelder")],use = "complete.obs")
+```
+
+# Inequality perceptions
+
+```{r}
+frq(df1$v59)
+df1$hhdepriv <- car::recode(df1$v59,recodes = "c(0,8,9)=NA")
+df1$hhdepriv <- set_na(df1$hhdepriv,na = c(0,8,9))
+df1$hhdepriv <- sjmisc::rec(x = df1$hhdepriv,rec = "rev")
+sjlabelled::set_label(df1$hhdepriv) <- "Household economic deprivation (household difficulties)"
+frq(df1$hhdepriv)
+
+frq(df1$v11)
+df1$perineq <- car::recode(df1$v11,recodes = "c(0,8,9)=NA")
+df1$perineq <- set_na(df1$perineq,na = c(0,8,9))
+df1$perineq <- sjmisc::rec(x = df1$perineq,rec = "rev")
+sjlabelled::set_label(df1$perineq) <- "Perceived economic inequality (Inc. diff. too large)"
+frq(df1$perineq)
+
+frq(df1$v12)
+df1$prefineq <- car::recode(df1$v12,recodes = "c(0,8,9)=NA")
+df1$prefineq <- set_na(df1$prefineq,na = c(0,8,9))
+df1$prefineq <- sjmisc::rec(x = df1$prefineq,rec = "rev")
+sjlabelled::set_label(df1$prefineq) <- "Preference inequality (society has to be fair)"
+frq(df1$prefineq)
+
+frq(df1$v14)
+df1$pertransfer <- car::recode(df1$v14,recodes = "c(0,8,9)=NA")
+df1$pertransfer <- set_na(df1$pertransfer,na = c(0,8,9))
+df1$pertransfer <- sjmisc::rec(x = df1$pertransfer,rec = "rev")
+sjlabelled::set_label(df1$pertransfer) <- "Perception about welfare (people become lazy)"
+frq(df1$pertransfer)
+```
+
+# Perceived integration
+
+```{r}
+frq(df1$v31)
+df1$pi_compa <- car::recode(df1$v31,recodes = "c(0,8,9)=NA")
+df1$pi_compa <- set_na(df1$pi_compa,na = c(0,8,9))
+df1$pi_compa <- sjmisc::rec(x = df1$pi_compa,rec = "rev")
+sjlabelled::set_label(df1$pi_compa) <- "Perceived integration: companionship lacking"
+frq(df1$pi_compa)
+
+frq(df1$v32)
+df1$pi_isola <- car::recode(df1$v32,recodes = "c(0,8,9)=NA")
+df1$pi_isola <- set_na(df1$pi_isola,na = c(0,8,9))
+df1$pi_isola <- sjmisc::rec(x = df1$pi_isola,rec = "rev")
+sjlabelled::set_label(df1$pi_isola) <- "Perceived integration: isolated from others"
+frq(df1$pi_compa)
+
+frq(df1$v33)
+df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
+df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
+df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
+sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
+frq(df1$pi_left)
+```
+
+# Social status
+
+```{r income-hhold}
+income_country <- names(df1 %>% select(ends_with("_INC")))
+lapply(df1[,income_country], table)
+for (i in income_country) {
+  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  df1[[i]] <- as.numeric(df1[[i]])
   }
 
-frq(df1$v1)
-df1$busdriver <- as.numeric(car::recode(df1$v1,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$busdriver) <- "Know: bus/lorry driver" 
-frq(df1$busdriver)
+lapply(df1[,income_country], table)  # Ok el recode de ingresos familiares 
+# Crear variable ingresos unica 
+df1 <- df1 %>% mutate(income = coalesce(AT_INC,AU_INC,CH_INC,CN_INC,CZ_INC,DE_INC,DK_INC,ES_INC,FI_INC,FR_INC,GB_INC,HR_INC,HU_INC,IL_INC,IN_INC,IS_INC,
+                                        JP_INC,LT_INC,MX_INC,NZ_INC,PH_INC,RU_INC,SE_INC,SI_INC,SK_INC,SR_INC,TH_INC,TW_INC,US_INC,ZA_INC))
 
-frq(df1$v2)
-df1$ceo <- as.numeric(car::recode(df1$v2,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$ceo) <- "Know: CEO large company" 
-frq(df1$ceo)
+frq(df1$income==0)
+frq(df1$HOMPOP)
+df1$hhpop <- as.numeric(df1$HOMPOP) 
+df1$hhpop[df1$hhpop %in%c(0,97,99)] <- NA
+frq(df1$hhpop)
+df1$incomepcap <- as.numeric(df1$income/df1$hhpop) # Ingreso per capita del hogar
 
-frq(df1$v3)
-df1$cleaner <- as.numeric(car::recode(df1$v3,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$cleaner) <- "Know: home or office cleaner" 
-frq(df1$cleaner)
+df1 <- df1 %>%group_by(country)  %>% mutate(D10pc=ntile(incomepcap,10),
+                                              Q05pc=ntile(incomepcap,5),
+                                              zincpc=scale(incomepcap,center = TRUE),
+                                              logincpc=log(incomepcap)) %>% ungroup()
 
-frq(df1$v4)
-df1$hairbarber <- as.numeric(car::recode(df1$v4,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$hairbarber) <- "Know: hairdresser/barber" 
-frq(df1$hairbarber)
-
-frq(df1$v5)
-df1$hrmanager <- as.numeric(car::recode(df1$v5,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$hrmanager) <- "Know: human resource manager" 
-frq(df1$hrmanager)
-
-frq(df1$v6)
-df1$lawyer <- as.numeric(car::recode(df1$v6,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$lawyer) <- "Know: lawyer" 
-frq(df1$lawyer)
-
-frq(df1$v7)
-df1$mechanic <- as.numeric(car::recode(df1$v7,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$mechanic) <- "Know: car mechanic" 
-frq(df1$mechanic)
-
-frq(df1$v8)
-df1$nurse <- as.numeric(car::recode(df1$v8,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$nurse) <- "Know: nurse" 
-frq(df1$mechanic)
-
-frq(df1$v9)
-df1$police <- as.numeric(car::recode(df1$v9,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$police) <- "Know: police officer" 
-frq(df1$police)
-
-frq(df1$v10)
-df1$teacher <- as.numeric(car::recode(df1$v10,"1:3=1;4=0")) 
-sjlabelled::set_label(df1$teacher) <- "Know: school teacher" 
-frq(df1$teacher)
-
-# Total of known occupations
-isei_ocupnames<- names(select(df1,busdriver:teacher))
-df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
-summary(df1$know_total)
-sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
-sjPlot::plot_frq(df1$know_total,type = 'density')
+sjlabelled::set_label(df1$D10pc) <- "Household income (D10)"
+sjlabelled::set_label(df1$Q05pc) <- "Household income (Q05)"
+sjlabelled::set_label(df1$zincpc) <- "Household income (zscore)"
+sjlabelled::set_label(df1$logincpc) <- "Household income (log)"
 ```
 
-```{r isei-generador}
-df1$isei_busdriver <- as.numeric(ifelse(df1$busdriver ==1,37,NA)) 
-sjlabelled::set_label(df1$isei_busdriver) <- "ISEI: bus/lorry driver" 
-frq(df1$isei_busdriver)
+```{r income-respondent}
+income_country <- names(df1 %>% select(ends_with("_RINC")))
+lapply(df1[,income_country], table)
+for (i in income_country) {
+  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  df1[[i]] <- as.numeric(df1[[i]])
+  }
 
-df1$isei_ceo <- as.numeric(ifelse(df1$ceo==1,70,NA)) 
-sjlabelled::set_label(df1$isei_ceo) <- "ISEI: CEO large company" 
-frq(df1$isei_ceo)
+lapply(df1[,income_country], table)  # Ok el recode de ingresos familiares 
+# Crear variable ingresos unica 
+df1 <- df1 %>% mutate(incomer = coalesce(AT_RINC,AU_RINC,
+                                        CH_RINC, CN_RINC,
+                                        CZ_RINC, DE_RINC,
+                                        DK_RINC, ES_RINC,
+                                        FI_RINC, FR_RINC,
+                                        GB_RINC, HR_RINC,
+                                        HU_RINC, IL_RINC,
+                                        IN_RINC, IS_RINC,
+                                        JP_RINC, LT_RINC,
+                                        MX_RINC, NZ_RINC,
+                                        PH_RINC, RU_RINC,
+                                        SE_RINC, SI_RINC,
+                                        SK_RINC, SR_RINC,
+                                        TH_RINC, TW_RINC,
+                                        US_RINC, ZA_RINC))
+frq(df1$incomer==0)
 
-df1$isei_cleaner <- as.numeric(ifelse(df1$cleaner==1,17,NA)) 
-sjlabelled::set_label(df1$isei_cleaner) <- "ISEI: home or office cleaner" 
-frq(df1$isei_cleaner)
-
-df1$isei_hairbarber <- as.numeric(ifelse(df1$hairbarber==1,32,NA)) 
-sjlabelled::set_label(df1$isei_hairbarber) <- "ISEI: hairdresser/barber" 
-frq(df1$isei_hairbarber)
-
-df1$isei_hrmanager <- as.numeric(ifelse(df1$hrmanager==1,68,NA)) 
-sjlabelled::set_label(df1$isei_hrmanager) <- "ISEI: human resource manager" 
-frq(df1$isei_hrmanager)
-
-df1$isei_lawyer <- as.numeric(ifelse(df1$lawyer==1,85,NA)) 
-sjlabelled::set_label(df1$isei_lawyer) <- "ISEI: lawyer" 
-frq(df1$isei_lawyer)
-
-df1$isei_mechanic <- as.numeric(ifelse(df1$mechanic==1,38,NA)) 
-sjlabelled::set_label(df1$isei_mechanic) <- "ISEI: car mechanic" 
-frq(df1$isei_mechanic)
-
-df1$isei_nurse <- as.numeric(ifelse(df1$nurse==1,48,NA)) 
-sjlabelled::set_label(df1$isei_nurse) <- "ISEI: nurse" 
-frq(df1$isei_nurse)
-
-df1$isei_police <- as.numeric(ifelse(df1$police==1,53,NA)) 
-sjlabelled::set_label(df1$isei_police) <- "ISEI: police officer" 
-frq(df1$isei_police)
-
-df1$isei_teacher <- as.numeric(ifelse(df1$teacher==1,63,NA)) 
-sjlabelled::set_label(df1$isei_teacher) <- "ISEI: school teacher" 
-frq(df1$isei_teacher)
+df1 <- df1 %>%group_by(country) %>% mutate(D10r=ntile(incomer,10),
+                                              Q05r=ntile(incomer,5),
+                                              zincpcr=scale(incomer,center = TRUE),
+                                              logincr=log(incomer)) %>% ungroup()
+frq(df1$incomer)
+frq(df1$incomepcap)
+# Single household 
+df1$incomerep <- ifelse(df1$hhpop==1 & is.na(df1$incomepcap),df1$incomer,df1$incomepcap)
+frq(is.na(df1$incomerep))
+frq(df1$incomerep==0)
+df1[,c("incomer","hhpop","incomepcap","incomerep")] %>% arrange(incomepcap,hhpop) %>% head()
+df1$incomerep <- ifelse(df1$hhpop==1 & df1$incomerep==0,df1$incomer,df1$incomerep)
+frq(df1$incomerep==0)
+df1[,c("incomer","hhpop","incomepcap","incomerep")] %>% arrange(incomepcap,hhpop) %>% head()
 ```
 
-```{r social-capital}
-# Social capital measures
-isei_ocupnames<- names(select(df1,starts_with("isei_")))
+```{r}
+frq(df1$EDUCYRS)
+df1$edyears <- as.numeric(car::recode(df1$EDUCYRS,recodes = "98:99=NA")) 
+sjlabelled::set_label(df1$edyear) <- "Years of schooling"
+frq(df1$edyears)
 
-# number of high status contacts
-df1$n_high <- 
-  rowSums(x = select(df1,c("lawyer","hrmanager","ceo")),na.rm = T)
-sjlabelled::set_label(df1$n_high) <- 'Number of high status contacts'
-sjPlot::plot_frq(df1$n_high,type = 'density')
-
-# percentage of high status contacts
-
-df1$pct_high <- (df1$n_high/df1$know_total)*100
-sjlabelled::set_label(df1$df1$pct_high ) <- 'Percentage of high status contacts'
-sjPlot::plot_frq(df1$pct_high,type = 'density')
-
-# number of middle status contacts
-df1$n_middle <-
-  rowSums(x = select(df1,c("teacher","police","nurse")),na.rm = T)
-sjlabelled::set_label(df1$n_middle) <- 'Number of middle status contacts'
-sjPlot::plot_frq(df1$n_middle,type = 'density')
-
-# percentage of middle status contacts
-df1$pct_middle <- (df1$n_middle/df1$know_total)*100
-sjlabelled::set_label(df1$pct_middle) <- 'Percentage of middle status contacts'
-sjPlot::plot_frq(df1$pct_middle,type = 'density')
-
-# number of low status contacts
-# df1$n_low <- 
-#   rowSums(x = select(df1,c("n_waiter","n_carmech","n_taxi","n_stvend","n_cleaner")),na.rm = T)
-df1$n_low <- 
-  rowSums(x = select(df1,c("mechanic","busdriver","hairbarber","cleaner")),na.rm = T)
-sjlabelled::set_label(df1$n_low) <- 'Number of low status contacts'
-sjPlot::plot_frq(df1$n_low,type = 'density')
-
-# percentage of low status contacts
-df1$pct_low <- (df1$n_low/df1$know_total)*100
-sjlabelled::set_label(df1$pct_low) <- 'Percentage of low status contacts'
-sjPlot::plot_frq(df1$pct_low,type = 'density')
-
-# Average ISEI 
-df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) #REVISAR NO DEBERIA CONTENER 0
-sjlabelled::set_label(df1$isei_avg) <- 'Average contact prestige'
-summary(df1$isei_avg)
-
-sjPlot::plot_frq(df1$isei_avg,type = 'density')
-
-# Total ISEI 
-df1$isei_tot <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
-sjlabelled::set_label(df1$isei_tot) <- 'Total contact prestige'
-summary(df1$isei_tot)
-sjPlot::plot_frq(df1$isei_tot,type = 'density')
-
-# skimr::skim(df1$isei_tot/df1$n_total)
-# skimr::skim(df1$isei_tot/df1$know_total)
-# skimr::skim(df1$isei_avg)
-
-# max ISEI 
-df1 <- df1 %>% 
-mutate(isei_max = do.call(pmax, c(select(., isei_ocupnames), na.rm = TRUE)))
-sjlabelled::set_label(df1$isei_max) <- 'Maximum contact prestige'
-sjmisc::frq(df1$isei_max)
-sjPlot::plot_frq(df1$isei_max)
-
-# min ISEI
-df1 <- df1 %>% 
-mutate(isei_min = do.call(pmin, c(select(., isei_ocupnames), na.rm = TRUE)))
-sjlabelled::set_label(df1$isei_min) <- 'Minimum contact prestige'
-sjmisc::frq(df1$isei_min)
-sjPlot::plot_frq(df1$isei_min)
-
-# range ISEI
-table(df1$know_total>=2)
-df1$isei_range <- ifelse(df1$know_total>=2,(df1$isei_max - df1$isei_min),no = NA)
-
-sjlabelled::set_label(df1$isei_range) <- 'Range contact prestige'
-sjmisc::frq(df1$isei_range)
-# sjPlot::plot_frq(df1$isei_range)
-# df1 %>% select(starts_with("isei_")) %>%View
-
-# ggpairs(df1[,c("isei_avg","isei_max","isei_range",
-#                  "know_total","n_high","n_middle","n_low",
-#                  "pct_high","pct_middle","pct_low")],
-#         title="Social capital measures")
-
+frq(df1$DEGREE)
+df1$ednum <- car::recode(df1$DEGREE+1,"10=NA")
+sjlabelled::set_label(df1$ednum) <- "Educational level"
+frq(df1$ednum)
+df1$edcat <- car::recode(df1$ednum,recodes = "1:2='Primary or less';
+                         3:4='Secondary';
+                         5='Terciary short-cycle';
+                         6:7='Terciary or higher';
+                         9=NA",
+                         levels =c('Primary or less',
+                                   'Secondary',
+                                   'Post-secondary non-terciary',
+                                   'Terciary or higher'),as.factor = T)
+sjlabelled::set_label(df1$edcat) <- "Educational level"
+frq(df1$edcat)
 ```
 
-# Occupational status
+# Occupational variables
+
+```{r labour-status}
+frq(df1$MAINSTAT)
+df1$labst <- car::recode(
+  as.numeric(df1$MAINSTAT),
+  recodes = "1='In labour force';2:9='Not in labour force';c(0,99)='No information'",
+  levels = c('In labour force', 'Not in labour force', 'No information'),
+  as.factor = T
+)
+sjlabelled::set_label(df1$labst) <- "Occupational status"
+frq(df1$labst)
+```
+
+```{r union}
+frq(df1$WORK)
+frq(df1$UNION)
+df1$union <- car::recode(as.numeric(df1$UNION),
+                         recodes= "1:2='Yes';c(0,3,7,8)='No';9=NA",
+                         levels = c("No","Yes"))
+frq(df1$union)
+```
 
@@
 summary(df1$isei08)
+sjlabelled::set_label(df1$isei08) <- "ISEI respondent"
 
@@
 summary(df1$isei08sp)
+sjlabelled::set_label(df1$isei08sp) <- "ISEI spouse"
 ```
-
-# Class scheme
 
@@
 
+# Networks
+
+```{r generador}
+ocupations <- names(dplyr::select(df1,v1:v10))
+
+for (i in ocupations) {
+  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
+  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
+}http://127.0.0.1:19795/graphics/88e884e6-abc7-4561-b89b-4ef0590bcf13.png
+
+frq(df1$v1)
+df1$busdriver <- as.numeric(car::recode(df1$v1,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$busdriver) <- "Know: bus/lorry driver" 
+frq(df1$busdriver)
+
+frq(df1$v2)
+df1$ceo <- as.numeric(car::recode(df1$v2,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$ceo) <- "Know: CEO large company" 
+frq(df1$ceo)
+
+frq(df1$v3)
+df1$cleaner <- as.numeric(car::recode(df1$v3,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$cleaner) <- "Know: home or office cleaner" 
+frq(df1$cleaner)
+
+frq(df1$v4)
+df1$hairbarber <- as.numeric(car::recode(df1$v4,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hairbarber) <- "Know: hairdresser/barber" 
+frq(df1$hairbarber)
+
+frq(df1$v5)
+df1$hrmanager <- as.numeric(car::recode(df1$v5,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hrmanager) <- "Know: human resource manager" 
+frq(df1$hrmanager)
+
+frq(df1$v6)
+df1$lawyer <- as.numeric(car::recode(df1$v6,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$lawyer) <- "Know: lawyer" 
+frq(df1$lawyer)
+
+frq(df1$v7)
+df1$mechanic <- as.numeric(car::recode(df1$v7,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$mechanic) <- "Know: car mechanic" 
+frq(df1$mechanic)
+
+frq(df1$v8)
+df1$nurse <- as.numeric(car::recode(df1$v8,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$nurse) <- "Know: nurse" 
+frq(df1$mechanic)
+
+frq(df1$v9)
+df1$police <- as.numeric(car::recode(df1$v9,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$police) <- "Know: police officer" 
+frq(df1$police)
+
+frq(df1$v10)
+df1$teacher <- as.numeric(car::recode(df1$v10,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$teacher) <- "Know: school teacher" 
+frq(df1$teacher)
+
+# Total of known occupations
+isei_ocupnames<- names(select(df1,busdriver:teacher))
+df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+summary(df1$know_total)
+sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
+```
+
+```{r isei-generador}
+df1$isei_busdriver <- as.numeric(ifelse(df1$busdriver ==1,37,NA)) 
+sjlabelled::set_label(df1$isei_busdriver) <- "ISEI: bus/lorry driver" 
+frq(df1$isei_busdriver)
+
+df1$isei_ceo <- as.numeric(ifelse(df1$ceo==1,70,NA)) 
+sjlabelled::set_label(df1$isei_ceo) <- "ISEI: CEO large company" 
+frq(df1$isei_ceo)
+
+df1$isei_cleaner <- as.numeric(ifelse(df1$cleaner==1,17,NA)) 
+sjlabelled::set_label(df1$isei_cleaner) <- "ISEI: home or office cleaner" 
+frq(df1$isei_cleaner)
+
+df1$isei_hairbarber <- as.numeric(ifelse(df1$hairbarber==1,32,NA)) 
+sjlabelled::set_label(df1$isei_hairbarber) <- "ISEI: hairdresser/barber" 
+frq(df1$isei_hairbarber)
+
+df1$isei_hrmanager <- as.numeric(ifelse(df1$hrmanager==1,68,NA)) 
+sjlabelled::set_label(df1$isei_hrmanager) <- "ISEI: human resource manager" 
+frq(df1$isei_hrmanager)
+
+df1$isei_lawyer <- as.numeric(ifelse(df1$lawyer==1,85,NA)) 
+sjlabelled::set_label(df1$isei_lawyer) <- "ISEI: lawyer" 
+frq(df1$isei_lawyer)
+
+df1$isei_mechanic <- as.numeric(ifelse(df1$mechanic==1,38,NA)) 
+sjlabelled::set_label(df1$isei_mechanic) <- "ISEI: car mechanic" 
+frq(df1$isei_mechanic)
+
+df1$isei_nurse <- as.numeric(ifelse(df1$nurse==1,48,NA)) 
+sjlabelled::set_label(df1$isei_nurse) <- "ISEI: nurse" 
+frq(df1$isei_nurse)
+
+df1$isei_police <- as.numeric(ifelse(df1$police==1,53,NA)) 
+sjlabelled::set_label(df1$isei_police) <- "ISEI: police officer" 
+frq(df1$isei_police)
+
+df1$isei_teacher <- as.numeric(ifelse(df1$teacher==1,63,NA)) 
+sjlabelled::set_label(df1$isei_teacher) <- "ISEI: school teacher" 
+frq(df1$isei_teacher)
+```
+
+```{r social-capital}
+# Social capital measures
+isei_ocupnames<- names(select(df1,starts_with("isei_")))
+
+# number of high status contacts
+df1$n_high <- 
+  rowSums(x = select(df1,c("lawyer","hrmanager","ceo")),na.rm = T)
+sjlabelled::set_label(df1$n_high) <- 'Number of high status contacts'
+# sjPlot::plot_frq(df1$n_high,type = 'density')
+
+# percentage of high status contacts
+
+df1$pct_high <- (df1$n_high/df1$know_total)*100
+sjlabelled::set_label(df1$df1$pct_high ) <- 'Percentage of high status contacts'
+# sjPlot::plot_frq(df1$pct_high,type = 'density')
+
+# number of middle status contacts
+df1$n_middle <-
+  rowSums(x = select(df1,c("teacher","police","nurse")),na.rm = T)
+sjlabelled::set_label(df1$n_middle) <- 'Number of middle status contacts'
+# sjPlot::plot_frq(df1$n_middle,type = 'density')
+
+# percentage of middle status contacts
+df1$pct_middle <- (df1$n_middle/df1$know_total)*100
+sjlabelled::set_label(df1$pct_middle) <- 'Percentage of middle status contacts'
+# sjPlot::plot_frq(df1$pct_middle,type = 'density')
+
+# number of low status contacts
+# df1$n_low <- 
+#   rowSums(x = select(df1,c("n_waiter","n_carmech","n_taxi","n_stvend","n_cleaner")),na.rm = T)
+df1$n_low <- 
+  rowSums(x = select(df1,c("mechanic","busdriver","hairbarber","cleaner")),na.rm = T)
+sjlabelled::set_label(df1$n_low) <- 'Number of low status contacts'
+# sjPlot::plot_frq(df1$n_low,type = 'density')
+
+# percentage of low status contacts
+df1$pct_low <- (df1$n_low/df1$know_total)*100
+sjlabelled::set_label(df1$pct_low) <- 'Percentage of low status contacts'
+# sjPlot::plot_frq(df1$pct_low,type = 'density')
+
+# Average ISEI 
+df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) #REVISAR NO DEBERIA CONTENER 0
+sjlabelled::set_label(df1$isei_avg) <- 'Average contact prestige'
+summary(df1$isei_avg)
+
+# sjPlot::plot_frq(df1$isei_avg,type = 'density')
+
+# Total ISEI 
+df1$isei_tot <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+sjlabelled::set_label(df1$isei_tot) <- 'Total contact prestige'
+summary(df1$isei_tot)
+# sjPlot::plot_frq(df1$isei_tot,type = 'density')
+
+# skimr::skim(df1$isei_tot/df1$n_total)
+# skimr::skim(df1$isei_tot/df1$know_total)
+# skimr::skim(df1$isei_avg)
+
+# max ISEI 
+df1 <- df1 %>% 
+mutate(isei_max = do.call(pmax, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_max) <- 'Maximum contact prestige'
+sjmisc::frq(df1$isei_max)
+# sjPlot::plot_frq(df1$isei_max)
+
+# min ISEI
+df1 <- df1 %>% 
+mutate(isei_min = do.call(pmin, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_min) <- 'Minimum contact prestige'
+sjmisc::frq(df1$isei_min)
+# sjPlot::plot_frq(df1$isei_min)
+
+# range ISEI
+table(df1$know_total>=2)
+df1$isei_range <- ifelse(df1$know_total>=2,(df1$isei_max - df1$isei_min),no = NA)
+
+sjlabelled::set_label(df1$isei_range) <- 'Range contact prestige'
+sjmisc::frq(df1$isei_range)
+# sjPlot::plot_frq(df1$isei_range)
+# df1 %>% select(starts_with("isei_")) %>%View
+
+cor(df1[,c("isei_avg","isei_max","isei_range",
+                 "know_total","n_high","n_middle","n_low",
+                 "pct_high","pct_middle","pct_low")],use = "complete.obs")
+
+```
+
+```{r heterogeneity}
+isei_ocupnames<- names(select(df1,busdriver:teacher))
+
+df1$hindex_sta<- 
+as.numeric(
+  1 - (
+    #p1^2
+    (df1$n_high / df1$know_total)^2 +
+    #p2^2
+    (df1$n_middle / df1$know_total)^2 +
+    #p3^2
+    (df1$n_low / df1$know_total)^2
+    )
+  )
+
+sjlabelled::set_label(df1$hindex_sta) <- "D-index: status groups"
+
+df1$hindex_10<- 
+as.numeric(
+  1 - (
+    #p1^2
+    (df1$busdriver/df1$know_total)^2 +
+    #p2^2
+    (df1$ceo / df1$know_total)^2 +
+    #p3^2
+    (df1$cleaner / df1$know_total)^2 +
+    #p3^2
+    (df1$hairbarber / df1$know_total)^2 +
+     #p3^2
+    (df1$hrmanager / df1$know_total)^2 +
+    #p3^2
+    (df1$lawyer / df1$know_total)^2+
+    #p3^2
+    (df1$mechanic / df1$know_total)^2+
+    #p3^2
+    (df1$nurse / df1$know_total)^2+
+    #p3^2
+    (df1$police / df1$know_total)^2+    
+    #p3^2
+    (df1$teacher / df1$know_total)^2        
+    )
+  )
+
+sjlabelled::set_label(df1$hindex_10) <- "D-index: 10 ocupations"
+```
+
+```{r homogeneity}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+frq(df1$outgroup)
+
+df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex) <- "EI homophily index"
+frq(df1$eindex)
+
+df1 %>% select(class3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass) <- "Class homogeneity"
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r social distance}
+
+df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
+df1$dis_ceo <- df1$isei08 - df1$isei_ceo
+df1$dis_cleaner <- df1$isei08 - df1$isei_cleaner
+df1$dis_hairbarber <- df1$isei08 - df1$isei_hairbarber
+df1$dis_hrmanager <- df1$isei08 - df1$isei_hrmanager
+df1$dis_lawyer <- df1$isei08 - df1$isei_lawyer
+df1$dis_mechanic <- df1$isei08 - df1$isei_mechanic
+df1$dis_nurse <- df1$isei08 - df1$isei_nurse
+df1$dis_police <- df1$isei08 - df1$isei_police
+df1$dis_teacher <- df1$isei08 - df1$isei_teacher
+
+# 88 - 37  = 51
+# 88 - 17  = 71
+
+df1$socdist<- rowMeans(x = df1 %>% select(starts_with("dis_")),na.rm = T)
+sjlabelled::set_label(df1$socdist) <- "Social distance: ISEI (respondent - contacts)"
+sjPlot::plot_frq(df1$socdist,type = "histogram")
+
+df1$socdist_tot<- (df1$isei08- df1$isei_avg)
+sjPlot::plot_frq(df1$socdist_tot,type = "histogram")
+sjlabelled::set_label(df1$socdist_tot) <- "Social distance: ISEI (respondent - contacts)"
+
+#higher values represent higher socioeconomic distance from my contacts.
+In other words, higher values means that in average, my contacts are more different from me in terms of socioeconomic status (ISEI), while lower values represent higher homogeneity.
+```
+
+# Demographics
+
+```{r demographics}
+df1$agenum <- as.numeric(car::recode(df1$AGE,recodes = "999=NA",as.numeric = T))
+sjlabelled::set_label(df1$agenum) <- "Age in years"
+frq(df1$agenum)
+
+frq(df1$SEX)
+df1$female <- car::recode(as.numeric(df1$SEX),"2='Female';1='Male';9=NA",
+                          levels = c('Male','Female'),as.factor = T)
+frq(df1$female)
+```
+
+```{r}
+names(df1)
+```
+
 ```{r}

### 2023-07-24 procesamiento/prod_analysis.Rmd
update weak strong ties

@@
 
-```{r}
+# Descriptive
+
+```{r ineq-attitudes}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
     ggplot2::theme(legend.position = "bottom")
+
+ggsave(plot = last_plot(),filename = "ineq-attitudes.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
 load(here::here("input/data/proc/study1.RData"))
@@
     sjPlot::plot_likert(geom.colors = "PuBu",
-                        grid.range  =  c (0.9 , 0.5),
+                        grid.range  =  c (1 , 1),
                         # title = "a. Perception meritocratic",
@@
                         title = 'Who do you think should primarily provide...') +
+    scale_colour_discrete(labels = function(x) str_wrap(x, width = 10))+
     ggplot2::theme(legend.position = "bottom")
+
+ggsave(plot = last_plot(),filename = "welf-attitudes.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 16)
 ```
+
+```{r perc-integration}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
+load(here::here("input/data/proc/study1.RData"))
+df1 %>%
+    dplyr::select(starts_with("pi_")) %>%
+    na.omit() %>% 
+    sjPlot::plot_likert(geom.colors = "PuBu",
+                        grid.range  =  c (0.2 , 1),
+                        # title = "a. Perception meritocratic",
+                          geom.size = c(0.62),
+                          catcount = 5,
+                          expand.grid = T,
+                          # values  =  "sum.outside",
+                          reverse.colors = T,
+                          reverse.scale = T,
+                          show.n = FALSE,show.prc.sign = T,sort.frq = "pos.asc",
+                        title = 'How often in the past 4 weeks have you felt that...') +
+    scale_colour_discrete(labels = function(x) str_wrap(x, width = 10))+ 
+    ggplot2::theme(legend.position = "bottom")
+
+ggsave(plot = last_plot(),filename = "perc-integration.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+df1 %>%
+    dplyr::select(starts_with("pi_")) %>% 
+  psych::alpha()
+```
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
+load(here::here("input/data/proc/study1.RData"))
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+dfcor <- 
+df1 %>%
+    dplyr::select(pi_nteg,class6,sstatus,redist) %>% 
+  as.data.frame()
+
+levels(df1$class6)
+table(df1$know_total)
+table(df1$n_high)
+table(df1$n_middle)
+table(df1$n_low)
+
+# dfcor$hhdepriv <- as.factor(dfcor$hhdepriv)
+# dfcor$sstatus <- as.numeric(dfcor$sstatus)
+cormat<- polycor::hetcor(dfcor,parallel = T,thresholds = F)
+
+jpeg(file=here::here("output/network-structure.jpeg"),units = "cm",width = 17,height = 15,res = 300)
+# Set up the layout for the multi-panel plot
+par(mfrow = c(1, 1))
+# Create the histograms
+# hist(df1$prestige, main = sjlabelled::get_label(df1$prestige),xlab = NULL)
+# hist(df1$diversity, main = sjlabelled::get_label(df1$diversity),xlab = NULL)
+hist(df1$homclass, main = sjlabelled::get_label(df1$homclass),xlab = NULL)
+dev.off()
+
+sjPlot::plot_frq(df1$class3,show.n = F) +
+  theme_grey()
+ggsave(plot = last_plot(),filename = "class6.png",device = "png",
+       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 10)
+
+jpeg(file=here::here("output/n_known.jpeg"),units = "cm",width = 15,height = 15,res = 300)
+# Set up the layout for the multi-panel plot
+par(mfrow = c(2, 2))
+
+# Create the histograms
+hist(df1$n_low, main = sjlabelled::get_label(df1$n_low),xlab = NULL)
+hist(df1$n_middle, main = sjlabelled::get_label(df1$n_middle),xlab = NULL)
+hist(df1$n_high, main = sjlabelled::get_label(df1$n_high),xlab = NULL)
+hist(df1$know_total, main = sjlabelled::get_label(df1$know_total),xlab = NULL)
+# hist(df1$prestige, main = sjlabelled::get_label(df1$prestige),xlab = NULL)
+# hist(df1$diversity, main = sjlabelled::get_label(df1$diversity),xlab = NULL)
+dev.off()
+
+sjPlot::plot_grpfrq(var.cnt = df1$know_total,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
+ggsave(plot = last_plot(),filename = "known_total_class6.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
+
+sjPlot::plot_grpfrq(var.cnt = df1$diversity,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
+ggsave(plot = last_plot(),filename = "diversity_class6.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
+
+sjPlot::plot_grpfrq(var.cnt = df1$prestige,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
+ggsave(plot = last_plot(),filename = "prestige_class6.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
+
+sjPlot::plot_grpfrq(var.cnt = df1$homclass,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
+ggsave(plot = last_plot(),filename = "homclass_class6.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
+
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
+sjPlot::plot_grpfrq(var.cnt = df1$pi_nteg,var.grp = df1$class3,type = 'box',geom.colors = "Blues",ylim = c(1,5))
+ggsave(plot = last_plot(),filename = "pint_class3.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
+```
+
+# Descriptive x country
 
@@
 load(here::here("input/data/proc/study1.RData"))
+df1$country<- as.numeric(df1$country)
 df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
@@
        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+resits_count <- df1 %>%
+  group_by(country,country2) %>%
+  summarise(redist = mean(redist,na.rm = T),
+            homclass = mean(homclass,na.rm = T),
+            pi_nteg = mean(pi_nteg,na.rm = T),
+            pi_ntegm = median(pi_nteg,na.rm = T)
+            ) %>%
+  na.omit()
+
+cor(df1[,c("redist","homclass","pi_nteg")],use = "complete.obs")
+
+ggplot(data = resits_count,aes(x = homclass,y = redist,label=country2)) +
+  xlab("Class-based homogeneity") +
+  ylab("Redistributive preferences")+  
+  labs(alt = "A",caption = "r=0.42") +  
+  geom_smooth(method = "lm") +
+  geom_text()
+
+myorder <-  resits_count$country2[order(resits_count$homclass)]
+ggplot(data = resits_count,aes(x =country2,y = homclass)) + 
+  geom_segment(aes(x=country2, xend=country2, y=0, yend=homclass), color="black") +
+  geom_point() +
+  scale_x_discrete(limits=myorder) +
+  ylab("Class-based homogeneity")+
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 45))
+
+ggsave(plot = last_plot(),filename = "homclass_cn.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
+
+myorder <-  resits_count$country2[order(resits_count$pi_nteg)]
+ggplot(data = resits_count,aes(x =country2,y = pi_nteg)) + 
+  geom_segment(aes(x=country2, xend=country2, y=0, yend=pi_nteg), color="black") +
+  geom_point() +
+  scale_x_discrete(limits=myorder) +
+  ylab("Perceived isolation")+
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 45))
+
+ggsave(plot = last_plot(),filename = "p_isolat_cn.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 ```
 
-```{r ealth}
+```{r health}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
 
-sjPlot::plot_grpfrq(var.cnt = (df1$eindex),
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-sjPlot::plot_grpfrq(var.cnt = df1$hindex_sta,
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-sjPlot::plot_grpfrq(var.cnt = df1$hindex_10,
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-sjPlot::plot_grpfrq(var.cnt = df1$homclass,
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-sjPlot::plot_grpfrq(var.cnt = df1$socdist,
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-sjPlot::plot_grpfrq(var.cnt = df1$socdist_tot,
-                    var.grp = df1$class6,
-                    type = "boxplot")
-
-df1 %>% 
-  group_by(class6) %>% 
-  summarise(df1$socdist_tot)
-
 df1 %>% 
@@
 
-```{r}
+# Modelos
+
+dicotomizar homogeneidad en 1=50% similar,49% similar
+
+```{r isei}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
+pacman::p_load(sjmisc,ggplot2,lme4,interplot)
 load(here::here("input/data/proc/study1.RData"))
-
-df1$class3 <- forcats::fct_rev(df1$class3)
-df1$class5 <- forcats::fct_rev(df1$class5)
-df1$class6 <- forcats::fct_rev(df1$class6)
-
-dfreg <- df1 %>% select(redist,
+# remove.packages("Matrix")
+# install.packages("Matrix")
+df1$class3<-forcats::fct_rev(df1$class3)
+df1$class5<-forcats::fct_rev(df1$class5)
+df1$class6<-forcats::fct_rev(df1$class6)
+dfreg <- df1 %>% dplyr::select(redist,
                         isei08,
-                        class3,
                         eindex,
+                        prestige,
+                        diversity,
                         # isei_range,
@@
 
+dfreg$country <- to_factor(dfreg$country)
+dim(dfreg)
+
 base <- lmer(redist~1 + (1|country),data=dfreg)
 demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-scapital <- lmer(redist~1 + female+agenum + eindex + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ eindex + (1|country),data=dfreg)
+
 class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
 class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + eindex+isei08+ (1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + eindex*isei08+ (1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + eindex*isei08+ (1+eindex|country),data=dfreg)
-models <- list(scapital,class,class_status,full,full_int1,full_int2)
+full <- lmer(redist~1+female+agenum+isei08+ednum+prestige+diversity+eindex+(1|country),data=dfreg)
+full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
+full_int2 <- lmer(redist~1+female+agenum+prestige+diversity+eindex*isei08+ednum+(1+diversity|country),data=dfreg)
+models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
 texreg::knitreg(models)
@@
 
+interplot::interplot(m = full_int1,var1 = "eindex",var2="isei08") +
+  ylab("Network diversity coefficient")+
+  xlab("SES Respondent")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+#-----------
+dfreg <- df1 %>% select(redist,
+                        isei08,
+                        eindex,
+                        prestige,
+                        # diversity,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        ednum,female,agenum,country) %>% na.omit()
+
+dim(dfreg)
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+diversity <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
+
+class <- lmer(redist~1+female+agenum+isei08+(1|country),data=dfreg)
+class_status <- lmer(redist~1+female+agenum+isei08+ednum+(1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1|country),data=dfreg)
+fullrs <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1+eindex|country),data=dfreg)
+full_int1 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1|country),data=dfreg)
+full_int2 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1+eindex|country),data=dfreg)
+models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+texreg::plotreg(full, omit.coef = "(Intercept)")
+
 interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
-  ylab("Network diversity coefficient")+
+  ylab("Network heterogeneity coefficient")+
   xlab("SES Respondent")+
@@
 ```
+
+```{r class-diversity}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
+load(here::here("input/data/proc/study1.RData"))
+
+levels(df1$class3)
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+levels(df1$class3)
+levels(df1$class5)
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+levels(df1$class6)
+
+dfreg <- df1 %>% select(redist,
+                        class6,
+                        class3,
+                        class5,
+                        # eindex,
+                        prestige,
+                        diversity,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        ednum,female,agenum,country) %>% na.omit()
+dim(dfreg)
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class6 +ednum +  prestige + diversity +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum + (1+diversity|country),data=dfreg)
+models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + diversity +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum + (1+diversity|country),data=dfreg)
+models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + diversity +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum + (1+diversity|country),data=dfreg)
+models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+interplot::interplot(m = full_int1,var1 = "diversity",var2="class3") +
+  ylab("Network diversity coefficient")+
+  xlab("SES Respondent")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+```
+
+```{r class-homclass}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
+load(here::here("input/data/proc/study1.RData"))
+
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+frq(df1$Q05pcm)
+dfreg <- df1 %>% dplyr::select(redist,
+                        class6,
+                        class3,
+                        class5,
+                        # eindex,
+                        # know_total,
+                        homclass,
+                        # prestige,
+                        # diversity,
+                        pi_nteg,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        Q05pcm,
+                        ednum,female,agenum,country) %>% na.omit()
+dfreg$country <- to_factor(dfreg$country)
+
+sjPlot::plot_model(lmer(pi_nteg~1 + female+agenum + homclass+class3 +ednum+ (1|country),data=dfreg))
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+homclass <- lmer(redist~1 + female+agenum + homclass+ (1|country),data=dfreg)
+class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass + pi_nteg + Q05pcm + (1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ pi_nteg+ ednum +(1|country),data=dfreg)
+full_int3 <- lmer(redist~1 +female+agenum + homclass+pi_nteg*class3+ pi_nteg+ ednum + (1|country),data=dfreg)
+
+models <- list(homclass,class,class_status,full,full_int1,full_int3)
+texreg::knitreg(models)
+texreg::knitreg(full)
+sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
+ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
+       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)
+
+interplot <- 
+interplot::interplot(m = full_int2,var1 = "homclass",var2="class3")
+
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int
+df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  ylab("Class-based homogeneity coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "margins_homoxclass.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+isolation <- 
+interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
+df_int2 <- isolation$data
+df_int2 <- df_int2[c(1,2,4),]
+df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int2
+df_int2$value <- factor(df_int2$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int2 %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  ylab("Perceived isolation coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+```{r eindex}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
+load(here::here("input/data/proc/study1.RData"))
+
+levels(df1$class3)
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+levels(df1$class3)
+levels(df1$class5)
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+levels(df1$class6)
+
+dfreg <- df1 %>% select(redist,
+                        class6,
+                        class3,
+                        class5,
+                        eindex,
+                        homclass,
+                        prestige,
+                        diversity,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        ednum,female,agenum,country) %>% na.omit()
+
+dim(dfreg)
+cor(dfreg[,c("eindex","prestige","diversity")])
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+eindex <- lmer(redist~1 + female+agenum + prestige +diversity+eindex+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class6 +ednum + prestige +diversity+ eindex +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum + (1+eindex|country),data=dfreg)
+models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + eindex +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum + (1+eindex|country),data=dfreg)
+models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+base <- lmer(redist~1 + (1|country),data=dfreg)
+demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
+prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
+eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
+
+class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + eindex +(1|country),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum +(1|country),data=dfreg)
+full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum + (1+eindex|country),data=dfreg)
+models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
+texreg::knitreg(models)
+
+interplot <- 
+interplot::interplot(m = full_int2,var1 = "eindex",var2="class3") +
+  ylab("Network heterophily coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int
+df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  ylab("Network heterophily coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "margins_hetxclass.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```

### 2023-07-24 procesamiento/prod_prep.Rmd
update weak strong ties

--- 2023-02-01 procesamiento/prod_prep.Rmd
@@
 editor_options: 
-  chunk_output_type: console
+  chunk_output_type: inline
 ---
@@
 
-```{css, echo=FALSE}
-# /* expandir el espacio del documento*/
-body .main-container {
-      max-width: 1600px !important;
-      width: 1600px !important;
-    }
-#/* expandir width de la TOC*/
-div.tocify {
-    width: 22% !important;
-    max-width: 331px !important;
-    max-height: 102% !important;
-}
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,sjlabelled)
+df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
+dfTR <- haven::read_dta(here::here("input/data/original/ZA5521_v1-0-0.dta"))
+dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))
+
+df1 <- df1 %>% rename(topbot=TOPBOT)
+dfES <- dfES %>% rename(topbot=TOPBOT)
+dfES$c_alphan <- NULL
+dfTR$c_alphan <- NULL
+df2 <- bind_rows(dfES,dfTR)
+df1<- bind_rows(df1,df2)
 ```
 
-## Librerías
+# Welfare attitudes
 
 ```{r}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-                            # cargar librerias
-pacman::p_load(dplyr,       # Manipulacion de datos 
-               haven,       # importar datos en .dta o .sav
-               car,         # recodificar variables
-               sjlabelled,  # etiquetado de variables
-               sjmisc,      # descriptivos y frecuencias
-               sjPlot,      # tablas, plots y descriptivos
-               summarytools,# resumen de dataframe
+#frq(df1$v13)
+df1$redist <- car::recode(df1$v13,recodes = "c(0,8,9)=NA")
+df1$redist <- set_na(df1$redist,na = c(0,8,9))
+df1$redist <- sjmisc::rec(x = df1$redist,rec = "rev")
+sjlabelled::set_label(df1$redist) <- "Preferences goverment redistribution"
+#frq(df1$redist)
+
+#frq(df1$v15)
+df1$whealth <- car::recode(df1$v15,recodes = "c(0,8,9)=NA")
+df1$whealth <- set_na(df1$whealth,na = c(0,8,9))
+df1$whealth <- sjmisc::rec(x = df1$whealth,rec = "rev")
+sjlabelled::set_label(df1$whealth) <- "Welfare provision: health"
+#frq(df1$whealth)
+
+#frq(df1$v16)
+df1$wcarelder <- car::recode(df1$v16,recodes = "c(0,8,9)=NA")
+df1$wcarelder <- set_na(df1$wcarelder,na = c(0,8,9))
+df1$wcarelder <- sjmisc::rec(x = df1$wcarelder,rec = "rev")
+sjlabelled::set_label(df1$wcarelder) <- "Welfare provision: elderly care"
+#frq(df1$wcarelder)
+# cor(df1[,c("redist","whealth","wcarelder")],use = "complete.obs")
+```
+
+# Inequality perceptions
+
+```{r}
+#frq(df1$v59)
+df1$hhdepriv <- car::recode(df1$v59,recodes = "c(0,8,9)=NA")
+df1$hhdepriv <- set_na(df1$hhdepriv,na = c(0,8,9))
+# df1$hhdepriv <- sjmisc::rec(x = df1$hhdepriv,rec = "rev")
+sjlabelled::set_label(df1$hhdepriv) <- "Household economic deprivation (household difficulties)"
+#frq(df1$hhdepriv)
+
+#frq(df1$v11)
+df1$perineq <- car::recode(df1$v11,recodes = "c(0,8,9)=NA")
+df1$perineq <- set_na(df1$perineq,na = c(0,8,9))
+df1$perineq <- sjmisc::rec(x = df1$perineq,rec = "rev")
+sjlabelled::set_label(df1$perineq) <- "Perceived economic inequality (Inc. diff. too large)"
+#frq(df1$perineq)
+
+#frq(df1$v12)
+df1$prefineq <- car::recode(df1$v12,recodes = "c(0,8,9)=NA")
+df1$prefineq <- set_na(df1$prefineq,na = c(0,8,9))
+df1$prefineq <- sjmisc::rec(x = df1$prefineq,rec = "rev")
+sjlabelled::set_label(df1$prefineq) <- "Preference inequality (society has to be fair)"
+#frq(df1$prefineq)
+
+#frq(df1$v14)
+df1$pertransfer <- car::recode(df1$v14,recodes = "c(0,8,9)=NA")
+df1$pertransfer <- set_na(df1$pertransfer,na = c(0,8,9))
+df1$pertransfer <- sjmisc::rec(x = df1$pertransfer,rec = "rev")
+sjlabelled::set_label(df1$pertransfer) <- "Perception about welfare (people become lazy)"
+#frq(df1$pertransfer)
+```
+
+# Perceived integration
+
+```{r}
+#frq(df1$v31)
+df1$pi_compa <- car::recode(df1$v31,recodes = "c(0,8,9)=NA")
+df1$pi_compa <- set_na(df1$pi_compa,na = c(0,8,9))
+# df1$pi_compa <- sjmisc::rec(x = df1$pi_compa,rec = "rev")
+sjlabelled::set_label(df1$pi_compa) <- "Perceived integration: companionship lacking"
+#frq(df1$pi_compa)
+
+#frq(df1$v32)
+df1$pi_isola <- car::recode(df1$v32,recodes = "c(0,8,9)=NA")
+df1$pi_isola <- set_na(df1$pi_isola,na = c(0,8,9))
+# df1$pi_isola <- sjmisc::rec(x = df1$pi_isola,rec = "rev")
+sjlabelled::set_label(df1$pi_isola) <- "Perceived integration: isolated from others"
+#frq(df1$pi_compa)
+
+#frq(df1$v33)
+df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
+df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
+# df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
+sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
+#frq(df1$pi_left)
+```
+
+# Social status
+
+```{r income-hhold}
+income_country <- names(df1 %>% dplyr::select(dplyr::ends_with("_INC")))
+# lapply(df1[,income_country], table)
+for (i in income_country) {
+  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  df1[[i]] <- as.numeric(df1[[i]])
+  }
+
+# lapply(df1[,income_country], table)  # Ok el recode de ingresos familiares 
+# Crear variable ingresos unica 
+df1 <- df1 %>% mutate(income = coalesce(AT_INC,AU_INC,CH_INC,CN_INC,CZ_INC,DE_INC,DK_INC,ES_INC,FI_INC,FR_INC,GB_INC,HR_INC,HU_INC,IL_INC,IN_INC,IS_INC,
+                                        JP_INC,LT_INC,MX_INC,NZ_INC,PH_INC,RU_INC,SE_INC,SI_INC,SK_INC,SR_INC,TH_INC,TW_INC,US_INC,ZA_INC))
+
+#frq(df1$income==0)
+#frq(df1$HOMPOP)
+df1$hhpop <- as.numeric(df1$HOMPOP) 
+df1$hhpop[df1$hhpop %in%c(0,97,99)] <- NA
+#frq(df1$hhpop)
+df1$incomepcap <- as.numeric(df1$income/df1$hhpop) # Ingreso per capita del hogar
+
+df1 <- df1 %>%group_by(country)  %>% mutate(D10pc=ntile(incomepcap,10),
+                                              Q05pc=ntile(incomepcap,5),
+                                              zincpc=scale(incomepcap,center = TRUE),
+                                              logincpc=log(incomepcap)) %>% ungroup()
+
+sjlabelled::set_label(df1$D10pc) <- "Household income (D10)"
+sjlabelled::set_label(df1$Q05pc) <- "Household income (Q05)"
+sjlabelled::set_label(df1$zincpc) <- "Household income (zscore)"
+sjlabelled::set_label(df1$logincpc) <- "Household income (log)"
+```
+
+```{r income-respondent}
+income_country <- names(df1 %>% select(dplyr::ends_with("_RINC")))
+# lapply(df1[,income_country], table)
+for (i in income_country) {
+  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  df1[[i]] <- as.numeric(df1[[i]])
+  }
+
+# lapply(df1[,income_country], table)  # Ok el recode de ingresos familiares 
+# Crear variable ingresos unica 
+df1 <- df1 %>% mutate(incomer = coalesce(AT_RINC,AU_RINC,
+                                        CH_RINC, CN_RINC,
+                                        CZ_RINC, DE_RINC,
+                                        DK_RINC, ES_RINC,
+                                        FI_RINC, FR_RINC,
+                                        GB_RINC, HR_RINC,
+                                        HU_RINC, IL_RINC,
+                                        IN_RINC, IS_RINC,
+                                        JP_RINC, LT_RINC,
+                                        MX_RINC, NZ_RINC,
+                                        PH_RINC, RU_RINC,
+                                        SE_RINC, SI_RINC,
+                                        SK_RINC, SR_RINC,
+                                        TH_RINC, TW_RINC,
+                                        US_RINC, ZA_RINC))
+#frq(df1$incomer==0)
+
+df1 <- df1 %>%group_by(country) %>% mutate(D10r=ntile(incomer,10),
+                                              Q05r=ntile(incomer,5),
+                                              zincpcr=scale(incomer,center = TRUE),
+                                              logincr=log(incomer)) %>% ungroup()
+#frq(df1$incomer)
+#frq(df1$incomepcap)
+# Single household 
+df1$incomerep <- ifelse(df1$hhpop==1 & is.na(df1$incomepcap),df1$incomer,df1$incomepcap)
+#frq(is.na(df1$incomerep))
+#frq(df1$incomerep==0)
+df1[,c("incomer","hhpop","incomepcap","incomerep")] %>% arrange(incomepcap,hhpop) %>% head()
+df1$incomerep <- ifelse(df1$hhpop==1 & df1$incomerep==0,df1$incomer,df1$incomerep)
+#frq(df1$incomerep==0)
+df1[,c("incomer","hhpop","incomepcap","incomerep")] %>% arrange(incomepcap,hhpop) %>% head()
+```
+
+```{r}
+#frq(df1$EDUCYRS)
+df1$edyears <- as.numeric(car::recode(df1$EDUCYRS,recodes = "98:99=NA")) 
+sjlabelled::set_label(df1$edyear) <- "Years of schooling"
+#frq(df1$edyears)
+
+#frq(df1$DEGREE)
+df1$ednum <- car::recode(df1$DEGREE+1,"10=NA")
+sjlabelled::set_label(df1$ednum) <- "Educational level"
+#frq(df1$ednum)
+df1$edcat <- car::recode(df1$ednum,recodes = "1:2='Primary or less';
+                         3:4='Secondary';
+                         5='Terciary short-cycle';
+                         6:7='Terciary or higher';
+                         9=NA",
+                         levels =c('Primary or less',
+                                   'Secondary',
+                                   'Post-secondary non-terciary',
+                                   'Terciary or higher'),as.factor = T)
+sjlabelled::set_label(df1$edcat) <- "Educational level"
+#frq(df1$edcat)
+```
+
+```{r subjstatus}
+df1$sstatus <- car::recode(df1$topbot, "c(0,98,99)=NA") 
+#frq(df1$sstatus)
+```
+
+# Occupational variables
+
+```{r labour-status}
+#frq(df1$MAINSTAT)
+df1$labst <- car::recode(
+  as.numeric(df1$MAINSTAT),
+  recodes = "1='In labour force';2:9='Not in labour force';c(0,99)='No information'",
+  levels = c('In labour force', 'Not in labour force', 'No information'),
+  as.factor = T
+)
+sjlabelled::set_label(df1$labst) <- "Occupational status"
+#frq(df1$labst)
+```
+
+```{r union}
+#frq(df1$WORK)
+#frq(df1$UNION)
+df1$union <- car::recode(as.numeric(df1$UNION),
+                         recodes= "1:2='Yes';c(0,3,7,8)='No';9=NA",
+                         levels = c("No","Yes"))
+#frq(df1$union)
+```
+
+```{r isei}
+df1$ISCO08[df1$ISCO08 %in% c(9998,9999)] <- NA
+df1$isei08 <- occupar::isco08toISEI08(isco08 = df1$ISCO08,display.nas = T)
+# summary(df1$isei08)
+sjlabelled::set_label(df1$isei08) <- "ISEI respondent"
+
+#frq(df1$SPISCO08)
+df1$SPISCO08[df1$SPISCO08 %in% c(9998,9999)] <- NA
+df1$isei08sp <- occupar::isco08toISEI08(isco08 = df1$SPISCO08,display.nas = T)
+# summary(df1$isei08sp)
+sjlabelled::set_label(df1$isei08sp) <- "ISEI spouse"
+```
+
+```{r class}
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+#frq(df1$SPISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
+#frq(df1$isco88spo)
+
+#Relación de Empleo encuestado
+#frq(df1$SPEMPREL)
+
+df1$sempspo <- df1$SPEMPREL
+df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
+#frq(df1$sempspo)
+
+df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
+#frq(df1$sempspo)
+
+# superivison
+#frq(df1$SPWRKSUP) #supervision spouse
+df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
+#frq(df1$supvisspo)
+
+## Ocupación
+# Ocupación u oficio actual ISCO 08
+#frq(df1$ISCO08) # isco08 
+# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
+df1$isco88r <- occupar::isco08to88(df1$ISCO08)
+#frq(df1$isco88r)
+
+#Note: the package generate identical recodes as my own manual recoding
+
+#Employment relation encuestado
+#frq(df1$EMPREL)
+#frq(df1$WORK)
+df1$semp <- df1$EMPREL
+df1$semp <- as.numeric(car::recode(df1$semp, "c(2,3,4)=1;c(1)=2;c(0,8,9)=NA"))
+#frq(df1$semp)
+df1$semp <- sjlabelled::set_labels(x = df1$semp,labels=c('Self-employed','Employee'))
+#frq(df1$semp)
+
+# superivison
+#frq(df1$NEMPLOY) #supervision respondent
+df1$supvis <- as.numeric(car::recode(df1$NEMPLOY,"c(9998,9999)=NA"))
+#frq(df1$supvis)
+# save the occupational variables for using them in stata-----------------------
+df1$id <- NULL
+df1 <- tibble::rowid_to_column(df1, "id")
+haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
+                              "isco88spo","sempspo","supvisspo")],
+                 path = here::here("input/data/proc/ocup_respondent-spouse.dta"))
+```
+
+```{r class-stata}
+# Load the data created in stata------------------------------------------------
+df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
+df1 <- left_join(df1,df_class,by='id')
+
+df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$class10 <- sjlabelled::set_labels(df1$class10, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$class10) <- "Social Class - respondent"
+
+#frq(df1$class10)
+
+df1$class10spo <- car::recode(df1$class10spo, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$class10spo <- sjlabelled::set_labels(df1$class10spo, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$class10spo) <- "Social Class - spouse"
+
+#frq(df1$class10spo)
+
+#if NA in class of respondent, replace with household
+
+#frq(df1$class10)
+#frq(df1$class10spo)
+
+df1$class11 <- ifelse(is.na(df1$class10),df1$class10spo,df1$class10)
+#frq(df1$class11)
+
+# if NA in respondents it is assumed to be lower than spouse
+# know, with the cases in we have information for respondent and spouse
+# we replace the value by the highest one, just for those
+
+# Replace the highest class by dominance criteria 
+# Keep the highest of two values:
+df1$class11d <- pmax(df1$class11, #social class respondent + spouse vs:
+                       df1$class10spo,#social class spouse
+                       na.rm = T) # if NA, do nothing
+
+df1$class11d <- 
+  sjlabelled::set_labels(df1$class11d,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                         labels =  c("I", "II", "IIIa", "IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
+#frq(df1$class11d)
+sjlabelled::set_label(df1$class11d) <- "Social Class"
+
+# Class Scheme 3 classes
+df1$class3 <- car::recode(df1$class11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3) <- "Social Class"
+#frq(df1$class3)
+
+# Class Scheme 5 classes
+df1$class5 <- car::recode(
+  df1$class11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$class5) <- "Social Class"
+#frq(df1$class5)
+
+# Class Scheme 6 classes
+df1$class6 <- car::recode(
+  df1$class11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
 )
@@
 
-## Datos
+# Networks
 
-Para este ejemplo se va utilizar una base de datos proveniente del paquete `carData`:
+```{r generador}
+ocupations <- names(dplyr::select(df1,v1:v10))
+for (i in ocupations) {
+  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
+  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
+}
 
-> The Chile data frame has 2700 rows and 8 columns. The data are from a national survey conducted in April and May of 1988 by FLACSO/Chile. There are some missing data.
+#frq(df1$v1)
+df1$busdriver <- as.numeric(car::recode(df1$v1,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$busdriver) <- "Know: bus/lorry driver" 
+#frq(df1$busdriver)
 
-```{r echo=TRUE}
-df<- carData::Chile
-df1 <- df %>% select(zona=region,
-                     poblacion=population,
-                     sexo=sex,
-                     edad=age,
-                     educ=education,
-                     statusquo)
+#frq(df1$v2)
+df1$ceo <- as.numeric(car::recode(df1$v2,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$ceo) <- "Know: CEO large company" 
+#frq(df1$ceo)
+
+#frq(df1$v3)
+df1$cleaner <- as.numeric(car::recode(df1$v3,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$cleaner) <- "Know: home or office cleaner" 
+#frq(df1$cleaner)
+
+#frq(df1$v4)
+df1$hairbarber <- as.numeric(car::recode(df1$v4,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hairbarber) <- "Know: hairdresser/barber" 
+#frq(df1$hairbarber)
+
+#frq(df1$v5)
+df1$hrmanager <- as.numeric(car::recode(df1$v5,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$hrmanager) <- "Know: human resource manager" 
+#frq(df1$hrmanager)
+
+#frq(df1$v6)
+df1$lawyer <- as.numeric(car::recode(df1$v6,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$lawyer) <- "Know: lawyer" 
+#frq(df1$lawyer)
+
+#frq(df1$v7)
+df1$mechanic <- as.numeric(car::recode(df1$v7,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$mechanic) <- "Know: car mechanic" 
+#frq(df1$mechanic)
+
+#frq(df1$v8)
+df1$nurse <- as.numeric(car::recode(df1$v8,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$nurse) <- "Know: nurse" 
+#frq(df1$mechanic)
+
+#frq(df1$v9)
+df1$police <- as.numeric(car::recode(df1$v9,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$police) <- "Know: police officer" 
+#frq(df1$police)
+
+#frq(df1$v10)
+df1$teacher <- as.numeric(car::recode(df1$v10,"1:3=1;4=0")) 
+sjlabelled::set_label(df1$teacher) <- "Know: school teacher" 
+#frq(df1$teacher)
+
+# Total of known occupations
+isei_ocupnames<- names(select(df1,busdriver:teacher))
+df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+# summary(df1$know_total)
+sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
 ```
 
-# Preparación
+```{r strenght-ties}
+ocupations <- names(dplyr::select(df1,v1:v10))
+vl<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Tie strenght:")
+vl2<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Strong tie:")
+vl3<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Weak tie:")
 
-En esta sección se realizará la preparación de datos. Se sugiere seguir los siguientes pasos para cada variable:
+for (i in 1:length(ocupations)) {
+  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
+  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
+}
+lb <- c("Absent"=0,"Weak"=1,"Strong"=2)
+lb2 <- c("Strong"=1,"Weak"=0)
+lb3 <- c("Strong"=0,"Weak"=1)
+r <- "4=0;3=1;1:2=2"
+r2 <- "1:2=1;3=0;4=NA"
+r3 <- "1:2=0;3=1;4=NA"
 
-| Paso                      | Función                         |
-|---------------------------|---------------------------------|
-| 1. Descriptivo inicial    | sjmisc::frq() o sjmisc::descr() |
-| 2. Recodificación         | car::recode()                   |
-| 3. Etiquetado de valores  | sjlabelled::set_labels()        |
-| 4. Etiquetado de variable | sjlabelled::set_label()         |
-| 5. Descriptivo final      | sjmisc::frq o sjmisc::descr()   |
+df1 <- df1 %>%
+  # Tie strenght
+  mutate("busdriver_ts" = set_labels(car::recode(df1$v1,r),labels = lb),
+         "ceo_ts" =  set_labels(car::recode(df1$v2,r),labels = lb),
+         "cleaner_ts" = set_labels(car::recode(df1$v3,r),labels = lb),
+         "hairbarber_ts"  = set_labels(car::recode(df1$v4,r),labels = lb),
+         "hrmanager_ts" = set_labels(car::recode(df1$v5,r),labels = lb),
+         "lawyer_ts"  = set_labels(car::recode(df1$v6,r),labels = lb),
+         "mechanic_ts" = set_labels(car::recode(df1$v7,r),labels = lb),
+         "nurse_ts" = set_labels(car::recode(df1$v8,r),labels = lb),
+         "police_ts"  = set_labels(car::recode(df1$v9,r),labels = lb),
+         "teacher_ts" = set_labels(car::recode(df1$v10, r, as.factor = T), labels = lb)) %>%
+  # strong ties  
+  mutate("busdriver_s" = set_labels(car::recode(df1$v1,r2),labels = lb2),
+         "ceo_s" =  set_labels(car::recode(df1$v2,r2),labels = lb2),
+         "cleaner_s" = set_labels(car::recode(df1$v3,r2),labels = lb2),
+         "hairbarber_s"  = set_labels(car::recode(df1$v4,r2),labels = lb2),
+         "hrmanager_s" = set_labels(car::recode(df1$v5,r2),labels = lb2),
+         "lawyer_s"  = set_labels(car::recode(df1$v6,r2),labels = lb2),
+         "mechanic_s" = set_labels(car::recode(df1$v7,r2),labels = lb2),
+         "nurse_s" = set_labels(car::recode(df1$v8,r2),labels = lb2),
+         "police_s"  = set_labels(car::recode(df1$v9,r2),labels = lb2),
+         "teacher_s" = set_labels(car::recode(df1$v10, r2), labels = lb2)) %>% 
+  # weak ties
+  mutate("busdriver_w" = set_labels(car::recode(df1$v1,r3),labels = lb3),
+         "ceo_w" =  set_labels(car::recode(df1$v2,r3),labels = lb3),
+         "cleaner_w" = set_labels(car::recode(df1$v3,r3),labels = lb3),
+         "hairbarber_w"  = set_labels(car::recode(df1$v4,r3),labels = lb3),
+         "hrmanager_w" = set_labels(car::recode(df1$v5,r3),labels = lb3),
+         "lawyer_w"  = set_labels(car::recode(df1$v6,r3),labels = lb3),
+         "mechanic_w" = set_labels(car::recode(df1$v7,r3),labels = lb3),
+         "nurse_w" = set_labels(car::recode(df1$v8,r3),labels = lb3),
+         "police_w"  = set_labels(car::recode(df1$v9,r3),labels = lb3),
+         "teacher_w" = set_labels(car::recode(df1$v10, r3), labels = lb3))
 
-## Variables individuales
+v = names(dplyr::select(df1,ends_with("_ts")))
+df1[,v]<- set_label(x = df1[,v],label = vl) #label Tie strenght
 
-### Edad 
-```{r edad}
-sjmisc::descr(df1$edad)
-df1$edadcat <- car::recode(var = df1$edad,
-                           recodes = "18:24=1;25:44=2;45:64=3;65:70=4",
-                           as.factor = T) 
-df1$edadcat <- set_labels(x = df1$edadcat,
-                          labels = c("18 a 24 años" = 1,
-                                     "25 a 44 años" = 2,
-                                     "45 a 65 años" = 3,
-                                     "65 años o más" = 4))
-df1$edadcat <- set_label(df1$edadcat,label = "Tramos de edad")
-sjmisc::frq(df1$edadcat,out = "txt")
+s = names(dplyr::select(df1,ends_with("_s")))
+df1[,s]<- set_label(x = df1[,s],label = vl2) #label strong tie
+
+w = names(dplyr::select(df1,ends_with("_w")))
+df1[,w]<- set_label(x = df1[,w],label = vl3) #label weak tie
+
+df1$know_total_s <- rowSums(x = select(df1,ends_with("_s")),na.rm = T)
+sjlabelled::set_label(df1$know_total_s) <- 'Total of known occupations (strong ties)'
+
+df1$know_total_w <- rowSums(x = select(df1,ends_with("_w")),na.rm = T)
+sjlabelled::set_label(df1$know_total_s) <- 'Total of known occupations (weak ties)'
+
 ```
 
-### Sexo 
-```{r sexo}
-sjmisc::frq(df1$sexo)
-df1$mujer <- car::recode(var = df1$sexo,
-                           recodes = "'F'=1;'M'=0",
-                           as.factor = T)
+```{r strenght-num}
+# strong ties
+df1$n_high_s<-rowSums(x = df1[c("lawyer_s","hrmanager_s","ceo_s")],na.rm = T)
+set_label(df1$n_high_s) <- 'Number of high status contacts (strong ties)'
 
-df1$mujer <- set_labels(x = df1$mujer,
-                          labels = c("Hombre" = 0,
-                                     "Mujer" = 1))
-df1$mujer <- set_label(df1$mujer,label = "Sexo entrevistado")
-sjmisc::frq(df1$mujer,out = "txt")
+df1$n_middle_s<-rowSums(x = df1[c("teacher_s","police_s","nurse_s")],na.rm = T)
+set_label(df1$n_middle_s) <- 'Number of middle status contacts (strong ties)'
+
+df1$n_low_s <- rowSums(x = df1[c("mechanic_s","busdriver_s","hairbarber_s","cleaner_s")],na.rm = T)
+set_label(df1$n_low_s) <- 'Number of low status contacts (strong ties)'
+
+# weak ties
+df1$n_high_w<-rowSums(x = df1[c("lawyer_w","hrmanager_w","ceo_w")],na.rm = T)
+set_label(df1$n_high_w) <- 'Number of high status contacts (weak ties)'
+
+df1$n_middle_w<-rowSums(x = df1[c("teacher_w","police_w","nurse_w")],na.rm = T)
+set_label(df1$n_middle_w) <- 'Number of middle status contacts (weak ties)'
+
+df1$n_low_w <- rowSums(x = df1[c("mechanic_w","busdriver_w","hairbarber_w","cleaner_w")],na.rm = T)
+set_label(df1$n_low_w) <- 'Number of low status contacts (weak ties)'
 ```
 
-### Nivel educacional
+```{r isei-generador}
+df1$isei_busdriver <- as.numeric(ifelse(df1$busdriver ==1,37,NA)) 
+sjlabelled::set_label(df1$isei_busdriver) <- "ISEI: bus/lorry driver" 
+#frq(df1$isei_busdriver)
+
+df1$isei_ceo <- as.numeric(ifelse(df1$ceo==1,70,NA)) 
+sjlabelled::set_label(df1$isei_ceo) <- "ISEI: CEO large company" 
+#frq(df1$isei_ceo)
+
+df1$isei_cleaner <- as.numeric(ifelse(df1$cleaner==1,17,NA)) 
+sjlabelled::set_label(df1$isei_cleaner) <- "ISEI: home or office cleaner" 
+#frq(df1$isei_cleaner)
+
+df1$isei_hairbarber <- as.numeric(ifelse(df1$hairbarber==1,32,NA)) 
+sjlabelled::set_label(df1$isei_hairbarber) <- "ISEI: hairdresser/barber" 
+#frq(df1$isei_hairbarber)
+
+df1$isei_hrmanager <- as.numeric(ifelse(df1$hrmanager==1,68,NA)) 
+sjlabelled::set_label(df1$isei_hrmanager) <- "ISEI: human resource manager" 
+#frq(df1$isei_hrmanager)
+
+df1$isei_lawyer <- as.numeric(ifelse(df1$lawyer==1,85,NA)) 
+sjlabelled::set_label(df1$isei_lawyer) <- "ISEI: lawyer" 
+#frq(df1$isei_lawyer)
+
+df1$isei_mechanic <- as.numeric(ifelse(df1$mechanic==1,38,NA)) 
+sjlabelled::set_label(df1$isei_mechanic) <- "ISEI: car mechanic" 
+#frq(df1$isei_mechanic)
+
+df1$isei_nurse <- as.numeric(ifelse(df1$nurse==1,48,NA)) 
+sjlabelled::set_label(df1$isei_nurse) <- "ISEI: nurse" 
+#frq(df1$isei_nurse)
+
+df1$isei_police <- as.numeric(ifelse(df1$police==1,53,NA)) 
+sjlabelled::set_label(df1$isei_police) <- "ISEI: police officer" 
+#frq(df1$isei_police)
+
+df1$isei_teacher <- as.numeric(ifelse(df1$teacher==1,63,NA)) 
+sjlabelled::set_label(df1$isei_teacher) <- "ISEI: school teacher" 
+#frq(df1$isei_teacher)
+```
+
+```{r social-capital}
+# Social capital measures
+isei_ocupnames<- names(select(df1,starts_with("isei_")))
+
+# number of high status contacts
+df1$n_high <- 
+  rowSums(x = select(df1,c("lawyer","hrmanager","ceo")),na.rm = T)
+sjlabelled::set_label(df1$n_high) <- 'Number of high status contacts'
+# sjPlot::plot_#frq(df1$n_high,type = 'density')
+
+# percentage of high status contacts
+
+df1$pct_high <- (df1$n_high/df1$know_total)*100
+sjlabelled::set_label(df1$df1$pct_high ) <- 'Percentage of high status contacts'
+# sjPlot::plot_#frq(df1$pct_high,type = 'density')
+
+# number of middle status contacts
+df1$n_middle <-
+  rowSums(x = select(df1,c("teacher","police","nurse")),na.rm = T)
+sjlabelled::set_label(df1$n_middle) <- 'Number of middle status contacts'
+# sjPlot::plot_#frq(df1$n_middle,type = 'density')
+
+# percentage of middle status contacts
+df1$pct_middle <- (df1$n_middle/df1$know_total)*100
+sjlabelled::set_label(df1$pct_middle) <- 'Percentage of middle status contacts'
+# sjPlot::plot_#frq(df1$pct_middle,type = 'density')
+
+# number of low status contacts
+# df1$n_low <- 
+#   rowSums(x = select(df1,c("n_waiter","n_carmech","n_taxi","n_stvend","n_cleaner")),na.rm = T)
+df1$n_low <- 
+  rowSums(x = select(df1,c("mechanic","busdriver","hairbarber","cleaner")),na.rm = T)
+sjlabelled::set_label(df1$n_low) <- 'Number of low status contacts'
+# sjPlot::plot_#frq(df1$n_low,type = 'density')
+
+# percentage of low status contacts
+df1$pct_low <- (df1$n_low/df1$know_total)*100
+sjlabelled::set_label(df1$pct_low) <- 'Percentage of low status contacts'
+# sjPlot::plot_#frq(df1$pct_low,type = 'density')
+
+# Average ISEI 
+df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) #REVISAR NO DEBERIA CONTENER 0
+sjlabelled::set_label(df1$isei_avg) <- 'Average contact prestige'
+summary(df1$isei_avg)
+
+# sjPlot::plot_#frq(df1$isei_avg,type = 'density')
+
+# Total ISEI 
+df1$isei_tot <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+sjlabelled::set_label(df1$isei_tot) <- 'Total contact prestige'
+summary(df1$isei_tot)
+# sjPlot::plot_#frq(df1$isei_tot,type = 'density')
+
+# skimr::skim(df1$isei_tot/df1$n_total)
+# skimr::skim(df1$isei_tot/df1$know_total)
+# skimr::skim(df1$isei_avg)
+
+# max ISEI 
+df1 <- df1 %>% 
+mutate(isei_max = do.call(pmax, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_max) <- 'Maximum contact prestige'
+# sjmisc::frq(df1$isei_max)
+# sjPlot::plot_#frq(df1$isei_max)
+
+# min ISEI
+df1 <- df1 %>% 
+mutate(isei_min = do.call(pmin, c(select(., isei_ocupnames), na.rm = TRUE)))
+sjlabelled::set_label(df1$isei_min) <- 'Minimum contact prestige'
+# sjmisc::frq(df1$isei_min)
+# sjPlot::plot_#frq(df1$isei_min)
+
+# range ISEI
+table(df1$know_total>=2)
+df1$isei_range <- ifelse(df1$know_total>=2,(df1$isei_max - df1$isei_min),no = NA)
+
+sjlabelled::set_label(df1$isei_range) <- 'Range contact prestige'
+# sjmisc::frq(df1$isei_range)
+# sjPlot::plot_#frq(df1$isei_range)
+# df1 %>% select(starts_with("isei_")) %>%View
+
+cor(df1[,c("isei_avg","isei_max","isei_range",
+                 "know_total","n_high","n_middle","n_low",
+                 "pct_high","pct_middle","pct_low")],use = "complete.obs")
+
+```
+
+```{r heterogeneity}
+isei_ocupnames<- names(select(df1,busdriver:teacher))
+
+df1$hindex_sta<- 
+as.numeric(
+  1 - (
+    #p1^2
+    (df1$n_high / df1$know_total)^2 +
+    #p2^2
+    (df1$n_middle / df1$know_total)^2 +
+    #p3^2
+    (df1$n_low / df1$know_total)^2
+    )
+  )
+
+sjlabelled::set_label(df1$hindex_sta) <- "D-index: status groups"
+
+df1$hindex_10<- 
+as.numeric(
+  1 - (
+    #p1^2
+    (df1$busdriver/df1$know_total)^2 +
+    #p2^2
+    (df1$ceo / df1$know_total)^2 +
+    #p3^2
+    (df1$cleaner / df1$know_total)^2 +
+    #p3^2
+    (df1$hairbarber / df1$know_total)^2 +
+     #p3^2
+    (df1$hrmanager / df1$know_total)^2 +
+    #p3^2
+    (df1$lawyer / df1$know_total)^2+
+    #p3^2
+    (df1$mechanic / df1$know_total)^2+
+    #p3^2
+    (df1$nurse / df1$know_total)^2+
+    #p3^2
+    (df1$police / df1$know_total)^2+    
+    #p3^2
+    (df1$teacher / df1$know_total)^2        
+    )
+  )
+
+sjlabelled::set_label(df1$hindex_10) <- "D-index: 10 ocupations"
+```
+
+```{r homogeneity}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex) <- "EI homophily index"
+#frq(df1$eindex)
+hist.default(df1$eindex)
+
+df1 %>% select(class3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass) <- "Class homogeneity"
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r homogeneity-strong}
+# EI homophily index
+df1$ingroup_s<- NA 
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low_s,df1$ingroup_s)
+#frq(df1$ingroup_s)
+
+df1$outgroup_s <- NA 
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
+#frq(df1$outgroup_s)
+
+df1$eindex_s<- (df1$outgroup_s-df1$ingroup_s)/(df1$outgroup_s+df1$ingroup_s)
+sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
+#frq(df1$eindex_s)
+hist.default(df1$eindex_s)
+
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
+df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
+sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
+hist.default(df1$homclass_s)
+```
+
+```{r homogeneity-weak}
+# EI homophily index
+df1$ingroup_w<- NA 
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low_w,df1$ingroup_w)
+# frq(df1$ingroup_w)
+
+df1$outgroup_w <- NA 
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
+# frq(df1$outgroup_w)
+
+df1$eindex_w<- (df1$outgroup_w-df1$ingroup_w)/(df1$outgroup_w+df1$ingroup_w)
+sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
+frq(df1$eindex_w)
+hist.default(df1$eindex_w)
+
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
+df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
+sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
+hist.default(df1$homclass_s)
+```
+
+```{r social distance}
+
+df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
+df1$dis_ceo <- df1$isei08 - df1$isei_ceo
+df1$dis_cleaner <- df1$isei08 - df1$isei_cleaner
+df1$dis_hairbarber <- df1$isei08 - df1$isei_hairbarber
+df1$dis_hrmanager <- df1$isei08 - df1$isei_hrmanager
+df1$dis_lawyer <- df1$isei08 - df1$isei_lawyer
+df1$dis_mechanic <- df1$isei08 - df1$isei_mechanic
+df1$dis_nurse <- df1$isei08 - df1$isei_nurse
+df1$dis_police <- df1$isei08 - df1$isei_police
+df1$dis_teacher <- df1$isei08 - df1$isei_teacher
+
+# 88 - 37  = 51
+# 88 - 17  = 71
+
+df1$socdist<- rowMeans(x = df1 %>% select(starts_with("dis_")),na.rm = T)
+sjlabelled::set_label(df1$socdist) <- "Social distance: ISEI (respondent - contacts)"
+# sjPlot::plot_#frq(df1$socdist,type = "histogram")
+
+# df1$socdist_tot<- (df1$isei08- df1$isei_avg)
+# sjPlot::plot_#frq(df1$socdist_tot,type = "histogram")
+# sjlabelled::set_label(df1$socdist_tot) <- "Social distance: ISEI (respondent - contacts)"
+
+#higher values represent higher socioeconomic distance from my contacts.
+In other words, higher values means that in average, my contacts are more different from me in terms of socioeconomic status (ISEI), while lower values represent higher homogeneity.
+```
+
+(i)  the highest status job accessed (upper reachability),
+(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
+(iii) the total number of occupations accessed (network extensity),
+(iv) the total accessed prestige (resource volume),
+(v) the average status of jobs accessed (network prestige),
+(vi) the total number of higher-status positions accessed,
+(vii) the total number of medium-status positions accessed,
+(viii) the total number of lower-status positions accessed.
+
+```{r pca}
+library(psych)
+library(dplyr)
+isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
+
+# Calculate the standard deviation for each column
+df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
+
+# Print the standard deviation for each column
+df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
+
+# reduce dimensions in 2: diversity and prestige
+df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
+summary(df_cs)
+dim(df_cs)
+
+# df_cs <- na.omit(df_cs)
+cor<- corr.test(df_cs)
+psych::KMO(r = cor$r)
+cortest.bartlett(cor$r,n = dim(df_cs)[1])
+plot(scree(df_cs,factors = 2))
+
+# Porcentaje de varianza explicada
+fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
+fit1$loadings
+plot(fit1,labels = c(names(df_cs)))
+cor(fit1$scores)
+
+fit2<- psych::fa(df_cs,nfactors = 2)
+plot(fit2,labels = c(names(df_cs)))
+fit2$scores
+cor(fit2$scores)
+fs<- as.data.frame(fit2$scores)
+names(fs) <- c("diversity","prestige")
+
+df1 <- bind_cols(df1,fs)
+sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
+sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
+```
+
+# Demographics
+
+```{r demographics}
+df1$agenum <- as.numeric(car::recode(df1$AGE,recodes = "999=NA",as.numeric = T))
+sjlabelled::set_label(df1$agenum) <- "Age in years"
+#frq(df1$agenum)
+
+#frq(df1$SEX)
+df1$female <- car::recode(as.numeric(df1$SEX),"2='Female';1='Male';9=NA",
+                          levels = c('Male','Female'),as.factor = T)
+#frq(df1$female)
+```
 
 ```{r}
-sjmisc::frq(df1$educ)
-df1$educ <- car::recode(df1$educ,
-                        recodes = "'P'=1;'S'=2;'PS'=3",
-                        as.factor = T)
-
-df1$educ <- set_labels(df1$educ,labels = c("Primaria"=1,
-                                           "Secundaria"=2,
-                                           "Post-secundaria"=3))
-df1$educ <- set_label(df1$educ,label = "Nivel educacional")
-sjmisc::frq(df1$educ)
+names(df1)
 ```
 
-### Apoyo statusquo
-
 ```{r}
-sjmisc::descr(df1$statusquo)
-df1$statusquo <- set_label(df1$statusquo,label = "Escala de apoyo al status-quo")
-sjmisc::descr(df1$statusquo)
+save(df1,file = here::here("input/data/proc/study1.RData"))
 ```
-
-## Variables contextuales
-
-### Zona
-
-```{r zona}
-sjmisc::frq(df1$zona)
-df1$zona <- set_labels(x = df1$zona,
-                          labels = c("Centro" = "C",
-                                     "Metropolitana Santiago" = "M",
-                                     "Norte"="N",
-                                     "Sur"="S",
-                                     "Santiago ciudad"='SA'))
-df1$zona <- set_label(df1$zona,label = "Zona geográfica")
-sjmisc::frq(df1$zona,out = "txt")
-```
-
-### Proporcion de mujeres x zona
-```{r}
-tab_xtab(var.row = df1$zona, # Filas= zona
-         var.col = df1$mujer,# columna= sexo 
-         show.obs = FALSE,   
-         show.row.prc = T)
-df1 %>% group_by(zona) %>% summarise(propmuj=mean(as.numeric(mujer))-1)
-
-prop.muj<- df1 %>%
-  group_by(zona, mujer) %>%
-  summarise(n = n()) %>%
-  mutate(propmuj = n / sum(n)) %>%
-  filter(mujer==1) %>% 
-  ungroup() %>% 
-  select(zona,propmuj)
-
-df1 <- left_join(df1,prop.muj,by="zona")
-df1$propmuj <- set_label(df1$propmuj,label = "Proporción de mujeres por zona geográfica")
-sjmisc::descr(df1$propmuj)
-```
-
-### Población por zona
-
-```{r poblacion}
-sjmisc::frq(df1$poblacion)
-df1$poblacion <- set_label(df1$poblacion,label = "Población por zona geofráfica")
-sjmisc::frq(df1$poblacion,out = "txt")
-```
-
-# Seleccionar variables
-
-```{r}
-df_final<- df1 %>%
-  select(zona,
-         poblacion,
-         mujer,
-         edadcat,
-         educ,
-         statusquo)
-```
-
-# Resumen
-
-```{r,results='asis', echo=FALSE}
-st_css() # esto configura el css de dfsummary
-print(dfSummary(df_final),
-      method = "render")
-view_df(df_final)
-```
-
-# Guardar datos
-
-```{r}
-save(df_final,file = "../input/data/proc/df_final.Rdata")
-```

### 2023-07-25 paper.Rmd
update

@@
 
-# Introducción
+- Class: 
+  - having a working class position is associated with higher redistributive preferences
+  - class homogeneity is higher among the working class, and lower in the upper-class
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+- Network segregation
+  - being more segregated increase redistributive preferences
+- Perceived isolation
+  - perceived isolation increases redistributive preferences
 
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Note: network segregation decreases perceived isolation *
 
-## Hipótesis
+- class x network segregation
 
-$H_{1}$: Individuos con mayor percepción de Estatus Social para su familia de origen tenderían a percibir más meritocracia
+  - the influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
 
-$H_{2}$: Una posición superior en la distribución de ingresos se asocia positivamente con la percepción de meritocracia.
-
-$H_{3}$: Pertenecer a grupos con mayor logro educativo, se asocia con una mayor percepción de meritocracia
-
-## Datos
-
-* Descripción de la muestra
-
-## Variables
-
-* Variable(s) dependiente(s)
-* Variables independientes
-
-* Descriptivos
-* Bivariados
-
-## Métodos
-
-# Resultados
-
-> Para referencias una imagen generada en ggplot2 debemos fijar un label en el chunk: ` ```{r biscuits}` Luego, en el texto, usamos el tag `\@ref(fig:label)` como en el ejemplo:
-
-```{r biscuits, echo=FALSE, fig.cap = "Relación entre biscuits y tea", fig.align='center',fig.width=10,fig.height=8,out.width='50%'}
-tea <- rnorm(100)
-biscuits <- tea + rnorm(100, 0, 1.3)
-data <- data.frame(tea, biscuits) 
-p <- ggplot(data, aes(x = tea, y = biscuits)) +
-    geom_point() + 
-    geom_smooth(method = "lm") + 
-    labs(x = "Tea", y = "Biscuits") + theme_bw() 
-print(p)
-```
-
-Como podemos ver la correlación en la Figura \@ref(fig:biscuits)
-
-> Para referencias una tabla generada en `knitr::kable()` debemos fijar un label en las opciones del chunk : ` ```{r modelo1}`. Luego, en el texto, usamos el tag `\@ref(tab:label)` como en el ejemplo:
-
-```{r modelo01, echo=FALSE}
-data(efc) # Cargar datos
-efc <- to_factor(efc, c161sex, e42dep, c172code) # convertir variables a factor
-m   <- lm(neg_c_7 ~ pos_v_4 + c12hour + e42dep + c172code, data = efc)# Modelo 1
-m2   <- lm(neg_c_7 ~ pos_v_4 + c12hour + e42dep , data = efc)         # Modelo 2
-broom::tidy(m) %>%                      # resumen de modelo en formato tidy
-  kable(format = table_format,          # formato de tabla ("html" o "latex")
-        caption = "Tabla de regresión", # Título de tabla
-        digits = 2,                     # decimales
-        booktabs= TRUE,                 # lineas horizontales de tabla
-        col.names = c("Variable","Coef.","SE","t","p")) %>% # etiquetas columnas
-  kable_styling(full_width = fwidth,                        # ancho de tabla
-                latex_options = c("HOLD_position")          # opciones de tabla pdf
-                )   
-```
-
-La Tabla \@ref(tab:modelo01) muestra los resultados del modelo de regresión. @Brady2014 lo enuncia.
-
-> En tablas que **NO SON** generadas con `knitr::kable()` debemos usar otro método:
-En este caso usamos: `paste("(\\#tab:model2)",cap)`, donde previamente definimos el objeto `cap` y luego usamos `paste0()` para unir ambos vectores de caracteres lo cual se debería ver así: `"(\\#tab:model2) Modelos de regresión para autos y sus partes."`
-
-```{r results='asis'}
-cap <- "Modelos de regresión para autos y sus partes." # Titulo de tabla
-custom.coef.names = c( # Custom names para coeficientes:                                                     
-  "Intercept",
-  "Positive value with 4 items",
-  "average number of hours of care per week",
-  "slightly dependent", "moderately dependent", "severely dependent",
-  "intermediate level of education","high level of education"
-  )
-# Custom footnote de tabla: 
-custom.note = "$^{***}$p < 0,001;$^{**}$p < 0,01;$^{*}$p < 0,05. Errores estándar robustos entre paréntesis (HC2)"
-# texreg::knitreg() decide si usar formato tabla html o latex según corresponda. 
-knitreg(list(m,m2),                            # Modelos 1 y 2
-       caption = paste("(\\#tab:model2)",cap), # Label para crossref + titulo  
-       caption.above = T,                      # Titulo de tabla arriba
-       custom.coef.names=custom.coef.names,    # Definir custom names para coeficientes
-       custom.note = custom.note,              # Definir footnote de tabla
-       booktabs = TRUE,                        # Usar líneas horizontales en tabla
-       scalebox = 0.75,                         # tamaño de tabla a .75
-       float.pos = "hp!"
-       )                        
-```
-
-Table \@ref(tab:model2) contrasta el Modelo 1 saturado, versus el Modelo 2 simplificado.
-
-# Conclusiones
-
-# References
-
-<div id="refs"> </div>  <!-- Aunque <div> es tag HTML, este método funciona para otros formatos de salida como el PDF. -->
-
-# (APPENDIX) Appendix {-}
-
-`r if (knitr::is_latex_output()){ '\\appendix'}`          <!-- Si documento es latex, se genera sección de Anexos -->
-`r if (knitr::is_latex_output()){ '\\section{Appendix}'}` <!-- Si documento es latex, se genera titulo de Anexos -->
-
-|                     | Sample  |   CEP  |
-|---------------------|:-------:|:------:|
-| __Gender__          |         |        |
-| Men                 | 49,82%  | 50,52% |
-| Women               | 50.18%  | 49,47% |
-| __Age__             |         |        |
-| 18 - 24             | 18,55%  | 18,17% |
-| 25 - 34             | 18,86%  | 17,48% |
-| 35 - 44             | 19.09%  | 19,98% |
-| 45 - 54             | 17,96%  | 19,23% |
-| 55 - or more        | 25,54%  | 25.11% |
-| __Education__       |         |        |
-| Primary  or less    | 2,93%   | 15,88% |
-| High school          | 43,23%  | 37,04% |
-| Non university      | 32,63%  | 28,93% |
-| university or more  | 21,21%  | 18,13% |
-Table: `r as.character(paste("(\\#tab:rep-samp)", "Representativeness of the sample"))`. <!-- Label+titulo de tabla en syntax Markdown pura -->
+- Economic inequality
+  - expected: economic inequality increases segregation (maybe weak or null effect)
+  - expected: increase redistributive preferences
+  - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger

### 2023-07-25 procesamiento/prod_analysis.Rmd
update

@@
 
-```{r}
+```{r class5}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
 
-```{r}
+```{r class3}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
 
-```{r}
+```{r correlation-socap}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
 load(here::here("input/data/proc/study1.RData"))
-
-df1 %>% 
-  group_by(class6) %>% 
-  summarise(mean(eindex,na.rm = T))
-
-df1 %>% 
-  select('redist',"eindex","hindex_sta","hindex_10","homclass","socdist","class6") %>% 
-  group_by(class6) %>% 
-  summarise(mean(homclass,na.rm = T))
-
 # df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
@@
        cex = 0.75)
+```
 
+```{r correlation-segregation}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2)
+load(here::here("input/data/proc/study1.RData"))
+# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
+cormat1 <- 
 df1 %>% 
-  select("eindex","hindex_sta","hindex_10","homclass","socdist","class6",class5) %>% 
-  group_by(class5) %>% 
-  summarise(mean(eindex,na.rm = T))
+    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3) %>% 
+  na.omit() %>% 
+  polycor::hetcor(parallel = T)
 
-sjPlot::tab_corr((df1[,c("eindex","hindex_sta","hindex_10","homclass","socdist")]),
-                 triangle = "lower") 
+  corrplot::corrplot(cormat1$correlations,
+    method = "color",
+    addCoef.col = "#000390",
+    type = "upper",
+    tl.col = "black",
+    col=colorRampPalette(c("white","#0068DC"))(12),
+    bg = "white",
+    na.label = "-")
+  text(4.7, 0.6, paste0("Source: Authors calculation based on ISSP 2017",
+                             " (N = ",")"),   
+       cex = 0.75)
 ```
@@
                         homclass,
+                        # homclass_s,homclass_w,
                         # prestige,
@@
                         Q05pcm,
+                        # sstatus,
+                        giniwd,
                         ednum,female,agenum,country) %>% na.omit()
+dim(dfreg)
 dfreg$country <- to_factor(dfreg$country)
 
-sjPlot::plot_model(lmer(pi_nteg~1 + female+agenum + homclass+class3 +ednum+ (1|country),data=dfreg))
+sjPlot::plot_model(lmer(redist~1 + female+agenum + homclass*giniwd + pi_nteg+class3 +ednum + Q05pcm + giniwd + (1+homclass|country),data=dfreg),show.values = T)
 
@@
                         homclass,
+                        # homclass_s,homclass_w,
                         prestige,

### 2023-07-25 procesamiento/prod_prep.Rmd
update

@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
 ---
@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,sjlabelled)
+pacman::p_load(dplyr,sjmisc,GGally,sjlabelled,tidyverse)
 df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
@@
 #frq(df1$pi_left)
+
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived integration"
 ```
@@
 
+# Country level
+
 ```{r}
-names(df1)
+countries <- 
+df1 %>% 
+  group_by(country) %>% 
+  summarise(n=n())
+countries$ccode <- as.numeric(countries$country)
+countries$countryname <- as_character(countries$country)
 ```
@@
 ```{r}
-save(df1,file = here::here("input/data/proc/study1.RData"))
+# install.packages("wbstats")
+library(wbstats)
+ineq<- c("3.0.Rate75-25","3.0.Rate90-10","SI.POV.GINI","3.0.Gini","3.0.Gini_nozero")
+# Gini
+giniwb <- wb_data("SI.POV.GINI", start_date = 2015, end_date = 2020,return_wide = F)
+gini_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
+gini_wb$ccode <- countrycode::countrycode(sourcevar = gini_wb$iso3c,origin = "iso3c",destination = "iso3n")
+gini_wb<- gini_wb %>% filter(ccode %in% countries$ccode)
+
+skimr::skim(gini_wb)
+
+gini_wb$giniwb <-  gini_wb$"2017"
+summary(gini_wb$giniwb)
+gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2018",no = gini_wb$giniwb)
+summary(gini_wb$giniwb)
+gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2016",no = gini_wb$giniwb)
+summary(gini_wb$giniwb)
+
+country_data <- 
+countries %>% left_join(select(gini_wb,iso3c,ccode,giniwb),by="ccode")
+
+# Rate 90-1
+rate90_10 <- wb_data("3.0.Rate90-10", start_date = 2015, end_date = 2020,return_wide = F)
+rate90_10_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
+rate90_10_wb$ccode <- countrycode::countrycode(sourcevar = rate90_10_wb$iso3c,origin = "iso3c",destination = "iso3n")
+rate90_10_wb<- rate90_10_wb %>% filter(ccode %in% countries$ccode)
+
 ```
+
+```{r}
+wiid<- haven::read_dta(here::here("input/data/original/WIID_30JUN2022_0/WIID_30JUN2022_0.dta"))
+summary(wiid$gini)
+gini_wiid <- wiid %>% select(c3,year,gini) %>% filter(year %in% c(2010:2020))
+summary(gini_wiid)
+
+gini_wiid <- panelr::widen_panel(data = panelr::panel_data(as.data.frame(gini_wiid), id = c3 , wave = year))
+gini_wiid$ccode <- countrycode::countrycode(sourcevar = gini_wiid$c3,origin = "iso3c",destination = "iso3n")
+
+gini_wiid<- gini_wiid %>% filter(ccode %in% countries$ccode)
+
+gini_wiid$giniwd <- gini_wiid$gini_2017
+summary(gini_wiid$giniwd)
+gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2018,no = gini_wiid$giniwd)
+summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2019,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2020,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2016,no = gini_wiid$giniwd)
+summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2015,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2014,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2013,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+# gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2012,no = gini_wiid$giniwd)
+# summary(gini_wiid$giniwd)
+
+country_data2 <- 
+country_data %>% left_join(gini_wiid[,c("ccode","giniwd","c3")],by="ccode")
+```
+
+```{r}
+df1$ccode <- as.numeric(df1$country)
+df2 <- 
+df1 %>% left_join(country_data2[,c("ccode","c3","giniwb","giniwd")],by = "ccode")
+```
+
+https://fsolt.org/swiid/
+
+```{r}
+names(df2)
+```
+
+```{r}
+df1 <- df2
+save(df2,file = here::here("input/data/proc/study1.RData"))
+```

### 2023-07-26 procesamiento/prod_analysis.Rmd
modelos ok

@@
 
+Modelos homogeneidad
+
+```{r class-homclass}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"))
+df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+frq(df1$Q05pcm)
+dfreg <- df1 %>% dplyr::select(redist,
+                        class6,class3,class5,
+                        # tr_inte,
+                        # eindex,
+                        # know_total,
+                        homclass,
+                        homclass_s,homclass_w,
+                        # prestige,
+                        # diversity,
+                        # pi_nteg,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        Q05pcm,labst,union,
+                        # sstatus,
+                        gini_disp,
+                        gini_mkt,
+                        # palmawd,
+                        rgdpna,
+                        # giniwb,
+                        # giniwd,
+                        ednum,female,agenum,country) %>% 
+  mutate(logrgdpna=log(rgdpna)) %>% 
+  # filter(country!=233) %>% 
+  na.omit()
+
+dfreg$homclass_bi <- ifelse(dfreg$homclass>0.5,1,0)
+frq(dfreg$homclass_bi)
+
+base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
+demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
+homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass + (1|country),data=dfreg)
+class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm + (1|country),data=dfreg)
+full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
+
+# Interactions segregation x class
+full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ ednum + Q05pcm + (1|country),data=dfreg)
+# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
+
+models <- list(homclass,class,class_status,full,full_int1)
+texreg::knitreg(models)
+
+sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
+ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
+       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)
+
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
+  ylab("Class-based homogeneity coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# Predicted values 
+pred1<- plot_model(full_int1,type = "int")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+
+ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# isolation <- 
+# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
+# df_int2 <- isolation$data
+# df_int2 <- df_int2[c(1,2,4),]
+# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+# df_int2
+# df_int2$value <- factor(df_int2$value,ordered = T,
+#                         levels = c("Working Class (V+VI+VII)",
+#                                    "Intermediate class (III+IV)",
+#                                    "Service Class (I+II)"))
+# 
+# df_int2 %>% 
+# ggplot() +
+#   geom_point(aes(x = value,y = coef1)) + 
+#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+#   ylab("Perceived isolation coefficient")+
+#   xlab("Social Class")+
+#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+#   geom_hline(yintercept = 0)
+# 
+# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+```
+
+```{r homclass-macro}
+# Interactions segregation x inequality
+full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass|country),data=dfreg)
+# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
+models_m <- list(full_int4)
+texreg::knitreg(models_m)
+
+interplot::interplot(m = full_int4,var1 = "homclass",var2="gini_disp") +
+  geom_point()+
+  ylab("Class-based homogeneity coefficient")+
+  xlab("Economic Inequality")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_homclass_gini.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
+#   geom_point()+
+#   ylab("Perceived isolation coefficient")+
+#   xlab("Economic Inequality")+
+#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+#   geom_hline(yintercept = 0)
+# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+Modelos strong ties
+
+```{r strong-ties}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"))
+df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+frq(df1$Q05pcm)
+dfreg <- df1 %>% dplyr::select(redist,
+                        class6,class3,class5,
+                        # tr_inte,
+                        # eindex,
+                        # know_total,
+                        homclass,
+                        homclass_s,
+                        homclass_w,
+                        # prestige,
+                        # diversity,
+                        # pi_nteg,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        Q05pcm,labst,union,
+                        # sstatus,
+                        gini_disp,
+                        gini_mkt,
+                        # palmawd,
+                        rgdpna,
+                        # giniwb,
+                        # giniwd,
+                        ednum,female,agenum,country) %>% 
+  mutate(logrgdpna=log(rgdpna)) %>% 
+  # filter(country!=233) %>% 
+  na.omit()
+dim(dfreg)
+base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
+demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
+homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_s + (1|country),data=dfreg)
+class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + (1|country),data=dfreg)
+full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)
+
+# Interactions segregation x class
+full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s*class3+ ednum + Q05pcm + (1|country),data=dfreg)
+# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
+
+models <- list(homclass,class,class_status,full,full_m,full_int1)
+texreg::knitreg(models)
+
+# Conditional Marginal effect---------------------------------------------------
+interplot <- 
+interplot::interplot(m = full_int1,var1 = "homclass_s",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  ylab("Class-based homogeneity (s) coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_strong-ties_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# Predicted values -------------------------------------------------------------
+pred1<- plot_model(full_int1,type = "int")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
+  xlab("Network homogeneity (strong ties)")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+
+ggsave(plot = last_plot(),filename = "pred_strong-ties_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# isolation <- 
+# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
+# df_int2 <- isolation$data
+# df_int2 <- df_int2[c(1,2,4),]
+# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+# df_int2
+# df_int2$value <- factor(df_int2$value,ordered = T,
+#                         levels = c("Working Class (V+VI+VII)",
+#                                    "Intermediate class (III+IV)",
+#                                    "Service Class (I+II)"))
+
+# df_int2 %>% 
+# ggplot() +
+#   geom_point(aes(x = value,y = coef1)) + 
+#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+#   ylab("Perceived isolation coefficient")+
+#   xlab("Social Class")+
+#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+#   geom_hline(yintercept = 0)
+
+# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+```
+
+```{r strong-ties-macro}
+# Interactions segregation x inequality
+full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s*gini_disp+ednum + Q05pcm +logrgdpna + (1+homclass_s|country),data=dfreg)
+# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s+pi_nteg*gini_disp+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
+
+models_m <- list(full_int4)
+texreg::knitreg(models_m)
+
+interplot::interplot(m = full_int4,var1 = "homclass_s",var2="gini_disp") +
+  geom_point()+
+  ylab("Class-based homogeneity (s) coefficient")+
+  xlab("Economic Inequality")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_strong-ties_gini.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
+#   geom_point()+
+#   ylab("Perceived isolation coefficient")+
+#   xlab("Economic Inequality")+
+#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+#   geom_hline(yintercept = 0)
+# 
+# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+Modelos weak ties
+
+```{r weak-ties}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"))
+df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (I+II)"
+                                           ))
+df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
+                                           "Routine non-manual (IIIa+b)",
+                                           "Skilled manual workers and supv. (V+VI)",
+                                           "Non-skilled manual workers (VIIa+b)",
+                                           "Service class (II - lower grade)",
+                                           "Service class (I - higher grade)" 
+                                           ))
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+frq(df1$Q05pcm)
+dfreg <- df1 %>% dplyr::select(redist,
+                        class6,class3,class5,
+                        # tr_inte,
+                        # eindex,
+                        # know_total,
+                        homclass,
+                        homclass_s,
+                        homclass_w,
+                        # prestige,
+                        # diversity,
+                        # pi_nteg,
+                        # isei_range,
+                        # hindex_sta,
+                        # hindex_10,
+                        Q05pcm,labst,union,
+                        # sstatus,
+                        gini_disp,
+                        gini_mkt,
+                        # palmawd,
+                        rgdpna,
+                        # giniwb,
+                        # giniwd,
+                        ednum,female,agenum,country) %>% 
+  mutate(logrgdpna=log(rgdpna)) %>% 
+  # filter(country!=233) %>% 
+  na.omit()
+dim(dfreg)
+base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
+demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
+homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_w + (1|country),data=dfreg)
+class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
+class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
+full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + (1|country),data=dfreg)
+full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)
+
+# Interactions segregation x class
+full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_w*class3+ ednum + Q05pcm + (1|country),data=dfreg)
+# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
+
+models <- list(homclass,class,class_status,full,full_m,full_int1)
+texreg::knitreg(models)
+
+# Conditional Marginal effect---------------------------------------------------
+interplot <- 
+interplot::interplot(m = full_int1,var1 = "homclass_w",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  ylab("Class-based homogeneity (w) coefficient")+
+  xlab("Social Class")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_weak-ties_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# Predicted values -------------------------------------------------------------
+pred1<- plot_model(full_int1,type = "int")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
+  xlab("Network homogeneity (weak ties)")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+
+ggsave(plot = last_plot(),filename = "pred_weak-ties_class.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+
+```
+
+```{r weak-ties-macro}
+# Interactions segregation x inequality
+full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_w*gini_disp+ednum + Q05pcm +logrgdpna + (1+homclass_w|country),data=dfreg)
+# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s+pi_nteg*gini_disp+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
+
+models_m <- list(full_int4)
+texreg::knitreg(models_m)
+
+interplot::interplot(m = full_int4,var1 = "homclass_w",var2="gini_disp") +
+  geom_point()+
+  ylab("Class-based homogeneity (w) coefficient")+
+  xlab("Economic Inequality")+
+  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
+  theme(plot.title = element_text(size = 8))
+
+ggsave(plot = last_plot(),filename = "mar_weak-ties_gini.png",device = "png",
+       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
+
+# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
+#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+```
+
+# Modelos alternativos
+
 ```{r isei}
@@
 
-```{r class-homclass}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
-load(here::here("input/data/proc/study1.RData"))
-
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class6,
-                        class3,
-                        class5,
-                        # eindex,
-                        # know_total,
-                        homclass,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,
-                        # sstatus,
-                        giniwd,
-                        ednum,female,agenum,country) %>% na.omit()
-dim(dfreg)
-dfreg$country <- to_factor(dfreg$country)
-
-sjPlot::plot_model(lmer(redist~1 + female+agenum + homclass*giniwd + pi_nteg+class3 +ednum + Q05pcm + giniwd + (1+homclass|country),data=dfreg),show.values = T)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + homclass+ (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass + pi_nteg + Q05pcm + (1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ pi_nteg+ ednum +(1|country),data=dfreg)
-full_int3 <- lmer(redist~1 +female+agenum + homclass+pi_nteg*class3+ pi_nteg+ ednum + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_int1,full_int3)
-texreg::knitreg(models)
-texreg::knitreg(full)
-sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
-ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
-       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)
-
-interplot <- 
-interplot::interplot(m = full_int2,var1 = "homclass",var2="class3")
-
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Class-based homogeneity coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_homoxclass.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-isolation <- 
-interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-df_int2 <- isolation$data
-df_int2 <- df_int2[c(1,2,4),]
-df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int2
-df_int2$value <- factor(df_int2$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int2 %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Perceived isolation coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
-
 ```{r eindex}

### 2023-07-26 procesamiento/prod_prep-country.Rmd
modelos ok

---
title: "Data preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica
if (!require("pacman")) install.packages("pacman") # instalar pacman
load(here::here("input/data/proc/study1.RData"))
pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse)
```

# Country level

```{r}
countries <- 
df1 %>% 
  group_by(country) %>% 
  summarise(n=n())
countries$ccode <- as.numeric(countries$country)
countries$countryname <- as_character(countries$country)
```

# Economic inequality

```{r world-bank, eval=FALSE, include=FALSE}
# install.packages("wbstats")
library(wbstats)
ineq<- c("3.0.Rate75-25","3.0.Rate90-10","SI.POV.GINI","3.0.Gini","3.0.Gini_nozero")
# Gini
giniwb <- wb_data("SI.POV.GINI", start_date = 2015, end_date = 2020,return_wide = F)
gini_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
gini_wb$ccode <- countrycode::countrycode(sourcevar = gini_wb$iso3c,origin = "iso3c",destination = "iso3n")
gini_wb<- gini_wb %>% filter(ccode %in% countries$ccode)

skimr::skim(gini_wb)

gini_wb$giniwb <-  gini_wb$"2017"
summary(gini_wb$giniwb)
gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2018",no = gini_wb$giniwb)
summary(gini_wb$giniwb)
gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2016",no = gini_wb$giniwb)
summary(gini_wb$giniwb)

# Rate 90-1
rate90_10 <- wb_data("3.0.Rate90-10", start_date = 2015, end_date = 2020,return_wide = F)
rate90_10_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
rate90_10_wb$ccode <- countrycode::countrycode(sourcevar = rate90_10_wb$iso3c,origin = "iso3c",destination = "iso3n")
rate90_10_wb<- rate90_10_wb %>% filter(ccode %in% country_data$ccode)

# Rate 90-1
rate75_25 <- wb_data("3.0.Rate75-25", start_date = 2015, end_date = 2020,return_wide = F)
rate75_25_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
rate75_25_wb$ccode <- countrycode::countrycode(sourcevar = rate75_25_wb$iso3c,origin = "iso3c",destination = "iso3n")
rate75_25_wb<- rate75_25_wb %>% filter(ccode %in% country_data$ccode)

country_data <- 
countries %>% left_join(select(gini_wb,iso3c,ccode,giniwb),by="ccode")
```

```{r WIID}
wiid<- haven::read_dta(here::here("input/data/original/WIID_30JUN2022_0/WIID_30JUN2022_0.dta"))
summary(wiid$gini)

gini_wiid <- wiid %>% dplyr::select(c3,year,gini,palma) %>% dplyr::filter(year %in% c(2014:2019))
summary(gini_wiid)

gini_wiid <- panelr::widen_panel(data = panelr::panel_data(as.data.frame(gini_wiid), id = c3 , wave = year))
gini_wiid$ccode <- countrycode::countrycode(sourcevar = gini_wiid$c3,origin = "iso3c",destination = "iso3n")

gini_wiid<- gini_wiid %>% filter(ccode %in% countries$ccode)

gini_wiid$giniwd <- gini_wiid$gini_2017
summary(gini_wiid$giniwd)
gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2018,no = gini_wiid$giniwd)
summary(gini_wiid$giniwd)
gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2016,no = gini_wiid$giniwd)
summary(gini_wiid$giniwd)

skimr::skim(gini_wiid)

gini_wiid$palmawd <- gini_wiid$palma_2017
summary(gini_wiid$palmawd)
gini_wiid$palmawd <- ifelse(is.na(gini_wiid$palmawd),gini_wiid$palma_2018,no = gini_wiid$palmawd)
summary(gini_wiid$palmawd)
gini_wiid$palmawd <- ifelse(is.na(gini_wiid$palmawd),gini_wiid$palma_2016,no = gini_wiid$palmawd)
summary(gini_wiid$palmawd)

country_data2 <- 
countries %>% left_join(gini_wiid[,c("ccode","c3","giniwd","palmawd")],by="ccode")
```

```{r Solt}
load(file = here::here("input/data/original/swiid9_5/swiid9_5.rda"))
solt <- 
swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt) %>% dplyr::filter(year %in% c(2016))
solt$ccode <- countrycode::countrycode(sourcevar = solt$country,origin = "country.name",destination = "iso3n")
solt$country <- NULL
solt <-  solt %>% filter(ccode %in% country_data2$ccode)
country_data3 <- country_data2 %>% 
  left_join(solt,by="ccode")
```

# GDP

```{r pen-data}
pendata<- haven::read_dta(file = "input/data/original/pen-world/pwt1001.dta")
pendata$ccode <- countrycode::countrycode(sourcevar = pendata$countrycode,origin = "iso3c",destination = "iso3n")
pen <- pendata %>% filter(ccode %in% countries$ccode,year %in% 2017)

skimr::skim(pen)
country_data4 <- country_data3 %>% 
  left_join(pen,by="ccode")
```

```{r merge}
df1$ccode <- as.numeric(df1$country)
df2 <- 
df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","palmawd","rgdpna")],by = "ccode")
```

```{r save}
save(df2,file = here::here("input/data/proc/study1_country.RData"))
```

### 2023-07-26 procesamiento/prod_prep.Rmd
modelos ok

--- 2023-07-24 procesamiento/prod_prep.Rmd
@@
 #frq(df1$pi_left)
+
+df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$pi_nteg) <- "Perceived integration"
+```
+
+# Trust
+
+```{r}
+df1$tr_inte <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
+df1$tr_inte <- set_na(df1$tr_inte,na = c(0,8,9))
+df1$tr_inte <- sjmisc::rec(x = df1$tr_inte,rec = "rev")
+sjlabelled::set_label(df1$tr_inte) <- "Interpersonal trust"
+frq(df1$tr_inte)
+
+df1$tr_courts <- car::recode(df1$v36,recodes = "c(98,99)=NA")
+df1$tr_courts <- set_na(df1$tr_courts,na = c(98,99))
+# df1$tr_courts <- sjmisc::rec(x = df1$tr_courts,rec = "rev")
+sjlabelled::set_label(df1$tr_courts) <- "Trust in courts"
+frq(df1$tr_courts)
 ```
@@
 
+# Group-mean center
+
 ```{r}
-names(df1)
+
 ```
@@
 ```{r}
+df1
 save(df1,file = here::here("input/data/proc/study1.RData"))

### 2023-09-19 paper.Rmd
ajuste modelos

@@
 ---
-title: "Lorem ipsum dolor sit amet"
+title: "Network segregation, Social Isolation and Preference for Redistribution across societies"
 css: "input/css/custom.css" # custom CSS para html
@@
 author:
-- name: Duke A Caboom
-  affiliation: University of Tuktoyaktuk
-  email: dtholmes@mail.ubc.ca
-  number: 1
-- name: Justin d'Ottawa
-  affiliation: University of Ottawa
-  number: 2
-- name: Pedro Torres
-  number: 1,2 
+# - name: Julio Iturra-Sanhueza
+#   affiliation: University of Bremen
+#   email: jiturra@uni-bremen.de
+#   number: 1
+# - name: Justin d'Ottawa
+#   affiliation: University of Ottawa
+#   number: 2
+# - name: Pedro Torres
+#   number: 1,2 
 # Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
-abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua.
+# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua.
 Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
 output:
+  bookdown::html_document2:
+    number_sections: false
   bookdown::pdf_document2:
@@
       - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
-  bookdown::html_document2:
-    number_sections: false
 linkcolor: blue                         # enlaces y citas en color azul
@@
 options(knitr.kable.NA = '') # NA en kable = ''
-
-table_format = if(is_html_output()) { # Usar en argumento "format=" de kable
-  "html"
-} else if(is_latex_output()) {
-  "latex"
-}
-
-fwidth = if(is_html_output()) { #Usar en argumento "full_width" de kableExtra
-  T
-} else if(is_latex_output()) {
-  F
-}
 ```
@@
 - class x network segregation 
-
 - the influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
@@
   - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger
+
+The structure of the social network provide access to social resources.
+On the one hand, contacts can be translated into resources, access to the life of others that could provide information and life opportunities.
+
+- stratified access to resources
+- class and networks (focus of this paper)
+
+Some research has connected social capital with economic rational dimension, while others have conected it to more value-driven or moralistic dimension
+
+Both assume direct effects,but other literature such as Otero et al has suggested that experiences might vary across social classes.
+
+For example, we trust other people because we know about them (connected)
+
+<!-- Across all countries, a nurse (41.2%) and a schoolteacher (39.6%) are mentioned the most often and a human resource manager (19.2%) and a lawyer (22.2%) the least often.
+Considering the scope of the network, Suriname (42%), the United States (41.4%), and Iceland (41.3%) are the countries in which respondents are connected to the widest array of occupations, while Thailand (13.2%), Japan (15%), and Taiwan (18.9%) represent the other end.
+The social network thus is larger and more diverse in the former countries -->
+
+# Results
+
+## Descriptive
+
+```{r redistribution}
+# x country
+
+```
+
+```{r homogeneity}
+# x country
+```
+
+```{r macro}
+
+```
+
+- class x homogeneity (3 plots)
+- homogeneity x redistribution (1 plot)
+- perceived isolation x redistribution (1 plot)
+- homogeneity x perceived isolation (1 plot)
+
+## Multivariate
+
+```{r,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        incomepcap,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,pi_isola,
+                        # union,
+                        # labst,
+                        # WEIGHT
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna)) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
+  na.omit()
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+homclass <- lmer(redist~1 + female+agenum + homclass +(1|country2),data=dfreg)
+class <- lmer(redist~1 +female+agenum + class3+(1|country2),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+incomepcap+(1|country2),data=dfreg)
+# Interactions segregation x class
+full_int1 <- lmer(redist~1 +female+agenum + edyears + incomepcap + homclass*class3 +(1|country2),data=dfreg)
+models <- list(homclass,class,full,full_int1)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+omitcoef <- "(Intercept)|(agenum)|(female)|(incomepcap)|(edyears)|(logrgdpna)"
+coefname <- c("Network class homogeneity","Service Class","Working Class",
+              "Homogeneity x Service Class","Homogeneity x Working Class")
+coefgroup <- list("Social Class (ref: Intermediate class)"=2:3,"Interaction:"=4:5)
+gofrow <-  list(Controls=c("Yes","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. countries:","Var: Group",NA)
+
+texreg::knitreg(models)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  omit.coef = omitcoef,include.thresholds=FALSE,
+                  custom.coef.names = coefname,
+                  groups = coefgroup,custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1)
+```
+
+## Interactions
+
+```{r inter1,fig.height=5,fig.width=7,fig.cap=c("Conditional marginal effects for network class-based homogeneity on preferences for redistribution","Conditional predicted values")}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        Q05pcm,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        ednum,
+                        female,
+                        agenum,
+                        country2,pi_isola,
+                        # union,
+                        # labst,
+                        # WEIGHT
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna)) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
+  na.omit()
+# Interactions segregation x class
+full_int1 <- lmer(redist~1 +female+agenum + ednum + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
+  ylab("Class-based homogeneity coefficient")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +  
+  theme(plot.title = element_text(size = 8))
+
+# Predicted values 
+pred1<- plot_model(full_int1,type = "int")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+```
+
+```{r intermacro}
+
+```

### 2023-09-19 procesamiento/prod_analysis-models.Rmd
ajuste modelos

---
title: "Multilevel regression models"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

- mantener clase R´s y calcular homogeneidad
- mantener clase de Partner a parte como un control

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```

# Modelos

dicotomizar homogeneidad en 1=50% similar,49% similar

Modelos homogeneidad

```{r class-homclass}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_gc,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,
                        female,
                        agenum,
                        country2,
                        # WEIGHT
                        ) %>% 
  mutate(logrgdpna=log(rgdpna)) %>%
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)

base <- lmer(redist~1 + (1|country2),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + (1|country2),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + homclass + (1|country2),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+ (1|country2),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country2),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm + (1|country2),data=dfreg)
full_b <- lmer(redist~1 +female+agenum + class3 +ednum+homclass_gc +  Q05pcm + (1|country2),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1|country2),data=dfreg)
full_m_rs <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1+homclass|country2),data=dfreg)

anova(full_m,full_m_rs)
plot_model(full_m_rs,type = "re")
# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + ednum + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,full,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
```

```{r homclass-gini}
# Interactions segregation x inequality
df1$homclass_gc <- MLMusingR::group_center(df1$homclass,df1$country) 
df1$logrgdpna=log(df1$rgdpna)
df1$ratio10_50 <- df1$pc10_2017/df1$pc50_2017

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
int_giniot<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)

# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090,int_giniot)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_gc",var2="gini_disp")+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_mkt)

df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_disp)

p3<- interplot::interplot(m = int_palma,var1 = "homclass_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "homclass_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "homclass_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "homclass_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

p7<- interplot::interplot(m = int_giniot,var1 = "homclass_gc",var2="gini") +
  xlab("Gini (WD)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation × Inequality")

ggsave(plot = g,filename = "mar_homclass_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

```{r class-homclass-res}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")

df1$class3spo <-  car::recode(df1$class3spo,recodes = "NA='No information'")
frq(df1$class3spo)
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class3res,
                        # class3spo,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass_res,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        labst,
                        union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)

dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_res + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3res+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3res+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3res + ednum+homclass_res +  Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3res+ednum+homclass_res +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_res*class3res+ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass_res",var2="class3res")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Class-based homogeneity (R's) coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homores_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Network homogeneity (R's)")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_homores_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))
# 
# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# 
# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r homclass-macro-res}
# Interactions segregation x inequality
df1$homclass_res_gc <- MLMusingR::group_center(df1$homclass_res,df1$country) 
df1$logrgdpna=log(df1$rgdpna)

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_res_gc",var2="gini_disp")+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_res_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

p3<- interplot::interplot(m = int_palma,var1 = "homclass_res_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "homclass_res_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "homclass_res_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "homclass_res_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (R's) × Inequality")

ggsave(plot = g,filename = "mar_homclass_rs_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

Modelos strong ties

```{r strong-ties}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        # homclass,
                        homclass_s,
                        # homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,labst,union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)
dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_s + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_m,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect---------------------------------------------------
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass_s",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity (s) coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_strong-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values -------------------------------------------------------------
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  xlab("Network homogeneity (strong ties)")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_strong-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))

# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)

# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r strong-ties-macro}
df1$homclass_s_gc <- MLMusingR::group_center(df1$homclass_s,df1$country) 
df1$logrgdpna=log(df1$rgdpna)

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_s_gc",var2="gini_disp")+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_s_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

p3<- interplot::interplot(m = int_palma,var1 = "homclass_s_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "homclass_s_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "homclass_s_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "homclass_s_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (strong ties) × Inequality")

ggsave(plot = g,filename = "mar_homclass_st_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

Modelos weak ties

```{r weak-ties}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_s,
                        homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,labst,union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country,) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)
dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_w + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_w*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_m,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect---------------------------------------------------
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass_w",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity (w) coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_weak-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values -------------------------------------------------------------
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  xlab("Network homogeneity (weak ties)")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_weak-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r weak-ties-macro}
df1$homclass_w_gc <- MLMusingR::group_center(df1$homclass_w,df1$country) 
df1$logrgdpna=log(df1$rgdpna)

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_w_gc",var2="gini_disp")+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_w_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

p3<- interplot::interplot(m = int_palma,var1 = "homclass_w_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "homclass_w_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "homclass_w_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "homclass_w_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (weak ties) × Inequality")

ggsave(plot = g,filename = "mar_homclass_wt_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

# Models perceived isolation

```{r class-pinsolation}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_gc,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        labst,
                        union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)

dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
full_b <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
full_m_rs <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1+pi_nteg|country),data=dfreg)

plot_model(full_m_rs,type = "re")
anova(full_m,full_m_rs)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + pi_nteg*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_b,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "pi_nteg",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Perceived Isolation coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_pisolation_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_pisolation_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))
# 
# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# 
# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r pinsolation-macro}
# Interactions segregation x inequality
df1$pi_isola_gc <- MLMusingR::group_center(df1$pi_isola,df1$country) 
df1$logrgdpna=log(df1$rgdpna)
df1$ratio10_50 <- df1$pc10_2017/df1$pc50_2017

df1$homclass

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_giniot<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)

# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090,int_giniot)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "pi_isola_gc",var2="gini_disp")+
  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "pi_isola_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_mkt)

df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_disp)

p3<- interplot::interplot(m = int_palma,var1 = "pi_isola_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "pi_isola_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "pi_isola_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "pi_isola_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

p7<- interplot::interplot(m = int_giniot,var1 = "pi_isola_gc",var2="gini") +
  xlab("Gini (WD)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Perceived Isolation × Inequality")

ggsave(plot = g,filename = "mar_pisolation_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

# Modelos alternativos

```{r eindex-homclass}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        eindex,
                        # know_total,
                        # homclass,
                        # homclass_gc,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        labst,
                        union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)

dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  eindex + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm + (1|country),data=dfreg)
full_b <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+eindex +  Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+eindex +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_b,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "eindex",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))
# 
# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# 
# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r eindex-macro}
# Interactions segregation x inequality
df1$homclass_gc <- MLMusingR::group_center(df1$homclass,df1$country) 
df1$logrgdpna=log(df1$rgdpna)

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)

# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(int_ginidis,int_ginimkt,int_palma,int_giniwd)
texreg::knitreg(models_m)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_gc",var2="gini_disp")+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p2$data$fake[p2$data$ub>0]
min(p2$data$fake[p2$data$ub>0])
max(p2$data$fake[p2$data$ub>0])

df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_mkt)

df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
  group_by(country) %>% 
  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
  arrange(gini_disp)

p3<- interplot::interplot(m = int_palma,var1 = "homclass_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
grid.arrange(p1,p2,p3,nrow = 1)
g<- arrangeGrob(p1,p2,p3,nrow = 1,top = "Network segregation")

ggsave(plot = g,filename = "mar_homclass_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 12)

interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
  geom_point()+
  ylab("Class-based homogeneity coefficient")+
  xlab("Economic Inequality")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homclass_gini.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
#   geom_point()+
#   ylab("Perceived isolation coefficient")+
#   xlab("Economic Inequality")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r isei, eval=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(sjmisc,ggplot2,lme4,interplot)
load(here::here("input/data/proc/study1.RData"))
# remove.packages("Matrix")
# install.packages("Matrix")
df1$class3<-forcats::fct_rev(df1$class3)
df1$class5<-forcats::fct_rev(df1$class5)
df1$class6<-forcats::fct_rev(df1$class6)
dfreg <- df1 %>% dplyr::select(redist,
                        isei08,
                        eindex,
                        prestige,
                        diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()

dfreg$country <- to_factor(dfreg$country)
dim(dfreg)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ eindex + (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1+female+agenum+isei08+ednum+prestige+diversity+eindex+(1|country),data=dfreg)
full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
full_int2 <- lmer(redist~1+female+agenum+prestige+diversity+eindex*isei08+ednum+(1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

texreg::plotreg(full,omit.coef = "(Intercept)")

interplot::interplot(m = full_int1,var1 = "eindex",var2="isei08") +
  ylab("Network diversity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

#-----------
dfreg <- df1 %>% select(redist,
                        isei08,
                        eindex,
                        prestige,
                        # diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()

dim(dfreg)
base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)

class <- lmer(redist~1+female+agenum+isei08+(1|country),data=dfreg)
class_status <- lmer(redist~1+female+agenum+isei08+ednum+(1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1|country),data=dfreg)
fullrs <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1+eindex|country),data=dfreg)
full_int1 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1|country),data=dfreg)
full_int2 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1+eindex|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

texreg::plotreg(full, omit.coef = "(Intercept)")

interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
  ylab("Network heterogeneity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
# en la medida que aumenta el status, el efecto de la diversidad de la red se vuelve positivo.
# en personas de estatus bajo la diversidad hace que demanden menos redistribucion
# en personas de estatus alto la diversidad hace que demanden más redistribucion
```

```{r class-diversity, eval=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
load(here::here("input/data/proc/study1.RData"))

levels(df1$class3)
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
levels(df1$class3)
levels(df1$class5)
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))

df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
levels(df1$class6)

dfreg <- df1 %>% select(redist,
                        class6,
                        class3,
                        class5,
                        # eindex,
                        prestige,
                        diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()
dim(dfreg)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class6 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

interplot::interplot(m = full_int1,var1 = "diversity",var2="class3") +
  ylab("Network diversity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

```

### 2023-09-19 procesamiento/prod_analysis.Rmd
ajuste modelos

--- 2023-07-25 procesamiento/prod_analysis.Rmd
@@
 df1$redistF <- factor(df1$redist,levels = 1:5,labels = sjlabelled::get_labels(df1$redist))
+
+df1 %>%
+  group_by(country2, ) %>%
+  summarise(redist = mean(redist, na.rm = T)) %>% 
+  View()
+
 percentage_data <- df1 %>%
@@
   arrange(percentage) %>% 
-  select(country2)
+  dplyr::select(country2)
 
@@
 df1 %>% 
-    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3) %>% 
+    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3,) %>% 
   na.omit() %>% 
@@
 ```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
+load(here::here("input/data/proc/study1.RData"))
 df1$country2 <- sjlabelled::to_character(df1$country)
@@
 
-# Modelos
+# macro correlations
 
-dicotomizar homogeneidad en 1=50% similar,49% similar
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,sjmisc,ggplot2,haven)
+load(here::here("input/data/proc/study1_country.RData"))
+df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
+df2$country3 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "iso3c")
+df2 <- bind_cols(df2,sjmisc::to_dummy(x = df2$class3,suffix = "numeric"))
 
-```{r isei}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(sjmisc,ggplot2,lme4,interplot)
-load(here::here("input/data/proc/study1.RData"))
-# remove.packages("Matrix")
-# install.packages("Matrix")
-df1$class3<-forcats::fct_rev(df1$class3)
-df1$class5<-forcats::fct_rev(df1$class5)
-df1$class6<-forcats::fct_rev(df1$class6)
-dfreg <- df1 %>% dplyr::select(redist,
-                        isei08,
-                        eindex,
-                        prestige,
-                        diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
+macro_data <- df2 %>%
+  group_by(country2,country3) %>%
+  summarise_at(c("redist","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
+                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
 
-dfreg$country <- to_factor(dfreg$country)
-dim(dfreg)
+macro_data %>%  
+ggplot(aes(y=redist, x=homclass)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Class homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(title = "Redistributive preferences and Class homogeneity",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$redist, use='complete.obs'),digits = 2)))
 
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ eindex + (1|country),data=dfreg)
+ggsave(plot = last_plot(),filename = "macro_homo_redist.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
-class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1+female+agenum+isei08+ednum+prestige+diversity+eindex+(1|country),data=dfreg)
-full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
-full_int2 <- lmer(redist~1+female+agenum+prestige+diversity+eindex*isei08+ednum+(1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
+macro_data %>%  
+ggplot(aes(y=redist, x=pi_isola)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Perceived isolation")+
+  ylab("Redistributive preferences") +
+  labs(title = "Redistributive preferences and Perceived isolation",
+       caption =paste("r=",round(cor(macro_data$pi_isola,
+                                     macro_data$redist, use='complete.obs'),digits = 2)))
 
-texreg::plotreg(full,omit.coef = "(Intercept)")
+ggsave(plot = last_plot(),filename = "macro_pisol_redist.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
-interplot::interplot(m = full_int1,var1 = "eindex",var2="isei08") +
-  ylab("Network diversity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
+macro_data %>%  
+ggplot(aes(y=pi_isola, x=homclass)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Class homogeneity")+
+  ylab("Perceived isolation") +
+  labs(title = "Perceived isolation and Class homogeneity",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$pi_isola),digits = 2)))
+ggsave(plot = last_plot(),filename = "macro_homo_pisol.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
-ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+macro_data %>%  
+ggplot(aes(y=homclass, x=class3_3)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Working class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Working class (%)",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$class3_3),digits = 2)))
 
-#-----------
-dfreg <- df1 %>% select(redist,
-                        isei08,
-                        eindex,
-                        prestige,
-                        # diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
+ggsave(plot = last_plot(),filename = "macro_working_homo.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
-dim(dfreg)
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
+macro_data %>%  
+ggplot(aes(y=homclass, x=class3_2)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Intermediate class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Intermediate class (%)",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$class3_2),digits = 2)))
 
-class <- lmer(redist~1+female+agenum+isei08+(1|country),data=dfreg)
-class_status <- lmer(redist~1+female+agenum+isei08+ednum+(1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1|country),data=dfreg)
-fullrs <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1+eindex|country),data=dfreg)
-full_int1 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1|country),data=dfreg)
-full_int2 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1+eindex|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
+ggsave(plot = last_plot(),filename = "macro_middle_homo.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
-texreg::plotreg(full, omit.coef = "(Intercept)")
+macro_data %>%  
+ggplot(aes(y=homclass, x=class3_1)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Service class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Service class (%)",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$class3_1),digits = 2)))
 
-interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
-  ylab("Network heterogeneity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-# en la medida que aumenta el status, el efecto de la diversidad de la red se vuelve positivo.
-# en personas de estatus bajo la diversidad hace que demanden menos redistribucion
-# en personas de estatus alto la diversidad hace que demanden más redistribucion
-```
-
-```{r class-diversity}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
-load(here::here("input/data/proc/study1.RData"))
-
-levels(df1$class3)
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-levels(df1$class3)
-levels(df1$class5)
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-levels(df1$class6)
-
-dfreg <- df1 %>% select(redist,
-                        class6,
-                        class3,
-                        class5,
-                        # eindex,
-                        prestige,
-                        diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
-dim(dfreg)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class6 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-interplot::interplot(m = full_int1,var1 = "diversity",var2="class3") +
-  ylab("Network diversity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
+ggsave(plot = last_plot(),filename = "macro_service_homo.png",device = "png",
+       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
 
 ```
-
-```{r class-homclass}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
-load(here::here("input/data/proc/study1.RData"))
-
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class6,
-                        class3,
-                        class5,
-                        # eindex,
-                        # know_total,
-                        homclass,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,
-                        # sstatus,
-                        giniwd,
-                        ednum,female,agenum,country) %>% na.omit()
-dim(dfreg)
-dfreg$country <- to_factor(dfreg$country)
-
-sjPlot::plot_model(lmer(redist~1 + female+agenum + homclass*giniwd + pi_nteg+class3 +ednum + Q05pcm + giniwd + (1+homclass|country),data=dfreg),show.values = T)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + homclass+ (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass + pi_nteg + Q05pcm + (1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ pi_nteg+ ednum +(1|country),data=dfreg)
-full_int3 <- lmer(redist~1 +female+agenum + homclass+pi_nteg*class3+ pi_nteg+ ednum + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_int1,full_int3)
-texreg::knitreg(models)
-texreg::knitreg(full)
-sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
-ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
-       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)
-
-interplot <- 
-interplot::interplot(m = full_int2,var1 = "homclass",var2="class3")
-
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Class-based homogeneity coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_homoxclass.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-isolation <- 
-interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-df_int2 <- isolation$data
-df_int2 <- df_int2[c(1,2,4),]
-df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int2
-df_int2$value <- factor(df_int2$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int2 %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Perceived isolation coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
-
-```{r eindex}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
-load(here::here("input/data/proc/study1.RData"))
-
-levels(df1$class3)
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-levels(df1$class3)
-levels(df1$class5)
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-levels(df1$class6)
-
-dfreg <- df1 %>% select(redist,
-                        class6,
-                        class3,
-                        class5,
-                        eindex,
-                        homclass,
-                        # homclass_s,homclass_w,
-                        prestige,
-                        diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
-
-dim(dfreg)
-cor(dfreg[,c("eindex","prestige","diversity")])
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-eindex <- lmer(redist~1 + female+agenum + prestige +diversity+eindex+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class6 +ednum + prestige +diversity+ eindex +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum + (1+eindex|country),data=dfreg)
-models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + eindex +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum + (1+eindex|country),data=dfreg)
-models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + eindex +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum + (1+eindex|country),data=dfreg)
-models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-interplot <- 
-interplot::interplot(m = full_int2,var1 = "eindex",var2="class3") +
-  ylab("Network heterophily coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Network heterophily coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_hetxclass.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```

### 2023-09-19 procesamiento/prod_prep-country.Rmd
ajuste modelos

@@
 
+```{r wid-dataset}
+wid <- 
+  read.csv(file = here::here("input/data/original/wid-percentiles/WID_Data_Metadata/WID_Data_28072023-104940.csv"),sep = ";")
+country_data3 <- country_data3 %>% 
+  left_join(wid,by="ccode")
+summary(country_data3)
+```
+
+```{r otero23}
+otero <- 
+  read.csv(file = here::here("input/data/original/otero23.csv"),sep = ";")
+otero$ccode <- countrycode::countrycode(sourcevar = otero$iso3n,origin = "iso2c",destination = "iso3n")
+country_data3 <- country_data3 %>% 
+  left_join(otero,by="ccode")
+summary(country_data3)
+```
+
 # GDP
@@
 ```{r pen-data}
-pendata<- haven::read_dta(file = "input/data/original/pen-world/pwt1001.dta")
+pendata<- haven::read_dta(file = here::here("input/data/original/pen-world/pwt1001.dta"))
 pendata$ccode <- countrycode::countrycode(sourcevar = pendata$countrycode,origin = "iso3c",destination = "iso3n")
@@
 df2 <- 
-df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","palmawd","rgdpna")],by = "ccode")
+df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")
 ```

### 2023-09-19 procesamiento/prod_prep.Rmd
ajuste modelos

@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,sjlabelled,tidyverse)
+pacman::p_load(dplyr,sjmisc,GGally,sjlabelled,tidyverse,MLMusingR)
 df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
@@
 dfES <- dfES %>% rename(topbot=TOPBOT)
+#fix problem with variable names
+dfTR <- dfTR %>% rename(SEX=sex,
+                        DEGREE=degree,
+                        EDUCYRS=educyrs,
+                        AGE=age,
+                        MAINSTAT=mainstat,
+                        UNION=union)  
 dfES$c_alphan <- NULL
@@
 ```{r income-respondent}
-income_country <- names(df1 %>% select(dplyr::ends_with("_RINC")))
+income_country <- names(df1 %>% dplyr::select(dplyr::ends_with("_RINC")))
 # lapply(df1[,income_country], table)
@@
 
+# Class R´s and Spouse
 df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
@@
 )
+
+# Class only R's --------------------------------------------------------------
+df1$class10
+
+# Class Scheme 3 classes
+df1$class3res <- car::recode(as.numeric(df1$class10),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3res) <- "Social Class (R's)"
+# frq(df1$class3res)
+
+# Class Scheme 5 classes
+df1$class5res <- car::recode(
+  as.numeric(df1$class10),
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$class5res) <- "Social Class (R's)"
+# frq(df1$class5res)
+
+# Class Scheme 6 classes
+df1$class6res <- car::recode(
+  as.numeric(df1$class10),
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$class6res) <- "Social Class (R's)"
+frq(df1$class6res)
+# Class only Spouse --------------------------------------------------------------
+df1$class10spo
+
+# Class Scheme 3 classes
+df1$class3spo <- car::recode(as.numeric(df1$class10spo),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3spo) <- "Social Class (Spouse)"
+frq(df1$class3spo)
+
+# Class Scheme 5 classes
+df1$class5spo <- car::recode(
+  as.numeric(df1$class10spo),
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$class5spo) <- "Social Class (Spouse)"
+# frq(df1$class5res)
+
+# Class Scheme 6 classes
+df1$class6spo <- car::recode(
+  as.numeric(df1$class10spo),
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+sjlabelled::set_label(df1$class6spo) <- "Social Class (Spouse)"
 ```
@@
 hist.default(df1$eindex)
+df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
+hist.default(df1$eindex_gc)
 
@@
 sjlabelled::set_label(df1$homclass) <- "Class homogeneity"
+df1$homclass_gc <- group_center(x = df1$homclass,grp = df1$country)
+View(df1[,c("homclass","homclass_gc")])
 # Weighted EI index
@@
 
+```{r homogeneity-resp}
+# EI homophily index
+df1$ingroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+# frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+# frq(df1$outgroup_res)
+
+df1$eindex_res<- (df1$outgroup_res-df1$ingroup_res)/(df1$outgroup_res+df1$ingroup_res)
+sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
+# frq(df1$eindex)
+# hist.default(df1$eindex)
+
+df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
+df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
 (i)  the highest status job accessed (upper reachability),
@@
 
-# Group-mean center
-
-```{r}
-
-```
+# Variable centering
 

### 2023-09-19 paper.Rmd
Update paper.Rmd

@@
 ---
+
+- controls educ and income
+- laborstatus
 
@@
                         homclass,
-                        incomepcap,
+                        Q05pcm,
                         gini_disp,
@@
                         country2,pi_isola,
-                        # union,
-                        # labst,
+                        union,
+                        labst,
                         # WEIGHT
@@
 class <- lmer(redist~1 +female+agenum + class3+(1|country2),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+incomepcap+(1|country2),data=dfreg)
+full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+Q05pcm+(1|country2),data=dfreg)
 # Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + edyears + incomepcap + homclass*class3 +(1|country2),data=dfreg)
+full_int1 <- lmer(redist~1 +female+agenum + edyears + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
 models <- list(homclass,class,full,full_int1)
@@
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-omitcoef <- "(Intercept)|(agenum)|(female)|(incomepcap)|(edyears)|(logrgdpna)"
+omitcoef <- "(Intercept)|(agenum)|(female)|(Q05pcm)|(edyears)|(logrgdpna)"
 coefname <- c("Network class homogeneity","Service Class","Working Class",

### 2023-09-20 paper.Rmd
modelos micro macro

--- 2023-07-25 paper.Rmd
@@
 author:
-- name: Duke A Caboom
-  affiliation: University of Tuktoyaktuk
-  email: dtholmes@mail.ubc.ca
-  number: 1
-- name: Justin d'Ottawa
-  affiliation: University of Ottawa
-  number: 2
-- name: Pedro Torres
-  number: 1,2 
+# - name: Julio Iturra-Sanhueza
+#   affiliation: University of Bremen
+#   email: jiturra@uni-bremen.de
+#   number: 1
+# - name: Justin d'Ottawa
+#   affiliation: University of Ottawa
+#   number: 2
+# - name: Pedro Torres
+#   number: 1,2 
 # Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
-abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua.
+# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua.
 Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
 output:
+  bookdown::html_document2:
+    toc: yes
+    code_folding: hide
+    toc_float: 
+      collapsed: true
+      smooth_scroll: false
+      number_sections: false    
   bookdown::pdf_document2:
@@
 
+```{css, echo=FALSE}
+/* expandir el espacio del documento*/
+
+/* expandir width de la TOC*/
+div.tocify {
+    width: 22% !important;
+    max-width: 331px !important;
+    max-height: 102% !important;
+}
+```
+
 ```{r setup, include=FALSE}
@@
                       message = FALSE,  # mensajes/avisos de librerias  
-                      cache = FALSE,    # cache de los chunks,usar analisis pesados
-                      out.width = '85%',# largo de imagen en %
+                      cache = TRUE,    # cache de los chunks,usar analisis pesados
+                      out.width = '100%',
                       fig.pos= "H",     # posicion figuras H = HERE
+                      fig.align = "center",
                       echo = FALSE      # incluir chunk en output
@@
 options(knitr.kable.NA = '') # NA en kable = ''
+```
+#  Introduction
 
-table_format = if(is_html_output()) { # Usar en argumento "format=" de kable
-  "html"
-} else if(is_latex_output()) {
-  "latex"
-}
+The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens.
+However, these consequences have been unevenly experienced across the social structure.
+The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
+Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support.
+Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
+Consequently, inequalities in access to certain social positions (i.e.
+occupations) are translated into a lack of social resources beyond individual economic and cultural capital.
+Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
+Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties.
+For addresing this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
+The results of multilevel estimations show that being socially segregated increases demand for redistribution.
+Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class.
+At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution.
+However, cross-level interactions do not provide supporting evidence on this behalf.
 
-fwidth = if(is_html_output()) { #Usar en argumento "full_width" de kableExtra
-  T
-} else if(is_latex_output()) {
-  F
-}
+<!-- The structure of the social network provide access to social resources.
+On the one hand, contacts can be translated into resources, access to the life of others that could provide information and life opportunities.
+-->
+
+<!-- - stratified access to resources -->
+<!-- - class and networks (focus of this paper) -->
+
+<!-- Some research has connected social capital with economic rational dimension, while others have conected it to more value-driven or moralistic dimension  -->
+
+<!-- Both assume direct effects, but other literature such as Otero et al has suggested that experiences might vary across social classes. -->
+
+<!-- For example, we trust other people because we know about them (connected) -->
+
+# Data, variables and methods
+
+*Data*
+
+*Variables*
+
+*Methods*
+
+<!-- Across all countries, a nurse (41.2%) and a schoolteacher (39.6%) are mentioned the most often and a human resource manager (19.2%) and a lawyer (22.2%) the least often.
+Considering the scope of the network, Suriname (42%), the United States (41.4%), and Iceland (41.3%) are the countries in which respondents are connected to the widest array of occupations, while Thailand (13.2%), Japan (15%), and Taiwan (18.9%) represent the other end.
+The social network thus is larger and more diverse in the former countries -->
+
+# Results
+
+## Descriptive
+
+```{r redistribution,fig.height=5,fig.width=8,fig.cap=c("Redistributive preferences by country in the ISSP 2017"), out.width = '80%'}
+# x country
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+# df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+df1$redistF <- factor(df1$redist,levels = 1:5,labels = sjlabelled::get_labels(df1$redist))
+dfreg <- df1 %>% dplyr::select(redist,
+                               # perineq,
+                        class3,
+                        # class3=class3res,
+                        homclass,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        # Q05pc,
+                        Q03pcm,
+                        # Q03pc,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        # ednum,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        pi_nteg,
+                        union,
+                        labst,
+                        labst1,
+                        # WEIGHT
+                        # incomer,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+
+# dfreg %>%
+#   group_by(country2) %>%
+#   summarise(redist = mean(redist, na.rm = T)) %>% 
+#   View()
+
+percentage_data <- df1 %>%
+  group_by(country2, redistF) %>%
+  summarise(count = n()) %>%
+  group_by(country2) %>%
+  na.omit() %>% 
+  mutate(percentage = count / sum(count)) %>% 
+  arrange(country2,redistF,percentage) %>% 
+  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
+  mutate(pct_lab=ifelse(!redistF %in% c("Strongly agree"),NA,pct_lab))
+
+order <- 
+percentage_data %>% 
+  filter(redistF=="Strongly agree") %>% 
+  arrange(percentage) %>% 
+  dplyr::select(country2)
+
+order$orden <- 1:31
+ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=redistF,group=redistF,label = pct_lab))+
+  geom_bar(stat = 'identity') +
+  # geom_text(position = position_fill(vjust =100)) +
+  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
+  scale_x_discrete(limits=order$country2,name=NULL) +  
+  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
+  theme_classic() +
+  ggtitle(label= "REdistributive preferences") + 
+  theme(legend.position = 'bottom',legend.title = element_blank())  +
+  coord_flip()
 ```
 
-- Class: 
+```{r homogeneity,fig.height=4,fig.width=8,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '80%'}
+# x country
+resits_count <- dfreg %>%
+  group_by(country2) %>%
+  summarise(redist = mean(redist,na.rm = T),
+            homclass = mean(homclass,na.rm = T),
+            ) %>%
+  na.omit()
+
+myorder <-  resits_count$country2[order(resits_count$homclass)]
+ggplot(data = resits_count,aes(x =country2,y = homclass)) + 
+  geom_segment(aes(x=country2, xend=country2, y=0, yend=homclass), color="black") +
+  geom_point() +
+  scale_x_discrete(limits=myorder) +
+  ylab("Class-based homogeneity")+
+  xlab("") +
+  theme(axis.text.x = element_text(angle = 45))
+```
+
+```{r macro}
+
+```
+
+- Class x homogeneity (3 plots)
+- Homogeneity x redistribution (1 plot)
+<!-- - perceived isolation x redistribution (1 plot) -->
+<!-- - homogeneity x perceived isolation (1 plot) -->
+
+## Individual level
+
+1. Class: 
     - having a working class position is associated with higher redistributive preferences
@@
 
-- Network segregation
+2. Network segregation
     - being more segregated increase redistributive preferences
-- Perceived isolation
-  - perceived isolation increases redistributive preferences
 
-Note: network segregation decreases perceived isolation *
+<!-- - Perceived isolation -->
+<!--   - perceived isolation increases redistributive preferences -->
 
-- class x network segregation
+<!-- Note: network segregation decreases perceived isolation *   -->
 
-  - the influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
+3. Network segregation x Social Class
+    - The influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
 
-- Economic inequality
+```{r microlevel,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+
+dfreg <- df1 %>% dplyr::select(redist,
+                               # perineq,
+                        class3,
+                        # class3=class3res,
+                        homclass,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        # Q05pc,
+                        Q03pcm,
+                        # Q03pc,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        # ednum,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        pi_nteg,
+                        union,
+                        labst,
+                        labst1,
+                        # WEIGHT
+                        # incomer,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(rob3,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Household Income (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1)
+```
+
+```{r marg1,fig.height=4,fig.width=5,fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = '50%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Class-based homogeneity coefficient")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +  
+  theme_minimal()+
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred1,fig.height=4,fig.width=6,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)    
+# Predicted values 
+pred1<- sjPlot::plot_model(int_homo,type = "pred",terms = c("homclass [0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1]","class3"))
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+```
+
+## Macro level
   - expected: economic inequality increases segregation (maybe weak or null effect)
-  - expected: increase redistributive preferences
-  - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger
+  - expected: economic inequality increase the influence of network homogeneity
+
+  <!-- - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger  -->
+
+```{r intermacro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        labst,
+                        labst1) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
+  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+pred1<- plot_model(giniD_int,type = "int", mdrt.values = "meansd")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+
+predval1 <- 
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+
+# Predicted values 
+pred1<- plot_model(giniM_int,type = "int", mdrt.values = "meansd")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+
+predval2 <- 
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+```
+
+```{r, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
+grid.arrange(p1,predval1,nrow = 1,top = "Network homogeneity × Gini (Disposable)")
+```
+
+```{r, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
+grid.arrange(p2,predval2,nrow = 1,top = "Network homogeneity × Gini (Market)")
+```
+
+# Other analysis
+
+- close ties
+- weak ties
+- R's data only

### 2023-09-20 procesamiento/prod_prep-macro.Rmd
modelos micro macro

--- 2023-09-19 procesamiento/prod_prep-country.Rmd
@@
 df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")
+
+df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
+df2 <- df2 %>% rename(country3=c3)
+df2 <- df2 %>% select(country,country2, country3, everything())
 ```
@@
 save(df2,file = here::here("input/data/proc/study1_country.RData"))
+sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )
 ```

### 2023-09-20 procesamiento/prod_prep.Rmd
modelos micro macro

@@
                         MAINSTAT=mainstat,
-                        UNION=union)  
+                        UNION=union,
+                        WEIGHT=weight)  
 dfES$c_alphan <- NULL
@@
                                               Q05pc=ntile(incomepcap,5),
+                                              Q03pc=ntile(incomepcap,3),
                                               zincpc=scale(incomepcap,center = TRUE),
                                               logincpc=log(incomepcap)) %>% ungroup()
+
+df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing"))
+
+df1$Q03pcm <- car::recode(df1$Q03pc,"1='T01';2='T02';3='T03';NA='Missing'",
+                          as.factor = T,
+                          levels = c("T01","T02","T03","Missing"))
 
@@
 df1[,c("incomer","hhpop","incomepcap","incomerep")] %>% arrange(incomepcap,hhpop) %>% head()
+
+summary(df1[,c("incomer","hhpop","incomepcap","incomerep")])
 ```
@@
 df1$homclass_gc <- group_center(x = df1$homclass,grp = df1$country)
-View(df1[,c("homclass","homclass_gc")])
+# View(df1[,c("homclass","homclass_gc")])
 # Weighted EI index
@@
 ```{r social distance}
-
 df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
@@
 # Print the standard deviation for each column
-df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
+# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
 
@@
 
-# Variable centering
+# Save
 
 ```{r}
-df1
 save(df1,file = here::here("input/data/proc/study1.RData"))

### 2023-09-21 paper.Rmd
update results

@@
 link-citations: yes         # citas linkeadas
+# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
+date: "`r format(Sys.Date(), '%d %B %Y')`"
 author:
@@
 ---
-
-```{css, echo=FALSE}
-/* expandir el espacio del documento*/
-
-/* expandir width de la TOC*/
-div.tocify {
-    width: 22% !important;
-    max-width: 331px !important;
-    max-height: 102% !important;
-}
-```
 
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
 # df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                               # perineq,
                         class3,
-                        # class3=class3res,
                         homclass,
-                        # homclass=homclass_res,
                         Q05pcm,
-                        # Q05pc,
                         Q03pcm,
-                        # Q03pc,
                         gini_disp,
                         gini_mkt,
+                        giniot=gini,
                         rgdpna,
-                        # ednum,
                         edyears,
@@
                         agenum,
-                        country2,
-                        pi_nteg,
+                        country2,country,
                         union,
                         labst,
-                        labst1,
-                        # WEIGHT
-                        # incomer,
+                        labst1
                         ) %>% 
@@
   na.omit()
-
-# dfreg %>%
-#   group_by(country2) %>%
-#   summarise(redist = mean(redist, na.rm = T)) %>% 
-#   View()
 
@@
 
-```{r homogeneity,fig.height=4,fig.width=8,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '80%'}
+```{r homogeneity,fig.height=4,fig.width=8,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '90%'}
 # x country
+dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
 resits_count <- dfreg %>%
-  group_by(country2) %>%
-  summarise(redist = mean(redist,na.rm = T),
-            homclass = mean(homclass,na.rm = T),
-            ) %>%
-  na.omit()
+  group_by(country2,country) %>%
+  summarise_at(c("redist","homclass",
+                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
 
@@
 
-```{r macro}
+```{r class-hom,fig.height=11,fig.width=11,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '100%'}
+predis <- 
+resits_count %>%  
+ggplot(aes(y=redist, x=homclass)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0.3,0.5))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Class homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(title = "Redistributive preferences and Class homogeneity",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$redist),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$redist)
 
+p1 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_3)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Working class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Working class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_3),digits = 2),""))
+
+# cor.test(resits_count$homclass,resits_count$class3_3)
+
+p2 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_2)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Intermediate class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Intermediate class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_2),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$class3_2)
+p3 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_1)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Service class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Service class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_1),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$class3_3)
+grid.arrange(predis,p1,p2,p3,nrow = 2,top = "Network homogeneity × Social Class")
 ```
 
-- Class x homogeneity (3 plots)
-- Homogeneity x redistribution (1 plot)
 <!-- - perceived isolation x redistribution (1 plot) -->
@@
 df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-
 dfreg <- df1 %>% dplyr::select(redist,
-                               # perineq,
                         class3,
-                        # class3=class3res,
                         homclass,
-                        # homclass=homclass_res,
                         Q05pcm,
-                        # Q05pc,
                         Q03pcm,
-                        # Q03pc,
                         gini_disp,
                         gini_mkt,
+                        giniot=gini,
                         rgdpna,
-                        # ednum,
                         edyears,
@@
   na.omit()
-# T03dim(dfreg)
+# dim(dfreg)
 
@@
 #                rob4)
-# texreg::screenreg(rob3,single.row = F)
+# texreg::screenreg(int_homo,single.row = F)
 
@@
 coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Household Income (ref: Low)"=4:5,
+                  "Income Tercile (ref: Low)"=4:5,
                   "Homogeneity x Social Class"=9:10
@@
                   include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1)
+                  custom.gof.names = gof1
+                )
 ```
 
-```{r marg1,fig.height=4,fig.width=5,fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = '50%'}
+```{r marg1,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "50%"}
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
@@
   scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Class-based homogeneity coefficient")+
+  ylab("Class-based homogeneity")+
   xlab("Social Class")+
@@
 
-```{r pred1,fig.height=4,fig.width=6,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
+```{r pred1,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
@@
 
+\pagebreak
 ## Macro level
+
   - expected: economic inequality increases segregation (maybe weak or null effect)
   - expected: economic inequality increase the influence of network homogeneity
+
+```{r ineq-homo,fig.height=5,fig.width=10,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '100%'}
+resits_count <- dfreg %>%
+  group_by(country2,country) %>%
+  summarise_at(c("redist","homclass",
+                 "gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
+p1 <- resits_count %>%  
+ggplot(aes(y=homclass, x=gini_disp)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Disposable)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Income Inequality (Disposable)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$gini_disp),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$gini_disp)
+p2 <- resits_count %>%  
+ggplot(aes(y=homclass, x=gini_mkt)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Market)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Income Inequality (Market)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$gini_mkt),digits = 2),""))
+
+# cor.test(resits_count$homclass,resits_count$class3_3)
+grid.arrange(p1,p2,nrow = 1,top = "Network homogeneity and Economic Inequality")
+```
 
@@
 
-```{r, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
+```{r crossginiD, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
 grid.arrange(p1,predval1,nrow = 1,top = "Network homogeneity × Gini (Disposable)")
@@
 
-```{r, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
+```{r crossginiM, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
 grid.arrange(p2,predval2,nrow = 1,top = "Network homogeneity × Gini (Market)")
@@
 
+\pagebreak
 # Other analysis
 
-- close ties
+- strong ties
 - weak ties
 - R's data only
+
+```{r strongties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_s,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r weakties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_w,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r ownclass, cache=TRUE, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
+
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        # homclass,
+                        homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
+coefmap <-  list(homclass ="Class-based network homogeneity - Resp.",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
+                 'class3spoService Class (I+II)' ='Service Class (Partner)',
+                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'
+
+                 )
+coefgroup <- list("Social Class - Resp. (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,rob4,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```

### 2023-09-21 procesamiento/prod_analysis-robust.Rmd
update results

---
title: "Robustness checks"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
output:
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: false    
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = TRUE,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```
#  Intro

- maintain class R's and calculate homogeneity
- keep Partner class apart as a control

```{r ord-micro,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
df1$redistF <- as.factor(df1$redist)

dfreg <- df1 %>% dplyr::select(redist=redistF,
                        class3,
                        homclass,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# dim(dfreg)

# lineal
base <- clmm(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
class <- clmm(redist~ class3+ (1|country2),data=dfreg)
homclass <- clmm(redist~homclass + (1|country2),data=dfreg)
full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
# rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
# rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
# Interactions segregation x class
int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
# texreg::screenreg(int_homo,single.row = F)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
coefmap <-  list(homclass ="Class-based network homogeneity",
                 'class3Service Class (I+II)' ='Service Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "labst1Not in labour force"="Not in labor force",
                 "unionYes" = 'Union: Yes',
                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
                 )
coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

```{r ord-strongties,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
df1$redistF <- as.factor(df1$redist)
dfreg <- df1 %>% dplyr::select(redist=redistF,
                        class3,
                        homclass=homclass_s,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# dim(dfreg)

# lineal
base <- clmm(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
class <- clmm(redist~ class3+ (1|country2),data=dfreg)
homclass <- clmm(redist~homclass + (1|country2),data=dfreg)
full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
# rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
# rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
# Interactions segregation x class
int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
# texreg::screenreg(int_homo,single.row = F)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
                 'class3Service Class (I+II)' ='Service Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "labst1Not in labour force"="Not in labor force",
                 "unionYes" = 'Union: Yes',
                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
                 )
coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

```{r orde-weakties,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
df1$redistF <- as.factor(df1$redist)
dfreg <- df1 %>% dplyr::select(redist=redistF,
                        class3,
                        homclass=homclass_w,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# dim(dfreg)

# lineal
base <- clmm(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
class <- clmm(redist~ class3+ (1|country2),data=dfreg)
homclass <- clmm(redist~homclass + (1|country2),data=dfreg)
full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
# rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
# rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
# Interactions segregation x class
int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
# texreg::screenreg(int_homo,single.row = F)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (Weak) and social class" 
coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
                 'class3Service Class (I+II)' ='Service Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "labst1Not in labour force"="Not in labor force",
                 "unionYes" = 'Union: Yes',
                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
                 )
coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

```{r ownclass,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
df1$redistF <- as.factor(df1$redist)

dfreg <- df1 %>% dplyr::select(redist=redistF,
                        class3=class3res,
                        class3spo,
                        # homclass,
                        homclass=homclass_res,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# dim(dfreg)

# lineal
base <- clmm(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
class <- clmm(redist~ class3+ (1|country2),data=dfreg)
homclass <- clmm(redist~homclass + (1|country2),data=dfreg)
full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
rob4 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)

# Interactions segregation x class
int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
# texreg::screenreg(int_homo,single.row = F)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
coefmap <-  list(homclass ="Class-based network homogeneity - Resp.",
                 'class3Service Class (I+II)' ='Service Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "labst1Not in labour force"="Not in labor force",
                 "unionYes" = 'Union: Yes',
                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
                 'class3spoService Class (I+II)' ='Service Class (Partner)',
                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'

                 )
coefgroup <- list("Social Class - Resp. (ref: Intermediate Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,rob4,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

### 2023-09-21 procesamiento/prod_prep.Rmd
update results

@@
 
-# Class R´s and Spouse
+# Class R´s and Spouse----------------------------------------------------------
 df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")

### 2023-09-21 paper.Rmd
check eindex

@@
 
+- considerar ISEI08 como alternativa de social class
+- darle una oportunidad al h-index
+
 ```{r setup, include=FALSE}
@@
 *Variables*
+
+Homogeneity:
+
+Thus, an EI score of 1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of -1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types.
 
@@
 df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
+                        class3,class5,
                         homclass,
@@
                         Q03pcm,
+                        # isei08,
                         gini_disp,
@@
 rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~isei08+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
 # Interactions segregation x class

### 2023-09-21 procesamiento/prod_analysis-robust.Rmd
check eindex

@@
 
-```{r ownclass,results='asis', cache=T}
+```{r ownclass, cache=TRUE, results='asis'}
 if (!require("pacman")) install.packages("pacman")

### 2023-09-21 paper.Rmd
ajustes varios al modelo

--- 2023-09-21 paper.Rmd
@@
 
+- considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad
+- darle una oportunidad al h-index
+    - en general es prácticamente lo mismo que el indicador de homogeneidad
+- controlaria por social activities index ()
+- social resources
+
 ```{r setup, include=FALSE}
@@
 
+Homogeneity:
+
+Thus, an EI score of 1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of -1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types.
+
 *Methods*
@@
                         class3,
-                        homclass,
+                        homclass
+                        # homclass=eindex,
                         Q05pcm,
@@
                         labst,
-                        labst1
+                        labst1,
                         ) %>% 
@@
   theme_classic() +
-  ggtitle(label= "REdistributive preferences") + 
+  ggtitle(label= "Redistributive preferences") + 
   theme(legend.position = 'bottom',legend.title = element_blank())  +
@@
 ggplot(data = resits_count,aes(x =country2,y = homclass)) + 
-  geom_segment(aes(x=country2, xend=country2, y=0, yend=homclass), color="black") +
+  geom_segment(aes(x=country2, xend=country2, y=-1, yend=homclass), color="black") +
   geom_point() +
@@
 df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass,
+                        class3,class5,
+                        homclass
                         Q05pcm,
                         Q03pcm,
+                        # isei08,
                         gini_disp,
@@
                         labst,
-                        labst1
+                        labst1,
+                        isolation,
                         ) %>% 
@@
 rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +(1|country2),data=dfreg)
 # Interactions segregation x class
@@
 #                rob4)
-# texreg::screenreg(int_homo,single.row = F)
+texreg::screenreg(rob3,single.row = F)
 
@@
 df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-
 dfreg <- df1 %>% dplyr::select(redist,
                         class3,
-                        homclass,
+                        # homclass,
+                        homclass=eindex,                      
                         Q05pcm,
@@
 giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
+anova(giniD_gdp,giniD_rs)
 giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
@@
                         class3,
-                        homclass=homclass_s,
+                        homclass,
+                        # homclass=eindex_s,
                         Q05pcm,
@@
                         class3,
-                        homclass=homclass_w,
+                        homclass,
+                        # homclass=eindex_w,
                         Q05pcm,
@@
                         class3spo,
-                        # homclass,
-                        homclass=homclass_res,
+                        homclass,
+                        # homclass=eindex_res,
                         Q05pcm,
@@
 ```
+
+```{r isolation,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,class5,
+                        homclass,
+                        # isolation
+                        Q05pcm,
+                        Q03pcm,
+                        # isei08,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ pi_nteg+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```

### 2023-09-22 paper.Rmd
update paper

@@
 
-- considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad
-- darle una oportunidad al h-index
-    - en general es prácticamente lo mismo que el indicador de homogeneidad
-- controlaria por social activities index ()
-- social resources
-
 ```{r setup, include=FALSE}
@@
 Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties.
-For addresing this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
+For addressing this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
 The results of multilevel estimations show that being socially segregated increases demand for redistribution.
@@
 
+The literature review (possible structure)
+
+* Class and political attitudes (Svallfors, Edlund & Lindh)
+* Inequality in social networks (Lin, Wright, Bourdieu, Volker)
+* Interplay of class, networks and attitudes toward inequality (Lindh, McCall)
+
 <!-- The structure of the social network provide access to social resources.
@@
 
+International Social Survey - Social Networks 2017
+
 *Variables*
 
-Homogeneity:
-
-Thus, an EI score of 1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
-An EI score of -1 means complete heterophily- all the alters are of a different “type” than they themselves are.
-Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types.
+* __Redistributive preferences__
+
+A widely used method for evaluating people's views on redistribution is by employing a standard measure commonly found in the literature.
+The measure involves asking respondents to indicate their level of agreement with the statement, "It is the responsibility of the government to decrease the income gap between individuals with high and low incomes." Respondents are asked to indicate their level of agreement on a scale of one to five, with one being "Strongly agree" and five being "Strongly disagree." In this case, a reverse code is utilized to interpret higher values as indicating greater support for redistribution.
+
+* __Social Class__
+
+A synthetic version of the EGP class was used, including three main classes: Service class (I+II), Intermediate class (III+IV) and Working class (V+VI+VII)
+
+* ___Class-based network homogeneity___
+
+For measuring the personal network of the respondent, a short version of the position generator was included in the survey.
+In this regard, the instrument presents a set of 10 occupations that represent hierarchical societal positions according to their status.
+Therefore, as the following Table shows, each position was classified into three status groups according to their scores in the International Socioeconomic Index (ISEI).
+
+```{r}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,kable,kableExtra)
+rm(list=ls())
+options(knitr.kable.NA = '') # NA en kable = ''
+xlsx::read.xlsx(file = "input/tables/tables.xlsx",sheetName = "ties") %>% 
+  kable() %>% 
+  kable_styling(full_width = F)
+```
+
+Consequently, we calculate the number of contacts that belong to a similar class/status to create the number of ingroup and outgroup contacts.
+It is considered ingroup (i) when the ego's class matches the Alter's status.
+This measure represents the proportion of similar contacts, where 0 implies that all contacts are different to Ego's social class, while 1 represents complete network homogeneity.
+Therefore, higher values represent greater social distance from other groups in society.
+The calculation of the class-based network homogeneity variables is as follows:
+
+$$H_i= \frac{\text{Ingroup}}{(\text{Ingroup}+\text{Outgroup})}$$
+
+* ___Perceived Isolation___
+
+  * Past 4 weeks how often felt: 
+    - companionship lacking?
+    - isolated from others?
+    - left out?
+
+The response categories are '"Never", "Rarely", "Sometimes", "Often"  and "Very often".
+As the indicators show an acceptable internal consistency ($\alpha=.85$), an index of the three items was created.
+Positive values indicate higher perceived isolation.
 
 *Methods*
+
+- Multilevel regression with random intercept and slopes
 
@@
 
-```{r redistribution,fig.height=5,fig.width=8,fig.cap=c("Redistributive preferences by country in the ISSP 2017"), out.width = '80%'}
+```{r redistribution,fig.height=4.5,fig.width=7.1,fig.cap=c("Redistributive preferences by country in the ISSP 2017"), out.width = '50%'}
 # x country
@@
                         class3,
-                        homclass
+                        homclass,
                         # homclass=eindex,
@@
 
-```{r homogeneity,fig.height=4,fig.width=8,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '90%'}
+```{r homogeneity,fig.height=3.4,fig.width=6,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '50%'}
 # x country
@@
 ggplot(data = resits_count,aes(x =country2,y = homclass)) + 
-  geom_segment(aes(x=country2, xend=country2, y=-1, yend=homclass), color="black") +
+  geom_segment(aes(x=country2, xend=country2, y=0, yend=homclass), color="black") +
   geom_point() +
@@
   xlab("") +
-  theme(axis.text.x = element_text(angle = 45))
-```
-
-```{r class-hom,fig.height=11,fig.width=11,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '100%'}
+  theme_minimal()+  
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+```{r class-hom,fig.height=7,fig.width=7,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '50%'}
+ggplot2::theme_set(new = theme_bw())
+ggplot2::theme_set(theme(text = element_text(size = 8)))
+sizetext <- 2.5
+
 predis <- 
@@
   # geom_point() +
-  geom_text(label=as.character(resits_count$country3)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
   # scale_x_continuous(limits = c(0.3,0.5))+
@@
   # geom_point() +
-  geom_text(label=as.character(resits_count$country3)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
   # scale_x_continuous(limits = c(0,1))+
@@
 # cor.test(resits_count$homclass,resits_count$class3_3)
-grid.arrange(predis,p1,p2,p3,nrow = 2,top = "Network homogeneity × Social Class")
+grid.arrange(predis,p1,p2,p3,nrow = 2)
 ```
@@
 2. Network segregation
-    - being more segregated increase redistributive preferences
+    - being more segregated in terms of network homogeneity increase demand for redistribution
 
@@
 
-```{r microlevel,results='asis', cache=T}
+The literature have discussed two complementary social mechanisms that could explain what role does social ties play in shaping people's demand for redistribution.
+
+```{r homclass,results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
@@
                         class3,class5,
-                        homclass
+                        homclass,
+                        # outgroup,
+                        # know_total,
                         Q05pcm,
@@
 rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 + (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+# anova(rob3,rob4)
+ranef1<- plot_model(rob4,type = "re",show.values = T)
+
 # Interactions segregation x class
@@
 #                rob4)
-texreg::screenreg(rob3,single.row = F)
+# texreg::screenreg(rob3,single.row = F)know_total
 
@@
                  'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 # know_total="Number contacts"
+                 # outgroup="Number outgroup"
                  )
@@
                 )
+
 ```
@@
                         class3,
-                        # homclass,
-                        homclass=eindex,                      
+                        homclass,
+                        # homclass=eindex,
+                        # homclass=ingroup,
                         Q05pcm,
@@
 giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
-anova(giniD_gdp,giniD_rs)
+# anova(giniD_gdp,giniD_rs)
 giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
@@
                   # include.thresholds=FALSE,
-                  custom.coef.map=list(logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                  custom.coef.map=list(homclass="Network Homogeneity",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
                                        "homclass:gini_disp"="Homogeneity x Gini (D)",
@@
 
-- strong ties
-- weak ties
-- R's data only
+- Perceived Isolation
+- Network homogeneity (Strong ties)
+- Network homogeneity (Weak ties)
+- R's and Partner social class
+
+___Perceived Isolation___
+
+```{r isolation,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,class5,
+                        homclass,
+                        isolation,
+                        Q05pcm,
+                        Q03pcm,
+                        # isei08,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
+coefmap <-  list(isolation ="Perceived Isolation",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):isolation'='Isolation x Service Class',
+                 'class3Working Class (V+VI+VII):isolation'='Isolation x Working Class',
+                  homclass ="Class-based network homogeneity"
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Isolation x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "50%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Perceived Isolation")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
+  theme_minimal()+
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
+# Predicted values 
+pred1<- sjPlot::plot_model(int_homo,type = "pred",terms = c("isolation [1,1.5,2,2.5,3,3.5,4,4.5,5]","class3"))
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+pred_data$group <- factor(pred_data$group,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+```
+
+```{r intermacro2,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        isolation,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        labst,
+                        labst1) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +homclass"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(isolation="Perceived Isolation",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "isolation:gini_mkt"="Isolation x Gini (M)",
+                                       homclas="Class-based homogeneity"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel2}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
+  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
+  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+pred1<- plot_model(giniD_int,type = "int", mdrt.values = "meansd")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+
+predval1 <- 
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+
+# Predicted values 
+pred1<- plot_model(giniM_int,type = "int", mdrt.values = "meansd")
+pred_data <- data.frame(pred1$data)
+pred_data <- pred_data %>% arrange(pred_data$group)
+
+predval2 <- 
+pred_data %>% 
+ggplot() +
+  geom_point(aes(x = x,y = predicted)) +
+  geom_line(aes(x = x,y = predicted))+
+  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
+  facet_grid(. ~ group) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") + 
+  theme_minimal()
+```
+
+```{r crossginiD2, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
+grid.arrange(p1,predval1,nrow = 1,top = "Perceived Isolation × Gini (Disposable)")
+```
+
+```{r crossginiM2, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
+grid.arrange(p2,predval2,nrow = 1,top = "Perceived Isolation × Gini (Market)")
+```
+
+## Strong & weak ties
+
+___Homogeneity: strong ties___
 
@@
 
+___Homogeneity: weak ties___
+
 ```{r weakties,results='asis', cache=T}
@@
 
+___Homogeneity: respondent class___
+
 ```{r ownclass, cache=TRUE, results='asis'}
@@
 rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+rob5 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(homclass|country2),data=dfreg)
 
@@
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
-coefmap <-  list(homclass ="Class-based network homogeneity - Resp.",
+coefmap <-  list(homclass ="Class-based network homogeneity",
                  'class3Service Class (I+II)' ='Service Class',
@@
 ```
-
-```{r isolation,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        # isolation
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ pi_nteg+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-texreg::screenreg(full1,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```

### 2023-09-22 procesamiento/prod_prep-macro.Rmd
update paper

@@
 load(here::here("input/data/proc/study1.RData"))
-pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse)
+pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse,haven)
 ```

### 2023-09-22 procesamiento/prod_prep.Rmd
update paper

@@
                         UNION=union,
-                        WEIGHT=weight)  
+                        WEIGHT=weight,
+                        URBRURAL=urbrural)  
 dfES$c_alphan <- NULL
@@
 
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived integration"
+df1$isolation<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
+sjlabelled::set_label(df1$isolation) <- "Perceived isolation"
 ```
@@
 
-df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
 sjlabelled::set_label(df1$eindex) <- "EI homophily index"
@@
 
-df1$eindex_s<- (df1$outgroup_s-df1$ingroup_s)/(df1$outgroup_s+df1$ingroup_s)
+df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
 sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
@@
 
-df1$eindex_w<- (df1$outgroup_w-df1$ingroup_w)/(df1$outgroup_w+df1$ingroup_w)
+df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
 sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
@@
 
-df1$eindex_res<- (df1$outgroup_res-df1$ingroup_res)/(df1$outgroup_res+df1$ingroup_res)
+df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
 sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"

### 2023-09-22 paper.Rmd

@@
                         class3,
-                        homclass,
+                        homclass
                         # homclass=eindex,
@@
                         class3,class5,
-                        homclass,
-                        # outgroup,
-                        # know_total,
+                        homclass
                         Q05pcm,

### 2023-09-25 paper.Rmd
modelos chao

--- 2023-09-22 paper.Rmd
@@
 linkcolor: blue                         # enlaces y citas en color azul
-bibliography: input/bib/library.bib     # bibliografia en bibtex
+bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
+csl: input/bib/apa6.csl
 editor_options:
@@
 
+<!-- - considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad -->
+<!-- - darle una oportunidad al h-index -->
+<!--     - en general es prácticamente lo mismo que el indicador de homogeneidad -->
+<!-- - controlaria por social activities index () -->
+<!-- - social resources  -->
+
 ```{r setup, include=FALSE}
@@
 options(knitr.kable.NA = '') # NA en kable = ''
+old<- ggplot2::theme_set(theme_minimal())
+ggplot2::theme_set(old)
+ggplot2::theme_update(text=element_text(size=8,  family="serif"))
 ```
@@
 
+network segregation decreases  attachment to society (Otero et al., 2022)
+
+subjective marginalization increases alienation (Gidron & Hall, 2020)
+
+social ties with lower or upper class influence welfare attitudes aligned to class interests (Paskov & Weisstanner, 2022; Lindh et al., 2021)
+
+Focus on the sociability/relational dimension and its consequences on inequality attitudes - redistributive and welfare attitudes
+
 The literature review (possible structure)
@@
 
+The literature have discussed two complementary social mechanisms that could explain what role does social ties play in shaping people's demand for redistribution.
+
 <!-- The structure of the social network provide access to social resources.
@@
 
-*Data*
+**Data**
 
@@
 
-*Variables*
-
-* __Redistributive preferences__
+**Variables**
+
+_Redistributive preferences_
 
@@
 
-* __Social Class__
+_Social Class_
 
@@
 
-* ___Class-based network homogeneity___
-
-For measuring the personal network of the respondent, a short version of the position generator was included in the survey.
-In this regard, the instrument presents a set of 10 occupations that represent hierarchical societal positions according to their status.
-Therefore, as the following Table shows, each position was classified into three status groups according to their scores in the International Socioeconomic Index (ISEI).
-
-```{r}
+_Class-based network homogeneity_
+
+For measuring the personal network of the respondent, a short version of the position generator was included in the survey, which presents a set of ten occupations that seek to represent the hierarchical status order in society [@joye_measuring_2019], declaring four possible response alternatives: "Family or relative", "Close friend", "Someone else I know" or "No one".
+For this research, a binary variable is created by coding the first three categories as 1 and the last one as 0, representing if the person knows (or not) one of the occupations.
+The following text corresponds to the original phrasing of the questionnaire:
+
+> *Here is a list of jobs that people you know may have.
+These people could be family or relatives, close friends or someone else you know.
+By "knowing" a person, we mean that you know him/her by name and well enough to contact him/her.
+If you know several people who have a job from the list below, please only tick the box for the person who you feel closest to.
+Each of these jobs could be held by a woman or a man.*
+
+Therefore, Table \@ref(tab:posgen) shows the classification of each occupation into three status groups according to their scores in the International Socioeconomic Index (ISEI)[@ganzeboom_internationally_1996].
+
+```{r posgen}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,kable,kableExtra)
+pacman::p_load(dplyr,knitr,kableExtra)
 rm(list=ls())
 options(knitr.kable.NA = '') # NA en kable = ''
+cap <- "Clasification of occupations of the position generator in the ISSP 2017"
 xlsx::read.xlsx(file = "input/tables/tables.xlsx",sheetName = "ties") %>% 
-  kable() %>% 
+  kable(caption = cap) %>% 
   kable_styling(full_width = F) 
@@
 
-* ___Perceived Isolation___
-
-  * Past 4 weeks how often felt: 
-    - companionship lacking?
-    - isolated from others?
-    - left out?
-
-The response categories are '"Never", "Rarely", "Sometimes", "Often"  and "Very often".
-As the indicators show an acceptable internal consistency ($\alpha=.85$), an index of the three items was created.
+_Perceived Isolation_
+
+"The next questions are about how you feel about different aspects of your life.
+For each one, please indicate how often during the past 4 weeks you have felt that way.
+How often in the past 4 weeks have you felt that..." 1) "companionship lacking?",(2) "isolated from others?" and (3) "left out?".
+
+The response categories are  (1)"Never", (2)"Rarely", (3) "Sometimes", (4)"Often" and  (5)"Very often".
+As the indicators show an acceptable internal consistency (α=.85), an index of the three items was created.
 Positive values indicate higher perceived isolation.
 
-*Methods*
+**Methods**
 
@@
   scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
-  theme_classic() +
   ggtitle(label= "Redistributive preferences") + 
-  theme(legend.position = 'bottom',legend.title = element_blank())  +
+  theme(legend.position = 'bottom',legend.title = element_blank(), text = element_text(size = 12))  +  
   coord_flip()
@@
   xlab("") +
-  theme_minimal()+  
-  theme(axis.text.x = element_text(angle = 90))
+  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1.2))   
 ```
@@
 ```{r class-hom,fig.height=7,fig.width=7,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '50%'}
-ggplot2::theme_set(new = theme_bw())
-ggplot2::theme_set(theme(text = element_text(size = 8)))
 sizetext <- 2.5
@@
 
-The literature have discussed two complementary social mechanisms that could explain what role does social ties play in shaping people's demand for redistribution.
-
 ```{r homclass,results='asis', cache=T}
@@
 df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-
 dfreg <- df1 %>% dplyr::select(redist,
@@
                         homclass,
-                        # outgroup,
-                        # know_total,
                         Q05pcm,
@@
                         isolation,
+                        MAINSTAT,
                         ) %>% 
@@
   # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
   na.omit()
@@
 rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 + (1|country2),data=dfreg)
-rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1 + union+ female+agenum +age2 + (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1 + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
 # anova(rob3,rob4)
-ranef1<- plot_model(rob4,type = "re",show.values = T)
+# plot_model(rob4,type = "re",show.values = T)
 
@@
 int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
+# anova(int_homo,int_homo2)
+# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
+
 # models <- list(homclass,class,full1,
@@
 #                rob4)
-# texreg::screenreg(rob3,single.row = F)know_total
-
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
@@
                   include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
+                  # custom.gof.names = gof1
                 )
@@
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
-  theme_minimal()+
   theme(plot.title = element_text(size = 8))  
@@
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
+  ylab("Redistributive preferences")
 ```
@@
   - expected: economic inequality increases segregation (maybe weak or null effect)
-  - expected: economic inequality increase the influence of network homogeneity
-
-```{r ineq-homo,fig.height=5,fig.width=10,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '100%'}
+  - expected: economic inequality increase the influence of network homogeneity/segregation
+
+```{r ineq-homo,fig.height=4,fig.width=7.5,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '50%'}
+sizetext <- 2.5
 resits_count <- dfreg %>%
@@
 ggplot(aes(y=homclass, x=gini_disp)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
   # scale_x_continuous(limits = c(0,1))+
@@
   ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Income Inequality (Disposable)",
+  labs(
+    # title = "Class homogeneity and Income Inequality (Disposable)",
        caption =paste("r=",round(cor(resits_count$homclass,
@@
 ggplot(aes(y=homclass, x=gini_mkt)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
   # scale_x_continuous(limits = c(0,1))+
@@
   ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Income Inequality (Market)",
+  labs(
+    # title = "Class homogeneity and Income Inequality (Market)",
        caption =paste("r=",round(cor(resits_count$homclass,
@@
 # cor.test(resits_count$homclass,resits_count$class3_3)
-grid.arrange(p1,p2,nrow = 1,top = "Network homogeneity and Economic Inequality")
+grid.arrange(p1,p2,nrow = 1)
 ```
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
 rm(list=ls())
@@
                         class3,
-                        homclass,
+                        homclass=homclass_gc,
                         # homclass=eindex,
@@
                         gini_mkt,
-                        giniot=gini,
+                        # giniot=gini,
+                        giniot=gv_spen,
                         rgdpna,
@@
                         labst,
-                        labst1) %>% 
+                        labst1,
+                        isolation,
+                        MAINSTAT) %>% 
   mutate(logrgdpna=log(rgdpna),
@@
   # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
   na.omit()
@@
 
+giniOT_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1|country2),data=dfreg)
+giniOT_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)
+# anova(giniOT_gdp,giniOT_rs)
+giniOT_int <- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)
+
 models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
+               giniM_gdp,giniM_rs,giniM_int )
 
@@
 p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
 
 # Predicted values  
-pred1<- plot_model(giniD_int,type = "int", mdrt.values = "meansd")
+pred1<- sjPlot::plot_model(model = giniD_int,type = "int", mdrt.values = "meansd")
 pred_data <- data.frame(pred1$data)
@@
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
+  ylab("Redistributive preferences")
 
 # Predicted values 
-pred1<- plot_model(giniM_int,type = "int", mdrt.values = "meansd")
+pred1<- sjPlot::plot_model(giniM_int,type = "int", mdrt.values = "meansd")
 pred_data <- data.frame(pred1$data)
@@
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-```
-
-```{r crossginiD, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
-grid.arrange(p1,predval1,nrow = 1,top = "Network homogeneity × Gini (Disposable)")
-```
-
-```{r crossginiM, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
-grid.arrange(p2,predval2,nrow = 1,top = "Network homogeneity × Gini (Market)")
+  ylab("Redistributive preferences")
+```
+
+```{r crossginiD, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='50%'}
+grid.arrange(p1,predval1,nrow = 1
+             # top = "Network homogeneity × Gini (Disposable)" 
+             )
+```
+
+```{r crossginiM, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='50%'}
+grid.arrange(p2,predval2,nrow = 1 
+             # top = "Network homogeneity × Gini (Market)"
+             )
+```
+
+```{r econineq,fig.height=4,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='50%'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        gv_spen=gv_spen,
+                        pc10_2017,pc50_2017,
+                        ratio10_50,
+                        palmawd,
+                        rgdpna,
+                        individualism,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        labst,
+                        labst1,
+                        isolation,
+                        MAINSTAT) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2)
+    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) 
+  # filter(agenum %in% c(25:65))
+
+int_palma <- lmer(redist~class3+ homclass*palmawd+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ homclass*pc10_2017+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+ homclass*pc50_2017+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_r1090 <- lmer(redist~class3+ homclass*ratio10_50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_r1090,int_giniot,int_indivi,int_govspe)
+texreg::knitreg(models_m)
+
+library(gridExtra)
+
+p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmawd") +
+  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
+
+p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="pc10_2017") +
+  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))
+
+p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="pc50_2017") +
+  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
+
+p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
+  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))
+
+grid.arrange(p4,p5,p6,nrow = 1)
+```
+
+```{r, fig.height=3.5,fig.width=6.5,fig.cap=c("Cross-level interaction for Network homogeneity Gov. Spending and Individualism"),out.width='50%'}
+p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
+  xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
+
+p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
+  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+
+p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
+  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+
+grid.arrange(p9,p8,nrow = 1)
 ```
@@
 \pagebreak
+
+# References
+
+<div id="refs"></div>
+
 # Other analysis
 
+- Homogeneity x Economic Inequality
 - Perceived Isolation
@@
 
-___Perceived Isolation___
+## Perceived Isolation
 
@@
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme_minimal()+
   theme(plot.title = element_text(size = 8))  
@@
   xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
+  ylab("Redistributive preferences") 
 ```
@@
 p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
+  geom_point()+ geom_hline(yintercept = 0)
 
@@
   xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
+  ylab("Redistributive preferences")
 
@@
   xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-```
-
-```{r crossginiD2, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality I")}
-grid.arrange(p1,predval1,nrow = 1,top = "Perceived Isolation × Gini (Disposable)")
-```
-
-```{r crossginiM2, fig.height=5,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality II")}
-grid.arrange(p2,predval2,nrow = 1,top = "Perceived Isolation × Gini (Market)")
+  ylab("Redistributive preferences") 
+```
+
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction forPerceived Isolation and Gini (Disposable)"),out.width='50%'}
+grid.arrange(p1,predval1,nrow = 1
+             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"
+             )
+```
+
+```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='50%'}
+grid.arrange(p2,predval2,nrow = 1
+             # top = "Perceived Isolation × Gini (Market)"
+             )
 ```
@@
                         class3,
-                        homclass,
+                        homclass=homclass_s,
                         # homclass=eindex_s,
@@
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
+coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
                  'class3Service Class (I+II)' ='Service Class',
@@
                         class3,
-                        homclass,
+                        homclass=homclass_w,
                         # homclass=eindex_w,
@@
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
+coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
                  'class3Service Class (I+II)' ='Service Class',
@@
 ```
+
+# (APPENDIX) Appendix {-}

### 2023-09-25 procesamiento/prod_prep-macro.Rmd
modelos chao

@@
 df2 <- 
-df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")
-
+df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017","individualism","gdp")],by = "ccode")
+df2$ratio10_50 <- df2$pc10_2017/df2$pc50_2017
 df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")

### 2023-09-26 paper.Rmd
modelos macro

@@
     toc_float:
-      collapsed: true
+      collapsed: false
       smooth_scroll: false
@@
 options(knitr.kable.NA = '') # NA en kable = ''
+```
+
+```{r}
 old<- ggplot2::theme_set(theme_minimal())
 ggplot2::theme_set(old)
-ggplot2::theme_update(text=element_text(size=8,  family="serif"))
-```
+ggplot2::theme_update(text=element_text(size=9,  family="serif"))
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+```
+
 #  Introduction
@@
 
-```{r homclass,results='asis', cache=T}
+```{r mod-homclass,results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
 rm(list=ls())
@@
 ```{r pred1,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra,papaja)        
 # Predicted values
-pred1<- sjPlot::plot_model(int_homo,type = "pred",terms = c("homclass [0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1]","class3"))
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
+
+plot_predictions(int_homo, condition = c("homclass","class3")) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences")
+  ylab("Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+  # scale_fill_grey(start = 0.40, end = 0.6) +
+  # scale_color_grey(start = 0.40, end = 0.6)
 ```
@@
 
-```{r intermacro,results='asis'}
+```{r mod-intermacro,results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 ```{r crosslevel}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
 p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
@@
 # Predicted values 
-pred1<- sjPlot::plot_model(model = giniD_int,type = "int", mdrt.values = "meansd")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-
 predval1 <- 
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+plot_predictions(giniD_int, condition = list("homclass",gini_disp="threenum"),gray = T) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       linetype='Gini (Disposable)') +
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences")
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
 
 # Predicted values 
-pred1<- sjPlot::plot_model(giniM_int,type = "int", mdrt.values = "meansd")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-
 predval2 <- 
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
+plot_predictions(giniM_int, condition = list("homclass",gini_mkt="threenum"),gray = T)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       linetype='Gini (Market)') +
   xlab("Network homogeneity")+
-  ylab("Redistributive preferences")
-```
-
-```{r crossginiD, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='50%'}
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='60%'}
 grid.arrange(p1,predval1,nrow = 1 
@@
 
-```{r crossginiM, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='50%'}
+```{r crossginiM, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='60%'}
 grid.arrange(p2,predval2,nrow = 1  
@@
 
-```{r econineq,fig.height=4,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='50%'}
+\pagebreak
+
+# References
+
+<div id="refs"></div>
+
+# Other analysis
+
+- Perceived Isolation
+- Network homogeneity (Strong ties)
+- Network homogeneity (Weak ties)
+- R's and Partner social class
+- Homogeneity x other macro variables
+
+## Perceived Isolation
+
+```{r mod-isolation,results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,class5,
+                        homclass,
+                        isolation,
+                        Q05pcm,
+                        Q03pcm,
+                        # isei08,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears, 
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
+coefmap <-  list(isolation ="Perceived Isolation",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):isolation'='Isolation x Service Class',
+                 'class3Working Class (V+VI+VII):isolation'='Isolation x Working Class',
+                  homclass ="Class-based network homogeneity"
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Isolation x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "50%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() + 
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Perceived Isolation")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
+# Predicted values 
+plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(legend.position = "none")+ 
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences")
+```
+
+```{r mod-intermacro2,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        isolation,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        labst,
+                        labst1) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +homclass"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(isolation="Perceived Isolation",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "isolation:gini_mkt"="Isolation x Gini (M)",
+                                       homclas="Class-based homogeneity"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel2}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
+  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
+  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("isolation",gini_disp="threenum"),gray = T) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       linetype='Gini (Disposable)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("isolation",gini_mkt="threenum"),gray = T)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       linetype='Gini (Market)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction forPerceived Isolation and Gini (Disposable)"),out.width='50%'}
+grid.arrange(p1,predval1,nrow = 1  
+             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"
+             )
+```
+
+```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='50%'}
+grid.arrange(p2,predval2,nrow = 1  
+             # top = "Perceived Isolation × Gini (Market)"
+             )
+```
+
+## Strong & weak ties
+
+___Homogeneity: strong ties___
+
+```{r mod-strongties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_s,
+                        # homclass=eindex_s,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+___Homogeneity: weak ties___
+
+```{r mod-weakties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_w,
+                        # homclass=eindex_w,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+___Homogeneity: respondent class___
+
+```{r mod-ownclass, cache=TRUE, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
+
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        homclass,
+                        # homclass=eindex_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        labst,
+                        labst1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+rob5 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(homclass|country2),data=dfreg)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "labst1Not in labour force"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
+                 'class3spoService Class (I+II)' ='Service Class (Partner)',
+                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'
+
+                 )
+coefgroup <- list("Social Class - Resp. (ref: Intermediate Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,rob4,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+## Other macro variables
+
+Source: https://www4.wider.unu.edu/?ind=1&type=ChoroplethSeq&year=70&byCountry=false&slider=buttons
+
+* The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
+* **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income
+<!-- * 90/50 ratio = the ratio of Decile 10 income to Decile 5 income (the median) -->
+<!-- * 50/10 ratio = the ratio of Decile 5 income (the median) to Decile 1 income. -->
+
+```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
 rm(list=ls())
@@
 
-int_palma <- lmer(redist~class3+ homclass*palmawd+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_pc10  <- lmer(redist~class3+ homclass*pc10_2017+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_pc50  <- lmer(redist~class3+ homclass*pc50_2017+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_r1090 <- lmer(redist~class3+ homclass*ratio10_50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_r1090,int_giniot,int_indivi,int_govspe)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0) +
-    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
+int_palma <- lmer(redist~class3+ isolation+homclass*palmawd+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ isolation+homclass*pc10_2017+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+ isolation+homclass*pc50_2017+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_r1090 <- lmer(redist~class3+ isolation+homclass*ratio10_50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+# int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_indivi<- lmer(redist~class3+ isolation+homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_govspe<- lmer(redist~class3+ isolation+homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_r1090,int_indivi,int_govspe)
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  palmawd               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  pc10_2017             = "Share National Income - top 10%",
+  "homclass:pc10_2017"    = "Homogeneity x top 10",
+  pc50_2017             = "Share National Income -  bottom 50%",
+  "homclass:pc50_2017"    = "Homogeneity x bottom 50",
+  ratio10_50            = "Ratio (90/50)",
+  "homclass:ratio10_50"   = "Homogeneity x Ratio (90/50)",
+  individualism         = "Individualism Index*",
+  "homclass:individualism" = "Homogeneity x Individualism",
+  gv_spen               = "Gov. Spending (% GDP)*",
+  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
+)
+texreg::knitreg(models_m,custom.coef.map = customcoef,caption.above = T,caption = cap1)
+```
+
+```{r,fig.height=4,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
+# p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmawd") +
+#   xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0) +
+#     labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
 
 p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0) +
+  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
   labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))
@@
 p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0) +
+  xlab("Share National Income - bottom 50%") + geom_point()+ geom_hline(yintercept = 0) +
   labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
@@
   labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
-
 grid.arrange(p4,p5,p6,nrow = 1)  
@@
 
-```{r, fig.height=3.5,fig.width=6.5,fig.cap=c("Cross-level interaction for Network homogeneity Gov. Spending and Individualism"),out.width='50%'}
-p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
-  xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
+```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%'}
+# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
+#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
+#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
 
@@
 
+predval8 <- 
+plot_predictions(int_indivi, condition = list("homclass",individualism="threenum"),gray = T) +
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+       linetype='Individualism') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
 p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
@@
 
-grid.arrange(p9,p8,nrow = 1)
-```
-
-\pagebreak
-
-# References
-
-<div id="refs"></div>
-
-# Other analysis
-
-- Homogeneity x Economic Inequality
-- Perceived Isolation
-- Network homogeneity (Strong ties)
-- Network homogeneity (Weak ties)
-- R's and Partner social class
-
-## Perceived Isolation
-
-```{r isolation,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        isolation,
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears, 
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(full1,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
-coefmap <-  list(isolation ="Perceived Isolation",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):isolation'='Isolation x Service Class',
-                 'class3Working Class (V+VI+VII):isolation'='Isolation x Working Class',
-                  homclass ="Class-based network homogeneity"
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Isolation x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
-```
-
-```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "50%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() + 
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Perceived Isolation")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
-# Predicted values 
-pred1<- sjPlot::plot_model(int_homo,type = "pred",terms = c("isolation [1,1.5,2,2.5,3,3.5,4,4.5,5]","class3"))
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") 
-```
-
-```{r intermacro2,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass,
-                        isolation,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        labst,
-                        labst1) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# T03dim(dfreg)
-
-main <- "redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +homclass"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# summary(giniD_int)
-
-giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
-                caption.above=T,
-                  # include.thresholds=FALSE,
-                  custom.coef.map=list(isolation="Perceived Isolation",
-                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "isolation:gini_disp"="Isolation x Gini (D)",
-                                       "gini_mkt"="Gini (Market) ",
-                                       "isolation:gini_mkt"="Isolation x Gini (M)",
-                                       homclas="Class-based homogeneity"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-```
-
-```{r crosslevel2}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
-p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-pred1<- plot_model(giniD_int,type = "int", mdrt.values = "meansd")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-
-predval1 <- 
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences")
-
-# Predicted values 
-pred1<- plot_model(giniM_int,type = "int", mdrt.values = "meansd")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-
-predval2 <- 
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int))) +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") 
-```
-
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction forPerceived Isolation and Gini (Disposable)"),out.width='50%'}
-grid.arrange(p1,predval1,nrow = 1
-             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"
-             )
-```
-
-```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='50%'}
-grid.arrange(p2,predval2,nrow = 1
-             # top = "Perceived Isolation × Gini (Market)"
-             )
-```
-
-## Strong & weak ties
-
-___Homogeneity: strong ties___
-
-```{r strongties,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_s,
-                        # homclass=eindex_s,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-___Homogeneity: weak ties___
-
-```{r weakties,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_w,
-                        # homclass=eindex_w,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-___Homogeneity: respondent class___
-
-```{r ownclass, cache=TRUE, results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
-
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3=class3res,
-                        class3spo,
-                        homclass,
-                        # homclass=eindex_res,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
-rob5 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(homclass|country2),data=dfreg)
-
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
-                 'class3spoService Class (I+II)' ='Service Class (Partner)',
-                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'
-
-                 )
-coefgroup <- list("Social Class - Resp. (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,rob4,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-# (APPENDIX) Appendix {-}
+predval9 <- 
+plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = T) +
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
+       linetype='Gov.Spend') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p9,predval9,
+             p8,predval8,nrow = 2)
+```
+
+<!-- # (APPENDIX) Appendix {-}  -->

### 2023-09-27 paper.Rmd
cloud

@@
                       message = FALSE,  # mensajes/avisos de librerias  
-                      cache = TRUE,    # cache de los chunks,usar analisis pesados
+                      cache = F,    # cache de los chunks,usar analisis pesados
                       out.width = '100%',
@@
 ```{r}
-old<- ggplot2::theme_set(theme_minimal())
-ggplot2::theme_set(old)
-ggplot2::theme_update(text=element_text(size=9,  family="serif"))
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(theme_minimal())
+ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
 ```
@@
                         giniot=gini,
+                        giniindex,
                         rgdpna,
@@
          edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
@@
 
+```{r leverage1, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c(1,4),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
 ```{r marg1,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "50%"}
@@
   summarise_at(c("redist","homclass", 
-                 "gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
+                 "gini_disp","gini_mkt","giniindex"), mean, na.rm = TRUE) %>% 
   as.data.frame()
@@
 giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
-
-giniOT_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1|country2),data=dfreg)
-giniOT_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)
 # anova(giniOT_gdp,giniOT_rs)
-giniOT_int <- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)
 
 models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int )
+               giniM_gdp,giniM_rs,giniM_int)
 
@@
 predval1 <- 
-plot_predictions(giniD_int, condition = list("homclass",gini_disp="threenum"),gray = T) +
+plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F) +
   labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       linetype='Gini (Disposable)') +
+       colour='Gini (Disposable)',fill='Gini (Disposable)') +
   xlab("Network homogeneity")+
@@
 predval2 <- 
-plot_predictions(giniM_int, condition = list("homclass",gini_mkt="threenum"),gray = T)+
+plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)+
   labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       linetype='Gini (Market)') +
+       colour='Gini (Disposable)',fill='Gini (Disposable)') +
   xlab("Network homogeneity")+
@@
 
+```
+
+```{r leverage2, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c("isolation"),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
 ```
@@
 predval1 <- 
-plot_predictions(giniD_int, condition = list("isolation",gini_disp="threenum"),gray = T) +
+plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
   labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
@@
 predval2 <- 
-plot_predictions(giniM_int, condition = list("isolation",gini_mkt="threenum"),gray = T)+
+plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
   labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
@@
 
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction forPerceived Isolation and Gini (Disposable)"),out.width='50%'}
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='50%'}
 grid.arrange(p1,predval1,nrow = 1    
@@
 * The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
-* **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income
+<!-- * **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income -->
 <!-- * 90/50 ratio = the ratio of Decile 10 income to Decile 5 income (the median) -->
@@
 
-```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis'}
+```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
@@
                         homclass=homclass_gc,
+                        # homclass=homclass_res,
                         Q05pcm,
@@
                         giniot=gini,
+                        giniindex,ttheilge1,
                         gv_spen=gv_spen,
-                        pc10_2017,pc50_2017,
-                        ratio10_50,
-                        palmawd,
+                        top10,
+                        middle50,
+                        palmaratio,
                         rgdpna,
@@
          age2=agenum^2,
-         edyears2=edyears^2)
+         edyears2=edyears^2) %>%
     # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) 
-  # filter(agenum %in% c(25:65))
-
-int_palma <- lmer(redist~class3+ isolation+homclass*palmawd+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_pc10  <- lmer(redist~class3+ isolation+homclass*pc10_2017+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_pc50  <- lmer(redist~class3+ isolation+homclass*pc50_2017+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_r1090 <- lmer(redist~class3+ isolation+homclass*ratio10_50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-# int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+   na.omit()
+
+int_palma <- lmer(redist~class3+ isolation+homclass*palmaratio+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ isolation+homclass*top10+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+ isolation+homclass*middle50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_gini_wiid  <- lmer(redist~class3+ isolation+homclass*giniindex+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_theil  <- lmer(redist~class3+ isolation+homclass*ttheilge1+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
 int_indivi<- lmer(redist~class3+ isolation+homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
@@
 
-models_m <- list(int_palma,int_pc10,int_pc50,int_r1090,int_indivi,int_govspe)
+models_m <- list(int_palma,int_pc10,int_pc50,int_indivi,int_govspe
+                 # int_gini_wiid,int_theil
+                 )
 
@@
   logrgdpna           = "log GDP",
-  palmawd               = "Palma Ratio",
+  palmaratio               = "Palma Ratio",
   "homclass:palmawd"      = "Homogeneity x Palma Ratio",
-  pc10_2017             = "Share National Income - top 10%",
-  "homclass:pc10_2017"    = "Homogeneity x top 10",
-  pc50_2017             = "Share National Income -  bottom 50%",
-  "homclass:pc50_2017"    = "Homogeneity x bottom 50",
-  ratio10_50            = "Ratio (90/50)",
-  "homclass:ratio10_50"   = "Homogeneity x Ratio (90/50)",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
   individualism         = "Individualism Index*",
@@
 )
-texreg::knitreg(models_m,custom.coef.map = customcoef,caption.above = T,caption = cap1)
+texreg::knitreg(models_m,
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
 ```
@@
 ```{r,fig.height=4,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
-# p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmawd") +
-#   xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0) +
-#     labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="pc10_2017") +
+p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
+  xlab("Palma ratio (top 10%/ bottom 40%)") + geom_point()+ geom_hline(yintercept = 0) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
+
+# plot_predictions(int_palma, condition = list("homclass",palmaratio=range),gray = F) +
+#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+#        linetype='Palma Ratio') +
+#   xlab("Class-based homogeneity")+
+#   ylab("Redistributive preferences") +
+#   theme(legend.position = "right")
+
+p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="top10") +
   xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
@@
 
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="pc50_2017") +
-  xlab("Share National Income - bottom 50%") + geom_point()+ geom_hline(yintercept = 0) +
+# plot_predictions(int_pc10, condition = list("homclass",top10=range),gray = F) +
+#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+#        linetype='Palma Ratio') +
+#   xlab("Class-based homogeneity")+
+#   ylab("Redistributive preferences") +
+#   theme(legend.position = "right")
+p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="middle50") +
+  xlab("Share National Income - middle 50%") + geom_point()+ geom_hline(yintercept = 0) +
   labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
 
-p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
-grid.arrange(p4,p5,p6,nrow = 1)  
-```
-
-```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%'}
+# plot_predictions(int_pc50, condition = list("homclass",middle50=range),gray = F) +
+#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+#        linetype='Palma Ratio') +
+#   xlab("Class-based homogeneity")+
+#   ylab("Redistributive preferences") +
+#   theme(legend.position = "right")
+
+# interplot::interplot(m = int_gini_wiid,var1 = "homclass",var2="giniindex") +
+#   xlab("Gini (WIID)") + geom_point()+ geom_hline(yintercept = 0) +
+#     labs(caption = paste0("N=",nobs(int_gini_wiid),", Countries=",lme4::ngrps(int_gini_wiid)))
+
+# interplot::interplot(m = int_theil,var1 = "homclass",var2="ttheilge1") +
+#   xlab("Theil Index") + geom_point()+ geom_hline(yintercept = 0) +
+#     labs(caption = paste0("N=",nobs(int_theil),", Countries=",lme4::ngrps(int_theil)))
+
+# p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
+#   xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
+#   labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
+grid.arrange(p3,p4,p5,nrow = 1) 
+```
+
+```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%',}
 # p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
@@
 predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism="threenum"),gray = T) +
+plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
@@
 predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = T) +
+plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
   labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
@@
 ```
-
-<!-- # (APPENDIX) Appendix {-}  -->

### 2023-09-27 procesamiento/prod_analysis-robust.Rmd
cloud

@@
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-css: "input/css/custom.css" # custom CSS para html
+css: "../input/css/custom.css" # custom CSS para html
 linestretch: '1.5'          # interlineado 
@@
 dfreg <- df1 %>% dplyr::select(redist=redistF,
-                        class3,
+                        class3,class5,
                         homclass,
@@
                         labst,
-                        labst1
+                        labst1,
+                        isolation,
+                        MAINSTAT,
                         ) %>% 
@@
          edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
   na.omit()
-# dim(dfreg)
 
@@
 rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# rob4 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# anova(rob3,rob4)
 # Interactions segregation x class

### 2023-09-27 procesamiento/prod_prep-macro.Rmd
cloud

--- 2023-09-22 procesamiento/prod_prep-macro.Rmd
@@
 
-# Economic inequality
+**World Income Inequality Database (WIID)**
 
-```{r world-bank, eval=FALSE, include=FALSE}
-# install.packages("wbstats")
-library(wbstats)
-ineq<- c("3.0.Rate75-25","3.0.Rate90-10","SI.POV.GINI","3.0.Gini","3.0.Gini_nozero")
-# Gini
-giniwb <- wb_data("SI.POV.GINI", start_date = 2015, end_date = 2020,return_wide = F)
-gini_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
-gini_wb$ccode <- countrycode::countrycode(sourcevar = gini_wb$iso3c,origin = "iso3c",destination = "iso3n")
-gini_wb<- gini_wb %>% filter(ccode %in% countries$ccode)
+> UNU-WIDER, World Income Inequality Database (WIID) Companion dataset (wiidcountry and/or wiidglobal). Version 30 June 2022. https://doi.org/10.35188/UNU-WIDER/WIIDcomp-300622
 
-skimr::skim(gini_wb)
+```{r , eval=FALSE, include=FALSE}
+wiid_long<- haven::read_dta(here::here("input/data/original/WIID_30JUN2022_0/WIID_30JUN2022_0.dta"))
+wiid_long$ccode <- countrycode::countrycode(sourcevar = wiid_long$c3,origin = "iso3c",destination = "iso3n")
 
-gini_wb$giniwb <-  gini_wb$"2017"
-summary(gini_wb$giniwb)
-gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2018",no = gini_wb$giniwb)
-summary(gini_wb$giniwb)
-gini_wb$giniwb <- ifelse(is.na(gini_wb$giniwb),yes = gini_wb$"2016",no = gini_wb$giniwb)
-summary(gini_wb$giniwb)
+wiid_long1 <- 
+wiid_long %>% 
+  filter(ccode %in% countries$ccode) %>% 
+  filter(year==2017)
 
-# Rate 90-1
-rate90_10 <- wb_data("3.0.Rate90-10", start_date = 2015, end_date = 2020,return_wide = F)
-rate90_10_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
-rate90_10_wb$ccode <- countrycode::countrycode(sourcevar = rate90_10_wb$iso3c,origin = "iso3c",destination = "iso3n")
-rate90_10_wb<- rate90_10_wb %>% filter(ccode %in% country_data$ccode)
-
-# Rate 90-1
-rate75_25 <- wb_data("3.0.Rate75-25", start_date = 2015, end_date = 2020,return_wide = F)
-rate75_25_wb<- reshape::cast(giniwb[,c("iso3c","date","value")],formula = iso3c ~ date,value = "value")
-rate75_25_wb$ccode <- countrycode::countrycode(sourcevar = rate75_25_wb$iso3c,origin = "iso3c",destination = "iso3n")
-rate75_25_wb<- rate75_25_wb %>% filter(ccode %in% country_data$ccode)
-
-country_data <- 
-countries %>% left_join(select(gini_wb,iso3c,ccode,giniwb),by="ccode")
 ```
 
-```{r WIID}
-wiid<- haven::read_dta(here::here("input/data/original/WIID_30JUN2022_0/WIID_30JUN2022_0.dta"))
-summary(wiid$gini)
-
-gini_wiid <- wiid %>% dplyr::select(c3,year,gini,palma) %>% dplyr::filter(year %in% c(2014:2019))
-summary(gini_wiid)
-
-gini_wiid <- panelr::widen_panel(data = panelr::panel_data(as.data.frame(gini_wiid), id = c3 , wave = year))
-gini_wiid$ccode <- countrycode::countrycode(sourcevar = gini_wiid$c3,origin = "iso3c",destination = "iso3n")
-
-gini_wiid<- gini_wiid %>% filter(ccode %in% countries$ccode)
-
-gini_wiid$giniwd <- gini_wiid$gini_2017
-summary(gini_wiid$giniwd)
-gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2018,no = gini_wiid$giniwd)
-summary(gini_wiid$giniwd)
-gini_wiid$giniwd <- ifelse(is.na(gini_wiid$giniwd),gini_wiid$gini_2016,no = gini_wiid$giniwd)
-summary(gini_wiid$giniwd)
-
-skimr::skim(gini_wiid)
-
-gini_wiid$palmawd <- gini_wiid$palma_2017
-summary(gini_wiid$palmawd)
-gini_wiid$palmawd <- ifelse(is.na(gini_wiid$palmawd),gini_wiid$palma_2018,no = gini_wiid$palmawd)
-summary(gini_wiid$palmawd)
-gini_wiid$palmawd <- ifelse(is.na(gini_wiid$palmawd),gini_wiid$palma_2016,no = gini_wiid$palmawd)
-summary(gini_wiid$palmawd)
-
-country_data2 <- 
-countries %>% left_join(gini_wiid[,c("ccode","c3","giniwd","palmawd")],by="ccode")
+```{r}
+wiid <- 
+  read.csv(file = here::here("input/data/original/wid-percentiles/wiid-data-2015-2020.csv"),sep = ";")
+names(wiid) <- tolower(names(wiid))
+names(wiid) <- gsub('\\.', '', names(wiid))
+wiid$ccode <- countrycode::countrycode(sourcevar = wiid$iso,origin = "iso3c",destination = "iso3n")
+wiid_2017 <- 
+wiid %>% 
+  filter(ccode %in% countries$ccode) %>% 
+  filter(year==2017) %>% 
+  select(ccode,everything(),-iso,-country,-year) 
 ```
 
+**Solt SWDIID**
 ```{r Solt}
@@
 solt$country <- NULL
-solt <-  solt %>% filter(ccode %in% country_data2$ccode)
-country_data3 <- country_data2 %>% 
-  left_join(solt,by="ccode")
+solt_2017 <-  solt %>% filter(ccode %in% countries$ccode) %>% 
+  select(ccode,gini_disp,gini_mkt)
 ```
 
-```{r wid-dataset}
-wid <- 
-  read.csv(file = here::here("input/data/original/wid-percentiles/WID_Data_Metadata/WID_Data_28072023-104940.csv"),sep = ";")
-country_data3 <- country_data3 %>% 
-  left_join(wid,by="ccode")
-summary(country_data3)
-```
+**Otero et.al (2023)**
 
@@
 otero$ccode <- countrycode::countrycode(sourcevar = otero$iso3n,origin = "iso2c",destination = "iso3n")
-country_data3 <- country_data3 %>% 
-  left_join(otero,by="ccode")
-summary(country_data3)
+otero$gdp <- gsub('\\,', '',otero$gdp) 
+otero<- otero %>% select(ccode,gv_spen,individualism,gini,gdp)
 ```
 
-# GDP
-
+**GDP: PEN data**
 ```{r pen-data}
@@
 pendata$ccode <- countrycode::countrycode(sourcevar = pendata$countrycode,origin = "iso3c",destination = "iso3n")
-pen <- pendata %>% filter(ccode %in% countries$ccode,year %in% 2017)
-
-skimr::skim(pen)
-country_data4 <- country_data3 %>% 
-  left_join(pen,by="ccode")
+pen_2017 <- pendata %>% filter(ccode %in% countries$ccode,year %in% 2017) %>% select(ccode,everything(),-country,-countrycode,-currency_unit,-year)
 ```
@@
 ```{r merge}
+macro_data <- 
+  left_join(wiid_2017,solt_2017) %>%
+  left_join(pen_2017) %>% 
+  left_join(otero)
+
 df1$ccode <- as.numeric(df1$country)
+df2 <- left_join(df1,macro_data,by="ccode")
 df2 <- 
-df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")
-
-df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
-df2 <- df2 %>% rename(country3=c3)
-df2 <- df2 %>% select(country,country2, country3, everything())
+df2 %>% mutate(country2=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "iso3c"),
+               country3=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "country.name")) %>% 
+  select(ccode,country2,country3,everything())
 ```

### 2023-09-27 procesamiento/prod_prep.Rmd
modelos chao
Update prod_prep.Rmd

@@
 
+# Community participation
+
+```{r}
+# frq(df1$v17)
+df1$act_lei <- car::recode(df1$v17,recodes = "c(0,8,9)=NA")
+df1$act_lei <- set_na(df1$act_lei,na = c(0,8,9))
+df1$act_lei <- sjmisc::rec(x = df1$act_lei,rec = "rev")
+sjlabelled::set_label(df1$act_lei) <- "Activities: groups for leisure, sports or culture"
+# frq(df1$act_lei)
+
+# frq(df1$v18)
+df1$act_pol <- car::recode(df1$v18,recodes = "c(0,8,9)=NA")
+df1$act_pol <- set_na(df1$act_pol,na = c(0,8,9))
+df1$act_pol <- sjmisc::rec(x = df1$act_pol,rec = "rev")
+sjlabelled::set_label(df1$act_pol) <- "Activities: political parties, groups, associations"
+# frq(df1$act_pol)
+
+# frq(df1$v19)
+df1$act_vol <- car::recode(df1$v19,recodes = "c(0,8,9)=NA")
+df1$act_vol <- set_na(df1$act_vol,na = c(0,8,9))
+df1$act_vol <- sjmisc::rec(x = df1$act_vol,rec = "rev")
+sjlabelled::set_label(df1$act_vol) <- "Activities: charitable or religious - voluntary"
+# frq(df1$act_vol)
+
+# cor(df1[,c("act_lei","act_pol","act_vol")],use="complete.obs")
+# psych::alpha(df1[,c("act_lei","act_pol","act_vol")])
+
+df1$activities<- rowMeans(df1[,c("act_lei","act_pol","act_vol")],na.rm = T)
+sjlabelled::set_label(df1$activities) <- "Participation in social activities"
+# summary(df1$activities)
+```
+
 # Demographics

### 2023-09-29 paper.Rmd
pdf

@@
 output:
+  bookdown::pdf_document2:
+    template: null
+    toc: false
+    keep_tex: false
+    pandoc_args:
+      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
   bookdown::html_document2:
@@
     number_sections: false   
-  bookdown::pdf_document2:
-    template: null
-    toc: false
-    keep_tex: false
-    pandoc_args:
-      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
 linkcolor: blue                         # enlaces y citas en color azul
@@
 The response categories are  (1)"Never", (2)"Rarely", (3) "Sometimes", (4)"Often" and  (5)"Very often".
-As the indicators show an acceptable internal consistency (α=.85), an index of the three items was created.
+As the indicators show an acceptable internal consistency ($\alpha$=.85), an index of the three items was created.
 Positive values indicate higher perceived isolation.

### 2023-10-09 paper.Rmd
avance lunes

@@
 author:
-# - name: Julio Iturra-Sanhueza
+- name: Julio Iturra-Sanhueza
 #   affiliation: University of Bremen
@@
 Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties.
-For addressing this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
+To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
 The results of multilevel estimations show that being socially segregated increases demand for redistribution.
@@
 
-network segregation decreases  attachment to society (Otero et al., 2022)
-
-subjective marginalization increases alienation (Gidron & Hall, 2020)
-
-social ties with lower or upper class influence welfare attitudes aligned to class interests (Paskov & Weisstanner, 2022; Lindh et al., 2021)
-
-Focus on the sociability/relational dimension and its consequences on inequality attitudes - redistributive and welfare attitudes
-
-The literature review (possible structure)
-
-* Class and political attitudes (Svallfors, Edlund & Lindh)
-* Inequality in social networks (Lin, Wright, Bourdieu, Volker)
-* Interplay of class, networks and attitudes toward inequality (Lindh, McCall)
-
-The literature have discussed two complementary social mechanisms that could explain what role does social ties play in shaping people's demand for redistribution.
+<!-- * network segregation decreases  attachment to society (Otero et al., 2022)  -->
+
+<!-- * subjective marginalization increases alienation (Gidron & Hall, 2020) -->
+
+<!-- * social ties with lower or upper class influence welfare attitudes aligned to class interests (Paskov & Weisstanner, 2022; Lindh et al., 2021)  -->
+
+<!-- Focus on the sociability/relational dimension and its consequences on inequality attitudes - redistributive and welfare attitudes -->
+
+<!-- The literature review (possible structure) -->
+
+<!-- * Class and political attitudes (Svallfors, Edlund & Lindh) -->
+<!-- * Inequality in social networks (Lin, Wright, Bourdieu, Volker) -->
+<!-- * Interplay of class, networks and attitudes toward inequality (Lindh, McCall)  -->
+
+<!-- The literature have discussed two complementary social mechanisms that could explain what role does social ties play in shaping people's demand for redistribution.  -->
+
+## Class interests and redistribution
+
+The following paragraph will briefly present the class-preference link.
+While previous research have focus more extensevely on the economic dimension of social class such as employment relations and occupation, the focus of this research is idea  to argue that the patterns of social interactions (social ties) are also a constituent dimension of how classes shape their interests.
+
+- The "Democratic" class struggle [@edlund_democratic_2015]
+
+- The moral economy of class [@Svallfors2006]
+
+- Class interests in the economic domain [@lindh_class_2020]
+
+<!-- en paises donde el bienestar material a incrementado y las diferencias entre las clases ha disminuido se espera que el conflicto distributivo sea menor.
+
+se cree que en lops paises escandinavos con un estado de bienestar mas desarrollado la hipotesis debiese ser mas valida que en paises anglosajones
+
+Hi: la desigualdad o distancia entre grupos
+Hi: el tamagno del wlefare state
+-->
+
+## Class-based inequality in social networks
+
+Recent studies have focused on social capital formation processes [@volker_social_2020], concentrating on structural processes, such as intergenerational social mobility and class inequalities, demonstrating how meeting opportunities and association preferences are stratified [@lin_theory_2008].
+Consequently, access to higher and diverse resources through social ties follows a pattern of accumulation that reproduces pre-existing inequalities, in which class positions are vital in accounting for mechanisms of exclusion and segregation across the class structure.
+
+According to Weber [-@weber_economy_1978], classes are a common basis for action, defined by the labour market position and access to opportunities and goods.
+Additionally, the degree of intergenerational exchange leads to the development of social classes, characterised by the reproduction of socialisation patterns and lifestyles over time.
+Therefore, marriages, friendships, and social relationships between individuals of similar status groups represent class sociability practices.
+Similarly, two processes are described in class formation [@goldthorpe_sobre_1992].
+First, demographic identity refers to when classes become identifiable as collectivities regarding how individuals and families retain their class positions across generations.
+Second, cultural identity is expressed in distinctive shared lifestyles along with preferred patterns of association, which class members perform.
+As Bourdieu [-@bourdieu_distinction_1984] suggested, cultural capital is the pivotal attribute of these distinctive practices in class *habitus*, in which educational credentials represent the most salient cultural resources [@bourdieu_distinction_1984].
+Hence, the socialisation of common lifestyles and shared worldviews facilitates the consolidation of social classes.
+Moreover, upper classes also choose socially segregated environments, increasing their chances of establishing ties with similar others, maintaining privileged social positions, and excluding lower classes [@bourdieu_reproduccion_1981].
+Altogether, these processes further reinforce social distinctions between classes and contribute to the persistence of class structures.
+
+Class-based research shows that class permeability is affected by property-based boundaries, in which owners are less likely to connect to the working class through friendship ties, whereas interactions between supervisors and workers might explain why the authority dimension is more permeable [@wright_relative_1992a].
+Similarly, extended network diversity is lower in the upper-middle class than in the intermediate class, whereas friendship diversity increases for upwardly mobile individuals [@cepic_how_2020].
+However, the gain for this group is moderated by class background, where upward mobility cannot equalise access to social capital compared to those stable in the upper class [@carrascosa_class_2023].
+Moreover, the distribution of ties between the two extremes of the class structure depicts the higher permeability of intermediate classes, in contrast to the higher exclusion of the working class and self-selected upper-class homogenous networks [@otero_open_2021].
+Additionally, engagement in formal organisations increases the chances of the upper class bridging with diverse people, while the working class is homogeneous in their civic engagement behaviour, limiting its access to social capital [@pichler_social_2009].
+This tendency is strengthened over time, where social capital increases for those with higher education compared to those with less education [@volker_social_2020].
+
+## Social ties on the demand for redistribution and welfare
+
+As mentioned above, social networks influence people's experience of social life, self-evaluations, and the surrounding social and economic conditions.
+Notably, it has been shown that social perceptions of economic inequality influence their preferences towards it.
+However, it is less known about how the composition and resources embedded in social networks influence what people prefer in terms of economic inequality, mainly what are their views regarding the role of government in terms of social policy measures, which in turn are expressed in demands for economic redistribution and social welfare.
+Despite this, some insights in the literature highlight the role of social networks on redistributive preferences by describing the impact of civic engagement in voluntary organisations, cross-class embeddedness through kinship and friendship ties, and socioeconomic network diversity.
+
+As mentioned, the literature has previously addressed efforts to address the link between social networks and redistributive preferences.
+For example, a study in Japan by @yamamura_social_2012 argued that participation in community organisations boosts connections among different income groups.
+Consequently, contact might trigger envy from the poorer groups toward the wealthy, suggesting that negative externalities like unhappiness and crime rates will motivate altruistic behaviour, showing that the highest community participation rates increase support for redistribution for those above the median income of each prefecture.
+Also, research has focused on class-based networks, particularly how embeddedness in cross-class relationships influences attitudes through a synthetic scope that entails class material interests, socio-cultural or normative views, and political preferences [@lindh_class_2020].
+Hence, the discussion regarding how social class and network segregation intersect for explaining attitudes can be summarised in two mechanisms: (i) social influence and (ii) socialisation processes.
+
+@lindh_missing_2021 scrutinised how social influence and class segregation affect redistributive and social welfare preferences in Sweden, arguing that people tend to assimilate their opinions and attitudes according to their surrounding peers (*influence*), which is reinforced by class homophily (*segregation*).
+Therefore, higher contacts in the managerial class negatively impact redistributive demands, while ties to the working class increase them.
+Additionally, contact with socio-cultural professionals that entail more inclusive and egalitarian attitudes lowers welfare chauvinism, while it rises with working-class ties that might perceive immigrants as a threat.
+Similarly, aside from the current class position, additional socialisation sources are cross-class ties through the family of origin and partners.
+For instance, @lee_consider_2023 found that family of origin class position shapes economic redistributive and tax preferences, being crucial for political socialisation during childhood and early adulthood, where class interests and norms are nurtured.
+As a result, those with parents from the upper classes are less supportive of redistribution, while those having working-class origins hold favourable attitudes.
+Also,  @paskov_crossclass_2022 found that the class position of family and partners shapes redistributive preferences, where kinship ties are considered a source of inter-group contact, suggesting that heterogeneity in class ties can reduce negative prejudges toward out groups as contact theory suggests [@pettigrew_intergroup_1998], what in turn might motivate changes in political attitudes [@nathan_context_2023].
+As a result, homogeneity in ties polarises preferences between lower and upper classes.
+However, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
+
+Friendship ties are also relevant in preference formation.
+In this regard, @londono-velez_impact_2022 suggests that socioeconomic diversity at the school level introduces changes in friendship ties that influence (i) perceived inequality and (ii) support for redistribution in affluent students, claiming that homogeneous networks restrict economic inequality inferences.
+Therefore, exposure to diverse reference groups (e.g.
+friends) influences redistributive demands via self-interest, mobility prospects and distributive justice.
+On the one hand, contrary to self-interest, redistributive preferences increase when exposure to low-income peers improves accuracy in perceived inequality.
+On the other hand, heterogeneity has a null effect on mobility prospects.
+Finally, heterogeneity triggers concerns about the fairness of market-based life outcomes for low-income students, motivating higher support for government intervention.
+Similarly, @beck_explorando_2019 demonstrate that occupational network heterogeneity diminishes preferences for the marketisation of welfare provision in Chile, suggesting that contact diversity shortens the social distance between low and upper-status groups, providing them with broader images of inequality and the living conditions of others.
+
+The literature on social networks and inequality preferences makes two major contributions.
+First, it comprises the social influence and socialisation processes in social networks, where segregation entails a certain degree of social closure regarding others' life experiences and living conditions.
+In addition, heterogeneity provides a broader image of society in terms of social and economic inequality, contributing to preference formation.
+Consequently, studying preferences toward economic inequality from a social network perspective goes beyond the individual perspective by including the relational dimension.
+Hence, considering the degree of embeddedness of people in a network provides a more explicit image of how social environments are composed and of the social distance between individuals and groups.
 
@@
 
+\pagebreak
+
 # Data, variables and methods
@@
 A synthetic version of the EGP class was used, including three main classes: Service class (I+II), Intermediate class (III+IV) and Working class (V+VI+VII)
+
+<!-- -  in this research the *unit* for class is assumed as the family unit.  -->
 
@@
 cap <- "Clasification of occupations of the position generator in the ISSP 2017"
-xlsx::read.xlsx(file = "input/tables/tables.xlsx",sheetName = "ties") %>% 
-  kable(caption = cap) %>% 
-  kable_styling(full_width = F) 
+read.csv(file = "input/tables/tables.csv") %>% 
+  kable(caption = cap,booktabs = T,col.names = c("Status","Occupation","ISEI")) %>% 
+  kable_styling(full_width = F,latex_options = "HOLD_position") 
 ```
@@
 
-```{r redistribution,fig.height=4.5,fig.width=7.1,fig.cap=c("Redistributive preferences by country in the ISSP 2017"), out.width = '50%'}
+```{r homogeneity,fig.height=3.4,fig.width=6,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '100%'}
+# x country   
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3, 
+                        homclass,
+                        # homclass=eindex,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# x country
+dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
+resits_count <- dfreg %>%
+  group_by(country2,country) %>%
+  summarise_at(c("redist","homclass",
+                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
+
+myorder <-  resits_count$country2[order(resits_count$homclass)]
+ggplot(data = resits_count,aes(x =country3,y = homclass)) + 
+  geom_segment(aes(x=country2, xend=country3, y=0, yend=homclass), color="black") +
+  geom_point() +
+  scale_x_discrete(limits=myorder) +
+  ylab("Class-based homogeneity")+   
+  xlab("") +
+  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1.2))    
+```
+
+```{r class-hom,fig.height=7,fig.width=7,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '100%'}
+sizetext <- 2.5
+
+predis <-  
+resits_count %>%  
+ggplot(aes(y=redist, x=homclass)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0.3,0.5))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Class homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(title = "Redistributive preferences and Class homogeneity",
+       caption =paste("r=",round(cor(resits_count$homclass, 
+                                     resits_count$redist),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$redist)
+
+p1 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_3)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Working class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Working class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_3),digits = 2),""))
+
+# cor.test(resits_count$homclass,resits_count$class3_3)
+
+p2 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_2)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Intermediate class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Intermediate class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_2),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$class3_2)
+p3 <- resits_count %>%  
+ggplot(aes(y=homclass, x=class3_1)) +
+  # geom_point() +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Service class (%)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Service class (%)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$class3_1),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$class3_3)
+grid.arrange(predis,p1,p2,p3,nrow = 2)
+```
+
+\pagebreak
+
+## Individual level
+
+1. Class: 
+    - having a working class position is associated with higher redistributive preferences
+    - class homogeneity is higher among the working class, and lower in the upper-class
+
+2. Network segregation
+    - being more segregated in terms of network homogeneity increase demand for redistribution
+
+<!-- - Perceived isolation -->
+<!--   - perceived isolation increases redistributive preferences -->
+
+<!-- Note: network segregation decreases perceived isolation *   -->
+
+3. Network segregation x Social Class
+    - The influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
+
+```{r mod-homclass,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        class5,
+                        homclass,
+                        Q03pcm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=zincpc,
+                        # Q03rm=
+                        # isei08,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst,
+                        # isolation,  
+                        # MAINSTAT,
+                        # activities,
+                        # WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt"
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  na.omit()
+
+# frq(df1$region)
+# frq(dfreg$country2)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+anova(rob3,rob4)
+
+# plot_model(rob4,type = "re",show.values = T)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
+# anova(int_homo,int_homo2)
+# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
+
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r leverage1, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c(1,4),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
+```{r marg1,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)   
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Class-based homogeneity")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred1,fig.height=3.6,fig.width=5.7,fig.cap=c("Conditional linear Predictions for network homogeneity on redistributive Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra,papaja)        
+# Predicted values
+
+plot_predictions(int_homo, condition = c("homclass","class3")) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+  # scale_fill_grey(start = 0.40, end = 0.6) +
+  # scale_color_grey(start = 0.40, end = 0.6)
+```
+
+\pagebreak
+
+## Macro level
+
+  - Expectation: Economic inequality increases segregation (maybe weak or null effect)
+  - Expectation: Economic inequality increase the influence of network homogeneity/segregation
+
+```{r ineq-homo,fig.height=4,fig.width=7.5,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '100%'}
+sizetext <- 2.5
+resits_count <- dfreg %>%
+  group_by(country2,country) %>%
+  summarise_at(c("redist","homclass", 
+                 "gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
+p1 <- resits_count %>%  
+ggplot(aes(y=homclass, x=gini_disp)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Disposable)")+
+  ylab("Class homogeneity") +
+  labs(
+    # title = "Class homogeneity and Income Inequality (Disposable)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$gini_disp),digits = 2),""))
+# cor.test(resits_count$homclass,resits_count$gini_disp)
+p2 <- resits_count %>%  
+ggplot(aes(y=homclass, x=gini_mkt)) +
+  geom_text(label=as.character(resits_count$country3),size=sizetext) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Market)")+
+  ylab("Class homogeneity") +
+  labs(
+    # title = "Class homogeneity and Income Inequality (Market)",
+       caption =paste("r=",round(cor(resits_count$homclass,
+                                     resits_count$gini_mkt),digits = 2),""))
+
+# cor.test(resits_count$homclass,resits_count$class3_3)
+grid.arrange(p1,p2,nrow = 1)
+```
+
+  <!-- - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger  -->
+
+```{r mod-intermacro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        # giniot=gini,
+                        giniot=gv_spen,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        WEIGHT,
+                        workst) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg,weights = WEIGHT)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg,weights = WEIGHT)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg,weights = WEIGHT)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg,weights = WEIGHT)
+giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg,weights = WEIGHT)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg,weights = WEIGHT)
+# anova(giniOT_gdp,giniOT_rs)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                # include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+\pagebreak
+```{r crosslevel}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
+p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       colour='Gini (Disposable)',fill='Gini (Disposable)') +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       colour='Gini (Disposable)',fill='Gini (Disposable)') +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='100%'}
+grid.arrange(p1,predval1,nrow = 1 
+             # top = "Network homogeneity × Gini (Disposable)"   
+             )
+```
+
+```{r crossginiM, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='100%'}
+grid.arrange(p2,predval2,nrow = 1  
+             # top = "Network homogeneity × Gini (Market)"
+             ) 
+```
+
+\pagebreak
+
+# Additional analysis
+
+- Homogeneity x other macro variables
+- Network homogeneity (Strong ties)
+- Network homogeneity (Weak ties)
+- R's and Partner social class
+- Perceived Isolation
+
+## Other macro variables
+
+Source: https://www4.wider.unu.edu/?ind=1&type=ChoroplethSeq&year=70&byCountry=false&slider=buttons
+
+* The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
+* **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income
+* **90/50 ratio** = the ratio of Decile 10 income to Decile 5 income (the median)
+<!-- * 50/10 ratio = the ratio of Decile 5 income (the median) to Decile 1 income. -->
+
+```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        giniindex,ttheilge1,
+                        gv_spen=gv_spen,
+                        top10,
+                        middle50,
+                        palmaratio,
+                        d10d1,
+                        rgdpna,
+                        individualism,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+   na.omit()
+
+int_palma <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ homclass*top10+edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+homclass*middle50+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_d10d1<- lmer(redist~class3+ homclass*d10d1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_gini_wiid  <- lmer(redist~class3+ homclass*giniindex+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_theil  <- lmer(redist~class3+ homclass*ttheilge1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_indivi,int_govspe,int_d10d1
+                 # int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  palmaratio               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
+  individualism         = "Individualism Index*",
+  "homclass:individualism" = "Homogeneity x Individualism",
+  gv_spen               = "Gov. Spending (% GDP)*",
+  "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+    d10d1             = "Ratio D10/D01",
+  "homclass:d10d1"    = "Homogeneity x Ratio D10/D01"  
+)
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+```
+
+```{r,fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
+p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
+  xlab("Palma ratio (top 10%/ bottom 40%)") + geom_point()+ geom_hline(yintercept = 0) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
+
+p3.pred <- plot_predictions(int_palma, condition = list("homclass",palmaratio=range),gray = F) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)),
+       linetype='Palma Ratio',fill='Palma Ratio',color='Palma Ratio') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="top10") +
+  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))
+
+# plot_predictions(int_pc10, condition = list("homclass",top10=range),gray = F)
+
+p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="middle50") +
+  xlab("Share National Income - middle 50%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
+
+# plot_predictions(int_pc50, condition = list("homclass",middle50=range),gray = F)
+
+p6<- interplot::interplot(m = int_d10d1,var1 = "homclass",var2="d10d1") +
+  xlab("Ratio (Top 10%/Bottom 10%)") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_d10d1),", Countries=",lme4::ngrps(int_d10d1)))
+
+p6.pred<- plot_predictions(int_d10d1, condition = list("homclass",d10d1=range),gray = F) +
+      labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)),
+       linetype='Ratio D10/D01',fill='Ratio D10/D01',color='Ratio D10/D01') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p3,p3.pred,p6,p6.pred,nrow = 2)
+```
+
+```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
+# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
+#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
+#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
+
+p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
+  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+
+predval8 <- 
+plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+       linetype='Individualism') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
+  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+
+predval9 <- 
+plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
+       linetype='Gov.Spend') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p9,predval9,
+             p8,predval8,nrow = 2)
+```
+
+\pagebreak
+
+## Strong ties
+
+```{r mod-strongties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+# df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_s,
+                        # homclass=eindex_s,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
+                 'class3Intermediate class (III+IV)' ='Intermediate class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,scalebox = 1,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+\pagebreak
+
+## Weak ties
+
+```{r mod-weakties,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+# df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+# df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_w,
+                        # homclass=eindex_w,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
+                 'class3Intermediate class (III+IV)' ='Intermediate class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,scalebox = 1,
+                float.pos="h!",
+                include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+\pagebreak
+
+## Respondent class
+
+```{r mod-ownclass, cache=TRUE, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+# df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
+# df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
+
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        homclass,
+                        # homclass=eindex_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+rob5 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ class3spo +(homclass|country2),data=dfreg)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(int_homo,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
+                 'class3spoIntermediate class (III+IV)' ='Intermediate Class (Partner)',
+                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'
+                 )
+coefgroup <- list("Social Class - Resp. (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,rob4,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,scalebox = 1,
+                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+\pagebreak
+
+## Perceived Isolation
+
+```{r mod-isolation,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,class5,
+                        homclass,
+                        isolation,
+                        Q05pcm,
+                        Q03pcm,
+                        # isei08,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears, 
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Isolation x Social Class"=9:10
+                  )
+
+coefmap <-  list(isolation ="Perceived Isolation",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union: Yes',
+                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
+                 # know_total="Number contacts"
+                 # outgroup="Number outgroup"
+                 homclass ="Class-based network homogeneity"
+                 )
+
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+```
+
+```{r leverage2, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c("isolation"),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() + 
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Perceived Isolation")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
+# Predicted values 
+plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(legend.position = "none")+ 
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences")
+```
+
+```{r mod-intermacro2,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        isolation,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(isolation="Perceived Isolation",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "isolation:gini_mkt"="Isolation x Gini (M)",
+                                       homclas="Class-based homogeneity"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel2}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
+  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
+  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       linetype='Gini (Disposable)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       linetype='Gini (Market)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
+grid.arrange(p1,predval1,nrow = 1    
+             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
+             )
+```
+
+```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
+grid.arrange(p2,predval2,nrow = 1    
+             # top = "Perceived Isolation × Gini (Market)"  
+             )
+```
+
+\pagebreak
+
+# References
+
+<div id="refs"></div>
+
+# (APPENDIX) Appendix {-}
+
+`r if (knitr::is_latex_output()){ '\\appendix'}`          <!-- Si documento es latex, se genera sección de Anexos -->
+`r if (knitr::is_latex_output()){ '\\section{Appendix}'}` <!-- Si documento es latex, se genera titulo de Anexos -->
+```{r redistribution, echo=FALSE, fig.cap=c("Redistributive preferences by country in the ISSP 2017"), fig.height=4.5, fig.width=7.1, out.width='100%'}
 # x country   
@@
 ```
-
-```{r homogeneity,fig.height=3.4,fig.width=6,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '50%'}
-# x country
-dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
-resits_count <- dfreg %>%
-  group_by(country2,country) %>%
-  summarise_at(c("redist","homclass",
-                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
-
-myorder <-  resits_count$country2[order(resits_count$homclass)]
-ggplot(data = resits_count,aes(x =country2,y = homclass)) + 
-  geom_segment(aes(x=country2, xend=country2, y=0, yend=homclass), color="black") +
-  geom_point() +
-  scale_x_discrete(limits=myorder) +
-  ylab("Class-based homogeneity")+   
-  xlab("") +
-  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1.2))    
-```
-
-```{r class-hom,fig.height=7,fig.width=7,fig.cap=c("Redistribution, Network homogeneity and Social Class in the ISSP 2017"), out.width = '50%'}
-sizetext <- 2.5
-
-predis <-  
-resits_count %>%  
-ggplot(aes(y=redist, x=homclass)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0.3,0.5))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Class homogeneity")+
-  ylab("Redistributive preferences") +
-  labs(title = "Redistributive preferences and Class homogeneity",
-       caption =paste("r=",round(cor(resits_count$homclass, 
-                                     resits_count$redist),digits = 2),""))
-# cor.test(resits_count$homclass,resits_count$redist)
-
-p1 <- resits_count %>%  
-ggplot(aes(y=homclass, x=class3_3)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Working class (%)")+
-  ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Working class (%)",
-       caption =paste("r=",round(cor(resits_count$homclass,
-                                     resits_count$class3_3),digits = 2),""))
-
-# cor.test(resits_count$homclass,resits_count$class3_3)
-
-p2 <- resits_count %>%  
-ggplot(aes(y=homclass, x=class3_2)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Intermediate class (%)")+
-  ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Intermediate class (%)",
-       caption =paste("r=",round(cor(resits_count$homclass,
-                                     resits_count$class3_2),digits = 2),""))
-# cor.test(resits_count$homclass,resits_count$class3_2)
-p3 <- resits_count %>%  
-ggplot(aes(y=homclass, x=class3_1)) +
-  # geom_point() +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Service class (%)")+
-  ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Service class (%)",
-       caption =paste("r=",round(cor(resits_count$homclass,
-                                     resits_count$class3_1),digits = 2),""))
-# cor.test(resits_count$homclass,resits_count$class3_3)
-grid.arrange(predis,p1,p2,p3,nrow = 2)
-```
-
-<!-- - perceived isolation x redistribution (1 plot) -->
-<!-- - homogeneity x perceived isolation (1 plot) -->
-
-## Individual level
-
-1. Class: 
-    - having a working class position is associated with higher redistributive preferences
-    - class homogeneity is higher among the working class, and lower in the upper-class
-
-2. Network segregation
-    - being more segregated in terms of network homogeneity increase demand for redistribution
-
-<!-- - Perceived isolation -->
-<!--   - perceived isolation increases redistributive preferences -->
-
-<!-- Note: network segregation decreases perceived isolation *   -->
-
-3. Network segregation x Social Class
-    - The influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class
-
-```{r mod-homclass,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)") 
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1,
-                        isolation,
-                        MAINSTAT,
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("CHN")) %>%
-  # filter(!country2 %in% c("TWN")) %>%
-  # filter(!country2 %in% c("ZAF")) %>%
-  # filter(!country2 %in% c("FIN")) %>%
-  # filter(!country2 %in% c("USA")) %>%
-  # filter(!country2 %in% c("GBR")) %>%
-  # filter(!country2 %in% c("ISL")) %>%
-  # filter(!country2 %in% c("TUR","EST")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1 + union+ female+agenum +age2 + (1|country2),data=dfreg)
-rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1 + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
-# anova(rob3,rob4)
-# plot_model(rob4,type = "re",show.values = T)
-
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
-# anova(int_homo,int_homo2)
-# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
-
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 # know_total="Number contacts"
-                 # outgroup="Number outgroup"
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-
-```
-
-```{r leverage1, eval=FALSE, include=FALSE}
-pacman::p_load(influence.ME,lattice)
-# dfbetas-----------------------------------------------------------------------
-influence <- influence(rob3, "country2")
-dfbetas(influence,parameters=c(1,4)) 
-n_groups <- lme4::ngrps(rob3)
-
-influence_est=as.data.frame(dfbetas(influence))
-influence_est %>%  filter(homclass > 2/sqrt(n_groups))
-
-plot(influence, which="dfbetas", 
-     parameters=c(1,4),
-     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
-
-# cook-distance-----------------------------------------------------------------
-# cooks.distance(rob3, sort = TRUE)
-plot(influence, which="cook",
-     cutoff=4/n_groups, sort=TRUE,
-     xlab="Cooks Distance",
-     ylab="Country")
-
-sigtest1<- sigtest(influence, test=-1.96)
-sigtest1$homclass
-```
-
-```{r marg1,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "50%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)   
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Class-based homogeneity")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred1,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra,papaja)        
-# Predicted values
-
-plot_predictions(int_homo, condition = c("homclass","class3")) +
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "none", legend.title = element_blank())
-  # scale_fill_grey(start = 0.40, end = 0.6) +
-  # scale_color_grey(start = 0.40, end = 0.6)
-```
-
-\pagebreak
-## Macro level
-
-  - expected: economic inequality increases segregation (maybe weak or null effect)
-  - expected: economic inequality increase the influence of network homogeneity/segregation
-
-```{r ineq-homo,fig.height=4,fig.width=7.5,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '50%'}
-sizetext <- 2.5
-resits_count <- dfreg %>%
-  group_by(country2,country) %>%
-  summarise_at(c("redist","homclass", 
-                 "gini_disp","gini_mkt","giniindex"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
-p1 <- resits_count %>%  
-ggplot(aes(y=homclass, x=gini_disp)) +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Gini (Disposable)")+
-  ylab("Class homogeneity") +
-  labs(
-    # title = "Class homogeneity and Income Inequality (Disposable)",
-       caption =paste("r=",round(cor(resits_count$homclass,
-                                     resits_count$gini_disp),digits = 2),""))
-# cor.test(resits_count$homclass,resits_count$gini_disp)
-p2 <- resits_count %>%  
-ggplot(aes(y=homclass, x=gini_mkt)) +
-  geom_text(label=as.character(resits_count$country3),size=sizetext) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Gini (Market)")+
-  ylab("Class homogeneity") +
-  labs(
-    # title = "Class homogeneity and Income Inequality (Market)",
-       caption =paste("r=",round(cor(resits_count$homclass,
-                                     resits_count$gini_mkt),digits = 2),""))
-
-# cor.test(resits_count$homclass,resits_count$class3_3)
-grid.arrange(p1,p2,nrow = 1)
-```
-
-  <!-- - expected: in unequal countries the effect of network segregation and perceived isolation will be stronger  -->
-
-```{r mod-intermacro,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_gc,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        # giniot=gini,
-                        giniot=gv_spen,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        labst,
-                        labst1,
-                        isolation,
-                        MAINSTAT) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
-  na.omit()
-# T03dim(dfreg)
-
-main <- "redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
-# summary(giniD_int)
-
-giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
-# anova(giniOT_gdp,giniOT_rs)
-
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
-                caption.above=T,
-                  # include.thresholds=FALSE,
-                  custom.coef.map=list(homclass="Network Homogeneity",
-                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "homclass:gini_disp"="Homogeneity x Gini (D)",
-                                       "gini_mkt"="Gini (Market) ",
-                                       "homclass:gini_mkt"="Homogeneity x Gini (M)"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-```
-
-```{r crosslevel}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
-p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-predval1 <- 
-plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       colour='Gini (Disposable)',fill='Gini (Disposable)') +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-# Predicted values 
-predval2 <- 
-plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)+
-  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       colour='Gini (Disposable)',fill='Gini (Disposable)') +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-```
-
-```{r crossginiD, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='60%'}
-grid.arrange(p1,predval1,nrow = 1 
-             # top = "Network homogeneity × Gini (Disposable)"   
-             )
-```
-
-```{r crossginiM, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='60%'}
-grid.arrange(p2,predval2,nrow = 1  
-             # top = "Network homogeneity × Gini (Market)"
-             ) 
-```
-
-\pagebreak
-
-# References
-
-<div id="refs"></div>
-
-# Other analysis
-
-- Perceived Isolation
-- Network homogeneity (Strong ties)
-- Network homogeneity (Weak ties)
-- R's and Partner social class
-- Homogeneity x other macro variables
-
-## Perceived Isolation
-
-```{r mod-isolation,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        isolation,
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears, 
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(full1,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
-coefmap <-  list(isolation ="Perceived Isolation",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):isolation'='Isolation x Service Class',
-                 'class3Working Class (V+VI+VII):isolation'='Isolation x Working Class',
-                  homclass ="Class-based network homogeneity"
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Isolation x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
-```
-
-```{r leverage2, eval=FALSE, include=FALSE}
-pacman::p_load(influence.ME,lattice)
-# dfbetas-----------------------------------------------------------------------
-influence <- influence(rob3, "country2")
-dfbetas(influence,parameters=c(1,4)) 
-n_groups <- lme4::ngrps(rob3)
-
-influence_est=as.data.frame(dfbetas(influence))
-influence_est %>%  filter(homclass > 2/sqrt(n_groups))
-
-plot(influence, which="dfbetas", 
-     parameters=c("isolation"),
-     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
-
-# cook-distance-----------------------------------------------------------------
-# cooks.distance(rob3, sort = TRUE)
-plot(influence, which="cook",
-     cutoff=4/n_groups, sort=TRUE,
-     xlab="Cooks Distance",
-     ylab="Country")
-
-sigtest1<- sigtest(influence, test=-1.96)
-sigtest1$homclass
-```
-
-```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "50%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() + 
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Perceived Isolation")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '50%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
-# Predicted values 
-plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
-    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(legend.position = "none")+ 
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences")
-```
-
-```{r mod-intermacro2,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass,
-                        isolation,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        labst,
-                        labst1) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# T03dim(dfreg)
-
-main <- "redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2 +homclass"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# summary(giniD_int)
-
-giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
-                caption.above=T,
-                  # include.thresholds=FALSE,
-                  custom.coef.map=list(isolation="Perceived Isolation",
-                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "isolation:gini_disp"="Isolation x Gini (D)",
-                                       "gini_mkt"="Gini (Market) ",
-                                       "isolation:gini_mkt"="Isolation x Gini (M)",
-                                       homclas="Class-based homogeneity"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-```
-
-```{r crosslevel2}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
-p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-predval1 <- 
-plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       linetype='Gini (Disposable)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-# Predicted values 
-predval2 <- 
-plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
-  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       linetype='Gini (Market)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-```
-
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='50%'}
-grid.arrange(p1,predval1,nrow = 1    
-             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
-             )
-```
-
-```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='50%'}
-grid.arrange(p2,predval2,nrow = 1    
-             # top = "Perceived Isolation × Gini (Market)"  
-             )
-```
-
-## Strong & weak ties
-
-___Homogeneity: strong ties___
-
-```{r mod-strongties,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_s,
-                        # homclass=eindex_s,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-___Homogeneity: weak ties___
-
-```{r mod-weakties,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_w,
-                        # homclass=eindex_w,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-___Homogeneity: respondent class___
-
-```{r mod-ownclass, cache=TRUE, results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
-
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3=class3res,
-                        class3spo,
-                        homclass,
-                        # homclass=eindex_res,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        labst,
-                        labst1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+ (1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
-rob5 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(homclass|country2),data=dfreg)
-
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ class3spo +(1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and Own social class " 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class',
-                 'class3spoService Class (I+II)' ='Service Class (Partner)',
-                 "class3spoWorking Class (V+VI+VII)"='Working Class (Partner)'
-
-                 )
-coefgroup <- list("Social Class - Resp. (ref: Intermediate Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,rob4,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-## Other macro variables
-
-Source: https://www4.wider.unu.edu/?ind=1&type=ChoroplethSeq&year=70&byCountry=false&slider=buttons
-
-* The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
-<!-- * **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income -->
-<!-- * 90/50 ratio = the ratio of Decile 10 income to Decile 5 income (the median) -->
-<!-- * 50/10 ratio = the ratio of Decile 5 income (the median) to Decile 1 income. -->
-
-```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_gc,
-                        # homclass=homclass_res,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,ttheilge1,
-                        gv_spen=gv_spen,
-                        top10,
-                        middle50,
-                        palmaratio,
-                        rgdpna,
-                        individualism,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        labst,
-                        labst1,
-                        isolation,
-                        MAINSTAT) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-    # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
-   na.omit()
-
-int_palma <- lmer(redist~class3+ isolation+homclass*palmaratio+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_pc10  <- lmer(redist~class3+ isolation+homclass*top10+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_pc50  <- lmer(redist~class3+ isolation+homclass*middle50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_gini_wiid  <- lmer(redist~class3+ isolation+homclass*giniindex+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_theil  <- lmer(redist~class3+ isolation+homclass*ttheilge1+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_indivi<- lmer(redist~class3+ isolation+homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_govspe<- lmer(redist~class3+ isolation+homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_indivi,int_govspe
-                 # int_gini_wiid,int_theil
-                 )
-
-cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
-customcoef <- 
-list(homclass = "Class-based network homogeneity",
-  logrgdpna           = "log GDP",
-  palmaratio               = "Palma Ratio",
-  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
-  top10             = "Share National Income - top 10%",
-  "homclass:top10"    = "Homogeneity x top 10",
-  middle50             = "Share National Income -  bottom 50%",
-  "homclass:middle50"    = "Homogeneity x bottom 50",
-  individualism         = "Individualism Index*",
-  "homclass:individualism" = "Homogeneity x Individualism",
-  gv_spen               = "Gov. Spending (% GDP)*",
-  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
-)
-texreg::knitreg(models_m,
-                custom.coef.map = customcoef,
-                caption.above = T,caption = cap1)
-```
-
-```{r,fig.height=4,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
-p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
-  xlab("Palma ratio (top 10%/ bottom 40%)") + geom_point()+ geom_hline(yintercept = 0) +
-    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
-
-# plot_predictions(int_palma, condition = list("homclass",palmaratio=range),gray = F) +
-#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-#        linetype='Palma Ratio') +
-#   xlab("Class-based homogeneity")+
-#   ylab("Redistributive preferences") +
-#   theme(legend.position = "right")
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="top10") +
-  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))
-
-# plot_predictions(int_pc10, condition = list("homclass",top10=range),gray = F) +
-#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-#        linetype='Palma Ratio') +
-#   xlab("Class-based homogeneity")+
-#   ylab("Redistributive preferences") +
-#   theme(legend.position = "right")
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="middle50") +
-  xlab("Share National Income - middle 50%") + geom_point()+ geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
-
-# plot_predictions(int_pc50, condition = list("homclass",middle50=range),gray = F) +
-#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-#        linetype='Palma Ratio') +
-#   xlab("Class-based homogeneity")+
-#   ylab("Redistributive preferences") +
-#   theme(legend.position = "right")
-
-# interplot::interplot(m = int_gini_wiid,var1 = "homclass",var2="giniindex") +
-#   xlab("Gini (WIID)") + geom_point()+ geom_hline(yintercept = 0) +
-#     labs(caption = paste0("N=",nobs(int_gini_wiid),", Countries=",lme4::ngrps(int_gini_wiid)))
-
-# interplot::interplot(m = int_theil,var1 = "homclass",var2="ttheilge1") +
-#   xlab("Theil Index") + geom_point()+ geom_hline(yintercept = 0) +
-#     labs(caption = paste0("N=",nobs(int_theil),", Countries=",lme4::ngrps(int_theil)))
-
-# p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
-#   xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
-#   labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
-grid.arrange(p3,p4,p5,nrow = 1) 
-```
-
-```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%',}
-# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
-#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
-#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
-
-p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
-  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
-
-predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-       linetype='Individualism') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
-  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
-
-predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
-       linetype='Gov.Spend') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-grid.arrange(p9,predval9,
-             p8,predval8,nrow = 2)
-```

### 2023-10-09 procesamiento/prod_prep.Rmd
avance lunes

@@
 
+relig <- haven::read_dta(here::here("input/data/original/ZA7570_v2-1-0.dta"))
+religTR <- relig %>% filter(country==792)
+
 df1 <- df1 %>% rename(topbot=TOPBOT)
@@
                         WEIGHT=weight,
-                        URBRURAL=urbrural)  
+                        URBRURAL=urbrural,
+                        WORK=work,
+                        HOMPOP=hompop)  
 dfES$c_alphan <- NULL
@@
 for (i in income_country) {
-  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  # df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
   df1[[i]] <- as.numeric(df1[[i]])
@@
 
+df1$AT_INC<- car::recode( df1$AT_INC,"999990:999999=NA")
+df1$AU_INC<- car::recode( df1$AU_INC,"9999990:9999999=NA")
+df1$CH_INC<- car::recode( df1$CH_INC,"999990:999999=NA")
+df1$CN_INC<- car::recode( df1$CN_INC,"9999990:9999999=NA")
+df1$CZ_INC<- car::recode( df1$CZ_INC,"999990:999999=NA")
+df1$DE_INC<- car::recode( df1$DE_INC,"999990:999999=NA")
+df1$DK_INC<- car::recode( df1$DK_INC,"9999990:9999999=NA")
+df1$ES_INC<- car::recode( df1$ES_INC,"999990:999999=NA")
+df1$FI_INC<- car::recode( df1$FI_INC,"999990:999999=NA")
+df1$FR_INC<- car::recode( df1$FR_INC,"999990:999999=NA")
+df1$GB_INC<- car::recode( df1$GB_INC,"999990:999999=NA")
+df1$HR_INC<- car::recode( df1$HR_INC,"999990:999999=NA")
+df1$HU_INC<- car::recode( df1$HU_INC,"9999990:9999999=NA")
+df1$IL_INC<- car::recode( df1$IL_INC,"999990:999999=NA")
+df1$IN_INC<- car::recode( df1$IN_INC,"999990:999999=NA")
+df1$IS_INC<- car::recode( df1$IS_INC,"99999990:99999999=NA")
+df1$JP_INC<- car::recode( df1$JP_INC,"99999990:99999999=NA")
+df1$LT_INC<- car::recode( df1$LT_INC,"999990:999999=NA")
+df1$MX_INC<- car::recode( df1$MX_INC,"999990:999999=NA")
+df1$NZ_INC<- car::recode( df1$NZ_INC,"999990:999999=NA")
+df1$PH_INC<- car::recode( df1$PH_INC,"999990:999999=NA")
+df1$RU_INC<- car::recode( df1$RU_INC,"999990:999999=NA")
+df1$SE_INC<- car::recode( df1$SE_INC,"999990:999999=NA")
+df1$SI_INC<- car::recode( df1$SI_INC,"999990:999999=NA")
+df1$SK_INC<- car::recode( df1$SK_INC,"999990:999999=NA")
+df1$SR_INC<- car::recode( df1$SR_INC,"999990:999999=NA")
+df1$TH_INC<- car::recode( df1$TH_INC,"999990:999999=NA")
+df1$TW_INC<- car::recode( df1$TW_INC,"9999990:9999999=NA")
+df1$US_INC<- car::recode( df1$US_INC,"999990:999999=NA")
+df1$ZA_INC<- car::recode( df1$ZA_INC,"999990:999999=NA")
+
+frq(df1$EE_INC)
+
+c((200 )/1,
+    (201 + 300)/2,
+    (301 + 400)/2,
+    (401 + 500)/2,
+    (501 + 650)/2,
+    (651 + 800)/2,
+    (801 + 1000)/2,
+    (1001 +1300)/2,
+    (1301 + 1600)/2,
+    (1601 +2100)/2,
+    (2500)/1)
+
+df1$EE_INC<- car::recode( df1$EE_INC,"1=200.0;2=250.5;3=350.5;4=450.5;5=575.5;6=725.5;7=900.5;8=1150.5;9=1450.5;10=1850.5;11=2500.0;999990:999999=NA")
+
+frq(df1$TR_INC)
+df1$TR_INC<- car::recode( df1$TR_INC,"999990:999997=NA")
 # lapply(df1[,income_country], table)  # Ok el recode de ingresos familiares 
 # Crear variable ingresos unica 
-df1 <- df1 %>% mutate(income = coalesce(AT_INC,AU_INC,CH_INC,CN_INC,CZ_INC,DE_INC,DK_INC,ES_INC,FI_INC,FR_INC,GB_INC,HR_INC,HU_INC,IL_INC,IN_INC,IS_INC,
-                                        JP_INC,LT_INC,MX_INC,NZ_INC,PH_INC,RU_INC,SE_INC,SI_INC,SK_INC,SR_INC,TH_INC,TW_INC,US_INC,ZA_INC))
+df1 <- df1 %>% 
+  mutate(income = coalesce(AT_INC,AU_INC,CH_INC,CN_INC,CZ_INC,DE_INC,DK_INC,ES_INC,
+                           FI_INC,FR_INC,GB_INC,HR_INC,HU_INC,IL_INC,IN_INC,IS_INC,
+                           JP_INC,LT_INC,MX_INC,NZ_INC,PH_INC,RU_INC,SE_INC,SI_INC,
+                           SK_INC,SR_INC,TH_INC,TW_INC,US_INC,ZA_INC,EE_INC,TR_INC))
+
+table(df1$c_alphan,is.na(df1$income))
+
+# summary(df1$JP_RINC)
+# summary(df1$JP_RINC)
+# 
+# summary(df1$EE_INC)
+# summary(df1$TR_INC)
 
 #frq(df1$income==0)
-#frq(df1$HOMPOP)
+frq(df1$HOMPOP)
 df1$hhpop <- as.numeric(df1$HOMPOP) 
 df1$hhpop[df1$hhpop %in%c(0,97,99)] <- NA
-#frq(df1$hhpop)
+# frq(df1$hhpop)
 df1$incomepcap <- as.numeric(df1$income/df1$hhpop) # Ingreso per capita del hogar
@@
                           levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
+frq(df1$Q05pc)
 
@@
                           levels = c("T01","T02","T03","Missing")) 
+frq(df1$Q03pcm)
+
+table(as_character(df1$country),df1$Q03pcm)
 
@@
 for (i in income_country) {
-  df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
+  # df1[[i]] <- car::recode(var = df1[[i]],"999990:99999999=NA")
   df1[[i]] <- as.numeric(df1[[i]])
   }
+
+df1$AT_RINC<- car::recode( df1$AT_RINC,"999990:999999=NA")
+df1$AU_RINC<- car::recode( df1$AU_RINC,"999990:999999=NA")
+df1$CH_RINC<- car::recode( df1$CH_RINC,"999990:999999=NA")
+df1$CN_RINC<- car::recode( df1$CN_RINC,"9999990:9999999=NA")
+df1$CZ_RINC<- car::recode( df1$CZ_RINC,"999990:999999=NA")
+df1$DE_RINC<- car::recode( df1$DE_RINC,"999990:999999=NA")
+df1$DK_RINC<- car::recode( df1$DK_RINC,"999990:999999=NA")
+df1$ES_RINC<- car::recode( df1$ES_RINC,"999990:999999=NA")
+df1$FI_RINC<- car::recode( df1$FI_RINC,"999990:999999=NA")
+df1$FR_RINC<- car::recode( df1$FR_RINC,"999990:999999=NA")
+df1$GB_RINC<- car::recode( df1$GB_RINC,"999990:999999=NA")
+df1$HR_RINC<- car::recode( df1$HR_RINC,"999990:999999=NA")
+df1$HU_RINC<- car::recode( df1$HU_RINC,"999990:999999=NA")
+df1$IL_RINC<- car::recode( df1$IL_RINC,"999990:999999=NA")
+df1$IN_RINC<- car::recode( df1$IN_RINC,"999990:999999=NA")
+df1$IS_RINC<- car::recode( df1$IS_RINC,"9999990:9999999=NA")
+df1$JP_RINC<- car::recode( df1$JP_RINC,"99999990:99999999=NA")
+df1$LT_RINC<- car::recode( df1$LT_RINC,"999990:999999=NA")
+df1$MX_RINC<- car::recode( df1$MX_RINC,"999990:999999=NA")
+df1$NZ_RINC<- car::recode( df1$NZ_RINC,"999990:999999=NA")
+df1$PH_RINC<- car::recode( df1$PH_RINC,"999990:999999=NA")
+df1$RU_RINC<- car::recode( df1$RU_RINC,"999990:999999=NA")
+df1$SE_RINC<- car::recode( df1$SE_RINC,"999990:999999=NA")
+df1$SI_RINC<- car::recode( df1$SI_RINC,"999990:999999=NA")
+df1$SK_RINC<- car::recode( df1$SK_RINC,"999990:999999=NA")
+df1$SR_RINC<- car::recode( df1$SR_RINC,"999990:999999=NA")
+df1$TH_RINC<- car::recode( df1$TH_RINC,"999990:999999=NA")
+df1$TW_RINC<- car::recode( df1$TW_RINC,"999990:999999=NA")
+df1$US_RINC<- car::recode( df1$US_RINC,"999990:999999=NA")
+df1$ZA_RINC<- car::recode( df1$ZA_RINC,"999990:999999=NA")
+
+frq(df1$EE_RINC)
+df1$EE_RINC<- car::recode( df1$EE_RINC,"1=200.0;2=250.5;3=350.5;4=450.5;5=575.5;6=725.5;7=900.5;8=1150.5;9=1450.5;10=1850.5;11=2500.0;999990:999999=NA")
+frq(df1$EE_RINC)
+
+frq(df1$TR_RINC)
+df1$TR_RINC<- car::recode( df1$TR_RINC,"999990:999997=NA")
+frq(df1$TR_RINC)
 
@@
                                         TH_RINC, TW_RINC,
-                                        US_RINC, ZA_RINC))
-#frq(df1$incomer==0)
+                                        US_RINC, ZA_RINC, 
+                                        EE_RINC,TR_RINC))
+table(df1$c_alphan,is.na(df1$income))
+prop.table(table(df1$c_alphan,is.na(df1$income)),margin =1)
 
@@
                                               Q05r=ntile(incomer,5),
+                                           Q03r=ntile(incomer,3),
                                               zincpcr=scale(incomer,center = TRUE),
                                               logincr=log(incomer)) %>% ungroup()
-#frq(df1$incomer)
-#frq(df1$incomepcap)
+
+df1$Q05rm <- car::recode(df1$Q05r,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
+                          as.factor = T,
+                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing"))
+
+df1$Q03rm <- car::recode(df1$Q03r,"1='T01';2='T02';3='T03';NA='Missing'",
+                          as.factor = T,
+                          levels = c("T01","T02","T03","Missing"))
+
+table(as_character(df1$country),df1$Q03rm)
+
+# frq(df1$incomer)
+# frq(df1$incomepcap)
 # Single household 
@@
 
+```{r paid-work}
+frq(df1$WORK)
+df1$workst <- car::recode(
+  as.numeric(df1$WORK),
+  recodes = "1='In paid work';2:3='Not in paid work';c(9)=NA",
+  levels = c('In paid work', 'Not in paid work'),
+  as.factor = T
+)
+sjlabelled::set_label(df1$workst) <- "Work status"
+frq(df1$workst)
+```
+
 ```{r union}
-#frq(df1$WORK)
-#frq(df1$UNION)
+frq(df1$UNION)
 df1$union <- car::recode(as.numeric(df1$UNION),
-                         recodes= "1:2='Yes';c(0,3,7,8)='No';9=NA",
+                         recodes= "1:2='Yes';c(0,3,7)='No';8:9=NA",
                          levels = c("No","Yes"))
-#frq(df1$union)
+frq(df1$union)
 ```

### 2023-10-09 paper.Rmd
avances lunes

@@
 rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
-anova(rob3,rob4)
+# anova(rob3,rob4)
 
@@
 
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg,weights = WEIGHT)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg,weights = WEIGHT)
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
 # anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg,weights = WEIGHT)
+giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
 # summary(giniD_int)
 
-giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg,weights = WEIGHT)
-giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg,weights = WEIGHT)
+giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
 # anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg,weights = WEIGHT)
+giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
 # anova(giniOT_gdp,giniOT_rs)
@@
 int_theil  <- lmer(redist~class3+ homclass*ttheilge1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_indivi,int_govspe,int_d10d1
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1
                  # int_gini_wiid,int_theil
@@
 
-```{r,fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
+```{r homclass-ineq,fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
 p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
@@
 grid.arrange(p3,p3.pred,p6,p6.pred,nrow = 2)
-```
-
-```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
-# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
-#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
-#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))
-
-p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
-  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
-
-predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-       linetype='Individualism') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
-  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
-
-predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
-       linetype='Gov.Spend') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-grid.arrange(p9,predval9,
-             p8,predval8,nrow = 2)
 ```
@@
                         gini_mkt,
-                        giniot=gini,
+                        giniot=gini,palmaratio,d10d1,
                         rgdpna,
@@
          edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
   na.omit()
@@
 rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# rob4 <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# anova(rob3,rob4)
 # Interactions segregation x class
 int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
 
@@
                         gini_mkt,
-                        giniot=gini,
+                        giniot=gini,d10d1,palmaratio,
                         rgdpna,
@@
 rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# rob4 <- lmer(redist~class3+ homclass+logrgdpna+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# anova(rob3,rob4)
 # Interactions segregation x class
 int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
 
@@
                 )
+```
+
+\pagebreak
+
+## Gov's spending and individualism
+
+```{r mod-spend-indv, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        giniindex,ttheilge1,
+                        gv_spen=gv_spen,
+                        top10,
+                        middle50,
+                        palmaratio,
+                        d10d1,
+                        rgdpna,
+                        individualism,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+   na.omit()
+int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+models_m <- list(int_indivi,int_govspe)
+cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  individualism         = "Individualism Index*",
+  "homclass:individualism" = "Homogeneity x Individualism",
+  gv_spen               = "Gov. Spending (% GDP)*",
+  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
+)
+texreg::knitreg(models_m,scalebox = 1,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+```
+
+```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
+p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
+  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+
+predval8 <- 
+plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+       linetype='Individualism') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
+  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+
+predval9 <- 
+plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
+       linetype='Gov.Spend') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p9,predval9,
+             p8,predval8,nrow = 2)
 ```

### 2023-10-09 paper.Rmd
render html

@@
 output:
-  bookdown::pdf_document2:
-    template: null
-    toc: false
-    keep_tex: false
-    pandoc_args:
-      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
   bookdown::html_document2:
@@
     number_sections: false   
+  bookdown::pdf_document2:
+    template: null
+    toc: false
+    keep_tex: false
+    pandoc_args:
+      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
 linkcolor: blue                         # enlaces y citas en color azul

### 2023-10-10 paper.Rmd
reunion miercoles

@@
 
-- The moral economy of class [@Svallfors2006]
-
 - Class interests in the economic domain [@lindh_class_2020]
+- The moral economy of class - the attitudinal domain of redistribution and the role of the state [@Svallfors2006]
 
@@
 ## Class-based inequality in social networks
+
+This section will review the state of the art on the link between class/status and social networks, particularly the existing literature on the different forms of social capital.
 
@@
 ## Social ties on the demand for redistribution and welfare
+
+This section will focus on the link between social ties and attitude formation in the economic domain.
+Also, it will address neighbouring evidence that could support the argument.
+At this point, at least two mechanisms are discussed in the literature.
+The first one is social influence or socialization mechanism.
+The second one is attitude polarization as a result of network segregation.
+
+<!-- Following Lin's approach to the role fo social ties, these are understood as resources that provide opportunities for action.
+Therefore, lacking of them can be interpreted as lower resources.
+Homogeneity in terms of social ties could represent the concentration of high-resource social ties, in the case of the upper-classes, and the opposite in the case of the lower-classes.
+-->
 
@@
                   "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
+                 "unionYes" = 'Union membership: Yes',
                  'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
@@
                   custom.gof.names = gof1
+                )
+```
+
+```{r coefplot,eval=FALSE, include=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,dotwhisker,ggplot2,broom.mixed)
+
+m1_df <-
+    broom.mixed::tidy(rob3) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                    "class3Working Class (V+VI+VII)",
+                                                    "homclass")) %>% mutate(model = "Model 1")
+m2_df <-
+    broom.mixed::tidy(int_homo) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                        "class3Working Class (V+VI+VII)",
+                                                        "homclass",
+                                                        "class3Intermediate class (III+IV):homclass",
+                                                        "class3Working Class (V+VI+VII):homclass")) %>% mutate(model = "Model 2")
+
+two_models <- rbind(m1_df)
+
+  dwplot(two_models,
+       vline = geom_vline(xintercept = 0,colour = "black",linetype = 1,size=0.01),
+       style = "dotwhisker",
+       dot_args =  list(size=5),
+       whisker_args = list(size=2),
+       vars_order = c("homclass",
+                      "class3Intermediate class (III+IV)",
+          "class3Working Class (V+VI+VII)",
+          "class3Intermediate class (III+IV):homclass",
+          "class3Working Class (V+VI+VII):homclass")) %>%
+
+     relabel_predictors(
+        c("homclass"="Class based network homogeneity",
+          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
+          "class3Working Class (V+VI+VII)"="Working Class",
+          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
+          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
+      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(
+        plot.title = element_text(face = "bold"),
+        legend.position = c(0.007, 0.01),
+        legend.justification = c(0, 0),
+        legend.background = element_rect(colour = "grey80"),
+        legend.title = element_blank(),
+        axis.text.y.left = element_text(face = "bold",size = 12)
   )
@@
                         union,
-                        WEIGHT,
                         workst) %>% 
@@
   labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       colour='Gini (Disposable)',fill='Gini (Disposable)') +
+       colour='Gini (Market)',fill='Gini (Market)') +
   xlab("Network homogeneity")+
@@
                   "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
+                 "unionYes" = 'Union membership: Yes',
                  'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate class',
@@
                   "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
+                 "unionYes" = 'Union membership: Yes',
                  'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',

### 2023-10-10 procesamiento/prod_analysis-robust.Rmd
reunion miercoles

--- 2023-09-21 procesamiento/prod_analysis-robust.Rmd
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
 df1$redistF <- as.factor(df1$redist)
-
 dfreg <- df1 %>% dplyr::select(redist=redistF,
                         class3,
+                        class5,
                         homclass,
-                        Q05pcm,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=zincpc,
+                        # Q03rm=
+                        # isei08,
                         rgdpna,
@@
                         union,
-                        labst,
-                        labst1
+                        workst,
+                        # isolation,  
+                        # MAINSTAT,
+                        # activities,
+                        # WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt"
                         ) %>% 
@@
          edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
   na.omit()
-# dim(dfreg)
 
@@
 full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-# rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-# rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+anova(rob3,rob4)
 # Interactions segregation x class
-int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
+int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
 
@@
 coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                  'class3Working Class (V+VI+VII)' ='Working Class',
@@
                  "edyears" = 'Education in years',
-                  "labst1Not in labour force"="Not in labor force",
-                 "unionYes" = 'Union: Yes',
-                 'class3Service Class (I+II):homclass'='Homogeneity x Service Class',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
                  'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
                  )
-coefgroup <- list("Social Class (ref: Intermediate Class)"=2:3,
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
                   "Income Tercile (ref: Low)"=4:5,
@@
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
                   include.thresholds=FALSE,
@@
                 )
+
+avg_slopes(
+  int_homo,
+  by = "class3",
+  variables = "homclass")
 ```

### 2023-10-10 procesamiento/prod_prep-macro.Rmd
reunion miercoles

@@
 wiid$ccode <- countrycode::countrycode(sourcevar = wiid$iso,origin = "iso3c",destination = "iso3n")
+
+wiid_d10d01 <- 
+  read.csv(file = here::here("input/data/original/wid-percentiles/wiid-data-D10D01-ratio.csv"),sep = ";")
+
+names(wiid_d10d01) <- tolower(names(wiid_d10d01))
+names(wiid_d10d01) <- gsub('\\.', '', names(wiid_d10d01))
+wiid_d10d01$ccode <- countrycode::countrycode(sourcevar = wiid_d10d01$iso,origin = "iso3c",destination = "iso3n")
+wiid_d10d01 <- 
+  wiid_d10d01 %>%  
+  filter(ccode %in% countries$ccode) %>% 
+  filter(year==2017) %>% 
+  select(ccode,everything(),-iso,-country,-year,-giniindex)
+
 wiid_2017 <- 
@@
   filter(year==2017) %>% 
-  select(ccode,everything(),-iso,-country,-year) 
+  select(ccode,everything(),-iso,-country,-year) %>% 
+  left_join(wiid_d10d01,by="ccode")
 ```
@@
 df2 %>% mutate(country2=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "iso3c"),
-               country3=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "country.name")) %>% 
+               country3=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "country.name"),
+               region=countrycode::countrycode(sourcevar = ccode,origin = "iso3n",destination = "region23")) %>% 
   select(ccode,country2,country3,everything())

### 2023-10-10 paper.Rmd

@@
 author:
+- name: Julio Iturra-Sanhueza
 - name: Julio Iturra-Sanhueza
@@
 
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(theme_minimal())
+ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
+```
+
 #  Introduction

### 2023-10-11 paper.Rmd
meeting patrick

--- 2023-10-10 paper.Rmd
@@
 ---
-title: "Network segregation, Social Isolation and Preference for Redistribution across societies"
+title: "Network segregation and Preferences for Redistribution across societies"
 css: "input/css/custom.css" # custom CSS para html
@@
 # Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
-# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua.
-Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
+abstract: |
+ The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens.
+However, these consequences have been unevenly experienced across the social structure.
+The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
+Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support.
+Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
+Consequently, inequalities in access to certain social positions (i.e.
+occupations) are translated into a lack of social resources beyond individual economic and cultural capital.
+Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
+Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties.
+To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
+The results of multilevel estimations show that being socially segregated increases demand for redistribution.
+Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class.
+At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution.
+However, cross-level interactions do not provide supporting evidence on this behalf.
+
+   **Keywords**: network segregation, redistributive preferences, economic inequality 
 output:
+  bookdown::pdf_document2:
+    template: null
+    toc: false
+    keep_tex: false
+    pandoc_args:
+      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
   bookdown::html_document2:
@@
     number_sections: false   
-  bookdown::pdf_document2:
-    template: null
-    toc: false
-    keep_tex: false
-    pandoc_args:
-      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
+always_allow_html: true      
 linkcolor: blue                         # enlaces y citas en color azul
@@
 
+```{r eval=FALSE, include=FALSE}
+ # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
+ # clean #in the yml
+ rmarkdown::render("paper.Rmd", output_format = "bookdown::pdf_document2")
+ rmarkdown::render("paper.Rmd", output_format = "bookdown::html_document2")
+ rmarkdown::render("paper.Rmd", output_format = "bookdown::word_document2")
+```
+
 <!-- - considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad -->
@@
 options(knitr.kable.NA = '') # NA en kable = ''
+```
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(theme_minimal())
+ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
 ```
@@
 
+gini_sig <- 
+p1$data %>% 
+  filter(ub>0 & lb >0) %>% 
+  dplyr::select(fake)
+
+dfreg %>% filter(gini_disp >= min(gini_sig$fake),gini_disp <= max(gini_sig$fake)) %>% dplyr::select(country2)
+
+table(dfreg$gini_disp)
+
+dfreg %>% filter(gini_disp %in%)
+
 p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
@@
 - Homogeneity x other macro variables
+- Egalitarian economic preferences (Index)
 - Network homogeneity (Strong ties)
@@
 - R's and Partner social class
-- Perceived Isolation
 
@@
 
+## Egalitarian economic preferences
+
+```{r mod-homclass-egal,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist=egal3,
+                        class3,
+                        class5,
+                        homclass,
+                        Q03pcm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=zincpc,
+                        # Q03rm=
+                        # isei08,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst,
+                        # isolation,  
+                        # MAINSTAT,
+                        # activities,
+                        # WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt"
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  na.omit()
+
+# frq(df1$region)
+# frq(dfreg$country2)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+# anova(rob3,rob4)
+
+# plot_model(rob4,type = "re",show.values = T)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
+# anova(int_homo,int_homo2)
+# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
+
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+cap1 <- "Multilevel regression for egalitarian preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modegalindex)",cap1),caption.above=T,scalebox = 0.5,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r coefplot2,eval=FALSE, include=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,dotwhisker,ggplot2,broom.mixed)
+
+m1_df <-
+    broom.mixed::tidy(rob3) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                    "class3Working Class (V+VI+VII)",
+                                                    "homclass")) %>% mutate(model = "Model 1")
+m2_df <-
+    broom.mixed::tidy(int_homo) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                        "class3Working Class (V+VI+VII)",
+                                                        "homclass",
+                                                        "class3Intermediate class (III+IV):homclass",
+                                                        "class3Working Class (V+VI+VII):homclass")) %>% mutate(model = "Model 2")
+
+two_models <- rbind(m1_df)
+
+  dwplot(two_models,
+       vline = geom_vline(xintercept = 0,colour = "black",linetype = 1,size=0.01),
+       style = "dotwhisker",
+       dot_args =  list(size=5),
+       whisker_args = list(size=2),
+       vars_order = c("homclass",
+                      "class3Intermediate class (III+IV)",
+          "class3Working Class (V+VI+VII)",
+          "class3Intermediate class (III+IV):homclass",
+          "class3Working Class (V+VI+VII):homclass")) %>%
+
+     relabel_predictors(
+        c("homclass"="Class based network homogeneity",
+          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
+          "class3Working Class (V+VI+VII)"="Working Class",
+          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
+          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
+      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(
+        plot.title = element_text(face = "bold"),
+        legend.position = c(0.007, 0.01),
+        legend.justification = c(0, 0),
+        legend.background = element_rect(colour = "grey80"),
+        legend.title = element_blank(),
+        axis.text.y.left = element_text(face = "bold",size = 12)
+  )
+```
+
+```{r leverage2, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c(1,4),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on egalitarian economic preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)   
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Class-based homogeneity")+
+  xlab("Social Class")+
+  ggtitle("Egalitarian economic preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Conditional linear Predictions for network homogeneity on egalitarian economic Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra,papaja)        
+# Predicted values
+
+plot_predictions(int_homo, condition = c("homclass","class3")) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Network homogeneity")+
+  ylab("Egalitarian economic preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+  # scale_fill_grey(start = 0.40, end = 0.6) +
+  # scale_color_grey(start = 0.40, end = 0.6)
+```
+
+```{r mod-intermacro-egal,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist=egal3,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        # giniot=gini,
+                        # giniot=gv_spen,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                # include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+\pagebreak
+```{r crosslevel-egal}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
+p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "homclass",var2="gini_mkt") +
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       colour='Gini (Disposable)',fill='Gini (Disposable)') +
+  xlab("Network homogeneity")+
+  ylab("Egalitarian economic preferences") +
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       colour='Gini (Market)',fill='Gini (Market)') +
+  xlab("Network homogeneity")+
+  ylab("Egalitarian economic preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD-egal, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Disposable)"),out.width='100%'}
+grid.arrange(p1,predval1,nrow = 1 
+             # top = "Network homogeneity × Gini (Disposable)"   
+             )
+```
+
+```{r crossginiM-egal, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Network homogeneity and Gini (Market)"),out.width='100%'}
+grid.arrange(p2,predval2,nrow = 1  
+             # top = "Network homogeneity × Gini (Market)"
+             ) 
+```
+
+```{r mod-other-macro-egal,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist=egal3,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        top10,
+                        middle50,
+                        palmaratio,
+                        d10d1,
+                        giniindex,
+                        ttheilge1,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+   na.omit()
+
+int_palma <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ homclass*top10+edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+homclass*middle50+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_d10d1<- lmer(redist~class3+ homclass*d10d1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_gini_wiid  <- lmer(redist~class3+ homclass*giniindex+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_theil  <- lmer(redist~class3+ homclass*ttheilge1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality for Egaliatarian economic preferences")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  palmaratio               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
+  # individualism         = "Individualism Index*",
+  # "homclass:individualism" = "Homogeneity x Individualism",
+  # gv_spen               = "Gov. Spending (% GDP)*",
+  # "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+    d10d1             = "Ratio D10/D01",
+  "homclass:d10d1"    = "Homogeneity x Ratio D10/D01",
+    giniindex             = "Gini (WIID)",
+  "homclass:giniindex"    = "Homogeneity x Gini (WIID)",
+   ttheilge1             = "Theil Index",
+  "homclass:ttheilge1"    = "Homogeneity x Theil Index"
+)
+texreg::knitreg(models_m,scalebox = 0.50,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)    
+```
+
+```{r homclass-ineq-egal,fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
+p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
+  xlab("Palma ratio (top 10%/ bottom 40%)") + geom_point()+ geom_hline(yintercept = 0) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))
+
+p3.pred <- plot_predictions(int_palma, condition = list("homclass",palmaratio=range),gray = F) +
+    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)),
+       linetype='Palma Ratio',fill='Palma Ratio',color='Palma Ratio') +
+  xlab("Class-based homogeneity")+
+  ylab("Egalitarian economic preferences") +
+  theme(legend.position = "right")
+
+p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="top10") +
+  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))
+
+# plot_predictions(int_pc10, condition = list("homclass",top10=range),gray = F)
+
+p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="middle50") +
+  xlab("Share National Income - middle 50%") + geom_point()+ geom_hline(yintercept = 0) +
+  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))
+
+# plot_predictions(int_pc50, condition = list("homclass",middle50=range),gray = F)
+
+p6<- interplot::interplot(m = int_d10d1,var1 = "homclass",var2="d10d1") +
+  xlab("Ratio (Top 10%/Bottom 10%)") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_d10d1),", Countries=",lme4::ngrps(int_d10d1)))
+
+p6.pred<- plot_predictions(int_d10d1, condition = list("homclass",d10d1=range),gray = F) +
+      labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)),
+       linetype='Ratio D10/D01',fill='Ratio D10/D01',color='Ratio D10/D01') +
+  xlab("Class-based homogeneity")+
+  ylab("Egalitarian economic preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p3,p3.pred,p6,p6.pred,nrow = 2)
+```
+
 \pagebreak
@@
                         gini_mkt,
-                        giniot=gini,palmaratio,d10d1,
                         rgdpna,
@@
 
-# lineal
+# Models for Redistributive Preferences ----------------------------------------
 base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (strong) and social class" 
+# Models for Egalitarian Economic Preferences (EEP)-----------------------------
+dfreg <- df1 %>% dplyr::select(redist=egal3,
+                        class3,
+                        homclass=homclass_s,
+                        # homclass=eindex_s,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  na.omit()
+
+base_e<- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base_e)
+class_e <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass_e <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1_e <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1_e <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2_e <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3_e <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# rob4 <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# anova(rob3,rob4)
+# Interactions segregation x class
+int_homo_e <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+
+cap1 <- "Multilevel regression Redistribution and Egalitarian Preferences, network homogeneity (strong) and social class" 
 coefmap <-  list(homclass ="Class-based network homogeneity (Strong)",
@@
 
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,scalebox = 1,
+models <- list(homclass,full1,rob3,int_homo,homclass_e,full1_e,rob3_e,int_homo_e)
+texreg::knitreg(models,caption=paste("(\\#tab:modstrongties)",cap1),caption.above=T,scalebox = 0.5,
                                 float.pos="h!",
@@
                   groups = coefgroup,
-                  custom.gof.rows=gofrow,
+                  # custom.gof.rows=gofrow,
                   include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-```
-
-\pagebreak
+                  # custom.gof.names = gof1,
+                custom.header = list("Redistributive preferences" = 1:4, "Egalitarian preferences (Index)" = 5:8),
+                )
+```
 
@@
 rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# rob4 <- lmer(redist~class3+ homclass+logrgdpna+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# rob4 <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
 # anova(rob3,rob4)
@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity (weak) and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity (Weak)",
+# Models for Egalitarian Economic Preferences (EEP)-----------------------------
+dfreg <- df1 %>% dplyr::select(redist=egal3,
+                        class3,
+                        homclass=homclass_s,
+                        # homclass=eindex_s,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  na.omit()
+
+base_e<- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base_e)
+class_e <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass_e <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1_e <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1_e <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2_e <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3_e <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# rob4 <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(homclass|country2),data=dfreg)
+# anova(rob3,rob4)
+# Interactions segregation x class
+int_homo_e <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+
+cap1 <- "Multilevel regression Redistribution and Egalitarian Preferences, network homogeneity (weak) and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity (weak)",
                  'class3Intermediate class (III+IV)' ='Intermediate class',
@@
 
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,scalebox = 1,
+models <- list(homclass,full1,rob3,int_homo,homclass_e,full1_e,rob3_e,int_homo_e)
+texreg::knitreg(models,caption=paste("(\\#tab:weakties)",cap1),caption.above=T,scalebox = 0.5,
                                 float.pos="h!",
@@
                   groups = coefgroup,
-                  custom.gof.rows=gofrow,
+                  # custom.gof.rows=gofrow,
                   include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
+                  # custom.gof.names = gof1,
+                custom.header = list("Redistributive preferences" = 1:4, "Egalitarian preferences (Index)" = 5:8),
                 )
@@
                   custom.gof.names = gof1
-                )
-```
-
-\pagebreak
-
-## Gov's spending and individualism
-
-```{r mod-spend-indv, results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_gc,
-                        # homclass=homclass_res,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,ttheilge1,
-                        gv_spen=gv_spen,
-                        top10,
-                        middle50,
-                        palmaratio,
-                        d10d1,
-                        rgdpna,
-                        individualism,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        workst
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-    # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
-   na.omit()
-int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-models_m <- list(int_indivi,int_govspe)
-cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
-customcoef <- 
-list(homclass = "Class-based network homogeneity",
-  logrgdpna           = "log GDP",
-  individualism         = "Individualism Index*",
-  "homclass:individualism" = "Homogeneity x Individualism",
-  gv_spen               = "Gov. Spending (% GDP)*",
-  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
-)
-texreg::knitreg(models_m,scalebox = 1,
-                float.pos="h!",                
-                custom.coef.map = customcoef,
-                caption.above = T,caption = cap1)
-```
-
-```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
-p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
-  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
-
-predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-       linetype='Individualism') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
-  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
-
-predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
-       linetype='Gov.Spend') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-grid.arrange(p9,predval9,
-             p8,predval8,nrow = 2)
-```
-
-\pagebreak
-
-## Perceived Isolation
-
-```{r mod-isolation,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        isolation,
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears, 
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        workst
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(full1,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Isolation x Social Class"=9:10
-                  )
-
-coefmap <-  list(isolation ="Perceived Isolation",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
-                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
-                 # know_total="Number contacts"
-                 # outgroup="Number outgroup"
-                 homclass ="Class-based network homogeneity"
-                 )
-
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
-```
-
-```{r leverage2, eval=FALSE, include=FALSE}
-pacman::p_load(influence.ME,lattice)
-# dfbetas-----------------------------------------------------------------------
-influence <- influence(rob3, "country2")
-dfbetas(influence,parameters=c(1,4)) 
-n_groups <- lme4::ngrps(rob3)
-
-influence_est=as.data.frame(dfbetas(influence))
-influence_est %>%  filter(homclass > 2/sqrt(n_groups))
-
-plot(influence, which="dfbetas", 
-     parameters=c("isolation"),
-     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
-
-# cook-distance-----------------------------------------------------------------
-# cooks.distance(rob3, sort = TRUE)
-plot(influence, which="cook",
-     cutoff=4/n_groups, sort=TRUE,
-     xlab="Cooks Distance",
-     ylab="Country")
-
-sigtest1<- sigtest(influence, test=-1.96)
-sigtest1$homclass
-```
-
-```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() + 
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Perceived Isolation")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
-# Predicted values 
-plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
-    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(legend.position = "none")+ 
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences")
-```
-
-```{r mod-intermacro2,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass,
-                        isolation,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        workst) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# T03dim(dfreg)
-
-main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# summary(giniD_int)
-
-giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
-                caption.above=T,
-                  # include.thresholds=FALSE,
-                  custom.coef.map=list(isolation="Perceived Isolation",
-                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "isolation:gini_disp"="Isolation x Gini (D)",
-                                       "gini_mkt"="Gini (Market) ",
-                                       "isolation:gini_mkt"="Isolation x Gini (M)",
-                                       homclas="Class-based homogeneity"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-```
-
-```{r crosslevel2}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
-p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-predval1 <- 
-plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       linetype='Gini (Disposable)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-# Predicted values 
-predval2 <- 
-plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
-  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       linetype='Gini (Market)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-```
-
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
-grid.arrange(p1,predval1,nrow = 1    
-             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
-             )
-```
-
-```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
-grid.arrange(p2,predval2,nrow = 1    
-             # top = "Perceived Isolation × Gini (Market)"  
                 )

### 2023-10-11 procesamiento/prod_analysis-models.Rmd
meeting patrick

@@
 
-# Models perceived isolation
-
-```{r class-pinsolation}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled)
+## Perceived Isolation
+
+```{r mod-isolation,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
 rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(redist,
-                        class6,class3,class5,
-                        # tr_inte,
-                        # eindex,
-                        # know_total,
+                        class3,class5,
                         homclass,
-                        homclass_gc,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
+                        isolation,
                         Q05pcm,
-                        labst,
-                        union,
-                        # sstatus,
+                        Q03pcm,
+                        # isei08,
                         gini_disp,
                         gini_mkt,
-                        # palmawd,
+                        giniot=gini,
                         rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,female,agenum,country) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>% 
-  # filter(country!=233) %>% 
+                        edyears, 
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
   na.omit()
-dim(dfreg)
-
-dfreg$country <- sjlabelled::as_factor(dfreg$country)
-base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass + (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
-full_b <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
-full_m_rs <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1+pi_nteg|country),data=dfreg)
-
-plot_model(full_m_rs,type = "re")
-anova(full_m,full_m_rs)
-
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
 # Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + pi_nteg*class3+ ednum + Q05pcm + (1|country),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_b,full_int1)
-texreg::knitreg(models)
-
+int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Isolation x Social Class"=9:10
+                  )
+
+coefmap <-  list(isolation ="Perceived Isolation",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
+                 # know_total="Number contacts"
+                 # outgroup="Number outgroup"
+                 homclass ="Class-based network homogeneity"
+                 )
+
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+```
+
+```{r leverage2, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c("isolation"),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
 # Conditional Marginal effect
 interplot <- 
-interplot::interplot(m = full_int1,var1 = "pi_nteg",var2="class3")
+interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
 df_int <- interplot$data
 df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
 df_int$value <- factor(df_int$value,ordered = T,
@@
   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  ylab("Perceived Isolation coefficient")+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Perceived Isolation")+
   xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
+  ggtitle("Redistributive preferences") +
   geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
   theme(plot.title = element_text(size = 8))  
-
-ggsave(plot = last_plot(),filename = "mar_pisolation_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
 # Predicted values 
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
+plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(legend.position = "none")+ 
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences")
+```
+
+```{r mod-intermacro2,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        isolation,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(isolation="Perceived Isolation",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "isolation:gini_mkt"="Isolation x Gini (M)",
+                                       homclas="Class-based homogeneity"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel2}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
+  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
+  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       linetype='Gini (Disposable)') +
   xlab("Perceived Isolation")+
   ylab("Redistributive preferences") +
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_pisolation_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# isolation <- 
-# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-# df_int2 <- isolation$data
-# df_int2 <- df_int2[c(1,2,4),]
-# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-# df_int2
-# df_int2$value <- factor(df_int2$value,ordered = T,
-#                         levels = c("Working Class (V+VI+VII)",
-#                                    "Intermediate class (III+IV)",
-#                                    "Service Class (I+II)"))
-# 
-# df_int2 %>% 
-# ggplot() +
-#   geom_point(aes(x = value,y = coef1)) + 
-#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-#   ylab("Perceived isolation coefficient")+
-#   xlab("Social Class")+
-#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-#   geom_hline(yintercept = 0)
-# 
-# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-```
-
-```{r pinsolation-macro}
-# Interactions segregation x inequality
-df1$pi_isola_gc <- MLMusingR::group_center(df1$pi_isola,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-df1$ratio10_50 <- df1$pc10_2017/df1$pc50_2017
-
-df1$homclass
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-int_giniot<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
-
-# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090,int_giniot)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "pi_isola_gc",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "pi_isola_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_mkt)
-
-df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_disp)
-
-p3<- interplot::interplot(m = int_palma,var1 = "pi_isola_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-
-p4<- interplot::interplot(m = int_pc10,var1 = "pi_isola_gc",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)
-
-p5<- interplot::interplot(m = int_pc50,var1 = "pi_isola_gc",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)
-
-p6<- interplot::interplot(m = int_r1090,var1 = "pi_isola_gc",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)
-
-p7<- interplot::interplot(m = int_giniot,var1 = "pi_isola_gc",var2="gini") +
-  xlab("Gini (WD)") + geom_point()+ geom_hline(yintercept = 0)
-
-grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
-g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Perceived Isolation × Inequality")
-
-ggsave(plot = g,filename = "mar_pisolation_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       linetype='Gini (Market)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
+grid.arrange(p1,predval1,nrow = 1    
+             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
+             )
+```
+
+```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
+grid.arrange(p2,predval2,nrow = 1    
+             # top = "Perceived Isolation × Gini (Market)"  
+             )
 ```
@@
 ```
+
+## Gov's spending and individualism
+
+```{r mod-spend-indv, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        giniindex,ttheilge1,
+                        gv_spen=gv_spen,
+                        top10,
+                        middle50,
+                        palmaratio,
+                        d10d1,
+                        rgdpna,
+                        individualism,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>%
+   na.omit()
+int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+models_m <- list(int_indivi,int_govspe)
+cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  individualism         = "Individualism Index*",
+  "homclass:individualism" = "Homogeneity x Individualism",
+  gv_spen               = "Gov. Spending (% GDP)*",
+  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
+)
+texreg::knitreg(models_m,scalebox = 1,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+```
+
+```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
+p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
+  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+
+predval8 <- 
+plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
+       linetype='Individualism') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
+  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+
+predval9 <- 
+plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
+  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
+       linetype='Gov.Spend') +
+  xlab("Class-based homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+grid.arrange(p9,predval9,
+             p8,predval8,nrow = 2)
+```

### 2023-10-17 procesamiento/prod_analysis-robust.Rmd
meeting patrick

--- 2023-09-21 procesamiento/prod_analysis-robust.Rmd
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
 df1$redistF <- as.factor(df1$redist)
-
 dfreg <- df1 %>% dplyr::select(redist=redistF,
                         class3,
+                        class5,
                         homclass,
-                        Q05pcm,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=zincpc,
+                        # Q03rm=
+                        # isei08,
                         rgdpna,
@@
 full1 <- clmm(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-# rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-# rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+(1|country2),data=dfreg)
+rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+anova(rob3,rob4)
+rob1 <- clmm(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- clmm(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+anova(rob3,rob4)
 # Interactions segregation x class
-int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(int_homo,single.row = F)
+int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+int_homo <- clmm(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
 
@@
 coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Service Class (I+II)' ='Service Class',
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                  'class3Working Class (V+VI+VII)' ='Working Class',
@@
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                                float.pos="h!",
                   include.thresholds=FALSE,

### 2023-10-17 procesamiento/prod_prep.Rmd

@@
 #frq(df1$pertransfer)
+```
+
+# Index egalitarian attitudes
+```{r}
+df1 %>% select(redist,prefineq,perineq) %>% 
+  psych::cor2()
+df1 %>% select(redist,prefineq,perineq) %>% 
+  psych::alpha()
+
+df1$egal3<- rowMeans(df1[,c("redist","prefineq","perineq")],na.rm = T)
+df1$egal3 <- ((df1$egal3-min(df1$egal3,na.rm = T))/(max(df1$egal3,na.rm = T)-min(df1$egal3,na.rm = T)))*100
+
+sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
+hist.default(df1$egal3)
+
+df1$egal2<- rowMeans(df1[,c("redist","prefineq")],na.rm = T)
+df1$egal2 <- ((df1$egal2-min(df1$egal2,na.rm = T))/(max(df1$egal2,na.rm = T)-min(df1$egal2,na.rm = T)))*100
+sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
+hist.default(df1$egal2)
 ```

### 2023-10-17 paper.Rmd
AJUSTES 17 OCTUBRE

@@
                         class3, 
-                        homclass,
+                        homclass=homclass2,
                         # homclass=eindex,
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
+                        class3=dclass3,
                         class5,
-                        homclass,
+                        homclass=homclass2,
                         Q03pcm,
@@
                         # isolation,  
-                        # MAINSTAT,
+                        MAINSTAT,
                         # activities,
@@
                         "gini_disp",
-                        "gini_mkt"
+                        "gini_mkt",oecd
                         ) %>% 
@@
   # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
   na.omit()
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_gc,
+                        class3=dclass3,
+                        homclass=homclass2,
                         # homclass=eindex,
@@
                         union,
-                        workst) %>% 
+                        workst,oecd) %>% 
   mutate(logrgdpna=log(rgdpna),
@@
   # filter(agenum %in% c(25:65)) %>%
+  filter(oecd=="OECD") %>% 
   na.omit()
@@
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
-p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp")+
+p1<- interplot::interplot(m = giniD_int,var1 = "homclass",var2="gini_disp",ci = .95)+
   ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
@@
 dfreg %>% filter(gini_disp %in%)
+
+gini_sig <- 
+p1$data %>% 
+  filter(ub>0 & lb >0) %>% 
+  dplyr::select(fake)
+
+conditional1<- 
+dfreg %>% 
+  # filter(gini_disp >= min(gini_sig$fake),gini_disp <= max(gini_sig$fake)) %>% 
+  dplyr::select(country2,gini_disp) %>% 
+  group_by(country2) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  arrange(gini_disp)
 
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass=homclass_gc,
+                        class3=dclass3,
+                        homclass=homclass2,
                         # homclass=homclass_res,
@@
                         union,
-                        workst
+                        workst,
+                        oecd
                         ) %>% 
@@
   # filter(agenum %in% c(25:65)) %>%
+  # filter(oecd=="OECD") %>% 
   na.omit()
@@
 
+## Perceived Isolation
+
+```{r mod-isolation,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,class5,
+                        homclass,
+                        isolation,
+                        Q05pcm,
+                        Q03pcm,
+                        # isei08,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears, 
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        workst
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# dim(dfreg)
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+# texreg::screenreg(full1,single.row = F)
+
+cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Isolation x Social Class"=9:10
+                  )
+
+coefmap <-  list(isolation ="Perceived Isolation",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
+                 # know_total="Number contacts"
+                 # outgroup="Number outgroup"
+                 homclass ="Class-based network homogeneity"
+                 )
+
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+```
+
+```{r leverage2, eval=FALSE, include=FALSE}
+pacman::p_load(influence.ME,lattice)
+# dfbetas-----------------------------------------------------------------------
+influence <- influence(rob3, "country2")
+dfbetas(influence,parameters=c(1,4)) 
+n_groups <- lme4::ngrps(rob3)
+
+influence_est=as.data.frame(dfbetas(influence))
+influence_est %>%  filter(homclass > 2/sqrt(n_groups))
+
+plot(influence, which="dfbetas", 
+     parameters=c("isolation"),
+     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
+
+# cook-distance-----------------------------------------------------------------
+# cooks.distance(rob3, sort = TRUE)
+plot(influence, which="cook",
+     cutoff=4/n_groups, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+
+sigtest1<- sigtest(influence, test=-1.96)
+sigtest1$homclass
+```
+
+```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() + 
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Perceived Isolation")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
+# Predicted values 
+plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(legend.position = "none")+ 
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences")
+```
+
+```{r mod-intermacro2,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
+df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        isolation,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        workst) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
+                caption.above=T,
+                  # include.thresholds=FALSE,
+                  custom.coef.map=list(isolation="Perceived Isolation",
+                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                       "gini_mkt"="Gini (Market) ",
+                                       "isolation:gini_mkt"="Isolation x Gini (M)",
+                                       homclas="Class-based homogeneity"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r crosslevel2}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
+p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
+  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
+  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
+  geom_point()+ geom_hline(yintercept = 0)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       linetype='Gini (Disposable)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+# Predicted values 
+predval2 <- 
+plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       linetype='Gini (Market)') +
+  xlab("Perceived Isolation")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+```
+
+```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
+grid.arrange(p1,predval1,nrow = 1    
+             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
+             )
+```
+
+```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
+grid.arrange(p2,predval2,nrow = 1    
+             # top = "Perceived Isolation × Gini (Market)"  
+             )
+```
+
+\pagebreak
+
 # References

### 2023-10-17 procesamiento/prod_analysis-robust.Rmd
AJUSTES 17 OCTUBRE

@@
       - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
+editor_options: 
+  chunk_output_type: console
 ---
@@
 dfreg <- df1 %>% dplyr::select(redist=redistF,
-                        class3,
-                        class5,
-                        homclass,
+                        class3=dclass3,
+                        # class5,
+                        homclass=homclass2,
                         Q03pcm,
@@
                         "gini_disp",
-                        "gini_mkt"
+                        "gini_mkt",
                         ) %>% 
@@
 
-avg_slopes(
-  int_homo,
-  by = "class3",
-  variables = "homclass")
 ```
@@
 ```
+
+# OCDE countries
+
+```{r mod-homclass,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+                        redist,
+                        class3,
+                        class5,
+                        homclass,
+                        Q03pcm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=Q03rm,
+                        # Q03pcm=zincpc,
+                        # Q03rm=
+                        # isei08,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,country,
+                        union,
+                        # # isolation,  
+                        # # MAINSTAT,
+                        # # activities,
+                        # # WEIGHT,
+                        "gini_disp",
+                        "gini_mkt",
+                        oecd,
+                        MAINSTAT,
+                        WORK
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2,3,4) & WORK %in% c(1,2) ) %>%
+  filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  filter(oecd=="OECD") %>%
+  dplyr::select(-MAINSTAT,-WORK) %>%
+  na.omit()
+
+# lineal
+base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
+class <- lmer(redist~ class3+ (1|country2),data=dfreg)
+homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
+full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
+rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
+rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
+rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ union+ female+agenum +age2 +  (1|country2),data=dfreg)
+rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ union+ female+agenum +age2 + (homclass|country2),data=dfreg)
+anova(rob3,rob4)
+
+# plot_model(rob4,type = "re",show.values = T)
+
+# Interactions segregation x class
+int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ union+ female+agenum +age2+ (1|country2),data=dfreg)
+# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
+# anova(int_homo,int_homo2)
+# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
+
+# models <- list(homclass,class,full1,
+#                # rob1,rob2,
+#                rob4)
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                  # "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
+                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,class,full1,rob3,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  # groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r coefplot,eval=FALSE, include=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,dotwhisker,ggplot2,broom.mixed)
+
+m1_df <-
+    broom.mixed::tidy(rob3) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                    "class3Working Class (V+VI+VII)",
+                                                    "homclass")) %>% mutate(model = "Model 1")
+m2_df <-
+    broom.mixed::tidy(int_homo) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+                                                        "class3Working Class (V+VI+VII)",
+                                                        "homclass",
+                                                        "class3Intermediate class (III+IV):homclass",
+                                                        "class3Working Class (V+VI+VII):homclass")) %>% mutate(model = "Model 2")
+
+two_models <- rbind(m1_df)
+
+  dwplot(two_models,
+       vline = geom_vline(xintercept = 0,colour = "black",linetype = 1,size=0.01),
+       style = "dotwhisker",
+       dot_args =  list(size=5),
+       whisker_args = list(size=2),
+       vars_order = c("homclass",
+                      "class3Intermediate class (III+IV)",
+          "class3Working Class (V+VI+VII)",
+          "class3Intermediate class (III+IV):homclass",
+          "class3Working Class (V+VI+VII):homclass")) %>%
+
+     relabel_predictors(
+        c("homclass"="Class based network homogeneity",
+          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
+          "class3Working Class (V+VI+VII)"="Working Class",
+          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
+          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
+      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(
+        plot.title = element_text(face = "bold"),
+        legend.position = c(0.007, 0.01),
+        legend.justification = c(0, 0),
+        legend.background = element_rect(colour = "grey80"),
+        legend.title = element_blank(),
+        axis.text.y.left = element_text(face = "bold",size = 12)
+  )
+```
+
+```{r marg1,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Network homogeneity on redistributive preferences"),out.width = "75%"}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)   
+# Conditional Marginal effect
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Class-based homogeneity")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
+  theme(plot.title = element_text(size = 8))  
+```
+
+```{r pred1,fig.height=3.6,fig.width=5.7,fig.cap=c("Conditional linear Predictions for network homogeneity on redistributive Preferences"),out.width = '75%'}
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra,papaja)      
+# Predicted values 
+plot_predictions(int_homo, condition = c("homclass","class3")) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+  # scale_fill_grey(start = 0.40, end = 0.6) +
+  # scale_color_grey(start = 0.40, end = 0.6)
+```
+
+```{r mod-intermacro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=eindex,
+                        # homclass=ingroup,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        rgdpna,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        oecd,
+                        MAINSTAT, WORK
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2,3,4) & WORK %in% c(1,2)) %>%
+  filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+  filter(oecd=="OECD") %>%
+  na.omit()
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ union+ female+agenum +age2"
+
+giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
+giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+anova(giniD_gdp,giniD_rs)
+giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+# summary(giniD_int)
+
+giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
+giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+anova(giniM_gdp,giniM_rs)
+giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                # include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_gc,
+                        # homclass=homclass_res,
+                        Q05pcm,
+                        Q03pcm,
+                        gini_disp,
+                        gini_mkt,
+                        giniot=gini,
+                        giniindex,ttheilge1,
+                        gv_spen=gv_spen,
+                        top10,
+                        middle50,
+                        palmaratio,
+                        d10d1,
+                        rgdpna,
+                        individualism,
+                        edyears,
+                        female,
+                        agenum,
+                        country2,
+                        union,
+                        MAINSTAT,WORK,
+                        oecd
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         age2=agenum^2,
+         edyears2=edyears^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(MAINSTAT %in% c(1,2,3,4) & WORK %in% c(1,2) ) %>%
+  filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(region %in% c("Northern America","South America")) %>%
+   filter(oecd=="OECD") %>%
+   # dplyr::select(-MAINSTAT,-WORK) %>%
+   na.omit()
+
+int_palma <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
+int_pc10  <- lmer(redist~class3+ homclass*top10+edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_pc50  <- lmer(redist~class3+homclass*middle50+ edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_d10d1<- lmer(redist~class3+ homclass*d10d1+ edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_gini_wiid  <- lmer(redist~class3+ homclass*giniindex+ edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+int_theil  <- lmer(redist~class3+ homclass*ttheilge1+ edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+
+int_gvspen  <- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+  union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,int_gvspen
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  palmaratio               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
+  individualism         = "Individualism Index*",
+  "homclass:individualism" = "Homogeneity x Individualism",
+  gv_spen               = "Gov. Spending (% GDP)*",
+  "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+    d10d1             = "Ratio D10/D01",
+  "homclass:d10d1"    = "Homogeneity x Ratio D10/D01"  
+)
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",
+                # custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+```
+
+```{r}
+interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
+  ylab("Class-based homogeneity coefficient")+ geom_hline(yintercept = 0)
+
+interplot::interplot(m = int_d10d1,var1 = "homclass",var2="d10d1") +
+  ylab("Class-based homogeneity coefficient")+ geom_hline(yintercept = 0)
+
+interplot::interplot(m = int_gini_wiid,var1 = "homclass",var2="giniindex") +
+  ylab("Class-based homogeneity coefficient")+ geom_hline(yintercept = 0)
+
+interplot::interplot(m = int_theil,var1 = "homclass",var2="ttheilge1") +
+  ylab("Class-based homogeneity coefficient")+ geom_hline(yintercept = 0)
+
+interplot::interplot(m = int_gvspen,var1 = "homclass",var2="gv_spen") +
+  ylab("Class-based homogeneity coefficient")+ geom_hline(yintercept = 0)
+
+```

### 2023-10-17 procesamiento/prod_prep-macro.Rmd
AJUSTES 17 OCTUBRE

@@
 
+*OCDE data*
+```{r ocde}
+ocde<- 
+  read.csv(file = here::here("input/data/original/ocde-countries.csv"),sep = ",")
+
+ocde$ccode <- countrycode::countrycode(sourcevar = ocde$iso3n,origin = "iso3c",destination = "iso3n")
+ocde <- ocde[,c("ccode","oecd")]
+```
+
 ```{r merge}
@@
   left_join(pen_2017) %>% 
-  left_join(otero)
-
+  left_join(otero) %>%
+  left_join(ocde) 
 df1$ccode <- as.numeric(df1$country)

### 2023-10-17 procesamiento/prod_prep.Rmd
AJUSTES 17 OCTUBRE

--- 2023-10-09 procesamiento/prod_prep.Rmd
@@
 
-relig <- haven::read_dta(here::here("input/data/original/ZA7570_v2-1-0.dta"))
-religTR <- relig %>% filter(country==792)
+# relig <- haven::read_dta(here::here("input/data/original/ZA7570_v2-1-0.dta"))
+# religTR <- relig %>% filter(country==792)
 
@@
                         WORK=work,
-                        HOMPOP=hompop)  
+                        HOMPOP=hompop,
+                        EMPREL=emprel,
+                        NSUP=nsup,
+                        WRKSUP=wrksup,
+                        SPEMPREL=spemprel,
+                        SPWRKSUP=spwrksup)  
 dfES$c_alphan <- NULL
@@
 #frq(df1$pertransfer)
+```
+
+# Index egalitarian attitudes
+```{r}
+df1 %>% select(redist,prefineq,perineq) %>% 
+  psych::cor2()
+df1 %>% select(redist,prefineq,perineq) %>% 
+  psych::alpha()
+
+df1$egal3<- rowMeans(df1[,c("redist","prefineq","perineq")],na.rm = T)
+df1$egal3 <- ((df1$egal3-min(df1$egal3,na.rm = T))/(max(df1$egal3,na.rm = T)-min(df1$egal3,na.rm = T)))*100
+
+sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
+# hist.default(df1$egal3)
+
+df1$egal2<- rowMeans(df1[,c("redist","prefineq")],na.rm = T)
+df1$egal2 <- ((df1$egal2-min(df1$egal2,na.rm = T))/(max(df1$egal2,na.rm = T)-min(df1$egal2,na.rm = T)))*100
+sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
+# hist.default(df1$egal2)
 ```
@@
 #Employment relation encuestado
-#frq(df1$EMPREL)
-#frq(df1$WORK)
+frq(df1$EMPREL)
+# frq(df1$WORK)
 df1$semp <- df1$EMPREL
 df1$semp <- as.numeric(car::recode(df1$semp, "c(2,3,4)=1;c(1)=2;c(0,8,9)=NA"))
-#frq(df1$semp)
+frq(df1$semp)
 df1$semp <- sjlabelled::set_labels(x = df1$semp,labels=c('Self-employed','Employee'))
@@
 # superivison
-#frq(df1$NEMPLOY) #supervision respondent
+frq(df1$NEMPLOY) #supervision respondent
+frq(df1$NSUP)
 df1$supvis <- as.numeric(car::recode(df1$NEMPLOY,"c(9998,9999)=NA"))
-#frq(df1$supvis)
+
+frq(df1$supvis)
+
 # save the occupational variables for using them in stata-----------------------
@@
 df1 <- tibble::rowid_to_column(df1, "id")
+
+# For comparing with the DIGCLASS
+
+frq(df1$WRKSUP)
+frq(df1$EMPREL)
+frq(df1$NSUP)
+
+df1 <-
+  df1 %>%
+  mutate(
+    is_supervisor = ifelse(WRKSUP == 2, 0, as.numeric(car::recode(df1$WRKSUP,"c(8,9)=NA"))),
+    self_employed = case_when(
+      EMPREL %in% c(1,4) ~ 0,
+      EMPREL %in% 2:3 ~ 1
+    ),
+    n_employees = ifelse(is_supervisor == 0, 0, as.numeric(car::recode(df1$NSUP,"c(9998,9999)=NA")))
+  )
+
+frq(df1$is_supervisor)
+frq(df1$self_employed)
+frq(df1$n_employees)
+
+frq(df1$SPWORK)
+frq(df1$SPEMPREL)
+
+df1$NSUPSPO <- 1
+frq(df1$NSUPSPO)
+
+df1 <-
+  df1 %>%
+  mutate(
+    is_supervisor_spo = ifelse(SPWORK == 2, 0, as.numeric(car::recode(df1$SPWORK,"c(8,9)=NA"))),
+    self_employed_spo = case_when(
+      SPEMPREL %in% c(1,4) ~ 0,
+      SPEMPREL %in% 2:3 ~ 1
+    ),
+    n_employees_spo = ifelse(is_supervisor_spo == 0, 0, as.numeric(car::recode(df1$NSUPSPO,"c(9998,9999)=NA")))
+  )
+
+frq(df1$is_supervisor_spo)
+frq(df1$self_employed_spo)
+frq(df1$n_employees_spo)
+
+df1 %>% select(isco88r, is_supervisor, self_employed,"semp", n_employees,"supvis")
 haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
-                              "isco88spo","sempspo","supvisspo")],
+                              "is_supervisor","self_employed","n_employees",
+                              "isco88spo","sempspo","supvisspo",
+                              "is_supervisor_spo","self_employed_spo","n_employees_spo")],
                  path = here::here("input/data/proc/ocup_respondent-spouse.dta"))
@@
 
-```{r class-stata}
+```{r class-from-stata}
 # Load the data created in stata------------------------------------------------
@@
 # Class R´s and Spouse----------------------------------------------------------
-df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$class10 <- sjlabelled::set_labels(df1$class10, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-sjlabelled::set_label(df1$class10) <- "Social Class - respondent"
-
-#frq(df1$class10)
-
-df1$class10spo <- car::recode(df1$class10spo, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$class10spo <- sjlabelled::set_labels(df1$class10spo, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-sjlabelled::set_label(df1$class10spo) <- "Social Class - spouse"
-
-#frq(df1$class10spo)
-
-#if NA in class of respondent, replace with household
-
-#frq(df1$class10)
-#frq(df1$class10spo)
-
-df1$class11 <- ifelse(is.na(df1$class10),df1$class10spo,df1$class10)
-#frq(df1$class11)
+frq(df1$class10)
+
+# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$class10f <- as_factor(df1$class10)
+frq(df1$class10f)
+
+df1$class10f <- factor(df1$class10f,
+                       levels = c("higher controllers","lo controllers",
+                                 "routine nonmanual",
+                                 "sempl with emp","sempl without empl","selfempl farm",
+                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
+                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+df1$class10f <- as_labelled(df1$class10f)
+sjlabelled::set_label(df1$class10f) <- "Social Class - respondent"
+frq(df1$class10f)
+
+df1$class10spof <- as_factor(df1$class10spo)
+frq(df1$class10spof)
+
+df1$class10spof <-factor(df1$class10spof,
+                       levels = c("higher controllers","lo controllers",
+                                 "routine nonmanual",
+                                 "sempl with emp","sempl without empl","selfempl farm",
+                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
+                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+df1$class10spof <- as_labelled(df1$class10spof)
+sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse"
+
+frq(df1$class10spof)
+#if NA in class of respondent, replace with spouse
+
+frq(df1$class10f)
+frq(df1$class10spof)
+
+df1$class11 <- ifelse(is.na(df1$class10f),df1$class10spof,df1$class10f)
+frq(df1$class11)
 
 # if NA in respondents it is assumed to be lower than spouse
-# know, with the cases in we have information for respondent and spouse
+# now, with the cases in we have information for respondent and spouse
 # we replace the value by the highest one, just for those
@@
 df1$class11d <- pmax(df1$class11, #social class respondent + spouse vs:
-                       df1$class10spo,#social class spouse
+                     df1$class10spof,#social class spouse
                      na.rm = T) # if NA, do nothing
-
+frq(df1$class11d)
 df1$class11d <- 
   sjlabelled::set_labels(df1$class11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                         labels =  c("I", "II", "IIIa", "IIIb", "IVa", "IVb", 
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
+                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
                                      "IVc", "V", "VI", "VIIa", "VIIb")) 
-#frq(df1$class11d)
+frq(df1$class11d)
 sjlabelled::set_label(df1$class11d) <- "Social Class"
@@
 sjlabelled::set_label(df1$class3) <- "Social Class"
-#frq(df1$class3)
+frq(df1$class3)
 
@@
 sjlabelled::set_label(df1$class6spo) <- "Social Class (Spouse)"
+```
+
+```{r class-from-stata2}
+# Load the data created in stata------------------------------------------------
+# Class R´s and Spouse----------------------------------------------------------
+df1$digclass10 <- car::recode(df1$digclass10, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$digclass10 <- sjlabelled::set_labels(df1$digclass10, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$digclass10) <- "Social Class - respondent"
+
+#frq(df1$class10)
+
+df1$digclass10spo <- car::recode(df1$digclass10spo, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$digclass10spo <- sjlabelled::set_labels(df1$digclass10spo, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+sjlabelled::set_label(df1$digclass10spo) <- "Social Class - spouse"
+
+#frq(df1$class10spo)
+
+#if NA in class of respondent, replace with spouse
+
+#frq(df1$class10)
+#frq(df1$class10spo)
+
+df1$digclass11 <- ifelse(is.na(df1$digclass10),df1$digclass10spo,df1$digclass10)
+#frq(df1$class11)
+
+# if NA in respondents it is assumed to be lower than spouse
+# now, with the cases in we have information for respondent and spouse
+# we replace the value by the highest one, just for those
+
+# Replace the highest class by dominance criteria 
+# Keep the highest of two values:
+df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
+                       df1$digclass10spo,#social class spouse
+                       na.rm = T) # if NA, do nothing
+
+df1$digclass11d <- 
+  sjlabelled::set_labels(df1$digclass11d,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
+                         labels =  c("I", "II", "IIIa", "IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
+frq(df1$digclass11d)
+sjlabelled::set_label(df1$digclass11d) <- "Social Class"
+
+# Class Scheme 3 classes
+df1$digclass3 <- car::recode(df1$digclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3) <- "Social Class"
+frq(df1$digclass3)
+
+# Class Scheme 5 classes
+df1$digclass5 <- car::recode(
+  df1$digclass11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$digclass5) <- "Social Class"
+frq(df1$digclass5)
+# Class Scheme 6 classes
+df1$digclass6 <- car::recode(
+  df1$digclass11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+# Class only R's --------------------------------------------------------------
+df1$digclass10
+
+# Class Scheme 3 classes
+df1$digclass3res <- car::recode(as.numeric(df1$digclass10),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3res) <- "Social Class (R's)"
+# frq(df1$class3res)
+
+# Class Scheme 5 classes
+df1$digclass5res <- car::recode(
+  as.numeric(df1$digclass10),
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$digclass5res) <- "Social Class (R's)"
+# frq(df1$class5res)
+
+# Class Scheme 6 classes
+df1$digclass6res <- car::recode(
+  as.numeric(df1$digclass10),
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$digclass6res) <- "Social Class (R's)"
+frq(df1$digclass6res)
+# Class only Spouse --------------------------------------------------------------
+df1$digclass10spo
+
+# Class Scheme 3 classes
+df1$digclass3spo <- car::recode(as.numeric(df1$digclass10spo),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3spo) <- "Social Class (Spouse)"
+frq(df1$digclass3spo)
+
+# Class Scheme 5 classes
+df1$digclass5spo <- car::recode(
+  as.numeric(df1$digclass10spo),
+  as.factor = T,
+  levels = c(
+    'Service class (I+II)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1:2='Service class (I+II)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$digclass5spo) <- "Social Class (Spouse)"
+# frq(df1$class5res)
+
+# Class Scheme 6 classes
+df1$digclass6spo <- car::recode(
+  as.numeric(df1$digclass10spo),
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+sjlabelled::set_label(df1$digclass6spo) <- "Social Class (Spouse)"
+```
+
+# Class using R
+
+```{r digclass}
+# install.packages("devtools")
+# devtools::install_git("https://code.europa.eu/digclass/digclass.git")
+library("DIGCLASS")
+library(dplyr)
+
+df1 <- 
+df1 %>% 
+mutate(egp11 = isco88_to_egp(isco88r, self_employed, n_employees, label = F,to_factor = T),
+       egp11spo = isco88_to_egp(isco88spo, self_employed_spo, n_employees_spo, label = F,to_factor = T))
+
+frq(df1$egp11)
+df1$egp11 <- as_numeric(df1$egp11)
+frq(df1$egp11)
+
+frq(df1$egp11spo)
+df1$egp11spo <- as_numeric(df1$egp11spo)
+frq(df1$egp11spo)
+
+#if NA in class of respondent, replace with spouse
+df1$dclass11 <- ifelse(is.na(df1$egp11),df1$egp11spo,df1$egp11)
+
+# if NA in respondents it is assumed to be lower than spouse
+# now, with the cases in we have information for respondent and spouse
+# we replace the value by the highest one, just for those
+
+# Replace the highest class by dominance criteria 
+# Keep the highest of two values:
+df1$dclass11d <- pmax(df1$egp11, #social class respondent + spouse vs:
+                     df1$egp11spo,#social class spouse
+                     na.rm = T) # if NA, do nothing
+frq(df1$dclass11d)
+df1$dclass11d <- as_numeric(df1$dclass11d)
+frq(df1$dclass11d)
+
+df1$dclass11d <- 
+  sjlabelled::set_labels(df1$dclass11d,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
+                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
+frq(df1$dclass11d)
+sjlabelled::set_label(df1$dclass11d) <- "Social Class"
+
+# Class Scheme 3 classes
+df1$dclass3 <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3) <- "Social Class"
+frq(df1$dclass3)
+frq(df1$class3)
 ```
@@
 
-```{r social-capital}
+```{r social-capital-measures}
 # Social capital measures
@@
 
-```{r heterogeneity}
+```{r heterogeneity, eval=FALSE, include=FALSE}
 isei_ocupnames<- names(select(df1,busdriver:teacher))
@@
 
-```{r homogeneity}
+```{r homogeneity-v01}
 # EI homophily index
@@
 
-```{r homogeneity-strong}
+```{r homogeneity-strong-v01}
 # EI homophily index
@@
 
-```{r homogeneity-weak}
+```{r homogeneity-weak-v01}
 # EI homophily index
@@
 
-```{r social distance}
+```{r homogeneity-resp-v01}
+# EI homophily index
+df1$ingroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+# frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+# frq(df1$outgroup_res)
+
+df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
+sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
+# frq(df1$eindex)
+# hist.default(df1$eindex)
+
+df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
+df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r homogeneity-v02}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(class3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
+#frq(df1$eindex)
+hist.default(df1$eindex)
+df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
+hist.default(df1$eindex_gc)
+
+df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass2) <- "Class homogeneity"
+df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
+# View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+(i)  the highest status job accessed (upper reachability),
+(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
+(iii) the total number of occupations accessed (network extensity),
+(iv) the total accessed prestige (resource volume),
+(v) the average status of jobs accessed (network prestige),
+(vi) the total number of higher-status positions accessed,
+(vii) the total number of medium-status positions accessed,
+(viii) the total number of lower-status positions accessed.
+
+```{r pca, eval=FALSE, include=FALSE}
+library(psych)
+library(dplyr)
+isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
+
+# Calculate the standard deviation for each column
+df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
+
+# Print the standard deviation for each column
+# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
+
+# reduce dimensions in 2: diversity and prestige
+df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
+summary(df_cs)
+dim(df_cs)
+
+# df_cs <- na.omit(df_cs)
+cor<- corr.test(df_cs)
+psych::KMO(r = cor$r)
+cortest.bartlett(cor$r,n = dim(df_cs)[1])
+plot(scree(df_cs,factors = 2))
+
+# Porcentaje de varianza explicada
+fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
+fit1$loadings
+plot(fit1,labels = c(names(df_cs)))
+cor(fit1$scores)
+
+fit2<- psych::fa(df_cs,nfactors = 2)
+plot(fit2,labels = c(names(df_cs)))
+fit2$scores
+cor(fit2$scores)
+fs<- as.data.frame(fit2$scores)
+names(fs) <- c("diversity","prestige")
+
+df1 <- bind_cols(df1,fs)
+sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
+sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
+```
+
+```{r social distance, eval=FALSE, include=FALSE}
 df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
@@
 
-```{r homogeneity-resp}
-# EI homophily index
-df1$ingroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
-# frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
-# frq(df1$outgroup_res)
-
-df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
-sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
-# frq(df1$eindex)
-# hist.default(df1$eindex)
-
-df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
-df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-
-# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
-An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
-Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
-```
-
-(i)  the highest status job accessed (upper reachability),
-(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
-(iii) the total number of occupations accessed (network extensity),
-(iv) the total accessed prestige (resource volume),
-(v) the average status of jobs accessed (network prestige),
-(vi) the total number of higher-status positions accessed,
-(vii) the total number of medium-status positions accessed,
-(viii) the total number of lower-status positions accessed.
-
-```{r pca}
-library(psych)
-library(dplyr)
-isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
-
-# Calculate the standard deviation for each column
-df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
-
-# Print the standard deviation for each column
-# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
-
-# reduce dimensions in 2: diversity and prestige
-df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
-summary(df_cs)
-dim(df_cs)
-
-# df_cs <- na.omit(df_cs)
-cor<- corr.test(df_cs)
-psych::KMO(r = cor$r)
-cortest.bartlett(cor$r,n = dim(df_cs)[1])
-plot(scree(df_cs,factors = 2))
-
-# Porcentaje de varianza explicada
-fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
-fit1$loadings
-plot(fit1,labels = c(names(df_cs)))
-cor(fit1$scores)
-
-fit2<- psych::fa(df_cs,nfactors = 2)
-plot(fit2,labels = c(names(df_cs)))
-fit2$scores
-cor(fit2$scores)
-fs<- as.data.frame(fit2$scores)
-names(fs) <- c("diversity","prestige")
-
-df1 <- bind_cols(df1,fs)
-sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
-sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
-```
-
 # Community participation

### 2023-10-17 paper.Rmd
lunch

@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3=dclass3,
-                        class5,
-                        homclass=homclass2,
+                        class3=digclass3,
+                        homclass,
                         Q03pcm,
-                        # Q03pcm=Q03rm,
-                        # Q03pcm=Q03rm,
-                        # Q03pcm=zincpc,
-                        # Q03rm=
-                        # isei08,
-                        rgdpna,
                         edyears,
@@
                         agenum,
-                        country2,country,
                         union,
                         workst,
-                        # isolation,  
-                        MAINSTAT,
-                        # activities,
                         # WEIGHT,
@@
                         "gini_disp",
-                        "gini_mkt",oecd
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
                         ) %>% 
@@
   # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
   # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
   # filter(!country2 %in% c("FIN")) %>%
@@
   # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
@@
   # filter(PARTLIV %in% c(0,1,2,3)) %>%
-  # filter(region %in% c("Northern America","South America")) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
   # filter(Q03pcm!="Missing") %>%
@@
   na.omit()
-
 # frq(df1$region)
@@
 # anova(rob3,rob4)
-
 # plot_model(rob4,type = "re",show.values = T)
@@
 # int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
-# anova(int_homo,int_homo2)
-# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
-
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
+
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 

### 2023-10-17 procesamiento/prod_prep.Rmd
lunch

@@
                                      "IVc", "V", "VI", "VIIa", "VIIb")) 
+sjlabelled::set_label(df1$class11d) <- "Social Class"
 frq(df1$class11d)
-sjlabelled::set_label(df1$class11d) <- "Social Class"
 
@@
 ```{r class-from-stata2}
-# Load the data created in stata------------------------------------------------
 # Class R´s and Spouse----------------------------------------------------------
-df1$digclass10 <- car::recode(df1$digclass10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$digclass10 <- sjlabelled::set_labels(df1$digclass10, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-sjlabelled::set_label(df1$digclass10) <- "Social Class - respondent"
-
-#frq(df1$class10)
-
-df1$digclass10spo <- car::recode(df1$digclass10spo, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$digclass10spo <- sjlabelled::set_labels(df1$digclass10spo, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                        labels = c("I", "II", "IIIa", "IIIb", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-sjlabelled::set_label(df1$digclass10spo) <- "Social Class - spouse"
-
-#frq(df1$class10spo)
-
+frq(df1$digclass10)
+
+# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
+df1$digclass10f <- as_factor(df1$digclass10)
+frq(df1$digclass10f)
+
+df1$digclass10f <- factor(df1$digclass10f,
+                       levels = c("higher controllers","lo controllers",
+                                 "routine nonmanual",
+                                 "sempl with emp","sempl without empl","selfempl farm",
+                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
+                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+df1$digclass10f <- as_labelled(df1$digclass10f)
+sjlabelled::set_label(df1$digclass10f) <- "Social Class - respondent"
+frq(df1$digclass10f)
+
+df1$digclass10spof <- as_factor(df1$digclass10spo)
+frq(df1$digclass10spof)
+
+df1$digclass10spof <-factor(df1$digclass10spof,
+                       levels = c("higher controllers","lo controllers",
+                                 "routine nonmanual",
+                                 "sempl with emp","sempl without empl","selfempl farm",
+                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
+                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
+
+df1$digclass10spof <- as_labelled(df1$digclass10spof)
+sjlabelled::set_label(df1$digclass10spof) <- "Social Class - spouse"
+
+frq(df1$digclass10spof)
 #if NA in class of respondent, replace with spouse
 
-#frq(df1$class10)
-#frq(df1$class10spo)
-
-df1$digclass11 <- ifelse(is.na(df1$digclass10),df1$digclass10spo,df1$digclass10)
-#frq(df1$class11)
+frq(df1$digclass10f)
+frq(df1$digclass10spof)
+
+df1$digclass11 <- ifelse(is.na(df1$digclass10f),df1$digclass10spof,df1$digclass10f)
+frq(df1$class11)
 
@@
 df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
-                       df1$digclass10spo,#social class spouse
+                     df1$digclass10spof,#social class spouse
                      na.rm = T) # if NA, do nothing
-
+frq(df1$digclass11d)
 df1$digclass11d <- 
   sjlabelled::set_labels(df1$digclass11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
-                         labels =  c("I", "II", "IIIa", "IIIb", "IVa", "IVb", 
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
+                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
                                      "IVc", "V", "VI", "VIIa", "VIIb")) 
+sjlabelled::set_label(df1$digclass11d) <- "Social Class"
 frq(df1$digclass11d)
-sjlabelled::set_label(df1$digclass11d) <- "Social Class"
 
@@
 
-```{r digclass}
+```{r digclass-egp}
 # install.packages("devtools")
@@
 frq(df1$class3)
+frq(df1$digclass3)
+```
+
+```{r oesch-class}
+df1 <- df1 %>% 
+  mutate(oesch16 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 16,to_factor = T,label=T),
+         oesch8 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 8,to_factor = T,label=T))
+
+frq(df1$oesch16)
+frq(df1$oesch8)
+
+df1 <- df1 %>% 
+  mutate(oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
+         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))
+
+frq(df1$oesch8)
+frq(df1$oesch8spo)
 ```
@@
 
+- using my original coding
 ```{r homogeneity-v01}
@@
 
+- Using my edited original coding. I recoded the variables from n_employees y self_employed. The class scheme changed a bit, where the Service class was overestimated. This should be better:
+
 ```{r homogeneity-v02}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(digclass3,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$digclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(digclass3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$digclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
+#frq(df1$eindex)
+hist.default(df1$eindex2)
+df1$eindex2_gc <- group_center(x = df1$eindex2,grp = df1$country)
+hist.default(df1$eindex2_gc)
+
+df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
+df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
+# View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+```
+
+```{r homogeneity-resp-v02}
+# EI homophily index
+df1$ingroup_res <- NA 
+df1 %>% select(ddigclass3res,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+# frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+# frq(df1$outgroup_res)
+
+df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
+sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
+# frq(df1$eindex)
+# hist.default(df1$eindex)
+
+df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
+df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+```
+
+```{r homogeneity-R-digclass}
 # EI homophily index
@@
 # df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
-df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
+df1$eindex3<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex3) <- "EI homophily index"
 #frq(df1$eindex)
@@
 df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
-df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass2) <- "Class homogeneity"
-df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
+df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
+df1$homclass3_gc <- group_center(x = df1$homclass3,grp = df1$country)
 # View(df1[,c("homclass","homclass_gc")])

### 2023-10-17 paper.Rmd
ordenar codigo

--- 2023-10-17 paper.Rmd
@@
                         class3, 
-                        homclass=homclass2,
+                        homclass=homclass,
                         # homclass=eindex,
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3=dclass3,
-                        class5,
-                        homclass=homclass2,
+                        class3,
+                        homclass,
                         Q03pcm,
-                        # Q03pcm=Q03rm,
-                        # Q03pcm=Q03rm,
-                        # Q03pcm=zincpc,
-                        # Q03rm=
-                        # isei08,
-                        rgdpna,
                         edyears,
@@
                         agenum,
-                        country2,country,
                         union,
                         workst,
-                        # isolation,  
-                        MAINSTAT,
-                        # activities,
-                        # WEIGHT,
+                        WEIGHT,
                         region,
                         "gini_disp",
-                        "gini_mkt",oecd
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
                         ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
   # filter(!country2 %in% c("CHN")) %>%
   # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
   # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
   # filter(!country2 %in% c("FIN")) %>%
@@
   # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
@@
 
-# frq(df1$region)
-# frq(dfreg$country2)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +homclass+ female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 +  (1|country2),data=dfreg)
-rob4 <- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst + union+ female+agenum +age2 + (homclass|country2),data=dfreg)
-# anova(rob3,rob4)
-
-# plot_model(rob4,type = "re",show.values = T)
-
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
 # Interactions segregation x class
-int_homo <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# int_homo2 <- lmer(redist~class3*homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+  (homclass + class3*homclass|country2),data=dfreg)
-# anova(int_homo,int_homo2)
-# plot_model(int_homo2,type = "re",show.values = F,vline.color = "black")
-
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
 cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
@@
                  "unionYes" = 'Union membership: Yes',
-                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
-                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
                  )
@@
                   )
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob2,int_homo)
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 m1_df <-
-    broom.mixed::tidy(rob3) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+    broom.mixed::tidy(rob1) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                     "class3Working Class (V+VI+VII)",
-                                                    "homclass")) %>% mutate(model = "Model 1")
+                                                    "homclass")) 
+# %>% mutate(model = "Model 1")
 m2_df <-
@@
 
-  dwplot(two_models,
+  dwplot(m1_df,
        vline = geom_vline(xintercept = 0,colour = "black",linetype = 1,size=0.01),
@@
         plot.title = element_text(face = "bold"),
-        legend.position = c(0.007, 0.01),
-        legend.justification = c(0, 0),
-        legend.background = element_rect(colour = "grey80"),
-        legend.title = element_blank(),
+        # legend.position = c(0.007, 0.01),
+        # legend.justification = c(0, 0),
+        # legend.background = element_rect(colour = "grey80"),
+        # legend.title = element_blank(),
         axis.text.y.left = element_text(face = "bold",size = 12)
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
 dfreg <- df1 %>% dplyr::select(redist,
@@
 
-main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <-update(base, . ~ . - (1|country2) + (homclass|country2))
+anova(giniD_gdp,giniD_rs)
 giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
@@
 dfreg %>% filter(gini_disp >= min(gini_sig$fake),gini_disp <= max(gini_sig$fake)) %>% dplyr::select(country2)
-
-table(dfreg$gini_disp)
-
-dfreg %>% filter(gini_disp %in%)
 

### 2023-10-17 procesamiento/prod_prep.Rmd
ordenar codigo

@@
 
+```{r eval=FALSE, include=FALSE}
+knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
+```
+
 # Setup
@@
                       message = FALSE, 
-                      echo = TRUE 
+                      echo = TRUE,
+                      cache = T
                       )
@@
 dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))
-
-# relig <- haven::read_dta(here::here("input/data/original/ZA7570_v2-1-0.dta"))
-# religTR <- relig %>% filter(country==792)
-
+dfTR$weight <- 1
 df1 <- df1 %>% rename(topbot=TOPBOT)
 dfES <- dfES %>% rename(topbot=TOPBOT)
-#fix problem with variable names
+# fix problem with variable names
 dfTR <- dfTR %>% rename(SEX=sex,
@@
                         SPWRKSUP=spwrksup)
+
 dfES$c_alphan <- NULL
@@
 sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
-# hist.default(df1$egal3)
+# #hist.default(df1$egal3)
 
@@
 sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
-# hist.default(df1$egal2)
+# #hist.default(df1$egal2)
 ```
@@
 
+df1 <- df1 %>% 
+  mutate(oesch16spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
+         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))
+
 frq(df1$oesch16)
-frq(df1$oesch8)
-
-df1 <- df1 %>% 
-  mutate(oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
-         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))
-
-frq(df1$oesch8)
-frq(df1$oesch8spo)
+
+df1$oesch16 <- as_labelled(df1$oesch16)
+df1$oesch16spo <- as_labelled(df1$oesch16spo)
+# # Upper-middle class
+#  [1] "'Large employers'"
+#  [2] "'Self-employed professionals'"
+# 
+#  [9] "'Higher-grade managers and administrators'"
+# [10] "'Lower-grade managers and administrators'"
+
+#  [5] "'Technical experts'"
+#  [6] "'Technicians'"
+# 
+# [13] "'Socio-cultural professionals'"
+# [14] "'Socio-cultural semi-professionals'"
+
+# # Lower-middle class
+#  [3] "'Small business owners with employees'"
+#  [4] "'Small business owners without employees'"
+# [11] "'Skilled clerks'"
+# 
+# # Working class
+#  [7] "'Skilled manual'"
+#  [8] "'Low-skilled manual'"
+# 
+# [12] "'Unskilled clerks'"
+# [15] "'Skilled service'"
+# [16] "'Low-skilled service'"
+
+df1$oesch3res <- car::recode(df1$oesch16,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
+df1$oesch3spo <- car::recode(df1$oesch16spo,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
 ```
@@
 #frq(df1$eindex)
-hist.default(df1$eindex)
+#hist.default(df1$eindex)
 df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
-hist.default(df1$eindex_gc)
+#hist.default(df1$eindex_gc)
 
@@
 #frq(df1$eindex_s)
-hist.default(df1$eindex_s)
+#hist.default(df1$eindex_s)
 
@@
 sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
-hist.default(df1$homclass_s)
+#hist.default(df1$homclass_s)
 ```
@@
 frq(df1$eindex_w)
-hist.default(df1$eindex_w)
+#hist.default(df1$eindex_w)
 
@@
 sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
-hist.default(df1$homclass_s)
+#hist.default(df1$homclass_s)
 ```
@@
 # frq(df1$eindex)
-# hist.default(df1$eindex)
+# #hist.default(df1$eindex)
 
@@
 #frq(df1$eindex)
-hist.default(df1$eindex2)
+#hist.default(df1$eindex2)
 df1$eindex2_gc <- group_center(x = df1$eindex2,grp = df1$country)
-hist.default(df1$eindex2_gc)
+#hist.default(df1$eindex2_gc)
 
@@
 df1$ingroup_res <- NA 
-df1 %>% select(ddigclass3res,n_high,n_middle,n_low,ingroup_res)
+df1 %>% select(digclass3res,n_high,n_middle,n_low,ingroup_res)
 df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
@@
 
-df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
+df1$eindex2_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
 sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
 # frq(df1$eindex)
-# hist.default(df1$eindex)
+# #hist.default(df1$eindex)
 
 df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
-df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
+df1$homclass2_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass2_res) <- "Class homogeneity (R's)"
 # Weighted EI index
@@
 save(df1,file = here::here("input/data/proc/study1.RData"))
-```
+knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
+```

### 2023-10-17 paper.Rmd
plots bonitos

@@
                   include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
+                  # custom.coef.map=coefmap,
+                  # groups = coefgroup,
                   custom.gof.rows=gofrow,
@@
 
-plot_predictions(int_homo, condition = c("homclass","class3")) +
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+# plot_predictions(int_homo, condition = c("homclass","class3")) +
+#   facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
+#   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+#   xlab("Network homogeneity")+
+#   ylab("Redistributive preferences") +
+#   theme(legend.position = "none", legend.title = element_blank())
+#   # scale_fill_grey(start = 0.40, end = 0.6) +
+#   # scale_color_grey(start = 0.40, end = 0.6)
+
+df_pred1 <- plot_predictions(int_homo, condition = c("homclass","class3"),draw = F) 
+# names(df_pred1)
+df_pred1 %>% 
+ggplot(aes(y =estimate,x=homclass, fill=class3, color=class3,ymin=conf.low, ymax=conf.high)) +
+  geom_line(size=0.75) +
+  geom_point(size=1.5) +
+  geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
@@
   ylab("Redistributive preferences") +
-  theme(legend.position = "none", legend.title = element_blank())
-  # scale_fill_grey(start = 0.40, end = 0.6) +
-  # scale_color_grey(start = 0.40, end = 0.6)
+  theme(legend.position = "bottom", legend.title = element_blank())
 ```
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3=dclass3,
-                        homclass=homclass2,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
+                        class3,
+                        homclass,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        # giniot=gini,
-                        giniot=gv_spen,
-                        rgdpna,
                         edyears,
@@
                         agenum,
-                        country2,
                         union,
-                        workst,oecd) %>% 
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
     filter(oecd=="OECD") %>%
@@
 giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
-giniD_rs <-update(base, . ~ . - (1|country2) + (homclass|country2))
-anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
 # summary(giniD_int)
 
-giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
 # anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
-# anova(giniOT_gdp,giniOT_rs)
-
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
 models <- list(giniD_gdp,giniD_rs,giniD_int,
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3=dclass3,
-                        homclass=homclass2,
-                        # homclass=homclass_res,
-                        Q05pcm,
+                        class3,
+                        homclass,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,ttheilge1,
-                        gv_spen=gv_spen,
-                        top10,
-                        middle50,
-                        palmaratio,
-                        d10d1,
-                        rgdpna,
-                        individualism,
                         edyears,
@@
                         agenum,
-                        country2,
                         union,
                         workst,
-                        oecd
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
                         ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("THA")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
     # filter(oecd=="OECD") %>%
@@
 
-int_palma <- lmer(redist~class3+ homclass*palmaratio+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_pc10  <- lmer(redist~class3+ homclass*top10+edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_pc50  <- lmer(redist~class3+homclass*middle50+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_d10d1<- lmer(redist~class3+ homclass*d10d1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_gini_wiid  <- lmer(redist~class3+ homclass*giniindex+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-int_theil  <- lmer(redist~class3+ homclass*ttheilge1+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1
-                 # int_gini_wiid,int_theil
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
                  )
@@
   "homclass:middle50"    = "Homogeneity x bottom 50",
-  individualism         = "Individualism Index*",
-  "homclass:individualism" = "Homogeneity x Individualism",
-  gv_spen               = "Gov. Spending (% GDP)*",
-  "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+  # individualism         = "Individualism Index*",
+  # "homclass:individualism" = "Homogeneity x Individualism",
+  # gv_spen               = "Gov. Spending (% GDP)*",
+  # "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
     d10d1             = "Ratio D10/D01",
@@
                 float.pos="h!",                
-                custom.coef.map = customcoef,
+                # custom.coef.map = customcoef,
                 caption.above = T,caption = cap1)

### 2023-10-17 procesamiento/prod_analysis-models.Rmd
lunch
plots bonitos

@@
                         eindex,
-                        prestige,
-                        diversity,
+                        # prestige,
+                        # diversity,
                         # isei_range,
@@
 full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
-full_int2 <- lmer(redist~1+female+agenum+prestige+diversity+eindex*isei08+ednum+(1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
+full_int2 <- lmer(redist~1+female+agenum+eindex*isei08+ednum+(1|country),data=dfreg)
+models <- list(class,class_status,full,full_int1,full_int2)
+texreg::knitreg(full_int2)
 texreg::plotreg(full,omit.coef = "(Intercept)")
@@
                         # eindex,
-                        prestige,
-                        diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
+                        # prestige,
+                        # diversity,
+                        isei_range,
+                        hindex_sta,
+                        hindex_10,
                         ednum,female,agenum,country) %>% na.omit()

### 2023-10-17 procesamiento/prod_prep.Rmd
plots bonitos

@@
 
-frq(df1$oesch16)
+frq(df1$oesch8spo)
+frq(df1$oesch8)
 
@@
 df1$oesch3spo <- car::recode(df1$oesch16spo,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
+
+sjPlot::tab_xtab(df1$oesch3res,df1$oesch3spo,show.na = T)
 ```

### 2023-10-18 paper.Rmd
plots
ajuste

@@
 rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# anova(rob1,rob2)
+anova(rob1,rob2)
 # Interactions segregation x class
@@
 
-## Perceived Isolation
-
-```{r mod-isolation,results='asis', cache=T}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
-                        homclass,
-                        isolation,
-                        Q05pcm,
-                        Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears, 
-                        female,
-                        agenum,
-                        country2,country,
-                        union,
-                        workst
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# dim(dfreg)
-
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
-# Interactions segregation x class
-int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(full1,single.row = F)
-
-cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Isolation x Social Class"=9:10
-                  )
-
-coefmap <-  list(isolation ="Perceived Isolation",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                  "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
-                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
-                 # know_total="Number contacts"
-                 # outgroup="Number outgroup"
-                 homclass ="Class-based network homogeneity"
-                 )
-
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
-```
-
-```{r leverage2, eval=FALSE, include=FALSE}
-pacman::p_load(influence.ME,lattice)
-# dfbetas-----------------------------------------------------------------------
-influence <- influence(rob3, "country2")
-dfbetas(influence,parameters=c(1,4)) 
-n_groups <- lme4::ngrps(rob3)
-
-influence_est=as.data.frame(dfbetas(influence))
-influence_est %>%  filter(homclass > 2/sqrt(n_groups))
-
-plot(influence, which="dfbetas", 
-     parameters=c("isolation"),
-     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
-
-# cook-distance-----------------------------------------------------------------
-# cooks.distance(rob3, sort = TRUE)
-plot(influence, which="cook",
-     cutoff=4/n_groups, sort=TRUE,
-     xlab="Cooks Distance",
-     ylab="Country")
-
-sigtest1<- sigtest(influence, test=-1.96)
-sigtest1$homclass
-```
-
-```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() + 
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Perceived Isolation")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
-# Predicted values 
-plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
-    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(legend.position = "none")+ 
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences")
-```
-
-```{r mod-intermacro2,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        homclass,
-                        isolation,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
-                        Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
-                        edyears,
-                        female,
-                        agenum,
-                        country2,
-                        union,
-                        workst) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  na.omit()
-# T03dim(dfreg)
-
-main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
-# summary(giniD_int)
-
-giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
-                caption.above=T,
-                  # include.thresholds=FALSE,
-                  custom.coef.map=list(isolation="Perceived Isolation",
-                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "isolation:gini_disp"="Isolation x Gini (D)",
-                                       "gini_mkt"="Gini (Market) ",
-                                       "isolation:gini_mkt"="Isolation x Gini (M)",
-                                       homclas="Class-based homogeneity"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-```
-
-```{r crosslevel2}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
-p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-predval1 <- 
-plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       linetype='Gini (Disposable)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-# Predicted values 
-predval2 <- 
-plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
-  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       linetype='Gini (Market)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-```
-
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
-grid.arrange(p1,predval1,nrow = 1    
-             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
-             )
-```
-
-```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
-grid.arrange(p2,predval2,nrow = 1    
-             # top = "Perceived Isolation × Gini (Market)"  
-             )
-```
-
-\pagebreak
-
 # References

### 2023-10-18 procesamiento/prod_analysis-models.Rmd
ajuste

@@
 
-Modelos homogeneidad
+## Ordinal
 
-```{r class-homclass}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3,
-                        # tr_inte,
-                        # eindex,
-                        # know_total,
-                        homclass,
-                        homclass_gc,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        # pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,
-                        # sstatus,
-                        gini_disp,
-                        gini_mkt,
-                        # palmawd,
-                        rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,
-                        female,
-                        agenum,
-                        country2,
-                        # WEIGHT
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>%
-  # filter(country!=233) %>% 
-  na.omit()
-dim(dfreg)
-
-base <- lmer(redist~1 + (1|country2),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + (1|country2),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + homclass + (1|country2),data=dfreg)
-class <- lmer(redist~1 +female+agenum + class3+ (1|country2),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country2),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm + (1|country2),data=dfreg)
-full_b <- lmer(redist~1 +female+agenum + class3 +ednum+homclass_gc +  Q05pcm + (1|country2),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1|country2),data=dfreg)
-full_m_rs <- lmer(redist~1 +female+agenum + class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1+homclass|country2),data=dfreg)
-
-anova(full_m,full_m_rs)
-plot_model(full_m_rs,type = "re")
-# Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + ednum + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,full,full_int1)
-texreg::knitreg(models)
-
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  ylab("Class-based homogeneity coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# Predicted values 
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-```
-
-```{r homclass-gini}
-# Interactions segregation x inequality
-df1$homclass_gc <- MLMusingR::group_center(df1$homclass,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-df1$ratio10_50 <- df1$pc10_2017/df1$pc50_2017
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-int_giniot<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini+ednum + Q05pcm  +logrgdpna + (1+homclass_gc|country),data=df1)
-
-# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090,int_giniot)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_gc",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_mkt)
-
-df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_disp)
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass_gc",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)
-
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass_gc",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)
-
-p6<- interplot::interplot(m = int_r1090,var1 = "homclass_gc",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)
-
-p7<- interplot::interplot(m = int_giniot,var1 = "homclass_gc",var2="gini") +
-  xlab("Gini (WD)") + geom_point()+ geom_hline(yintercept = 0)
-
-grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
-g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation × Inequality")
-
-ggsave(plot = g,filename = "mar_homclass_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
-```
-
-```{r class-homclass-res}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)")
-df1$class3spo <- relevel(df1$class3spo,ref =  "Intermediate class (III+IV)")
-
-df1$class3spo <-  car::recode(df1$class3spo,recodes = "NA='No information'")
-frq(df1$class3spo)
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3res,
-                        # class3spo,
-                        # tr_inte,
-                        # eindex,
-                        # know_total,
-                        homclass_res,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        # pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,
-                        labst,
-                        union,
-                        # sstatus,
-                        gini_disp,
-                        gini_mkt,
-                        # palmawd,
-                        rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,female,agenum,country) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>% 
-  # filter(country!=233) %>% 
-  na.omit()
-dim(dfreg)
-
-dfreg$country <- sjlabelled::as_factor(dfreg$country)
-base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_res + (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + labst + union+ class3res+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + labst + union+ class3res+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + labst + union+ class3res + ednum+homclass_res +  Q05pcm + (1|country),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + labst + union+ class3res+ednum+homclass_res +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
-
-# Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_res*class3res+ednum + Q05pcm + (1|country),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_int1)
-texreg::knitreg(models)
-
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = full_int1,var1 = "homclass_res",var2="class3res")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  ylab("Class-based homogeneity (R's) coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_homores_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# Predicted values 
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  xlab("Network homogeneity (R's)")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_homores_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# isolation <- 
-# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-# df_int2 <- isolation$data
-# df_int2 <- df_int2[c(1,2,4),]
-# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-# df_int2
-# df_int2$value <- factor(df_int2$value,ordered = T,
-#                         levels = c("Working Class (V+VI+VII)",
-#                                    "Intermediate class (III+IV)",
-#                                    "Service Class (I+II)"))
-# 
-# df_int2 %>% 
-# ggplot() +
-#   geom_point(aes(x = value,y = coef1)) + 
-#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-#   ylab("Perceived isolation coefficient")+
-#   xlab("Social Class")+
-#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-#   geom_hline(yintercept = 0)
-# 
-# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-```
-
-```{r homclass-macro-res}
-# Interactions segregation x inequality
-df1$homclass_res_gc <- MLMusingR::group_center(df1$homclass_res,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_res_gc",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_res_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass_res_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass_res_gc",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)
-
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass_res_gc",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)
-
-p6<- interplot::interplot(m = int_r1090,var1 = "homclass_res_gc",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)
-
-grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
-g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (R's) × Inequality")
-
-ggsave(plot = g,filename = "mar_homclass_rs_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
-```
-
-Modelos strong ties
-
-```{r strong-ties}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class6,class3,class5,
-                        # tr_inte,
-                        # eindex,
-                        # know_total,
-                        # homclass,
-                        homclass_s,
-                        # homclass_w,
-                        # prestige,
-                        # diversity,
-                        # pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,labst,union,
-                        # sstatus,
-                        gini_disp,
-                        gini_mkt,
-                        # palmawd,
-                        rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,female,agenum,country) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>% 
-  # filter(country!=233) %>% 
-  na.omit()
-dim(dfreg)
-dfreg$country <- sjlabelled::as_factor(dfreg$country)
-base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_s + (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + (1|country),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)
-
-# Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s*class3+ ednum + Q05pcm + (1|country),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_m,full_int1)
-texreg::knitreg(models)
-
-# Conditional Marginal effect---------------------------------------------------
-interplot <- 
-interplot::interplot(m = full_int1,var1 = "homclass_s",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Class-based homogeneity (s) coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_strong-ties_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# Predicted values -------------------------------------------------------------
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
-  xlab("Network homogeneity (strong ties)")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_strong-ties_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# isolation <- 
-# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-# df_int2 <- isolation$data
-# df_int2 <- df_int2[c(1,2,4),]
-# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-# df_int2
-# df_int2$value <- factor(df_int2$value,ordered = T,
-#                         levels = c("Working Class (V+VI+VII)",
-#                                    "Intermediate class (III+IV)",
-#                                    "Service Class (I+II)"))
-
-# df_int2 %>% 
-# ggplot() +
-#   geom_point(aes(x = value,y = coef1)) + 
-#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-#   ylab("Perceived isolation coefficient")+
-#   xlab("Social Class")+
-#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-#   geom_hline(yintercept = 0)
-
-# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-```
-
-```{r strong-ties-macro}
-df1$homclass_s_gc <- MLMusingR::group_center(df1$homclass_s,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_s_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_s_gc",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_s_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass_s_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass_s_gc",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)
-
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass_s_gc",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)
-
-p6<- interplot::interplot(m = int_r1090,var1 = "homclass_s_gc",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)
-
-grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
-g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (strong ties) × Inequality")
-
-ggsave(plot = g,filename = "mar_homclass_st_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
-```
-
-Modelos weak ties
-
-```{r weak-ties}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class6,class3,class5,
-                        # tr_inte,
-                        # eindex,
-                        # know_total,
-                        homclass,
-                        homclass_s,
-                        homclass_w,
-                        # prestige,
-                        # diversity,
-                        # pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,labst,union,
-                        # sstatus,
-                        gini_disp,
-                        gini_mkt,
-                        # palmawd,
-                        rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,female,agenum,country,) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>% 
-  # filter(country!=233) %>% 
-  na.omit()
-dim(dfreg)
-dfreg$country <- sjlabelled::as_factor(dfreg$country)
-base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_w + (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + (1|country),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)
-
-# Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_w*class3+ ednum + Q05pcm + (1|country),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_m,full_int1)
-texreg::knitreg(models)
-
-# Conditional Marginal effect---------------------------------------------------
-interplot <- 
-interplot::interplot(m = full_int1,var1 = "homclass_w",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  ylab("Class-based homogeneity (w) coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_weak-ties_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# Predicted values -------------------------------------------------------------
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
-  xlab("Network homogeneity (weak ties)")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_weak-ties_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-```
-
-```{r weak-ties-macro}
-df1$homclass_w_gc <- MLMusingR::group_center(df1$homclass_w,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_s_gc|country),data=df1)
-# int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_res_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
-int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
-int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3res + homclass_w_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+homclass_w_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_pc10,int_pc50,int_r1090)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_w_gc",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_w_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass_w_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-
-p4<- interplot::interplot(m = int_pc10,var1 = "homclass_w_gc",var2="pc10_2017") +
-  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)
-
-p5<- interplot::interplot(m = int_pc50,var1 = "homclass_w_gc",var2="pc50_2017") +
-  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)
-
-p6<- interplot::interplot(m = int_r1090,var1 = "homclass_w_gc",var2="ratio10_50") +
-  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)
-
-grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
-g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Network segregation (weak ties) × Inequality")
-
-ggsave(plot = g,filename = "mar_homclass_wt_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
-```
-
-## Perceived Isolation
-
-```{r mod-isolation,results='asis', cache=T}
+```{r mod-homclass,results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
 rm(list=ls())
@@
 dfreg <- df1 %>% dplyr::select(redist,
-                        class3,class5,
+                        class3,
                         homclass,
-                        isolation,
-                        Q05pcm,
                         Q03pcm,
-                        # isei08,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
                         edyears,
@@
                         agenum,
-                        country2,country,
                         union,
-                        workst
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
                         ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
   na.omit()
-# dim(dfreg)
 
-# lineal
-base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
-class <- lmer(redist~ class3+ (1|country2),data=dfreg)
-homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
-full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
-rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
-rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
-rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
+# Models 
+base <- clmm(factor(redist)~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+anova(rob1,rob2)
 # Interactions segregation x class
-int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
-# models <- list(homclass,class,full1,
-#                # rob1,rob2,
-#                rob4)
-# texreg::screenreg(full1,single.row = F)
+int_homo <- update(rob1, . ~ . +class3*homclass)
 
-cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Isolation x Social Class"=9:10
-                  )
-
-coefmap <-  list(isolation ="Perceived Isolation",
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
                  'class3Intermediate class (III+IV)' ='Intermediate Class',
@@
                  "unionYes" = 'Union membership: Yes',
-                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
-                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
-                 # know_total="Number contacts"
-                 # outgroup="Number outgroup"
-                 homclass ="Class-based network homogeneity"
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
                  )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
 
-gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
-
-models <- list(homclass,class,full1,rob3,int_homo)
+models <- list(homclass,full1,rob1,int_homo)
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
                   include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
+                  # custom.gof.names = gof1
                 )
-
 ```
 
-```{r leverage2, eval=FALSE, include=FALSE}
-pacman::p_load(influence.ME,lattice)
-# dfbetas-----------------------------------------------------------------------
-influence <- influence(rob3, "country2")
-dfbetas(influence,parameters=c(1,4)) 
-n_groups <- lme4::ngrps(rob3)
-
-influence_est=as.data.frame(dfbetas(influence))
-influence_est %>%  filter(homclass > 2/sqrt(n_groups))
-
-plot(influence, which="dfbetas", 
-     parameters=c("isolation"),
-     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))
-
-# cook-distance-----------------------------------------------------------------
-# cooks.distance(rob3, sort = TRUE)
-plot(influence, which="cook",
-     cutoff=4/n_groups, sort=TRUE,
-     xlab="Cooks Distance",
-     ylab="Country")
-
-sigtest1<- sigtest(influence, test=-1.96)
-sigtest1$homclass
-```
-
-```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() + 
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  ylab("Perceived Isolation")+
-  xlab("Social Class")+
-  ggtitle("Redistributive preferences") +
-  geom_hline(yintercept = 0) + 
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(plot.title = element_text(size = 8))  
-```
-
-```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
-# Predicted values 
-plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
-    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
-  theme(legend.position = "none")+ 
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences")
-```
-
-```{r mod-intermacro2,results='asis'}
+```{r mod-intermacro,results='asis'}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot,ordinal)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
 dfreg <- df1 %>% dplyr::select(redist,
@@
                         homclass,
-                        isolation,
-                        # homclass=eindex,
-                        # homclass=ingroup,
-                        Q05pcm,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        rgdpna,
                         edyears,
@@
                         agenum,
-                        country2,
                         union,
-                        workst) %>% 
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
   na.omit()
@@
 
-main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"
-
-giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
-giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
 # anova(giniD_gdp,giniD_rs)
-giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
 # summary(giniD_int)
 
-giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
-giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
 # anova(giniM_gdp,giniM_rs)
-giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
-
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
 models <- list(giniD_gdp,giniD_rs,giniD_int,
@@
 texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
-                caption.above=T,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
                 # include.thresholds=FALSE,
-                  custom.coef.map=list(isolation="Perceived Isolation",
+                custom.coef.map=list(homclass="Network Homogeneity",
                                      logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                       "isolation:gini_disp"="Isolation x Gini (D)",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
                                      "gini_mkt"="Gini (Market) ",
-                                       "isolation:gini_mkt"="Isolation x Gini (M)",
-                                       homclas="Class-based homogeneity"),
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
                   # groups = coefgroup,
@@
                 )
-```
-
-```{r crosslevel2}
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
-p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
-  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
-  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
-  geom_point()+ geom_hline(yintercept = 0)
-
-# Predicted values 
-predval1 <- 
-plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
-  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
-       linetype='Gini (Disposable)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-
-# Predicted values 
-predval2 <- 
-plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
-  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
-       linetype='Gini (Market)') +
-  xlab("Perceived Isolation")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
-```
-
-```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
-grid.arrange(p1,predval1,nrow = 1    
-             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
-             )
-```
-
-```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
-grid.arrange(p2,predval2,nrow = 1    
-             # top = "Perceived Isolation × Gini (Market)"  
-             )
-```
-
-# Modelos alternativos
-
-```{r eindex-homclass}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"))
-df1 <- df2
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
-                          as.factor = T,
-                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
-frq(df1$Q05pcm)
-dfreg <- df1 %>% dplyr::select(redist,
-                        class6,class3,class5,
-                        # tr_inte,
-                        eindex,
-                        # know_total,
-                        # homclass,
-                        # homclass_gc,
-                        # homclass_s,homclass_w,
-                        # prestige,
-                        # diversity,
-                        # pi_nteg,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        Q05pcm,
-                        labst,
-                        union,
-                        # sstatus,
-                        gini_disp,
-                        gini_mkt,
-                        # palmawd,
-                        rgdpna,
-                        # giniwb,
-                        # giniwd,
-                        ednum,female,agenum,country) %>% 
-  mutate(logrgdpna=log(rgdpna)) %>% 
-  # filter(country!=233) %>% 
-  na.omit()
-dim(dfreg)
-
-dfreg$country <- sjlabelled::as_factor(dfreg$country)
-base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
-demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
-homclass <- lmer(redist~1 + female+agenum + labst + union+  eindex + (1|country),data=dfreg)
-class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm + (1|country),data=dfreg)
-full_b <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+eindex +  Q05pcm + (1|country),data=dfreg)
-full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+eindex +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
-
-# Interactions segregation x class
-full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ ednum + Q05pcm + (1|country),data=dfreg)
-# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)
-
-models <- list(homclass,class,class_status,full,full_b,full_int1)
-texreg::knitreg(models)
-
-# Conditional Marginal effect
-interplot <- 
-interplot::interplot(m = full_int1,var1 = "eindex",var2="class3")
-df_int <- interplot$data
-df_int <- df_int[c(1,2,4),]
-df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-df_int
-df_int$value <- factor(df_int$value,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-df_int %>% 
-ggplot() +
-  geom_point(aes(x = value,y = coef1)) + 
-  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  ylab("Class-based homogeneity coefficient")+
-  xlab("Social Class")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# Predicted values 
-pred1<- plot_model(full_int1,type = "int")
-pred_data <- data.frame(pred1$data)
-pred_data <- pred_data %>% arrange(pred_data$group)
-pred_data$group <- factor(pred_data$group,ordered = T,
-                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))
-
-pred_data %>% 
-ggplot() +
-  geom_point(aes(x = x,y = predicted)) +
-  geom_line(aes(x = x,y = predicted))+
-  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
-  facet_grid(. ~ group) +
-  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") + 
-  theme_minimal()
-
-ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# isolation <- 
-# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
-# df_int2 <- isolation$data
-# df_int2 <- df_int2[c(1,2,4),]
-# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
-# df_int2
-# df_int2$value <- factor(df_int2$value,ordered = T,
-#                         levels = c("Working Class (V+VI+VII)",
-#                                    "Intermediate class (III+IV)",
-#                                    "Service Class (I+II)"))
-# 
-# df_int2 %>% 
-# ggplot() +
-#   geom_point(aes(x = value,y = coef1)) + 
-#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
-#   ylab("Perceived isolation coefficient")+
-#   xlab("Social Class")+
-#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-#   geom_hline(yintercept = 0)
-# 
-# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-```
-
-```{r eindex-macro}
-# Interactions segregation x inequality
-df1$homclass_gc <- MLMusingR::group_center(df1$homclass,df1$country) 
-df1$logrgdpna=log(df1$rgdpna)
-
-int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-int_giniwd <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_gc*giniwd+ednum + Q05pcm  +logrgdpna + (1+homclass_res_gc|country),data=df1)
-
-# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
-models_m <- list(int_ginidis,int_ginimkt,int_palma,int_giniwd)
-texreg::knitreg(models_m)
-
-library(gridExtra)
-p1<- interplot::interplot(m = int_ginidis,var1 = "homclass_gc",var2="gini_disp")+
-  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") +
-  geom_point()+ geom_hline(yintercept = 0)
-p1$data$fake[p1$data$ub>0]
-min(p1$data$fake[p1$data$ub>0])
-max(p1$data$fake[p1$data$ub>0])
-
-p2<- interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
-  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
-
-p2$data$fake[p2$data$ub>0]
-min(p2$data$fake[p2$data$ub>0])
-max(p2$data$fake[p2$data$ub>0])
-
-df1 %>% filter(gini_mkt>=min(p2$data$fake[p2$data$ub>0]) &  gini_mkt<= max(p2$data$fake[p2$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_mkt=mean(gini_mkt),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_mkt)
-
-df1 %>% filter(gini_disp>=min(p1$data$fake[p1$data$ub>0]) &  gini_disp<= max(p1$data$fake[p1$data$ub>0])) %>% 
-  group_by(country) %>% 
-  summarise(n(),gini_disp=mean(gini_disp),homclass_gc=mean(homclass,na.rm=T)) %>% 
-  arrange(gini_disp)
-
-p3<- interplot::interplot(m = int_palma,var1 = "homclass_gc",var2="palmawd") +
-  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)
-grid.arrange(p1,p2,p3,nrow = 1)
-g<- arrangeGrob(p1,p2,p3,nrow = 1,top = "Network segregation")
-
-ggsave(plot = g,filename = "mar_homclass_ineq.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 12)
-
-interplot::interplot(m = int_ginimkt,var1 = "homclass_gc",var2="gini_mkt") +
-  geom_point()+
-  ylab("Class-based homogeneity coefficient")+
-  xlab("Economic Inequality")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0) +
-  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
-  theme(plot.title = element_text(size = 8))
-
-ggsave(plot = last_plot(),filename = "mar_homclass_gini.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)
-
-# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
-#   geom_point()+
-#   ylab("Perceived isolation coefficient")+
-#   xlab("Economic Inequality")+
-#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-#   geom_hline(yintercept = 0)
-# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
-#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
-
-```{r isei, eval=FALSE, include=FALSE}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(sjmisc,ggplot2,lme4,interplot)
-load(here::here("input/data/proc/study1.RData"))
-# remove.packages("Matrix")
-# install.packages("Matrix")
-df1$class3<-forcats::fct_rev(df1$class3)
-df1$class5<-forcats::fct_rev(df1$class5)
-df1$class6<-forcats::fct_rev(df1$class6)
-dfreg <- df1 %>% dplyr::select(redist,
-                        isei08,
-                        eindex,
-                        # prestige,
-                        # diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
-
-dfreg$country <- to_factor(dfreg$country)
-dim(dfreg)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ eindex + (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1+female+agenum+isei08+ednum+prestige+diversity+eindex+(1|country),data=dfreg)
-full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
-full_int2 <- lmer(redist~1+female+agenum+eindex*isei08+ednum+(1|country),data=dfreg)
-models <- list(class,class_status,full,full_int1,full_int2)
-texreg::knitreg(full_int2)
-texreg::plotreg(full,omit.coef = "(Intercept)")
-
-interplot::interplot(m = full_int1,var1 = "eindex",var2="isei08") +
-  ylab("Network diversity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-
-#-----------
-dfreg <- df1 %>% select(redist,
-                        isei08,
-                        eindex,
-                        prestige,
-                        # diversity,
-                        # isei_range,
-                        # hindex_sta,
-                        # hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
-
-dim(dfreg)
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)
-
-class <- lmer(redist~1+female+agenum+isei08+(1|country),data=dfreg)
-class_status <- lmer(redist~1+female+agenum+isei08+ednum+(1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1|country),data=dfreg)
-fullrs <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1+eindex|country),data=dfreg)
-full_int1 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1|country),data=dfreg)
-full_int2 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1+eindex|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-texreg::plotreg(full, omit.coef = "(Intercept)")
-
-interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
-  ylab("Network heterogeneity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
-ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-# en la medida que aumenta el status, el efecto de la diversidad de la red se vuelve positivo.
-# en personas de estatus bajo la diversidad hace que demanden menos redistribucion
-# en personas de estatus alto la diversidad hace que demanden más redistribucion
-```
-
-```{r class-diversity, eval=FALSE, include=FALSE}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
-load(here::here("input/data/proc/study1.RData"))
-
-levels(df1$class3)
-df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
-levels(df1$class3)
-levels(df1$class5)
-df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (I+II)"
-                                           ))
-
-df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
-                                           "Routine non-manual (IIIa+b)",
-                                           "Skilled manual workers and supv. (V+VI)",
-                                           "Non-skilled manual workers (VIIa+b)",
-                                           "Service class (II - lower grade)",
-                                           "Service class (I - higher grade)" 
-                                           ))
-levels(df1$class6)
-
-dfreg <- df1 %>% select(redist,
-                        class6,
-                        class3,
-                        class5,
-                        # eindex,
-                        # prestige,
-                        # diversity,
-                        isei_range,
-                        hindex_sta,
-                        hindex_10,
-                        ednum,female,agenum,country) %>% na.omit()
-dim(dfreg)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class6 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-base <- lmer(redist~1 + (1|country),data=dfreg)
-demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
-prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
-diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)
-
-class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
-class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
-full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + diversity +(1|country),data=dfreg)
-full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum +(1|country),data=dfreg)
-full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum + (1+diversity|country),data=dfreg)
-models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
-texreg::knitreg(models)
-
-interplot::interplot(m = full_int1,var1 = "diversity",var2="class3") +
-  ylab("Network diversity coefficient")+
-  xlab("SES Respondent")+
-  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
-  geom_hline(yintercept = 0)
-
 ```

### 2023-10-18 procesamiento/prod_prep.Rmd
ajuste

--- 2023-10-17 procesamiento/prod_prep.Rmd
@@
 ```{r eval=FALSE, include=FALSE}
-knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
+# knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
+# knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
 ```
@@
 
-frq(df1$oesch16)
-
-df1$oesch16 <- as_labelled(df1$oesch16)
-df1$oesch16spo <- as_labelled(df1$oesch16spo)
-# # Upper-middle class
+# Traditional Upper-middle class
 #  [1] "'Large employers'"
@@
 # 
+# Salaried middle class
 #  [9] "'Higher-grade managers and administrators'"
@@
 
-df1$oesch3res <- car::recode(df1$oesch16,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
-df1$oesch3spo <- car::recode(df1$oesch16spo,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
+# reorder Oesch's scheme in a (semi)hierarchical order
+oesch_hierar <- 
+c("'Large employers'","'Self-employed professionals'",
+  "'Higher-grade managers and administrators'",
+  "'Lower-grade managers and administrators'",
+  "'Technical experts'","'Technicians'",
+  "'Socio-cultural professionals'","'Socio-cultural semi-professionals'",
+  "'Small business owners with employees'","'Small business owners without employees'","'Skilled clerks'",
+  "'Skilled manual'","'Skilled service'",
+  "'Low-skilled service'","'Unskilled clerks'","'Low-skilled manual'")
+
+# Respondent social class ------------------------------------------------------
+df1$oesch16 <- factor(df1$oesch16,
+                      levels = oesch_hierar)
+frq(df1$oesch16)
+
+# Partner social class ---------------------------------------------------------
+df1$oesch16spo <- factor(df1$oesch16spo,
+                      levels = oesch_hierar)
+frq(df1$oesch16spo)
+
+#   Given that the Oesch's Scheme consider the vertical (skills) and horizontal (work-logic) as the main distinction between classes
+# I will colapse in 4 classes that allow to distinguish between hierarchical differences
+
+# 1. Traditional Upper-middle class
+# 2. Salaried middle-class
+# 3. Lower middle class
+# 4. Working Class
+
+df1$oesch4 <- NA
+df1$oesch4[df1$oesch16 %in%c("'Large employers'","'Self-employed professionals'")] <- 4
+df1$oesch4[df1$oesch16 %in%c("'Higher-grade managers and administrators'",
+                             "'Lower-grade managers and administrators'",
+                             "'Technical experts'","'Technicians'",
+                             "'Socio-cultural professionals'",
+                             "'Socio-cultural semi-professionals'")] <- 3
+df1$oesch4[df1$oesch16 %in%c( "'Small business owners with employees'",
+                              "'Small business owners without employees'",
+                              "'Skilled clerks'")] <- 2
+
+df1$oesch4[df1$oesch16 %in%c("'Low-skilled service'",
+                             "'Unskilled clerks'",
+                             "'Low-skilled manual'")] <- 1
+
+frq(df1$oesch4) # higher number is the hierarchical order of the four main classes
+
+df1$oesch4spo <- NA
+df1$oesch4spo[df1$oesch16spo %in%c("'Large employers'","'Self-employed professionals'")] <- 4
+df1$oesch4spo[df1$oesch16spo %in%c("'Higher-grade managers and administrators'",
+                             "'Lower-grade managers and administrators'",
+                             "'Technical experts'","'Technicians'",
+                             "'Socio-cultural professionals'",
+                             "'Socio-cultural semi-professionals'")] <- 3
+df1$oesch4spo[df1$oesch16spo %in%c( "'Small business owners with employees'",
+                              "'Small business owners without employees'",
+                              "'Skilled clerks'")] <- 2
+
+df1$oesch4spo[df1$oesch16spo %in%c("'Low-skilled service'",
+                             "'Unskilled clerks'",
+                             "'Low-skilled manual'")] <- 1
+frq(df1$oesch4spo)
+#if NA in class of respondent, replace with spouse
+df1$oesch4_dom  <- ifelse(is.na(df1$oesch4),df1$oesch4spo,df1$oesch4)
+frq(df1$oesch4_dom)
+# if NA in respondents it is assumed to be lower than spouse
+# now, with the cases in we have information for respondent and spouse
+# we replace the value by the highest one
+
+# Replace the highest class by dominance criteria 
+# Keep the highest of two values:
+df1$oesch4_dom <- pmax(df1$oesch4, #social class respondent
+                       df1$oesch4spo,#social class spouse
+                       na.rm = T) # if NA, do nothing
+frq(df1$oesch4_dom)
+df1$oesch4_dom <- as_numeric(df1$oesch4_dom)
+frq(df1$oesch4_dom)
+
+# 3-class scheme Oesch
+df1$oesch3 <- car::recode(df1$oesch4,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
+                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
+frq(df1$oesch3)
+df1$oesch3spo <- car::recode(df1$oesch4spo,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
+                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
+frq(df1$oesch3spo)
+
+df1$oesch3_dom <- car::recode(df1$oesch4_dom,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
+                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
+frq(df1$oesch3_dom)
 ```
@@
 save(df1,file = here::here("input/data/proc/study1.RData"))
-knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
-```
+```

### 2023-10-19 paper.Rmd
Update paper.Rmd

@@
 gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
-models <- list(homclass,full1,rob2,int_homo)
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)
+
+models <- list(homclass,full1,rob1,int_homo)
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
                   include.thresholds=FALSE,
-                  # custom.coef.map=coefmap,
-                  # groups = coefgroup,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
                   custom.gof.rows=gofrow,
                   include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
+                  custom.gof.names = gof1
                 )
@@
                                                     "homclass"))
+
 # %>% mutate(model = "Model 1")

### 2023-10-19 paper.Rmd
plotcoef

@@
 m1_df <-
-    broom.mixed::tidy(rob1) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
+    broom.mixed::tidy(rob1,conf.int = TRUE) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                     "class3Working Class (V+VI+VII)",
@@
   )
+
+ggplot(
+  m1_df,
+  aes(x = estimate, y = term, colour=term)) +
+  geom_vline(xintercept = 0) +
+  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
+  # scale_x_continuous(labels = label_percent()) +
+  guides(color = "none") +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  theme(
+        axis.text.y.left = element_text(face = "bold",size = 12)
+  )
+
 ```

### 2023-10-19 paper.Rmd
plot

@@
   m1_df,
-  aes(x = estimate, y = term, colour=term)) +
+  aes(x = estimate, y = term)) +
   geom_vline(xintercept = 0) +
-  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
-  # scale_x_continuous(labels = label_percent()) +
+  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),size=1, width=0.2) +
+  geom_point(shape=21, size=3, fill="white") +
+  scale_y_discrete(labels=c("Working Class (V+VI+VII)",
+                            "Intermediate class (III+IV)",  
+                            "Class-based homogeneity")) +
   guides(color = "none") +
@@
   theme(
-        axis.text.y.left = element_text(face = "bold",size = 12)
+        axis.text.y.left = element_text(face = "plain",size = 12)
   )

### 2023-10-19 procesamiento/prod_analysis-models.Rmd
Update prod_analysis-models.Rmd

@@
 
-- mantener clase R´s y calcular homogeneidad
-- mantener clase de Partner a parte como un control
-
 ```{r setup}
@@
 
-## Ordinal
+# Ordinal
 
-```{r mod-homclass,results='asis', cache=T}
+```{r mod-homclass-ordinal,results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
@@
 full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 anova(rob1,rob2)
@@
 
-```{r mod-intermacro,results='asis'}
+```{r mod-intermacro-ordinal,results='asis'}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot,ordinal,brms)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+df1$redistF <- as.factor(df1$redist)
+dfreg <- df1 %>% dplyr::select(redist=redistF,
                         class3,
@@
 main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
-base <- clmm(formula(main),data=dfreg,weights = WEIGHT)
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT,Hess = T)
 giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
@@
 
-## Gov's spending and individualism
-
-```{r mod-spend-indv, results='asis'}
+```{r mod-other-macro-ordinal,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+df1$redistF <- as.factor(df1$redist)
+dfreg <- df1 %>% dplyr::select(redist=redistF,
                         class3,
-                        homclass=homclass_gc,
-                        # homclass=homclass_res,
-                        Q05pcm,
+                        homclass,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,ttheilge1,
-                        gv_spen=gv_spen,
-                        top10,
-                        middle50,
-                        palmaratio,
-                        d10d1,
-                        rgdpna,
-                        individualism,
                         edyears,
@@
                         agenum,
-                        country2,
                         union,
-                        workst
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
                         ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-    # filter(!country2 %in% c("Turkey","Estonia")) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("THA")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
   # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
   na.omit()
-int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-models_m <- list(int_indivi,int_govspe)
-cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
 customcoef <- 
@@
   logrgdpna           = "log GDP",
-  individualism         = "Individualism Index*",
-  "homclass:individualism" = "Homogeneity x Individualism",
-  gv_spen               = "Gov. Spending (% GDP)*",
-  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
+  palmaratio               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
+  # individualism         = "Individualism Index*",
+  # "homclass:individualism" = "Homogeneity x Individualism",
+  # gv_spen               = "Gov. Spending (% GDP)*",
+  # "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+    d10d1             = "Ratio D10/D01",
+  "homclass:d10d1"    = "Homogeneity x Ratio D10/D01"  
 )
-texreg::knitreg(models_m,scalebox = 1,
+texreg::knitreg(models_m,scalebox = 0.75,
                 float.pos="h!",                
-                custom.coef.map = customcoef,
+                # custom.coef.map = customcoef,
                 caption.above = T,caption = cap1)
@@
 
-```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
-p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
-  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+# Binary logit
 
-predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-       linetype='Individualism') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
+```{r mod-homclass-binary,results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
+  na.omit()
 
-p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
-  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
 
-predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
-       linetype='Gov.Spend') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
 
-grid.arrange(p9,predval9,
-             p8,predval8,nrow = 2)
+models <- list(homclass,full1,rob1,int_homo)
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
 ```
+
+```{r mod-intermacro-binary,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot,ordinal,brms)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("FIN")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
+  na.omit()
+# T03dim(dfreg)
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+```
+
+```{r mod-other-macro-ordinal,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  # filter(!country2 %in% c("CHN")) %>%
+  # filter(!country2 %in% c("TWN")) %>%
+  # filter(!country2 %in% c("JPN")) %>%
+  # filter(!country2 %in% c("ZAF")) %>%
+  # filter(!country2 %in% c("PHL")) %>%
+  # filter(!country2 %in% c("THA")) %>%
+  # filter(!country2 %in% c("USA")) %>%
+  # filter(!country2 %in% c("GBR")) %>%
+  # filter(!country2 %in% c("ISL")) %>%
+  # filter(!country2 %in% c("TUR","EST")) %>%
+  # filter(!country2 %in% c("MEX")) %>%
+# filter(!country2 %in% c("HUN")) %>%
+  # filter(MAINSTAT %in% c(1,2)) %>%
+  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
+  # filter(PARTLIV %in% c(0,1,2,3)) %>%
+  # filter(!region %in% c("Northern America","South America")) %>%
+  # filter(Q03pcm!="Missing") %>%
+    # filter(oecd=="OECD") %>%
+  na.omit()
+
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+list(homclass = "Class-based network homogeneity",
+  logrgdpna           = "log GDP",
+  palmaratio               = "Palma Ratio",
+  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
+  top10             = "Share National Income - top 10%",
+  "homclass:top10"    = "Homogeneity x top 10",
+  middle50             = "Share National Income -  bottom 50%",
+  "homclass:middle50"    = "Homogeneity x bottom 50",
+  # individualism         = "Individualism Index*",
+  # "homclass:individualism" = "Homogeneity x Individualism",
+  # gv_spen               = "Gov. Spending (% GDP)*",
+  # "homclass:gv_spen"      = "Homogeneity x Gov. Spend.",
+    d10d1             = "Ratio D10/D01",
+  "homclass:d10d1"    = "Homogeneity x Ratio D10/D01"  
+)
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                # custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+```

### 2023-10-19 procesamiento/prod_analysis-full-sample.Rmd
variables

--- 2023-10-19 procesamiento/prod_analysis-models.Rmd
@@
 title: "Multilevel regression models"
+subtitle: "Full sample"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
 giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
-# summary(giniD_int)
+summary(giniD_int)
 
@@
 
-```{r mod-other-macro-ordinal,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
+```{r mod-other-macro-binary,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
 if (!require("pacman")) install.packages("pacman")

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

--- 2023-10-18 procesamiento/prod_analysis-models.Rmd
@@
 
-# Modelos
+# Binary logit
 
-dicotomizar homogeneidad en 1=50% similar,49% similar
+## Full network
 
-## Ordinal
-
-```{r mod-homclass,results='asis', cache=T}
+```{r mod-homclass-binary,results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
                         class3,
@@
          age2=agenum^2) %>%
-  # filter(!country2 %in% c("CHN")) %>%
-  # filter(!country2 %in% c("TWN")) %>%
-  # filter(!country2 %in% c("JPN")) %>%
-  # filter(!country2 %in% c("ZAF")) %>%
-  # filter(!country2 %in% c("PHL")) %>%
-  # filter(!country2 %in% c("FIN")) %>%
-  # filter(!country2 %in% c("USA")) %>%
-  # filter(!country2 %in% c("GBR")) %>%
-  # filter(!country2 %in% c("ISL")) %>%
-  # filter(!country2 %in% c("TUR","EST")) %>%
-  # filter(!country2 %in% c("MEX")) %>%
-# filter(!country2 %in% c("HUN")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
-  # filter(PARTLIV %in% c(0,1,2,3)) %>%
-  # filter(!region %in% c("Northern America","South America")) %>%
-  # filter(Q03pcm!="Missing") %>%
-    # filter(oecd=="OECD") %>%
   na.omit()
@@
 # Models 
-base <- clmm(factor(redist)~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
 homclass<- update(base, . ~ . +homclass)
@@
 rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
-anova(rob1,rob2)
+# anova(rob1,rob2)
 # Interactions segregation x class
@@
 models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 
-```{r mod-intermacro,results='asis'}
+```{r mod-intermacro-binary,results='asis'}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+  list(
+    homclass = "Class-based network homogeneity",
+    logrgdpna = "log GDP",
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
+  )
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
+```
+
+## Strong ties
+
+```{r mod-homclass-binary-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r mod-intermacro-binary-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+  list(
+    homclass = "Class-based network homogeneity",
+    logrgdpna = "log GDP",
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
+  )
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
+```
+
+## Weak ties
+
+```{r mod-homclass-binary-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r mod-intermacro-binary-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  custom.gof.names = gof1
+                )
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+  list(
+    homclass = "Class-based network homogeneity",
+    logrgdpna = "log GDP",
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
+  )
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
+```
+
+# Ordinal
+
+## Full network
+
+```{r mod-homclass-ordinal,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
                         class3,
@@
          age2=agenum^2) %>%
-  # filter(!country2 %in% c("CHN")) %>%
-  # filter(!country2 %in% c("TWN")) %>%
-  # filter(!country2 %in% c("JPN")) %>%
-  # filter(!country2 %in% c("ZAF")) %>%
-  # filter(!country2 %in% c("PHL")) %>%
-  # filter(!country2 %in% c("FIN")) %>%
-  # filter(!country2 %in% c("USA")) %>%
-  # filter(!country2 %in% c("GBR")) %>%
-  # filter(!country2 %in% c("ISL")) %>%
-  # filter(!country2 %in% c("TUR","EST")) %>%
-  # filter(!country2 %in% c("MEX")) %>%
-# filter(!country2 %in% c("HUN")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
-  # filter(PARTLIV %in% c(0,1,2,3)) %>%
-  # filter(!region %in% c("Northern America","South America")) %>%
-  # filter(Q03pcm!="Missing") %>%
-    # filter(oecd=="OECD") %>%
   na.omit()
-# T03dim(dfreg)
 
+# Models 
+# base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+# homclass<- update(base, . ~ . +homclass)
+# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Bayesian ordinal logit
+# brms::brm()
+base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r mod-intermacro-ordinal,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
 main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
-base <- clmm(formula(main),data=dfreg,weights = WEIGHT)
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT,Hess = T)
 giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
@@
                 caption.above=T,float.pos="h!",
-                # include.thresholds=FALSE,
+                include.thresholds=FALSE,
                 custom.coef.map=list(homclass="Network Homogeneity",
@@
                 )
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- clmm(redistOR,data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+  list(
+    homclass = "Class-based network homogeneity",
+    logrgdpna = "log GDP",
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
+  )
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
 ```
 
-## Gov's spending and individualism
+## Strong ties
 
-```{r mod-spend-indv, results='asis'}
+```{r mod-homclass-ordinal-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+# base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+# homclass<- update(base, . ~ . +homclass)
+# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Bayesian ordinal logit
+# brms::brm()
+base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+```
+
+```{r mod-intermacro-ordinal-strong-ties,results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
                         class3,
-                        homclass=homclass_gc,
-                        # homclass=homclass_res,
-                        Q05pcm,
+                        homclass=homclass_s,
                         Q03pcm,
-                        gini_disp,
-                        gini_mkt,
-                        giniot=gini,
-                        giniindex,ttheilge1,
-                        gv_spen=gv_spen,
-                        top10,
-                        middle50,
-                        palmaratio,
-                        d10d1,
-                        rgdpna,
-                        individualism,
                         edyears,
@@
                         agenum,
-                        country2,
                         union,
-                        workst
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
                         ) %>% 
   mutate(logrgdpna=log(rgdpna),
-         age2=agenum^2,
-         edyears2=edyears^2) %>%
-    # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
   na.omit()
-int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
-models_m <- list(int_indivi,int_govspe)
-cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT,Hess = T)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- clmm(redistOR,data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
 customcoef <- 
-list(homclass = "Class-based network homogeneity",
+  list(
+    homclass = "Class-based network homogeneity",
     logrgdpna = "log GDP",
-  individualism         = "Individualism Index*",
-  "homclass:individualism" = "Homogeneity x Individualism",
-  gv_spen               = "Gov. Spending (% GDP)*",
-  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
   )
-texreg::knitreg(models_m,scalebox = 1,
+texreg::knitreg(models_m,scalebox = 0.75,
                 float.pos="h!",                
@@
                 caption.above = T,caption = cap1)
+
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
 ```
 
-```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
-p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
-  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))
+## Weak ties
 
-predval8 <- 
-plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
-       linetype='Individualism') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
+```{r mod-homclass-ordinal-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 
-p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
-  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
 
-predval9 <- 
-plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
-  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
-       linetype='Gov.Spend') +
-  xlab("Class-based homogeneity")+
-  ylab("Redistributive preferences") +
-  theme(legend.position = "right")
+# Models 
+# base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+# homclass<- update(base, . ~ . +homclass)
+# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Bayesian ordinal logit
+# brms::brm()
+base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
 
-grid.arrange(p9,predval9,
-             p8,predval8,nrow = 2)
+cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+coefgroup <- list("Social Class (ref: Service Class)"=2:3,
+                  "Income Tercile (ref: Low)"=4:5,
+                  "Homogeneity x Social Class"=9:10
+                  )
+gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
+gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(list = models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
+texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
+                                float.pos="h!",
+                  include.thresholds=FALSE,
+                  custom.coef.map=coefmap,
+                  groups = coefgroup,
+                  custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
 ```
+
+```{r mod-intermacro-ordinal-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT,Hess = T)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+texreg::knitreg(models,
+                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
+                caption.above=T,float.pos="h!",
+                include.thresholds=FALSE,
+                custom.coef.map=list(homclass="Network Homogeneity",
+                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
+                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
+                                     "gini_mkt"="Gini (Market) ",
+                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
+                  # groups = coefgroup,
+                  # custom.gof.rows=gofrow,
+                  include.loglik = FALSE,include.aic = FALSE,
+                  # custom.gof.names = gof1
+                )
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ logrgdpna +(homclass|country2)"
+base <- clmm(redistOR,data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+
+cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
+customcoef <- 
+  list(
+    homclass = "Class-based network homogeneity",
+    logrgdpna = "log GDP",
+    palmaratio = "Palma Ratio",
+    "homclass:palmawd" = "Homogeneity x Palma Ratio",
+    top10 = "Share National Income - top 10%",
+    "homclass:top10"= "Homogeneity x top 10",
+    middle50 = "Share National Income -  bottom 50%",
+    "homclass:middle50" = "Homogeneity x bottom 50",
+    d10d1 = "Ratio D10/D01",
+    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
+    giniindex = "Gini (World Bank)",
+    "homclass:giniindex" = "Homogeneity x Gini (WB)",
+    ttheilge1 = "Theil Index",
+    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
+  )
+texreg::knitreg(models_m,scalebox = 0.75,
+                float.pos="h!",                
+                custom.coef.map = customcoef,
+                caption.above = T,caption = cap1)
+
+save(list = list(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil),
+     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
+```

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # anova(rob1,rob2)
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
+save( models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 
-save(list = list(giniD_gdp,giniD_rs,giniD_int,
+save( list(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
+save( models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
+save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
+save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
                 caption.above = T,caption = cap1)
-save(list = list(giniD_gdp,giniD_rs,giniD_int,
+save( list(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
+save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(list = models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
+save( models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
 texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
@@
 
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
@@
 
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
@@
                 caption.above = T,caption = cap1)
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
@@
 
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
@@
 
-save( list(giniD_gdp,giniD_rs,giniD_int,
+save(giniD_gdp,giniD_rs,giniD_int,
                  giniM_gdp,giniM_rs,giniM_int,
                  int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil),
+                 int_gini_wiid,int_theil,
      file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
 models <- list(homclass,full1,rob1,int_homo)
 save( models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
 ```
@@
 
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
-                caption.above=T,float.pos="h!",
-                include.thresholds=FALSE,
-                custom.coef.map=list(homclass="Network Homogeneity",
-                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
-                                     "gini_mkt"="Gini (Market) ",
-                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
 # Homoclass x Other Economic Inequality-----------------------------------------
@@
                  )
-cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
-customcoef <- 
-  list(
-    homclass = "Class-based network homogeneity",
-    logrgdpna = "log GDP",
-    palmaratio = "Palma Ratio",
-    "homclass:palmawd" = "Homogeneity x Palma Ratio",
-    top10 = "Share National Income - top 10%",
-    "homclass:top10"= "Homogeneity x top 10",
-    middle50 = "Share National Income -  bottom 50%",
-    "homclass:middle50" = "Homogeneity x bottom 50",
-    d10d1 = "Ratio D10/D01",
-    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
-    giniindex = "Gini (World Bank)",
-    "homclass:giniindex" = "Homogeneity x Gini (WB)",
-    ttheilge1 = "Theil Index",
-    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
-  )
-texreg::knitreg(models_m,scalebox = 0.75,
-                float.pos="h!",                
-                custom.coef.map = customcoef,
-                caption.above = T,caption = cap1)
-
 save(giniD_gdp,giniD_rs,giniD_int,
@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
+save(models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
 ```
@@
 
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
-                caption.above=T,float.pos="h!",
-                include.thresholds=FALSE,
-                custom.coef.map=list(homclass="Network Homogeneity",
-                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
-                                     "gini_mkt"="Gini (Market) ",
-                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
 # Homoclass x Other Economic Inequality-----------------------------------------
@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
 models <- list(homclass,full1,rob1,int_homo)
 save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
 ```
@@
                giniM_gdp,giniM_rs,giniM_int)
-
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
-                caption.above=T,float.pos="h!",
-                include.thresholds=FALSE,
-                custom.coef.map=list(homclass="Network Homogeneity",
-                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
-                                     "gini_mkt"="Gini (Market) ",
-                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  custom.gof.names = gof1
-                )
-
 # Homoclass x Other Economic Inequality-----------------------------------------
@@
 int_homo <- update(rob1, . ~ . +class3*homclass)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
 models <- list(homclass,full1,rob1,int_homo)
 save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
 ```
@@
 
-texreg::knitreg(models,
-                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Network homogeneity and Economic Inequality"),
-                caption.above=T,float.pos="h!",
-                include.thresholds=FALSE,
-                custom.coef.map=list(homclass="Network Homogeneity",
-                                     logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
-                                     "homclass:gini_disp"="Homogeneity x Gini (D)",
-                                     "gini_mkt"="Gini (Market) ",
-                                     "homclass:gini_mkt"="Homogeneity x Gini (M)"),
-                  # groups = coefgroup,
-                  # custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
-
 # Homoclass x Other Economic Inequality-----------------------------------------
@@
 
-cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
-customcoef <- 
-  list(
-    homclass = "Class-based network homogeneity",
-    logrgdpna = "log GDP",
-    palmaratio = "Palma Ratio",
-    "homclass:palmawd" = "Homogeneity x Palma Ratio",
-    top10 = "Share National Income - top 10%",
-    "homclass:top10"= "Homogeneity x top 10",
-    middle50 = "Share National Income -  bottom 50%",
-    "homclass:middle50" = "Homogeneity x bottom 50",
-    d10d1 = "Ratio D10/D01",
-    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
-    giniindex = "Gini (World Bank)",
-    "homclass:giniindex" = "Homogeneity x Gini (WB)",
-    ttheilge1 = "Theil Index",
-    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
-  )
-texreg::knitreg(models_m,scalebox = 0.75,
-                float.pos="h!",                
-                custom.coef.map = customcoef,
-                caption.above = T,caption = cap1)
 save(giniD_gdp,giniD_rs,giniD_int,
@@
 
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
-
 models <- list(homclass,full1,rob1,int_homo)
 save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
 ```
@@
                  )
-
-cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
-customcoef <- 
-  list(
-    homclass = "Class-based network homogeneity",
-    logrgdpna = "log GDP",
-    palmaratio = "Palma Ratio",
-    "homclass:palmawd" = "Homogeneity x Palma Ratio",
-    top10 = "Share National Income - top 10%",
-    "homclass:top10"= "Homogeneity x top 10",
-    middle50 = "Share National Income -  bottom 50%",
-    "homclass:middle50" = "Homogeneity x bottom 50",
-    d10d1 = "Ratio D10/D01",
-    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
-    giniindex = "Gini (World Bank)",
-    "homclass:giniindex" = "Homogeneity x Gini (WB)",
-    ttheilge1 = "Theil Index",
-    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
-  )
-texreg::knitreg(models_m,scalebox = 0.75,
-                float.pos="h!",                
-                custom.coef.map = customcoef,
-                caption.above = T,caption = cap1)
-
 save(giniD_gdp,giniD_rs,giniD_int,
@@
 int_homo <- update(rob1, . ~ . +class3*homclass)
-
-cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
-coefmap <-  list(homclass ="Class-based network homogeneity",
-                 'class3Intermediate class (III+IV)' ='Intermediate Class',
-                 'class3Working Class (V+VI+VII)' ='Working Class',
-                 "Q03pcmT02" = "Middle",
-                 "Q03pcmT03" = "High",
-                 "edyears" = 'Education in years',
-                 "workstNot in paid work"="Not in labor force",
-                 "unionYes" = 'Union membership: Yes',
-                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
-                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
-                 )
-coefgroup <- list("Social Class (ref: Service Class)"=2:3,
-                  "Income Tercile (ref: Low)"=4:5,
-                  "Homogeneity x Social Class"=9:10
-                  )
-gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
-gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)
 

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
binary logit models

@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
+save(models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
+     file = here::here("output/fullsample-logit-homclass-full-macro.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save(models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
+save(models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
+     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
+save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
+     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
+save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
+     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
+save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
+     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
-texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
-                                float.pos="h!",
-                  include.thresholds=FALSE,
-                  custom.coef.map=coefmap,
-                  groups = coefgroup,
-                  custom.gof.rows=gofrow,
-                  include.loglik = FALSE,include.aic = FALSE,
-                  # custom.gof.names = gof1
-                )
+save( models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"),compress = "gzip")
 ```
@@
                  int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
+     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"),compress = "gzip")
 ```

### 2023-10-23 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 # Models 
-# base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Bayesian ordinal logit
+# brms::brm()
+# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
 # homclass<- update(base, . ~ . +homclass)
@@
 # rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# Bayesian ordinal logit
-# brms::brm()
-base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
-homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # Interactions segregation x class
@@
 
-# Models 
-# base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+## Models 
+base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# Bayesian ordinal logit
+# brms::brm()
+# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
 # homclass<- update(base, . ~ . +homclass)

### 2023-10-23 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 # Models 
-base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
 homclass<- update(base, . ~ . +homclass)
@@
 rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # Bayesian ordinal logit
@@
 ## Models 
-base <- clmm(redistF~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
 homclass<- update(base, . ~ . +homclass)

### 2023-10-23 paper.Rmd
ajustes

@@
   geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
@@
          age2=agenum^2) %>%
-  # filter(!country2 %in% c("CHN")) %>%
-  # filter(!country2 %in% c("TWN")) %>%
-  # filter(!country2 %in% c("JPN")) %>%
-  # filter(!country2 %in% c("ZAF")) %>%
-  # filter(!country2 %in% c("PHL")) %>%
-  # filter(!country2 %in% c("FIN")) %>%
-  # filter(!country2 %in% c("USA")) %>%
-  # filter(!country2 %in% c("GBR")) %>%
-  # filter(!country2 %in% c("ISL")) %>%
-  # filter(!country2 %in% c("TUR","EST")) %>%
-  # filter(!country2 %in% c("MEX")) %>%
-# filter(!country2 %in% c("HUN")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
-  # filter(PARTLIV %in% c(0,1,2,3)) %>%
-  # filter(!region %in% c("Northern America","South America")) %>%
-  # filter(Q03pcm!="Missing") %>%
-    filter(oecd=="OECD") %>%
   na.omit()
@@
 giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
-summary(giniM_int)
+# summary(giniM_int)
 models <- list(giniD_gdp,giniD_rs,giniD_int,
@@
          edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("CHN")) %>%
-  # filter(!country2 %in% c("TWN")) %>%
-  # filter(!country2 %in% c("ZAF")) %>%
-  # filter(!country2 %in% c("FIN")) %>%
-  # filter(!country2 %in% c("USA")) %>%
-  # filter(!country2 %in% c("GBR")) %>%
-  # filter(!country2 %in% c("ISL")) %>%
-  # filter(!country2 %in% c("TUR","EST")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
-  # filter(PARTLIV %in% c(0,1,2,3)) %>%
-  # filter(region %in% c("Northern America","South America")) %>%
-  # filter(Q03pcm!="Missing") %>%
   na.omit()
@@
                         homclass=homclass_gc,
-                        # homclass=eindex,
-                        # homclass=ingroup,
                         Q05pcm,
@@
                         gini_mkt,
-                        # giniot=gini,
-                        # giniot=gv_spen,
                         rgdpna,
@@
          edyears2=edyears^2) %>%
-  # filter(!country2 %in% c("Turkey","Estonia")) %>%
-  # filter(MAINSTAT %in% c(1,2)) %>%
-  # filter(agenum %in% c(25:65)) %>%
   na.omit()
@@
 main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2"
-
 giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
@@
 \pagebreak
+
 ```{r crosslevel-egal}

### 2023-10-23 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

@@
 options(scipen=9999) # desactivar notacion cientifica
+```
+
+# Numeric
+
+## Full network
+
+```{r mod-homclass-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-numeric-homclass-full-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                               class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-numeric-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-numeric-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-numeric-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Strong ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-numeric-homclass-strong-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-numeric-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-numeric-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-numeric-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Weak ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-numeric-homclass-weak-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-numeric-homclass-weak-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-numeric-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-numeric-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
 ```
@@
 
+```{r}
+load(here::here("output/fullsample-logit-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
 ## Strong ties
@@
      file = here::here("output/fullsample-logit-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-logit-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
 ```
@@
 
+```{r}
+load(here::here("output/fullsample-logit-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
 # Ordinal
@@
 # Homoclass x Gini--------------------------------------------------------------
-main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
+main <- "redistOR~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
 base <- clmm(formula(main),data=dfreg,weights = WEIGHT,Hess = T)
@@
      file = here::here("output/fullsample-ologit-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-ologit-homclass-full-individual.RData"))
+texreg::knitreg(models)
 ```
@@
      file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
+texreg::knitreg(models)
 ```
@@
 ```
+
+```{r}
+load(here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+```

### 2023-10-24 procesamiento/prod_analysis-full-sample.Rmd
ologit en stata

@@
 # Numeric
+<!----------------------------------------------------------------------------->
 
@@
 ```
+## R's class
+
+```{r mod-homclass-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        homclass,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-numeric-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-numeric-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-numeric-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-numeric-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
 
 # Binary logit 
+<!----------------------------------------------------------------------------->
 
@@
 
+## R's class
+
+```{r mod-homclass-binary-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        homclass=homclass_res,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-binary-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-binary-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        homclass=homclass_res,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-binary-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-binary-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-binary-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
 # Ordinal 
+<!----------------------------------------------------------------------------->
 
@@
 
-```{r mod-intermacro-ordinal,results='asis'}
+```{r mod-intermacro-ordinal, eval=FALSE, include=FALSE, results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 
-```{r mod-intermacro-ordinal-strong-ties,results='asis'}
+```{r mod-intermacro-ordinal-strong-ties, eval=FALSE, include=FALSE, results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 
-```{r mod-intermacro-ordinal-weak-ties,results='asis'}
+```{r mod-intermacro-ordinal-weak-ties, eval=FALSE, include=FALSE, results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 ```
+
+## R's class
+
+```{r mod-homclass-ologit-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3=class3res,
+                        homclass=homclass_res,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-ologit-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-ologit-respondent, eval=FALSE, include=FALSE, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistOR <- ordered(x = df1$redist)
+dfreg <- df1 %>% dplyr::select(redistOR,
+                        class3=class3res,
+                        class3spo,
+                        homclass=homclass_res,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redistOR~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- clmm(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-ologit-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-ologit-homclass-respondent.RData"))
+texreg::knitreg(models)
+```
+
+# Ologit Stata
+
+See https://ignacioriveros1.github.io/r/2020/03/22/r_and_stata.html
+
+```{r}
+# install.packages('RStata')
+library(RStata) 
+options("RStata.StataPath" = "C:/Stata15/Stata-64")
+options("RStata.StataVersion" = 15)
+
+stata('estimates use output/fullsample-ologit-homclass-respondent-macro')
+
+```

### 2023-10-24 procesamiento/prod_prep-macro.Rmd
ologit en stata

@@
 save(df2,file = here::here("input/data/proc/study1_country.RData"))
+haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
 sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )

### 2023-10-24 procesamiento/prod_prep.Rmd
ologit en stata

@@
                          recodes= "1:2='Yes';c(0,3,7)='No';8:9=NA",
-                         levels = c("No","Yes"))
+                         levels = c("No","Yes"),as.factor = T)
 frq(df1$union)

### 2023-10-25 procesamiento/prod_analysis-full-sample.Rmd
update

@@
 
-stata('estimates use output/fullsample-ologit-homclass-respondent-macro')
-
-```
+stata("")
+
+clear all
+eret list
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(1)
+estimates store model1
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(2)
+estimates store model2
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(3)
+estimates store model3
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(4)
+estimates store model4
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(5)
+estimates store model5
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(6)
+estimates store model6
+estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(7)
+estimates store model7
+
+esttab model1 model2 model3 model4 model5 model6 model7, drop(logrgdpna 1.class3 2.class3 3.class3 female agenum edyears workst union 1.Q03pcm 2.Q03pcm 3.Q03pcm 4.Q03pcm )
+
+```

### 2023-10-25 procesamiento/prod_prep.Rmd
Update prod_prep.Rmd

@@
 Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+
+# Group means
+df1 <- df1 %>% group_by(country) %>% mutate(eindex_gm=mean(eindex,na.rm=T),
+                                            homclass_gm=mean(homclass,na.rm=T))  
 ```
@@
 
+# Group means
+df1 <- df1 %>% group_by(country) %>% mutate(eindex2_gm=mean(eindex2,na.rm=T),
+                                            homclass2_gm=mean(homclass2,na.rm=T))
 ```

### 2023-10-26 procesamiento/prod_analysis-tables-macro.Rmd
update main analysis and robustness

---
title: "Cross-level interactions"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```

```{css}
body {
    text-align: initial;
    font-size: 20px;
    font-family: "Times New Roman", Times, serif;
}
```

## All countries

```{r full-lmer-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

load(here::here("output/fullsample-numeric-homclass-full-macro.RData"));fsample_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/fullsample-numeric-homclass-strong-macro.RData"));fsample_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/fullsample-numeric-homclass-weak-macro.RData")); fsample_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

htmlreg(
  c(fsample_num_full_mac,fsample_num_strong_mac,fsample_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

```{r full-clmm-macro,results='asis'}

```

## Non-confusian

```{r nonconfusian-lmer-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
load(here::here("output/nonconfusian-numeric-homclass-full-macro.RData")); nconf_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/nonconfusian-numeric-homclass-strong-macro.RData"));nconf_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/nonconfusian-numeric-homclass-weak-macro.RData")); nconf_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

htmlreg(
  c(nconf_num_full_mac,nconf_num_strong_mac,nconf_num_weak_mac),
  caption = "Multilevel linear regression: Non-confusian country sample cross-level interaction",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

```{r nonconfusian-clmm-macro,results='asis'}

```

## OECD

```{r ocde-lmer-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
load(here::here("output/ocde-numeric-homclass-full-macro.RData")); ocde_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/ocde-numeric-homclass-strong-macro.RData"));ocde_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/ocde-numeric-homclass-weak-macro.RData")); ocde_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

htmlreg(
  c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
  caption = "Multilevel linear regression: OECD country sample cross-level interaction",
  custom.coef.map= coef_map,
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

```{r oecd-clmm-macro,results='asis'}

```

### 2023-10-26 procesamiento/prod_analysis-tables-micro.Rmd
update main analysis and robustness

---
title: "Additional analyses"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```

## All countries

```{r full-lmer-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/fullsample-numeric-homclass-full-individual.RData")); fsample_num_full_ind<- models
load(here::here("output/fullsample-numeric-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
load(here::here("output/fullsample-numeric-homclass-weak-individual.RData")); fsample_num_weak_ind<- models

htmlreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: full country sample",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

```{r full-clmm-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg,ordinal)  
rm(list=ls())

load(here::here("output/fullsample-ologit-homclass-full-individual.RData"));fsample_ologit_full_ind<- models
load(here::here("output/fullsample-ologit-homclass-strong-individual.RData"));fsample_ologit_strong_ind<- models
load(here::here("output/fullsample-ologit-homclass-weak-individual.RData"));fsample_ologit_weak_ind<- models

htmlreg(
  c(fsample_ologit_full_ind,
    fsample_ologit_strong_ind,
    fsample_ologit_weak_ind),
  include.threshold=F,
  caption = "Multilevel ordinal logistic regression: full country sample",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

## Non-confusian

```{r nonconfusian-lmer-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/nonconfusian-numeric-homclass-full-individual.RData")); nconf_num_full_ind<- models
load(here::here("output/nonconfusian-numeric-homclass-strong-individual.RData"));nconf_num_strong_ind<- models
load(here::here("output/nonconfusian-numeric-homclass-weak-individual.RData")); nconf_num_weak_ind<- models

htmlreg(
  c(nconf_num_full_ind,nconf_num_strong_ind,nconf_num_weak_ind),
  caption = "Multilevel linear regression: Non-confusian country sample",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

```{r nonconfusian-clmm-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg,ordinal)  
rm(list=ls())

load(here::here("output/nonconfusian-ologit-homclass-full-individual.RData"));nconf_ologit_full_ind<- models
load(here::here("output/nonconfusian-ologit-homclass-strong-individual.RData"));nconf_ologit_strong_ind<- models
load(here::here("output/nonconfusian-ologit-homclass-weak-individual.RData"));nconf_ologit_weak_ind<- models

htmlreg(
  c(nconf_ologit_full_ind,
    nconf_ologit_strong_ind,
    nconf_ologit_weak_ind),
  include.threshold=F,
  caption = "Multilevel ordinal logistic regression: Non-confusian country sample",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

## OECD

```{r ocde-lmer-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/ocde-numeric-homclass-full-individual.RData")); ocde_num_full_ind<- models
load(here::here("output/ocde-numeric-homclass-strong-individual.RData"));ocde_num_strong_ind<- models
load(here::here("output/ocde-numeric-homclass-weak-individual.RData")); ocde_num_weak_ind<- models

htmlreg(
  c(ocde_num_full_ind,ocde_num_strong_ind,ocde_num_weak_ind),
  caption = "Multilevel linear regression: OECD country sample",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

```{r oecd-clmm-micro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/ocde-ologit-homclass-full-individual.RData")); ocde_ologit_full_ind<- models
load(here::here("output/ocde-ologit-homclass-strong-individual.RData"));ocde_ologit_strong_ind<- models
load(here::here("output/ocde-ologit-homclass-weak-individual.RData")); ocde_ologit_weak_ind<- models

htmlreg(
  c(ocde_ologit_full_ind,ocde_ologit_strong_ind,ocde_ologit_weak_ind),
  caption = "Multilevel ordinal logistic regression: OECD country sample",
  caption.above = T,
  include.threshold=F,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

### 2023-10-27 procesamiento/prod_analysis-tables-macro.Rmd
modelos ordinales macro

@@
 ---
-title: "Cross-level interactions"
-subtitle: "Full sample"
+title: "Additional analyses"
+subtitle: "Cross-level interactions"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
 ```{r full-clmm-macro,results='asis'}
-
+htmltools::includeHTML("../output/fullsample-ologit-homclass-full-strong-weak-macro.html")
 ```

### 2023-10-27 procesamiento/prod_analysis-tables-micro.Rmd
modelos ordinales macro

@@
 title: "Additional analyses"
-subtitle: "Full sample"
+subtitle: "Micro level"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"

### 2023-10-29 procesamiento/prod_analysis-full-sample.Rmd

--- 2023-10-24 procesamiento/prod_analysis-full-sample.Rmd
@@
 ---
-title: "Multilevel regression models"
+title: "Multilevel regression models micro level"
 subtitle: "Full sample"
@@
 main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
 giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
@@
 main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
 int_palma <- update(base, . ~ . +homclass*palmaratio)
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"),compress = "gzip")
+save(models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"),compress = "gzip")
 ```
@@
 models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"),compress = "gzip")
+save(models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"),compress = "gzip")
 ```
@@
 ```
-
-# Ologit Stata
-
-See https://ignacioriveros1.github.io/r/2020/03/22/r_and_stata.html
-
-```{r}
-# install.packages('RStata')
-library(RStata) 
-options("RStata.StataPath" = "C:/Stata15/Stata-64")
-options("RStata.StataVersion" = 15)
-
-stata('estimates use output/fullsample-ologit-homclass-respondent-macro')
-
-```

### 2023-10-29 procesamiento/prod_analysis-non-confusian-sample.Rmd

---
title: "Multilevel regression models"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica

c("TWN","CHN","JPN")
```

# Numeric
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-numeric-homclass-full-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                               class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
# summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-numeric-homclass-full-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-numeric-homclass-full-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-numeric-homclass-full-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```
## Strong ties

```{r mod-homclass-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-numeric-homclass-strong-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-numeric-homclass-strong-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-numeric-homclass-strong-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-numeric-homclass-strong-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Weak ties

```{r mod-homclass-numeric-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-numeric-homclass-weak-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-numeric-homclass-weak-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-numeric-homclass-weak-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-numeric-homclass-weak-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```
## R's class

```{r mod-homclass-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        homclass,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-numeric-homclass-respondent.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        class3spo,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-numeric-homclass-respondent-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-numeric-homclass-respondent.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-numeric-homclass-respondent-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

# Binary logit 
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-binary,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-logit-homclass-full-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-logit-homclass-full-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-logit-homclass-full-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-logit-homclass-full-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Strong ties

```{r mod-homclass-binary-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-logit-homclass-strong-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-logit-homclass-strong-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-logit-homclass-strong-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-logit-homclass-strong-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Weak ties

```{r mod-homclass-binary-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/nonconfusian-logit-homclass-weak-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)
# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-logit-homclass-weak-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-logit-homclass-weak-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-logit-homclass-weak-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## R's class

```{r mod-homclass-binary-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        homclass=homclass_res,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-binary-homclass-respondent.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        class3spo,
                        homclass=homclass_res,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-binary-homclass-respondent-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-binary-homclass-respondent.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-binary-homclass-respondent-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

# Ordinal 
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-ordinal,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)
models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-ologit-homclass-full-individual.RData"),compress = "gzip")
```

## Strong ties

```{r mod-homclass-ordinal-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

## Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-ologit-homclass-strong-individual.RData"),compress = "gzip")
```

## Weak ties

```{r mod-homclass-ordinal-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/nonconfusian-ologit-homclass-weak-individual.RData"),compress = "gzip")
```

## R's class

```{r mod-homclass-ologit-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3=class3res,
                        homclass=homclass_res,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN")) %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-ologit-homclass-respondent.RData"),compress = "gzip")
```

### 2023-10-29 procesamiento/prod_analysis-ocde-sample.Rmd

---
title: "Multilevel regression models"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica

c("TWN","CHN","JPN")
```

# Numeric
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-numeric-homclass-full-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                               class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
# summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-numeric-homclass-full-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-numeric-homclass-full-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-numeric-homclass-full-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```
## Strong ties

```{r mod-homclass-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-numeric-homclass-strong-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-numeric-homclass-strong-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-numeric-homclass-strong-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-numeric-homclass-strong-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Weak ties

```{r mod-homclass-numeric-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-numeric-homclass-weak-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-numeric-homclass-weak-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-numeric-homclass-weak-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-numeric-homclass-weak-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```
## R's class

```{r mod-homclass-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        homclass,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-numeric-homclass-respondent.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        class3spo,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-numeric-homclass-respondent-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-numeric-homclass-respondent.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-numeric-homclass-respondent-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

# Binary logit 
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-binary,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-logit-homclass-full-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-logit-homclass-full-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-logit-homclass-full-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-logit-homclass-full-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Strong ties

```{r mod-homclass-binary-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-logit-homclass-strong-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-logit-homclass-strong-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-logit-homclass-strong-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-logit-homclass-strong-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## Weak ties

```{r mod-homclass-binary-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/ocde-logit-homclass-weak-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)
# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-logit-homclass-weak-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-logit-homclass-weak-individual.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-logit-homclass-weak-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

## R's class

```{r mod-homclass-binary-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        homclass=homclass_res,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-binary-homclass-respondent.RData"),compress = "gzip")
```

```{r mod-intermacro-binary-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=class3res,
                        class3spo,
                        homclass=homclass_res,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/ocde-binary-homclass-respondent-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/ocde-binary-homclass-respondent.RData"))
texreg::knitreg(models)

load(here::here("output/ocde-binary-homclass-respondent-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

# Ordinal 
<!----------------------------------------------------------------------------->

## Full network

```{r mod-homclass-ordinal,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)
models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-ologit-homclass-full-individual.RData"),compress = "gzip")
```

## Strong ties

```{r mod-homclass-ordinal-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

## Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-ologit-homclass-strong-individual.RData"),compress = "gzip")
```

## Weak ties

```{r mod-homclass-ordinal-weak-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,haven,ordinal,brms)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Bayesian ordinal logit
# brms::brm()
# base <- brm(redistOR~1 + (1|country2),data=dfreg,family=cumulative("logit"))
# homclass<- update(base, . ~ . +homclass)
# full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
# rob1 <- update(full1, . ~ . + edyears+ Q03pcm+union+workst)
# rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/ocde-ologit-homclass-weak-individual.RData"),compress = "gzip")
```

## R's class

```{r mod-homclass-ologit-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistOR <- ordered(x = df1$redist)
dfreg <- df1 %>% dplyr::select(redistOR,
                        class3=class3res,
                        homclass=homclass_res,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(oecd=="OECD") %>% 
  na.omit()

# Models 
base <- clmm(redistOR~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/ocde-ologit-homclass-respondent.RData"),compress = "gzip")
```

### 2023-10-29 procesamiento/prod_analysis.Rmd
medidas de clase social

@@
 ```
+
+# Check on homogeneity
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,haven,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1_country.RData"))
+
+test <- df2
+
+frq(df2$class11d)
+
+test$egp3_v1 <- car::recode(test$class11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
+test$egp3_v2 <- car::recode(test$digclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
+test$egp3_v3 <- car::recode(test$dclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
+
+frq(test$egp3_v1)
+frq(test$egp3_v2)
+frq(test$egp3_v3)
+frq(test$class3)
+
+test$ingroup1 <- NA 
+test$ingroup1 <- ifelse(test$egp3_v1==1,test$n_high,test$ingroup1)
+test$ingroup1 <- ifelse(test$egp3_v1==2,test$n_middle,test$ingroup1)
+test$ingroup1 <- ifelse(test$egp3_v1==3,test$n_low,test$ingroup1)
+
+test$ingroup2 <- NA 
+test$ingroup2 <- ifelse(test$egp3_v2==1,test$n_high,test$ingroup2)
+test$ingroup2 <- ifelse(test$egp3_v2==2,test$n_middle,test$ingroup2)
+test$ingroup2 <- ifelse(test$egp3_v2==3,test$n_low,test$ingroup2)
+
+test$ingroup3 <- NA 
+test$ingroup3 <- ifelse(test$egp3_v3==1,test$n_high,test$ingroup2)
+test$ingroup3 <- ifelse(test$egp3_v3==2,test$n_middle,test$ingroup2)
+test$ingroup3 <- ifelse(test$egp3_v3==3,test$n_low,test$ingroup2)
+
+test$homclass_v1 <- as.numeric(test$ingroup1/test$know_total)
+
+test$homclass_v2 <- as.numeric(test$ingroup2/test$know_total)
+
+test$homclass_v3 <- as.numeric(test$ingroup3/test$know_total)
+
+sjPlot::plot_frq(test$homclass_v1,type = "density")
+sjPlot::plot_frq(test$homclass_v2,type = "density")
+sjPlot::plot_frq(test$homclass_v3,type = "density")
+sjPlot::plot_frq(df2$homclass)
+```
+
+```{r}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- test %>% dplyr::select(
+                        class3=class6,
+                        homclass=homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- lmer(homclass~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +class3)
+full1 <- update(homclass, . ~ . + female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+knitreg(list(homclass,full1,rob1))
+```

### 2023-10-29 procesamiento/prod_prep.Rmd
medidas de clase social

@@
                             "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV)';
-                             8:11='Working Class (V+VI+VII)'")
+                             3:7='Intermediate class (III+IV+V)';
+                             8:11='Working Class (VI+VII)'")
 

### 2023-10-30 procesamiento/prod_analysis-full-sample.Rmd
lunes

@@
 ```
+
+# Numeric -  Egalitarian Attitudes Index
+
+Cronbach's alpha is 0.7 for:
+
+1. It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes. 
+2. For a society to be fair, differences in people's standard of living should be small.
+
+Note: the item "Differences in income in [COUNTRY] are too large" is not included because of two reasons.
+First, the item is fuzzy in terms of what is it measuring, "are" refers to a perception about inequality and "too large" as a normative judgement.
+Second, the literature has addressed this indicator as perceived or concerns about inequality.
+
+<!----------------------------------------------------------------------------->
+
+## Full network
+
+```{r mod-homclass-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+                        egal=egal2,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+knitreg(models)
+save(models,file = here::here("output/fullsample-egalitarian-homclass-full-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                               class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+# summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-egalitarian-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-egalitarian-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-egalitarian-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Strong ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%  
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-egalitarian-homclass-strong-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-egalitarian-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-egalitarian-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-egalitarian-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Weak ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-egalitarian-homclass-weak-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-egalitarian-homclass-weak-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-egalitarian-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-egalitarian-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+## R's class
+
+```{r mod-homclass-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        homclass,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-egalitarian-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        class3spo,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-egalitarian-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-egalitarian-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-egalitarian-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```

### 2023-10-30 procesamiento/prod_analysis-non-confusian-sample.Rmd
lunes

@@
 ```
+
+# Numeric -  Egalitarian Attitudes Index
+
+Cronbach's alpha is 0.7 for:
+
+1. It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes. 
+2. For a society to be fair, differences in people's standard of living should be small.
+
+Note: the item "Differences in income in [COUNTRY] are too large" is not included because of two reasons.
+First, the item is fuzzy in terms of what is it measuring, "are" refers to a perception about inequality and "too large" as a normative judgement.
+Second, the literature has addressed this indicator as perceived or concerns about inequality.
+
+<!----------------------------------------------------------------------------->
+
+## Full network
+
+```{r mod-homclass-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+                        egal=egal2,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+knitreg(models)
+save(models,file = here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                               class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+# summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Strong ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%  
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Weak ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+## R's class
+
+```{r mod-homclass-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        homclass=homclass_res,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(!country2 %in% c("TWN","CHN","JPN","SLV"))
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/nonconfusian-egalitarian-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        class3spo,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(!country2 %in% c("TWN","CHN","JPN","SLV"))
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+class3spo+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/nonconfusian-egalitarian-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/nonconfusian-egalitarian-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/nonconfusian-egalitarian-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```

### 2023-10-30 procesamiento/prod_analysis-tables-macro.Rmd
lunes

@@
 
+```{r full-lmer-macro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+coef_map <-
+  list(
+    homclass = "Homogeneity",
+    logrgdpna = "log GDP",
+    "gini_disp" = "GiniD ",
+    "homclass:gini_disp" = "Hom:Gini(D)",
+    "gini_mkt" = "Gini(M) ",
+    "homclass:gini_mkt" = "Hom:Gini(M)",
+    palmaratio               = "Palma",
+    "homclass:palmawd"      = "Hom:Palma",
+    top10             = "Top 10%",
+    "homclass:top10"    = "Hom:top10",
+    middle50             = "Bott.50%",
+    "homclass:middle50"    = "Hom:bott50",
+    d10d1             = "D10/D01",
+    "homclass:d10d1"    = "Hom:D10D01",
+    giniindex             = "Gini(WIID)",
+    "homclass:giniindex"    = "Hom:Gini(WD)",
+    ttheilge1             = "Theil",
+    "homclass:ttheilge1"    = "Hom:Theil"
+  )
+
+load(here::here("output/fullsample-egalitarian-homclass-full-macro.RData"));fsample_egal_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/fullsample-egalitarian-homclass-strong-macro.RData"));fsample_egal_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/fullsample-egalitarian-homclass-weak-macro.RData")); fsample_egal_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+
+htmlreg(
+  c(fsample_egal_full_mac,fsample_egal_strong_mac,fsample_egal_weak_mac),
+  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
+  caption.above = T,
+  custom.coef.map= coef_map,
+  custom.header = 
+    list(
+      "Full network"=1:8,
+      "Strong ties"=9:16,
+      "Weak ties"=17:24
+      ))
+```
+
 ## Non-confusian
@@
 
+```
+
+```{r nonconfusian-lmer-egalitarian-macro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+coef_map <-
+  list(
+    homclass = "Homogeneity",
+    logrgdpna = "log GDP",
+    "gini_disp" = "GiniD ",
+    "homclass:gini_disp" = "Hom:Gini(D)",
+    "gini_mkt" = "Gini(M) ",
+    "homclass:gini_mkt" = "Hom:Gini(M)",
+    palmaratio               = "Palma",
+    "homclass:palmawd"      = "Hom:Palma",
+    top10             = "Top 10%",
+    "homclass:top10"    = "Hom:top10",
+    middle50             = "Bott.50%",
+    "homclass:middle50"    = "Hom:bott50",
+    d10d1             = "D10/D01",
+    "homclass:d10d1"    = "Hom:D10D01",
+    giniindex             = "Gini(WIID)",
+    "homclass:giniindex"    = "Hom:Gini(WD)",
+    ttheilge1             = "Theil",
+    "homclass:ttheilge1"    = "Hom:Theil"
+  )
+
+load(here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"));nconf_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"));nconf_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData")); nconf_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+
+htmlreg(
+  c(nconf_num_full_mac,nconf_num_strong_mac,nconf_num_weak_mac),
+  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
+  caption.above = T,
+  custom.coef.map= coef_map,
+  custom.header = 
+    list(
+      "Full network"=1:8,
+      "Strong ties"=9:16,
+      "Weak ties"=17:24
+      ))
 ```
@@
 ```
+
+```{r ocde-lmer-egalitarian-macro,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+coef_map <-
+  list(
+    homclass = "Homogeneity",
+    logrgdpna = "log GDP",
+    "gini_disp" = "GiniD ",
+    "homclass:gini_disp" = "Hom:Gini(D)",
+    "gini_mkt" = "Gini(M) ",
+    "homclass:gini_mkt" = "Hom:Gini(M)",
+    palmaratio               = "Palma",
+    "homclass:palmawd"      = "Hom:Palma",
+    top10             = "Top 10%",
+    "homclass:top10"    = "Hom:top10",
+    middle50             = "Bott.50%",
+    "homclass:middle50"    = "Hom:bott50",
+    d10d1             = "D10/D01",
+    "homclass:d10d1"    = "Hom:D10D01",
+    giniindex             = "Gini(WIID)",
+    "homclass:giniindex"    = "Hom:Gini(WD)",
+    ttheilge1             = "Theil",
+    "homclass:ttheilge1"    = "Hom:Theil"
+  )
+
+load(here::here("output/ocde-egalitarian-homclass-full-macro.RData"));ocde_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/ocde-egalitarian-homclass-strong-macro.RData"));ocde_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+load(here::here("output/ocde-egalitarian-homclass-weak-macro.RData")); ocde_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+
+htmlreg(
+  c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
+  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
+  caption.above = T,
+  custom.coef.map= coef_map,
+  custom.header = 
+    list(
+      "Full network"=1:8,
+      "Strong ties"=9:16,
+      "Weak ties"=17:24
+      ))
+```

### 2023-10-30 procesamiento/prod_analysis-tables-micro.Rmd
lunes

@@
 
+```{r full-lmer-micro-egalitarian,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+
+load(here::here("output/fullsample-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
+load(here::here("output/fullsample-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
+load(here::here("output/fullsample-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models
+
+htmlreg(
+  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
+  caption = "Multilevel linear regression: full country sample - egalitarian preferences index",
+  caption.above = T,
+  custom.header = 
+    list(
+      "Full network"=1:4,
+      "Strong ties"=5:8,
+      "Weak ties"=9:12
+      ))
+```
+
 ## Non-confusian
@@
   caption = "Multilevel ordinal logistic regression: Non-confusian country sample",
+  caption.above = T,
+  custom.header = 
+    list(
+      "Full network"=1:4,
+      "Strong ties"=5:8,
+      "Weak ties"=9:12
+      ))
+```
+
+```{r nonconfusian-lmer-micro-egalitarian,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+
+load(here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
+load(here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
+load(here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models
+
+knitreg(
+  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
+  caption = "Multilevel linear regression: Non-confusian sample - egalitarian preferences index",
   caption.above = T,
@@
 ```
+
+```{r oecd-lmer-micro-egalitarian,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,texreg)  
+rm(list=ls())
+
+load(here::here("output/ocde-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
+load(here::here("output/ocde-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
+load(here::here("output/ocde-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models
+
+knitreg(
+  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
+  caption = "Multilevel linear regression: OECD country sample - egalitarian preferences index",
+  caption.above = T,
+  custom.header = 
+    list(
+      "Full network"=1:4,
+      "Strong ties"=5:8,
+      "Weak ties"=9:12
+      ))
+```

### 2023-10-30 procesamiento/prod_analysis.Rmd
lunes

--- 2023-09-19 procesamiento/prod_analysis.Rmd
@@
 ```
+
+# Check on homogeneity
+
+```{r}
+if (!require("pacman")) install.packages("pacman") # instalar pacman
+pacman::p_load(dplyr,haven,sjmisc,GGally,ggplot2)
+load(here::here("input/data/proc/study1_country.RData"))
+
+test <- df2
+frq(df2$class11d)
+test$egp3_v1 <- car::recode(test$class11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
+test$egp3_v2 <- car::recode(test$digclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
+
+# I   II IIIa IIIb  IVa  IVb  IVc    V   VI VIIa VIIb 
+#   1    2    3    4    5    6    7    8    9   10   11 
+frq(df2$dclass11d)
+test$egp3_v3 <- car::recode(test$dclass11d,"1:2=1;c(3,4,5,6,7,8)=2;9:11=3",as.factor = T,levels = c(1,2,3))
+test$egp3_v4 <- car::recode(test$dclass11d,"1:2=1;c(3,5,6,7,8)=2;c(4,9,10,11)=3",as.factor = T,levels = c(1,2,3))
+
+# Service class II to middle class
+test$egp3_v5 <- car::recode(test$dclass11d,"1=1;c(2,3,5,6,7,8)=2;c(4,9,10,11)=3",as.factor = T,levels = c(1,2,3))
+
+frq(test$egp3_v1)
+frq(test$egp3_v2)
+frq(test$egp3_v3)
+frq(test$egp3_v4)
+frq(test$egp3_v5)
+frq(test$class3)
+
+test$ingroup1 <- NA 
+test$ingroup1 <- ifelse(test$egp3_v1==1,test$n_high,test$ingroup1)
+test$ingroup1 <- ifelse(test$egp3_v1==2,test$n_middle,test$ingroup1)
+test$ingroup1 <- ifelse(test$egp3_v1==3,test$n_low,test$ingroup1)
+
+test$ingroup2 <- NA 
+test$ingroup2 <- ifelse(test$egp3_v2==1,test$n_high,test$ingroup2)
+test$ingroup2 <- ifelse(test$egp3_v2==2,test$n_middle,test$ingroup2)
+test$ingroup2 <- ifelse(test$egp3_v2==3,test$n_low,test$ingroup2)
+
+test$ingroup3 <- NA 
+test$ingroup3 <- ifelse(test$egp3_v3==1,test$n_high,test$ingroup3)
+test$ingroup3 <- ifelse(test$egp3_v3==2,test$n_middle,test$ingroup3)
+test$ingroup3 <- ifelse(test$egp3_v3==3,test$n_low,test$ingroup3)
+
+#ingroup with Routine non-manual IIIa as middle class and IIIb as working class
+test$ingroup4 <- NA 
+test$ingroup4 <- ifelse(test$egp3_v4==1,test$n_high,test$ingroup4)
+test$ingroup4 <- ifelse(test$egp3_v4==2,test$n_middle,test$ingroup4)
+test$ingroup4 <- ifelse(test$egp3_v4==3,test$n_low,test$ingroup4)
+
+#ingroup with Service II + Routine non-manual IIIa as middle class and IIIb as working class
+test$ingroup5 <- NA 
+test$ingroup5 <- ifelse(test$egp3_v5==1,test$n_high,test$ingroup4)
+test$ingroup5 <- ifelse(test$egp3_v5==2,test$n_middle,test$ingroup4)
+test$ingroup5 <- ifelse(test$egp3_v5==3,test$n_low,test$ingroup4)
+
+test$homclass_v1 <- as.numeric(test$ingroup1/test$know_total)
+test$homclass_v2 <- as.numeric(test$ingroup2/test$know_total)
+test$homclass_v3 <- as.numeric(test$ingroup3/test$know_total)
+test$homclass_v4 <- as.numeric(test$ingroup4/test$know_total)
+test$homclass_v5 <- as.numeric(test$ingroup5/test$know_total)
+
+sjPlot::plot_frq(test$homclass_v1,type = "bar")
+sjPlot::plot_frq(test$homclass_v2)
+sjPlot::plot_frq(test$homclass_v3,type = "bar")
+sjPlot::plot_frq(test$homclass_v4,type = "bar")
+sjPlot::plot_frq(test$homclass_v5,type = "bar")
+
+hist.default(df2$homclass)
+```
+
+```{r}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- test %>% dplyr::select(redist,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+hist.default(dfreg$homclass,main = "Class-based network homogeneity",xlab = NULL)
+
+# Models 
+base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,rob1,int_homo)
+
+knitreg(list(homclass,full1,rob1,int_homo))
+```

### 2023-10-31 procesamiento/prod_analysis-full-sample.Rmd
centrado de variables

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,MLMusingR)  
 rm(list=ls())

### 2023-10-31 procesamiento/prod_analysis-tables-macro.Rmd
centrado de variables

@@
 
-htmlreg(
+knitreg(
   c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
-  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
+  caption = "Multilevel linear regression: full country samp <- <- <- <- <- <- <- <- le cross-level interaction - egalitarian index",
   caption.above = T,
+  stars = c(.001, .01, .05, .1),
+  symbol = '\\dagger',
   custom.coef.map= coef_map,

### 2023-10-31 procesamiento/prod_prep-macro.Rmd
centrado de variables

@@
 load(here::here("input/data/proc/study1.RData"))
-pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse,haven)
+pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse,haven,MLMusingR)
 ```
@@
 
+# centering micro level
+
+```{r}
+df2 <- 
+df2 %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(class3),to_dummy(class3spo),to_dummy(class3res),to_dummy(Q03pcm))
+
+df2$female_gc = group_center(df2$female_2, grp = df2$country2)
+df2$union_gc = group_center(df2$union_2, grp = df2$country2)
+df2$workst_gc = group_center(df2$workst_2, grp = df2$country2)
+df2$edyears_gc = group_center(df2$edyears, grp = df2$country2)
+df2$agenum_gc = group_center(df2$agenum, grp = df2$country2)
+
+# EGP: dominance
+df2$class3_ser_gc = group_center(df2$class3_1, grp = df2$country2)
+df2$class3_mid_gc = group_center(df2$class3_2, grp = df2$country2)
+df2$class3_wor_gc = group_center(df2$class3_3, grp = df2$country2)
+# EGP: Respondent
+df2$class3res_ser_gc = group_center(df2$class3res_1, grp = df2$country2)
+df2$class3res_mid_gc = group_center(df2$class3res_2, grp = df2$country2)
+df2$class3res_wor_gc = group_center(df2$class3res_3, grp = df2$country2)
+# EGP: Respondent
+df2$class3spo_ser_gc = group_center(df2$class3spo_1, grp = df2$country2)
+df2$class3spo_mid_gc = group_center(df2$class3spo_2, grp = df2$country2)
+df2$class3spo_wor_gc = group_center(df2$class3spo_3, grp = df2$country2)
+# Household Income Tercile
+df2$Q03pcm_1_gc = group_center(df2$Q03pcm_1, grp = df2$country2)
+df2$Q03pcm_2_gc = group_center(df2$Q03pcm_2, grp = df2$country2)
+df2$Q03pcm_3_gc = group_center(df2$Q03pcm_3, grp = df2$country2)
+df2$Q03pcm_NA_gc = group_center(df2$Q03pcm_4, grp = df2$country2)
+
+names(df2)
+# drop dummies
+df2 <- 
+  df2 %>% 
+  select(-c(female_1,female_2,union_1,union_2,workst_1,workst_2,
+            class3_1,class3_2,class3_3,class3res_1,class3res_2,class3res_3,
+            class3spo_1,class3spo_2,class3spo_3,
+            Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
+names(df2)
+```
+
+# centering macro level
+
+```{r}
+df2$gini_disp_c <- center(df2$gini_disp)
+df2$gini_mkt_c <- center(df2$gini_mkt)
+df2$palmaratio_c <- center(df2$palmaratio)
+df2$top10_c <- center(df2$top10)
+df2$middle50_c <- center(df2$middle50)
+df2$d10d1_c <- center(df2$d10d1)
+df2$giniindex_c <- center(df2$giniindex)
+df2$ttheilge1_c <- center(df2$ttheilge1)
+df2$rgdpna_c <- center(df2$rgdpna)
+
+df2$gini_disp_z <- center(df2$gini_disp)
+df2$gini_mkt_z <- center(df2$gini_mkt)
+df2$palmaratio_z <- center(df2$palmaratio)
+df2$top10_z <- center(df2$top10)
+df2$middle50_z <- center(df2$middle50)
+df2$d10d1_z <- center(df2$d10d1)
+df2$giniindex_z <- center(df2$giniindex)
+df2$ttheilge1_z <- center(df2$ttheilge1)
+df2$rgdpna_z <- center(log(df2$rgdpna))
+
+df2 %>% 
+  select(country3,ends_with("_c")) %>% group_by(country3) %>% summarise_all(.funs = mean) %>% View()
+```
+
 ```{r save}

### 2023-10-31 procesamiento/prod_analysis-centrado.R

@@ -1,0 +1,123 @@
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                               class3_ser_gc,
+                               class3_mid_gc,
+                               class3_wor_gc,
+                               # class3_ser_gc=class3res_ser_gc, 
+                               # class3_mid_gc=class3res_mid_gc, 
+                               # class3_wor_gc=class3res_wor_gc,
+                               # class3spo,
+                               homclass = homclass_gc,
+                               Q03pcm_1_gc, Q03pcm_2_gc, Q03pcm_3_gc, Q03pcm_NA_gc,
+                               edyears = edyears_gc,
+                               female = female_gc,
+                               agenum = agenum_gc,
+                               union = union_gc,
+                               workst = workst_gc,
+                               #----------------------------
+                                 # gini_disp=gini_disp_c,
+                                 # gini_mkt=gini_mkt_c,
+                                 # palmaratio=palmaratio_c,
+                                 # top10=top10_c,
+                                 # middle50=middle50_c,
+                                 # d10d1=d10d1_c,
+                                 # giniindex=giniindex_c,
+                                 # ttheilge1=ttheilge1_c,
+                                #----------------------------
+                                 # gini_disp=gini_disp_z,
+                                 # gini_mkt=gini_mkt_z,
+                                 # palmaratio=palmaratio_z,
+                                 # top10=top10_z,
+                                 # middle50=middle50_z,
+                                 # d10d1=d10d1_z,
+                                 # giniindex=giniindex_z,
+                                 # ttheilge1=ttheilge1_z,
+                               #------------------------------
+                               gini_disp,
+                               gini_mkt,
[…]

### 2023-11-01 procesamiento/prod_analysis-tables-macro.Rmd
update

--- 2023-10-30 procesamiento/prod_analysis-tables-macro.Rmd
@@
 
-```{r full-lmer-macro,results='asis'}
+```{r full-lmer-egalitarian-macro,results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 
-```{r oecd-clmm-macro,results='asis'}
-
-```
-
 ```{r ocde-lmer-egalitarian-macro,results='asis'}
@@
 
-htmlreg(
+knitreg(
   c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
@@
   caption.above = T,
+  stars = c(.001, .01, .05, .1),
+  symbol = '\\dagger',
   custom.coef.map= coef_map,

### 2023-11-01 procesamiento/prod_analysis-centrado.R

@@ -2,7 +2,7 @@ if (!require("pacman")) install.packages("pacman")
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
+dfreg <- df1 %>% dplyr::select(redist=egal2,
                                class3_ser_gc,
                                class3_mid_gc,
                                class3_wor_gc,
@@ -46,7 +46,7 @@ dfreg <- df1 %>% dplyr::select(redist,
                                ttheilge1,
                                  WEIGHT,
                                  region,                              
-                                 country2=country3,
+                                 country2,
                                  country,
                                rgdpna,
                                oecd
@@ -57,6 +57,7 @@ mutate(logrgdpna=log(rgdpna),
   # mutate(homclass=group_center(homclass,country2))  %>%
   # filter(!country2 %in% c("TWN","CHN","JPN")) %>%
   # filter(oecd=="OECD" & country2!="SVN") %>%
+  filter(country2!="SVN") %>% 
   na.omit()
 
 base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
@@ -68,8 +69,7 @@ rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # anova(rob1,rob2)
 # Interactions segregation x class
 int_homo <- update(rob1, . ~ . +class3_mid_gc*homclass+class3_wor_gc*homclass)
-int_homo_country <- update(rob2, . ~ . -(1|country2) + (class3_mid_gc*homclass+class3_wor_gc*homclass|country2))
-models <- list(homclass,full1,rob1,int_homo,int_homo_country)
+models <- list(homclass,full1,rob1,int_homo)
 texreg::knitreg(models,stars = c(.001, .01, .05, .1),symbol = '\u2020')
 
   # Homoclass x Other Economic Inequality-----------------------------------------
@@ -90,8 +90,6 @@ models_m <- list(int_ginid,int_ginim,int_palma,int_pc10,int_pc50,int_d10d1,
                  int_gini_wiid,int_theil)
 
 texreg::knitreg(models_m,stars = c(.001, .01, .05, .1))
-
-
[…]

### 2023-11-01 procesamiento/prod_analysis-centrado.R
Update prod_analysis-centrado.R

@@ -2,7 +2,42 @@ if (!require("pacman")) install.packages("pacman")
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
 rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist=egal2,
+df1$egal <- df1$redist+df1$prefineq
+
+# Porcentaje de varianza explicada
+fit1<- psych::fa(df1[,c("redist","prefineq")],nfactors = 1,rotate = "varimax",missing = F,weight = df1$WEIGHT)
+fit1$loadings
+fs<- as.data.frame(fit1$scores)
+names(fs) <- c("lvegal")
+df1 <- bind_cols(df1,fs)
+
+df1[,c("redist","prefineq","lvegal")] %>% sjPlot::tab_corr()
+summary(df1$lvegal)
+
+model1 <- 
+'cfaegal=~ redist +prefineq ' 
+
+
+fit1 <- lavaan::cfa(model1,data = df1,sampling.weights = "WEIGHT",cluster = "country2",missing = "ML")
+summary(fit1)
+predicted2 <- lavaan::lavPredict(fit1,newdata = df1)  
+
+idx <- lavaan::lavInspect(fit1, "case.idx")
+fscores <- lavaan::lavPredict(fit1)
+## loop over factors
+for (fs in colnames(fscores)) {
+  df1[idx, fs] <- fscores[ , fs]
+}
+
+summary(df1$cfaegal)
+summary(df1$egal2)
+summary(df1$lvegal)
+
+df1[,c("egal2","cfaegal","lvegal")] %>% cor(use = "na.or.complete")
+
+dfreg <- df1 %>% dplyr::select(egal2=egal2,
+                               redist,
+                               prefineq,
                                class3_ser_gc,
                                class3_mid_gc,
                                class3_wor_gc,
@@ -56,24 +91,24 @@ mutate(logrgdpna=log(rgdpna),
        age2=agenum^2) %>%
   # mutate(homclass=group_center(homclass,country2))  %>%
   # filter(!country2 %in% c("TWN","CHN","JPN")) %>%
-  # filter(oecd=="OECD" & country2!="SVN") %>%
+  # filter(oecd=="OECD" & country2!="SVN") %>% 
   filter(country2!="SVN") %>% 
   na.omit()
 
[…]

### 2023-11-02 procesamiento/prod_analysis-descriptives.Rmd
ajuste

--- 2023-10-30 procesamiento/prod_analysis.Rmd
@@
 ---
-title: "Análisis de datos"
+title: "Analysis Descriptives"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
+pacman::p_load(dplyr,sjmisc,GGally,ggplot2,haven)
 load(here::here("input/data/proc/study1.RData"))
@@
 df1 %>% 
-    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3,) %>% 
+    select('redist',homclass,homclass_s,homclass_w,,class3,) %>% 
   na.omit() %>% 
@@
 
-```{r}
+- checking how different the measures for homogeneity are.
+- the original one is the best oneó
+
+```{r check-homogeneity}
 if (!require("pacman")) install.packages("pacman") # instalar pacman
@@
 hist.default(df2$homclass)
-```
 
-```{r}
 if (!require("pacman")) install.packages("pacman")

### 2023-11-02 procesamiento/prod_analysis-full-sample.Rmd
ajuste

@@
 output: 
-  html_document: 
+  bookdown::html_document2: 
     toc: yes
@@
 load(here::here("output/fullsample-numeric-homclass-respondent-macro.RData"))
-texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil))
-```
-
-# Binary logit 
-<!----------------------------------------------------------------------------->
-
-## Full network
-
-```{r mod-homclass-binary,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Models 
-base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
-homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# anova(rob1,rob2)
-# Interactions segregation x class
-int_homo <- update(rob1, . ~ . +class3*homclass)
-
-models <- list(homclass,full1,rob1,int_homo)
-save(models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"),compress = "gzip")
-```
-
-```{r mod-intermacro-binary,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country,
-                        palmaratio,
-                        top10,
-                        middle50,
-                        d10d1,
-                        giniindex,
-                        ttheilge1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Homoclass x Gini--------------------------------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
-giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
-summary(giniD_int)
-
-giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
-giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
-summary(giniM_int)
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-# Homoclass x Other Economic Inequality-----------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-int_palma <- update(base, . ~ . +homclass*palmaratio)
-int_pc10  <- update(base, . ~ . +homclass*top10)
-int_pc50  <- update(base, . ~ . +homclass*middle50)
-int_d10d1 <- update(base, . ~ . +homclass*d10d1)
-int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
-int_theil  <- update(base, . ~ . +homclass*ttheilge1)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil
-                 )
-save(giniD_gdp,giniD_rs,giniD_int,
-                 giniM_gdp,giniM_rs,giniM_int,
-                 int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-full-macro.RData"),compress = "gzip")
-```
-
-```{r}
-load(here::here("output/fullsample-logit-homclass-full-individual.RData"))
-texreg::knitreg(models)
-
-load(here::here("output/fullsample-logit-homclass-full-macro.RData"))
-texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil))
-```
-
-## Strong ties
-
-```{r mod-homclass-binary-strong-ties,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass=homclass_s,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Models 
-base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
-homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# anova(rob1,rob2)
-# Interactions segregation x class
-int_homo <- update(rob1, . ~ . +class3*homclass)
-
-models <- list(homclass,full1,rob1,int_homo)
-save(models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"),compress = "gzip")
-```
-
-```{r mod-intermacro-binary-strong-ties,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass=homclass_s,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country,
-                        palmaratio,
-                        top10,
-                        middle50,
-                        d10d1,
-                        giniindex,
-                        ttheilge1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Homoclass x Gini--------------------------------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
-giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
-summary(giniD_int)
-
-giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
-giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
-summary(giniM_int)
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-# Homoclass x Other Economic Inequality-----------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-int_palma <- update(base, . ~ . +homclass*palmaratio)
-int_pc10  <- update(base, . ~ . +homclass*top10)
-int_pc50  <- update(base, . ~ . +homclass*middle50)
-int_d10d1 <- update(base, . ~ . +homclass*d10d1)
-int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
-int_theil  <- update(base, . ~ . +homclass*ttheilge1)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil
-                 )
-save(giniD_gdp,giniD_rs,giniD_int,
-                 giniM_gdp,giniM_rs,giniM_int,
-                 int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"),compress = "gzip")
-```
-
-```{r}
-load(here::here("output/fullsample-logit-homclass-strong-individual.RData"))
-texreg::knitreg(models)
-
-load(here::here("output/fullsample-logit-homclass-strong-macro.RData"))
-texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil))
-```
-
-## Weak ties
-
-```{r mod-homclass-binary-weak-ties,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass=homclass_w,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Models 
-base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
-homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# anova(rob1,rob2)
-# Interactions segregation x class
-int_homo <- update(rob1, . ~ . +class3*homclass)
-
-models <- list(homclass,full1,rob1,int_homo)
-save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"),compress = "gzip")
-```
-
-```{r mod-intermacro-binary-weak-ties,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
-dfreg <- df1 %>% dplyr::select(redist=redistB,
-                        class3,
-                        homclass=homclass_w,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country,
-                        palmaratio,
-                        top10,
-                        middle50,
-                        d10d1,
-                        giniindex,
-                        ttheilge1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Homoclass x Gini--------------------------------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
-giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
-summary(giniD_int)
-
-giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
-giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
-summary(giniM_int)
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-# Homoclass x Other Economic Inequality-----------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
-int_palma <- update(base, . ~ . +homclass*palmaratio)
-int_pc10  <- update(base, . ~ . +homclass*top10)
-int_pc50  <- update(base, . ~ . +homclass*middle50)
-int_d10d1 <- update(base, . ~ . +homclass*d10d1)
-int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
-int_theil  <- update(base, . ~ . +homclass*ttheilge1)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil
-                 )
-save(giniD_gdp,giniD_rs,giniD_int,
-                 giniM_gdp,giniM_rs,giniM_int,
-                 int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"),compress = "gzip")
-```
-
-```{r}
-load(here::here("output/fullsample-logit-homclass-weak-individual.RData"))
-texreg::knitreg(models)
-
-load(here::here("output/fullsample-logit-homclass-weak-macro.RData"))
-texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil))
-```
-
-## R's class
-
-```{r mod-homclass-binary-respondent,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3=class3res,
-                        homclass=homclass_res,
-                        class3spo,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Models 
-base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
-homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
-rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
-rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
-# anova(rob1,rob2)
-# Interactions segregation x class
-int_homo <- update(rob1, . ~ . +class3*homclass)
-
-models <- list(homclass,full1,rob1,int_homo)
-save(models,file = here::here("output/fullsample-binary-homclass-respondent.RData"),compress = "gzip")
-```
-
-```{r mod-intermacro-binary-respondent,results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(redist,
-                        class3=class3res,
-                        class3spo,
-                        homclass=homclass_res,
-                        Q03pcm,
-                        edyears,
-                        female,
-                        agenum,
-                        union,
-                        workst,
-                        WEIGHT,
-                        region,
-                        "gini_disp",
-                        "gini_mkt",
-                        rgdpna,
-                        oecd,
-                        country2,country,
-                        palmaratio,
-                        top10,
-                        middle50,
-                        d10d1,
-                        giniindex,
-                        ttheilge1
-                        ) %>% 
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
-  na.omit()
-
-# Homoclass x Gini--------------------------------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
-base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
-giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
-giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniD_gdp,giniD_rs)
-giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
-summary(giniD_int)
-
-giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
-giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
-# anova(giniM_gdp,giniM_rs)
-giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
-summary(giniM_int)
-models <- list(giniD_gdp,giniD_rs,giniD_int,
-               giniM_gdp,giniM_rs,giniM_int)
-
-# Homoclass x Other Economic Inequality-----------------------------------------
-main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
-base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
-int_palma <- update(base, . ~ . +homclass*palmaratio)
-int_pc10  <- update(base, . ~ . +homclass*top10)
-int_pc50  <- update(base, . ~ . +homclass*middle50)
-int_d10d1 <- update(base, . ~ . +homclass*d10d1)
-int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
-int_theil  <- update(base, . ~ . +homclass*ttheilge1)
-
-models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil
-                 )
-save(giniD_gdp,giniD_rs,giniD_int,
-                 giniM_gdp,giniM_rs,giniM_int,
-                 int_palma,int_pc10,int_pc50,int_d10d1,
-                 int_gini_wiid,int_theil,
-     file = here::here("output/fullsample-binary-homclass-respondent-macro.RData"),compress = "gzip")
-```
-
-```{r}
-load(here::here("output/fullsample-binary-homclass-respondent.RData"))
-texreg::knitreg(models)
-
-load(here::here("output/fullsample-binary-homclass-respondent-macro.RData"))
 texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
@@
 ```
+
+# Binary logit 
+<!----------------------------------------------------------------------------->
+
+## Full network
+
+```{r mod-homclass-binary,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-binary,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-logit-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-logit-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Strong ties
+
+```{r mod-homclass-binary-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-binary-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-logit-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Weak ties
+
+```{r mod-homclass-binary-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-binary-weak-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
+dfreg <- df1 %>% dplyr::select(redist=redistB,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-logit-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-logit-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## R's class
+
+```{r mod-homclass-binary-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        homclass=homclass_res,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Models 
+base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/fullsample-binary-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-binary-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,
+                        class3=class3res,
+                        class3spo,
+                        homclass=homclass_res,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "redist~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- glmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/fullsample-binary-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/fullsample-binary-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/fullsample-binary-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```

### 2023-11-02 procesamiento/prod_analysis-plots-models.Rmd
ajuste

---
title: "Estimations plots"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  bookdown::html_document2: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_bw())
ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
```

# Preferences for Goverment redistribution

```{r full-redist-est}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg,broom.mixed,ggplot2,haven)  
rm(list=ls())

load(here::here("output/fullsample-numeric-homclass-full-individual.RData")); fsample_num_full_ind<- models
load(here::here("output/fullsample-numeric-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
load(here::here("output/fullsample-numeric-homclass-weak-individual.RData")); fsample_num_weak_ind<- models

coef <- c("homclass","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")

df_p_full<- 
bind_rows(
  fsample_num_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  fsample_num_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  fsample_num_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_full$depvar <- "Full sample"
```

```{r nonconfusian-redist-est}
load(here::here("output/nonconfusian-numeric-homclass-full-individual.RData")); nconf_num_full_ind<- models
load(here::here("output/nonconfusian-numeric-homclass-strong-individual.RData"));nconf_num_strong_ind<- models
load(here::here("output/nonconfusian-numeric-homclass-weak-individual.RData")); nconf_num_weak_ind<- models

coef <- c("homclass","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")

df_p_nconf<- 
bind_rows(
  nconf_num_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  nconf_num_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  nconf_num_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_nconf$depvar <- "Non-Confusian"
```

```{r oecd-redist-est}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
load(here::here("output/ocde-numeric-homclass-full-individual.RData")); ocde_num_full_ind<- models
load(here::here("output/ocde-numeric-homclass-strong-individual.RData"));ocde_num_strong_ind<- models
load(here::here("output/ocde-numeric-homclass-weak-individual.RData")); ocde_num_weak_ind<- models

df_p_ocde<- 
bind_rows(
  ocde_num_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  ocde_num_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  ocde_num_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_ocde$depvar <- "OECD"
```

```{r coefplot-redist}
df_p<- bind_rows(df_p_full,df_p_nconf,df_p_ocde)
df_p$term <- 
  factor(df_p$term,
         levels = c("class3Working Class (V+VI+VII)",
                    "class3Intermediate class (III+IV)",
                    "homclass"))
df_p$group <- factor(df_p$group,levels = c("Weak ties","Strong ties","Full network"))

ggplot(df_p,
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Preferences for Goverment redistribution") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))
ggsave(plot = last_plot(),filename = "coefplot-redist.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

# Egalitarian economic preferences

```{r full-redist-est}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg,broom.mixed,ggplot2,haven)  
rm(list=ls())

load(here::here("output/fullsample-egalitarian-homclass-full-individual.RData")); fsample_egal_full_ind<- models
load(here::here("output/fullsample-egalitarian-homclass-strong-individual.RData"));fsample_egal_strong_ind<- models
load(here::here("output/fullsample-egalitarian-homclass-weak-individual.RData")); fsample_egal_weak_ind<- models

coef <- c("homclass","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")

df_p_full<- 
bind_rows(
  fsample_egal_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  fsample_egal_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  fsample_egal_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_full$depvar <- "Full sample"
```

```{r nonconfusian-redist-est}
load(here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData")); nconf_egal_full_ind<- models
load(here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"));nconf_egal_strong_ind<- models
load(here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData")); nconf_egal_weak_ind<- models

coef <- c("homclass","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")

df_p_nconf<- 
bind_rows(
  nconf_egal_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  nconf_egal_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  nconf_egal_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_nconf$depvar <- "Non-Confusian"
```

```{r oecd-redist-est}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
load(here::here("output/ocde-egalitarian-homclass-full-individual.RData")); ocde_egal_full_ind<- models
load(here::here("output/ocde-egalitarian-homclass-strong-individual.RData"));ocde_egal_strong_ind<- models
load(here::here("output/ocde-egalitarian-homclass-weak-individual.RData")); ocde_egal_weak_ind<- models

df_p_ocde<- 
bind_rows(
  ocde_egal_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  ocde_egal_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  ocde_egal_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_ocde$depvar <- "OECD"
```

```{r coefplot-egal}
df_p<- bind_rows(df_p_full,df_p_nconf,df_p_ocde)
df_p$term <- 
  factor(df_p$term,
         levels = c("class3Working Class (V+VI+VII)",
                    "class3Intermediate class (III+IV)",
                    "homclass"))
df_p$group <- factor(df_p$group,levels = c("Weak ties","Strong ties","Full network"))

ggplot(df_p,
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Egalitarian Economic Preferences (Index)") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))

ggsave(plot = last_plot(),filename = "coefplot-egal.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

### 2023-11-02 procesamiento/prod_analysis-tables-micro.Rmd
ajuste

@@
 output: 
-  html_document: 
+  bookdown::html_document2: 
     toc: false
-    code_folding: hide
-    toc_float: 
-      collapsed: true
-      smooth_scroll: false
-      number_sections: true
+    # toc_float: 
+    #   collapsed: true
+    #   smooth_scroll: false
+    #   number_sections: true
 editor_options: 
@@
 
-```{r setup}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+```{r echo=FALSE}
+knitr::opts_chunk$set(
+	message = FALSE,
+	warning = FALSE,
+  echo=FALSE, results='asis'
+)
 options(scipen=9999) # desactivar notacion cientifica
@@
 
-## All countries
+# All countries
 
-```{r full-lmer-micro,results='asis'}
+```{r full-lmer-micro, echo=FALSE, results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 
-## Non-confusian
+# Non-confusian
 
@@
 
-## OECD
+# OECD
 

### 2023-11-17 paper.Rmd
update descriptivos

@@
 
-```{r}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(theme_minimal())
-ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
-```
-
 #  Introduction
@@
 The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
-Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support.
-Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
+Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalization and increasing the demand for welfare support.
+Particularly, social resources through network ties have been suggested to have a direct link with an individual's welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
 Consequently, inequalities in access to certain social positions (i.e.
@@
 Employing data from the International Social Survey Programme - Social Networks this research aims to understand to what extent the demand for redistribution is linked to social ties.
-To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
+To address this, ego-centered social networks are used to represent the degree of class-based homogeneity of social ties.
 The results of multilevel estimations show that being socially segregated increases demand for redistribution.
 Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class.
-At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution.
+At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesized that income inequality could bolster the influence of social segregation on the demand for redistribution.
 However, cross-level interactions do not provide supporting evidence on this behalf.
@@
 
-## Class interests and redistribution
-
-The following paragraph will briefly present the class-preference link.
-While previous research have focus more extensevely on the economic dimension of social class such as employment relations and occupation, the focus of this research is idea  to argue that the patterns of social interactions (social ties) are also a constituent dimension of how classes shape their interests.
-
-- The "Democratic" class struggle [@edlund_democratic_2015]
-
-- Class interests in the economic domain [@lindh_class_2020]
-- The moral economy of class - the attitudinal domain of redistribution and the role of the state [@Svallfors2006]
+## The role of social class on attitudes towards economic inequality and redistribution
+
+Paragraph 1: class-attitude link
+
+- The moral economy of class - the attitudinal domain of redistribution and the role of the state [@Svallfors2006] / Svallfors, S.
+(2006).
+The moral economy of class: Class and attitudes in comparative perspective.
+Stanford University Press.
+https://doi.org/10.1515/9781503625624
+
+- Class interests in the economic, socio-cultural and political domains [@lindh_class_2020]
+
+- The "Democratic" class struggle [@edlund_democratic_2015] and the role of the welfare state
+
+The main mechanism to be shown is the economic interests, normative dimension, risk exposure and sociability (classes are defined in a relational way by definition)
 
@@
 
-_Redistributive preferences_
-
-A widely used method for evaluating people's views on redistribution is by employing a standard measure commonly found in the literature.
-The measure involves asking respondents to indicate their level of agreement with the statement, "It is the responsibility of the government to decrease the income gap between individuals with high and low incomes." Respondents are asked to indicate their level of agreement on a scale of one to five, with one being "Strongly agree" and five being "Strongly disagree." In this case, a reverse code is utilized to interpret higher values as indicating greater support for redistribution.
-
-_Social Class_
-
-A synthetic version of the EGP class was used, including three main classes: Service class (I+II), Intermediate class (III+IV) and Working class (V+VI+VII)
+_Support for redistribution_.
+For measuring people's attitudes toward redistribution, an Egalitarian Economic Preferences Index is calculated based on two indicators [@svallfors_government_2013].
+The first corrresponds to (1) "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes" , followed by (2) "For a society to be fair, differences in people's standard of living should be small" .
+Each item corresponds to a five-point Likert scale indicating the level of agreement on each statement from "Strongly agree" (1), "Agree" (2), "Neither agree nor disagree" (2), "Disagree" (3) and "Strongly disagree." (5), which show an acceptable internal consistency ($\alpha$= 0.7).
+Consequently, the first step is to reverse code both indicators; therefore, higher values represent greater support for redistribution.
+The following step is computing the average value of both indicators and standardizing it as an indicator from 0 to 100.
+
+This is a measure of about respondents’ principled support for redistribution (redistribution in principle)
+
+<!-- Svallfors, Stefan.
+2013.
+‘Government Quality, Egalitarianism, and Attitudes to Taxes and Social Spending: A European Comparison’.
+European Political Science Review 5(3):363–80.
+doi: 10.1017/S175577391200015X.
+-->
+
+[Points x clase social] con un custom facet por paises (agrupado)
+
+_Social Class_. A synthetic version of the EGP class was used, including three main classes: Service class (I+II), Intermediate class (III+IV) and Working class (V+VI+VII).
+
+Declare the class scheme used, according to the class voting and the political attitude literature, even when the EGP class scheme was originally created for the study of social mobility in industrialized societies the rationale
 
@@
 
-_Class-based network homogeneity_
-
-For measuring the personal network of the respondent, a short version of the position generator was included in the survey, which presents a set of ten occupations that seek to represent the hierarchical status order in society [@joye_measuring_2019], declaring four possible response alternatives: "Family or relative", "Close friend", "Someone else I know" or "No one".
+_Class-based network homogeneity_.
+For measuring the personal network of the respondent, a short version of the position generator was included in the survey, which presents a set of ten occupations that seek to represent the hierarchical status order in society, declaring four possible response alternatives: "Family or relative", "Close friend", "Someone else I know" or "No one".
 For this research, a binary variable is created by coding the first three categories as 1 and the last one as 0, representing if the person knows (or not) one of the occupations.
@@
 
-_Perceived Isolation_
-
-"The next questions are about how you feel about different aspects of your life.
-For each one, please indicate how often during the past 4 weeks you have felt that way.
-How often in the past 4 weeks have you felt that..." 1) "companionship lacking?",(2) "isolated from others?" and (3) "left out?".
-
-The response categories are  (1)"Never", (2)"Rarely", (3) "Sometimes", (4)"Often" and  (5)"Very often".
-As the indicators show an acceptable internal consistency ($\alpha$=.85), an index of the three items was created.
-Positive values indicate higher perceived isolation.
+[Plot de paises en eje X]
+
+- paises ordenados por tipos x ejemplo regiones del mundo
+
+- eje Y es homogeneity, group por clase social (point type)
+
+- esto mejor que sea como resultados de un modelo lineal para que sean estimaciones en vez de mean values brutos.
 

### 2023-11-17 procesamiento/prod_analysis-descriptives.Rmd
update descriptivos

@@
 
+```{r redist-class-country}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
+               sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal2,redist,
+                        class3=digclass3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,country3,region,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit() %>% 
+  filter(oecd=="OECD")
+
+df_mean <- 
+dfreg %>% 
+  group_by(country3) %>% 
+  summarise(egal2_c=mean(egal2))
+
+df_region <- 
+dfreg %>% 
+  group_by(region,country3) %>% 
+  summarise(n())
+
+df_plot <- 
+dfreg %>% 
+  group_by(country3,class3) %>% 
+  summarise(egal2=mean(egal2),homclass=mean(homclass)) %>% 
+  left_join(df_mean) %>%
+  left_join(df_region) %>% 
+  arrange(egal2_c)
+
+df_plot %>% 
+ggplot()+
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=class3,color=class3)) +
+  scale_shape_manual(values = c(6, 15, 16)) +
+  scale_color_manual(values = c("blue", "#E7B800", "red")) +
+ # geom_point(aes(x = country3,y = egal2_c)) +    
+  theme_bw() +
+  theme(legend.position = "bottom",
+        axis.text.x=element_text(angle=90)) 
+```
+
 # macro correlations

### 2023-11-17 procesamiento/prod_analysis-class-scheme.R

@@ -1,0 +1,16 @@
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+
+df1$class11d
+
+
+frq(df1$class10spo)
+frq(df1$class10)
+
+frq(df1$digclass10)
+
+frq(df1$digclass11)
+frq(df1$digclass11d)

### 2023-11-28 procesamiento/prod_analysis-descriptives.Rmd
ajustes PAC

--- 2023-11-02 procesamiento/prod_analysis-descriptives.Rmd
@@
 options(scipen=9999) # desactivar notacion cientifica
+```
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(theme_bw())
+ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
 ```
@@
 
-```{r welfare}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
-load(here::here("input/data/proc/study1.RData"))
-df1 %>%
-    dplyr::select(whealth,wcarelder) %>%
-    na.omit() %>% 
-    sjPlot::plot_likert(geom.colors = "PuBu",
-                        grid.range  =  c (1 , 1),
-                        # title = "a. Perception meritocratic",
-                          geom.size = c(0.62),
-                          catcount = 5,
-                          expand.grid = T,
-                          # values  =  "sum.outside",
-                          reverse.colors = T,
-                          reverse.scale = T,
-                          show.n = FALSE,show.prc.sign = T,
-                        title = 'Who do you think should primarily provide...') +
-    scale_colour_discrete(labels = function(x) str_wrap(x, width = 10))+
-    ggplot2::theme(legend.position = "bottom")
+```{r redist-index}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
+               sjlabelled,haven,stringr,ordinal,texreg,likert)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(redist,prefineq,
+                        class3=class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,country3,region,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
 
-ggsave(plot = last_plot(),filename = "welf-attitudes.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 16)
-```
+labels <- get_labels(dfreg$redist)
 
-```{r perc-integration}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
-load(here::here("input/data/proc/study1.RData"))
-df1 %>%
-    dplyr::select(starts_with("pi_")) %>%
-    na.omit() %>% 
-    sjPlot::plot_likert(geom.colors = "PuBu",
-                        grid.range  =  c (0.2 , 1),
-                        # title = "a. Perception meritocratic",
-                          geom.size = c(0.62),
-                          catcount = 5,
-                          expand.grid = T,
-                          # values  =  "sum.outside",
-                          reverse.colors = T,
-                          reverse.scale = T,
-                          show.n = FALSE,show.prc.sign = T,sort.frq = "pos.asc",
-                        title = 'How often in the past 4 weeks have you felt that...') +
-    scale_colour_discrete(labels = function(x) str_wrap(x, width = 10))+ 
-    ggplot2::theme(legend.position = "bottom")
+dfreg$redist <- factor(dfreg$redist,levels = 1:5,labels = labels)
+set_label(dfreg$redist) <- "(b) It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes."
 
-ggsave(plot = last_plot(),filename = "perc-integration.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
+dfreg$prefineq <- factor(dfreg$prefineq,levels = 1:5,labels = labels)
+set_label(dfreg$prefineq) <- "(a) For a society to be fair, differences in people’s standard of living should be small."
 
-df1 %>%
-    dplyr::select(starts_with("pi_")) %>% 
-  psych::alpha()
-```
+set1 <- c("#5586B4","#D30132","#999999","#004481","#1C2747")
 
-```{r}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
-load(here::here("input/data/proc/study1.RData"))
-df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-dfcor <- 
-df1 %>%
-    dplyr::select(pi_nteg,class6,sstatus,redist) %>% 
-  as.data.frame()
+# sjlabelled::set_label(df2) <- paste0(varlab, " (n = ",summarise_all(df2,~ sum(!is.na(.))),")")
 
-levels(df1$class6)
-table(df1$know_total)
-table(df1$n_high)
-table(df1$n_middle)
-table(df1$n_low)
+as.data.frame(dfreg) %>%
+  dplyr::select(prefineq, redist) %>%
+  setNames(get_label(.)) %>%
+  likert() %>%
+plot(
+  low.color = "#D30132",
+  high.color = '#5586B4',
+  center = 3,
+  wrap = 30,
+  # plot.percents = TRUE,
+  text.size = 3
+) +
+  labs(title = "Redistributive preferences",caption = "\u03b1 = 0.70")
 
-# dfcor$hhdepriv <- as.factor(dfcor$hhdepriv)
-# dfcor$sstatus <- as.numeric(dfcor$sstatus)
-cormat<- polycor::hetcor(dfcor,parallel = T,thresholds = F)
+ggsave(plot = last_plot(),filename = "redist_index.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 0.75,units = "cm",scale = 18)
 
-jpeg(file=here::here("output/network-structure.jpeg"),units = "cm",width = 17,height = 15,res = 300)
-# Set up the layout for the multi-panel plot
-par(mfrow = c(1, 1))
-# Create the histograms
-# hist(df1$prestige, main = sjlabelled::get_label(df1$prestige),xlab = NULL)
-# hist(df1$diversity, main = sjlabelled::get_label(df1$diversity),xlab = NULL)
-hist(df1$homclass, main = sjlabelled::get_label(df1$homclass),xlab = NULL)
-dev.off()
-
-sjPlot::plot_frq(df1$class3,show.n = F) +
-  theme_grey()
-ggsave(plot = last_plot(),filename = "class6.png",device = "png",
-       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 10)
-
-jpeg(file=here::here("output/n_known.jpeg"),units = "cm",width = 15,height = 15,res = 300)
-# Set up the layout for the multi-panel plot
-par(mfrow = c(2, 2))
-
-# Create the histograms
-hist(df1$n_low, main = sjlabelled::get_label(df1$n_low),xlab = NULL)
-hist(df1$n_middle, main = sjlabelled::get_label(df1$n_middle),xlab = NULL)
-hist(df1$n_high, main = sjlabelled::get_label(df1$n_high),xlab = NULL)
-hist(df1$know_total, main = sjlabelled::get_label(df1$know_total),xlab = NULL)
-# hist(df1$prestige, main = sjlabelled::get_label(df1$prestige),xlab = NULL)
-# hist(df1$diversity, main = sjlabelled::get_label(df1$diversity),xlab = NULL)
-dev.off()
-
-sjPlot::plot_grpfrq(var.cnt = df1$know_total,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
-ggsave(plot = last_plot(),filename = "known_total_class6.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
-
-sjPlot::plot_grpfrq(var.cnt = df1$diversity,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
-ggsave(plot = last_plot(),filename = "diversity_class6.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
-
-sjPlot::plot_grpfrq(var.cnt = df1$prestige,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
-ggsave(plot = last_plot(),filename = "prestige_class6.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
-
-sjPlot::plot_grpfrq(var.cnt = df1$homclass,var.grp = df1$class3,type = 'box',geom.colors = "Blues")
-ggsave(plot = last_plot(),filename = "homclass_class6.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
-
-sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
-sjPlot::plot_grpfrq(var.cnt = df1$pi_nteg,var.grp = df1$class3,type = 'box',geom.colors = "Blues",ylim = c(1,5))
-ggsave(plot = last_plot(),filename = "pint_class3.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 15)
 ```
@@
   summarise(redist = mean(redist,na.rm = T),
+            egal
             homclass = mean(homclass,na.rm = T),
@@
 
-```{r health}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
-load(here::here("input/data/proc/study1.RData"))
-df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
+```{r redist-homclass-class-country}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
+               sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal2,redist,
+                        class3=class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,country3,region,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
 
-df1$whealthF <- factor(df1$whealth,levels = 1:5,labels = sjlabelled::get_labels(df1$whealth))
+df_mean <- 
+dfreg %>% 
+  group_by(country3) %>% 
+  summarise(egal2_c=mean(egal2),homclass_c=mean(homclass),gini_mkt=mean(gini_mkt),gini_disp=mean(gini_disp))
 
-percentage_data <- df1 %>%
-  group_by(country2, whealthF) %>%
-  summarise(count = n()) %>%
-  group_by(country2) %>%
-  na.omit() %>% 
-  mutate(percentage = count / sum(count)) %>% 
-  arrange(country2,whealthF,percentage) %>% 
-  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
-  mutate(pct_lab=ifelse(!whealthF %in% c("Government"),NA,pct_lab))
+df_region <- 
+dfreg %>% 
+  group_by(region,country3) %>% 
+  summarise(n())
 
-order <- 
-percentage_data %>% 
-  filter(whealthF=="Government") %>% 
-  arrange(percentage) %>% 
-  select(country2)
+df_full <- 
+dfreg %>% 
+  group_by(class3) %>% 
+  summarise(egal2=mean(egal2),homclass=mean(homclass),homclass_c=0.3910297,egal2_c=68.81757, country3="All")
 
-order$orden <- 1:32
-ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=whealthF,group=whealthF,label = pct_lab))+
-  geom_bar(stat = 'identity') +
-  geom_text(position = position_fill(vjust = 90)) + 
-  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
-  scale_x_discrete(limits=order$country2,name=NULL) +  
-  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
-  theme_classic() +
-  ggtitle(label= "Who do you think should primarily provide: health") + 
-  theme(legend.position = 'bottom',legend.title = element_blank())  +
-  coord_flip()
+df_plot <- 
+dfreg %>% 
+  group_by(country3,class3) %>% 
+  summarise(egal2=mean(egal2),homclass=mean(homclass)) %>% 
+  left_join(df_mean) %>%
+  left_join(df_region) %>% 
+  arrange(gini_mkt)
+df_plot <- 
+df_plot %>% 
+  bind_rows(df_full)
 
-ggsave(plot = last_plot(),filename = "whealth_cn.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
+df_plot$class3 <- factor(df_plot$class3,levels = levels(df_plot$class3),labels = c("Service Class (I+II)","Intermediate Class (III+IV+V)","Working Class (VI+VII)"))
 
-```{r elderlycare}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
-load(here::here("input/data/proc/study1.RData"))
-df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
-df1$wcarelderF <- factor(df1$wcarelder,levels = 1:5,labels = sjlabelled::get_labels(df1$wcarelder))
-percentage_data <- df1 %>%
-  group_by(country2, wcarelderF) %>%
-  summarise(count = n()) %>%
-  group_by(country2) %>%
-  na.omit() %>% 
-  mutate(percentage = count / sum(count)) %>% 
-  arrange(country2,wcarelderF,percentage) %>% 
-  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
-  mutate(pct_lab=ifelse(!wcarelderF %in% c("Government"),NA,pct_lab))
+table(df_plot$class3)
 
-order <- 
-percentage_data %>% 
-  filter(wcarelderF=="Government") %>% 
-  arrange(percentage) %>% 
-  select(country2)
+df_plot %>% 
+ggplot()+
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=class3,color=class3)) +
+  geom_hline(yintercept = 68.81757,linetype=2)+ 
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2_c),alpha=1,shape=4) +
+  scale_shape_manual(values = c(6, 15, 16)) +
+  scale_color_manual(values = c("blue", "#E7B800", "red")) +
+  labs(title = "Redistributive preferences (index) and social class by country",x=NULL,y="Redistributive Preferences") +
+  theme_bw() +
+  theme(legend.position = "bottom",
+        axis.text.x=element_text(angle=45,hjust = 1),
+        legend.title = element_blank())
 
-order$orden <- 1:32
-ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=wcarelderF,group=wcarelderF,label = pct_lab))+
-  geom_bar(stat = 'identity') +
-  geom_text(position = position_fill(vjust = 95)) + 
-  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
-  scale_x_discrete(limits=order$country2,name=NULL) +  
-  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
-  theme_classic() +
-  ggtitle(label= "Who do you think should primarily provide: elderly care") + 
-  theme(legend.position = 'bottom',legend.title = element_blank())  +
-  coord_flip()
+ggsave(plot = last_plot(),filename = "macro_class_redist.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 0.9,units = "cm",scale = 16)
 
-ggsave(plot = last_plot(),filename = "wcareelder_cn.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
+df_plot %>% 
+ggplot()+
+  geom_point(aes(x = reorder(country3, homclass_c),y = homclass,shape=class3,color=class3)) +
+  geom_hline(yintercept = 0.3910297,linetype=2)+ 
+  geom_point(aes(x = reorder(country3, homclass_c),y = homclass_c),alpha=1,shape=4) +
+  scale_shape_manual(values = c(6, 15, 16)) +
+  scale_color_manual(values = c("blue", "#E7B800", "red")) +
+  labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Redistributive Preferences") +
+  theme_bw() +
+  theme(legend.position = "bottom",
+        axis.text.x=element_text(angle=45,hjust = 1),
+        legend.title = element_blank())
 
-```{r class5}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2,haven)
-load(here::here("input/data/proc/study1.RData"))
-df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
-percentage_data <- df1 %>%
-  group_by(country2, class5) %>%
-  summarise(count = n()) %>%
-  group_by(country2) %>%
-  na.omit() %>% 
-  mutate(percentage = count / sum(count)) %>% 
-  arrange(country2,class5,percentage)
+ggsave(plot = last_plot(),filename = "macro_class_homclass.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 0.9,units = "cm",scale = 16)
 
-percentage_data$class5 <- forcats::fct_rev(percentage_data$class5)
-
-order <- 
-percentage_data %>% 
-  filter(class5=="Service class (I+II)") %>% 
-  arrange(percentage) %>% 
-  select(country2)
-
-order$orden <- 1:32
-ggplot(percentage_data, aes(x=country2,y=percentage*100,fill=class5,group=class5))+
-  geom_bar(stat = 'identity')+
-  scale_y_continuous(name=NULL,labels = scales::percent_format(scale = 1),limits = c(0,101), expand = c(0, 0)) +
-  scale_x_discrete(limits=order$country2,name=NULL) +  
-  scale_fill_ordinal(guide = guide_legend(reverse = TRUE)) +
-  theme_classic() +
-  ggtitle(label= "Social class by country") + 
-  theme(legend.position = 'bottom',legend.title = element_blank())  +
-  coord_flip()
-
-ggsave(plot = last_plot(),filename = "class5_cn.png",device = "png",
-       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
-```
-
-```{r class3}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
-load(here::here("input/data/proc/study1.RData"))
-
-df1$country2 <- sjlabelled::to_character(df1$country) 
-percentage_data <- df1 %>%
-  group_by(country2, class3) %>%
-  summarise(count = n()) %>%
-  group_by(country2) %>%
-  na.omit() %>% 
-  mutate(percentage = count / sum(count)) %>% 
-  arrange(country2,class3,percentage)
-
-percentage_data$class3 <- forcats::fct_rev(percentage_data$class3)
-
-order <- 
-percentage_data %>% 
-  filter(class3=="Working Class (V+VI+VII)") %>% 
-  arrange(percentage) %>% 
-  select(country2)
-
-order$orden <- 1:32
-ggplot(percentage_data, aes(x=country2,y=percentage,fill=class3,group=class3))+
-  geom_bar(stat = 'identity')+
-  # geom_text(aes(label=number_of_errors),position = position_stack(0.5))+
-  scale_y_continuous(labels = NULL) +
-  scale_x_discrete(limits=order$country2) +  
-  scale_fill_ordinal() +
-  theme_classic() +
-  theme(legend.position = 'bottom')  +
-  coord_flip()
-```
-
-```{r correlation-socap}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2)
-load(here::here("input/data/proc/study1.RData"))
-# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
-cormat1 <- 
-df1 %>% 
-    select('redist',wcarelder,whealth,isei_tot,isei_max,isei_range,"class6") %>% 
-  na.omit() %>% 
-  polycor::hetcor(parallel = T)
-
-  corrplot::corrplot(cormat1$correlations,
-    method = "color",
-    addCoef.col = "#000390",
-    type = "upper",
-    tl.col = "black",
-    col=colorRampPalette(c("white","#0068DC"))(12),
-    bg = "white",
-    na.label = "-")
-  text(4.7, 0.6, paste0("Source: Authors calculation based on ISSP 2017",
-                             " (N = ",")"),   
-       cex = 0.75)
-```
-
-```{r correlation-segregation}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2)
-load(here::here("input/data/proc/study1.RData"))
-# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
-cormat1 <- 
-df1 %>% 
-    select('redist',homclass,homclass_s,homclass_w,,class3,) %>% 
-  na.omit() %>% 
-  polycor::hetcor(parallel = T)
-
-  corrplot::corrplot(cormat1$correlations,
-    method = "color",
-    addCoef.col = "#000390",
-    type = "upper",
-    tl.col = "black",
-    col=colorRampPalette(c("white","#0068DC"))(12),
-    bg = "white",
-    na.label = "-")
-  text(4.7, 0.6, paste0("Source: Authors calculation based on ISSP 2017",
-                             " (N = ",")"),   
-       cex = 0.75)
-```
-
-```{r}
-if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
-load(here::here("input/data/proc/study1.RData"))
-df1$country2 <- sjlabelled::to_character(df1$country)
-library(scales)
-
-df1 %>% 
-  filter(!is.na(class5)) %>%
-ggplot(aes(x = class5, y = isei_avg))+
-  geom_boxplot(outlier.shape = NA)+
-  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red")+
-  ylim(25, 75) +
-  facet_wrap(.~country2, scales = "free")+ 
-  scale_x_discrete(labels=c("I+II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
-  ggtitle(sjlabelled::get_label(df1$isei_avg))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-df1 %>% 
-  # filter(!is.na(class5)) %>% 
-ggplot(aes(x = class5, y = hindex_10))+
-  geom_boxplot(outlier.shape = NA)+
-  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red")+
-  ylim(0, 1) +
-  facet_wrap(.~country2, scales = "free")+ 
-  scale_x_discrete(labels=c("I+II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
-  ggtitle(sjlabelled::get_label(df1$hindex_10))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-df1 %>% 
-  filter(!is.na(class6)) %>% 
-ggplot(aes(x = class6, y = hindex_10))+
-  geom_boxplot(outlier.shape = NA)+
-  facet_wrap(.~country2, scales = "free")+ 
-  scale_x_discrete(labels=c("I","II","IIIa+b","IVa+b+c","V+VI","VIIa+b"))+
-  ggtitle(sjlabelled::get_label(df1$hindex_10))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-levels(df1$class5)
 ```
@@
 if (!require("pacman")) install.packages("pacman") # instalar pacman
-pacman::p_load(dplyr,sjmisc,ggplot2,haven)
-load(here::here("input/data/proc/study1_country.RData"))
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
+               sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal2,redist,
+                        class3=class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,country3,region,
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  na.omit()
+
 df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
@@
   group_by(country2,country3) %>%
-  summarise_at(c("redist","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
+  summarise_at(c("redist","egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                  "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
@@
 macro_data %>%  
-ggplot(aes(y=redist, x=homclass)) +
+ggplot(aes(y=egal2, x=homclass)) +
   # geom_point() +
@@
 ggsave(plot = last_plot(),filename = "macro_homo_redist.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
-
-macro_data %>%  
-ggplot(aes(y=redist, x=pi_isola)) +
-  # geom_point() +
-  geom_text(label=as.character(macro_data$country3)) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Perceived isolation")+
-  ylab("Redistributive preferences") +
-  labs(title = "Redistributive preferences and Perceived isolation",
-       caption =paste("r=",round(cor(macro_data$pi_isola,
-                                     macro_data$redist, use='complete.obs'),digits = 2)))
-
-ggsave(plot = last_plot(),filename = "macro_pisol_redist.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
-
-macro_data %>%  
-ggplot(aes(y=pi_isola, x=homclass)) +
-  # geom_point() +
-  geom_text(label=as.character(macro_data$country3)) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Class homogeneity")+
-  ylab("Perceived isolation") +
-  labs(title = "Perceived isolation and Class homogeneity",
-       caption =paste("r=",round(cor(macro_data$homclass,
-                                     macro_data$pi_isola),digits = 2)))
-ggsave(plot = last_plot(),filename = "macro_homo_pisol.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
 
@@
 ggsave(plot = last_plot(),filename = "macro_working_homo.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
 
@@
   geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Intermediate class (%)")+
+  xlab("Intermediate Class (%)")+
   ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Intermediate class (%)",
+  labs(title = "Class homogeneity and Intermediate Class (%)",
        caption =paste("r=",round(cor(macro_data$homclass,
@@
 ggsave(plot = last_plot(),filename = "macro_middle_homo.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
 
@@
 ggsave(plot = last_plot(),filename = "macro_service_homo.png",device = "png",
-       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
+
+macro_data %>%  
+ggplot(aes(y=homclass, x=gini_disp)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Disposable)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Gini (Disposable)",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$gini_disp),digits = 2)))
+
+ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
+
+macro_data %>%  
+ggplot(aes(y=homclass, x=gini_mkt)) +
+  # geom_point() +
+  geom_text(label=as.character(macro_data$country3)) +
+  # scale_x_continuous(limits = c(0,1))+
+  # scale_y_continuous(limits = c(1,5))+
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  xlab("Gini (Market)")+
+  ylab("Class homogeneity") +
+  labs(title = "Class homogeneity and Gini (Market)",
+       caption =paste("r=",round(cor(macro_data$homclass,
+                                     macro_data$gini_mkt),digits = 2)))
+
+ggsave(plot = last_plot(),filename = "macro_giniM_homo.png",device = "png",
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
 

### 2023-11-28 procesamiento/prod_analysis-plots-models.Rmd
ajustes PAC

@@
 options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(theme_bw())
+ggplot2::theme_set(theme_minimal())
 ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
@@
 df_p_full$depvar <- "Full sample"
+
 ```
@@
     x="Coefficients (fixed effects)",y=NULL,
-    title = "Egalitarian Economic Preferences (Index)") +
+    title = "Redistributive Preferences (Index)") +
   theme(axis.text.y.left = element_text(face = "plain", size = 12))
@@
        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+
 ```
+
+```{r coef-egal-fullsample}
+ggplot(df_p %>% filter(depvar=="Full sample"),
+       aes(x = estimate, y = term, color = group)) +
+  geom_vline(xintercept = 0) +
+  geom_errorbar(
+    aes(xmin = conf.low, xmax = conf.high),
+    size = 1,
+    width = 0.2,
+    position = position_dodge(0.5)
+  ) +
+  geom_point(
+    shape = 21,
+    size = 3,
+    fill = "white",
+    position = position_dodge(0.5)
+  ) +
+  facet_grid(~depvar)+
+  scale_y_discrete(
+    labels = c(
+      "Working Class (VI+VII)",
+      "Intermediate class (III+IV+V)",
+      "Class-based homogeneity"
+    )
+  )+
+  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
+  labs(
+    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
+    color = "Model",
+    x="Coefficients (fixed effects)",y=NULL,
+    title = "Redistributive Preferences (Index)") +
+  theme(axis.text.y.left = element_text(face = "plain", size = 12))
+ggsave(plot = last_plot(),filename = "coefplot-egal-fullsample.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)
+
+```
+
+```{r inter-egal-fnet-fsample}
+int_homo <- fsample_egal_full_ind[[4]]
+interplot <- 
+interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
+df_int <- interplot$data
+df_int <- df_int[c(1,2,4),]
+df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV+V)","Working Class (VI+VII)")
+df_int$value <- factor(df_int$value,ordered = T,
+                       levels = c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))
+
+df_int %>% 
+ggplot() +
+  geom_point(aes(x = value,y = coef1)) + 
+  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  ylab("Class-based homogeneity (Full ties)")+
+  xlab("Social Class")+
+  ggtitle("Redistributive preferences") +
+  geom_hline(yintercept = 0) + 
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
+  theme(plot.title = element_text(size = 15))
+
+ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)
+
+df_pred1 <- plot_predictions(int_homo, condition = c("homclass","class3"),draw = F) 
+# names(df_pred1)
+df_pred1 %>% 
+ggplot(aes(y =estimate,x=homclass, fill=class3, color=class3,ymin=conf.low, ymax=conf.high)) +
+  geom_line(size=0.75) +
+  geom_point(size=1) +
+  geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
+  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),c("Service Class (I+II)","Intermediate class (III+IV+V)","Working Class (VI+VII)"))) +
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
+  xlab("Network homogeneity (Full ties)")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+
+ggsave(plot = last_plot(),filename = "predict-egal-fullsample.png",device = "png",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 14)
+```
+
+```{r inter-macro}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
+rm(list=ls())
+load(here::here("output/fullsample-egalitarian-homclass-full-macro.RData"));fsample_egal_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
+
+p1<- interplot::interplot(m = fsample_egal_full_mac[[1]],var1 = "homclass",var2="gini_disp",ci = .95)+
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
+  geom_point()+ geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "marginal-homoXginiD.png",device = "png",
+       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)
+
+p2<- interplot::interplot(m = fsample_egal_full_mac[[2]],var1 = "homclass",var2="gini_mkt") +
+  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)
+
+ggsave(plot = last_plot(),filename = "marginal-homoXginiM.png",device = "png",
+       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)
+
+# Predicted values 
+predval1 <- 
+plot_predictions(fsample_egal_full_mac[[1]], condition = list("homclass",gini_disp=range),gray = F) +
+  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
+       colour='Gini (Dis)',fill='Gini (Dis)') +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+ggsave(plot = last_plot(),filename = "predict-homoXginiD.png",device = "png",
+       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)
+
+# Predicted values 
+predval2 <- 
+plot_predictions(fsample_egal_full_mac[[2]], condition = list("homclass",gini_mkt=range),gray = F) +
+  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
+       colour='Gini (Mkt)',fill='Gini (Mkt)') +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  theme(legend.position = "right")
+
+ggsave(plot = last_plot(),filename = "predict-homoXginiM.png",device = "png",
+       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)
+
+```

### 2023-11-28 procesamiento/prod_analysis-tables-macro.Rmd
ajustes PAC

@@
 
-htmlreg(
+knitreg(
   c(fsample_num_full_mac,fsample_num_strong_mac,fsample_num_weak_mac),
@@
 
-htmlreg(
+knitreg(
   c(fsample_egal_full_mac,fsample_egal_strong_mac,fsample_egal_weak_mac),

### 2023-11-28 procesamiento/prod_analysis-tables-micro.Rmd
ajustes PAC

@@
 
+coefmap <-  list(homclass ="Class-based network homogeneity",
+                 'class3Intermediate class (III+IV)' ='Intermediate Class',
+                 'class3Working Class (V+VI+VII)' ='Working Class',
+                 "Q03pcmT02" = "Middle",
+                 "Q03pcmT03" = "High",
+                 "edyears" = 'Education in years',
+                 "workstNot in paid work"="Not in labor force",
+                 "unionYes" = 'Union membership: Yes',
+                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
+                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
+                 )
+
 htmlreg(
@@
       "Weak ties"=9:12
-      ))
+      ), 
+  custom.coef.map = coefmap
+  )
 ```

### 2023-12-04 procesamiento/prod_analysis-plots-models.Rmd
modelos 3-way interactions

@@
   geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
-  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),c("Service Class (I+II)","Intermediate class (III+IV+V)","Working Class (VI+VII)"))) +
+  facet_grid(~factor(class3, levels=
+                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
+                     c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))) +
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +

### 2023-12-04 procesamiento/prod_prep-macro.Rmd
modelos 3-way interactions

@@
          to_dummy(class3),to_dummy(class3spo),to_dummy(class3res),to_dummy(Q03pcm))
-
 df2$female_gc = group_center(df2$female_2, grp = df2$country2)

### 2023-12-04 procesamiento/prod_analysis-alternatives.R

@@ -1,0 +1,143 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(theme_minimal())
+ggplot2::theme_update(text=element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  class3,
+  homclass,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp",
+  "gini_mkt",
+  d10d1,
+  rgdpna,
+  oecd,
+  country2, country
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+knitreg(models)
+
+
+
+# Interacciones cross-level -----------------------------------------------
+
+# Gini Market
+int_homo_giniM <- update(rob1, . ~ . +class3*homclass*gini_mkt -(1|country2) + (class3+homclass|country2))
+
+# Gini Disposable
+int_homo_giniD <- update(rob1, . ~ . +class3*homclass*gini_disp -(1|country2) + (class3+homclass|country2))
+
+knitreg(list(int_homo_giniM,int_homo_giniD,int_homo_d10d01))
+
+summary(int_homo_giniD)
+
[…]

### 2023-12-04 procesamiento/prod_analysis-centrado.R

@@ -1,242 +1,0 @@
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$egal <- df1$redist+df1$prefineq
-
-# Porcentaje de varianza explicada
-fit1<- psych::fa(df1[,c("redist","prefineq")],nfactors = 1,rotate = "varimax",missing = F,weight = df1$WEIGHT)
-fit1$loadings
-fs<- as.data.frame(fit1$scores)
-names(fs) <- c("lvegal")
-df1 <- bind_cols(df1,fs)
-
-df1[,c("redist","prefineq","lvegal")] %>% sjPlot::tab_corr()
-summary(df1$lvegal)
-
-model1 <- 
-'cfaegal=~ redist +prefineq ' 
-
-
-fit1 <- lavaan::cfa(model1,data = df1,sampling.weights = "WEIGHT",cluster = "country2",missing = "ML")
-summary(fit1)
-predicted2 <- lavaan::lavPredict(fit1,newdata = df1)  
-
-idx <- lavaan::lavInspect(fit1, "case.idx")
-fscores <- lavaan::lavPredict(fit1)
-## loop over factors
-for (fs in colnames(fscores)) {
-  df1[idx, fs] <- fscores[ , fs]
-}
-
-summary(df1$cfaegal)
-summary(df1$egal2)
-summary(df1$lvegal)
-
-df1[,c("egal2","cfaegal","lvegal")] %>% cor(use = "na.or.complete")
-
-dfreg <- df1 %>% dplyr::select(egal2=egal2,
-                               redist,
-                               prefineq,
-                               class3_ser_gc,
-                               class3_mid_gc,
-                               class3_wor_gc,
-                               # class3_ser_gc=class3res_ser_gc, 
-                               # class3_mid_gc=class3res_mid_gc, 
-                               # class3_wor_gc=class3res_wor_gc,
-                               # class3spo,
-                               homclass = homclass_gc,
-                               Q03pcm_1_gc, Q03pcm_2_gc, Q03pcm_3_gc, Q03pcm_NA_gc,
-                               edyears = edyears_gc,
-                               female = female_gc,
-                               agenum = agenum_gc,
-                               union = union_gc,
-                               workst = workst_gc,
-                               #----------------------------
[…]

### 2023-12-07 procesamiento/01-prod_prep-micro.Rmd
3way interactions

--- 2023-10-29 procesamiento/prod_prep.Rmd
@@
 ```{r}
-df1 %>% select(redist,prefineq,perineq) %>% 
-  psych::cor2()
-df1 %>% select(redist,prefineq,perineq) %>% 
-  psych::alpha()
-
 df1$egal3<- rowMeans(df1[,c("redist","prefineq","perineq")],na.rm = T)
@@
 
-df1 %>% select(isco88r, is_supervisor, self_employed,"semp", n_employees,"supvis")
 haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
@@
                             levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
+                                      'Intermediate class (III+IV+V)',
+                                      'Working Class (VI+VII)'), 
                             "1:2='Service Class (I+II)';
@@
                             levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
+                                      'Intermediate class (III+IV+V)',
+                                      'Working Class (VI+VII)'), 
                             "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV)';
-                             8:11='Working Class (V+VI+VII)'")
+                             3:7='Intermediate class (III+IV+V)';
+                             8:11='Working Class (VI+VII)'")
 
@@
 df1$ingroup <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
 #frq(df1$ingroup)
@@
 df1$outgroup <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
 #frq(df1$outgroup)
@@
 df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_s,df1$ingroup_s)
 #frq(df1$ingroup_s)
@@
 df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
 #frq(df1$outgroup_s)
@@
 df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV)",df1$n_middle_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Working Class (V+VI+VII)",df1$n_low_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_w,df1$ingroup_w)
 # frq(df1$ingroup_w)
@@
 df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
 # frq(df1$outgroup_w)
@@
 df1$ingroup_res <- ifelse(df1$class3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res)
 # frq(df1$ingroup_res)
@@
 df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
 # frq(df1$outgroup_res)
@@
 df1$ingroup <- ifelse(df1$digclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
 #frq(df1$ingroup)
@@
 df1$outgroup <- ifelse(df1$digclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
 #frq(df1$outgroup)
@@
 df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res)
 # frq(df1$ingroup_res)
@@
 df1$outgroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
 # frq(df1$outgroup_res)
@@
 df1$ingroup <- ifelse(df1$dclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
 #frq(df1$ingroup)
@@
 df1$outgroup <- ifelse(df1$dclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
 #frq(df1$outgroup)
@@
 
-```{r social distance, eval=FALSE, include=FALSE}
+```{r social distance, include=FALSE}
 df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
@@
 
-df1$socdist<- rowMeans(x = df1 %>% select(starts_with("dis_")),na.rm = T)
+df1$socdist<- rowMeans(x = df1[,c("dis_busdriver","dis_ceo","dis_cleaner",
+                                          "dis_hairbarber","dis_hrmanager","dis_lawyer",
+                                          "dis_mechanic","dis_nurse","dis_police","dis_teacher")],na.rm = T)
 sjlabelled::set_label(df1$socdist) <- "Social distance: ISEI (respondent - contacts)"
-# sjPlot::plot_#frq(df1$socdist,type = "histogram")
-
-# df1$socdist_tot<- (df1$isei08- df1$isei_avg)
-# sjPlot::plot_#frq(df1$socdist_tot,type = "histogram")
-# sjlabelled::set_label(df1$socdist_tot) <- "Social distance: ISEI (respondent - contacts)"
+sjPlot::plot_frq(df1$socdist,type = "histogram")
+
+df1$socdist_tot<- (df1$isei08- df1$isei_avg)
+sjlabelled::set_label(df1$socdist_tot) <- "Social distance: ISEI (respondent - avg contacts)"
+sjPlot::plot_frq(df1$socdist_tot,type = "histogram")
 
@@
 #frq(df1$female)
+
 ```

### 2023-12-07 procesamiento/02-prod_prep-macro.Rmd
3way interactions

--- 2023-10-31 procesamiento/prod_prep-macro.Rmd
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 df2 <- 
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 df2$gini_disp_c <- center(df2$gini_disp)

### 2023-12-07 procesamiento/03-prod_analysis-descriptives.Rmd
3way interactions

--- 2023-11-28 procesamiento/prod_analysis-descriptives.Rmd
@@
 ) +
-  labs(title = "Redistributive preferences",caption = "\u03b1 = 0.70")
+  labs(title = "Redistributive preferences",caption = "r = 0.61")
 
@@
   scale_color_manual(values = c("blue", "#E7B800", "red")) +
-  labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Redistributive Preferences") +
+  labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Class-based network homogeneity ") +
   theme_bw() +
@@
 - checking how different the measures for homogeneity are.
-- the original one is the best oneó
+- the original one is the best one
 

### 2023-12-07 procesamiento/04-prod_analysis-full-sample.Rmd
3way interactions

--- 2023-11-02 procesamiento/prod_analysis-full-sample.Rmd
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
 rm(list=ls())
@@
                         egal=egal2,
-                        class3,
-                        homclass,
+                        class3=class3res,
+                        homclass=homclass_res,
                         Q03pcm,

### 2023-12-07 procesamiento/prod_analysis-alternatives.R

@@ -1,12 +1,13 @@
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
 options(ggplot2.discrete.fill = set1)
 options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(theme_minimal())
+ggplot2::theme_set(ggplot2::theme_bw())
 ggplot2::theme_update(text=element_text(size=15,  family="serif"))
 
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR)  
 rm(list=ls())
+
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
@@ -33,6 +34,57 @@ dfreg <- df1 %>% dplyr::select(
   filter(country2 != "SVN") %>%
   na.omit()
 
+
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(class3),
+         # to_dummy(class3spo),
+         # to_dummy(class3res),
+         to_dummy(Q03pcm)
+         )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$homclass_gc = group_center(dfreg$homclass, grp = dfreg$country2)
+
+
+# EGP: dominance
+dfreg$class3_ser_gc = group_center(dfreg$class3_1, grp = dfreg$country2)
+dfreg$class3_mid_gc = group_center(dfreg$class3_2, grp = dfreg$country2)
[…]

### 2023-12-07 procesamiento/01-prod_prep-micro.Rmd
code

@@
 # #hist.default(df1$egal2)
-```
-
-# Perceived integration
-
-```{r}
-#frq(df1$v31)
-df1$pi_compa <- car::recode(df1$v31,recodes = "c(0,8,9)=NA")
-df1$pi_compa <- set_na(df1$pi_compa,na = c(0,8,9))
-# df1$pi_compa <- sjmisc::rec(x = df1$pi_compa,rec = "rev")
-sjlabelled::set_label(df1$pi_compa) <- "Perceived integration: companionship lacking"
-#frq(df1$pi_compa)
-
-#frq(df1$v32)
-df1$pi_isola <- car::recode(df1$v32,recodes = "c(0,8,9)=NA")
-df1$pi_isola <- set_na(df1$pi_isola,na = c(0,8,9))
-# df1$pi_isola <- sjmisc::rec(x = df1$pi_isola,rec = "rev")
-sjlabelled::set_label(df1$pi_isola) <- "Perceived integration: isolated from others"
-#frq(df1$pi_compa)
-
-#frq(df1$v33)
-df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
-df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
-# df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
-sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
-#frq(df1$pi_left)
-
-df1$isolation<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
-sjlabelled::set_label(df1$isolation) <- "Perceived isolation"
-```
-
-# Trust
-
-```{r}
-df1$tr_inte <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
-df1$tr_inte <- set_na(df1$tr_inte,na = c(0,8,9))
-df1$tr_inte <- sjmisc::rec(x = df1$tr_inte,rec = "rev")
-sjlabelled::set_label(df1$tr_inte) <- "Interpersonal trust"
-frq(df1$tr_inte)
-
-df1$tr_courts <- car::recode(df1$v36,recodes = "c(98,99)=NA")
-df1$tr_courts <- set_na(df1$tr_courts,na = c(98,99))
-# df1$tr_courts <- sjmisc::rec(x = df1$tr_courts,rec = "rev")
-sjlabelled::set_label(df1$tr_courts) <- "Trust in courts"
-frq(df1$tr_courts)
 ```
@@
 
-```{r class-from-stata}
+```{r class-from-stata1}
 # Load the data created in stata------------------------------------------------
@@
 
-# Community participation
-
-```{r}
-# frq(df1$v17)
-df1$act_lei <- car::recode(df1$v17,recodes = "c(0,8,9)=NA")
-df1$act_lei <- set_na(df1$act_lei,na = c(0,8,9))
-df1$act_lei <- sjmisc::rec(x = df1$act_lei,rec = "rev")
-sjlabelled::set_label(df1$act_lei) <- "Activities: groups for leisure, sports or culture"
-# frq(df1$act_lei)
-
-# frq(df1$v18)
-df1$act_pol <- car::recode(df1$v18,recodes = "c(0,8,9)=NA")
-df1$act_pol <- set_na(df1$act_pol,na = c(0,8,9))
-df1$act_pol <- sjmisc::rec(x = df1$act_pol,rec = "rev")
-sjlabelled::set_label(df1$act_pol) <- "Activities: political parties, groups, associations"
-# frq(df1$act_pol)
-
-# frq(df1$v19)
-df1$act_vol <- car::recode(df1$v19,recodes = "c(0,8,9)=NA")
-df1$act_vol <- set_na(df1$act_vol,na = c(0,8,9))
-df1$act_vol <- sjmisc::rec(x = df1$act_vol,rec = "rev")
-sjlabelled::set_label(df1$act_vol) <- "Activities: charitable or religious - voluntary"
-# frq(df1$act_vol)
-
-# cor(df1[,c("act_lei","act_pol","act_vol")],use="complete.obs")
-# psych::alpha(df1[,c("act_lei","act_pol","act_vol")])
-
-df1$activities<- rowMeans(df1[,c("act_lei","act_pol","act_vol")],na.rm = T)
-sjlabelled::set_label(df1$activities) <- "Participation in social activities"
-# summary(df1$activities)
-```
-
 # Demographics

### 2024-01-24 paper1_jiturra.Rmd
a

---
title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
css: "input/css/custom.css" # custom CSS para html
fontsize: 11pt
linestretch: '1.5'          # interlineado 
papersize: a4
link-citations: yes         # citas linkeadas
# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
date: "`r format(Sys.Date(), '%d %B %Y')`"
author:
- name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: |
#  The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens. However, these consequences have been unevenly experienced across the social structure. The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience. Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support. Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need. Consequently, inequalities in access to certain social positions (i.e. occupations) are translated into a lack of social resources beyond individual economic and cultural capital. Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes. Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties. To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties. The results of multilevel estimations show that being socially segregated increases demand for redistribution. Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class. At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution. However, cross-level interactions do not provide supporting evidence on this behalf. 
#    **Keywords**: network segregation, redistributive preferences, economic inequality 
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    number_sections: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false

always_allow_html: true      
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa6.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \setlength\parindent{24pt} 
---

```{r eval=FALSE, include=FALSE}
 # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
 # clean #in the yml
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::pdf_document2")
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
```

<!-- - considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad -->
<!-- - darle una oportunidad al h-index -->
<!--     - en general es prácticamente lo mismo que el indicador de homogeneidad -->
<!-- - controlaria por social activities index () -->
<!-- - social resources  -->

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = F,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_minimal())
ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
```

# Class-based mechanism on attitudes toward economic inequality and welfare

key concepts: material interests, normative motivations, within-class differences,

The link between social class and political attitudes constitutes one of the most significant findings in sociology. The conceptual basis of these studies lies in the organization of classes as social barriers delineated mainly by ownership of the means of production, autonomy over one's work, and control over the work of others [@Erikson1992]. This perspective has been adopted from research on social mobility, focusing on occupations and their contractual status as fundamental characteristics to distinguish social classes [@ishida_trends_2005;@hertel_relation_2019]. Besides the literature on stratification and mobility, classes also trace distinctions in other domains of social life concerning voting behavior [@mainwaring_left_2015;@evans_decline_1993], cultural preferences [@Chan2007], and political attitudes [@Svallfors2006]. Regarding the latter, according to @lindh_class_2020, research on the link between class position and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and the social service functions of the welfare state (p. 421). In addition, the study of attitudes has been highlighted in the sociocultural domain, including people's views on issues such as gender relations, race and ethnicity, environmentalism, and sexuality (p. 425), as well as in the political domain concerning the capacity of political institutions to respond to the demands of the citizenry. Consequently, two main competing mechanisms that have linked class to attitudes in the economic domain can be mentioned. On the one hand, into those linked to material-self interests, and on the other hand, the mechanisms associated with normative motivations and values.

First, the self-interest mechanism has functioned as a canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981]. Similarly, an extension of the model has incorporated the dimension of economic risk (e.g., unemployment), paying attention to occupations as the unit that conveys it; consequently, positions with greater exposure to risk would tend to be more in favor of measures that mitigate labor market risks [@rehm_risks_2009]. Second, part of the literature on Western societies has highlighted the cognitive dimension in preference formation. On the one hand, it is suggested that people with limited material resources oppose redistributive measures due to the inability to successfully link their condition with the redistributive outcome because of a lack of information, distorting their views on fairness and misaligning their material interests from their preferences [@bartels_homer_2005;@hvidberg_social_2020]. On the other hand, part of the literature has paid more attention to high-income groups, suggesting that they are far from being monolithic towards inequality when expressing their preferences towards redistribution, arguing that although the rational interest model maintains its general implications, there are nuances within these groups regarding perceived negative externalities that inequality could have at a general level, which would ultimately motivate altruistic support towards redistribution [@rueda_who_2019,@dimick_models_2018].

Material interests and normative orientations can be comprehended as competing mechanisms in preference formation. For example, basic human values such as self-transcendence, characterized by the pursuit of equality and concern for others [@Kulin2013], or humanitarianism, which puts human dignity at the center [@feldman_humanitarian_2001], would be linked to altruistic motivations and might ultimately explain egalitarian economic preferences. However, this link may be weakened according to the exposure to risk and the possession of resources, becoming more salient under conditions of greater security against market risks and material prosperity, such as those experienced by the upper classes, and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019]. In a similar vein, class differences in skills and work logic might influence normative orientations that are ultimately expressed in political attitudes and behavior, being particularly salient among the professional class [@oesch_redrawing_2006]. Thus, the time that workers spend in their workplace, as well as the social interactions embedded in it, is argued that the work logic operates as a socialization agent according to the type of performed task, where those in interpersonal services tend to be more supportive of progressive political views than those in technical and managerial positions [@oesch_electoral_2018; @edlund_influence_2003]. However, related research has recently suggested that it is indeed challenging to disentangle whether work logic operates as a socialization agent, where reverse causality should be considered given that early-life socialization in the family context might motivate self-selection processes into specific career paths, or alternatively, decisions in the organizational hiring logic have to be taken into account considering that certain profiles might be preferred for interpersonal or managerial positions [@langsaether_more_2020].

Critical views have argued that a disincentive of political attitude and behavior in relation to class position. The "death of class" thesis has argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group memberships, reorienting the political debate towards post-material issues [@clark_declining_1993;@inglehart_culture_1990]. Although the process of modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been completely displaced but cohabits with people's attitudes towards the position of women in society as well as their views on migration [@Svallfors2006]. As far as people's attitudes toward redistribution and the role of the state in providing social welfare are concerned, this thesis has suggested that class cleavage would lose relevance as the material welfare of society increases. However, the claimed blurring of the class cleavage has not had particularly strong empirical support in terms of people's preferences around the economic domain.

	[Evidence on class and political attitudes]
# Network segregation and social class	
While previous research has focused more extensively on the economic dimension of social class, such as employment relations and occupation, patterns of social interactions are also a constituent dimension of how classes shape their political views toward economic inequality. Given that social classes are defined in terms of property, authority, and power, they can be understood as fundamentally relational. Therefore, it would be arguable that class positions are not merely distinguished by the labor market position, authority, and control over labor but are also relationally defined based on their patterns of sociability. Hereby, the scope of class analysis in the formation of attitudes and behavior can be extended further to the individual and household situation, stressing the role of social interactions and network segregation processes that might influence the internalization of shared norms, identity formation, and conflict between classes.

For stratification scholars, the study of segregation relates to the inequality in the distribution of status position and group membership heterogeneity as the observable patterns of association that shape interpersonal ties often referred to as relational networks [@blau_inequality_1977]. Indeed, one of the most significant findings on network research is the stronger contact frequency and tie formation between individuals of similar characteristics described as homophily [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], demonstrating that associations are segregated according to the degree of demographic availability of social groups, as well as by status differentiation that intersect group membership [@bargsted_pautas_2020; @plaza_juntos_2022]. However, it has been argued that segregation is also affected by sociopsychological factors, where in-group dynamics tend to be reinforced when attitudes and behavior are concentrated in isolated social environments, decreasing the chances of interchange of world views and opinions [@visser_attitudes_2004; @diprete_segregation_2011]. Nonetheless, besides the importance of socialization preferences, it has been argued that the distribution of status positions and group diversity tend to be more dominant in structuring social activities that provide opportunities for opportunity for contact and consolidation of social networks [@feld_focused_1981; @mcpherson_network_2019]. As for social classes, it could be argued that classes represent social differentiation insofar as they not only consider differences in status resources but also comprise patterns of sociability so that segregation can also be observed in terms of the distribution of social ties regarding class positions.

How classes are formed also provides insights regarding their social relations and sociability practices.  In sociology,  classes are understood as the common basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978]. According to habitus theory, classes seek to improve and maintain their position by stressing the importance of intergenerational transmission of resources, which is accomplished through the reproduction of socialization patterns and lifestyles expressed in tie formation between groups of similar status when it comes to partner and friendship choices, arguing that class *habitus* entails a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984]. Symbolic resources such as skills and education credentials serve to reinforce status distinctions between upper and lower classes, granting access to socially segregated environments and increasing the likelihood of reproducing privileged positions at the expense of lower classes [@bourdieu_reproduccion_1981]. Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992]. Altogether, these processes further reinforce social distinctions between classes and contribute to the persistence of class structures. Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes. Access to social resources embedded in social networks follows a pattern of accumulation that reproduces pre-existing inequalities, in which class positions are vital in accounting for mechanisms of exclusion and segregation across the class structure.

Previous research on social class and tie formation has suggested that class permeability, understood as the formation of cross-class social ties, is traced differently across property and authority boundaries. Empirically, evidence from Western industrialized countries has shown that the formation of friendship ties between owners and the working class is very less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the authority dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992]. Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that isolate them from others, while the upper class is less permeable and homogenous as a result of its tendency to self-selection as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].

In contrast, cross-class embeddedness can be described regarding their social activities as well as through their changes across generations and time. In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in its civic engagement behavior. Similarly, other studies in Argentina and Croatia have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation, whereas it does not equalize the weight of class background compared to those intergenerationally stable in the upper class [@cepic_how_2020;@carrascosa_class_2023]. Additionally, the few longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions while the lower class shows more stability across the life course [@volker_social_2020].

Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to vertically represent social resources embedded in social networks [@lin_social_2007]. Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977]. Therefore, _homogeneity_  is described as the lack of cross-class network ties. It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position. At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to a certain group that does not necessarily count with a reference position to describe the network composition. Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.

# Class boundaries and political attitudes

# References

### 2024-01-25 procesamiento/prod_analysis-alternatives.R
asd

@@ -2,7 +2,7 @@ set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
 options(ggplot2.discrete.fill = set1)
 options(ggplot2.discrete.colour = set1)
 ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=element_text(size=15,  family="serif"))
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
 
 if (!require("pacman")) install.packages("pacman")
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR)  
@@ -253,6 +253,8 @@ df_pred_giniM_gc <-
   )
 
 df_pred_giniM_gc <- as.data.frame(df_pred_giniM_gc)
+df_pred_giniM_gc$gini_mkt <- factor(df_pred_giniM_gc$gini_mkt,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+
 
 
 df_pred_giniM_gc %>% 
@@ -275,5 +277,85 @@ df_pred_giniM_gc %>%
 
 ggsave(plot = last_plot(),filename = "predict-egal-hom_class_giniM_fullsample_CWC.png",device = "png",
        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 18)
+
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginim_max<- round(max(dfreg$gini_mkt) ,2)
+# ginim_min<- round(min(dfreg$gini_mkt),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(min(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    int_homo_giniD_gc,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      homclass_gc = seq(min(dfreg$homclass_gc), max(dfreg$homclass_gc), by= 0.1),
+      class3=levels(dfreg$class3)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
[…]

### 2024-01-26 procesamiento/03-prod_analysis-descriptives.Rmd
a

@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(egal2,redist,
-                        class3=class3,
+dfreg <- df1 %>% dplyr::select(
+  egal2,
+  class3,
   homclass,
@@
   "gini_mkt",
+  d10d1,
   rgdpna,
   oecd,
-                        country2,country,country3,region,
+  country2, country
 ) %>%
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
+  mutate(logrgdpna = log(rgdpna),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN") %>%
   na.omit()
@@
   group_by(country2,country3) %>%
-  summarise_at(c("redist","egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
+  summarise_at(c("egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                  "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
@@
        caption =paste("r=",round(cor(macro_data$homclass,
-                                     macro_data$redist, use='complete.obs'),digits = 2)))
+                                     macro_data$egal2, use='complete.obs'),digits = 2)))
 
-ggsave(plot = last_plot(),filename = "macro_homo_redist.png",device = "png",
+ggsave(plot = last_plot(),filename = "macro_homo_egal.png",device = "png",
        path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)

### 2024-01-26 procesamiento/prod_analysis-plots-models.Rmd
a

@@
 options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(theme_minimal())
+ggplot2::theme_set(theme_bw())
 ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
@@
 ```{r coef-egal-fullsample}
-ggplot(df_p %>% filter(depvar=="Full sample"),
+coefplot1 <-  
+df_p %>% filter(depvar=="Full sample" & group =="Full network") %>% 
+  add_row(effect="fixed",group="Full network",term = "classService",depvar= "Full sample",.before = 2)
+
+coefplot1$term <- factor(coefplot1$term,levels = rev(c("homclass","classService","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")))
+
+ggplot(coefplot1,
        aes(x = estimate, y = term, color = group)) +
@@
     shape = 21,
-    size = 3,
+    size = 5,
     fill = "white",
@@
     labels = c(
-      "Working Class (VI+VII)",
-      "Intermediate class (III+IV+V)",
+      "Working Class",
+      # str_wrap("Service Class: Intermediate class",width = 20)),
+       # bquote(bold("Social Class (Ref: Service Class)") Intermediate class"),
+    # "Social Class (Ref: Service Class)\n\nIntermediate class\n\n",
+    "Intermediate class",
+    bquote(bold("Social Class \n(Ref: Service Class)")),
     "Class-based homogeneity"
-    )
-  )+
+    ))+
   scale_color_discrete(guide = guide_legend(reverse = TRUE))+
   labs(
-    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
+    # caption = paste0("N=", nobs(fsample_egal_full_ind), ", Countries=", lme4::ngrps(fsample_egal_full_ind)),
     color = "Model",
     x="Coefficients (fixed effects)",y=NULL,
-    title = "Redistributive Preferences (Index)") +
-  theme(axis.text.y.left = element_text(face = "plain", size = 12))
+    title = "Redistributive Preferences") +
+  theme(axis.text.y.left = element_text(face = "plain", size = 15),
+        legend.position="none")
+
 ggsave(plot = last_plot(),filename = "coefplot-egal-fullsample.png",device = "png",
        path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)
-
 ```

### 2024-01-26 procesamiento/prod_analysis-alternatives.R

@@ -95,8 +95,13 @@ rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # Interactions segregation x class
 int_homo <- update(rob1, . ~ . +class3*homclass)
 
+segregation <- lmer(homclass~class3+edyears+ Q03pcm+union+workst+(1|country2),data=dfreg,weights = WEIGHT)
+segregation2<- lmer(homclass~class3+edyears+ Q03pcm+union+workst+gini_disp+(1|country2),data=dfreg,weights = WEIGHT)
+segregation3<- lmer(homclass~class3+edyears*gini_disp+ Q03pcm+union+workst+gini_disp+(edyears|country2),data=dfreg,weights = WEIGHT)
+
+knitreg(list(segregation,segregation2,segregation3))
 models <- list(homclass,full1,rob1,int_homo)
-knitreg(models)
+
 
 # Interacciones cross-level -----------------------------------------------
 ## Gini Market--------------------------------------------------------------
@@ -132,6 +137,31 @@ knitreg(list(int_homo_giniM,int_homo_giniD,
              int_homo_giniM_gc,int_homo_giniD_gc))
 
 summary(int_homo_giniD)
+
+
+
+models_int <- list(rob1,int_homo,int_homo_giniD_gc)
+htmlreg(models_int,
+          custom.coef.map = list("class3Intermediate class (III+IV+V)"="Intermediate Class",
+                                 "class3Working Class (VI+VII)" = "Working Class",
+                                 "homclass"="Class-based network homogeneity",
+                                 "homclass_gc"="Class-based network homogeneity",
+                                 "homclass:class3Intermediate class (III+IV+V)" = "Homogeneity x Intermediate Class",
+                                 "homclass:class3Working Class (VI+VII)"= "Homogeneity x Working Class",
+                                 "homclass_gc:class3Intermediate class (III+IV+V)" = "Homogeneity x Intermediate Class",
+                                 "homclass_gc:class3Working Class (VI+VII)"= "Homogeneity x Working Class",
+                                 "gini_disp" = "Income Inequality (Gini Disposable)",
+                                 "homclass_gc:gini_disp"= "Homogeneity x Inequality",
+                                 "class3Intermediate class (III+IV+V):gini_disp" = "Intermediate Class x Inequality",
+                                 "class3Working Class (VI+VII):gini_disp" = "Working Class x Inequality",
[…]

### 2024-01-30 procesamiento/03-prod_analysis-descriptives.Rmd
up

@@
 dfreg <- df1 %>% dplyr::select(redist,prefineq,
-                        class3=class3,
+  class3,
   homclass,
@@
 
+# polycor::hetcor(data = dfreg$redist,dfreg$prefineq)
+
 dfreg$redist <- factor(dfreg$redist,levels = 1:5,labels = labels)
-set_label(dfreg$redist) <- "(b) It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes."
+set_label(dfreg$redist) <- "(B) It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes."
 
 dfreg$prefineq <- factor(dfreg$prefineq,levels = 1:5,labels = labels)
-set_label(dfreg$prefineq) <- "(a) For a society to be fair, differences in people’s standard of living should be small."
+set_label(dfreg$prefineq) <- "(A) For a society to be fair, differences in people’s standard of living should be small."
 
@@
   center = 3,
-  wrap = 30,
+  wrap = 50,
   # plot.percents = TRUE,
-  text.size = 3
+  text.size = 3,
 ) +
@@
 ggsave(plot = last_plot(),filename = "redist_index.png",device = "png",
-       path = here::here("output/images"),width = 1.5,height = 0.75,units = "cm",scale = 18)
+       path = here::here("output/images"),width = 1.7,height = 0.55,units = "cm",scale = 18)
 
+```
+
+```{r n-ties}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
+               sjlabelled,haven,stringr,ordinal,texreg)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$idunique <- 1:dim(df1)[[1]]
+
+dfreg <- df1 %>% dplyr::select(idunique,egal2,
+  class3,
+  homclass,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp",
+  "gini_mkt",
+  d10d1,
+  rgdpna,
+  oecd,
+  country2, country, country3,region,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN") %>%
+  na.omit() %>% 
+  left_join(df1[,c("idunique","n_high","n_middle","n_low")])
+
+phig<- sjPlot::plot_frq(data = dfreg$n_high,show.prc = F,show.n = F)
+pmid<- sjPlot::plot_frq(data = dfreg$n_middle,show.prc = F,show.n = F)
+plow<- sjPlot::plot_frq(data = dfreg$n_low,show.prc = F,show.n = F)
+
+cowplot::plot_grid(phig, pmid, plow, labels = NULL, nrow = 3,ncol = 1)
+
+ggsave(plot = last_plot(),filename = "n_status_class.png",device = "png",
+       path = here::here("output/images"),width = 0.5,height = 1,units = "cm",scale = 20)
 ```
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(egal2,redist,
-                        class3=class3,
+
+df1$idunique <- 1:dim(df1)[[1]]
+
+dfreg <- df1 %>% dplyr::select(idunique,egal2,
+  class3,
   homclass,
@@
   "gini_mkt",
+  d10d1,
   rgdpna,
   oecd,
-                        country2,country,country3,region,
+  country2, country, country3,region,
 ) %>%
-  mutate(logrgdpna=log(rgdpna),
-         edyears2=edyears^2,
-         age2=agenum^2) %>%
+  mutate(logrgdpna = log(rgdpna),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN") %>%
   na.omit()
+
+df1[,c("n_high","n_middle","n_low")]
 
@@
   scale_color_manual(values = c("blue", "#E7B800", "red")) +
-  labs(title = "Redistributive preferences (index) and social class by country",x=NULL,y="Redistributive Preferences") +
-  theme_bw() +
+  labs(title = "Redistributive preferences and social class by country",x=NULL,y="Redistributive Preferences") +
   theme(legend.position = "bottom",
@@
   labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Class-based network homogeneity ") +
-  theme_bw() +
   theme(legend.position = "bottom",

### 2024-01-30 procesamiento/prod_analysis-alternatives.R

@@ -95,13 +95,8 @@ rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # Interactions segregation x class
 int_homo <- update(rob1, . ~ . +class3*homclass)
 
-segregation <- lmer(homclass~class3+edyears+ Q03pcm+union+workst+(1|country2),data=dfreg,weights = WEIGHT)
-segregation2<- lmer(homclass~class3+edyears+ Q03pcm+union+workst+gini_disp+(1|country2),data=dfreg,weights = WEIGHT)
-segregation3<- lmer(homclass~class3+edyears*gini_disp+ Q03pcm+union+workst+gini_disp+(edyears|country2),data=dfreg,weights = WEIGHT)
-
-knitreg(list(segregation,segregation2,segregation3))
 models <- list(homclass,full1,rob1,int_homo)
-
+knitreg(models)
 
 # Interacciones cross-level -----------------------------------------------
 ## Gini Market--------------------------------------------------------------
@@ -137,31 +132,6 @@ knitreg(list(int_homo_giniM,int_homo_giniD,
              int_homo_giniM_gc,int_homo_giniD_gc))
 
 summary(int_homo_giniD)
-
-
-
-models_int <- list(rob1,int_homo,int_homo_giniD_gc)
-htmlreg(models_int,
-          custom.coef.map = list("class3Intermediate class (III+IV+V)"="Intermediate Class",
-                                 "class3Working Class (VI+VII)" = "Working Class",
-                                 "homclass"="Class-based network homogeneity",
-                                 "homclass_gc"="Class-based network homogeneity",
-                                 "homclass:class3Intermediate class (III+IV+V)" = "Homogeneity x Intermediate Class",
-                                 "homclass:class3Working Class (VI+VII)"= "Homogeneity x Working Class",
-                                 "homclass_gc:class3Intermediate class (III+IV+V)" = "Homogeneity x Intermediate Class",
-                                 "homclass_gc:class3Working Class (VI+VII)"= "Homogeneity x Working Class",
-                                 "gini_disp" = "Income Inequality (Gini Disposable)",
-                                 "homclass_gc:gini_disp"= "Homogeneity x Inequality",
-                                 "class3Intermediate class (III+IV+V):gini_disp" = "Intermediate Class x Inequality",
-                                 "class3Working Class (VI+VII):gini_disp" = "Working Class x Inequality",
[…]

### 2024-02-01 procesamiento/01-prod_prep-micro.Rmd
up

@@
 ```{r eval=FALSE, include=FALSE}
-# knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
-# knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
+knitr::knit(input = here::here("procesamiento/01-prod_prep-micro.Rmd"));file.remove("01-prod_prep-micro.md")
+knitr::knit(input = here::here("procesamiento/02-prod_prep-macro.Rmd"));file.remove("02-prod_prep-macro.md")
 ```
@@
 # Total of known occupations
-isei_ocupnames<- names(select(df1,busdriver:teacher))
-df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
+isei_ocupnames<- names(dplyr::select(df1,busdriver:teacher))
+df1$know_total <- rowSums(x = dplyr::select(df1,isei_ocupnames),na.rm = T)
 # summary(df1$know_total)
@@
 
+df1<- df1 %>% group_by(country) %>% mutate(sum_know_total=sum(know_total))
+
+df1$know_total_weight <- df1$know_total/df1$sum_know_total
+df1$homclass_wght <- (as.numeric(df1$ingroup/df1$know_total*df1$know_total_weight))*1000 #the 1000 is for scaling purposes
+
+summary(df1$homclass_wght)
+
+cor(df1[,c("homclass","homclass_wght","egal2")],use = "complete.obs")
+
+hist.default(df1$homclass)
+hist.default(df1$homclass_wght)
+
 # Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.

### 2024-02-01 procesamiento/prod_analysis-alternatives.R

@@ -13,6 +13,7 @@ dfreg <- df1 %>% dplyr::select(
   egal = egal2,
   class3,
   homclass,
+  homclass_wght,know_total,
   Q03pcm,
   edyears,
   female,
@@ -88,14 +89,15 @@ names(dfreg)
 # Models 
 base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
 homclass<- update(base, . ~ . +homclass)
-full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+homclass_know_total<- update(homclass, . ~ . +know_total)
+full1 <- update(homclass_know_total, . ~ . + class3+female+agenum+age2)
 rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
 rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
 # anova(rob1,rob2)
 # Interactions segregation x class
 int_homo <- update(rob1, . ~ . +class3*homclass)
 
-models <- list(homclass,full1,rob1,int_homo)
+models <- list(homclass,homclass_know_total,full1,rob1,int_homo)
 knitreg(models)
 
 # Interacciones cross-level -----------------------------------------------

### 2024-02-01 procesamiento/prod_analysis-plots-models.Rmd
ajustes color plots

@@
                      c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))) +
+    scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
+  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +

### 2024-02-01 procesamiento/prod_analysis-alternatives.R

@@ -133,9 +133,11 @@ int_homo_giniD_gc <-
 knitreg(list(int_homo_giniM,int_homo_giniD,
              int_homo_giniM_gc,int_homo_giniD_gc))
 
-summary(int_homo_giniD)
+knitreg(int_homo_giniD)
 
 ### Predicted values homo*class*GiniM ---------------------------------------
+
+
 # ginim_max<- round(max(dfreg$gini_mkt) ,2)
 # ginim_min<- round(min(dfreg$gini_mkt),2)
 
@@ -172,6 +174,8 @@ df_pred_giniM %>%
        title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality") +
   # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (Market)", breaks = NULL, labels = NULL)) +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
+  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+  
   theme(legend.position="bottom",
         legend.direction = "horizontal",
         axis.text=element_text(size=15),
@@ -220,6 +224,8 @@ df_pred_giniD %>%
        title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality") +
   # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (Disposable)", breaks = NULL, labels = NULL)) +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
+  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+  
   theme(legend.position="bottom",
         legend.direction = "horizontal",
         axis.text=element_text(size=15),
@@ -270,6 +276,8 @@ df_pred_giniM_gc %>%
        title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality") +
   # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (Market)", breaks = NULL, labels = NULL)) +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
[…]

### 2024-02-01 procesamiento/01-prod_prep-micro.Rmd
up

@@
 df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
+sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (isko - v2)"
 df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
@@
 df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
+sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (DIGCLASS version)"
 df1$homclass3_gc <- group_center(x = df1$homclass3,grp = df1$country)

### 2024-02-01 procesamiento/prod_analysis-alternatives.R

@@ -11,9 +11,10 @@ rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
-  class3,
+  class3,class11d,class6,
   homclass,
   homclass_wght,know_total,
+  homclass2,
   Q03pcm,
   edyears,
   female,
@@ -36,6 +37,28 @@ dfreg <- df1 %>% dplyr::select(
   na.omit()
 
 
+sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
+
+sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
+
+
+df1$homclass2
+
+
+sjPlot::plot_model(model = lmer(homclass~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
+
+sjPlot::plot_model(model = lmer(homclass_wght~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
+
+
+sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6")
+
+sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="DEU")),type = "pred",terms = "class6")
+
+sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="USA")),type = "pred",terms = "class6")
+
+
+
+df1$class11d
 dfreg <- 
   dfreg %>% 
   mutate(to_dummy(female),
@@ -85,6 +108,8 @@ dfreg <-
             Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
 names(dfreg)
 
+
+# dfreg$homclass<- dfreg$homclass2
 
 # Models 
 base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)

### 2024-02-04 paper1_jiturra.Rmd
up

@@
 css: "input/css/custom.css" # custom CSS para html
-fontsize: 11pt
-linestretch: '1.5'          # interlineado 
+fontsize: 12pt
+linestretch: '1.15'          # interlineado 
 papersize: a4
 link-citations: yes         # citas linkeadas
+lang: en-US
 # date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-date: "`r format(Sys.Date(), '%d %B %Y')`"
+date: "`r format(Sys.Date(), '%d %b %Y')`"
 author:
@@
     keep_tex: false
-    number_sections: false
+    number_sections: true
     pandoc_args:
@@
 always_allow_html: true      
-linkcolor: blue                         # enlaces y citas en color azul
+linkcolor: black                         # enlaces y citas en color azul
 bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
@@
 
-```{r}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(theme_minimal())
-ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
-```
+# Introduction
 
-# Class-based mechanism on attitudes toward economic inequality and welfare
+[~500 words]
 
-key concepts: material interests, normative motivations, within-class differences,
+# Theoretical views on class, social networks, and redistributive preferences
 
-The link between social class and political attitudes constitutes one of the most significant findings in sociology.
-The conceptual basis of these studies lies in the organization of classes as social barriers delineated mainly by ownership of the means of production, autonomy over one's work, and control over the work of others [@Erikson1992].
-This perspective has been adopted from research on social mobility, focusing on occupations and their contractual status as fundamental characteristics to distinguish social classes [@ishida_trends_2005;@hertel_relation_2019].
-Besides the literature on stratification and mobility, classes also trace distinctions in other domains of social life concerning voting behavior [@mainwaring_left_2015;@evans_decline_1993], cultural preferences [@Chan2007], and political attitudes [@Svallfors2006].
-Regarding the latter, according to @lindh_class_2020, research on the link between class position and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and the social service functions of the welfare state (p.
-421).
-In addition, the study of attitudes has been highlighted in the sociocultural domain, including people's views on issues such as gender relations, race and ethnicity, environmentalism, and sexuality (p.
-425), as well as in the political domain concerning the capacity of political institutions to respond to the demands of the citizenry.
-Consequently, two main competing mechanisms that have linked class to attitudes in the economic domain can be mentioned.
-On the one hand, into those linked to material-self interests, and on the other hand, the mechanisms associated with normative motivations and values.
+[~3000 words]
 
-First, the self-interest mechanism has functioned as a canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981].
-Similarly, an extension of the model has incorporated the dimension of economic risk (e.g., unemployment), paying attention to occupations as the unit that conveys it; consequently, positions with greater exposure to risk would tend to be more in favor of measures that mitigate labor market risks [@rehm_risks_2009].
-Second, part of the literature on Western societies has highlighted the cognitive dimension in preference formation.
-On the one hand, it is suggested that people with limited material resources oppose redistributive measures due to the inability to successfully link their condition with the redistributive outcome because of a lack of information, distorting their views on fairness and misaligning their material interests from their preferences [@bartels_homer_2005;@hvidberg_social_2020].
-On the other hand, part of the literature has paid more attention to high-income groups, suggesting that they are far from being monolithic towards inequality when expressing their preferences towards redistribution, arguing that although the rational interest model maintains its general implications, there are nuances within these groups regarding perceived negative externalities that inequality could have at a general level, which would ultimately motivate altruistic support towards redistribution [@rueda_who_2019,@dimick_models_2018].
+## Class divide in the economic domain
 
-Material interests and normative orientations can be comprehended as competing mechanisms in preference formation.
-For example, basic human values such as self-transcendence, characterized by the pursuit of equality and concern for others [@Kulin2013], or humanitarianism, which puts human dignity at the center [@feldman_humanitarian_2001], would be linked to altruistic motivations and might ultimately explain egalitarian economic preferences.
-However, this link may be weakened according to the exposure to risk and the possession of resources, becoming more salient under conditions of greater security against market risks and material prosperity, such as those experienced by the upper classes, and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019].
-In a similar vein, class differences in skills and work logic might influence normative orientations that are ultimately expressed in political attitudes and behavior, being particularly salient among the professional class [@oesch_redrawing_2006].
-Thus, the time that workers spend in their workplace, as well as the social interactions embedded in it, is argued that the work logic operates as a socialization agent according to the type of performed task, where those in interpersonal services tend to be more supportive of progressive political views than those in technical and managerial positions [@oesch_electoral_2018; @edlund_influence_2003].
-However, related research has recently suggested that it is indeed challenging to disentangle whether work logic operates as a socialization agent, where reverse causality should be considered given that early-life socialization in the family context might motivate self-selection processes into specific career paths, or alternatively, decisions in the organizational hiring logic have to be taken into account considering that certain profiles might be preferred for interpersonal or managerial positions [@langsaether_more_2020].
+The link between social class and political attitudes constitutes one of the most relevant findings in sociology.
+Theoretically, studies in the social mobility field have defined classes as structural positions given their difference in labor market situations distinguished by employment relations, skills level, and authority within the workplace, which traditionally has been represented by occupations instead of relative income or educational credentials [@Erikson1992;@Erikson1979].
+Besides the social stratification studies, political sociologists have systematically demonstrated that classes trace distinctions in other domains of social life as well, including ideological preferences [@evans_decline_1993], cultural consumption behavior [@Chan2007] and attitudes toward redistribution and welfare [@Svallfors2006].
+Regarding the latter, during the last decades, the research on class and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and social service functions of the welfare state [@lindh_class_2020, p.
+421].
 
-Critical views have argued that a disincentive of political attitude and behavior in relation to class position.
-The "death of class" thesis has argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group memberships, reorienting the political debate towards post-material issues [@clark_declining_1993;@inglehart_culture_1990].
-Although the process of modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been completely displaced but cohabits with people's attitudes towards the position of women in society as well as their views on migration [@Svallfors2006].
-As far as people's attitudes toward redistribution and the role of the state in providing social welfare are concerned, this thesis has suggested that class cleavage would lose relevance as the material welfare of society increases.
-However, the claimed blurring of the class cleavage has not had particularly strong empirical support in terms of people's preferences around the economic domain.
+Critical views have suggested that economic development and modernization have eroded the link between social class and political attitudes.
+Around the debate of the "death of class" thesis, it has been argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group identities as more relevant, reorienting the political debate towards post-material concerns [@clark_declining_1993;@inglehart_culture_1990].
+However, although modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been wholly displaced but cohabits with people's attitudes in the sociocultural domain [@lindh_class_2020].
+Empirically, the claimed blurring of the class cleavage has not been strongly supported, whereas class divides indeed shape attitudes in the economic domain in general, such as perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes toward market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences in particular [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
+In the broader context, scholars have identified two competing mechanisms to elucidate the relationship between social class and attitudes towards inequality, commonly referred to as the self-interest and normative value-driven motives perspectives.
 
-	[Evidence on class and political attitudes]
-# Network segregation and social class	
-While previous research has focused more extensively on the economic dimension of social class, such as employment relations and occupation, patterns of social interactions are also a constituent dimension of how classes shape their political views toward economic inequality.
-Given that social classes are defined in terms of property, authority, and power, they can be understood as fundamentally relational.
-Therefore, it would be arguable that class positions are not merely distinguished by the labor market position, authority, and control over labor but are also relationally defined based on their patterns of sociability.
-Hereby, the scope of class analysis in the formation of attitudes and behavior can be extended further to the individual and household situation, stressing the role of social interactions and network segregation processes that might influence the internalization of shared norms, identity formation, and conflict between classes.
+Theoretically, self-interest has served as the canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981].
+Similarly, extensions of the model have paid more attention to occupation as a representation of potential unemployment risk, arguing that social classes with greater risk exposure are prone to support redistributive policies as they reduce labor market insecurity [@rehm_risks_2009].
+Differently, part of the scholarly discussion has stressed the role of cognitive processes in preference formation for understanding why, even in contexts of greater economic disparities, the lower classes oppose redistributive policies, arguing that misinformation plays a crucial role in linking material conditions with the redistributive policies [@bartels_homer_2005;@druckman_preference_2000].
+Similarly, it has been argued that contexts of greater segregation affect the inferences about social and economic inequality [@summers_deliberating_2022;@mijs_inequality_2018] that ultimately contribute to the decoupling of material interests from economic preferences [@hvidberg_social_2020;@garcia-castro_changing_2022].
 
-For stratification scholars, the study of segregation relates to the inequality in the distribution of status position and group membership heterogeneity as the observable patterns of association that shape interpersonal ties often referred to as relational networks [@blau_inequality_1977].
-Indeed, one of the most significant findings on network research is the stronger contact frequency and tie formation between individuals of similar characteristics described as homophily [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], demonstrating that associations are segregated according to the degree of demographic availability of social groups, as well as by status differentiation that intersect group membership [@bargsted_pautas_2020; @plaza_juntos_2022].
-However, it has been argued that segregation is also affected by sociopsychological factors, where in-group dynamics tend to be reinforced when attitudes and behavior are concentrated in isolated social environments, decreasing the chances of interchange of world views and opinions [@visser_attitudes_2004; @diprete_segregation_2011].
-Nonetheless, besides the importance of socialization preferences, it has been argued that the distribution of status positions and group diversity tend to be more dominant in structuring social activities that provide opportunities for opportunity for contact and consolidation of social networks [@feld_focused_1981; @mcpherson_network_2019].
-As for social classes, it could be argued that classes represent social differentiation insofar as they not only consider differences in status resources but also comprise patterns of sociability so that segregation can also be observed in terms of the distribution of social ties regarding class positions.
+As material interests might prevail in scarcity, normative or value-driven motivations emerge as an alternative explanation in preference formation when pure self-interest weakens.
+Thus, values such as self-transcendence or humanitarianism share a common spirit regarding their desire for equality and concern for human dignity, providing the common ground for altruism that ultimately motivates egalitarian preferences [@Kulin2013;@feldman_humanitarian_2001].
+However, the protagonism of values is indeed conditioned to risk exposure and resource availability, becoming salient under conditions of greater security against market risks and material prosperity and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019].
+Related arguments have suggested that skills specificity and work logic represented in occupations play a role in forming political attitudes [@oesch_redrawing_2006].
+Specifically, it is argued that the work logic, together with the performed tasks, socializes individuals given the time spent in their job as well as the provision of goods and services, suggesting that technical and managerial occupations hold more conservative political views compared to those performing interpersonal services [@oesch_electoral_2018].
+However, it is challenging to disentangle if the class differences in attitudes are indeed explained through political socialization developed within workplaces because they might result from the internalization of social norms in early-life socialization that motivate self-selection into specific career paths or the organizational hiring logic requirements for interpersonal or managerial positions [@kitschelt_occupations_2014].
+
+While prior research has predominantly concentrated on examining the impact of social class through an individualistic lens, it is noteworthy that more attention needs to be devoted to understanding the role of social environments in class relations.
+This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
+Besides, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis of the legitimacy and popular support for welfare schemes [@mau_moral_2003].
+Hereby, we argue that the scope of class analysis in attitude formation urges to be extended further to the individual or household situation, stressing the role of social ties and segregation as part of the socialization processes involved in the internalization of shared norms, class identity formation, conflict, and cooperation between classes.
+
+## Class relations and social networks
+
+As social relations within the occupational structure serve as the foundation for class analysis, widening the examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relation to attitude formation.
+In this sense, social stratification scholars have paid attention to the intersection of status positions and group membership as the observable patterns of association referred to as relational networks [@blau_inequality_1977].
+Empirically, homophily is one of the most significant findings in network research, whereas the likelihood of tie formation between individuals of similar characteristics is strong [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], such as age and gender in tracing friendship and family ties, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022].
+In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing preferences towards in-group members and polarizing attitudes [@visser_attitudes_2004; @diprete_segregation_2011].
+Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities that work as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
+From this scope, we argue that class positions consider differences in economic or cultural resources and patterns of sociability observed in the distribution of social ties.
 
 How classes are formed also provides insights regarding their social relations and sociability practices.
-In sociology,  classes are understood as the common basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978].
-According to habitus theory, classes seek to improve and maintain their position by stressing the importance of intergenerational transmission of resources, which is accomplished through the reproduction of socialization patterns and lifestyles expressed in tie formation between groups of similar status when it comes to partner and friendship choices, arguing that class *habitus* entails a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
-Symbolic resources such as skills and education credentials serve to reinforce status distinctions between upper and lower classes, granting access to socially segregated environments and increasing the likelihood of reproducing privileged positions at the expense of lower classes [@bourdieu_reproduccion_1981].
+In sociology, classes are understood as the everyday basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978].
+According to habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
+Thus, classes seek to improve their position through the intergenerational transmission of resources, whereas similarities in friendship and family choices play a crucial role in the reproduction privilege.
+Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding the lower classes [@bourdieu_reproduccion_1981].
 Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
@@
 It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position.
-At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to a certain group that does not necessarily count with a reference position to describe the network composition.
+At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
 Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.
 
-# Class boundaries and political attitudes
+# Data, variables and method
+
+[1500 words]
+
+# Results
+
+# Discussion and conclusion
 

### 2024-02-04 procesamiento/prod_analysis-alternatives.R

@@ -11,10 +11,13 @@ rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
-  class3,class11d,class6,
+  class3,
+  # class3=digclass3,
+  # class3=dclass3,
   homclass,
-  homclass_wght,know_total,
-  homclass2,
+  # homclass=homclass2,
+  # homclass=homclass3,
+  know_total,
   Q03pcm,
   edyears,
   female,
@@ -25,6 +28,7 @@ dfreg <- df1 %>% dplyr::select(
   region,
   "gini_disp",
   "gini_mkt",
+  gv_spen,
   d10d1,
   rgdpna,
   oecd,
@@ -33,32 +37,18 @@ dfreg <- df1 %>% dplyr::select(
   mutate(logrgdpna = log(rgdpna),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
-  filter(country2 != "SVN") %>%
+  filter(country2 != "SVN") %>% 
   na.omit()
 
 
-sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
+# sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
+# sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
+# sjPlot::plot_model(model = lmer(homclass~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
+# sjPlot::plot_model(model = lmer(homclass_wght~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
+# sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6")
+# sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="DEU")),type = "pred",terms = "class6")
[…]

### 2024-02-05 paper1_jiturra.Rmd
up

@@
   - \setlength\parindent{24pt} 
+  - \usepackage{fancyhdr}
+  - \fancyhead{} 
 ---
@@
 ```
-
+\pagestyle{fancy}
+\fancyhead[R]{ \thepage}
+\fancyhead[L]{Julio Iturra-Sanhueza}
 # Introduction
@@
 Differently, part of the scholarly discussion has stressed the role of cognitive processes in preference formation for understanding why, even in contexts of greater economic disparities, the lower classes oppose redistributive policies, arguing that misinformation plays a crucial role in linking material conditions with the redistributive policies [@bartels_homer_2005;@druckman_preference_2000].
-Similarly, it has been argued that contexts of greater segregation affect the inferences about social and economic inequality [@summers_deliberating_2022;@mijs_inequality_2018] that ultimately contribute to the decoupling of material interests from economic preferences [@hvidberg_social_2020;@garcia-castro_changing_2022].
+Similarly, it has been argued that contexts of greater segregation affect the inferences about social and economic inequality [@mijs_inequality_2018] that ultimately contribute to the decoupling of material interests from economic preferences [@hvidberg_social_2020;@garcia-castro_changing_2022].
 
 As material interests might prevail in scarcity, normative or value-driven motivations emerge as an alternative explanation in preference formation when pure self-interest weakens.
-Thus, values such as self-transcendence or humanitarianism share a common spirit regarding their desire for equality and concern for human dignity, providing the common ground for altruism that ultimately motivates egalitarian preferences [@Kulin2013;@feldman_humanitarian_2001].
-However, the protagonism of values is indeed conditioned to risk exposure and resource availability, becoming salient under conditions of greater security against market risks and material prosperity and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019].
-Related arguments have suggested that skills specificity and work logic represented in occupations play a role in forming political attitudes [@oesch_redrawing_2006].
-Specifically, it is argued that the work logic, together with the performed tasks, socializes individuals given the time spent in their job as well as the provision of goods and services, suggesting that technical and managerial occupations hold more conservative political views compared to those performing interpersonal services [@oesch_electoral_2018].
-However, it is challenging to disentangle if the class differences in attitudes are indeed explained through political socialization developed within workplaces because they might result from the internalization of social norms in early-life socialization that motivate self-selection into specific career paths or the organizational hiring logic requirements for interpersonal or managerial positions [@kitschelt_occupations_2014].
+Thus, values such as self-transcendence or humanitarianism share a common spirit regarding their desire for equality and concern for human dignity, providing the common ground for altruism that ultimately motivates political preferences [@Kulin2013;@feldman_humanitarian_2001].
+Despite the protagonism of values, these are indeed conditioned to risk exposure and resource availability, becoming salient under conditions of greater security against market risks and material prosperity and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019].
+Besides, it has been argued that occupations play a role in political attitude formation as they represent a set of specific skills and work logic that convey particular normative views [@oesch_redrawing_2006].
+Thus, workspaces are conceived as socializing agents, considering that economically active people spend a substantial part of their time at work, including the social relations involved in providing goods and services.
+Hence, empirical evidence has suggested that technical and managerial professionals hold more conservative political views than occupations in interpersonal services [@oesch_electoral_2018;@lindh_class_2020].
+Despite this, it is challenging to disentangle if the class differences are indeed explained through work experiences because it is feasible to argue that political preferences are the result of early-life internalization of social norms, which might be crystalized in career self-selection paths, which also might be influenced by the organizational hiring requirements for specific jobs [@kitschelt_occupations_2014].
 
@@
 In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing preferences towards in-group members and polarizing attitudes [@visser_attitudes_2004; @diprete_segregation_2011].
-Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities that work as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
-From this scope, we argue that class positions consider differences in economic or cultural resources and patterns of sociability observed in the distribution of social ties.
+Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
+From this scope, we argue that class relations not only represent resources-based distinctions, but patterns of sociability and exchange observed in the differentiation of social ties.
 
@@
 Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
-Altogether, these processes further reinforce social distinctions between classes and contribute to the persistence of class structures.
-Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes.
-Access to social resources embedded in social networks follows a pattern of accumulation that reproduces pre-existing inequalities, in which class positions are vital in accounting for mechanisms of exclusion and segregation across the class structure.
+Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, whereas social resources embedded in social networks follow a pattern of accumulation and exclusion that ultimately leads to social segregation in both the upper and the lower bounds of the social structure.
 
 Previous research on social class and tie formation has suggested that class permeability, understood as the formation of cross-class social ties, is traced differently across property and authority boundaries.
-Empirically, evidence from Western industrialized countries has shown that the formation of friendship ties between owners and the working class is very less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the authority dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
+Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is very less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the authority dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
 Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that isolate them from others, while the upper class is less permeable and homogenous as a result of its tendency to self-selection as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
@@
 In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in its civic engagement behavior.
-Similarly, other studies in Argentina and Croatia have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation, whereas it does not equalize the weight of class background compared to those intergenerationally stable in the upper class [@cepic_how_2020;@carrascosa_class_2023].
+Similarly, other studies in Europe and South America have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation, whereas it does not equalize the weight of class background compared to those intergenerationally stable in the upper class [@cepic_how_2020;@carrascosa_class_2023].
 Additionally, the few longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions while the lower class shows more stability across the life course [@volker_social_2020].
 
-Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to vertically represent social resources embedded in social networks [@lin_social_2007].
+Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
 Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977].
-Therefore, _homogeneity_  is described as the lack of cross-class network ties.
+Besides, _homogeneity_  is described as the lack of cross-class network ties.
 It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position.
@@
 Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.
+
+## Network segregation and attitudes toward redistribution
+
+Apart from the individual approach to attitude formation, we argue that people also form their opinions in the economic domain on the basis of their social relations.
+Despite the limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of social networks in attitude formation.
+
+On the one hand, the _Reference Groups_ approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form their opinions about redistributive policies [@condon_economic_2020].
+This hypothesis can be traced to the studies on images of class and perceived class conflicts [@Evans1992;@KelleyEvans1995].
+Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
+467].
+From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping inequality perceptions [@mijs_is_2021].
+Thus, conversations with friends, family, and work colleagues shape inequality beliefs through experience sharing.
+Interestingly, research employing collaborative games has shown that the socioeconomic diversity of participants in conversations contributes to reconstructing more accurate images of income and wealth inequalities than isolated individuals [@summers_deliberating_2022].
+However, we argue that this research field has been more focused on the cognitive or informational dimension of preference formation through inequality perceptions [see @cansunar_who_2021;@garcia-castro_perceived_2022] or the role of informational treatments [see @Cruces2011;@mccall_exposure_2017;@becker_significant_2021], rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes towards inequality.
 

### 2024-02-06 paper1_jiturra.Rmd
update meeting

@@
 \fancyhead[R]{ \thepage}
-\fancyhead[L]{Julio Iturra-Sanhueza}
+\fancyhead[L]{Research Article Draft}
 # Introduction
@@
 [~500 words]
+
+- What is the role of class-based network segregation on redistributive preferences?
+
+- Does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
 
@@
 
-As social relations within the occupational structure serve as the foundation for class analysis, widening the examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relation to attitude formation.
-In this sense, social stratification scholars have paid attention to the intersection of status positions and group membership as the observable patterns of association referred to as relational networks [@blau_inequality_1977].
-Empirically, homophily is one of the most significant findings in network research, whereas the likelihood of tie formation between individuals of similar characteristics is strong [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], such as age and gender in tracing friendship and family ties, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022].
-In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing preferences towards in-group members and polarizing attitudes [@visser_attitudes_2004; @diprete_segregation_2011].
+As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
+In principle, social stratification scholars have traditionally paid attention to _differentiation_ as the observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
+Empirically, homophily is one of the most significant findings in network research, whereas the likelihood of tie formation between individuals of similar characteristics is strong [@mcpherson_birds_2001; @lazarsfeld_friendship_1954] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022].
+In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
 Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
@@
 Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
-Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977].
+Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_inequality_1977].
 Besides, _homogeneity_  is described as the lack of cross-class network ties.
@@
 
-On the one hand, the _Reference Groups_ approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form their opinions about redistributive policies [@condon_economic_2020].
-This hypothesis can be traced to the studies on images of class and perceived class conflicts [@Evans1992;@KelleyEvans1995].
+On the one hand, one approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form their opinions about redistributive policies [@condon_economic_2020].
+This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@KelleyEvans1995].
 Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
@@
 From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping inequality perceptions [@mijs_is_2021].
-Thus, conversations with friends, family, and work colleagues shape inequality beliefs through experience sharing.
-Interestingly, research employing collaborative games has shown that the socioeconomic diversity of participants in conversations contributes to reconstructing more accurate images of income and wealth inequalities than isolated individuals [@summers_deliberating_2022].
-However, we argue that this research field has been more focused on the cognitive or informational dimension of preference formation through inequality perceptions [see @cansunar_who_2021;@garcia-castro_perceived_2022] or the role of informational treatments [see @Cruces2011;@mccall_exposure_2017;@becker_significant_2021], rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes towards inequality.
+Thus, experience sharing in conversations with socioeconomically diverse networks has been proved to contribute to the accuracy of the images of income and wealth inequalities in contrast to people in more isolated discussion networks [@summers_deliberating_2022].
+Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [e.g.
+@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [e.g.
+@Cruces2011;@becker_significant_2021], rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
+
+On the other hand, a different approach has suggested that the observed patterns of social ties through a network approach provide a broader image of class relations that ultimately contribute to the consolidation of social norms and group identity [@kalmijn_social_2007, p.
+550].
+This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to the individual or household material well-being, cultural perspectives, and political preferences that structure the broader social experiences [@morris_attenuation_1996, p.
+48].
+
+More direct evidence on social ties, class, and redistributive preferences in general populations will be discussed here.
+First, starting with the case of the United States [@lee_consider_2023], then Sweden [@lindh_missing_2021], and cross-country comparisons in Europe [@paskov_crossclass_2022].
+Additionally, studies on network segregation on preferences for market distribution of social services [@beck_explorando_2019] and attitudes towards inequality in general [@otero_power_2023].
+
+## Economic Inequality, segregation, and redistributive preferences
+
+Income inequality can deteriorate social bonding and increase segregation.
+
+* status anxiety among the upper-classes [@wilkinson_spirit_2010] and lower interpersonal trust  [@kragten_income_2017]
+
+* limited opportunities for social mobility consequently reduce class permeability in social networks [@otero_differences_2023]
+
+However, it has been discussed that inequality might also increase egalitarian preferences among those in better material situations.
+
+* concerns about the negative consequences (e.g. crime) of inequality on overall social welfare, particularly in high-status groups (Altruism) [@rueda_who_2019]
+
+* convergence in egalitarian preferences in the upper-classes can be normatively grounded according to views about equality of opportunities (Procedural Justice) [@sachweh_why_2019]
+
+\pagebreak
+
+# Overview
+
+## At the micro-level:
+
+- (H1) Being segregated in similar class environments polarize own class interests:
+    * Segregated lower (upper) classes hold more (less) redistributive preferences
+
+## At the macro-level:
+
+- (H2a) Scenario A (booster): Inequality increases the influence of class segregation on redistributive preferences (polarization)
+
+- (H2b) Scenario B (mitigation): Inequality diminishes the influence of class segregation on redistributive preferences (consensus)
 
@@
 
-# References
+`r if (is_latex_output()) '
+# References {-}
+'`
+```{=tex}
+\scriptsize
+\singlespacing
+```

### 2024-02-06 procesamiento/01-prod_prep-micro.Rmd
update meeting

@@
 
+```{r}
+
+sjmisc::frq(df1$v46)
+
+table(df1$country,df1$v46)
+
+# (1+4)/2
+# (5+9)/2
+# (10+19)/2
+# (20+49)/2
+# (50+99)/2
+# 100
+
+df1$week_cont <- as.numeric(car::recode(df1$v46,"c(8,9)=NA;1=2.5;2=7;3=14.5;4=34.5;5=74.5;6=100"))
+
+sjmisc::frq(df1$week_cont)
+sjPlot::tab_corr(df1[,c("know_total","week_cont","homclass")])
+
+a <- df1 %>% dplyr::select("know_total","week_cont","homclass") 
+a$country <- NULL
+a$week_cont <- as.factor(a$week_cont)
+polycor::hetcor(data = as.data.frame(a))
+
+sjPlot::plot_grpfrq(var.grp = df1$class6,var.cnt = df1$know_total,type = "box",ylim = c(0,10))
+sjPlot::plot_grpfrq(var.grp = df1$class6,var.cnt = df1$week_cont,type = "box",ylim = c(2.5,100))
+```
+
 # Demographics

### 2024-02-06 procesamiento/prod_analysis-alternatives.R

@@ -17,7 +17,7 @@ dfreg <- df1 %>% dplyr::select(
   homclass,
   # homclass=homclass2,
   # homclass=homclass3,
-  know_total,
+  know_total=week_cont,
   Q03pcm,
   edyears,
   female,
@@ -40,6 +40,8 @@ dfreg <- df1 %>% dplyr::select(
   filter(country2 != "SVN") %>% 
   na.omit()
 
+# dfreg$know_total<- as.factor(dfreg$know_total)
+dfreg$know_total<- log(dfreg$know_total)
 
 # sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
 # sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
@@ -67,7 +69,7 @@ dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
 dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
 dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
 dfreg$homclass_gc = group_center(dfreg$homclass, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
 
 
 # EGP: dominance

### 2024-02-07 procesamiento/02-prod_prep-macro.Rmd
up

@@
 solt <- 
-swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt) %>% dplyr::filter(year %in% c(2016))
+swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt,abs_red,rel_red) %>% dplyr::filter(year %in% c(2016))
 solt$ccode <- countrycode::countrycode(sourcevar = solt$country,origin = "country.name",destination = "iso3n")
@@
 solt_2017 <-  solt %>% filter(ccode %in% countries$ccode) %>% 
-  select(ccode,gini_disp,gini_mkt)
+  dplyr::select(ccode,gini_disp,gini_mkt,abs_red,rel_red)
 ```
@@
 save(df2,file = here::here("input/data/proc/study1_country.RData"))
-haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
+# haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
 sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )

### 2024-02-07 procesamiento/prod_analysis-alternatives.R

@@ -17,7 +17,9 @@ dfreg <- df1 %>% dplyr::select(
   homclass,
   # homclass=homclass2,
   # homclass=homclass3,
-  know_total=week_cont,
+  # know_total=week_cont,
+  class6,
+  know_total,
   Q03pcm,
   edyears,
   female,
@@ -39,7 +41,9 @@ dfreg <- df1 %>% dplyr::select(
          age2 = agenum ^ 2) %>%
   filter(country2 != "SVN") %>% 
   na.omit()
-
+dfreg$abs_red <- dfreg$gini_mkt - dfreg$gini_disp 
+dfreg$rel_red <- dfreg$abs_red/dfreg$gini_mkt
+summary(dfreg$rel_red)
 # dfreg$know_total<- as.factor(dfreg$know_total)
 dfreg$know_total<- log(dfreg$know_total)
 
@@ -47,9 +51,18 @@ dfreg$know_total<- log(dfreg$know_total)
 # sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
 # sjPlot::plot_model(model = lmer(homclass~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
 # sjPlot::plot_model(model = lmer(homclass_wght~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
-# sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6")
-# sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="DEU")),type = "pred",terms = "class6")
-# sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="USA")),type = "pred",terms = "class6")
+sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6",title = "Sweden")
[…]

### 2024-02-07 procesamiento/prod_analysis-alternatives.R
Update prod_analysis-alternatives.R

@@ -51,18 +51,13 @@ dfreg$know_total<- log(dfreg$know_total)
 # sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
 # sjPlot::plot_model(model = lmer(homclass~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
 # sjPlot::plot_model(model = lmer(homclass_wght~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
-sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6",title = "Sweden")
-sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="DEU")),type = "pred",terms = "class6",title = "Germany")
-sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="GBR")),type = "pred",terms = "class6",title = "Great Britain")
-sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="USA")),type = "pred",terms = "class6",title = "United States")
 
-
-cowplot::plot_grid(
-  sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6",title = "Sweden"),
-  sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="DEU")),type = "pred",terms = "class6",title = "Germany"),
-  sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="GBR")),type = "pred",terms = "class6",title = "Great Britain"),
[…]

### 2024-02-07 procesamiento/prod_analysis-alternatives.R
Update prod_analysis-alternatives.R

@@ -214,7 +214,6 @@ int_homo_relR_gc <-
 
 knitreg(list(base_relR_gc,int_homo_relR_gc))
 
-
 # CROSS-LEVEL INTERACTION WITH CENTERED VARIABLES -------------------------------------------------------
 ############################################################################-
 

### 2024-02-08 procesamiento/02-prod_prep-macro.Rmd
update interacciones

@@
 
+wiid_s80s10 <- 
+  read.csv(file = here::here("input/data/original/wid-percentiles/wiid-data-P80P20.csv"),sep = ";")
+names(wiid_s80s10) <- tolower(names(wiid_s80s10))
+names(wiid_s80s10) <- gsub('\\.', '', names(wiid_s80s10))
+wiid_s80s10$ccode <- countrycode::countrycode(sourcevar = wiid_s80s10$iso,origin = "iso3c",destination = "iso3n")
+
+wiid_s80s10 <- 
+  wiid_s80s10 %>%  
+  filter(ccode %in% countries$ccode) %>% 
+  filter(year==2017) %>% 
+  select(ccode,everything(),-iso,-country,-year,-giniindex)
+
 wiid_2017 <- 
@@
   select(ccode,everything(),-iso,-country,-year) %>% 
-  left_join(wiid_d10d01,by="ccode")
+  left_join(wiid_d10d01,by="ccode") %>% 
+  left_join(wiid_s80s10,by="ccode")
 ```
@@
 swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt,abs_red,rel_red) %>% dplyr::filter(year %in% c(2016))
+summary(solt)
 solt$ccode <- countrycode::countrycode(sourcevar = solt$country,origin = "country.name",destination = "iso3n")
@@
 solt_2017 <-  solt %>% filter(ccode %in% countries$ccode) %>% 
-  dplyr::select(ccode,gini_disp,gini_mkt,abs_red,rel_red)
+  dplyr::select(ccode,gini_disp,gini_mkt)
+
+solt_2017$abs_red <- solt_2017$gini_mkt - solt_2017$gini_disp 
+solt_2017$rel_red <- solt_2017$abs_red/solt_2017$gini_mkt
+summary(solt_2017)
 ```

### 2024-02-08 procesamiento/prod_analysis-alternatives.R

@@ -30,22 +30,44 @@ dfreg <- df1 %>% dplyr::select(
   region,
   "gini_disp",
   "gini_mkt",
+  gini,
   gv_spen,
+  rel_red,
   d10d1,
+  s80s20,
+  top10,
+  palmaratio,
   rgdpna,
+  gdppercapita,
   oecd,
   country2, country
 ) %>%
   mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
   filter(country2 != "SVN") %>% 
+  # filter(country2 != "ZAF") %>%
+  # filter(country2 != "HUN") %>% 
+  filter(oecd == "OECD") %>%
   na.omit()
-dfreg$abs_red <- dfreg$gini_mkt - dfreg$gini_disp 
-dfreg$rel_red <- dfreg$abs_red/dfreg$gini_mkt
+
 summary(dfreg$rel_red)
 # dfreg$know_total<- as.factor(dfreg$know_total)
 dfreg$know_total<- log(dfreg$know_total)
+
+dfreg <- as.data.frame(dfreg)
+
+dfreg_country <- 
+dfreg %>% 
+  group_by(country2) %>% 
+  summarise_at(.vars = c("homclass","egal","gini_disp","gini_mkt",
+                         "rel_red","loggdppercapita"),
+               .funs = mean) %>% 
+  dplyr::select(-country2) 
+  
+sjPlot::tab_corr(dfreg_country,triangle = "lower")
+ggpairs(dfreg_country, lower=list(continuous="smooth"), diag = list(continuous = NULL))
 
 # sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
 # sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
@@ -109,10 +131,9 @@ dfreg <-
             Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
 names(dfreg)
 
-
 # dfreg$homclass<- dfreg$homclass2
 
-# Models 
+# Micro level models -----------------------------------------------------------
 base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
 homclass<- update(base, . ~ . +homclass)
 homclass_know_total<- update(homclass, . ~ . +know_total)
[…]

### 2024-02-09 procesamiento/03-prod_analysis-descriptives.Rmd
up all

@@
   summarise(redist = mean(redist,na.rm = T),
-            egal
             homclass = mean(homclass,na.rm = T),
@@
 
-df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
-df2$country3 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "iso3c")
-df2 <- bind_cols(df2,sjmisc::to_dummy(x = df2$class3,suffix = "numeric"))
+dfreg$country2 <- countrycode::countrycode(sourcevar = dfreg$country,origin = "iso3n",destination = "country.name")
+dfreg$country3 <- countrycode::countrycode(sourcevar = dfreg$country,origin = "iso3n",destination = "iso3c")
+dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
 
-macro_data <- df2 %>%
+macro_data <- dfreg %>%
   group_by(country2,country3) %>%
-  summarise_at(c("egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
-                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
+  summarise_at(c("egal2","homclass","gini_disp","gini_mkt",
+                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
   as.data.frame()
+
+homclass_work <- dfreg %>%
+  filter(class3=="Working Class (VI+VII)") %>% 
+  group_by(country3) %>%
+  summarize(homclass_work= mean(homclass, na.rm = TRUE))
+
+homclass_inte <- dfreg %>%
+  filter(class3=="Intermediate class (III+IV+V)") %>% 
+  group_by(country3) %>%
+  summarize(homclass_inte= mean(homclass, na.rm = TRUE))
+
+homclass_serv <- dfreg %>%
+  filter(class3=="Service Class (I+II)") %>% 
+  group_by(country3) %>%
+  summarize(homclass_serv= mean(homclass, na.rm = TRUE))
+macro_data <- 
+macro_data %>% 
+  full_join(homclass_work) %>% 
+  full_join(homclass_inte) %>% 
+  full_join(homclass_serv)
+
+macro_data %>% 
+  dplyr::select(egal2,gini_disp,starts_with("homclass"),"class3_1","class3_2","class3_3") %>% 
+  correlation::correlation() %>% 
+  summary()
 
@@
 
-macro_data %>%  
-ggplot(aes(y=homclass, x=gini_disp)) +
-  # geom_point() +
-  geom_text(label=as.character(macro_data$country3)) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
+homo_ineq <- dfreg %>%
+  # filter(country3 != "ZAF") %>%
+  group_by(country2,country3,class3) %>%
+  summarise_at(c("homclass","egal2","gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+
+homo_ineq %>%
+ggplot(aes(y=homclass, x=gini_disp, group=class3,fill=class3)) +
+  geom_text(label=as.character(homo_ineq$country3)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black") +
+  facet_wrap(~class3) +
   xlab("Gini (Disposable)")+
   ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Gini (Disposable)",
-       caption =paste("r=",round(cor(macro_data$homclass,
-                                     macro_data$gini_disp),digits = 2)))
+  labs(title = "Class homogeneity and Gini (Disposable)") +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
+  theme(legend.position = "bottom",legend.title = element_blank())
+
+homo_ineq %>%
+ggplot(aes(y=egal2, x=homclass, group=class3,fill=class3)) +
+  geom_text(label=as.character(homo_ineq$country3)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black") +
+  facet_wrap(~class3) +
+  xlab("Class homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(title = "Class homogeneity and Redistributive preferences") +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
+  theme(legend.position = "bottom",legend.title = element_blank())
 
 ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
-       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
-
-macro_data %>%  
-ggplot(aes(y=homclass, x=gini_mkt)) +
-  # geom_point() +
-  geom_text(label=as.character(macro_data$country3)) +
-  # scale_x_continuous(limits = c(0,1))+
-  # scale_y_continuous(limits = c(1,5))+
-  geom_smooth(method = "lm",fullrange=TRUE) +
-  xlab("Gini (Market)")+
-  ylab("Class homogeneity") +
-  labs(title = "Class homogeneity and Gini (Market)",
-       caption =paste("r=",round(cor(macro_data$homclass,
-                                     macro_data$gini_mkt),digits = 2)))
-
-ggsave(plot = last_plot(),filename = "macro_giniM_homo.png",device = "png",
-       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)
+       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 20)
 

### 2024-02-09 procesamiento/prod_analysis-alternatives.R

@@ -44,17 +44,21 @@ dfreg <- df1 %>% dplyr::select(
 ) %>%
   mutate(logrgdpna = log(rgdpna),
          loggdppercapita=log(gdppercapita),
+         know_total=log(know_total),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
   filter(country2 != "SVN") %>% 
   # filter(country2 != "ZAF") %>%
   # filter(country2 != "HUN") %>% 
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   na.omit()
 
-summary(dfreg$rel_red)
-# dfreg$know_total<- as.factor(dfreg$know_total)
-dfreg$know_total<- log(dfreg$know_total)
+dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric")) %>% 
+  rename(prop_serv=class3_1,prop_inte=class3_2,prop_work=class3_3)
+dfreg <- 
+dfreg %>% 
+  group_by(country2) %>% 
+  mutate(prop_serv=mean(prop_serv),prop_inte=mean(prop_inte),prop_work=mean(prop_work))
 
 dfreg <- as.data.frame(dfreg)
 
@@ -66,8 +70,8 @@ dfreg %>%
                .funs = mean) %>% 
   dplyr::select(-country2) 
   
-sjPlot::tab_corr(dfreg_country,triangle = "lower")
-ggpairs(dfreg_country, lower=list(continuous="smooth"), diag = list(continuous = NULL))
+# sjPlot::tab_corr(dfreg_country,triangle = "lower")
+# GGally::ggpairs(dfreg_country, lower=list(continuous="smooth"), diag = list(continuous = NULL))
 
 # sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
 # sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
@@ -140,12 +144,58 @@ homclass_know_total<- update(homclass, . ~ . +know_total)
 full1 <- update(homclass_know_total, . ~ . + class3+female+agenum+age2)
 rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
 rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
[…]

### 2024-02-12 procesamiento/01-prod_prep-micro.Rmd
a1

@@
 
+df1$class3_V <- car::recode(df1$class11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3_V) <- "Social Class (V to Working Class)"
+frq(df1$class3_V)
+
 # Class Scheme 5 classes
@@
                                      "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$digclass11d) <- "Social Class"
+sjlabelled::set_label(df1$digclass11d) <- "Social Class (isko - v2)"
 frq(df1$digclass11d)
@@
 
-sjlabelled::set_label(df1$digclass3) <- "Social Class"
+sjlabelled::set_label(df1$digclass3) <- "Social Class (isko - v2) "
 frq(df1$digclass3)
+
+df1$digclass3_V <- car::recode(df1$digclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3_V) <- "Social Class (V to Working Class - isko - v2)"
+frq(df1$digclass3_V)
 
@@
 frq(df1$dclass11d)
-sjlabelled::set_label(df1$dclass11d) <- "Social Class"
+sjlabelled::set_label(df1$dclass11d) <- "Social Class (EGP11 -  DIGICLASS)"
 
@@
                             "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3) <- "Social Class"
-frq(df1$dclass3)
-frq(df1$class3)
-frq(df1$digclass3)
+                             3:8='Intermediate class (III+IV+V)';
+                             9:11='Working Class (VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3) <- "Social Class (EGP3 -  DIGICLASS)"
+
+# Class Scheme 3 classes -  V to working class
+df1$dclass3_V <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3_V) <- "Social Class (V to Working Class - DIGCLASS)"
+frq(df1$dclass3_V)
+
+# Class Scheme 3 classes -  IIIb to working class
+
+df1$dclass3_III <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class',
+                                      'Intermediate class',
+                                      'Working Class'), 
+                            "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3_III) <- "Social Class (IIIb to Working Class - DIGCLASS)"
+frq(df1$dclass3_III)
+
+# Class Scheme 3 classes -  IIIb and V to working class
+df1$dclass3_III_V <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class',
+                                      'Intermediate class',
+                                      'Working Class'), 
+                            "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3_III_V) <- "Social Class (IIIb+V to Working Class - DIGCLASS)"
+frq(df1$dclass3_III)
+
+# Class Scheme 6 classes
+df1$dclass6 <- car::recode(
+  df1$dclass11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$dclass6) <- "Social Class (DIGCLASS)"
 ```
@@
 - using my original coding
-```{r homogeneity-v01}
+```{r homogeneity-v01-V-to-intermediate}
 # EI homophily index
@@
 df1$eindex<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-sjlabelled::set_label(df1$eindex) <- "EI homophily index"
+sjlabelled::set_label(df1$eindex) <- "EI homophily index (isko v1 - V to Intermediate)"
 #frq(df1$eindex)
@@
 df1$homclass <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass) <- "Class homogeneity"
+sjlabelled::set_label(df1$homclass) <- "Class homogeneity (V to Intermediate)"
 df1$homclass_gc <- group_center(x = df1$homclass,grp = df1$country)
@@
                                             homclass_gm=mean(homclass,na.rm=T))  
+```
+
+```{r homogeneity-v01-V-to-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(class3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(class3_V,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$class3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex_V<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex_V) <- "EI homophily index (isko v1 - V to Working)"
+#frq(df1$eindex)
+#hist.default(df1$eindex)
+df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
+#hist.default(df1$eindex_gc)
+
+df1 %>% select(class3_V,n_high,n_middle,n_low,outgroup,ingroup,eindex_V)
+df1$homclass_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass_V) <- "Class homogeneity (isko v1 - V to Working)"
+df1$homclass_V_gc <- group_center(x = df1$homclass_V,grp = df1$country)
+# View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
 ```
@@
 
-```{r homogeneity-v02}
+```{r homogeneity-v02-V-intermediate}
 # EI homophily index
@@
 df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
+# View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Group means
+df1 <- df1 %>% group_by(country) %>% mutate(eindex2_gm=mean(eindex2,na.rm=T),
+                                            homclass2_gm=mean(homclass2,na.rm=T))
+```
+
+```{r homogeneity-v02-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(digclass3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(digclass3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex2_V<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex2_V) <- "EI homophily index (isko - v2- V to Working)"
+#frq(df1$eindex)
+#hist.default(df1$eindex2)
+df1$eindex2_V_gc <- group_center(x = df1$eindex2_V,grp = df1$country)
+#hist.default(df1$eindex2_gc)
+
+df1 %>% select(dclass3_V,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass2_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass2_V) <- "Class homogeneity (isko - v2- V to Working)"
+df1$homclass2_V_gc <- group_center(x = df1$homclass2_V,grp = df1$country)
 # View(df1[,c("homclass","homclass_gc")])
@@
 
-```{r homogeneity-R-digclass}
+```{r homogeneity-R-digclass-V-intermediate}
 # EI homophily index
@@
 # View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r homogeneity-R-digclass-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_V,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
+df1$eindex3_V<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
+sjlabelled::set_label(df1$eindex3_V) <- "EI homophily index"
+#frq(df1$eindex)
+#hist.default(df1$eindex)
+df1$eindex3_V_gc <- group_center(x = df1$eindex3_V,grp = df1$country)
+#hist.default(df1$eindex_gc)
+
+df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass3_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_V) <- "Class homogeneity (DIGCLASS version - V to Working)"
+df1$homclass3_V_gc <- group_center(x = df1$homclass3_V,grp = df1$country)
+# View(df1[,c("homclass","homclass_gc")])
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r homogeneity-R-digclass-IIIb-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_III,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Service Class",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Intermediate class",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Working Class",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_III,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+df1 %>% select(dclass3_III,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass3_III <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III) <- "Class homogeneity (DIGCLASS version - IIIb to Working)"
+# Weighted EI index
+# https://arxiv.org/pdf/2109.00348.pdf
+
+# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
+An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
+Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+```
+
+```{r homogeneity-R-digclass-IIIb-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Service Class",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Intermediate class",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Working Class",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,outgroup,ingroup,eindex)
+df1$homclass3_III_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III_V) <- "Class homogeneity (DIGCLASS version - IIIb+V to Working)"
 # Weighted EI index
@@
 sjmisc::frq(df1$week_cont)
-sjPlot::tab_corr(df1[,c("know_total","week_cont","homclass")])
+sjPlot::tab_corr(df1[,c("know_total","week_cont","homclass","homclass_V","homclass2","homclass2_V")])
+
+df1$homclass
 

### 2024-02-12 procesamiento/prod_analysis-alternatives.R

@@ -11,14 +11,14 @@ rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
-  class3,
+  class3=class6,
   # class3=digclass3,
   # class3=dclass3,
   homclass,
   # homclass=homclass2,
   # homclass=homclass3,
   # know_total=week_cont,
-  class6,
+  # class6,
   know_total,
   Q03pcm,
   edyears,
@@ -356,12 +356,11 @@ interaction_list <- as.list(setNames(interaction_terms, interaction_terms))
 #                   file = "output/tables/int_homo_ineq_full-sample.txt")
 
 
-texreg::plotreg(list(int_homo_giniD_gc,
+texreg::screenreg(list(int_homo_giniD_gc,
                       int_homo_d10d1_gc,
                       int_homo_palma_gc,
                       int_homo_s80s20_gc,
-                      int_homo_top10_gc),single.row = T,
-                  custom.coef.map = interaction_list) +
+                      int_homo_top10_gc),single.row = T,"output/tables/int_homo_ineq_full-sample_class6.txt") 
 
 # texreg::screenreg(list(int_homo_giniD_gc,
 #                      int_homo_d10d1_gc,

### 2024-02-12 procesamiento/prod_analysis-class-scheme.R

@@ -1,16 +1,0 @@
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,ggplot2)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-
-df1$class11d
-
-
-frq(df1$class10spo)
-frq(df1$class10)
-
-frq(df1$digclass10)
-
-frq(df1$digclass11)
-frq(df1$digclass11d)

### 2024-02-12 procesamiento/prod_analysis-test-operationalization.R

@@ -1,0 +1,323 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  class3,
+  class3_V,
+  class6,
+  homclass,
+  homclass_V,
+  digclass3,
+  digclass3_V,
+  digclass6,
+  homclass2,
+  homclass2_V,
+  dclass3,
+  dclass3_V,
+  dclass3_III,
+  dclass3_III_V,
+  dclass6,
+  homclass3,
+  homclass3_V,
+  homclass3_III,
+  homclass3_III_V,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp",
+  "gini_mkt",
+  gini,
+  gv_spen,
+  rel_red,
+  d10d1,
+  s80s20,
+  top10,
+  palmaratio,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         # know_total=log(know_total),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN")  
+  # filter(country2 != "ZAF") %>%
+  # filter(country2 != "HUN") %>% 
+  # filter(oecd == "OECD") 
+
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(class3),
[…]

### 2024-02-12 procesamiento/prod_analysis-test-operationalization.R
Update prod_analysis-test-operationalization.R

@@ -281,15 +281,15 @@ homo3_V_giniD <-
   lmer(egal~ 
          homclass3_V_gc+
          know_total_gc+
-         dclass3+
+         dclass3_V+
          female_gc+agenum_gc+age2_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
          union_gc+workst_gc+
          gini_disp +loggdppercapita + rel_red + 
          homclass3_V_gc*
-         dclass3*
+         dclass3_V*
          gini_disp +
-         (homclass3_V_gc+dclass3|country2),data=dfreg,weights = WEIGHT)
+         (homclass3_V_gc+dclass3_V|country2),data=dfreg,weights = WEIGHT)
 
 homo3_III_giniD <- 
   lmer(egal~ 

### 2024-02-14 procesamiento/prod_analysis-alternatives.R
up

@@ -11,7 +11,8 @@ rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
-  class3=class6,
+  class3,
+  # class3=class6,
   # class3=digclass3,
   # class3=dclass3,
   homclass,
@@ -28,9 +29,8 @@ dfreg <- df1 %>% dplyr::select(
   workst,
   WEIGHT,
   region,
-  "gini_disp",
+  "gini_disp"=gini,
   "gini_mkt",
-  gini,
   gv_spen,
   rel_red,
   d10d1,
@@ -150,13 +150,13 @@ rob4 <- update(rob3, . ~ . -(1|country2) + prop_work + prop_serv + (homclass|cou
 # anova(rob1,rob2)
 # Interactions segregation x class
 int_homo <- update(rob4, . ~ . +class3*homclass)
-
 models <- list(homclass,homclass_know_total,full1,rob1,rob3,rob4,int_homo)
 knitreg(models)
 
+# Models for homogeneity by socoial class and inequality 
 fit_homclass <-
-  lmer(homclass~1 +class3+female+agenum+age2 +
-         edyears+ Q03pcm+union+workst +
+  lmer(homclass~1 +class3+female_gc+agenum_gc+age2_gc +
+         edyears_gc + Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+union+workst_gc +
          prop_work + prop_inte + 
          (class3|country2),data=dfreg,weights = WEIGHT)
 fit_homclass_giniM <- update(fit_homclass, . ~ . +class3*gini_mkt+loggdppercapita+rel_red)
@@ -167,8 +167,46 @@ fit_homclass_s80s20<- update(fit_homclass, . ~ .+class3*s80s20+loggdppercapita+r
 fit_homclass_top10 <- update(fit_homclass, . ~ . +class3*top10+loggdppercapita+rel_red)
 
 knitreg(list(fit_homclass,fit_homclass_giniM,
-             fit_homclass_giniD,fit_homclass_d10d1,fit_homclass_palma,
+                ,fit_homclass_d10d1,fit_homclass_palma,
              fit_homclass_s80s20,fit_homclass_top10))
+
+
+plot_predictions(fit_homclass, condition = "class3")
+
[…]

### 2024-02-15 procesamiento/prod_analysis-alternatives.R
update

@@ -11,6 +11,9 @@ rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 dfreg <- df1 %>% dplyr::select(
   egal = egal2,
+  # egal = perineq,
+  # egal = redist,
+  # egal = prefineq,
   class3,
   # class3=class6,
   # class3=digclass3,
@@ -171,7 +174,36 @@ knitreg(list(fit_homclass,fit_homclass_giniM,
              fit_homclass_s80s20,fit_homclass_top10))
 
 
-plot_predictions(fit_homclass, condition = "class3")
+plot_predictions(model = fit_homclass_giniD,condition = "class")
+
+predict_gini_class<- predictions(fit_homclass_giniD, newdata = datagrid(gini_disp = dfreg$gini_disp,class3=levels(dfreg$class3)))
+predict_gini_class <- predict_gini_class %>% dplyr::select(gini_disp,class3,estimate, conf.low, conf.high) %>% as.data.frame()
+
+predict_gini_class$gini_id <- as.character(predict_gini_class$gini_disp) 
+temp1 <- 
+dfreg %>% 
+  group_by(country2,gini_disp) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_id=as.character(gini_disp)) %>% 
+  dplyr::select(-gini_disp)
+
+fit1<- predict_gini_class %>% left_join(temp1,by = "gini_id")
+
+library(ggrepel)
+fit1 %>%
+  ggplot(aes(y=estimate,x=gini_disp, fill=class3,color=class3, group=class3,ymin=conf.low, ymax=conf.high)) +
+  geom_smooth(method = "lm",fullrange=TRUE) +
+  geom_text_repel(aes(x = gini_disp, y = estimate, label = country2),data = fit1,max.overlaps = 31,seed = 123) +
+  geom_ribbon(alpha=0.1) +
+  xlab("Gini (Disposable)")+
+  ylab("Class homogeneity") +
+  facet_grid(~class3) +
+  labs(title = "Class homogeneity and Gini (Disposable)") +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
+  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
+  theme(legend.position = "bottom") 
+
+
 
[…]

### 2024-02-20 paper1_jiturra.Rmd
parrafo class redes

@@
 
-- What is the role of class-based network segregation on redistributive preferences?
-
-- Does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
-
-# Theoretical views on class, social networks, and redistributive preferences
-
-[~3000 words]
-
 ## Class divide in the economic domain
@@
 Hereby, we argue that the scope of class analysis in attitude formation urges to be extended further to the individual or household situation, stressing the role of social ties and segregation as part of the socialization processes involved in the internalization of shared norms, class identity formation, conflict, and cooperation between classes.
+
+- What is the role of class-based network segregation on redistributive preferences?
+
+- Does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
+
+# Theoretical views on class, social networks, and redistributive preferences
+
+[~3000 words]
 
@@
 
-Apart from the individual approach to attitude formation, we argue that people also form their opinions in the economic domain on the basis of their social relations.
-Despite the limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of social networks in attitude formation.
+Apart from the individual approach to attitude formation, we argue that people also form their opinions in the economic domain based on their social relations.
+Despite the limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
 
@@
 From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping inequality perceptions [@mijs_is_2021].
-Thus, experience sharing in conversations with socioeconomically diverse networks has been proved to contribute to the accuracy of the images of income and wealth inequalities in contrast to people in more isolated discussion networks [@summers_deliberating_2022].
+Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared to people in more isolated discussion networks [@summers_deliberating_2022].
 Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [e.g.
@@
 
-On the other hand, a different approach has suggested that the observed patterns of social ties through a network approach provide a broader image of class relations that ultimately contribute to the consolidation of social norms and group identity [@kalmijn_social_2007, p.
+Differently, it has been suggested that the lens of a network approach provides a better picture of the class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
 550].
@@
 48].
+Furthermore, these social relations contribute to the degree to which people reflect on the collective, so that in societies where opportunities for contact between people of different social classes can be detrimental to social integration.
+It has been argued that the social distance among groups widened by extreme inequality can be described as an _empathy gulf_ that comprises barriers to imagining others’ lifestyles and goods, which can also be expressed in spatially segregated interactions and isolated lifeworlds that provide meaning to social inequality experiences, resulting in doubts about worthiness when the lower classes contrast themselves with extravagant lifestyles from the upper classes, undermining feelings of social inclusion and cohesion [@sachweh_moral_2012].
+Consequently, segregation drives the lives of others to become more distant and might have consequences on empathy and solidarity toward others, potentially leading to perceiving fellow citizens as strangers [@otero_lives_2022, p.
+758].
+Thus, we suggest that attitudes towards economic inequality may be influenced by the class situation of both the individual and network ties, resembling the core claims of intergroup contact theory [@pettigrew_metaanalytic_2006] so that social influence processes can either align or polarize attitudes according to the characteristic of groups as well as their contact opportunities given the degree of segregation.
 
-More direct evidence on social ties, class, and redistributive preferences in general populations will be discussed here.
-First, starting with the case of the United States [@lee_consider_2023], then Sweden [@lindh_missing_2021], and cross-country comparisons in Europe [@paskov_crossclass_2022].
-Additionally, studies on network segregation on preferences for market distribution of social services [@beck_explorando_2019] and attitudes towards inequality in general [@otero_power_2023].
+In recent years, we have seen an increase in this _network turn_ of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
+In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interact with those of upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
+Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images about the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
+
+In addition, studies that have more directly addressed the relationship between networks and social class have been consistent with previous findings.
+In this regard, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively impact redistributive demands, while ties to the working class increase them arguing that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
+698].
+Similarly, additional socialization sources are cross-class ties through the family members.
+Family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
+A study in the United States has shown that those tied to the upper class through parental relations are less supportive of redistribution and progressive taxation than those with working-class family backgrounds [@lee_consider_2023].
+Besides, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences en tanto que los households share risk according to the class position of its members, where class homogeneity in ties polarizes preferences between lower and upper classes.
+In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
+
+In sum, the attitudes of individuals toward redistribution are influenced by their class-embedded social relations.
+Thus, the degree of class segregation in these networks plays a crucial role in shaping people's beliefs about income distribution and redistributive policies.
+Furthermore, the degree of contact between different classes and class homophily reinforces the assimilation of opinions according to surrounding friends and acquaintances.
+Therefore, we expect that being segregated in similar class environments polarizes own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences.
 

### 2024-02-21 procesamiento/02-prod_prep-macro.Rmd
update

@@
 countries$countryname <- as_character(countries$country)
+```
+
+Revisar:
+
+https://wid.world/codes-dictionary#post-tax-income
+
+```
+ssc install wid
+
+help wid
+
+wid, indicators(gcainc) areas(_all) perc(_all) ages(992) pop(j) clear
 ```
@@
 otero$gdp <- gsub('\\,', '',otero$gdp) 
-otero<- otero %>% select(ccode,gv_spen,individualism,gini,gdp)
+otero<- otero %>% select(ccode,gv_spen,individualism)
 ```
@@
   select(country3,ends_with("_c")) %>% group_by(country3) %>% summarise_all(.funs = mean) %>% View()
+table(df2$country2)
 ```

### 2024-02-21 procesamiento/prod_analysis-test-operationalization.R

@@ -31,6 +31,7 @@ dfreg <- df1 %>% dplyr::select(
   homclass3_III,
   homclass3_III_V,
   know_total,
+  socialtrust,
   Q03pcm,
   edyears,
   female,
@@ -40,8 +41,9 @@ dfreg <- df1 %>% dplyr::select(
   WEIGHT,
   region,
   "gini_disp",
+  # "gini_disp"=giniindex,
   "gini_mkt",
-  gini,
+  giniindex,
   gv_spen,
   rel_red,
   d10d1,
@@ -80,6 +82,8 @@ dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
 dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
 dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
 dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+
 
 dfreg$homclass_gc  <-
   group_center(dfreg$homclass, grp = dfreg$country2)
@@ -135,96 +139,98 @@ names(dfreg)
 
 # Model -  EGP3 - isko v1 - V to Intermediate -----------------------------
 isko1_VI_1<- lmer(egal~1 + homclass +(1|country2),data=dfreg,weights = WEIGHT)
-isko1_VI_2<- update(isko1_VI_1, . ~ . +know_total)
+isko1_VI_2<- update(isko1_VI_1, . ~ . +know_total+socialtrust)
 isko1_VI_3 <- update(isko1_VI_2, . ~ . + class3+female+agenum+age2)
 isko1_VI_4 <- update(isko1_VI_3, . ~ . + class3+edyears+ Q03pcm+union+workst)
 isko1_VI_5 <- update(isko1_VI_4, . ~ . +class3*homclass)
 isko1_VI <- list(isko1_VI_1,isko1_VI_2,isko1_VI_3,isko1_VI_4,isko1_VI_5)
-screenreg(isko1_VI)
+screenreg(isko1_VI,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+")
 
 # Model -  EGP3 - isko v1 - V to Working -----------------------------------
 isko1_VW_1<- lmer(egal~1 + homclass_V +(1|country2),data=dfreg,weights = WEIGHT)
[…]

### 2024-02-23 procesamiento/02-prod_prep-macro.Rmd
update de ginis

@@
 
-```
-ssc install wid
+```{r}
+wid_gini <- haven::read_dta(here::here("input/data/original/wid_gini.dta"))
+wid_ratios <- haven::read_dta(here::here("input/data/original/wid_ratios.dta"))
+wid_shares <- haven::read_dta(here::here("input/data/original/wid_shares.dta"))
 
-help wid
+# wid_gini_2018 <- wid_gini %>% filter(year==2018)
+# wid_gini_2018$year[wid_gini_2018$year==2018] <- 2016
+# wid_gini_2018$country_yr <- stringi::stri_replace_all(str = wid_gini_2018$country_yr,replacement = "2016",regex = "2018")
 
-wid, indicators(gcainc) areas(_all) perc(_all) ages(992) pop(j) clear
+wid_df <-wid_ratios  %>% 
+  dplyr::left_join(wid_shares,by="country_yr") %>% 
+  dplyr::left_join(wid_gini,by="country_yr")
+
+names(wid_df)
+# summary(wid_df)
+wid_df <- 
+wid_df %>% 
+  select(country=country.x,year=year.x,country_yr,starts_with("wid_"))
+
+wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
+wid_df <- wid_df %>% filter(year==2018)%>% select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_gini_disp) 
 ```
@@
   filter(year==2017)
-
 ```
@@
 **Solt SWDIID**
+
 ```{r Solt}
@@
   left_join(otero) %>%
-  left_join(ocde) 
+  left_join(ocde) %>% 
+  left_join(wid_df)
+
 df1$ccode <- as.numeric(df1$country)
@@
   select(ccode,country2,country3,everything())
+```
+
+```{r}
+df2 %>% 
+  select(country3,wid_rd10d01,d10d1) %>%
+  group_by(country3) %>% 
+  summarise(wid_rd10d01=mean(wid_rd10d01), d10d1=mean(d10d1)) %>% View
 ```

### 2024-02-23 procesamiento/prod_analysis-alternatives.R

@@ -22,7 +22,7 @@ dfreg <- df1 %>% dplyr::select(
   # homclass=homclass2,
   # homclass=homclass3,
   # know_total=week_cont,
-  # class6,
+  class6,
   know_total,
   Q03pcm,
   edyears,
@@ -32,13 +32,14 @@ dfreg <- df1 %>% dplyr::select(
   workst,
   WEIGHT,
   region,
-  "gini_disp"=gini,
+  "gini_disp"=wid_gini_disp,
   "gini_mkt",
   gv_spen,
   rel_red,
-  d10d1,
-  s80s20,
-  top10,
+  d10d1=wid_rd10d01,
+  wid_rp90p50,
+  # s80s20=wid_rp80p20,
+  top10=wid_sharetop10,
   palmaratio,
   rgdpna,
   gdppercapita,
@@ -156,7 +157,7 @@ int_homo <- update(rob4, . ~ . +class3*homclass)
 models <- list(homclass,homclass_know_total,full1,rob1,rob3,rob4,int_homo)
 knitreg(models)
 
-# Models for homogeneity by socoial class and inequality 
+# Models for homogeneity by social class and inequality 
 fit_homclass <-
   lmer(homclass~1 +class3+female_gc+agenum_gc+age2_gc +
          edyears_gc + Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+union+workst_gc +
@@ -169,12 +170,29 @@ fit_homclass_palma <- update(fit_homclass, . ~ . +class3*palmaratio+loggdppercap
 fit_homclass_s80s20<- update(fit_homclass, . ~ .+class3*s80s20+loggdppercapita+rel_red)
 fit_homclass_top10 <- update(fit_homclass, . ~ . +class3*top10+loggdppercapita+rel_red)
 
-knitreg(list(fit_homclass,fit_homclass_giniM,
-                ,fit_homclass_d10d1,fit_homclass_palma,
-             fit_homclass_s80s20,fit_homclass_top10))
+homclass3_ineq <- list(fit_homclass,fit_homclass_giniD,fit_homclass_d10d1,fit_homclass_palma,
+     fit_homclass_s80s20,fit_homclass_top10)
 
+knitreg(homclass3_ineq)
 
-plot_predictions(model = fit_homclass_giniD,condition = "class")
+fit_homclass <-
+  lmer(homclass~1 +class6+female_gc+agenum_gc+age2_gc +
[…]

### 2024-02-23 procesamiento/prod_analysis-test-operationalization.R

@@ -40,16 +40,14 @@ dfreg <- df1 %>% dplyr::select(
   workst,
   WEIGHT,
   region,
-  "gini_disp",
-  # "gini_disp"=giniindex,
+  "gini_disp"=wid_gini_disp,
   "gini_mkt",
-  giniindex,
   gv_spen,
   rel_red,
-  d10d1,
-  s80s20,
-  top10,
-  palmaratio,
+  d10d1=wid_rd10d01,
+  s80s20=wid_rp80p20,
+  top10=wid_sharetop10,
+  palmaratio=wid_rpalma,
   rgdpna,
   gdppercapita,
   oecd,
@@ -60,10 +58,10 @@ dfreg <- df1 %>% dplyr::select(
          # know_total=log(know_total),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN")  
   # filter(country2 != "ZAF") %>%
-  # filter(country2 != "HUN") %>% 
-  # filter(oecd == "OECD") 
+  # filter(country2 != "HUN") 
 
 dfreg <- 
   dfreg %>% 
@@ -331,110 +329,4 @@ screenreg(list(homo_giniD,homo2_giniD,homo2_V_giniD,homo3_giniD,homo3_V_giniD,ho
           single.row = T)
 
 
-## Gini Disposable - WIID---------------------------------------------------------
-homo_giniDW <- 
-  lmer(egal~ homclass_gc+know_total_gc+socialtrust_gc+class3+female_gc+agenum_gc+age2_gc+edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+union_gc+workst_gc+giniindex +loggdppercapita + rel_red + homclass_gc*class3*giniindex +(homclass_gc+class3|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_giniDW <- 
-  lmer(egal~ 
-         homclass_V_gc+
-         know_total_gc+socialtrust_gc+
-         class3_V+
-         female_gc+agenum_gc+age2_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         giniindex +loggdppercapita + rel_red + 
-         homclass_V_gc*
-         class3_V*
-         giniindex +
-         (homclass_V_gc+class3_V|country2),data=dfreg,weights = WEIGHT)
-
[…]

### 2024-02-23 procesamiento/02-prod_prep-macro.Rmd
update ratios

@@
 wid_df %>% 
-  select(country=country.x,year=year.x,country_yr,starts_with("wid_"))
+  dplyr::select(country=country.x,year=year.x,country_yr,starts_with("wid_"))
 
 wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
-wid_df <- wid_df %>% filter(year==2018)%>% select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_gini_disp) 
+wid_df <- wid_df %>% filter(year==2018)%>% dplyr::select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_sd10d01,wid_gini_disp)
+
+cor(wid_df)
 ```

### 2024-02-26 procesamiento/02-prod_prep-macro.Rmd
ajustes medidas desigualdad y homogeneidad

@@
 wid_df$ccode <- countrycode::countrycode(sourcevar = wid_df$country,origin = "iso2c",destination = "iso3n")
-wid_df <- wid_df %>% filter(year==2018)%>% dplyr::select(ccode,wid_sharetop10,wid_rp90p50,wid_rd10d01,wid_sd10d01,wid_gini_disp)
 
-cor(wid_df)
+summary(wid_df)
+wid_df_fill<- 
+wid_df %>%
+  group_by(country) %>% 
+  fill(wid_p90p10, .direction = "up") %>%
+  fill(wid_sp90p10, .direction = "up") %>%
+  fill(wid_gini_disp, .direction = "up")
+summary(wid_df_fill)
+
+wid_df1 <- wid_df_fill %>% filter(year==2017) %>% select(ccode,starts_with("wid_"))
+wid_df1$country <- NULL
+sjPlot::tab_corr(wid_df1)
 ```
@@
   left_join(ocde) %>% 
-  left_join(wid_df)
+  left_join(wid_df1)
 
@@
   select(ccode,country2,country3,everything())
-```
-
-```{r}
-df2 %>% 
-  select(country3,wid_rd10d01,d10d1) %>%
-  group_by(country3) %>% 
-  summarise(wid_rd10d01=mean(wid_rd10d01), d10d1=mean(d10d1)) %>% View
 ```

### 2024-02-26 procesamiento/prod_analysis-alternatives.R

@@ -36,15 +36,15 @@ dfreg <- df1 %>% dplyr::select(
   "gini_mkt",
   gv_spen,
   rel_red,
-  d10d1=wid_rd10d01,
-  wid_rp90p50,
-  # s80s20=wid_rp80p20,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  s80s20,
   top10=wid_sharetop10,
   palmaratio,
   rgdpna,
   gdppercapita,
   oecd,
-  country2, country
+  country2
 ) %>%
   mutate(logrgdpna = log(rgdpna),
          loggdppercapita=log(gdppercapita),
@@ -54,7 +54,7 @@ dfreg <- df1 %>% dplyr::select(
   filter(country2 != "SVN") %>% 
   # filter(country2 != "ZAF") %>%
   # filter(country2 != "HUN") %>% 
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   na.omit()
 
 dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric")) %>% 
@@ -73,31 +73,13 @@ dfreg %>%
                          "rel_red","loggdppercapita"),
                .funs = mean) %>% 
   dplyr::select(-country2) 
-  
-# sjPlot::tab_corr(dfreg_country,triangle = "lower")
-# GGally::ggpairs(dfreg_country, lower=list(continuous="smooth"), diag = list(continuous = NULL))
-
-# sjPlot::plot_grpfrq(df1$homclass_wght,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
-# sjPlot::plot_grpfrq(df1$homclass,var.grp = df1$class11d,type = "boxplot",ylim = c(0,0.8))
-# sjPlot::plot_model(model = lmer(homclass~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
-# sjPlot::plot_model(model = lmer(homclass_wght~factor(class11d)+edyears+Q03pcm+female+(1|country2),data = dfreg),type = "pred",terms = "class11d")
-
-# cowplot::plot_grid(
-#   sjPlot::plot_model(model = lm(homclass~class6+edyears+Q03pcm+female+know_total,data = subset(x = dfreg,dfreg$country2=="SWE")),type = "pred",terms = "class6",title = "Sweden"),
[…]

### 2024-02-26 procesamiento/prod_analysis-test-operationalization.R

@@ -44,10 +44,9 @@ dfreg <- df1 %>% dplyr::select(
   "gini_mkt",
   gv_spen,
   rel_red,
-  d10d1=wid_rd10d01,
-  s80s20=wid_rp80p20,
+  d10d1=wid_p90p10,
+  wid_p90p50,
   top10=wid_sharetop10,
-  palmaratio=wid_rpalma,
   rgdpna,
   gdppercapita,
   oecd,
@@ -58,7 +57,7 @@ dfreg <- df1 %>% dplyr::select(
          # know_total=log(know_total),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN")  
   # filter(country2 != "ZAF") %>%
   # filter(country2 != "HUN") 
@@ -100,9 +99,7 @@ dfreg$homclass3_III_gc <-
 dfreg$homclass3_III_V_gc <-
   group_center(dfreg$homclass3_III_V, grp = dfreg$country2)
 
-
 dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-
 
 # EGP: dominance
 dfreg$class3_ser_gc = group_center(dfreg$class3_1, grp = dfreg$country2)
@@ -216,14 +213,16 @@ screenreg(digclas1_III_V_W,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+")
 # Contrast between operationalizations ------------------------------------
 screenreg(list(isko1_VI_5,isko1_VW_5,isko2_VI_5,isko2_VW_5,digclas1_VI_5,digclas1_VW_5,digclas1_IIIW_5,digclas1_III_V_W_5),
           stars = c(0.001, 0.01, 0.05, 0.1),
-          # "output/tables/int_homo-class3_diff-operat-full.txt", 
+          # "output/tables/micro_homo-class3_diff-operat-full.txt",
+          "output/tables/micro_homo-class3_diff-operat-oecd.txt",
           single.row = T)
 
 
+# Macro level models ------------------------------------------------------
 dfreg <- dfreg %>% mutate_all(~ifelse(is.nan(.), NA, .))
 ## Gini Disposable---------------------------------------------------------
 homo_giniD <- 
[…]

### 2024-02-26 procesamiento/01-prod_prep-micro.Rmd
update

--- 2024-02-06 procesamiento/01-prod_prep-micro.Rmd
@@
 # #hist.default(df1$egal2)
+```
+
+# Trust
+
+```{r}
+# sjmisc::frq(df1$v35)
+df1$socialtrust <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
+df1$socialtrust <- set_na(df1$socialtrust,na = c(0,8,9))
+df1$socialtrust <- sjmisc::rec(x = df1$socialtrust,rec = "rev")
+# sjmisc::frq(df1$socialtrust)
+# hist.default(df1$socialtrust)
 ```
@@
 df1$class10spof <- as_labelled(df1$class10spof)
-sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse"
-
-frq(df1$class10spof)
+sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse";frq(df1$class10spof)
 #if NA in class of respondent, replace with spouse
@@
 
-sjlabelled::set_label(df1$class3) <- "Social Class"
-frq(df1$class3)
-
-# Class Scheme 5 classes
-df1$class5 <- car::recode(
-  df1$class11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$class5) <- "Social Class"
-#frq(df1$class5)
+sjlabelled::set_label(df1$class3) <- "Social Class Dominance (isko - v1 - V to Intermediate)";frq(df1$class3)
+
+df1$class3_V <- car::recode(df1$class11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3_V) <- "Social Class Dominance (isko - v1 - V to Working Class)";frq(df1$class3_V)
 
@@
 # Class only R's --------------------------------------------------------------
-df1$class10
-
 # Class Scheme 3 classes
-df1$class3res <- car::recode(as.numeric(df1$class10),as.factor = T,
+df1$class3res <- car::recode(as.numeric(df1$class10f),as.factor = T,
                             levels =c('Service Class (I+II)',
@@
 
-sjlabelled::set_label(df1$class3res) <- "Social Class (R's)"
-# frq(df1$class3res)
-
-# Class Scheme 5 classes
-df1$class5res <- car::recode(
-  as.numeric(df1$class10),
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$class5res) <- "Social Class (R's)"
-# frq(df1$class5res)
+sjlabelled::set_label(df1$class3res) <- "Social Class 3 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class3res)
+
+df1$class3res_V <- car::recode(as.numeric(df1$class10f),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3res_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3res_V)
 
@@
 df1$class6res <- car::recode(
-  as.numeric(df1$class10),
+  as.numeric(df1$class10f),
   as.factor = T,
@@
 
-sjlabelled::set_label(df1$class6res) <- "Social Class (R's)"
-frq(df1$class6res)
+sjlabelled::set_label(df1$class6res) <- "Social Class 6 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class6res)
 # Class only Spouse --------------------------------------------------------------
-df1$class10spo
 
 # Class Scheme 3 classes
-df1$class3spo <- car::recode(as.numeric(df1$class10spo),as.factor = T,
+df1$class3spo <- car::recode(as.numeric(df1$class10spof),as.factor = T,
                             levels =c('Service Class (I+II)',
@@
                              3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3spo) <- "Social Class (Spouse)"
-frq(df1$class3spo)
-
-# Class Scheme 5 classes
-df1$class5spo <- car::recode(
-  as.numeric(df1$class10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$class5spo) <- "Social Class (Spouse)"
-# frq(df1$class5res)
+                             8:10='Working Class (VI+VII)'")
+
+sjlabelled::set_label(df1$class3spo) <- "Social Class 3 (Spouse) - (isko - v1 -  V to Intermediate)";frq(df1$class3spo)
+
+df1$class3spo_V <- car::recode(as.numeric(df1$class10spof),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:10='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$class3spo_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3spo_V)
 
@@
 )
-sjlabelled::set_label(df1$class6spo) <- "Social Class (Spouse)"
+sjlabelled::set_label(df1$class6spo) <- "Social Class 6 (Spouse) - (isko - v1)";frq(df1$class6spo) 
 ```
@@
                        labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
 df1$digclass10f <- as_labelled(df1$digclass10f)
@@
 frq(df1$digclass10f)
-
 df1$digclass10spof <- as_factor(df1$digclass10spo)
@@
                                      "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$digclass11d) <- "Social Class"
+sjlabelled::set_label(df1$digclass11d) <- "Social Class 11 (isko - v2)"
 frq(df1$digclass11d)
@@
 
-sjlabelled::set_label(df1$digclass3) <- "Social Class"
-frq(df1$digclass3)
-
-# Class Scheme 5 classes
-df1$digclass5 <- car::recode(
-  df1$digclass11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$digclass5) <- "Social Class"
-frq(df1$digclass5)
-# Class Scheme 6 classes
-df1$digclass6 <- car::recode(
-  df1$digclass11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
+sjlabelled::set_label(df1$digclass3) <- "Social Class 3 (isko - v2 - V to Intermediate) ";frq(df1$digclass3)
+
+df1$digclass3_V <- car::recode(df1$digclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3_V)
 
 # Class only R's --------------------------------------------------------------
-df1$digclass10
-
 # Class Scheme 3 classes
-df1$digclass3res <- car::recode(as.numeric(df1$digclass10),as.factor = T,
+df1$digclass3res <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
                             levels =c('Service Class (I+II)',
@@
 
-sjlabelled::set_label(df1$digclass3res) <- "Social Class (R's)"
-# frq(df1$class3res)
-
-# Class Scheme 5 classes
-df1$digclass5res <- car::recode(
-  as.numeric(df1$digclass10),
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$digclass5res) <- "Social Class (R's)"
-# frq(df1$class5res)
+sjlabelled::set_label(df1$digclass3res) <- "Social Class 3 (R's) - (V to Intermediate - isko - v2)";frq(df1$digclass3res)
+
+df1$digclass3res_V <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3res_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3res_V)
 
@@
 
-sjlabelled::set_label(df1$digclass6res) <- "Social Class (R's)"
-frq(df1$digclass6res)
+sjlabelled::set_label(df1$digclass6res) <- "Social Class 6 (R's) - (isko - v2)"
+
 # Class only Spouse --------------------------------------------------------------
-df1$digclass10spo
-
 # Class Scheme 3 classes
@@
 
-sjlabelled::set_label(df1$digclass3spo) <- "Social Class (Spouse)"
-frq(df1$digclass3spo)
-
-# Class Scheme 5 classes
-df1$digclass5spo <- car::recode(
-  as.numeric(df1$digclass10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I+II)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1:2='Service class (I+II)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$digclass5spo) <- "Social Class (Spouse)"
-# frq(df1$class5res)
+sjlabelled::set_label(df1$digclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate - isko - v2)";frq(df1$digclass3spo)
+
+df1$digclass3spo_V <- car::recode(as.numeric(df1$digclass10spof),as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:6='Intermediate class (III+IV)';
+                             7:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$digclass3spo_V) <- "Social Class 3 (Spouse) (V to Working Class - isko - v2)";frq(df1$digclass3spo_V)
 
@@
 )
-sjlabelled::set_label(df1$digclass6spo) <- "Social Class (Spouse)"
+sjlabelled::set_label(df1$digclass6spo) <- "Social Class  6 (Spouse) - (isko - v2)"
 ```
@@
 # devtools::install_git("https://code.europa.eu/digclass/digclass.git")
+
 library("DIGCLASS")
@@
 df1$dclass11 <- ifelse(is.na(df1$egp11),df1$egp11spo,df1$egp11)
+
+#0.1 label respondent egp11 classes
+df1$egp11 <- 
+  sjlabelled::set_labels(df1$egp11,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
+                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb"))
+
+#0.2 label spouse egp11 classes
+df1$egp11spo <- 
+  sjlabelled::set_labels(df1$egp11spo,
+                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
+                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
+                                     "IVc", "V", "VI", "VIIa", "VIIb"))
 
@@
                                      "IVc", "V", "VI", "VIIa", "VIIb"))
-frq(df1$dclass11d)
-sjlabelled::set_label(df1$dclass11d) <- "Social Class"
-
-# Class Scheme 3 classes
+
+sjlabelled::set_label(df1$dclass11d) <- "Social Class 11 Dominance (EGP11 -  DIGICLASS)";frq(df1$dclass11d)
+
+# Class scheme using dominance-------------------------------------------------
+# # Class Scheme 3 classes -  V to intermediate class
 df1$dclass3 <- car::recode(df1$dclass11d,as.factor = T,
@@
                             "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3) <- "Social Class"
-frq(df1$dclass3)
-frq(df1$class3)
-frq(df1$digclass3)
-```
-
-```{r oesch-class}
-df1 <- df1 %>% 
-  mutate(oesch16 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 16,to_factor = T,label=T),
-         oesch8 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 8,to_factor = T,label=T))
-
-df1 <- df1 %>% 
-  mutate(oesch16spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
-         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))
-
-# Traditional Upper-middle class
-#  [1] "'Large employers'"
-#  [2] "'Self-employed professionals'"
-# 
-# Salaried middle class
-#  [9] "'Higher-grade managers and administrators'"
-# [10] "'Lower-grade managers and administrators'"
-
-#  [5] "'Technical experts'"
-#  [6] "'Technicians'"
-# 
-# [13] "'Socio-cultural professionals'"
-# [14] "'Socio-cultural semi-professionals'"
-
-# # Lower-middle class
-#  [3] "'Small business owners with employees'"
-#  [4] "'Small business owners without employees'"
-# [11] "'Skilled clerks'"
-# 
-# # Working class
-#  [7] "'Skilled manual'"
-#  [8] "'Low-skilled manual'"
-# 
-# [12] "'Unskilled clerks'"
-# [15] "'Skilled service'"
-# [16] "'Low-skilled service'"
-
-# reorder Oesch's scheme in a (semi)hierarchical order
-oesch_hierar <- 
-c("'Large employers'","'Self-employed professionals'",
-  "'Higher-grade managers and administrators'",
-  "'Lower-grade managers and administrators'",
-  "'Technical experts'","'Technicians'",
-  "'Socio-cultural professionals'","'Socio-cultural semi-professionals'",
-  "'Small business owners with employees'","'Small business owners without employees'","'Skilled clerks'",
-  "'Skilled manual'","'Skilled service'",
-  "'Low-skilled service'","'Unskilled clerks'","'Low-skilled manual'")
-
-# Respondent social class ------------------------------------------------------
-df1$oesch16 <- factor(df1$oesch16,
-                      levels = oesch_hierar)
-frq(df1$oesch16)
-
-# Partner social class ---------------------------------------------------------
-df1$oesch16spo <- factor(df1$oesch16spo,
-                      levels = oesch_hierar)
-frq(df1$oesch16spo)
-
-#   Given that the Oesch's Scheme consider the vertical (skills) and horizontal (work-logic) as the main distinction between classes
-# I will colapse in 4 classes that allow to distinguish between hierarchical differences
-
-# 1. Traditional Upper-middle class
-# 2. Salaried middle-class
-# 3. Lower middle class
-# 4. Working Class
-
-df1$oesch4 <- NA
-df1$oesch4[df1$oesch16 %in%c("'Large employers'","'Self-employed professionals'")] <- 4
-df1$oesch4[df1$oesch16 %in%c("'Higher-grade managers and administrators'",
-                             "'Lower-grade managers and administrators'",
-                             "'Technical experts'","'Technicians'",
-                             "'Socio-cultural professionals'",
-                             "'Socio-cultural semi-professionals'")] <- 3
-df1$oesch4[df1$oesch16 %in%c( "'Small business owners with employees'",
-                              "'Small business owners without employees'",
-                              "'Skilled clerks'")] <- 2
-
-df1$oesch4[df1$oesch16 %in%c("'Low-skilled service'",
-                             "'Unskilled clerks'",
-                             "'Low-skilled manual'")] <- 1
-
-frq(df1$oesch4) # higher number is the hierarchical order of the four main classes
-
-df1$oesch4spo <- NA
-df1$oesch4spo[df1$oesch16spo %in%c("'Large employers'","'Self-employed professionals'")] <- 4
-df1$oesch4spo[df1$oesch16spo %in%c("'Higher-grade managers and administrators'",
-                             "'Lower-grade managers and administrators'",
-                             "'Technical experts'","'Technicians'",
-                             "'Socio-cultural professionals'",
-                             "'Socio-cultural semi-professionals'")] <- 3
-df1$oesch4spo[df1$oesch16spo %in%c( "'Small business owners with employees'",
-                              "'Small business owners without employees'",
-                              "'Skilled clerks'")] <- 2
-
-df1$oesch4spo[df1$oesch16spo %in%c("'Low-skilled service'",
-                             "'Unskilled clerks'",
-                             "'Low-skilled manual'")] <- 1
-frq(df1$oesch4spo)
-#if NA in class of respondent, replace with spouse
-df1$oesch4_dom  <- ifelse(is.na(df1$oesch4),df1$oesch4spo,df1$oesch4)
-frq(df1$oesch4_dom)
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$oesch4_dom <- pmax(df1$oesch4, #social class respondent
-                       df1$oesch4spo,#social class spouse
-                       na.rm = T) # if NA, do nothing
-frq(df1$oesch4_dom)
-df1$oesch4_dom <- as_numeric(df1$oesch4_dom)
-frq(df1$oesch4_dom)
-
-# 3-class scheme Oesch
-df1$oesch3 <- car::recode(df1$oesch4,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
-                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
-frq(df1$oesch3)
-df1$oesch3spo <- car::recode(df1$oesch4spo,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
-                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
-frq(df1$oesch3spo)
-
-df1$oesch3_dom <- car::recode(df1$oesch4_dom,"3:4='Upper-middle Class';2='Lower-middle Class';1='Working Class'",
-                          as.factor = T,levels = c("Upper-middle Class","Lower-middle Class","Working Class"))
-frq(df1$oesch3_dom)
+                             3:8='Intermediate class (III+IV+V)';
+                             9:11='Working Class (VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3) <- "Social Class 3 Dominance (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3)
+
+# Class Scheme 3 classes -  V to working class
+df1$dclass3_V <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class (I+II)',
+                                      'Intermediate class (III+IV)',
+                                      'Working Class (V+VI+VII)'), 
+                            "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3_V) <- "Social Class 3 Dominance (V to Working Class - DIGCLASS)";frq(df1$dclass3_V)
+
+# Class Scheme 3 classes -  IIIb to working class
+df1$dclass3_III <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class',
+                                      'Intermediate class',
+                                      'Working Class'), 
+                            "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3_III) <- "Social Class 3 Dominance (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3_III)
+
+# Class Scheme 3 classes -  IIIb and V to working class
+df1$dclass3_III_V <- car::recode(df1$dclass11d,as.factor = T,
+                            levels =c('Service Class',
+                                      'Intermediate class',
+                                      'Working Class'), 
+                            "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3_III_V) <- "Social Class 3 Dominance (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3_III)
+
+# Class Scheme 6 classes
+df1$dclass6 <- car::recode(
+  df1$dclass11d,
+  as.factor = T,
+  levels = c(
+    'Service class (I - higher grade)',
+    'Service class (II - lower grade)',
+    'Routine non-manual (IIIa+b)',
+    'Petty-bourgeoise (IVa+b+c)',
+    'Skilled manual workers and supv. (V+VI)',
+    'Non-skilled manual workers (VIIa+b)'
+  ),
+  "1='Service class (I - higher grade)';
+   2='Service class (II - lower grade)';
+   3:4='Routine non-manual (IIIa+b)';
+   5:7='Petty-bourgeoise (IVa+b+c)';
+   8:9='Skilled manual workers and supv. (V+VI)';
+   10:11='Non-skilled manual workers (VIIa+b)'"
+)
+
+sjlabelled::set_label(df1$dclass6) <- "Social Class 6 Dominance (DIGCLASS)"
+```
+
+```{r digclass-egp-respondent}
+# Class scheme using Respondent-------------------------------------------------
+# # Class Scheme 3 classes -  V to intermediate class
+
+df1$dclass3res <- car::recode(df1$egp11,as.factor = T,
+                           levels =c('Service Class (I+II)',
+                                     'Intermediate class (III+IV+V)',
+                                     'Working Class (VI+VII)'), 
+                           "1:2='Service Class (I+II)';
+                             3:8='Intermediate class (III+IV+V)';
+                             9:11='Working Class (VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3res) <- "Social Class 3 (R's) - (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3res)
+
+# Class Scheme 3 classes -  V to working class
+df1$dclass3res_V <- car::recode(df1$egp11,as.factor = T,
+                             levels =c('Service Class (I+II)',
+                                       'Intermediate class (III+IV)',
+                                       'Working Class (V+VI+VII)'), 
+                             "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3res_V) <- "Social Class 3 (R's) - (V to Working Class - DIGCLASS)";frq(df1$dclass3res_V)
+
+# Class Scheme 3 classes -  IIIb to working class
+df1$dclass3res_III <- car::recode(df1$egp11,as.factor = T,
+                               levels =c('Service Class',
+                                         'Intermediate class',
+                                         'Working Class'), 
+                               "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3res_III) <- "Social Class 3 (R's) - (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3res_III)
+
+# Class Scheme 3 classes -  IIIb and V to working class
+df1$dclass3res_III_V <- car::recode(df1$egp11,as.factor = T,
+                                 levels =c('Service Class',
+                                           'Intermediate class',
+                                           'Working Class'), 
+                                 "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3res_III_V) <- "Social Class 3 (R's) - (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3res_III_V)
+```
+
+```{r digclass-egp-spouse}
+# Class scheme using Spouse-------------------------------------------------
+# # Class Scheme 3 classes -  V to intermediate class
+
+df1$dclass3spo <- car::recode(df1$egp11spo,as.factor = T,
+                              levels =c('Service Class (I+II)',
+                                        'Intermediate class (III+IV+V)',
+                                        'Working Class (VI+VII)'), 
+                              "1:2='Service Class (I+II)';
+                             3:8='Intermediate class (III+IV+V)';
+                             9:11='Working Class (VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3spo)
+
+# Class Scheme 3 classes -  V to working class
+df1$dclass3spo_V <- car::recode(df1$egp11spo,as.factor = T,
+                                levels =c('Service Class (I+II)',
+                                          'Intermediate class (III+IV)',
+                                          'Working Class (V+VI+VII)'), 
+                                "1:2='Service Class (I+II)';
+                             3:7='Intermediate class (III+IV)';
+                             8:11='Working Class (V+VI+VII)'")
+
+sjlabelled::set_label(df1$dclass3spo_V) <- "Social Class 3 (Spouse) - (V to Working Class - DIGCLASS)";frq(df1$dclass3spo_V)
+
+# Class Scheme 3 classes -  IIIb to working class
+df1$dclass3spo_III <- car::recode(df1$egp11spo,as.factor = T,
+                                  levels =c('Service Class',
+                                            'Intermediate class',
+                                            'Working Class'), 
+                                  "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3spo_III) <- "Social Class 3 (Spouse) - (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3spo_III)
+
+# Class Scheme 3 classes -  IIIb and V to working class
+df1$dclass3spo_III_V <- car::recode(df1$egp11spo,as.factor = T,
+                                    levels =c('Service Class',
+                                              'Intermediate class',
+                                              'Working Class'), 
+                                    "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
+
+sjlabelled::set_label(df1$dclass3spo_III_V) <- "Social Class 3 (Spouse) - (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3spo_III_V)
 ```
@@
 - using my original coding
-```{r homogeneity-v01}
+
+```{r homogeneity-v01-V-to-intermediate}
 # EI homophily index
@@
 
-# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
-df1$eindex<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-sjlabelled::set_label(df1$eindex) <- "EI homophily index"
-#frq(df1$eindex)
-#hist.default(df1$eindex)
-df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
-#hist.default(df1$eindex_gc)
-
-df1 %>% select(class3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
 df1$homclass <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass) <- "Class homogeneity"
+sjlabelled::set_label(df1$homclass) <- "Class homogeneity (isko v1 - V to Intermediate)"
 df1$homclass_gc <- group_center(x = df1$homclass,grp = df1$country)
-# View(df1[,c("homclass","homclass_gc")])
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-
-df1<- df1 %>% group_by(country) %>% mutate(sum_know_total=sum(know_total))
-
-df1$know_total_weight <- df1$know_total/df1$sum_know_total
-df1$homclass_wght <- (as.numeric(df1$ingroup/df1$know_total*df1$know_total_weight))*1000 #the 1000 is for scaling purposes
-
-summary(df1$homclass_wght)
-
-cor(df1[,c("homclass","homclass_wght","egal2")],use = "complete.obs")
-
-hist.default(df1$homclass)
-hist.default(df1$homclass_wght)
-
-# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
-An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
-Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
-
-# Group means
-df1 <- df1 %>% group_by(country) %>% mutate(eindex_gm=mean(eindex,na.rm=T),
-                                            homclass_gm=mean(homclass,na.rm=T))  
-```
-
-```{r homogeneity-strong-v01}
-# EI homophily index
-df1$ingroup_s<- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_s,df1$ingroup_s)
-#frq(df1$ingroup_s)
-
-df1$outgroup_s <- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
-#frq(df1$outgroup_s)
-
-df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
-sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
-#frq(df1$eindex_s)
-#hist.default(df1$eindex_s)
-
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
-df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
-sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
-#hist.default(df1$homclass_s)
-```
-
-```{r homogeneity-weak-v01}
-# EI homophily index
-df1$ingroup_w<- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_w,df1$ingroup_w)
-# frq(df1$ingroup_w)
-
-df1$outgroup_w <- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
-# frq(df1$outgroup_w)
-
-df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
-sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
-frq(df1$eindex_w)
-#hist.default(df1$eindex_w)
-
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
-df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
-sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
-#hist.default(df1$homclass_s)
-```
-
-```{r homogeneity-resp-v01}
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
 # EI homophily index
@@
 
-df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
-sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
-# frq(df1$eindex)
-# #hist.default(df1$eindex)
-
-df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
 df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-
-# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
-An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
-Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
+sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's) (isko v1 - V to Intermediate)"
+```
+
+```{r homogeneity-v01-V-to-working}
+df1$ingroup <- NA 
+df1 %>% select(class3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1$outgroup <- ifelse(df1$class3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+#frq(df1$outgroup)
+
+df1$homclass_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass_V) <- "Class homogeneity (isko v1 - V to Working)"
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res_V=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$class3res_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
+# frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
+# frq(df1$outgroup_res)
+
+df1$homclass_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass_V_res) <- "Class homogeneity (R's) (isko v1 - V to Working)"
 ```
@@
 
-# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
-df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
-#frq(df1$eindex)
-#hist.default(df1$eindex2)
-df1$eindex2_gc <- group_center(x = df1$eindex2,grp = df1$country)
-#hist.default(df1$eindex2_gc)
-
-df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
 df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (isko - v2)"
-df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
-# View(df1[,c("homclass","homclass_gc")])
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-
-# Group means
-df1 <- df1 %>% group_by(country) %>% mutate(eindex2_gm=mean(eindex2,na.rm=T),
-                                            homclass2_gm=mean(homclass2,na.rm=T))
-```
-
-```{r homogeneity-resp-v02}
-# EI homophily index
+sjlabelled::set_label(df1$homclass2) <- "Class homogeneity Dominance (isko - v2 - V to intermediate)"
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
 df1$ingroup_res <- NA 
@@
 
-df1$eindex2_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
-sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
-# frq(df1$eindex)
-# #hist.default(df1$eindex)
-
-df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
 df1$homclass2_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass2_res) <- "Class homogeneity (R's)"
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-```
-
-```{r homogeneity-R-digclass}
+sjlabelled::set_label(df1$homclass3_res) <- "Class homogeneity (R's) (isko - v2 - V to intermediate)";frq(df1$homclass_res)
+```
+
+```{r homogeneity-v02-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(digclass3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(digclass3,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+# frq(df1$outgroup)
+
+df1$homclass2_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass2_V) <- "Class homogeneity Dominance (isko - v2- V to Working)";frq(df1$homclass2_V)
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(digclass3res_V,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res_V=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$digclass3res_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(digclass3res_V,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$digclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$homclass2_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass2_V_res) <- "Class homogeneity (R's) (isko - v2 - V to working)";frq(df1$homclass2_V_res)
+```
+
+```{r homogeneity-R-digclass-V-intermediate}
 # EI homophily index
@@
 df1$ingroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
-#frq(df1$ingroup)
 
@@
 df1$outgroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+
+df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3) <- "Class homogeneity Dominance (DIGCLASS - V to intermediate)";frq(df1$homclass3)
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$homclass3_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass3_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_res)
+```
+
+```{r homogeneity-R-digclass-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
+#frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_V,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
 #frq(df1$outgroup)
 
-# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
-df1$eindex3<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
-sjlabelled::set_label(df1$eindex3) <- "EI homophily index"
-#frq(df1$eindex)
-#hist.default(df1$eindex)
-df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
-#hist.default(df1$eindex_gc)
-
-df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
-df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (DIGCLASS version)"
-df1$homclass3_gc <- group_center(x = df1$homclass3,grp = df1$country)
-# View(df1[,c("homclass","homclass_gc")])
-# Weighted EI index
-# https://arxiv.org/pdf/2109.00348.pdf
-
-# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are.
-An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are.
-Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types
-```
-
-(i)  the highest status job accessed (upper reachability),
-(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
-(iii) the total number of occupations accessed (network extensity),
-(iv) the total accessed prestige (resource volume),
-(v) the average status of jobs accessed (network prestige),
-(vi) the total number of higher-status positions accessed,
-(vii) the total number of medium-status positions accessed,
-(viii) the total number of lower-status positions accessed.
-
-```{r pca, eval=FALSE, include=FALSE}
-library(psych)
-library(dplyr)
-isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
-
-# Calculate the standard deviation for each column
-df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
-
-# Print the standard deviation for each column
-# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
-
-# reduce dimensions in 2: diversity and prestige
-df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
-summary(df_cs)
-dim(df_cs)
-
-# df_cs <- na.omit(df_cs)
-cor<- corr.test(df_cs)
-psych::KMO(r = cor$r)
-cortest.bartlett(cor$r,n = dim(df_cs)[1])
-plot(scree(df_cs,factors = 2))
-
-# Porcentaje de varianza explicada
-fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
-fit1$loadings
-plot(fit1,labels = c(names(df_cs)))
-cor(fit1$scores)
-
-fit2<- psych::fa(df_cs,nfactors = 2)
-plot(fit2,labels = c(names(df_cs)))
-fit2$scores
-cor(fit2$scores)
-fs<- as.data.frame(fit2$scores)
-names(fs) <- c("diversity","prestige")
-
-df1 <- bind_cols(df1,fs)
-sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
-sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
+df1$homclass3_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_V) <- "Class homogeneity Dominance (DIGCLASS version - V to Working)"
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res_V,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res_V,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$homclass3_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass3_V_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res)
+```
+
+```{r homogeneity-R-digclass-IIIb-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_III,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Service Class",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Intermediate class",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III=="Working Class",df1$n_low,df1$ingroup);frq(df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_III,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup);frq(df1$outgroup)
+
+df1$homclass3_III <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III) <- "Class homogeneity Dominance (DIGCLASS version - IIIb to Working)";frq(df1$homclass3_III)
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res_III,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III=="Service Class",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res_V,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$homclass3_III_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_res)
+```
+
+```{r homogeneity-R-digclass-IIIb-V-working}
+# EI homophily index
+df1$ingroup <- NA 
+df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Service Class",df1$n_high,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Intermediate class",df1$n_middle,df1$ingroup)
+df1$ingroup <- ifelse(df1$dclass3_III_V=="Working Class",df1$n_low,df1$ingroup)
+
+df1$outgroup <- NA 
+df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
+df1$outgroup <- ifelse(df1$dclass3_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
+
+df1$homclass3_III_V <- as.numeric(df1$ingroup/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III_V) <- "Class homogeneity Dominance (DIGCLASS version - IIIb+V to Working)";frq(df1$homclass3_III_V)
+
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",df1$n_high,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",df1$n_middle,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$homclass3_III_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
+sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_V_res)
 ```
@@
 ```
+
+# Backup code
+
+```{r homogeneity-strong-v01, eval=FALSE, include=FALSE}
+# EI homophily index
+df1$ingroup_s<- NA 
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_s,df1$ingroup_s)
+df1$ingroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_s,df1$ingroup_s)
+#frq(df1$ingroup_s)
+
+df1$outgroup_s <- NA 
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
+df1$outgroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
+#frq(df1$outgroup_s)
+
+df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
+sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
+#frq(df1$eindex_s)
+#hist.default(df1$eindex_s)
+
+df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
+df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
+sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
+#hist.default(df1$homclass_s)
+```
+
+```{r homogeneity-weak-v01, eval=FALSE, include=FALSE}
+# EI homophily index
+df1$ingroup_w<- NA 
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_w,df1$ingroup_w)
+df1$ingroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_w,df1$ingroup_w)
+# frq(df1$ingroup_w)
+
+df1$outgroup_w <- NA 
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
+df1$outgroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
+# frq(df1$outgroup_w)
+
+df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
+sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
+frq(df1$eindex_w)
+#hist.default(df1$eindex_w)
+
+df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
+df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
+sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
+#hist.default(df1$homclass_s)
+```
+
+(i)  the highest status job accessed (upper reachability),
+(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
+(iii) the total number of occupations accessed (network extensity),
+(iv) the total accessed prestige (resource volume),
+(v) the average status of jobs accessed (network prestige),
+(vi) the total number of higher-status positions accessed,
+(vii) the total number of medium-status positions accessed,
+(viii) the total number of lower-status positions accessed.
+
+```{r pca, eval=FALSE, include=FALSE}
+library(psych)
+library(dplyr)
+isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
+
+# Calculate the standard deviation for each column
+df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
+
+# Print the standard deviation for each column
+# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
+
+# reduce dimensions in 2: diversity and prestige
+df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
+summary(df_cs)
+dim(df_cs)
+
+# df_cs <- na.omit(df_cs)
+cor<- corr.test(df_cs)
+psych::KMO(r = cor$r)
+cortest.bartlett(cor$r,n = dim(df_cs)[1])
+plot(scree(df_cs,factors = 2))
+
+# Porcentaje de varianza explicada
+fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
+fit1$loadings
+plot(fit1,labels = c(names(df_cs)))
+cor(fit1$scores)
+
+fit2<- psych::fa(df_cs,nfactors = 2)
+plot(fit2,labels = c(names(df_cs)))
+fit2$scores
+cor(fit2$scores)
+fs<- as.data.frame(fit2$scores)
+names(fs) <- c("diversity","prestige")
+
+df1 <- bind_cols(df1,fs)
+sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
+sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
+```

### 2024-02-26 procesamiento/prod_analysis-alternatives.R

@@ -19,6 +19,7 @@ dfreg <- df1 %>% dplyr::select(
   # class3=digclass3,
   # class3=dclass3,
   homclass,
+  homclass_V,
   # homclass=homclass2,
   # homclass=homclass3,
   # know_total=week_cont,
@@ -54,7 +55,7 @@ dfreg <- df1 %>% dplyr::select(
   filter(country2 != "SVN") %>% 
   # filter(country2 != "ZAF") %>%
   # filter(country2 != "HUN") %>% 
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   na.omit()
 
 dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric")) %>% 
@@ -160,7 +161,7 @@ screenreg(homclass3_ineq,
           single.row = T)
 
 fit_homclass <-
-  lmer(homclass~1 +class6+female_gc+agenum_gc+age2_gc +
+  lmer(homclass_V~1 +class6+female_gc+agenum_gc+age2_gc +
          edyears_gc + Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+union+workst_gc +
          prop_work + prop_inte + 
          (class6|country2),data=dfreg,weights = WEIGHT)

### 2024-02-26 procesamiento/prod_analysis-test-oper_dominance.R

@@ -1,0 +1,684 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  class3,
+  class3_V,
+  class6,
+  homclass,
+  homclass_V,
+  digclass3,
+  digclass3_V,
+  digclass6,
+  homclass2,
+  homclass2_V,
+  dclass3,
+  dclass3_V,
+  dclass3_III,
+  dclass3_III_V,
+  dclass6,
+  homclass3,
+  homclass3_V,
+  homclass3_III,
+  homclass3_III_V,
+  class3res,
+  class3spo,
+  homclass_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         # know_total=log(know_total),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")  
+  # filter(country2 != "ZAF") %>%
+  # filter(country2 != "HUN") 
+
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
[…]

### 2024-02-26 procesamiento/prod_analysis-test-oper_resp-spouse.R

@@ -1,0 +1,660 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  starts_with("class3"),
+  starts_with("digclass3"),
+  starts_with("dclass3"),
+  starts_with("homclass"),
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         # know_total=log(know_total),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")  
+  # filter(country2 != "ZAF") %>%
+  # filter(country2 != "HUN") 
+
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(class3),
+         # to_dummy(class3spo),
+         # to_dummy(class3res),
+         to_dummy(Q03pcm)
+  )
[…]

### 2024-02-26 procesamiento/prod_analysis-test-operationalization.R

@@ -1,662 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  class3,
-  class3_V,
-  class6,
-  homclass,
-  homclass_V,
-  digclass3,
-  digclass3_V,
-  digclass6,
-  homclass2,
-  homclass2_V,
-  dclass3,
-  dclass3_V,
-  dclass3_III,
-  dclass3_III_V,
-  dclass6,
-  homclass3,
-  homclass3_V,
-  homclass3_III,
-  homclass3_III_V,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         # know_total=log(know_total),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")  
-  # filter(country2 != "ZAF") %>%
-  # filter(country2 != "HUN") 
-
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
[…]

### 2024-02-27 paper1_jiturra.Rmd
up

@@
 
-The link between social class and political attitudes constitutes one of the most relevant findings in sociology.
-Theoretically, studies in the social mobility field have defined classes as structural positions given their difference in labor market situations distinguished by employment relations, skills level, and authority within the workplace, which traditionally has been represented by occupations instead of relative income or educational credentials [@Erikson1992;@Erikson1979].
-Besides the social stratification studies, political sociologists have systematically demonstrated that classes trace distinctions in other domains of social life as well, including ideological preferences [@evans_decline_1993], cultural consumption behavior [@Chan2007] and attitudes toward redistribution and welfare [@Svallfors2006].
-Regarding the latter, during the last decades, the research on class and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and social service functions of the welfare state [@lindh_class_2020, p.
+The class divide in political attitudes on the economic domain constitutes a core finding in policy attitudes, where material interests, normative motivations, and sociability practices intersect in attitude formation.
+Theoretically, the tradition in the social mobility field has defined classes as structural positions given their differences in labor market situation distinguished by employment relations, skills level, and authority within the workplace, which traditionally has focused on occupations instead of income or educational credentials [@Erikson1992;@Erikson1979].
+In addition, political sociologists have systematically demonstrated that classes trace differences in other domains of social life as well, including ideological preferences [@evans_decline_1993], cultural consumption behavior [@Chan2007], and attitudes toward redistribution and welfare [@Svallfors2006].
+Despite the claims of a supposed displacement of the distributive struggle between classes as a result of the salience of other group identities [@clark_declining_1993;@inglehart_culture_1990], during the last decades, the research has extensively developed on how class positions shape economic attitudes in the domains of redistribution, social security, and the welfare state [@lindh_class_2020, p.
 421].
+Empirically, the claimed blurring of the class cleavage has not been strongly supported, where class divides is clear regarding attitudes in the economic domain in general, such as perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes toward market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences in particular [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
 
-Critical views have suggested that economic development and modernization have eroded the link between social class and political attitudes.
-Around the debate of the "death of class" thesis, it has been argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group identities as more relevant, reorienting the political debate towards post-material concerns [@clark_declining_1993;@inglehart_culture_1990].
-However, although modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been wholly displaced but cohabits with people's attitudes in the sociocultural domain [@lindh_class_2020].
-Empirically, the claimed blurring of the class cleavage has not been strongly supported, whereas class divides indeed shape attitudes in the economic domain in general, such as perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes toward market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences in particular [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-In the broader context, scholars have identified two competing mechanisms to elucidate the relationship between social class and attitudes towards inequality, commonly referred to as the self-interest and normative value-driven motives perspectives.
-
-Theoretically, self-interest has served as the canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981].
-Similarly, extensions of the model have paid more attention to occupation as a representation of potential unemployment risk, arguing that social classes with greater risk exposure are prone to support redistributive policies as they reduce labor market insecurity [@rehm_risks_2009].
-Differently, part of the scholarly discussion has stressed the role of cognitive processes in preference formation for understanding why, even in contexts of greater economic disparities, the lower classes oppose redistributive policies, arguing that misinformation plays a crucial role in linking material conditions with the redistributive policies [@bartels_homer_2005;@druckman_preference_2000].
-Similarly, it has been argued that contexts of greater segregation affect the inferences about social and economic inequality [@mijs_inequality_2018] that ultimately contribute to the decoupling of material interests from economic preferences [@hvidberg_social_2020;@garcia-castro_changing_2022].
-
-As material interests might prevail in scarcity, normative or value-driven motivations emerge as an alternative explanation in preference formation when pure self-interest weakens.
-Thus, values such as self-transcendence or humanitarianism share a common spirit regarding their desire for equality and concern for human dignity, providing the common ground for altruism that ultimately motivates political preferences [@Kulin2013;@feldman_humanitarian_2001].
-Despite the protagonism of values, these are indeed conditioned to risk exposure and resource availability, becoming salient under conditions of greater security against market risks and material prosperity and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019].
-Besides, it has been argued that occupations play a role in political attitude formation as they represent a set of specific skills and work logic that convey particular normative views [@oesch_redrawing_2006].
-Thus, workspaces are conceived as socializing agents, considering that economically active people spend a substantial part of their time at work, including the social relations involved in providing goods and services.
-Hence, empirical evidence has suggested that technical and managerial professionals hold more conservative political views than occupations in interpersonal services [@oesch_electoral_2018;@lindh_class_2020].
-Despite this, it is challenging to disentangle if the class differences are indeed explained through work experiences because it is feasible to argue that political preferences are the result of early-life internalization of social norms, which might be crystalized in career self-selection paths, which also might be influenced by the organizational hiring requirements for specific jobs [@kitschelt_occupations_2014].
+In this regard, class-based explanations of redistributive attitudes have been mainly focused on the individual situation.
+Hence, one main claim is that economic preferences can be explained through the labor market situation, which comprises access to economic resources and exposure to unemployment risk [@meltzer_rational_1981;@rehm_risks_2009].
+However, as material interests might prevail in scarcity, normative or value-driven motivations can also explain egalitarian economic preferences [@Kulin2013;@feldman_humanitarian_2001].
+Besides, values become salient under greater security conditions but weaken under greater precariousness [@Maldonadoetal2019].
+Alternatively, part of the literature suggests that the class divide can also be explained on top of the social interactions experienced in work relations [@oesch_redrawing_2006].
+Given that workers spend a substantial part of their time at workplaces, social relations in the workspace might drive greater contact with diverse people in the case of interpersonal services, or vertical monitoring in managerial occupations can also imprint normative views that ultimately shape political opinions [@oesch_electoral_2018].
+However, it is challenging to disentangle if the class differences are undoubtedly explained through work experiences because it is feasible to argue that political preferences are the result of early-life internalization of social norms, which might be crystalized in career self-selection paths, which also might be influenced by the organizational hiring requirements for specific jobs [@kitschelt_occupations_2014].
 
@@
 As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
-In principle, social stratification scholars have traditionally paid attention to _differentiation_ as the observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
-Empirically, homophily is one of the most significant findings in network research, whereas the likelihood of tie formation between individuals of similar characteristics is strong [@mcpherson_birds_2001; @lazarsfeld_friendship_1954] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022].
+In principle, social stratification scholars have traditionally considered _differentiation_ as the observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
+Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001; p.416] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022,@lazarsfeld_friendship_1954].
 In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
-Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
-From this scope, we argue that class relations not only represent resources-based distinctions, but patterns of sociability and exchange observed in the differentiation of social ties.
+Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
+From this scope, we argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
 
 How classes are formed also provides insights regarding their social relations and sociability practices.
-In sociology, classes are understood as the everyday basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978].
+In sociology, classes are understood as the basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978].
 According to habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
-Thus, classes seek to improve their position through the intergenerational transmission of resources, whereas similarities in friendship and family choices play a crucial role in the reproduction privilege.
+From this approach, classes seek to improve their position through the intergenerational transmission of resources, where similarities in friendship and family choices play a crucial role in the reproduction privilege.
 Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding the lower classes [@bourdieu_reproduccion_1981].
 Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
-Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, whereas social resources embedded in social networks follow a pattern of accumulation and exclusion that ultimately leads to social segregation in both the upper and the lower bounds of the social structure.
+Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, where social resources embedded in social networks follow a pattern of accumulation and exclusion that ultimately leads to social segregation in both the upper and the lower bounds of the social structure.
 
-Previous research on social class and tie formation has suggested that class permeability, understood as the formation of cross-class social ties, is traced differently across property and authority boundaries.
-Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is very less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the authority dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
-Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that isolate them from others, while the upper class is less permeable and homogenous as a result of its tendency to self-selection as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
+Previous research on social class and tie formation has suggested that class permeability in social networks, understood as the formation of cross-class social ties, is traced differently across property and authority boundaries.
+Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is significantly less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the property dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
+Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that leads to social isolation, while the upper class is less permeable and homogenous as a result of its tendency to self-selection as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
 
-In contrast, cross-class embeddedness can be described regarding their social activities as well as through their changes across generations and time.
+In contrast, cross-class embeddedness can be described regarding social activities and changes across generations and life course.
 In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in its civic engagement behavior.
-Similarly, other studies in Europe and South America have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation, whereas it does not equalize the weight of class background compared to those intergenerationally stable in the upper class [@cepic_how_2020;@carrascosa_class_2023].
-Additionally, the few longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions while the lower class shows more stability across the life course [@volker_social_2020].
+Similarly, other studies in Europe and South America have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation [@cepic_how_2020;@carrascosa_class_2023].
+Nevertheless, it does not equalize the weight of class background compared to those intergenerationally stable in the upper class.
+Additionally, the few longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions, while the lower class shows more stability across the life course [@volker_social_2020].
 
-Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
-Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_inequality_1977].
-Besides, _homogeneity_  is described as the lack of cross-class network ties.
-It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position.
+Altogether, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
+Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977].
+Besides, _homogeneity_  is described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions.
 At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
-Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.
+Hence, both approaches provide alternatives for studying social class from a network perspective that has been increasingly discussed in the stratification literature and the scholarly discussion about social class and political attitudes.
 
@@
 758].
-Thus, we suggest that attitudes towards economic inequality may be influenced by the class situation of both the individual and network ties, resembling the core claims of intergroup contact theory [@pettigrew_metaanalytic_2006] so that social influence processes can either align or polarize attitudes according to the characteristic of groups as well as their contact opportunities given the degree of segregation.
+Thus, in a similar vein, as the intergroup contact approach has established [@pettigrew_metaanalytic_2006], we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
 
@@
 In addition, studies that have more directly addressed the relationship between networks and social class have been consistent with previous findings.
-In this regard, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively impact redistributive demands, while ties to the working class increase them arguing that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
+For instance, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively influence support for redistribution, while ties to the working class increase it regardless of the individual class position suggesting that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
 698].
@@
 A study in the United States has shown that those tied to the upper class through parental relations are less supportive of redistribution and progressive taxation than those with working-class family backgrounds [@lee_consider_2023].
-Besides, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences en tanto que los households share risk according to the class position of its members, where class homogeneity in ties polarizes preferences between lower and upper classes.
+Besides, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences while households share risk according to the class position of its members, where class homogeneity in ties polarizes preferences between lower and upper classes.
 In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
 
-In sum, the attitudes of individuals toward redistribution are influenced by their class-embedded social relations.
-Thus, the degree of class segregation in these networks plays a crucial role in shaping people's beliefs about income distribution and redistributive policies.
+In sum, we argue that redistributive preferences are influenced by their class-embedded social relations.
+Therefore, the degree of class segregation in these networks plays a crucial role in shaping support for redistribution.
 Furthermore, the degree of contact between different classes and class homophily reinforces the assimilation of opinions according to surrounding friends and acquaintances.
-Therefore, we expect that being segregated in similar class environments polarizes own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences.
+Thus, we hypothesize that segregation in similar class environments polarizes own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences.
 
@@
 
-Income inequality can deteriorate social bonding and increase segregation.
+###  Consequences of Economic Inequality on Social Networks  
+The consequences of economic inequality are diverse.
+Regarding social networks, the consequences of interpersonal trust, civic participation, and social resources have been previously reported in the literature.
+In addition, the unequal distribution of economic resources impacts coexistence through the socio-spatial segregation of the inhabitants of a territory.
 
-* status anxiety among the upper-classes [@wilkinson_spirit_2010] and lower interpersonal trust  [@kragten_income_2017]
-
-* limited opportunities for social mobility consequently reduce class permeability in social networks [@otero_differences_2023]
-
-However, it has been discussed that inequality might also increase egalitarian preferences among those in better material situations.
-
+### Consequences of Economic Inequality on redistributive preferences
 * concerns about the negative consequences (e.g. crime) of inequality on overall social welfare, particularly in high-status groups (Altruism) [@rueda_who_2019]

### 2024-02-28 paper1_jiturra.Rmd
up

@@
 In principle, social stratification scholars have traditionally considered _differentiation_ as the observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
-Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001; p.416] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022,@lazarsfeld_friendship_1954].
+Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020;@plaza_juntos_2022;@lazarsfeld_friendship_1954].
 In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].

### 2024-02-29 procesamiento/prod_analysis-alternatives.R
update

@@ -15,14 +15,7 @@ dfreg <- df1 %>% dplyr::select(
   # egal = redist,
   # egal = prefineq,
   class3,
-  # class3=class6,
-  # class3=digclass3,
-  # class3=dclass3,
   homclass,
-  homclass_V,
-  # homclass=homclass2,
-  # homclass=homclass3,
-  # know_total=week_cont,
   class6,
   know_total,
   Q03pcm,
@@ -37,15 +30,13 @@ dfreg <- df1 %>% dplyr::select(
   "gini_mkt",
   gv_spen,
   rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  s80s20,
+  d10d1=wid_rd10d01,
+  wid_rp90p50,
   top10=wid_sharetop10,
-  palmaratio,
   rgdpna,
   gdppercapita,
   oecd,
-  country2
+  country2, country
 ) %>%
   mutate(logrgdpna = log(rgdpna),
          loggdppercapita=log(gdppercapita),
@@ -53,8 +44,6 @@ dfreg <- df1 %>% dplyr::select(
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
   filter(country2 != "SVN") %>% 
-  # filter(country2 != "ZAF") %>%
-  # filter(country2 != "HUN") %>% 
   # filter(oecd == "OECD") %>%
   na.omit()
 
@@ -67,20 +56,15 @@ dfreg %>%
 
 dfreg <- as.data.frame(dfreg)
 
-dfreg_country <- 
-dfreg %>% 
-  group_by(country2) %>% 
-  summarise_at(.vars = c("homclass","egal","gini_disp","gini_mkt",
-                         "rel_red","loggdppercapita"),
-               .funs = mean) %>% 
-  dplyr::select(-country2) 
-  dfreg <- 
+dfreg <- 
   dfreg %>% 
   mutate(to_dummy(female),
          to_dummy(union),
          to_dummy(workst),
          # dummy for categorical variables-------------------------------------
          to_dummy(class3),
+         # to_dummy(class3spo),
+         # to_dummy(class3res),
          to_dummy(Q03pcm)
          )
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
@@ -140,45 +124,41 @@ int_homo <- update(rob4, . ~ . +class3*homclass)
 models <- list(homclass,homclass_know_total,full1,rob1,rob3,rob4,int_homo)
 knitreg(models)
 
[…]

### 2024-02-29 procesamiento/prod_analysis-test-oper_dominance.R

@@ -62,8 +62,6 @@ dfreg <- df1 %>% dplyr::select(
          age2 = agenum ^ 2) %>%
   # filter(oecd == "OECD") %>%
   filter(country2 != "SVN")  
-  # filter(country2 != "ZAF") %>%
-  # filter(country2 != "HUN") 
 
 dfreg <- 
   dfreg %>% 
@@ -71,9 +69,6 @@ dfreg <-
          to_dummy(union),
          to_dummy(workst),
          # dummy for categorical variables-------------------------------------
-         to_dummy(class3),
-         # to_dummy(class3spo),
-         # to_dummy(class3res),
          to_dummy(Q03pcm)
   )
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
@@ -84,56 +79,31 @@ dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
 dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
 dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
 
-
-dfreg$homclass_gc  <-
-  group_center(dfreg$homclass, grp = dfreg$country2)
-dfreg$homclass_V_gc <-
-  group_center(dfreg$homclass_V, grp = dfreg$country2)
-dfreg$homclass2_gc <-
-  group_center(dfreg$homclass2, grp = dfreg$country2)
-dfreg$homclass2_V_gc <-
-  group_center(dfreg$homclass2_V, grp = dfreg$country2)
-dfreg$homclass3_gc <-
-  group_center(dfreg$homclass3, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-
-  group_center(dfreg$homclass3_V, grp = dfreg$country2)
-dfreg$homclass3_III_gc <-
-  group_center(dfreg$homclass3_III, grp = dfreg$country2)
-dfreg$homclass3_III_V_gc <-
-  group_center(dfreg$homclass3_III_V, grp = dfreg$country2)
-
-dfreg$homclass_res_gc <-
-  group_center(dfreg$homclass_res, grp = dfreg$country2)
-
+dfreg$homclass_gc  <- group_center(dfreg$homclass, grp = dfreg$country2)
+dfreg$homclass_V_gc <-group_center(dfreg$homclass_V, grp = dfreg$country2)
[…]

### 2024-02-29 procesamiento/prod_analysis-test-oper_resp-spouse.R

@@ -35,27 +35,22 @@ dfreg <- df1 %>% dplyr::select(
   rgdpna,
   gdppercapita,
   oecd,
-  country2, country
+  country2, country, country3,
 ) %>%
   mutate(logrgdpna = log(rgdpna),
          loggdppercapita=log(gdppercapita),
-         # know_total=log(know_total),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2) %>%
   # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")  
-  # filter(country2 != "ZAF") %>%
-  # filter(country2 != "HUN") 
+  filter(country2 != "SVN")
 
+# Variable Group-Centering ------------------------------------------------
 dfreg <- 
   dfreg %>% 
   mutate(to_dummy(female),
          to_dummy(union),
          to_dummy(workst),
          # dummy for categorical variables-------------------------------------
-         to_dummy(class3),
-         # to_dummy(class3spo),
-         # to_dummy(class3res),
          to_dummy(Q03pcm)
   )
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
@@ -65,72 +60,44 @@ dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
 dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
 dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
 dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-
-
-dfreg$homclass_gc  <-
-  group_center(dfreg$homclass_res, grp = dfreg$country2)
-dfreg$homclass_V_gc <-
-  group_center(dfreg$homclass_V_res, grp = dfreg$country2)
-dfreg$homclass2_gc <-
-  group_center(dfreg$homclass2_res, grp = dfreg$country2)
-dfreg$homclass2_V_gc <-
-  group_center(dfreg$homclass2_V_res, grp = dfreg$country2)
-dfreg$homclass3_gc <-
-  group_center(dfreg$homclass3_res, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-
[…]

### 2024-02-29 procesamiento/01-prod_prep-micro.Rmd
Update 01-prod_prep-micro.Rmd

@@
 
-```{r class}
+```{r class-variables}
 ## Ocupación
@@
 
+frq(df1$dclass11)
 #0.1 label respondent egp11 classes

### 2024-03-14 paper1_jiturra.Rmd
upda

@@
 
-[~3000 words]
-
 ## Class relations and social networks
@@
 As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
-In principle, social stratification scholars have traditionally considered _differentiation_ as the observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
-Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] around demographic characteristics that trace friendship and family ties such as age and gender, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020;@plaza_juntos_2022;@lazarsfeld_friendship_1954].
-In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
+In principle, social stratification scholars have traditionally considered differentiation as observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
+Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] that trace friendship and family ties, such as age and gender, as well as segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
+In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of worldviews, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
 Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
-From this scope, we argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
+From this perspective, we argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
 
-How classes are formed also provides insights regarding their social relations and sociability practices.
-In sociology, classes are understood as the basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978].
-According to habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
-From this approach, classes seek to improve their position through the intergenerational transmission of resources, where similarities in friendship and family choices play a crucial role in the reproduction privilege.
-Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding the lower classes [@bourdieu_reproduccion_1981].
-Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
-Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, where social resources embedded in social networks follow a pattern of accumulation and exclusion that ultimately leads to social segregation in both the upper and the lower bounds of the social structure.
+How classes are formed also provides insight into social relations and sociability practices.
+In sociology, classes are understood as the basis for action given their labor market situation, which ultimately shapes their access to opportunities and resources [@weber_economy_1978].
+According to the habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
+From this approach, classes seek to improve their positions through the intergenerational transmission of resources, where similarities in friendship and family choices play a crucial role in reproducing privileged social positions.
+Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding lower classes [@bourdieu_reproduccion_1981].
+Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring the intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
+Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, where access to resources embedded in social networks follows a pattern of accumulation that ultimately leads to social segregation in both the upper and lower bounds of the social structure.
 
-Previous research on social class and tie formation has suggested that class permeability in social networks, understood as the formation of cross-class social ties, is traced differently across property and authority boundaries.
-Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is significantly less likely, in contrast to the tendency of higher tie formation between supervisors and workers, suggesting that the property dimension is much less permeable than authority-based boundaries given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
-Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that leads to social isolation, while the upper class is less permeable and homogenous as a result of its tendency to self-selection as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
+Previous research on social class and tie formation has suggested that class permeability in social networks, understood as the formation of cross-class social ties, can be traced differently across property and authority boundaries.
+Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is significantly less likely, in contrast to the tendency of higher tie formation between supervisors and manual workers.
+This suggests that the property dimension is much less permeable than authority-based boundaries, given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
+Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social isolation, whereas the upper class is less permeable and homogenous because of its tendency to self-select as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
 
-In contrast, cross-class embeddedness can be described regarding social activities and changes across generations and life course.
-In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in its civic engagement behavior.
-Similarly, other studies in Europe and South America have exhibited that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile does help to improve both dimensions in tie formation [@cepic_how_2020;@carrascosa_class_2023].
-Nevertheless, it does not equalize the weight of class background compared to those intergenerationally stable in the upper class.
-Additionally, the few longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions, while the lower class shows more stability across the life course [@volker_social_2020].
+By contrast, cross-class embeddedness can be described in terms of social activities, generational changes, and life courses.
+In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in civic engagement behavior.
+Similarly, other studies in Europe and South America have shown that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile helps to improve both dimensions in tie formation [@cepic_how_2020;@carrascosa_class_2023].
+Nevertheless, it does not equalize the weight of the class background compared with those that are intergenerationally stable in the upper class.
+Additionally, the little longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions, while the lower class shows more stability across the life course [@volker_social_2020].
 
-Altogether, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
-Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977].
-Besides, _homogeneity_  is described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions.
-At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
-Hence, both approaches provide alternatives for studying social class from a network perspective that has been increasingly discussed in the stratification literature and the scholarly discussion about social class and political attitudes.
+Altogether, these studies account for class-based network segregation, as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
+Drawing on this approach, stratification scholars have focused on how social connections are distributed across class structure as a matter of social integration [@blau_macrosociological_1977].
+In addition, homogeneity is described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions.
+Simultaneously, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
+Hence, both approaches provide alternatives for studying social class from a network perspective, which has been increasingly discussed in the stratification literature and scholarly discussion about social class and political attitudes.
 
@@
 
-Apart from the individual approach to attitude formation, we argue that people also form their opinions in the economic domain based on their social relations.
-Despite the limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
+Apart from the individual approach to attitude formation, we argue that people also form opinions in the economic domain based on their social relations.
+Despite limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
 
-On the one hand, one approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form their opinions about redistributive policies [@condon_economic_2020].
-This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@KelleyEvans1995].
-Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
+On the one hand, one approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form opinions about redistributive policies [@condon_economic_2020].
+This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@kelley_class_1995].
+Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers’ experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
 467].
-From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping inequality perceptions [@mijs_is_2021].
-Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared to people in more isolated discussion networks [@summers_deliberating_2022].
+From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping perceptions of inequality [@mijs_is_2021].
+Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more isolated discussion networks [@summers_deliberating_2022].
 Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [e.g.
 @cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [e.g.
-@Cruces2011;@becker_significant_2021], rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
+@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
 
-  Differently, it has been suggested that the lens of a network approach provides a better picture of the class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
+In contrast, it has been suggested that the lens of a network approach provides a better picture of class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
 550].
-This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to the individual or household material well-being, cultural perspectives, and political preferences that structure the broader social experiences [@morris_attenuation_1996, p.
+This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to individual or household material well-being, cultural perspectives, and political preferences that structure broader social experiences [@morris_attenuation_1996, p.
 48].
-Furthermore, these social relations contribute to the degree to which people reflect on the collective, so that in societies where opportunities for contact between people of different social classes can be detrimental to social integration.
-It has been argued that the social distance among groups widened by extreme inequality can be described as an _empathy gulf_ that comprises barriers to imagining others’ lifestyles and goods, which can also be expressed in spatially segregated interactions and isolated lifeworlds that provide meaning to social inequality experiences, resulting in doubts about worthiness when the lower classes contrast themselves with extravagant lifestyles from the upper classes, undermining feelings of social inclusion and cohesion [@sachweh_moral_2012].
-Consequently, segregation drives the lives of others to become more distant and might have consequences on empathy and solidarity toward others, potentially leading to perceiving fellow citizens as strangers [@otero_lives_2022, p.
+Furthermore, these social relations contribute to the degree to which people reflect on the collective, such that in societies where opportunities for contact between people of different social classes can be detrimental to social integration.
+It has been argued that the social distance among groups widened by extreme inequality can be described as an empathy gulf, which comprises barriers to imagining others’ lifestyles and goods.
+This can also be expressed in spatially segregated interactions and isolated life worlds that provide meaning to social inequality experiences, resulting in doubts about worthiness when the lower classes contrast themselves with extravagant lifestyles from the upper classes, undermining feelings of social inclusion and cohesion [@sachweh_moral_2012].
+Consequently, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
 758].
-Thus, in a similar vein, as the intergroup contact approach has established [@pettigrew_metaanalytic_2006], we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
+Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
 
-In recent years, we have seen an increase in this _network turn_ of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
-In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interact with those of upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
-Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images about the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
+In recent years, we have seen an increase in this network turn of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
+In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interacting with those of upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
+Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images of the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
 
-In addition, studies that have more directly addressed the relationship between networks and social class have been consistent with previous findings.
+In addition, studies that directly addressed the relationship between networks and social classes have been consistent with previous findings.
 For instance, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively influence support for redistribution, while ties to the working class increase it regardless of the individual class position suggesting that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
 698].
-Similarly, additional socialization sources are cross-class ties through the family members.
-Family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
-A study in the United States has shown that those tied to the upper class through parental relations are less supportive of redistribution and progressive taxation than those with working-class family backgrounds [@lee_consider_2023].
-Besides, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences while households share risk according to the class position of its members, where class homogeneity in ties polarizes preferences between lower and upper classes.
+Similarly, additional socialization sources are cross-class ties through family members.
+In this sense, the family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
+A study in the United States showed that those tied to the upper class through parental relations are less supportive of redistribution and progressive taxation than those with working-class family backgrounds [@lee_consider_2023].
+In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties polarizes preferences between lower and upper classes.
 In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
 
-In sum, we argue that redistributive preferences are influenced by their class-embedded social relations.
+In summary, we argue that redistributive preferences are influenced by class-embedded social relations.
 Therefore, the degree of class segregation in these networks plays a crucial role in shaping support for redistribution.
-Furthermore, the degree of contact between different classes and class homophily reinforces the assimilation of opinions according to surrounding friends and acquaintances.
-Thus, we hypothesize that segregation in similar class environments polarizes own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences.
+Furthermore, the degree of contact between different classes and class homophily reinforces the assimilation of opinions by surrounding friends and acquaintances.
+Thus, we hypothesize that segregation in similar class environments polarizes one’s own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences (H1).
 
-## Economic Inequality, segregation, and redistributive preferences
+##  Consequences of Economic Inequality on Social Networks and Redistributive Preferences
 
 ###  Consequences of Economic Inequality on Social Networks
-The consequences of economic inequality are diverse.
-Regarding social networks, the consequences of interpersonal trust, civic participation, and social resources have been previously reported in the literature.
-In addition, the unequal distribution of economic resources impacts coexistence through the socio-spatial segregation of the inhabitants of a territory.
+
+The consequences of inequality in social relationships are diverse.
+Theoretically, it has been stated that economic inequality deepens material and symbolic differences between members of a society, where those in the most favored positions generally become more distant from those who have access to fewer resources.
+This can constrain or discourage people from actively participating in social life, ultimately affecting the chances of meeting others who hold different economic conditions and lifestyles [@neckerman_inequality_2007, p.
+344].
+In this discussion, one approach has stressed the role of subjective experiences of inequality in social relations, arguing that a broader gap in economic resources has consequences on perceived competition and status anxiety [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024].
+Therefore, driving stronger experiences of relative deprivation undermines trust in others given the difficulties of setting shared goals and perceiving others as part of a collectivity that pursues the common good [@salgado_expectations_2021].
+In contrast, the neo-materialist approach sets the attention on resource availability and attributes much less importance to subjective experiences, arguing that more economically equal societies are also characterized by extended welfare institutions that seek to diminish the consequences of unequal access to resources that provide better conditions for people to be socially engaged by improving social trust and individual well-being [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
+In sum, living in more unequal societies goes hand in hand with more extraordinary experiences of uncertainty, which at the same time may be hindered by a lack of trust in the broader social context, affecting the motives to participate in social activities that play a fundamental role in establishing ties between dissimilar groups, either by status or social class [@lancee_diversity_2017].
+
+Empirically, the few studies on this subject share the assumption that economic inequality translates into social distance in terms of class and status positions, which is the basis for the consolidation of social network segregation.
+Some comparative evidence has shown that in Europe, the patterns of participation and association in formal organizations, as well as those of informal networks in providing social support, are manifested in the form of complementarity or substitution according to the cultural relevance of family or friendship networks and the character of the welfare regime [@pichler_patterns_2007].
+By contrast, @pichler_social_2009 accounts for the role of income inequality in participation in formal and informal networks, showing that more unequal societies depress the extensiveness of formal participation, but not the frequency.
+In addition, it is one of the few studies that shows how, in more unequal societies, class differences in participation are deepened in the diversity of formal participation networks.
+Similarly, @lancee_income_2012 shows that economic inequality reduces participation.
+However, in formal networks, the inhibiting effect of inequality is better evidenced, being less relevant to participation in informal networks.
+In addition, they show that in more unequal societies, the stratification of participation by income level is strengthened, favoring those with greater resources and marginalizing the poorest.
+
+In contrast to studies on participation in formal and informal networks, recent research has emphasized economic inequality in the structure of interpersonal networks.
+The authors @letki_getting_2015 argued that economic inequality may constrain access to more extensive networks and the chances of receiving support through them.
+First, they found that individuals in lower-income groups have smaller networks than those in wealthier groups and are less likely to access resources through their networks.
+However, as inequality increases, low-income individuals hold much more extensive family networks but are less inclined towards utilizing their social ties to access resources in contrast to middle- and higher-income groups, suggesting that "the poor see maintaining ties with a large extended family as crucial for accessing needed help, which they are unlikely to reach through non-kinship ties" [@letki_getting_2015, p.
+244].
+By contrast, @otero_differences_2023 found that income inequality is not directly associated with the network structure.
+However, they found that income inequality can enhance the relationship between educational level, occupational status, and the diversity of social ties.
+Therefore, suggesting that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
+Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and isolation because of the choices of others [@otero_open_2021, p.24].
+In this regard, if we assume that economic inequality sets the conditions for sociability, a consequence of this may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality are also affected by the extent of income differences.
 
 ### Consequences of Economic Inequality on redistributive preferences
-* concerns about the negative consequences (e.g. crime) of inequality on overall social welfare, particularly in high-status groups (Altruism) [@rueda_who_2019]
 
-* convergence in egalitarian preferences in the upper-classes can be normatively grounded according to views about equality of opportunities (Procedural Justice) [@sachweh_why_2019]
+As mentioned, economic inequality influences social relations, either in society as a whole or by strengthening inequalities throughout the social structure.
+However, studies on redistributive preferences have provided mixed evidence of the direct impact of income inequality on support for redistribution [@evans_strong_2018;@trump_income_2023].
+In turn, an open discussion has been raised regarding why those in upper social strata have shown to be more sensitive to changes in economic inequality than those in the lower strata.
 
-\pagebreak
+Theoretically, two approaches were considered in this discussion.
+On the one hand, some studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that, although the rational interest model maintains its general implications, there are nuances within the upper-income strata regarding their greater concerns about the negative externalities of economic inequality (e.g., crime), which ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
+Additionally, another body of literature has suggested that the differences among the affluent can also be understood from a distributive justice framework that focuses on the justice of outcomes and procedures under which resources are allocated [@liebig_sociology_2016].
+Briefly, the central argument suggests that for the affluent groups, procedural justice perceptions matter more for their perceived justice of outcomes.
+In contrast, low-income individuals tend to perceive that the ascribed characteristics are stronger in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
+656].
+Likewise, it has been argued that perceived inequality of opportunity can motivate support for redistribution as a matter of justice in the conditions for getting ahead, while this influence is particularly present in those in higher socioeconomic positions [@kim_socioeconomic_2018].
+Therefore, if the degree of segregation in social networks is indeed related to polarization in redistributive attitudes, we believe that income inequality might also play a role in the relationship between class relations and redistributive attitudes.
 
-# Overview
+Empirically, while an important part of the studies addressing the role of economic inequality and redistribution preferences has focused on income, it is also possible to find efforts that emphasize the role of social class.
+In the first case, comparative studies in various societies have demonstrated (1) the relevance of income position and (2) the sensitivity of high-income groups to material inequality [@Schmidt-Catran2016;@franetovic_preferences_2022;@finseraas_income_2009].
+However, class-based studies have contributed equally to the elucidation of this relationship.
+For example, @edlund_democratic_2015 established that the demand for state-organized redistribution reflects the level of political class conflict in a modern industrialized society.
+Thus, their argument suggests that inequality plays a key role in moderating these conflicts because there is evidence of greater political consensus supporting redistribution in societies with greater material inequality.
+They emphasize that social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
+323].
 
-## At the micro-level:
+Similarly, @curtis_how_2015 suggest two possible implications for the class cleavage in redistributive preferences in contexts of rising economic inequality.
+One argument suggests that the decline in social cohesion expressed in trust, civic participation, and prosocial attitudes might undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
+As a result, less cohesive societies can nurture stronger class polarization that undermines egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
+In contrast, the other argument posits that in the context of greater economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
+66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
+Additionally, it has been suggested that in societies with lower material inequality and predominant middle-class imaginery, the degree of perceived social conflict decreases [@hertel_conflict_2022].
+Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more unequal contexts, where their attitudes gradually converge with the interests of the working class.
 
-- (H1) Being segregated in similar class environments polarize own class interests:
-    * Segregated lower (upper) classes hold more (less) redistributive preferences
-
-## At the macro-level:
-
-- (H2a) Scenario A (booster): Inequality increases the influence of class segregation on redistributive preferences (polarization)
-
-- (H2b) Scenario B (mitigation): Inequality diminishes the influence of class segregation on redistributive preferences (consensus)
+To summarize, the field's current state has led us to establish two competing scenarios based on the reviewed evidence and theoretical assumptions regarding the role of economic inequality in the relationship between class-based segregation and redistributive preferences.
+On the one hand, if we assume that social relations are eroded in more unequal societies, this might lead social classes to be more distant from each other as a matter of lower social trust and participation in formal and informal networks.
+Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger (H2a).
+However, if we assume that economic inequality indeed has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness, it might be possible that the working classes are equally segregated regardless of income inequality in comparison to the more diverse contact and activity networks of the upper classes.
+Likewise, in line with evidence that suggests that the upper classes also tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes (H2b).
 

### 2024-03-18 paper1_jiturra.Rmd
ajustes paper1

@@
 always_allow_html: true      
-linkcolor: black                         # enlaces y citas en color azul
+linkcolor: gray                         # enlaces y citas en color azul
 bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
@@
 \fancyhead[L]{Research Article Draft}
+
 # Introduction
 
-[~500 words]
+Rising economic inequality over the past decades [@piketty_capital_2014] and the recent sanitary crisis have raised citizens' concerns about economic inequality, pushing governments to enact redistributive policies, which has tested the capacity of welfare systems to provide sufficient risk protection for their citizens [@breznau_welfare_2021].
+However, the privileged access to resources held by the upper and intermediate classes has consolidated their resilience capacity in times of greater economic hardship, allowing them to maintain a relatively stable standard of living, in contrast to the decline in the material conditions of working-class families [@moawad_myth_2023].
+In this regard, it has been claimed that economic gaps in economic resources also have a greater effect on social relations.
+Studies on the role of economic inequality have argued that social bonding can be threatened when economic inequality increases, undermines how people perceive each other, their opportunities to participate in social life, and the capacity to knit networks that contribute to social integration [@lancee_income_2012;@letki_getting_2015].
+Therefore, experiencing segregated networks is one of the consequences of greater economic gaps as it represents greater distance between the different social classes  [@pichler_patterns_2007;@otero_space_2022].
+In this regard, it has been argued that segregation can threaten social cohesion and solidarity [@joye_measuring_2019], which in turn can undermine public support for welfare schemes and redistribution [@baldassarri_diversity_2020].
 
-## Class divide in the economic domain
+The sociological tradition has understood social classes through the labor market situation of occupations in terms of employment relations, skill level, and authority within the workplace [@Erikson1992;@Erikson1979].
+Likewise, classes represent relations in the labor market and trace lines in terms of status relations as the foundations for opportunities for action and the consolidation of lifestyles [@weber_economy_1978].
+In this matter, the class situation of individuals and households also trace distinctions in various domains of social life, such as cultural consumption behavior [@Chan2007;@torche_social_2007], ideological preferences [@evans_decline_1993], and popular opinions about the welfare state and redistribution [@Svallfors2006].
+Regarding the latter, despite the claims of a displacement of the distributive struggle between classes by other group identities [@clark_declining_1993;@inglehart_culture_1990], past decade research has persistently demonstrated that class positions indeed still explain economic attitudes towards the welfare state and redistribution [@lindh_class_2020, p.
+421].
+Thus, the claimed blurring of the class cleavage has not been strongly supported while the class differences have been evidenced in perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes on market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
 
-The class divide in political attitudes on the economic domain constitutes a core finding in policy attitudes, where material interests, normative motivations, and sociability practices intersect in attitude formation.
-Theoretically, the tradition in the social mobility field has defined classes as structural positions given their differences in labor market situation distinguished by employment relations, skills level, and authority within the workplace, which traditionally has focused on occupations instead of income or educational credentials [@Erikson1992;@Erikson1979].
-In addition, political sociologists have systematically demonstrated that classes trace differences in other domains of social life as well, including ideological preferences [@evans_decline_1993], cultural consumption behavior [@Chan2007], and attitudes toward redistribution and welfare [@Svallfors2006].
-Despite the claims of a supposed displacement of the distributive struggle between classes as a result of the salience of other group identities [@clark_declining_1993;@inglehart_culture_1990], during the last decades, the research has extensively developed on how class positions shape economic attitudes in the domains of redistribution, social security, and the welfare state [@lindh_class_2020, p.
-421].
-Empirically, the claimed blurring of the class cleavage has not been strongly supported, where class divides is clear regarding attitudes in the economic domain in general, such as perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes toward market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences in particular [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
+However, the study of redistributive preferences has been mainly focused on the individual and household situation.
+In contrast, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
+In this regard, how people form their friendship and partnership ties tends to be homogeneous because of the tendency towards homophily in forming interpersonal networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+Hereby, we argue that the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes.
+In this regard, recent research has argued that the degree of segregation in the composition of social ties is a window for learning about others' lifestyles, economic conditions, and worldviews [@mijs_inequality_2018;@otero_power_2023].
+However, there has been no systematic dialogue regarding the role of social ties on preferences for redistribution from a social network perspective.
+Therefore, this research aims to contribute to the ongoing literature on class-based network segregation on attitudes toward redistribution [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
 
-In this regard, class-based explanations of redistributive attitudes have been mainly focused on the individual situation.
-Hence, one main claim is that economic preferences can be explained through the labor market situation, which comprises access to economic resources and exposure to unemployment risk [@meltzer_rational_1981;@rehm_risks_2009].
-However, as material interests might prevail in scarcity, normative or value-driven motivations can also explain egalitarian economic preferences [@Kulin2013;@feldman_humanitarian_2001].
-Besides, values become salient under greater security conditions but weaken under greater precariousness [@Maldonadoetal2019].
-Alternatively, part of the literature suggests that the class divide can also be explained on top of the social interactions experienced in work relations [@oesch_redrawing_2006].
-Given that workers spend a substantial part of their time at workplaces, social relations in the workspace might drive greater contact with diverse people in the case of interpersonal services, or vertical monitoring in managerial occupations can also imprint normative views that ultimately shape political opinions [@oesch_electoral_2018].
-However, it is challenging to disentangle if the class differences are undoubtedly explained through work experiences because it is feasible to argue that political preferences are the result of early-life internalization of social norms, which might be crystalized in career self-selection paths, which also might be influenced by the organizational hiring requirements for specific jobs [@kitschelt_occupations_2014].
+While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention must be devoted to understanding the role of social environments in class relations.
+This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
+In addition, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis for legitimacy and popular support for welfare schemes [@mau_moral_2003].
+This research aims to contribute to the literature on preferences toward redistribution from a relational perspective, focusing on how the structural properties of networks can influence people's preferences toward economic redistribution.
 
-While prior research has predominantly concentrated on examining the impact of social class through an individualistic lens, it is noteworthy that more attention needs to be devoted to understanding the role of social environments in class relations.
-This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
-Besides, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis of the legitimacy and popular support for welfare schemes [@mau_moral_2003].
-Hereby, we argue that the scope of class analysis in attitude formation urges to be extended further to the individual or household situation, stressing the role of social ties and segregation as part of the socialization processes involved in the internalization of shared norms, class identity formation, conflict, and cooperation between classes.
-
-- What is the role of class-based network segregation on redistributive preferences?
-
-- Does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
+Our research seeks to provide answers to two key questions.
+Firstly, at the micro-level, what is the impact of class-based network segregation on redistributive preferences?
+Secondly, at the macro-level, does economic inequality have a role to play in the relationship between class-based network segregation and redistributive preferences?
+To achieve this, we have analyzed data from the International Social Survey Program (ISSP) 2017, which comprises a sample of over 33,000 individuals across 31 countries globally.
+In this regard, the ISSP has a unique opportunity to date since it includes information on interpersonal networks through the position generator, the core questions for class position allocation, and attitudes toward economic inequality and redistribution.
 
@@
 
-By contrast, cross-class embeddedness can be described in terms of social activities, generational changes, and life courses.
+By contrast, cross-class embeddedness can be described in terms of social activities, generational changes, and the life course.
 In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in civic engagement behavior.
@@
 
-Apart from the individual approach to attitude formation, we argue that people also form opinions in the economic domain based on their social relations.
+Besides from the individual approach to attitude formation, we argue that people also form opinions in the economic domain based on their social relations.
 Despite limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
@@
 467].
-From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information, ultimately shaping perceptions of inequality [@mijs_is_2021].
+From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information that ultimately shapes their perceptions of inequality [@mijs_is_2021].
 Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more isolated discussion networks [@summers_deliberating_2022].
@@
 48].
-Furthermore, these social relations contribute to the degree to which people reflect on the collective, such that in societies where opportunities for contact between people of different social classes can be detrimental to social integration.
-It has been argued that the social distance among groups widened by extreme inequality can be described as an empathy gulf, which comprises barriers to imagining others’ lifestyles and goods.
-This can also be expressed in spatially segregated interactions and isolated life worlds that provide meaning to social inequality experiences, resulting in doubts about worthiness when the lower classes contrast themselves with extravagant lifestyles from the upper classes, undermining feelings of social inclusion and cohesion [@sachweh_moral_2012].
+Furthermore, social integration can be affected in societies with lower contact opportunities between different social classes, where social distance among them widened by extreme inequality can create an “empathy gulf” that comprises barriers to imagining others’ lifestyles [@sachweh_moral_2012].
+In this matter, spatially segregated interactions may nurture doubts about worthiness when the lower classes contrast themselves with the lifestyles of the upper classes, which might undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
 Consequently, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
 758].
-Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
+Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties, where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
 
 In recent years, we have seen an increase in this network turn of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
-In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interacting with those of upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
+In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interacting with those of the upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
 Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images of the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
@@
 In this sense, the family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
-A study in the United States showed that those tied to the upper class through parental relations are less supportive of redistribution and progressive taxation than those with working-class family backgrounds [@lee_consider_2023].
+A study in the United States showed that those tied to the upper class through parental relations support redistribution and progressive taxation less than those with working-class family backgrounds [@lee_consider_2023].
 In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties polarizes preferences between lower and upper classes.
@@
 
-In summary, we argue that redistributive preferences are influenced by class-embedded social relations.
-Therefore, the degree of class segregation in these networks plays a crucial role in shaping support for redistribution.
-Furthermore, the degree of contact between different classes and class homophily reinforces the assimilation of opinions by surrounding friends and acquaintances.
-Thus, we hypothesize that segregation in similar class environments polarizes one’s own class interests, where segregated lower (upper) classes hold more (less) redistributive preferences (H1).
+In summary, we argue that class-embedded social relations play a substantial role in shaping support for redistribution.
+In this sense, the tendency to form homophilous social ties in terms of social class reinforces attitudes and consolidates opinion similarity.
+Thus, we hypothesize that segregation in similar class environments polarizes individual class interests so that segregated lower (upper) classes hold more (less) redistributive preferences (H1).
 
@@
 The consequences of inequality in social relationships are diverse.
-Theoretically, it has been stated that economic inequality deepens material and symbolic differences between members of a society, where those in the most favored positions generally become more distant from those who have access to fewer resources.
-This can constrain or discourage people from actively participating in social life, ultimately affecting the chances of meeting others who hold different economic conditions and lifestyles [@neckerman_inequality_2007, p.
+Theoretically, it has been stated that economic inequality deepens material and symbolic differences between members of a society, where those in the most favored positions generally become more distant from those with access to fewer resources.
+Consequently, lower resources can constrain or discourage people from actively participating in social life, ultimately affecting the chances of meeting others with different economic conditions and lifestyles [@neckerman_inequality_2007, p.
 344].
 In this discussion, one approach has stressed the role of subjective experiences of inequality in social relations, arguing that a broader gap in economic resources has consequences on perceived competition and status anxiety [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024].
-Therefore, driving stronger experiences of relative deprivation undermines trust in others given the difficulties of setting shared goals and perceiving others as part of a collectivity that pursues the common good [@salgado_expectations_2021].
+Therefore, driving stronger experiences of relative deprivation undermines trust in others, given the difficulties of setting shared goals and perceiving others as part of a collectivity that pursues the common good [@salgado_expectations_2021].
 In contrast, the neo-materialist approach sets the attention on resource availability and attributes much less importance to subjective experiences, arguing that more economically equal societies are also characterized by extended welfare institutions that seek to diminish the consequences of unequal access to resources that provide better conditions for people to be socially engaged by improving social trust and individual well-being [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
@@
 
-Empirically, the few studies on this subject share the assumption that economic inequality translates into social distance in terms of class and status positions, which is the basis for the consolidation of social network segregation.
-Some comparative evidence has shown that in Europe, the patterns of participation and association in formal organizations, as well as those of informal networks in providing social support, are manifested in the form of complementarity or substitution according to the cultural relevance of family or friendship networks and the character of the welfare regime [@pichler_patterns_2007].
-By contrast, @pichler_social_2009 accounts for the role of income inequality in participation in formal and informal networks, showing that more unequal societies depress the extensiveness of formal participation, but not the frequency.
-In addition, it is one of the few studies that shows how, in more unequal societies, class differences in participation are deepened in the diversity of formal participation networks.
+Empirically, the few studies on this subject share the assumption that economic inequality translates into social distance in terms of class and status positions, which is the basis for consolidating network segregation.
+Cross-national comparisons in Europe show that the patterns of participation and association in formal organizations, as well as those of informal networks in providing social support, are manifested in the form of complementarity or substitution according to the cultural relevance of family or friendship networks and the character of the welfare regime [@pichler_patterns_2007].
+By contrast, @pichler_social_2009 accounts for the role of income inequality on participation in formal and informal networks, showing that more unequal societies depress the extensiveness of formal participation but not the frequency.
+In addition, it is one of the few studies that show how, in more unequal societies, class differences in participation are deepened in the diversity of formal participation networks.
 Similarly, @lancee_income_2012 shows that economic inequality reduces participation.
@@
 In contrast to studies on participation in formal and informal networks, recent research has emphasized economic inequality in the structure of interpersonal networks.
-The authors @letki_getting_2015 argued that economic inequality may constrain access to more extensive networks and the chances of receiving support through them.
-First, they found that individuals in lower-income groups have smaller networks than those in wealthier groups and are less likely to access resources through their networks.
-However, as inequality increases, low-income individuals hold much more extensive family networks but are less inclined towards utilizing their social ties to access resources in contrast to middle- and higher-income groups, suggesting that "the poor see maintaining ties with a large extended family as crucial for accessing needed help, which they are unlikely to reach through non-kinship ties" [@letki_getting_2015, p.
+For instance, @letki_getting_2015 argued that economic inequality may constrain access to more extensive networks and the chances of receiving support through them.
+First, they found that individuals in lower-income groups have smaller networks than those in wealthier groups and are less likely to access resources through them.
+However, as inequality increases, low-income individuals hold much more extensive family networks but are less inclined towards utilizing their social ties to access resources than middle- and higher-income groups.
+They suggest that "the poor see maintaining ties with a large extended family as crucial for accessing needed help, which they are unlikely to reach through non-kinship ties" [@letki_getting_2015, p.
 244].
@@
 However, they found that income inequality can enhance the relationship between educational level, occupational status, and the diversity of social ties.
-Therefore, suggesting that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
+They suggest that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
 Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and isolation because of the choices of others [@otero_open_2021, p.24].
-In this regard, if we assume that economic inequality sets the conditions for sociability, a consequence of this may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality are also affected by the extent of income differences.
+In this regard, if we assume that economic inequality sets the conditions for sociability, a possible consequence may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality is also affected by the extent of income differences.
 
-### Consequences of Economic Inequality on redistributive preferences
+### Consequences of Economic Inequality on Redistributive Preferences
 
-As mentioned, economic inequality influences social relations, either in society as a whole or by strengthening inequalities throughout the social structure.
+As mentioned, economic inequality influences social relations overall or strengthens inequalities throughout the social structure.
 However, studies on redistributive preferences have provided mixed evidence of the direct impact of income inequality on support for redistribution [@evans_strong_2018;@trump_income_2023].
-In turn, an open discussion has been raised regarding why those in upper social strata have shown to be more sensitive to changes in economic inequality than those in the lower strata.
+In turn, an open discussion has been raised regarding why those in the upper social strata are more sensitive to changes in economic inequality than those in the lower strata.
 
@@
 On the one hand, some studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that, although the rational interest model maintains its general implications, there are nuances within the upper-income strata regarding their greater concerns about the negative externalities of economic inequality (e.g., crime), which ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Additionally, another body of literature has suggested that the differences among the affluent can also be understood from a distributive justice framework that focuses on the justice of outcomes and procedures under which resources are allocated [@liebig_sociology_2016].
-Briefly, the central argument suggests that for the affluent groups, procedural justice perceptions matter more for their perceived justice of outcomes.
+Additionally, another body of literature has suggested that the differences among the affluent can be understood from a distributive justice framework that focuses on the justice evaluation under which economic resources are allocated [@liebig_sociology_2016].
+The central argument suggests that affluent groups are more sensitive to economic inequality changes as they perceive that the overall opportunity structure is affected.
 In contrast, low-income individuals tend to perceive that the ascribed characteristics are stronger in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
 656].
-Likewise, it has been argued that perceived inequality of opportunity can motivate support for redistribution as a matter of justice in the conditions for getting ahead, while this influence is particularly present in those in higher socioeconomic positions [@kim_socioeconomic_2018].
-Therefore, if the degree of segregation in social networks is indeed related to polarization in redistributive attitudes, we believe that income inequality might also play a role in the relationship between class relations and redistributive attitudes.
+Likewise, it has been argued that perceived inequality of opportunity can motivate support for redistribution as a matter of justice in the conditions for getting ahead, showing that this is particularly present in individuals in higher socioeconomic positions [@kim_socioeconomic_2018].
+Therefore, if the degree of segregation in social networks is related to polarization in redistributive attitudes, we believe that income inequality might also play a role in the relationship between class relations and redistributive attitudes.
 
 Empirically, while an important part of the studies addressing the role of economic inequality and redistribution preferences has focused on income, it is also possible to find efforts that emphasize the role of social class.
-In the first case, comparative studies in various societies have demonstrated (1) the relevance of income position and (2) the sensitivity of high-income groups to material inequality [@Schmidt-Catran2016;@franetovic_preferences_2022;@finseraas_income_2009].
+In the first case, comparative studies in various societies have demonstrated (1) the relevance of income position and (2) the sensitivity of high-income groups to material inequality [@Schmidt-Catran2016; @franetovic_preferences_2022; @finseraas_income_2009].
 However, class-based studies have contributed equally to the elucidation of this relationship.
@@
 66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
-Additionally, it has been suggested that in societies with lower material inequality and predominant middle-class imaginery, the degree of perceived social conflict decreases [@hertel_conflict_2022].
-Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more unequal contexts, where their attitudes gradually converge with the interests of the working class.
+Additionally, it has been suggested that the degree of perceived social conflict decreases in societies with lower material inequality and a predominant middle-class imaginery [@hertel_conflict_2022].
+Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class.
 
-To summarize, the field's current state has led us to establish two competing scenarios based on the reviewed evidence and theoretical assumptions regarding the role of economic inequality in the relationship between class-based segregation and redistributive preferences.
-On the one hand, if we assume that social relations are eroded in more unequal societies, this might lead social classes to be more distant from each other as a matter of lower social trust and participation in formal and informal networks.
+To summarize, the current state of research has led us to establish two competing scenarios based on the reviewed evidence and theoretical assumptions regarding the role of economic inequality in the relationship between class-based segregation and redistributive preferences.
+On the one hand, if we assume that social relations are eroded in more unequal societies, social classes might be more distant due to lower social trust and participation in formal and informal networks.
 Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger (H2a).
-However, if we assume that economic inequality indeed has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness, it might be possible that the working classes are equally segregated regardless of income inequality in comparison to the more diverse contact and activity networks of the upper classes.
-Likewise, in line with evidence that suggests that the upper classes also tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes (H2b).
+In contrast, if we assume that economic inequality has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness.
+In that case, it might be possible that the working classes are equally segregated regardless of income inequality compared to the more diverse contact and activity networks of the upper classes.
+Likewise, in line with evidence that suggests that the upper classes tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes (H2b).
 
@@
 
-[1500 words]
+_Data_
+
+_Variables_
+
+_Method_
 
 # Results
+
+## Descriptive
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+## Multivariate results
+
+```{r, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
+
+digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
+digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
+                    digclas1_VW_3,
+                    # digclas1_VW_4,
+                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class")
+
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
+       caption = "Multilevel models for class-based network segregation and redistributive preferences",
+       custom.note = "%stars. Models include sampling weights. Gender and Age included as controls",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.60,
+      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+       float.pos = "h!",
+       use.packages = F)
+```
+
+\newpage
+
+```{r, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class'}
+int_homo <- digclas1_VW_7
+df_pred1 <- 
+  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
+              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.1),
+                                 dclass3res_V = levels(dfreg$dclass3res_V)))
+# names(df_pred1)
+df_pred1 %>% 
+ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=2,color="black") +
+  facet_grid(~factor(dclass3res_V, levels=
+                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
+                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
+  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_y_continuous(limits = c(50,80))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+       x="Network homogeneity",y="Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+
+```
+
+\newpage
+
+```{r, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=gini_disp*100) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+socialtrust_gc+
+         dclass3res_V+dclass3spo_V+
+         female_gc+agenum_gc+age2_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_controls <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+socialtrust_gc+
+         dclass3res_V+dclass3spo_V+
+         female_gc+agenum_gc+age2_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + rel_red + gv_spen +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+socialtrust_gc+
+         dclass3res_V+dclass3spo_V+
+         female_gc+agenum_gc+age2_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + rel_red + gv_spen +
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,homo_V_gini_controls,homo_V_gini_full)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP (per capita)",
+              rel_red = "Relative Redistribution",
+              gv_spen = "Government spending (percentage of GDP)",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity x Intermediate Class x Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity x Working Class x Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive preferences",
+       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3, "Homogeneity x Social Class"=8:9, "Homogeneity x Social Class x Income Inequality"=11:12),
+       float.pos = "h!",
+       use.packages = F)
+```
+
+```{r}
+
+```
+
+\newpage
 

### 2024-03-19 paper1_jiturra.Rmd
backup

@@
   know_total,
-  socialtrust,
+  # socialtrust,
   Q03pcm,
@@
 digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
 digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
@@
               know_total="Network size",
-              socialtrust="Social Trust",
+              # socialtrust="Social Trust",
               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
@@
        symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      # groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
        float.pos = "h!",
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
 dfreg <- df1 %>% dplyr::select(
@@
   # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
+  filter(country2 != "SVN") %>% 
+  na.omit()
+
+# dfreg$wstate <- scale(scale(dfreg$rel_red) + scale(dfreg$gv_spen))
+dfreg$wstate <- scale(dfreg$gv_spen)
 
@@
 
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- na.omit(dfreg)
+dfreg$gini_disp <- scale(dfreg$gini_disp)
 
@@
          homclass3_V_gc+
-         know_total_gc+socialtrust_gc+
+         know_total_gc+
+         socialtrust_gc+
          dclass3res_V+dclass3spo_V+
@@
          union_gc+workst_gc+
-         gini_disp +loggdppercapita + rel_red + gv_spen +
+         gini_disp +loggdppercapita + wstate +
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
@@
          union_gc+workst_gc+
-         gini_disp +loggdppercapita + rel_red + gv_spen +
+         gini_disp +loggdppercapita + wstate +
          homclass3_V_gc*
@@
               loggdppercapita = "GDP (per capita)",
-              rel_red = "Relative Redistribution",
-              gv_spen = "Government spending (percentage of GDP)",
+              # rel_red = "Relative Redistribution",
+              # gv_spen = "Government spending (percentage of GDP)",
+               wstate="Size of Welfare State",
               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
@@
 
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+knitreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive preferences",
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3, "Homogeneity x Social Class"=8:9, "Homogeneity x Social Class x Income Inequality"=11:12),
+      # groups = list("Social Class (Ref.= Service Class)" = 2:3, "Homogeneity x Social Class"=8:9, "Homogeneity x Social Class x Income Inequality"=11:12),
        float.pos = "h!",
@@
 ```{r}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
 
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate=mean(dfreg$wstate),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc), max(dfreg$homclass3_V_gc), by= 0.1),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_line(size=0.75) +
+  geom_point(size=2) +
+  geom_ribbon(alpha=0.1,size=1,linetype=1) +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Class-based network homogeneity (CWC)",
+       title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality") +
+  # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax)", breaks = NULL, labels = NULL)) +
+  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
+  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
+  theme(legend.position="bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
 ```

### 2024-03-19 procesamiento/02-prod_prep-macro.Rmd
backup

@@
 
+**ILO Data**
+
+```{r}
+
+ilo_data <- read.csv(file = here::here("input/data/original/ILO-data/WEOApr2022all.csv"))
+frq(ilo_data$Subject.Descriptor)
+
+ilo_data_1 <- ilo_data %>% filter(Subject.Descriptor %in% c("General government total expenditure","General government revenue"))
+ilo_data_1$ccode <- countrycode::countrycode(sourcevar = ilo_data_1$ISO,origin = "iso3c",destination = "iso3n")
+
+```
+
 **GDP: PEN data**

### 2024-03-19 procesamiento/02-prod_prep-macro.Rmd
ajustes welfare state variables

--- 2024-02-26 procesamiento/02-prod_prep-macro.Rmd
@@
 
+**ILO Data**
+
+```{r}
+ilo_data <- read.csv(file = here::here("input/data/original/ILO-data/WEOApr2022all.csv"))
+frq(ilo_data$Subject.Descriptor)
+
+ilo_data_1 <- ilo_data %>% filter(Subject.Descriptor %in% c("General government total expenditure","General government revenue"), Units == "Percent of GDP")
+ilo_data_1$ccode <- countrycode::countrycode(sourcevar = ilo_data_1$ISO,origin = "iso3c",destination = "iso3n") 
+ilo_data_1<- ilo_data_1 %>% filter(ccode %in% countries$ccode)
+ilo_data_1 <- ilo_data_1 %>% select(ccode,WEO.Country.Code:Country.Series.specific.Notes,X2010:X2020)
+names(ilo_data_1) <- tolower(names(ilo_data_1))
+names(ilo_data_1) <- str_replace_all(string = names(ilo_data_1),pattern = "x",replacement = "Y_")
+
+ilo_tax <- ilo_data_1 %>% filter(weo.subject.code=="GGR_NGDP") 
+ilo_spe <- ilo_data_1 %>% filter(weo.subject.code=="GGX_NGDP") 
+# Example wide format data
+
+# Convert from wide to long format
+long_ilo_tax <- ilo_tax %>%
+  select(ccode,Y_2010:Y_2016) %>% 
+  pivot_longer(cols = starts_with("Y_"),
+               names_to = "year",
+               names_prefix = "Y_",
+               values_to = "ilo_taxrev")
+# long_ilo_tax$country <- countrycode::countrycode(sourcevar = long_ilo_tax$ccode,origin = "iso3n",destination = "iso3c")
+
+long_ilo_spe <- ilo_spe %>%
+  select(ccode,Y_2010:Y_2016) %>% 
+  pivot_longer(cols = starts_with("Y_"),
+               names_to = "year",
+               names_prefix = "Y_",
+               values_to = "ilo_govspe")
+
+ilo_df <- left_join(long_ilo_tax,long_ilo_spe) %>% filter(year==2016)
+
+# long_ilo_spe$country <- countrycode::countrycode(sourcevar = long_ilo_spe$ccode,origin = "iso3n",destination = "iso3c")
+
+# Plot points connected by a line representing time
+# ggplot(long_ilo_spe, aes(x = factor(year), y = govspe, group = factor(country), color = factor(country))) +
+#   geom_line() +
+#   geom_point(size = 3) +
+#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
+#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
+#   theme_minimal()
+# 
+# 
+# # Plot points connected by a line representing time
+# ggplot(long_ilo_tax, aes(x = factor(year), y = taxrev, group = factor(country), color = factor(country))) +
+#   geom_line() +
+#   geom_point(size = 3) +
+#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
+#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
+#   theme_minimal()
+
+```
+
 **GDP: PEN data**
@@
   left_join(ocde) %>% 
-  left_join(wid_df1)
+  left_join(wid_df1) %>% 
+  left_join(ilo_df)
 

### 2024-03-19 paper1_jiturra.Rmd
ajustes pdf

--- 2024-03-18 paper1_jiturra.Rmd
@@
 
-_Data_
+## Data {-}
 
-_Variables_
+## Variables {-}
 
-_Method_
+### _Individual level_ {-}
+
+* **Social class** (Erikson & Goldthorpe, 1992): EGP Class Scheme, based on ISCO-08 codes for (i) occupations and using the algorithm that considers (ii) self-employment status and (iii) number of workers (Ganzeboom & Treiman, 2003).
+As a result, three big classes are created: Service Class (I+II),  Intermediate Class (III+IV), and Working Class (VI+VII).
+
+* **Class-based network segregation** [@otero_open_2021]: Based on the ten occupations of the position generator, three status groups are created to mirror the three social classes described above:
+  - High: Lawyer, Executive of a large firm, and Human resource manager
+  - Middle: School teacher, Police officer and Nurse
+  - Low: Car mechanic, Bus driver, Hairdresser, and Home or office cleaner
+
+After this, we calculated the number of social ties for each status group.
+Consequently, the group closer to their class position obtains a proxy of the number of ingroup social ties.
+Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network.
+Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are similar (homogeneity).
+In substantial terms, higher values represent greater social distance from other social classes in society.
+
+### _Macro level_ {-}
+
+* Income Inequality (post-taxes): Gini Index from the World Income Inequality Dataset (https://wid.world/)
+
+* Gross Domestic Product per capita (WID, 2022)
+
+* Size of the welfare state [see @edlund_democratic_2015]
+  - Current Redistribution (Solt, 2020)
+  - Tax revenue, as percentage of GDP (ILO)
+  - Welfare expenditure, as Percentage of GDP (ILO)
+
+## Method {-}
+
+Multilevel regression models with random and fixed effects. For the cross-level interactions we include random slopes and all variables are group-mean centered (CWC)
 
@@
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Network homogeneity",y="Redistributive preferences") +
+       x="Class-based network homogeneity",y="Redistributive preferences") +
   theme(legend.position = "none", legend.title = element_blank())
@@
   rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
   d10d1=wid_p90p10,
@@
   # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
+  filter(country2 != "SVN") %>% 
+  na.omit()
+
+# dfreg %>% dplyr::select(gini_disp,rel_red,abs_red,ilo_taxrev,ilo_govspe) %>% tab_corr()
+
+dfreg$wstate1 <- scale(scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+# dfreg$wstate <- scale(dfreg$gv_spen)
 
@@
 
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- na.omit(dfreg)
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
 
@@
 
-homo_V_gini_controls <- 
+homo_V_gini_gdp <- 
   lmer(egal~ 
          homclass3_V_gc+
-         know_total_gc+socialtrust_gc+
+         know_total_gc+
+         socialtrust_gc+
          dclass3res_V+dclass3spo_V+
@@
          union_gc+workst_gc+
-         gini_disp +loggdppercapita + rel_red + gv_spen +
+         gini_disp +loggdppercapita +
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
 
-homo_V_gini_full <- 
+homo_V_gini_gdp_wstate2 <- 
   lmer(egal~ 
          homclass3_V_gc+
-         know_total_gc+socialtrust_gc+
+         know_total_gc+
+         socialtrust_gc+
          dclass3res_V+dclass3spo_V+
@@
          union_gc+workst_gc+
-         gini_disp +loggdppercapita + rel_red + gv_spen +
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V+
+         female_gc+agenum_gc+age2_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V+
+         female_gc+agenum_gc+age2_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
          homclass3_V_gc*
@@
 
-digclas1_macro <- list(homo_V_gini,homo_V_gini_controls,homo_V_gini_full)
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
 
@@
               loggdppercapita = "GDP (per capita)",
-              rel_red = "Relative Redistribution",
-              gv_spen = "Government spending (percentage of GDP)",
+              # ilo_taxrev = "Tax revenue (percentage of GDP)",
+              # ilo_govspe = "Government spending (percentage of GDP)",
+              # abs_red = "Redistribution",
+              # wstate1="Size of Welfare State (tax+spend)",
+              wstate2="Size of the welfare state",
               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3, "Homogeneity x Social Class"=8:9, "Homogeneity x Social Class x Income Inequality"=11:12),
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
        float.pos = "h!",
@@
 
-```{r}
+```{r, fig.dim=c(12,6),fig.cap='Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
 
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc), max(dfreg$homclass3_V_gc), by= 0.1),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+
+df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Class-based network homogeneity (CWC)",
+       # title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality"
+       ) +
+  # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax)", breaks = NULL, labels = NULL)) +
+ # scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
+  # scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position="bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
 ```
@@
 ```
+
+```{r oldcode, eval=FALSE, include=FALSE}
+
+# homo_V_gini_gdp_tax <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + ilo_taxrev +
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+# 
+# 
+# homo_V_gini_gdp_govsp <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + ilo_govspe +
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+# 
+# 
+# homo_V_gini_gdp_redis <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + abs_red +
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+# 
+# homo_V_gini_gdp_controls <-
+#   lmer(egal~
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+# 
+# 
+# homo_V_gini_gdp_wstate1 <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + wstate1+
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+# homo_V_gini_full <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
+#          homclass3_V_gc*
+#          dclass3res_V*
+#          gini_disp + 
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+# 
+# homo_V_gini_full1 <- 
+#   lmer(egal~ 
+#          homclass3_V_gc+
+#          know_total_gc+
+#          socialtrust_gc+
+#          dclass3res_V+dclass3spo_V+
+#          female_gc+agenum_gc+age2_gc+
+#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+#          union_gc+workst_gc+
+#          gini_disp +loggdppercapita + wstate1+
+#          homclass3_V_gc*
+#          dclass3res_V*
+#          gini_disp + 
+#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+```

### 2024-03-19 procesamiento/02-prod_prep-macro.Rmd
ajustes pdf

@@
                values_to = "ilo_taxrev")
-# long_ilo_tax$country <- countrycode::countrycode(sourcevar = long_ilo_tax$ccode,origin = "iso3n",destination = "iso3c")
+long_ilo_tax$ilo_taxrev <- as.numeric(long_ilo_tax$ilo_taxrev)
 
@@
                values_to = "ilo_govspe")
+
+long_ilo_spe$ilo_govspe <- as.numeric(long_ilo_spe$ilo_govspe)
 

### 2024-03-20 paper1_jiturra.Rmd
up trackdown

@@
  rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
+
+ # install.packages("trackdown")
+ trackdown::upload_file(file = "paper1_jiturra.Rmd", hide_code = TRUE,gpath = '001_PhD/002dissertation/paper1')
+
 ```
@@
 
-* **Social class** (Erikson & Goldthorpe, 1992): EGP Class Scheme, based on ISCO-08 codes for (i) occupations and using the algorithm that considers (ii) self-employment status and (iii) number of workers (Ganzeboom & Treiman, 2003).
-As a result, three big classes are created: Service Class (I+II),  Intermediate Class (III+IV), and Working Class (VI+VII).
+**Redistributive preferences**: Two indicators available in the questionnaire were used to measure redistributive preferences.
+First, support for government redistribution (1) is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and the egalitarian preferences represented by the item (2) 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
+Thus, based on previous research and the high degree of correlation between the indicators (_r_ = 0.7), we proceed to reverse-code and create a standardized average index ranging from 1 to 100, where higher values represent greater redistributive preferences [@svallfors_government_2013].
 
-* **Class-based network segregation** [@otero_open_2021]: Based on the ten occupations of the position generator, three status groups are created to mirror the three social classes described above:
-  - High: Lawyer, Executive of a large firm, and Human resource manager
-  - Middle: School teacher, Police officer and Nurse
-  - Low: Car mechanic, Bus driver, Hairdresser, and Home or office cleaner
+[likertplot]
+
+**Social class**: A collapsed version of the Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme was used [@Erikson1992;@Erikson1979], one of the most the most consistent and validated measure for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021].
+Thus, based on the recently developed DIGCLASS algorithm, we draw on the available information regarding (i) occupations, (ii) self-employment status and (iii) the number of workers [@cimentada_digclass_2023].
+As a result, following previous research, a version of three big classes is employed, including the Service Class (I+II),  Intermediate Class (III+IV), and Working Class(V+VI+VII) [@sosnaud_class_2013;@edlund_influence_2003].
+
+**Class-based network segregation**: To create our measure of network homogeneity based on social class, we employed the position generator available in the questionnaire.
+This instrument has been widely employed in social capital studies, based on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
+In this case, the position generator shows a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
+In the case of the indicator used here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
+On the basis of this, it is possible to obtain the total number of a person's social ties.
+Subsequently, the occupations were classified into three groups resembling social class positions [@otero_open_2021].
+First, the Lawyer, Executive of a large firm, and Human resource manager are classified as high status.
+Then, a School teacher, Police officer, and Nurse are considered as Intermediate status.
+Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered as low-status occupations.
 
@@
 Consequently, the group closer to their class position obtains a proxy of the number of ingroup social ties.
-Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network.
+Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
 Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are similar (homogeneity).
@@
   - Tax revenue, as percentage of GDP (ILO)
-  - Welfare expenditure, as Percentage of GDP (ILO)
+  - Welfare expenditure, as percentage of GDP (ILO)
 
@@
 
-Multilevel regression models with random and fixed effects. For the cross-level interactions we include random slopes and all variables are group-mean centered (CWC)
+Multilevel regression models with random and fixed effects. For the cross-level interactions, we include random slopes, and all variables are group-mean centered (CWC)
 

### 2024-03-22 paper1_jiturra.Rmd
upload

@@
   agenum,
+  partner,
+  religion,
   union,
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
 digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
@@
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = "Multilevel models for class-based network segregation and redistributive preferences",
-       custom.note = "%stars. Models include sampling weights. Gender and Age included as controls",
+       caption = "Multilevel models for Class-based network segregation and Redistributive Preferences",
+       custom.note = "%stars. Models include sampling weights. Gender, age, marital status and religion are included as controls",
        caption.above = T,leading.zero = T,
@@
       groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
        float.pos = "h!",
@@
   agenum,
+  religion,
+  partner,
   union,
@@
 dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
 
@@
          dclass3res_V+dclass3spo_V+
-         female_gc+agenum_gc+age2_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
@@
          dclass3res_V+dclass3spo_V+
-         female_gc+agenum_gc+age2_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
@@
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive preferences",
+       caption = "Multilevel models for Income Inequality, Network segregation and RedistributivePpreferences",
        custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
@@
        float.pos = "h!",
+      # custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),      
        use.packages = F)
@@
 
-```{r, fig.dim=c(12,6),fig.cap='Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality'}
+```{r, fig.dim=c(12,6),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------

### 2024-03-22 procesamiento/01-prod_prep-micro.Rmd
upload

@@
                         SPEMPREL=spemprel,
-                        SPWRKSUP=spwrksup)
+                        SPWRKSUP=spwrksup,
+                        ATTEND=attend, 
+                        RELIGGRP=religgrp,
+                        MARITAL=marital)
 
@@
 
+frq(df1$ATTEND)
+df1$relig <- car::recode(df1$ATTEND,recodes = "c(97,98,99)=NA",as.numeric = T)
+df1$relig <- set_na(df1$relig,na = c(97,98,99))
+df1$relig <- sjmisc::rec(x = df1$relig,rec = "rev")
+frq(df1$relig)
+
+df1$religcat <- car::recode(df1$ATTEND,recodes = "0=0;1:7=1;c(97,98,99)=NA",as.factor = T)
+df1$religcat <- set_na(df1$religcat,na = c(97,98,99))
+sjlabelled::set_label(df1$religcat) <- "Attendance of religious services"
+frq(df1$religcat)
+
+frq(df1$RELIGGRP)
+df1$religion <- car::recode(df1$RELIGGRP,recodes = "0=0;1:10=1;c(97,98,99)=NA",as.factor = T)
+df1$religion <- set_na(df1$religion,na = c(97,98,99))
+sjlabelled::set_label(df1$religion) <- "Religion"
+df1$religion <- factor(df1$religion,labels = c("No Religion","Has Religion"))
+frq(df1$religion)
+
+frq(df1$MARITAL)
+df1$partner <- df1$MARITAL
+frq(df1$partner)
+df1$partner <- ifelse(df1$partner==9& df1$c_alphan =="CN",yes = 2,no = df1$partner)
+frq(df1$partner)
+df1$partner <- car::recode(df1$partner,recodes = "1:2=1;3:6=0;c(7,9)=NA",as.factor = T)
+df1$partner <- factor(df1$partner,labels = c("No partner","Has a partner"))
+frq(df1$partner)
 ```

### 2024-03-25 paper1_jiturra.Rmd
ajustes

@@
 
-**Social class**: A collapsed version of the Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme was used [@Erikson1992;@Erikson1979], one of the most the most consistent and validated measure for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021].
+**Social class**:  The Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme is employed [@Erikson1992;@Erikson1979], one of the most consistent and validated measure for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
 Thus, based on the recently developed DIGCLASS algorithm, we draw on the available information regarding (i) occupations, (ii) self-employment status and (iii) the number of workers [@cimentada_digclass_2023].
-As a result, following previous research, a version of three big classes is employed, including the Service Class (I+II),  Intermediate Class (III+IV), and Working Class(V+VI+VII) [@sosnaud_class_2013;@edlund_influence_2003].
+As a result, following previous research on political attitudes, a collapsed version of three big classes is employed, including the Service Class (I+II),  Intermediate Class (III+IV), and Working Class (V+VI+VII) [@sosnaud_class_2013;@edlund_influence_2003].
 
 **Class-based network segregation**: To create our measure of network homogeneity based on social class, we employed the position generator available in the questionnaire.
-This instrument has been widely employed in social capital studies, based on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
+This instrument has been widely employed in social capital studies, relying on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
 In this case, the position generator shows a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
@@
 In substantial terms, higher values represent greater social distance from other social classes in society.
+
+As recently suggested, we have selected a set of control variables following substantive reasoning based on the current state of social network and redistributive preferences research [@kohler_control_2024].
+Studies on social capital, network size, and social trust have been included in the estimations.
+The number of social ties or volume in a network can also have implications for instrumental and expressive outcomes such as job prospects or evaluations of self-worth [@contreras_inequality_2019;@kim_social_2021].
+Likewise, social trust has been pointed out as a condition in forming social ties beyond the ingroup, as it means that people can rely on others and engage in supportive networks that may even play a substitute role in welfare provision [@jaime-castillo_social_2016].
+In addition, redistributive preferences can be explained through economic self-interest, with higher-income individuals typically opposing redistribution while recognizing that the reduction of inequality would be at their expense by increasing the tax burden [@meltzer_rational_1981].
+In addition, it has been argued that education provides greater security to cope with the dynamics of the labor market, which results in higher skills being linked to less support for redistribution [@kitschelt_occupations_2014].
+Likewise, job status represents labor market integration, where outsiders are more supportive of redistributive policies due to their willingness to cope with labor market vulnerability [@hausermann_highskilled_2015].
+Finally, it has been argued that besides the self-interest of the unionized working class members, unions also play a role as political socialization agents that seek to nurture egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
+
+Regarding sociodemographic characteristics, prosocial attitudes can be attributed to socialization and cultural norms, with women generally exhibiting a greater capacity for empathy that motivates them to engage in more communal and relational behavior than men [@eagly_his_2009].
+In addition, women tend to be placed in interpersonal service occupations with lower wages and higher market risk than their male counterparts [@waitkus_investigating_2021].
+Substantial differences have also been demonstrated according to the age of individuals, as life cycle stages constitute different degrees of dependence and exposure to risk, and different age cohorts encapsulate different experiences of economic and political shocks.
+[@vanheuvelen_intercohort_2018].
+Concerning religion, evidence has shown that religious individuals support redistribution to a greater extent, as religious communities incentivize uninterested altruistic behavior and prosocial values.
+However, it has also been suggested that religious behavior can decrease support for redistribution as it contributes to individual well-being [@arikan_was_2019].
+Thus, it has been shown that people who do not have a partner tend to be more supportive of redistribution, suggesting that marital ties constitute a support network through which it is possible to mobilize resources and social support [@alesina_preferences_2005].
 
@@
 
-```{r, results='asis'}
+```{r table1, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
               "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class")
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
 
@@
 
-```{r, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class'}
+```{r fig1, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Class-based network homogeneity",y="Redistributive preferences") +
+       x="Network homogeneity",y="Redistributive preferences") +
   theme(legend.position = "none", legend.title = element_blank())
-
 ```
@@
 
-```{r, results='asis'}
+```{r tab2, results='asis', cache=TRUE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
+options(scipen=999)
 if (!require("pacman")) install.packages("pacman")
@@
 ) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2, 
-         gini_disp=gini_disp*100) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit()
+         gini_disp=scale(gini_disp))
 
-# dfreg %>% dplyr::select(gini_disp,rel_red,abs_red,ilo_taxrev,ilo_govspe) %>% tab_corr()
-
-dfreg$wstate1 <- scale(scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-# dfreg$wstate <- scale(dfreg$gv_spen)
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
 
@@
          # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm)
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
   )
@@
 
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
 # drop dummies
 dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
 
@@
          socialtrust_gc+
-         dclass3res_V+dclass3spo_V+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
          female_gc+agenum_gc+age2_gc+partner_gc+
@@
          socialtrust_gc+
-         dclass3res_V+dclass3spo_V+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
@@
               "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP (per capita)",
-              # ilo_taxrev = "Tax revenue (percentage of GDP)",
-              # ilo_govspe = "Government spending (percentage of GDP)",
-              # abs_red = "Redistribution",
-              # wstate1="Size of Welfare State (tax+spend)",
+              loggdppercapita = "GDP/capita",
               wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity x Intermediate Class x Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity x Working Class x Income Inequality")
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
 
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and RedistributivePpreferences",
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
        custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
        float.pos = "h!",
-      # custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
-      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),      
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
        use.packages = F)
@@
 
-```{r, fig.dim=c(12,6),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+```{r fig2, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------
@@
       wstate2=mean(dfreg$wstate2),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc), max(dfreg$homclass3_V_gc), by= 0.1),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
       dclass3res_V=levels(dfreg$dclass3res_V)
@@
 df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-
 df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
@@
   labs(y = "Preferences for Redistribution",
-       x="Class-based network homogeneity (CWC)",
-       # title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality"
+       x="Network homogeneity (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
        ) +
-  # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax)", breaks = NULL, labels = NULL)) +
- # scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
-  # scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
    scale_fill_manual(values=c("#323232","#CCCCCC"))+
   scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position="bottom",
+  theme(legend.position = "bottom",
         legend.direction = "horizontal",

### 2024-03-25 paper1_jiturra.Rmd
descriptive plots

@@
  # install.packages("trackdown")
- trackdown::upload_file(file = "paper1_jiturra.Rmd", hide_code = TRUE,gpath = '001_PhD/002dissertation/paper1')
+ trackdown::update_file(file = "paper1_jiturra.Rmd", hide_code = TRUE,gpath = '001_PhD/002dissertation/paper1')
 
@@
 
-```{r}
+```{r fig1, fig.dim=c(12,5),fig.cap='Bivariate relationships between Income Inequality, Social Class and Network homogeneity',warning=FALSE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
 
-```
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
 
-```{r}
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp),
+         )
+
+homo_ineq <- dfreg %>%
+  # filter(country3 != "ZAF") %>%
+  group_by(country2,country3,dclass3res_V) %>%
+  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+
+homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
+
+homo_ineq$dclass3res_V <- forcats::fct_rev(homo_ineq$dclass3res_V)
+homo_ineq %>%
+ggplot(aes(y=homclass3_V_res, x=gini_disp, group=dclass3res_V,fill=dclass3res_V)) +
+  geom_text(label=as.character(homo_ineq$country),size=3) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = FALSE) +
+  facet_wrap(~dclass3res_V) +
+  xlab("Income Inequality")+
+  ylab("Network homogeneity") +
+  # labs(title = "Class homogeneity and Gini (post-taxes)") +
+  scale_fill_manual(values=c("#CCCCCC","#989898","#323232"))+
+  scale_color_manual(values=c("#CCCCCC","#989898","#323232")) +
+  theme(legend.position = "none",legend.title = element_blank())
 
@@
   egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
   dclass3res_V,
@@
 
-```{r fig1, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
+```{r fig3, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
 
-```{r fig2, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+```{r fig4, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------

### 2024-03-26 paper1_jiturra.Rmd
bonitos plots

@@
 
-```{r fig1, fig.dim=c(12,5),fig.cap='Bivariate relationships between Income Inequality, Social Class and Network homogeneity',warning=FALSE}
+```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country comparison of Redistributive preferences and Social Class ',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
 rm(list=ls())
@@
   "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
   d10d1=wid_p90p10,
@@
   top10=wid_sharetop10,
-  rgdpna,
   gdppercapita,
-  oecd,
   country2, country, country3,
@@
 
+df_mean <- 
+dfreg %>% 
+  group_by(country3) %>% 
+  summarise(egal2_c=mean(egal),homclass_c=mean(homclass3_V_res),gini_disp=mean(gini_disp))
+
+df_region <- 
+dfreg %>% 
+  group_by(region,country3) %>% 
+  summarise(n())
+
+df_full <- 
+dfreg %>% 
+  group_by(dclass3res_V) %>% 
+  summarise(egal2=mean(egal),homclass=mean(homclass3_V_res),homclass_c=mean(dfreg$homclass3_V_res),egal2_c=mean(dfreg$egal), country3="Sample")
+
+df_plot <- 
+dfreg %>% 
+  group_by(country3,dclass3res_V) %>% 
+  summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>% 
+  left_join(df_mean) %>%
+  left_join(df_region) 
+# df_plot <- 
+# df_plot %>% 
+#   bind_rows(df_full)
+
+df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))
+
+df_plot %>% 
+ggplot()+
+  geom_hline(yintercept = mean(dfreg$egal),linetype=2)+
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=dclass3res_V,color=dclass3res_V),size=3, alpha=2) +
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2_c),alpha=1,shape=4,size=2) +
+  scale_shape_manual(values = c(17, 15, 16)) +
+  scale_color_manual(values = c("#000000","#666666","#999999")) +
+  labs(x=NULL,y="Redistributive Preferences") +
+  theme(legend.position = c(0.90, 0.15),
+        axis.text.x=element_text(angle=45,hjust = 1,size=8),
+        legend.title = element_blank())
+
+# df_plot %>%
+# ggplot()+
+#   geom_point(aes(x = reorder(country3, homclass_c),y = homclass,shape=dclass3res_V,color=dclass3res_V),size=3, alpha=2) +
+#   geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
+#   geom_point(aes(x = reorder(country3, homclass_c),y = homclass_c),alpha=1,shape=4,size=2) +
+#   scale_shape_manual(values = c(17, 15, 16)) +
+#   scale_color_manual(values = c("#000000","#666666","#999999")) +
+#   labs(x=NULL,y="Network homogeneity") +
+#   theme(legend.position = c(0.90, 0.1),
+#         axis.text.x=element_text(angle=45,hjust = 1,size=10),
+#         legend.title = element_blank())
+```
+
+```{r fig2, fig.dim=c(10,5),fig.cap='Bivariate relationships between Income Inequality, Network homogeneity and Redistributive preferences',warning=FALSE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp),
+         )
 homo_ineq <- dfreg %>%
-  # filter(country3 != "ZAF") %>%
-  group_by(country2,country3,dclass3res_V) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
+  # filter(country3 != "HUN") %>%
+  group_by(country2,country3) %>%
+  summarise_at(c("homclass3_V_res","egal","gini_disp","d10d1"), mean, na.rm = TRUE) %>% 
   as.data.frame()
 
+# Plot Homogeneity and redistributive preferences
 homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
 
-homo_ineq$dclass3res_V <- forcats::fct_rev(homo_ineq$dclass3res_V)
+fig_egal_homo <- 
 homo_ineq %>%  
-ggplot(aes(y=homclass3_V_res, x=gini_disp, group=dclass3res_V,fill=dclass3res_V)) +
-  geom_text(label=as.character(homo_ineq$country),size=3) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = FALSE) +
-  facet_wrap(~dclass3res_V) +
-  xlab("Income Inequality")+
+ggplot(aes(y=egal, x=homclass3_V_res)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
+                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "A")
+fig_homo_gini<- 
+homo_ineq %>%  
+ggplot(aes(y=homclass3_V_res, x=gini_disp)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  # geom_text() +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Income Inequality") +
   ylab("Network homogeneity") +
-  # labs(title = "Class homogeneity and Gini (post-taxes)") +
-  scale_fill_manual(values=c("#CCCCCC","#989898","#323232"))+
-  scale_color_manual(values=c("#CCCCCC","#989898","#323232")) +
-  theme(legend.position = "none",legend.title = element_blank())
-
+  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
+                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "B")
+grid.arrange(fig_egal_homo,fig_homo_gini, nrow = 1)
 ```
@@
 ```
+
+```{r oldcode2, eval=FALSE, fig.cap='Bivariate relationships between Income Inequality, fig.dim=c(12,5), include=FALSE, Social Class and Network homogeneity',warning=FALSE}
+homo_ineq <- dfreg %>%
+  # filter(country3 != "ZAF") %>%
+  group_by(country2,country3,dclass3res_V) %>%
+  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+
+homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
+homo_ineq$dclass3res_V <- forcats::fct_rev(homo_ineq$dclass3res_V)
+homo_ineq %>%
+ggplot(aes(y=homclass3_V_res, x=gini_disp, group=dclass3res_V,fill=dclass3res_V)) +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = FALSE) +
+  facet_wrap(~dclass3res_V) +
+  xlab("Income Inequality")+
+  ylab("Network homogeneity") +
+  # labs(title = "Class homogeneity and Gini (post-taxes)") +
+  scale_fill_manual(values=c("#CCCCCC","#989898","#323232"))+
+  scale_color_manual(values=c("#CCCCCC","#989898","#323232")) +
+  theme(legend.position = "none",legend.title = element_blank())
+
+```

### 2024-03-27 paper1_jiturra.Rmd
ajustes plots OK

@@
 
-## Data {-}
-
-## Variables {-}
+## Data
+
+Individual data from the International Social Survey Programme (ISSP) 2017, titled "Social Networks and Social Resources," is utilized [@issp_research_group_international_2019].
+Established in 1984, the ISSP is a collaborative research project that conducts cross-national surveys on various topics related to social issues, attitudes, and values.
+Specifically, the ISSP 2017 survey includes questions on social ties and activities, evaluated through a position generator, as well as inquiries on social resources derived from network members.
+Additionally, respondents express their views on topics such as social trust and attitudes toward economic inequality.
+Initially, the dataset comprised 47,027 individual observations across 32 countries.
+However, Slovenia (SVN) was excluded from the analysis because the key dependent variable was not present in the questionnaire.
+Consequently, the present study comprises complete information on 31,191 individuals from 31 countries, representing a diverse range of economic, cultural, and institutional characteristics.
+
+## Variables
 
@@
 Thus, based on previous research and the high degree of correlation between the indicators (_r_ = 0.7), we proceed to reverse-code and create a standardized average index ranging from 1 to 100, where higher values represent greater redistributive preferences [@svallfors_government_2013].
-
-[likertplot]
 
@@
 Subsequently, the occupations were classified into three groups resembling social class positions [@otero_open_2021].
-First, the Lawyer, Executive of a large firm, and Human resource manager are classified as high status.
-Then, a School teacher, Police officer, and Nurse are considered as Intermediate status.
+First, the Lawyer, Executive of a large firm, and Human resource manager are classified as high-status.
+Then, a School teacher, Police officer, and Nurse are considered as intermediate-status.
 Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered as low-status occupations.
@@
 
-As recently suggested, we have selected a set of control variables following substantive reasoning based on the current state of social network and redistributive preferences research [@kohler_control_2024].
-Studies on social capital, network size, and social trust have been included in the estimations.
-The number of social ties or volume in a network can also have implications for instrumental and expressive outcomes such as job prospects or evaluations of self-worth [@contreras_inequality_2019;@kim_social_2021].
-Likewise, social trust has been pointed out as a condition in forming social ties beyond the ingroup, as it means that people can rely on others and engage in supportive networks that may even play a substitute role in welfare provision [@jaime-castillo_social_2016].
-In addition, redistributive preferences can be explained through economic self-interest, with higher-income individuals typically opposing redistribution while recognizing that the reduction of inequality would be at their expense by increasing the tax burden [@meltzer_rational_1981].
-In addition, it has been argued that education provides greater security to cope with the dynamics of the labor market, which results in higher skills being linked to less support for redistribution [@kitschelt_occupations_2014].
-Likewise, job status represents labor market integration, where outsiders are more supportive of redistributive policies due to their willingness to cope with labor market vulnerability [@hausermann_highskilled_2015].
-Finally, it has been argued that besides the self-interest of the unionized working class members, unions also play a role as political socialization agents that seek to nurture egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
-
-Regarding sociodemographic characteristics, prosocial attitudes can be attributed to socialization and cultural norms, with women generally exhibiting a greater capacity for empathy that motivates them to engage in more communal and relational behavior than men [@eagly_his_2009].
-In addition, women tend to be placed in interpersonal service occupations with lower wages and higher market risk than their male counterparts [@waitkus_investigating_2021].
-Substantial differences have also been demonstrated according to the age of individuals, as life cycle stages constitute different degrees of dependence and exposure to risk, and different age cohorts encapsulate different experiences of economic and political shocks.
-[@vanheuvelen_intercohort_2018].
-Concerning religion, evidence has shown that religious individuals support redistribution to a greater extent, as religious communities incentivize uninterested altruistic behavior and prosocial values.
-However, it has also been suggested that religious behavior can decrease support for redistribution as it contributes to individual well-being [@arikan_was_2019].
-Thus, it has been shown that people who do not have a partner tend to be more supportive of redistribution, suggesting that marital ties constitute a support network through which it is possible to mobilize resources and social support [@alesina_preferences_2005].
+As suggested recently, we have selected a set of control variables based on substantive reasoning informed by the current state of research on social networks and redistributive preferences [@kohler_control_2024].
+Our estimations incorporate studies on social capital, network size, and social trust.
+The volume of social ties within a network can have implications for both instrumental and expressive outcomes, such as job prospects or self-worth evaluations [@contreras_inequality_2019; @kim_social_2021].
+Moreover, social trust facilitates the formation of social ties beyond the ingroup, enabling individuals to rely on others and participate in supportive networks that may even serve as substitutes for welfare provision [@jaime-castillo_social_2016].
+Furthermore, redistributive preferences can be elucidated through economic self-interest.
+Typically, individuals with higher incomes oppose redistribution while acknowledging that reducing inequality would entail an increased tax burden [@meltzer_rational_1981].
+Education also plays a crucial role, providing individuals with greater security to navigate the dynamics of the labor market.
+Higher skills are associated with less support for redistribution, as individuals with higher levels of education are better equipped to handle market uncertainties [@kitschelt_occupations_2014].
+Similarly, job status reflects integration into the labor market.
+Outsiders, who are more vulnerable to labor market fluctuations, tend to be more supportive of redistributive policies [@hausermann_highskilled_2015].
+Finally, besides serving the self-interest of unionized working-class members, unions also function as political socialization agents, nurturing egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
+
+Sociodemographic characteristics play a significant role in shaping prosocial attitudes.
+Women, for instance, often demonstrate a greater capacity for empathy, motivating them to engage in more communal and relational behavior compared to men [@eagly_his_2009].
+Moreover, women are frequently employed in interpersonal service occupations characterized by lower wages and higher market risk compared to their male counterparts [@waitkus_investigating_2021].
+Age also emerges as a critical factor, with individuals at different life cycle stages exhibiting varying degrees of dependence and exposure to risk.
+Additionally, different age cohorts encompass distinct experiences of economic and political shocks [@vanheuvelen_intercohort_2018].
+Religion further influences attitudes towards redistribution.
+Religious individuals are generally more supportive of redistribution due to the encouragement of altruistic behavior and prosocial values within religious communities.
+However, there is also evidence suggesting that religious behavior may decrease support for redistribution by contributing to individual well-being [@arikan_was_2019].
+Furthermore, individuals without partners tend to exhibit greater support for redistribution.
+This suggests that marital ties serve as a support network through which individuals can mobilize resources and social support [@alesina_preferences_2005].
 
@@
 
-* Income Inequality (post-taxes): Gini Index from the World Income Inequality Dataset (https://wid.world/)
-
-* Gross Domestic Product per capita (WID, 2022)
-
-* Size of the welfare state [see @edlund_democratic_2015]
-  - Current Redistribution (Solt, 2020)
-  - Tax revenue, as percentage of GDP (ILO)
-  - Welfare expenditure, as percentage of GDP (ILO)
-
-## Method {-}
-
-Multilevel regression models with random and fixed effects. For the cross-level interactions, we include random slopes, and all variables are group-mean centered (CWC)
+The primary societal characteristic under examination is the current levels of economic inequality, for which we have utilized the Gini Index (post-taxes and transfers) sourced from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
+Additionally, two contextual variables have been incorporated as controls in the multilevel models.
+Firstly, economic prosperity has been considered to ensure consistency in the estimates for economic inequality, drawing from the World Income Inequality Dataset (WID) [@Schmidt-Catran2016; @finseraas_income_2009].
+Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state has been included [see @edlund_democratic_2015].
+This measure, as an index, considers three dimensions: (i) tax revenue as a percentage of gross domestic product (GDP) [@ilo_world_2022]; (ii) social spending as a share of GDP [@ilo_world_2022]; and (iii) the current level of redistribution [@solt_measuring_2020].
+
+## Method
+
+Multilevel linear models account for the hierarchical structure of the data, where individuals are nested within countries.
+Therefore, our first analysis begins with estimating the null model by declaring the nested structure using random intercept.
+This initial model allows us to assess the intraclass correlation, revealing that 13.7% of the variance in redistributive preferences can be attributed to belonging to higher-level units (countries).
+Subsequently, the micro-level models are estimated to determine the association between network homogeneity as well as the interaction with social class for testing our _segregation_ hypothesis ($H_1$).
+Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class to determine whether economic inequality moderates the effect of the micro-level interaction ($H_2$).
+Therefore, we estimate a three-way cross-level interaction to determine if the current levels of income inequality affects the interactions between network homogeneity and social class.
+In the macro-level models, all the individual level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
+Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].
 
@@
 rm(list=ls())
-
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
 df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
 dfreg <- df1 %>% dplyr::select(
@@
          age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp),
          )
@@
   summarise(egal2_c=mean(egal),homclass_c=mean(homclass3_V_res),gini_disp=mean(gini_disp))
-
-df_region <- 
-dfreg %>% 
-  group_by(region,country3) %>% 
-  summarise(n())
-
-df_full <- 
-dfreg %>% 
-  group_by(dclass3res_V) %>% 
-  summarise(egal2=mean(egal),homclass=mean(homclass3_V_res),homclass_c=mean(dfreg$homclass3_V_res),egal2_c=mean(dfreg$egal), country3="Sample")
+df_region <- dfreg %>% group_by(region,country3) %>% summarise(n())
+df_full <- dfreg %>% group_by(dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res),homclass_c=mean(dfreg$homclass3_V_res),egal2_c=mean(dfreg$egal), country3="Sample")
+df_plot <- dfreg %>% group_by(country3,dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>%left_join(df_mean) %>% left_join(df_region) 
+df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))
+
+# Calculate the difference between the mean value of working class and upper class within each country
+homo_class_diff <- df_plot %>%
+  dplyr::select(country3,homclass,dclass3res_V) %>% 
+  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass") %>% 
+  mutate(diff_working_upper = `Working Class` - `Service Class`) %>% 
+  dplyr::select(-`Working Class`, -`Service Class`,-`Intermediate Class`) %>% 
+  as.data.frame()
 
@@
   left_join(df_mean) %>%
-  left_join(df_region) 
-# df_plot <- 
-# df_plot %>% 
-#   bind_rows(df_full)
-
-df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))
-
-df_plot %>% 
+  left_join(df_region) %>% as.data.frame() %>% 
+  left_join(homo_class_diff)
+
+df_plot2 <- df_plot
+df_plot2$dclass3res_V <- "Country"
+df_plot2$homclass <- df_plot2$homclass_c
+df_plot2$egal2 <- df_plot2$egal2_c
+
+df_plot3 <- bind_rows(df_plot,df_plot2)
+# table(df_plot3$dclass3res_V)
+df_plot3$dclass3res_V <- factor(df_plot3$dclass3res_V,
+                                levels = c("Country","Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)"),labels = c("Country","Service Class","Intermediate Class","Working Class"))
+
+df_plot3 %>% 
 ggplot()+
   geom_hline(yintercept = mean(dfreg$egal),linetype=2)+
-  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=dclass3res_V,color=dclass3res_V),size=3, alpha=2) +
-  geom_point(aes(x = reorder(country3, egal2_c),y = egal2_c),alpha=1,shape=4,size=2) +
-  scale_shape_manual(values = c(17, 15, 16)) +
-  scale_color_manual(values = c("#000000","#666666","#999999")) +
+  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,
+                 shape=dclass3res_V,
+                 color=dclass3res_V
+                 ),size=3, alpha=2) +
+  scale_shape_manual(values = c(4,17, 15, 16)) +
+  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
   labs(x=NULL,y="Redistributive Preferences") +
-  theme(legend.position = c(0.90, 0.15),
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
         axis.text.x=element_text(angle=45,hjust = 1,size=8),
         legend.title = element_blank())
-
-# df_plot %>%
-# ggplot()+
-#   geom_point(aes(x = reorder(country3, homclass_c),y = homclass,shape=dclass3res_V,color=dclass3res_V),size=3, alpha=2) +
-#   geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
-#   geom_point(aes(x = reorder(country3, homclass_c),y = homclass_c),alpha=1,shape=4,size=2) +
-#   scale_shape_manual(values = c(17, 15, 16)) +
-#   scale_color_manual(values = c("#000000","#666666","#999999")) +
-#   labs(x=NULL,y="Network homogeneity") +
-#   theme(legend.position = c(0.90, 0.1),
-#         axis.text.x=element_text(angle=45,hjust = 1,size=10),
-#         legend.title = element_blank())
-```
-
-```{r fig2, fig.dim=c(10,5),fig.cap='Bivariate relationships between Income Inequality, Network homogeneity and Redistributive preferences',warning=FALSE}
+```
+
+```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country comparison of Network homogeneity and Social Class ',warning=FALSE}
+df_plot3 %>%
+ggplot()+
+  geom_point(aes(x = reorder(country3, diff_working_upper),
+                 y = homclass,
+                 shape=dclass3res_V,
+                 color=dclass3res_V),
+             size=3, alpha=2) +
+  geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
+  scale_shape_manual(values = c(4,17, 15, 16)) +
+  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
+  labs(x=NULL,y="Network homogeneity") +
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text.x=element_text(angle=45,hjust = 1,size=8),
+        legend.title = element_blank()) 
+```
+
+```{r fig3, fig.dim=c(10,5),fig.cap='Bivariate relationships between Income Inequality, Network homogeneity and Redistributive preferences',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-```{r fig3, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
+```{r fig4, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
 
-```{r fig4, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------
@@
 ```
+
+# (APPENDIX) Appendix {-}
+
+[Here Descriptive table]
 

### 2024-03-28 paper1_jiturra.Rmd
descrpitives done

@@
 
+Figure \@ref(fig:fig1) depicts the distribution of redistributive preferences across countries and social classes.
+First, it is possible to notice that the United States has lower redistributive preferences, whereas Russia is a society where redistributive preferences are stronger among all social classes.
+As was expected, in most societies, the working class holds stronger redistributive preferences in contrast to the intermediate and services classes, with four exceptions where the differences are close to zero between both classes.
+However, it is also notable that there are some differences between the two extreme cases.
+For example, in the U.S., the working class held lower redistributive preferences (49.1) than the intermediate class (50.6), but still above the service class (46.8).
+In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated increase in the working (85.5), intermediate (83.5), and service class (83.0).
+Another interesting fact is related to class differences in redistributive preferences.
+For example, the differences between the service and the working class are close to 2.3 points in the United States.
+At the same time, Finland represents the average case in the distribution but is also one of the most polarized societies in terms of class-based differences in redistributive preferences, showing a gap of 14.1 points between the upper and the lower classes.
+Interestingly, Russian society depicts class differences similar to the U.S., with an average difference of 2.4 points.
+
 ```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country comparison of Network homogeneity and Social Class ',warning=FALSE}
@@
 ```
+
+Regarding network segregation, Figure \@ref(fig:fig2) depicts the distribution of network homogeneity and social class across countries.
+In contrast to redistributive preferences, the distribution of network homogeneity is more scattered between countries and social classes.
+However, it is possible to identify at least two compelling findings.
+First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
+Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
+As noticed, in most cases observed, the general pattern is that the working class is highly homogeneous in their networks, except in the Philipines, where the intermediate class shows a slightly higher average homogeneity.
+In addition, the general pattern is that the service class is less segregated than the intermediate and working class.
+Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the middle and service classes are similar in their network homogeneity.
+Overall, one of the most substantial findings is that, with any exception, the working class is more segregated than the services class.
 
@@
 ```
+
+Moving to the bivariate macro relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, our main societal characteristic of interest.
+First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.45, _p_ <.001).
+In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social isolation among the working classes and consequently drive higher redistributive preferences.
+Second, Panel B depicts a positive but relatively weak and nonsignificant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
+In other words, average homogeneity also tends to increase in societies with greater income gaps.
+However, the macro association only shows the general pattern between countries but does not allow us to look deeper into class differences according to the levels of inequality.
+Interestingly, certain countries with higher levels of inequality and network homogeneity are societies that present class differences between the working class and the services class (e.g., Thailand or Mexico).
+By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
+As an additional exploratory analysis, we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderately low and statistically significant (_r_ = 0.29, _p_<.01).
+In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
 
@@
 
-`r if (is_latex_output()) '
-# References {-}
-'`
+# References
+
 ```{=tex}
@@
 
-# (APPENDIX) Appendix {-}
+<div id="refs"> </div>  <!-- Although <div> is an HTML tag, this method also works for other output formats such as PDF. -->
+
+\newpage
+
+`r if (knitr::is_latex_output()){ '\\appendix'}`
+
+`r if (knitr::is_latex_output()){ '\\section{Appendix}'}`
 
 [Here Descriptive table]
+
+```{r figapp1, fig.dim=c(5,5),out.width='50%',fig.cap='Bivariate relationships between Income Inequality and Class differences in network homogeneity',warning=FALSE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp),
+         )
+
+homo_ineq <- dfreg %>%
+  group_by(country2,country3) %>%
+  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+
+homo_class_diff <- dfreg %>%   
+  group_by(country2,country3,dclass3res_V) %>%
+  summarise_at(c("egal","homclass3_V_res"), mean, na.rm = TRUE) %>% 
+  as.data.frame() %>%
+  dplyr::select(country3,homclass3_V_res,dclass3res_V) %>% 
+  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass3_V_res") %>% 
+  mutate(diff_working_upper_homo = `Working Class (V+VI+VII)` - `Service Class (I+II)`) %>% 
+  as.data.frame()
+
+# Dataset with class differences in network homogeneity
+homo_ineq <- homo_ineq %>% left_join(homo_class_diff)
+
+# Plot Homogeneity and redistributive preferences
+homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
+
+fig_homodiff_gini<- 
+homo_ineq %>%  
+ggplot(aes(y=diff_working_upper_homo, x=gini_disp)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  # geom_text() +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Income Inequality") +
+  ylab("Class Differences in Network homogeneity \n (Working Class - Service Class)") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
+                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = NULL)
+
+grid.arrange(fig_homodiff_gini, nrow = 1)
+```
 

### 2024-03-28 paper1_jiturra.Rmd
descripcion tabla1

@@
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = "Multilevel models for Class-based network segregation and Redistributive Preferences",
+       caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
        custom.note = "%stars. Models include sampling weights. Gender, age, marital status and religion are included as controls",
@@
 
-\newpage
+The multilevel analysis results are shown in Table \@ref(tab:table1).
+Regarding our first hypothesis ($H_1$), our central argument is that class segregation has differential consequences on redistributive preferences.
+In other words, the association between network homogeneity and redistributive preferences is conditional on class position.
+
+Model 1 integrates our measure of network homogeneity.
+Initially, as previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
+This association persists in Model 2, where we control for network size and social trust—two pivotal factors in establishing and consolidating interpersonal networks.
+However, after including social class into the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (p<0.10).
+
+Subsequently, Model 4 incorporates socioeconomic status, employment status, and union membership characteristics.
+As expected, socioeconomic status is negatively associated with redistributive preferences regarding household economic resources and educational credentials.
+In addition, we find that people outside the labor market do not differ significantly from those who are economically active in their preferences.
+In contrast, as expected, being unionized increases redistributive preferences compared to those who have never been union members.
+Then, Model 5 incorporates the social class of the respondent's partner if such information is available.
+Thus, it is observed that the social class of the partner follows a similar pattern to that of the respondent, where belonging to the working or intermediate class presents higher redistributive preferences.
+
+Finally, in Model 6, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
+Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
+For the service class, the relationship is reversed, where more homogeneous networks for this social class decrease redistributive preferences.
+Altogether, these results provide evidence of our hypothesis, where a higher level of network segregation is related to a greater polarization of social class interests.
 
@@
 
-```{r oldcode, eval=FALSE, include=FALSE}
-
-# homo_V_gini_gdp_tax <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + ilo_taxrev +
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-# 
-# 
-# homo_V_gini_gdp_govsp <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + ilo_govspe +
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-# 
-# 
-# homo_V_gini_gdp_redis <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + abs_red +
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-# 
-# homo_V_gini_gdp_controls <-
-#   lmer(egal~
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-# 
-# 
-# homo_V_gini_gdp_wstate1 <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + wstate1+
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-# homo_V_gini_full <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
-#          homclass3_V_gc*
-#          dclass3res_V*
-#          gini_disp + 
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-# 
-# homo_V_gini_full1 <- 
-#   lmer(egal~ 
-#          homclass3_V_gc+
-#          know_total_gc+
-#          socialtrust_gc+
-#          dclass3res_V+dclass3spo_V+
-#          female_gc+agenum_gc+age2_gc+
-#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-#          union_gc+workst_gc+
-#          gini_disp +loggdppercapita + wstate1+
-#          homclass3_V_gc*
-#          dclass3res_V*
-#          gini_disp + 
-#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+\pagebreak 
+## Alternative models {-}
+
+```{r tab2-ratio9010, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(d10d1))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/10)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
 ```
 
-```{r oldcode2, eval=FALSE, fig.cap='Bivariate relationships between Income Inequality, fig.dim=c(12,5), include=FALSE, Social Class and Network homogeneity',warning=FALSE}
-homo_ineq <- dfreg %>%
-  # filter(country3 != "ZAF") %>%
-  group_by(country2,country3,dclass3res_V) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-
-homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
-homo_ineq$dclass3res_V <- forcats::fct_rev(homo_ineq$dclass3res_V)
-homo_ineq %>%
-ggplot(aes(y=homclass3_V_res, x=gini_disp, group=dclass3res_V,fill=dclass3res_V)) +
-  geom_text_repel(label=as.character(homo_ineq$country)) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = FALSE) +
-  facet_wrap(~dclass3res_V) +
-  xlab("Income Inequality")+
-  ylab("Network homogeneity") +
-  # labs(title = "Class homogeneity and Gini (post-taxes)") +
-  scale_fill_manual(values=c("#CCCCCC","#989898","#323232"))+
-  scale_color_manual(values=c("#CCCCCC","#989898","#323232")) +
-  theme(legend.position = "none",legend.title = element_blank())
-
+```{r tab2-ratio9050, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(wid_p90p50))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/50)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
 ```
+
+\pagebreak
+
+```{r tab2-ocde, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Network homogeneity (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
+       ) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
+```

### 2024-03-28 paper1_jiturra.Rmd
update headers

@@
 \pagebreak
-## Alternative models {-}
+
+## Inequality Ratios
 
@@
 
+## Alternative: Social Distance
+
+```{r table1-socdist, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res=socdist,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  religion,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
+
+digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
+digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
+                    digclas1_VW_3,
+                    # digclas1_VW_4,
+                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
+       caption = paste("(\\#tab:table2)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
+       custom.note = "%stars. Models include sampling weights. Gender, age, marital status and religion are included as controls",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.60,
+      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+       use.packages = F)
+```
+
+```{r fig4-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
+int_homo <- digclas1_VW_7
+df_pred1 <- 
+  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
+              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 10),
+                                 dclass3res_V = levels(dfreg$dclass3res_V)))
+# names(df_pred1)
+df_pred1 %>% 
+ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=2,color="black") +
+  facet_grid(~factor(dclass3res_V, levels=
+                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
+                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
+  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_y_continuous(limits = c(50,80))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+       x="Network homogeneity",y="Redistributive preferences") +
+  theme(legend.position = "none", legend.title = element_blank())
+```
+
+\pagebreak
+
+```{r tab2-socdist, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res=socdist,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r fig5-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=10),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Network homogeneity (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
+       ) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
+```
+
+\pagebreak
+
+## OECD Countries
+
 ```{r tab2-ocde, results='asis', cache=TRUE}

### 2024-03-28 paper1_jiturra.Rmd
ap

@@
 For example, in the U.S., the working class held lower redistributive preferences (49.1) than the intermediate class (50.6), but still above the service class (46.8).
-In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated increase in the working (85.5), intermediate (83.5), and service class (83.0).
+In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated decrease in the working (85.5), intermediate (83.5), and service class (83.0).
 Another interesting fact is related to class differences in redistributive preferences.
@@
 In contrast to redistributive preferences, the distribution of network homogeneity is more scattered between countries and social classes.
-However, it is possible to identify at least two compelling findings.
+However, it worth to mention at least two interesting findings.
 First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
@@
 Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the middle and service classes are similar in their network homogeneity.
-Overall, one of the most substantial findings is that, with any exception, the working class is more segregated than the services class.
+Overall, one of the most substantial findings is that, without any exception, the working class is more segregated than the services class.
 
@@
 By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
-As an additional exploratory analysis, we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderately low and statistically significant (_r_ = 0.29, _p_<.01).
+As an additional exploratory analysis, we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.29, _p_<.01).
 In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.

### 2024-03-29 paper1_jiturra.Rmd
ajustes tabla descriptiva y resultados macro

@@
        caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
-       custom.note = "%stars. Models include sampling weights. Gender, age, marital status and religion are included as controls",
+       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,
@@
 This association persists in Model 2, where we control for network size and social trust—two pivotal factors in establishing and consolidating interpersonal networks.
-However, after including social class into the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (p<0.10).
+However, after including social class into the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
 
@@
 
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.7,
+       caption = paste("(\\#tab:table2)","Multilevel models for Income Inequality, Network segregation and Redistributive Preferences"),
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,single.row = T,
@@
 
-```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+Table \@ref(tab:table2) presents the results of the multilevel models for income inequality.
+In Model 1, income inequality demonstrates a positive association, as expected, yet it fails to reach significance.
+Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (p > .05).
+Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05) while GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
+In other words, in Model 3, economic prosperity appears to depress redistributive preferences; however, when contextualized within a larger welfare state, greater redistributive preferences are observed.
+
+Finally, Model 4 incorporates the three-way interaction to determine whether the relationship established in $H_1$ is moderated by income inequality.
+The relationship observed at the micro level retains its original meaning, indicating that segregation in terms of network homogeneity polarizes the economic interests of the classes.
+Additionally, when observing how this relationship is moderated by the level of inequality in the country, it appears to mitigate, with its intensity decreasing as inequality increases.
+Figure \@ref(fig:fig5) illustrates how the relationship between network homogeneity and social class is more pronounced when inequality is low and gradually diminishes until it becomes almost absent when inequality is high.
+
+Overall, while Hypothesis 2a posited that greater income differences would amplify social segregation and, consequently, polarize redistributive preferences to a greater extent, the results provide evidence in favor of Hypothesis 2b.
+This suggests that inequality plays a mitigating role in class segregation regarding redistributive preferences.
+
+```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion Income Inequality, Network segregation and  Redistributive Preferences'}
 ### Predicted values homo*class*GiniD ---------------------------------------
@@
 
-[Here Descriptive table]
+```{r descriptive, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  "gini_disp"=wid_gini_disp,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+dfreg <- dfreg %>% dplyr::select(
+  egal,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  dclass3res_V,
+  Q03pcm,
+  edyears,
+  dclass3spo_V,  
+  workst,
+  union,
+  female,
+  agenum,
+  religion,
+  partner,
+  "gini_disp",,
+  loggdppercapita,
+  wstate2
+  )
+
+varlab <- 
+c("Redistributive preferences","Class-based network homogeneity",
+  "Network size","Social trust","Social class",
+  "Household Income","Education in years",
+  "Partner's Social Class","Labor status","Union membership",
+  "Gender","Age in years","Religion","Has partner",
+  "Income Inequality - Gini Index (z-score)",
+  "GDP/capita (z-score)",
+  "Size of the welfare state(z-score)")
+
+sjlabelled::set_label(dfreg) <- varlab
+# names(dfreg) <- varlab
+
+st(dfreg,labels=T,
+   title="Descriptive Statistics for Study Variables",
+   out = "latex",
+   digits = 1, 
+   factor.counts = F,
+   factor.numeric = F,
+   summ = list(
+     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
+     c('notNA(x)','mean(x)')
+   ),
+   summ.names = list(
+     c('N','Mean','SD','Min','Max'),
+     c('Count','Percent')   
+   ))
+
+```
 
@@
        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,single.row = T,
@@
        caption = paste("(\\#tab:table2)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
-       custom.note = "%stars. Models include sampling weights. Gender, age, marital status and religion are included as controls",
+       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,

### 2024-03-29 paper1_jiturra.Rmd
update detalles

@@
 In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated decrease in the working (85.5), intermediate (83.5), and service class (83.0).
+
 Another interesting fact is related to class differences in redistributive preferences.
@@
 However, the macro association only shows the general pattern between countries but does not allow us to look deeper into class differences according to the levels of inequality.
+
 Interestingly, certain countries with higher levels of inequality and network homogeneity are societies that present class differences between the working class and the services class (e.g., Thailand or Mexico).
 By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
-As an additional exploratory analysis, we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.29, _p_<.01).
+As an additional exploratory analysis (see Fig.
+\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.29, _p_<.01).
 In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
        float.pos = "h!",
@@
       custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Country (Intercept)",
+                           "Var: Country Homogeneity",
+                           "Var: Country Intermediate Class ",
+                           "Var: Country Working Class",
+                           "Cov: Country (Intercept), Homogeneity",
+                           "Cov: Country (Intercept), Intermediate Class ",
+                           "Cov: Country (Intercept), Working Class",
+                           "Cov: Country Homogeneity, Intermediate Class",
+                           "Cov: Country Homogeneity, Working Class",
+                           "Cov: Country Intermediate Class, Working Class",
                            "Var: Residual"),
@@
    ))
-
 ```
@@
 \pagebreak 
-
-## Inequality Ratios
+## Income Inequality Ratios
 
@@
 \pagebreak
-
-## Alternative: Social Distance
+## OECD Countries
+
+```{r tab2-ocde, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Network homogeneity (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
+       ) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
+```
+
+\pagebreak
+## Alternatives
 
@@
 ```
-
-\pagebreak
-
-## OECD Countries
-
-```{r tab2-ocde, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```

### 2024-03-29 paper1_jiturra.Rmd
ajuste up

@@
    out = "latex",
-   digits = 1, 
+   digits = 2, 
    factor.counts = F,

### 2024-03-31 paper1_jiturra.Rmd
ya

@@
 In this sense, the tendency to form homophilous social ties in terms of social class reinforces attitudes and consolidates opinion similarity.
-Thus, we hypothesize that segregation in similar class environments polarizes individual class interests so that segregated lower (upper) classes hold more (less) redistributive preferences (H1).
+Thus, we hypothesize that segregation in similar class environments polarizes individual class interests so that segregated lower (upper) classes hold more (less) redistributive preferences ($H_1$).
 
@@
 On the one hand, if we assume that social relations are eroded in more unequal societies, social classes might be more distant due to lower social trust and participation in formal and informal networks.
-Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger (H2a).
+Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger ($H_{2a}$).
 In contrast, if we assume that economic inequality has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness.
 In that case, it might be possible that the working classes are equally segregated regardless of income inequality compared to the more diverse contact and activity networks of the upper classes.
-Likewise, in line with evidence that suggests that the upper classes tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes (H2b).
+Likewise, in line with evidence that suggests that the upper classes tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes ($H_{2b}$).
 
@@
 In the case of the indicator used here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
-On the basis of this, it is possible to obtain the total number of a person's social ties.
+Based on this, it is possible to obtain the total number of a person's social ties.
 Subsequently, the occupations were classified into three groups resembling social class positions [@otero_open_2021].
@@
 Then, a School teacher, Police officer, and Nurse are considered as intermediate-status.
-Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered as low-status occupations.
+Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered low-status occupations.
 
@@
 Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state has been included [see @edlund_democratic_2015].
-This measure, as an index, considers three dimensions: (i) tax revenue as a percentage of gross domestic product (GDP) [@ilo_world_2022]; (ii) social spending as a share of GDP [@ilo_world_2022]; and (iii) the current level of redistribution [@solt_measuring_2020].
+This measure, as an index, considers three dimensions: (i) tax revenue as a percentage of gross domestic product (GDP) [@ilo_world_2022]; (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022]; and (iii) the current level of redistribution [@solt_measuring_2020].
 
@@
 Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class to determine whether economic inequality moderates the effect of the micro-level interaction ($H_2$).
-Therefore, we estimate a three-way cross-level interaction to determine if the current levels of income inequality affects the interactions between network homogeneity and social class.
-In the macro-level models, all the individual level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
+Therefore, we estimate a three-way cross-level interaction to determine if the current levels of income inequality affect the interactions between network homogeneity and social class.
+In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
 Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].
@@
 In contrast to redistributive preferences, the distribution of network homogeneity is more scattered between countries and social classes.
-However, it worth to mention at least two interesting findings.
-First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
+However, it is worth to mention at least two interesting findings.
+First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), with Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
 Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
@@
 This association persists in Model 2, where we control for network size and social trust—two pivotal factors in establishing and consolidating interpersonal networks.
-However, after including social class into the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
+However, after including social class in the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
 
@@
 In Model 1, income inequality demonstrates a positive association, as expected, yet it fails to reach significance.
-Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (p > .05).
+Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (*p* > .05).
 Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05) while GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
@@
 # Discussion and conclusion
+
+<!-- _Dicussion_  Luego de la presentación de los resultados, acá se comienza a volver a los argumentos del trabajo y se relaciona cada hipótesis con los resultados.
+Se sugiere ir por orden, y un párrafo para cada hipótesis.
+-->
+
+La presente investigación buscó responder dos preguntas centrales.
+Primero, ¿cuál es el rol de la class-based network segregation en las redistributive preferences?
+Segundo, ¿juega un rol la desigualdad económica en la relación entre class-based network segregation y las redistributive preferences?
+
+Lo que la evidencia aquí presentada sugiere es que una mayor homogeneidad en términos de clase social tiene un efecto polarizante en las preferencias redistributivas.
+Así, este estudio ha demostrado que la homogeneidad de la red posee implicancias diferenciadas en las preferencias redistributivas según la posición de clase.
+Por un lado, para la clase trabajadora, poseer redes sociales más homogéneas se traduce en mayores preferencias redistributivas.
+En contraste, es posible evidenciar lo opuesto en la clase servicio, en donde redes más homogéneas se traducen en una disminución de las preferencias redistributivas.
+
+En relación a el rol de la desigualdad económica, dos alternativas han sido puestas bajo escrutinio.
+Por un lado, nuestra expectativa era que la relación de nivel micro sería _amplificada_ por una mayor desigualdad economica, dado el incremento de la distancia social entre las clases sociales ($H_{2a}$).
+Por otro lado, hipotetizamos que la desigualdad economica puede _mitigar_ la relación entre segregación y preferenias redistributivias tiende a menguar en tanto aumenta la desigualdad económica ($H_{2b}$).
+En efecto, lo que encontramos es que en la medida que la desigualdad aumenta la relación a nivel micro se va debilitando, lo cual se traduce en una brecha de clase más acotada, principalmente a través de los cambios en las preferencias redistributivas en la clase servicio.
+
+<!-- _conclusion_  -->
+
+Por un lado, nuestra primera hipótesis se fundamenta en la claimed negative influence of the desigualdad económica en la cohesión social.
+
+Por otro lado, las investigaciones sobre desigualdad y preferencias redistributivas han establecido que las personas en la clase alta tiende a volverse más igualitarias en contextos mayor desigualdad económica [@edlund_democratic_2015;@sachweh_why_2019].
+Además, evidencia reciente ha establecido en sociedades más desiguales las personas en posicions más aventajadas tienden a tener mayor diversidad socioeconómica en sus lazos sociales [@otero_differences_2023].
+
+Pueden ser que sus chanches de participar incrementen sus posibilidades de diversidad al tener también mayor confianza - eso hace que también
+
+- network instrument, only a proxy of class positions, mainly the intermediate class positions 
+- measurement of redistributive preferences
+- causal claims and endogeneity problems
 

### 2024-04-03 paper1_jiturra.Rmd
update Konstanz

@@
 lang: en-US
-# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-date: "`r format(Sys.Date(), '%d %b %Y')`"
+date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
+# date: "April 2024"
 author:
 - name: Julio Iturra-Sanhueza
-#   affiliation: University of Bremen
-#   email: jiturra@uni-bremen.de
+  affiliation: Bremen International Graduate School of Social Sciences
+  email: jiturra@uni-bremen.de
 #   number: 1
@@
 # Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
-# abstract: |
-#  The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens.
-However, these consequences have been unevenly experienced across the social structure.
-The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
-Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support.
-Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
-Consequently, inequalities in access to certain social positions (i.e.
-occupations) are translated into a lack of social resources beyond individual economic and cultural capital.
-Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
-Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties.
-To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties.
-The results of multilevel estimations show that being socially segregated increases demand for redistribution.
-Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class.
-At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution.
-However, cross-level interactions do not provide supporting evidence on this behalf.
-#    **Keywords**: network segregation, redistributive preferences, economic inequality 
+abstract: | 
+  | The escalating economic inequality and the current sanitary crisis have threatened social solidarity among citizens.
+However, these consequences have been unevenly experienced across the social structure where the upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
+Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalization and increasing the demand for welfare support.
+Particularly, social resources through network ties have been suggested to have a direct link with an individual's welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
+Consequently, it has been argued that social isolation not only plays a role in terms of social resources, but higher levels of segregation can bolster opinions, suggesting that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
+In this regard, based on the ISSP 2017 -  Social Networks (N=31,191),  multilevel estimations suggest that the influence of network homogeneity is conditional to social class, where the working and intermediate classes with high homogeneous networks hold higher redistributive preferences than the upper classes.
+Additionally, income inequality has been shown to decrease the polarizing effect of network segregation, mainly among the upper classes, when overall inequality is high.
+In sum, this study highlights the role of both social class and network segregation together to understand redistributive preferences, as well as their implications for policies and cohesion.
+  | 
+  | **Keywords**: network segregation, redistributive preferences, economic inequality
 output:
@@
 \pagestyle{fancy}
-\fancyhead[R]{ \thepage}
+\fancyhead[R]{\thepage}
 \fancyhead[L]{Research Article Draft}
 
+\pagebreak 
 # Introduction
@@
 Our research seeks to provide answers to two key questions.
-Firstly, at the micro-level, what is the impact of class-based network segregation on redistributive preferences?
-Secondly, at the macro-level, does economic inequality have a role to play in the relationship between class-based network segregation and redistributive preferences?
-To achieve this, we have analyzed data from the International Social Survey Program (ISSP) 2017, which comprises a sample of over 33,000 individuals across 31 countries globally.
+Firstly, at the micro-level, what is the role of class-based network segregation on redistributive preferences?
+Secondly, at the macro-level, does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
+To achieve this, we have analyzed data from the International Social Survey Program (ISSP) 2017, which comprises a sample of 31,191 individuals across 31 countries globally.
 In this regard, the ISSP has a unique opportunity to date since it includes information on interpersonal networks through the position generator, the core questions for class position allocation, and attitudes toward economic inequality and redistribution.
@@
 
-\newpage
-
 # Discussion and conclusion
@@
 -->
-
-La presente investigación buscó responder dos preguntas centrales.
-Primero, ¿cuál es el rol de la class-based network segregation en las redistributive preferences?
-Segundo, ¿juega un rol la desigualdad económica en la relación entre class-based network segregation y las redistributive preferences?
-
-Lo que la evidencia aquí presentada sugiere es que una mayor homogeneidad en términos de clase social tiene un efecto polarizante en las preferencias redistributivas.
-Así, este estudio ha demostrado que la homogeneidad de la red posee implicancias diferenciadas en las preferencias redistributivas según la posición de clase.
-Por un lado, para la clase trabajadora, poseer redes sociales más homogéneas se traduce en mayores preferencias redistributivas.
-En contraste, es posible evidenciar lo opuesto en la clase servicio, en donde redes más homogéneas se traducen en una disminución de las preferencias redistributivas.
-
-En relación a el rol de la desigualdad económica, dos alternativas han sido puestas bajo escrutinio.
-Por un lado, nuestra expectativa era que la relación de nivel micro sería _amplificada_ por una mayor desigualdad economica, dado el incremento de la distancia social entre las clases sociales ($H_{2a}$).
-Por otro lado, hipotetizamos que la desigualdad economica puede _mitigar_ la relación entre segregación y preferenias redistributivias tiende a menguar en tanto aumenta la desigualdad económica ($H_{2b}$).
-En efecto, lo que encontramos es que en la medida que la desigualdad aumenta la relación a nivel micro se va debilitando, lo cual se traduce en una brecha de clase más acotada, principalmente a través de los cambios en las preferencias redistributivas en la clase servicio.
-
-<!-- _conclusion_  -->
-
-Por un lado, nuestra primera hipótesis se fundamenta en la claimed negative influence of the desigualdad económica en la cohesión social.
-
-Por otro lado, las investigaciones sobre desigualdad y preferencias redistributivas han establecido que las personas en la clase alta tiende a volverse más igualitarias en contextos mayor desigualdad económica [@edlund_democratic_2015;@sachweh_why_2019].
-Además, evidencia reciente ha establecido en sociedades más desiguales las personas en posicions más aventajadas tienden a tener mayor diversidad socioeconómica en sus lazos sociales [@otero_differences_2023].
-
-Pueden ser que sus chanches de participar incrementen sus posibilidades de diversidad al tener también mayor confianza - eso hace que también
-
-- network instrument, only a proxy of class positions, mainly the intermediate class positions 
-- measurement of redistributive preferences
-- causal claims and endogeneity problems
-
+In this research, we ask how class-based network segregation is related to preferences for redistribution and to what extent economic inequality conditions this relationship.
+In this context, the literature on interpersonal networks has shed light on how network structure harbors not only social resources [@lin_access_1986;@otero_open_2021] but also carries the capacity to establish niches that contribute to the formation of political opinions through social influence, as well as the degree of network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
+In this case, the micro-level relationship under scrutiny was that class-based network segregation does play a role in redistributive preferences.
+In contrast to evidence on the undermining role of network homogeneity on social cohesion [@otero_lives_2022], redistributive preferences are not the case.
+Indeed, we found that greater homogeneity in terms of social class has a polarizing effect on redistributive preferences because it has differentiated attitudinal consequences according to class position.
+In other words, for working-class members, homogeneity strengthens their redistributive preferences, while in the service class, homogeneity translates into even lower redistributive preferences.
+
+Our theoretical approach has established that social classes should be understood beyond labor market relationships but as relational networks that can provide an explanatory framework for attitude formation.
+Theoretically, what the literature has established as processes of social influence [@lindh_missing_2021] or political socialization [@lee_consider_2023] has echoed in how social closure in interpersonal networks generates distance between different social classes in terms of their redistributive preferences.
+Here, the extent to which social classes distance themselves in terms of network segregation indeed creates an "empathy gulf" [@sachweh_moral_2012] that can be observed in how the service class is less willing to take action to strive with inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments [@otero_power_2023], in contrast to the increasing redistributive pressures of the marginalized working class.
+Besides, as network homogeneity represents low cross-class ties, it can be argued that lower social integration [@blau_inequality_1977] can undermine social solidarity as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
+
+While the results are substantially consistent at the micro level, our theoretical framework established alternative scenarios regarding the role of economic inequality.
+In short, our competing hypothesis suggested that income inequality, which represents greater gaps in economic and social resources, should be related to class relations and redistributive preferences.
+In line with the social cohesion argument, it is suggested that social relations are undermined by economic inequality as it represents the distribution of available resources and, consequently, might _amplify_ the relationship between segregation and redistributive preferences given the increase in social distance between social classes.
+However, the evidence indicates the opposite as it shows that inequality _mitigates_ the micro-level relationship, which translates into a narrower class gap, mainly through changes in redistributive preferences in the service class.
+These results resonate with two key pieces of evidence on the role of inequality on (i) class relations and (ii) redistributive preferences.
+It has been argued that in unequal societies, the better-off class position tends to become more egalitarian in their stances on economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
+Additionally, recent cross-national studies suggest that upper classes can consolidate their distinctive position while their advantages allow them to navigate diverse networks at the expense of the marginalization of the poor in contexts of greater inequality [@otero_differences_2023].
+
+<!-- _conclusion_-->
+This research is a contribution to the field of study on social class and redistributive preferences, but it also contributes to previous studies that have emphasized the role of social ties in redistributive preferences [@newman_my_2014;@edlund_influence_2003;@langsaether_more_2020].
+In addition to the micro-level contribution, the cross-national component of this research dialogue with previous studies on the role of income inequality on social networks [@pichler_social_2009;@letki_getting_2015;@otero_differences_2023] and class-based research on redistributive preferences [@edlund_democratic_2015;@curtis_how_2015].
+Besides, this research broadly contributes to the ongoing research on social cohesion beyond Western industrialized countries, as our analyses include a heterogeneous group of societies.
+
+In the end, our research has been reached with limitations.
+On the side of our dependent variable, a two-item index is a rough proxy of what we conceptually claim as redistributive preferences.
+It is well established in the literature that the popular responses to economic inequality are diverse regarding how the government strives with economic inequality [@mccall_americans_2009;@garcia-sanchez_two_2022].
+In addition, the position generator included in the ISSP is limited in terms of the capability to reflect the class structure more precisely, mainly regarding the self-employed and the intermediate-class occupations.
+In this regard, we are aware of the limitations of the instrument, and therefore, we present these results with prudence.
+Finally, it has been established that network formation is structured by contact opportunities [@feld_focused_1981], but values-based interaction also play a role in consolidating networks [@visser_attitudes_2004].
+Thus, the cross-sectional nature of our data does not allow us to make causal claims because there could be problems of endogeneity between class position, the composition of social ties, and attitudes.
+
+To summarize, future survey research should consider better measurement strategies for attitudes in the economic domain, such as market-based social services, willingness to pay taxes as redistributive measures, or direct focalized transfers.
+In addition, the network dimension can be better approached with a more detailed measurement strategy incorporating other aspects of the occupational structure, such as authority or autonomy in the labor market.
+Finally, the causality-related issues can be addressed by employing longitudinal designs.
+
+\newpage
 # References

### 2024-04-03 paper1_jiturra.Rmd
Update paper1_jiturra.Rmd

@@
 \newpage
+
 # References
@@
 \pagebreak
-## Alternatives
-
-```{r table1-socdist, results='asis'}
+
+# Social distance
+
+**Social distance**: First, the average ISEI points for each occupation of the position generator are calculated.
+Second, the ISEI of the respondent (R's) is subtracted from the average ISEI points of the personal network.
+For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
+Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance.
+In addition, When the distance is 0, the network is entirely homogeneous.
+
+```{r eval=FALSE, include=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,correlation)
 rm(list=ls())
@@
          edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
+         age2 = agenum ^ 2,
+         homclass3_V_res=homclass3_V_res/10) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+```
+
+## Social Distance by Social Class
+
+```{r table1-socdistclass, echo=FALSE, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res=socdist,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  religion,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2,
+         homclass3_V_res=homclass3_V_res/10) %>%
   # filter(oecd == "OECD") %>%
@@
 
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+ccoef <- list(homclass3_V_res="Social distance",
               know_total="Network size",
@@
               "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class")
 
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table2)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
+       caption = paste("(\\#tab:table2)","Multilevel models for Social distance and Redistributive Preferences"),
        custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
@@
        symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Social distance x Social Class"=15:16),
       custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
@@
 
-```{r fig4-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
+```{r fig1-marg-socdistclass, echo=FALSE, fig.cap='Average Marginal Effects of Social Distance conditionated by Social Class on Redistributive Preferences', fig.dim=c(10,5), warning=FALSE}
+int_homo <- digclas1_VW_7
+plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
+labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+       x="",y="Redistributive preferences")
+```
+
+```{r fig1-pred-socdistclass, echo=FALSE, fig.cap='Linear Predictions for Social distance on Redistributive Preferences by Social Class', fig.dim=c(10,5), warning=FALSE}
 int_homo <- digclas1_VW_7
@@
   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 10),
+              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 1),
                                  dclass3res_V = levels(dfreg$dclass3res_V)))
@@
   scale_y_continuous(limits = c(50,80))+
+  # scale_x_continuous(limits = c(-9,9))+
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Network homogeneity",y="Redistributive preferences") +
+       x="Social Distance",y="Redistributive preferences") +
   theme(legend.position = "none", legend.title = element_blank())
@@
 
-```{r tab2-socdist, results='asis', cache=TRUE}
+```{r tab2-socdistclass, echo=FALSE, cache=TRUE, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
          age2 = agenum ^ 2,
-         gini_disp=scale(gini_disp))
+         gini_disp=scale(gini_disp),
+         homclass3_V_res=homclass3_V_res/10)
 
@@
 
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+ccoef <- list(homclass3_V_gc="Social distance (CWC)",
               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
@@
               wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class",
               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Distance*Working Class*Income Inequality")
 
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance x Social Class"=7:8, "Distance * Social Class x Income Inequality"=10:11),
        float.pos = "h!",
@@
 
-```{r fig5-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+```{r fig5-socdistclass, echo=FALSE, fig.cap='hree-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
 ### Predicted values homo*class*GiniD ---------------------------------------
@@
       loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=10),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5),
       dclass3res_V=levels(dfreg$dclass3res_V)
@@
   labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
+       x="Social Distance (CWC)",
        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
@@
 ```
+
+\pagebreak
+
+## Social Distance by ISEI
+
+```{r table1-socdist, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dummy_df <- df1 %>% dplyr::select(id,
+  egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust,
+  Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region,
+  "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
+  ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita,
+  oecd,country2, country, country3) %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+  dplyr::select(id)
+
+df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
+df1$isei08 <- car::recode(df1$isei08,"NA=0")
+
+dfreg <- df1 %>% dplyr::select(id,
+  egal = egal2,
+  dclass3res_V=isei08,
+  dclass3spo_V=isei08sp,
+  homclass3_V_res=socdist,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  religion,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2,
+         dclass3res_V=dclass3res_V/10,
+         dclass3spo_V=dclass3spo_V/10,
+         homclass3_V_res=homclass3_V_res/10) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")  %>% 
+  filter(id %in% dummy_df$id)
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
+
+digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
+digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
+                    digclas1_VW_3,
+                    # digclas1_VW_4,
+                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
+
+ccoef <- list(homclass3_V_res="Social Distance /10",
+              know_total="Network size",
+              socialtrust="Social Trust",
+              # "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              # "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "dclass3res_V"="ISEI/10",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              "dclass3spo_V" = "ISEI/10 (Partner)",
+              "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI")
+
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
+       caption = paste("(\\#tab:table2)","Multilevel models for Social Distance and Redistributive Preferences"),
+       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.60,
+      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+       use.packages = F)
+```
+
+```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE}
+int_homo <- digclas1_VW_7
+plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V" = "threenum"))+
+labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+       x="ISEI",y="Redistributive preferences")
+```
+
+```{r fig1-pred-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Social Distance on Redistributive Preferences by ISEI',warning=FALSE}
+int_homo <- digclas1_VW_7
+df_pred1 <- 
+  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
+              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.5),
+                                 dclass3res_V = c(min(dfreg$dclass3res_V),mean(dfreg$dclass3res_V),max(dfreg$dclass3res_V))))
+
+df_pred1$dclass3res_V <- factor(df_pred1$dclass3res_V,labels = c("ISEI (min)","ISEI (Mean)", "ISEI (max)"))
+
+# names(df_pred1)
+df_pred1 %>% 
+ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=2,color="black") +
+  # facet_grid(~dclass3res_V) +
+  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
+  scale_y_continuous(limits = c(40,100))+
+  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+       x="Social distance",y="Redistributive preferences") +
+  theme(legend.position = "bottom", legend.title = element_blank())
+```
+
+\pagebreak
+
+```{r tab2-socdist, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+dummy_df <- df1 %>% dplyr::select(id,
+  egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust,
+  Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region,
+  "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
+  ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita,
+  oecd,country2, country, country3) %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+  dplyr::select(id)
+
+df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
+dfreg <- df1 %>% dplyr::select(id,
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V=isei08,
+  dclass3spo_V=isei08sp,
+  homclass3_V_res=socdist,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp),
+         dclass3res_V=dclass3res_V/10,
+         dclass3spo_V=dclass3spo_V/10,
+         homclass3_V_res=homclass3_V_res/10)
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+dfreg$dclass3res_V = group_center(as.numeric(dfreg$dclass3res_V), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         dclass3spo_V_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         dclass3spo_V_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         dclass3spo_V_gc+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         dclass3spo_V_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         dclass3spo_V_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Social Distance (CWC)",
+              "dclass3res_V"="ISEI ",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_V" = "Distance*ISEI",
+              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
+              "dclass3res_V:gini_disp" ="ISEI*Inequality",
+              "homclass3_V_gc:dclass3res_V:gini_disp" = "Distance*Working Class*Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance*Social Class"=7:8, "Distance * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Soc. Distance",
+                           "Var: Group ISEI",
+                           "Cov: Group (Intercept), Soc. Distance",
+                           "Cov: Group (Intercept), ISEI",                           
+                           "Cov: Group Soc. Distance, ISEI",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5),
+      dclass3res_V=c(min(dfreg$dclass3res_V),max(dfreg$dclass3res_V))
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+
+df_pred_giniD_gc$dclass3res_V <- factor(df_pred_giniD_gc$dclass3res_V,labels = c("ISEI (min)","ISEI (max)"))
+# df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc$dclass3res_V <- as.factor(df_pred_giniD_gc$dclass3res_V)
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Social Distance (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
+       ) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
+```

### 2024-04-03 paper1_jiturra.Rmd
update paper

@@
 lang: en-US
-date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-# date: "April 2024"
+# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
+date: "`r format(Sys.Date(), '%d %B %Y')`"
 author:
@@
 
-Individual data from the International Social Survey Programme (ISSP) 2017, titled "Social Networks and Social Resources," is utilized [@issp_research_group_international_2019].
+Individual data from the International Social Survey Programme (ISSP) 2017, titled "Social Networks and Social Resources," is utilized [@issp_networks_2017].
 Established in 1984, the ISSP is a collaborative research project that conducts cross-national surveys on various topics related to social issues, attitudes, and values.
@@
 However, Slovenia (SVN) was excluded from the analysis because the key dependent variable was not present in the questionnaire.
-Consequently, the present study comprises complete information on 31,191 individuals from 31 countries, representing a diverse range of economic, cultural, and institutional characteristics.
+Consequently, the present study comprises complete information on 31,191 individuals from 31 countries, representing a group of diverse societies in terms of socio-economic and institutional arrangements.
 
@@
 \pagebreak 
+# Additional analysis
+
 ## Income Inequality Ratios
@@
 
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
@@
 
-# Social distance
-
-**Social distance**: First, the average ISEI points for each occupation of the position generator are calculated.
-Second, the ISEI of the respondent (R's) is subtracted from the average ISEI points of the personal network.
+## Social distance
+
+First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_three_2003] for each occupation of the position generator are calculated.
+Second, the ISEI score of the respondent (R's) is subtracted from the average ISEI points of the personal network.
 For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
@@
 In addition, When the distance is 0, the network is entirely homogeneous.
+
+To facilitate the interpretation of the indicator, we have calculated a homogeneity indicator based on social distance:
+
+1. The absolute values are calculated to represent the total distance to occupations respect to R's ISEI score.
+2. Since we have 0 values representing absolute homogeneity, we rescale the variable by adding 1.
+4. We have inverted the values to make higher values represent higher homogeneity.
+
+Thus, higher values represent greater homogeneity regarding R's ISEI score in contrast to the average network ISEI score.
 
@@
 
-## Social Distance by Social Class
+### Social Distance by Social Class
 
@@
   filter(country2 != "SVN")
-
 dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
@@
 dfreg <- na.omit(dfreg)
+
+# Step 1: Calculate absolute values
+absolute_values <- abs(dfreg$homclass3_V_res)
+# hist(absolute_values);summary(absolute_values)
+
+# Step 2: Add 1 to all values to eliminate zeros
+modified_values <- absolute_values + 0.1
+# hist(modified_values);summary(modified_values)
+
+# Step 3: Reverse the order of the scale
+reversed_values <- max(modified_values) + 0.1 - modified_values
+# hist(reversed_values);summary(reversed_values)
+
+dfreg$homclass3_V_res <- reversed_values
 
@@
 labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="",y="Redistributive preferences")
+       x="Social Distance",y="Redistributive preferences")
 ```
@@
 
+# Step 1: Calculate absolute values
+absolute_values <- abs(dfreg$homclass3_V_res)
+# hist(absolute_values);summary(absolute_values)
+
+# Step 2: Add 1 to all values to eliminate zeros
+modified_values <- absolute_values + 0.1
+# hist(modified_values);summary(modified_values)
+
+# Step 3: Reverse the order of the scale
+reversed_values <- max(modified_values) + 0.1 - modified_values
+# hist(reversed_values);summary(reversed_values)
+
+dfreg$homclass3_V_res <- reversed_values
+
 # Variable Group-Centering ------------------------------------------------
@@
               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality",
@@
 
-## Social Distance by ISEI
+### Social Distance by ISEI
 
@@
   filter(country2 != "SVN") %>% 
+  # filter(oecd == "OECD") %>%
   na.omit() %>% 
@@
 
+# Step 1: Calculate absolute values
+absolute_values <- abs(dfreg$homclass3_V_res)
+# hist(absolute_values);summary(absolute_values)
+
+# Step 2: Add 1 to all values to eliminate zeros
+modified_values <- absolute_values + 0.1
+# hist(modified_values);summary(modified_values)
+
+# Step 3: Reverse the order of the scale
+reversed_values <- max(modified_values) + 0.1 - modified_values
+# hist(reversed_values);summary(reversed_values) 
+dfreg$homclass3_V_res <- reversed_values
+
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
@@
 
+\newpage
+
 ```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE}
@@
 
-# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
 dummy_df <- df1 %>% dplyr::select(id,
@@
          dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10)
+         homclass3_V_res=homclass3_V_res/10) %>% 
+  filter(id %in% dummy_df$id)
 
 dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+# Step 1: Calculate absolute values
+absolute_values <- abs(dfreg$homclass3_V_res)
+# hist(absolute_values);summary(absolute_values)
+
+# Step 2: Add 1 to all values to eliminate zeros
+modified_values <- absolute_values + 0.1
+# hist(modified_values);summary(modified_values)
+
+# Step 3: Reverse the order of the scale
+reversed_values <- max(modified_values) + 0.1 - modified_values
+# hist(reversed_values);summary(reversed_values)
+
+dfreg$homclass3_V_res <- reversed_values
 
@@
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       caption = "Multilevel models for Income Inequality, Social Distance and Redistributive Preferences",
        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",

### 2024-04-03 paper1_jiturra_supp-material.Rmd
update paper

--- 2024-04-03 paper1_jiturra.Rmd
@@
 title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
+subtitle: "Supplementary material"
 css: "input/css/custom.css" # custom CSS para html
@@
 # Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
-abstract: | 
-  | The escalating economic inequality and the current sanitary crisis have threatened social solidarity among citizens.
+# abstract: | 
+#   # | The escalating economic inequality and the current sanitary crisis have threatened social solidarity among citizens.
 However, these consequences have been unevenly experienced across the social structure where the upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
@@
 In sum, this study highlights the role of both social class and network segregation together to understand redistributive preferences, as well as their implications for policies and cohesion.
-  | 
-  | **Keywords**: network segregation, redistributive preferences, economic inequality
+#   # | 
+#   # | **Keywords**: network segregation, redistributive preferences, economic inequality
 output:
@@
  # clean #in the yml
- rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::pdf_document2")
- rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
- rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
+ rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::pdf_document2")
+ rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::html_document2")
+ rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::word_document2")
 
@@
 
-\pagebreak 
-# Introduction
-
-Rising economic inequality over the past decades [@piketty_capital_2014] and the recent sanitary crisis have raised citizens' concerns about economic inequality, pushing governments to enact redistributive policies, which has tested the capacity of welfare systems to provide sufficient risk protection for their citizens [@breznau_welfare_2021].
-However, the privileged access to resources held by the upper and intermediate classes has consolidated their resilience capacity in times of greater economic hardship, allowing them to maintain a relatively stable standard of living, in contrast to the decline in the material conditions of working-class families [@moawad_myth_2023].
-In this regard, it has been claimed that economic gaps in economic resources also have a greater effect on social relations.
-Studies on the role of economic inequality have argued that social bonding can be threatened when economic inequality increases, undermines how people perceive each other, their opportunities to participate in social life, and the capacity to knit networks that contribute to social integration [@lancee_income_2012;@letki_getting_2015].
-Therefore, experiencing segregated networks is one of the consequences of greater economic gaps as it represents greater distance between the different social classes  [@pichler_patterns_2007;@otero_space_2022].
-In this regard, it has been argued that segregation can threaten social cohesion and solidarity [@joye_measuring_2019], which in turn can undermine public support for welfare schemes and redistribution [@baldassarri_diversity_2020].
-
-The sociological tradition has understood social classes through the labor market situation of occupations in terms of employment relations, skill level, and authority within the workplace [@Erikson1992;@Erikson1979].
-Likewise, classes represent relations in the labor market and trace lines in terms of status relations as the foundations for opportunities for action and the consolidation of lifestyles [@weber_economy_1978].
-In this matter, the class situation of individuals and households also trace distinctions in various domains of social life, such as cultural consumption behavior [@Chan2007;@torche_social_2007], ideological preferences [@evans_decline_1993], and popular opinions about the welfare state and redistribution [@Svallfors2006].
-Regarding the latter, despite the claims of a displacement of the distributive struggle between classes by other group identities [@clark_declining_1993;@inglehart_culture_1990], past decade research has persistently demonstrated that class positions indeed still explain economic attitudes towards the welfare state and redistribution [@lindh_class_2020, p.
-421].
-Thus, the claimed blurring of the class cleavage has not been strongly supported while the class differences have been evidenced in perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes on market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-
-However, the study of redistributive preferences has been mainly focused on the individual and household situation.
-In contrast, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
-In this regard, how people form their friendship and partnership ties tends to be homogeneous because of the tendency towards homophily in forming interpersonal networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-Hereby, we argue that the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes.
-In this regard, recent research has argued that the degree of segregation in the composition of social ties is a window for learning about others' lifestyles, economic conditions, and worldviews [@mijs_inequality_2018;@otero_power_2023].
-However, there has been no systematic dialogue regarding the role of social ties on preferences for redistribution from a social network perspective.
-Therefore, this research aims to contribute to the ongoing literature on class-based network segregation on attitudes toward redistribution [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-
-While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention must be devoted to understanding the role of social environments in class relations.
-This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
-In addition, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-This research aims to contribute to the literature on preferences toward redistribution from a relational perspective, focusing on how the structural properties of networks can influence people's preferences toward economic redistribution.
-
-Our research seeks to provide answers to two key questions.
-Firstly, at the micro-level, what is the role of class-based network segregation on redistributive preferences?
-Secondly, at the macro-level, does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
-To achieve this, we have analyzed data from the International Social Survey Program (ISSP) 2017, which comprises a sample of 31,191 individuals across 31 countries globally.
-In this regard, the ISSP has a unique opportunity to date since it includes information on interpersonal networks through the position generator, the core questions for class position allocation, and attitudes toward economic inequality and redistribution.
-
-# Theoretical views on class, social networks, and redistributive preferences
-
-## Class relations and social networks
-
-As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
-In principle, social stratification scholars have traditionally considered differentiation as observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
-Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] that trace friendship and family ties, such as age and gender, as well as segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
-In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of worldviews, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
-Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
-From this perspective, we argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
-
-How classes are formed also provides insight into social relations and sociability practices.
-In sociology, classes are understood as the basis for action given their labor market situation, which ultimately shapes their access to opportunities and resources [@weber_economy_1978].
-According to the habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
-From this approach, classes seek to improve their positions through the intergenerational transmission of resources, where similarities in friendship and family choices play a crucial role in reproducing privileged social positions.
-Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding lower classes [@bourdieu_reproduccion_1981].
-Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring the intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
-Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, where access to resources embedded in social networks follows a pattern of accumulation that ultimately leads to social segregation in both the upper and lower bounds of the social structure.
-
-Previous research on social class and tie formation has suggested that class permeability in social networks, understood as the formation of cross-class social ties, can be traced differently across property and authority boundaries.
-Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is significantly less likely, in contrast to the tendency of higher tie formation between supervisors and manual workers.
-This suggests that the property dimension is much less permeable than authority-based boundaries, given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
-Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social isolation, whereas the upper class is less permeable and homogenous because of its tendency to self-select as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
-
-By contrast, cross-class embeddedness can be described in terms of social activities, generational changes, and the life course.
-In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in civic engagement behavior.
-Similarly, other studies in Europe and South America have shown that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile helps to improve both dimensions in tie formation [@cepic_how_2020;@carrascosa_class_2023].
-Nevertheless, it does not equalize the weight of the class background compared with those that are intergenerationally stable in the upper class.
-Additionally, the little longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions, while the lower class shows more stability across the life course [@volker_social_2020].
-
-Altogether, these studies account for class-based network segregation, as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
-Drawing on this approach, stratification scholars have focused on how social connections are distributed across class structure as a matter of social integration [@blau_macrosociological_1977].
-In addition, homogeneity is described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions.
-Simultaneously, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
-Hence, both approaches provide alternatives for studying social class from a network perspective, which has been increasingly discussed in the stratification literature and scholarly discussion about social class and political attitudes.
-
-## Network segregation and attitudes toward redistribution
-
-Besides from the individual approach to attitude formation, we argue that people also form opinions in the economic domain based on their social relations.
-Despite limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
-
-On the one hand, one approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form opinions about redistributive policies [@condon_economic_2020].
-This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@kelley_class_1995].
-Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers’ experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
-467].
-From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information that ultimately shapes their perceptions of inequality [@mijs_is_2021].
-Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more isolated discussion networks [@summers_deliberating_2022].
-Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [e.g.
-@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [e.g.
-@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
-
-In contrast, it has been suggested that the lens of a network approach provides a better picture of class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
-550].
-This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to individual or household material well-being, cultural perspectives, and political preferences that structure broader social experiences [@morris_attenuation_1996, p.
-48].
-Furthermore, social integration can be affected in societies with lower contact opportunities between different social classes, where social distance among them widened by extreme inequality can create an “empathy gulf” that comprises barriers to imagining others’ lifestyles [@sachweh_moral_2012].
-In this matter, spatially segregated interactions may nurture doubts about worthiness when the lower classes contrast themselves with the lifestyles of the upper classes, which might undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
-Consequently, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
-758].
-Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties, where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
-
-In recent years, we have seen an increase in this network turn of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
-In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interacting with those of the upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
-Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images of the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
-
-In addition, studies that directly addressed the relationship between networks and social classes have been consistent with previous findings.
-For instance, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively influence support for redistribution, while ties to the working class increase it regardless of the individual class position suggesting that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
-698].
-Similarly, additional socialization sources are cross-class ties through family members.
-In this sense, the family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
-A study in the United States showed that those tied to the upper class through parental relations support redistribution and progressive taxation less than those with working-class family backgrounds [@lee_consider_2023].
-In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties polarizes preferences between lower and upper classes.
-In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
-
-In summary, we argue that class-embedded social relations play a substantial role in shaping support for redistribution.
-In this sense, the tendency to form homophilous social ties in terms of social class reinforces attitudes and consolidates opinion similarity.
-Thus, we hypothesize that segregation in similar class environments polarizes individual class interests so that segregated lower (upper) classes hold more (less) redistributive preferences ($H_1$).
-
-##  Consequences of Economic Inequality on Social Networks and Redistributive Preferences
-
-### Consequences of Economic Inequality on Social Networks
-
-The consequences of inequality in social relationships are diverse.
-Theoretically, it has been stated that economic inequality deepens material and symbolic differences between members of a society, where those in the most favored positions generally become more distant from those with access to fewer resources.
-Consequently, lower resources can constrain or discourage people from actively participating in social life, ultimately affecting the chances of meeting others with different economic conditions and lifestyles [@neckerman_inequality_2007, p.
-344].
-In this discussion, one approach has stressed the role of subjective experiences of inequality in social relations, arguing that a broader gap in economic resources has consequences on perceived competition and status anxiety [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024].
-Therefore, driving stronger experiences of relative deprivation undermines trust in others, given the difficulties of setting shared goals and perceiving others as part of a collectivity that pursues the common good [@salgado_expectations_2021].
-In contrast, the neo-materialist approach sets the attention on resource availability and attributes much less importance to subjective experiences, arguing that more economically equal societies are also characterized by extended welfare institutions that seek to diminish the consequences of unequal access to resources that provide better conditions for people to be socially engaged by improving social trust and individual well-being [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
-In sum, living in more unequal societies goes hand in hand with more extraordinary experiences of uncertainty, which at the same time may be hindered by a lack of trust in the broader social context, affecting the motives to participate in social activities that play a fundamental role in establishing ties between dissimilar groups, either by status or social class [@lancee_diversity_2017].
-
-Empirically, the few studies on this subject share the assumption that economic inequality translates into social distance in terms of class and status positions, which is the basis for consolidating network segregation.
-Cross-national comparisons in Europe show that the patterns of participation and association in formal organizations, as well as those of informal networks in providing social support, are manifested in the form of complementarity or substitution according to the cultural relevance of family or friendship networks and the character of the welfare regime [@pichler_patterns_2007].
-By contrast, @pichler_social_2009 accounts for the role of income inequality on participation in formal and informal networks, showing that more unequal societies depress the extensiveness of formal participation but not the frequency.
-In addition, it is one of the few studies that show how, in more unequal societies, class differences in participation are deepened in the diversity of formal participation networks.
-Similarly, @lancee_income_2012 shows that economic inequality reduces participation.
-However, in formal networks, the inhibiting effect of inequality is better evidenced, being less relevant to participation in informal networks.
-In addition, they show that in more unequal societies, the stratification of participation by income level is strengthened, favoring those with greater resources and marginalizing the poorest.
-
-In contrast to studies on participation in formal and informal networks, recent research has emphasized economic inequality in the structure of interpersonal networks.
-For instance, @letki_getting_2015 argued that economic inequality may constrain access to more extensive networks and the chances of receiving support through them.
-First, they found that individuals in lower-income groups have smaller networks than those in wealthier groups and are less likely to access resources through them.
-However, as inequality increases, low-income individuals hold much more extensive family networks but are less inclined towards utilizing their social ties to access resources than middle- and higher-income groups.
-They suggest that "the poor see maintaining ties with a large extended family as crucial for accessing needed help, which they are unlikely to reach through non-kinship ties" [@letki_getting_2015, p.
-244].
-By contrast, @otero_differences_2023 found that income inequality is not directly associated with the network structure.
-However, they found that income inequality can enhance the relationship between educational level, occupational status, and the diversity of social ties.
-They suggest that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
-Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and isolation because of the choices of others [@otero_open_2021, p.24].
-In this regard, if we assume that economic inequality sets the conditions for sociability, a possible consequence may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality is also affected by the extent of income differences.
-
-### Consequences of Economic Inequality on Redistributive Preferences
-
-As mentioned, economic inequality influences social relations overall or strengthens inequalities throughout the social structure.
-However, studies on redistributive preferences have provided mixed evidence of the direct impact of income inequality on support for redistribution [@evans_strong_2018;@trump_income_2023].
-In turn, an open discussion has been raised regarding why those in the upper social strata are more sensitive to changes in economic inequality than those in the lower strata.
-
-Theoretically, two approaches were considered in this discussion.
-On the one hand, some studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that, although the rational interest model maintains its general implications, there are nuances within the upper-income strata regarding their greater concerns about the negative externalities of economic inequality (e.g., crime), which ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Additionally, another body of literature has suggested that the differences among the affluent can be understood from a distributive justice framework that focuses on the justice evaluation under which economic resources are allocated [@liebig_sociology_2016].
-The central argument suggests that affluent groups are more sensitive to economic inequality changes as they perceive that the overall opportunity structure is affected.
-In contrast, low-income individuals tend to perceive that the ascribed characteristics are stronger in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
-656].
-Likewise, it has been argued that perceived inequality of opportunity can motivate support for redistribution as a matter of justice in the conditions for getting ahead, showing that this is particularly present in individuals in higher socioeconomic positions [@kim_socioeconomic_2018].
-Therefore, if the degree of segregation in social networks is related to polarization in redistributive attitudes, we believe that income inequality might also play a role in the relationship between class relations and redistributive attitudes.
-
-Empirically, while an important part of the studies addressing the role of economic inequality and redistribution preferences has focused on income, it is also possible to find efforts that emphasize the role of social class.
-In the first case, comparative studies in various societies have demonstrated (1) the relevance of income position and (2) the sensitivity of high-income groups to material inequality [@Schmidt-Catran2016; @franetovic_preferences_2022; @finseraas_income_2009].
-However, class-based studies have contributed equally to the elucidation of this relationship.
-For example, @edlund_democratic_2015 established that the demand for state-organized redistribution reflects the level of political class conflict in a modern industrialized society.
-Thus, their argument suggests that inequality plays a key role in moderating these conflicts because there is evidence of greater political consensus supporting redistribution in societies with greater material inequality.
-They emphasize that social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
-323].
-
-Similarly, @curtis_how_2015 suggest two possible implications for the class cleavage in redistributive preferences in contexts of rising economic inequality.
-One argument suggests that the decline in social cohesion expressed in trust, civic participation, and prosocial attitudes might undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
-As a result, less cohesive societies can nurture stronger class polarization that undermines egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
-In contrast, the other argument posits that in the context of greater economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
-66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
-Additionally, it has been suggested that the degree of perceived social conflict decreases in societies with lower material inequality and a predominant middle-class imaginery [@hertel_conflict_2022].
-Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class.
-
-To summarize, the current state of research has led us to establish two competing scenarios based on the reviewed evidence and theoretical assumptions regarding the role of economic inequality in the relationship between class-based segregation and redistributive preferences.
-On the one hand, if we assume that social relations are eroded in more unequal societies, social classes might be more distant due to lower social trust and participation in formal and informal networks.
-Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger ($H_{2a}$).
-In contrast, if we assume that economic inequality has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness.
-In that case, it might be possible that the working classes are equally segregated regardless of income inequality compared to the more diverse contact and activity networks of the upper classes.
-Likewise, in line with evidence that suggests that the upper classes tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes ($H_{2b}$).
-
-# Data, variables and method
-
-## Data
-
-Individual data from the International Social Survey Programme (ISSP) 2017, titled "Social Networks and Social Resources," is utilized [@issp_networks_2017].
-Established in 1984, the ISSP is a collaborative research project that conducts cross-national surveys on various topics related to social issues, attitudes, and values.
-Specifically, the ISSP 2017 survey includes questions on social ties and activities, evaluated through a position generator, as well as inquiries on social resources derived from network members.
-Additionally, respondents express their views on topics such as social trust and attitudes toward economic inequality.
-Initially, the dataset comprised 47,027 individual observations across 32 countries.
-However, Slovenia (SVN) was excluded from the analysis because the key dependent variable was not present in the questionnaire.
-Consequently, the present study comprises complete information on 31,191 individuals from 31 countries, representing a group of diverse societies in terms of socio-economic and institutional arrangements.
-
-## Variables
-
-### _Individual level_ {-}
-
-**Redistributive preferences**: Two indicators available in the questionnaire were used to measure redistributive preferences.
-First, support for government redistribution (1) is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and the egalitarian preferences represented by the item (2) 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
-Thus, based on previous research and the high degree of correlation between the indicators (_r_ = 0.7), we proceed to reverse-code and create a standardized average index ranging from 1 to 100, where higher values represent greater redistributive preferences [@svallfors_government_2013].
-
-**Social class**:  The Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme is employed [@Erikson1992;@Erikson1979], one of the most consistent and validated measure for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
-Thus, based on the recently developed DIGCLASS algorithm, we draw on the available information regarding (i) occupations, (ii) self-employment status and (iii) the number of workers [@cimentada_digclass_2023].
-As a result, following previous research on political attitudes, a collapsed version of three big classes is employed, including the Service Class (I+II),  Intermediate Class (III+IV), and Working Class (V+VI+VII) [@sosnaud_class_2013;@edlund_influence_2003].
-
-**Class-based network segregation**: To create our measure of network homogeneity based on social class, we employed the position generator available in the questionnaire.
-This instrument has been widely employed in social capital studies, relying on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
-In this case, the position generator shows a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
-In the case of the indicator used here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
-Based on this, it is possible to obtain the total number of a person's social ties.
-Subsequently, the occupations were classified into three groups resembling social class positions [@otero_open_2021].
-First, the Lawyer, Executive of a large firm, and Human resource manager are classified as high-status.
-Then, a School teacher, Police officer, and Nurse are considered as intermediate-status.
-Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered low-status occupations.
-
-After this, we calculated the number of social ties for each status group.
-Consequently, the group closer to their class position obtains a proxy of the number of ingroup social ties.
-Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
-Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are similar (homogeneity).
-In substantial terms, higher values represent greater social distance from other social classes in society.
-
-As suggested recently, we have selected a set of control variables based on substantive reasoning informed by the current state of research on social networks and redistributive preferences [@kohler_control_2024].
-Our estimations incorporate studies on social capital, network size, and social trust.
-The volume of social ties within a network can have implications for both instrumental and expressive outcomes, such as job prospects or self-worth evaluations [@contreras_inequality_2019; @kim_social_2021].
-Moreover, social trust facilitates the formation of social ties beyond the ingroup, enabling individuals to rely on others and participate in supportive networks that may even serve as substitutes for welfare provision [@jaime-castillo_social_2016].
-Furthermore, redistributive preferences can be elucidated through economic self-interest.
-Typically, individuals with higher incomes oppose redistribution while acknowledging that reducing inequality would entail an increased tax burden [@meltzer_rational_1981].
-Education also plays a crucial role, providing individuals with greater security to navigate the dynamics of the labor market.
-Higher skills are associated with less support for redistribution, as individuals with higher levels of education are better equipped to handle market uncertainties [@kitschelt_occupations_2014].
-Similarly, job status reflects integration into the labor market.
-Outsiders, who are more vulnerable to labor market fluctuations, tend to be more supportive of redistributive policies [@hausermann_highskilled_2015].
-Finally, besides serving the self-interest of unionized working-class members, unions also function as political socialization agents, nurturing egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
-
-Sociodemographic characteristics play a significant role in shaping prosocial attitudes.
-Women, for instance, often demonstrate a greater capacity for empathy, motivating them to engage in more communal and relational behavior compared to men [@eagly_his_2009].
-Moreover, women are frequently employed in interpersonal service occupations characterized by lower wages and higher market risk compared to their male counterparts [@waitkus_investigating_2021].
-Age also emerges as a critical factor, with individuals at different life cycle stages exhibiting varying degrees of dependence and exposure to risk.
-Additionally, different age cohorts encompass distinct experiences of economic and political shocks [@vanheuvelen_intercohort_2018].
-Religion further influences attitudes towards redistribution.
-Religious individuals are generally more supportive of redistribution due to the encouragement of altruistic behavior and prosocial values within religious communities.
-However, there is also evidence suggesting that religious behavior may decrease support for redistribution by contributing to individual well-being [@arikan_was_2019].
-Furthermore, individuals without partners tend to exhibit greater support for redistribution.
-This suggests that marital ties serve as a support network through which individuals can mobilize resources and social support [@alesina_preferences_2005].
-
-### _Macro level_ {-}
-
-The primary societal characteristic under examination is the current levels of economic inequality, for which we have utilized the Gini Index (post-taxes and transfers) sourced from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
-Additionally, two contextual variables have been incorporated as controls in the multilevel models.
-Firstly, economic prosperity has been considered to ensure consistency in the estimates for economic inequality, drawing from the World Income Inequality Dataset (WID) [@Schmidt-Catran2016; @finseraas_income_2009].
-Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state has been included [see @edlund_democratic_2015].
-This measure, as an index, considers three dimensions: (i) tax revenue as a percentage of gross domestic product (GDP) [@ilo_world_2022]; (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022]; and (iii) the current level of redistribution [@solt_measuring_2020].
-
-## Method
-
-Multilevel linear models account for the hierarchical structure of the data, where individuals are nested within countries.
-Therefore, our first analysis begins with estimating the null model by declaring the nested structure using random intercept.
-This initial model allows us to assess the intraclass correlation, revealing that 13.7% of the variance in redistributive preferences can be attributed to belonging to higher-level units (countries).
-Subsequently, the micro-level models are estimated to determine the association between network homogeneity as well as the interaction with social class for testing our _segregation_ hypothesis ($H_1$).
-Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class to determine whether economic inequality moderates the effect of the micro-level interaction ($H_2$).
-Therefore, we estimate a three-way cross-level interaction to determine if the current levels of income inequality affect the interactions between network homogeneity and social class.
-In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
-Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].
-
-# Results
-
-## Descriptive
-
-```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country comparison of Redistributive preferences and Social Class ',warning=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         )
-
-df_mean <- 
-dfreg %>% 
-  group_by(country3) %>% 
-  summarise(egal2_c=mean(egal),homclass_c=mean(homclass3_V_res),gini_disp=mean(gini_disp))
-df_region <- dfreg %>% group_by(region,country3) %>% summarise(n())
-df_full <- dfreg %>% group_by(dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res),homclass_c=mean(dfreg$homclass3_V_res),egal2_c=mean(dfreg$egal), country3="Sample")
-df_plot <- dfreg %>% group_by(country3,dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>%left_join(df_mean) %>% left_join(df_region) 
-df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))
-
-# Calculate the difference between the mean value of working class and upper class within each country
-homo_class_diff <- df_plot %>%
-  dplyr::select(country3,homclass,dclass3res_V) %>% 
-  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass") %>% 
-  mutate(diff_working_upper = `Working Class` - `Service Class`) %>% 
-  dplyr::select(-`Working Class`, -`Service Class`,-`Intermediate Class`) %>% 
-  as.data.frame()
-
-df_plot <- 
-dfreg %>% 
-  group_by(country3,dclass3res_V) %>% 
-  summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>% 
-  left_join(df_mean) %>%
-  left_join(df_region) %>% as.data.frame() %>% 
-  left_join(homo_class_diff)
-
-df_plot2 <- df_plot
-df_plot2$dclass3res_V <- "Country"
-df_plot2$homclass <- df_plot2$homclass_c
-df_plot2$egal2 <- df_plot2$egal2_c
-
-df_plot3 <- bind_rows(df_plot,df_plot2)
-# table(df_plot3$dclass3res_V)
-df_plot3$dclass3res_V <- factor(df_plot3$dclass3res_V,
-                                levels = c("Country","Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)"),labels = c("Country","Service Class","Intermediate Class","Working Class"))
-
-df_plot3 %>% 
-ggplot()+
-  geom_hline(yintercept = mean(dfreg$egal),linetype=2)+
-  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,
-                 shape=dclass3res_V,
-                 color=dclass3res_V
-                 ),size=3, alpha=2) +
-  scale_shape_manual(values = c(4,17, 15, 16)) +
-  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Redistributive Preferences") +
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text.x=element_text(angle=45,hjust = 1,size=8),
-        legend.title = element_blank())
-```
-
-Figure \@ref(fig:fig1) depicts the distribution of redistributive preferences across countries and social classes.
-First, it is possible to notice that the United States has lower redistributive preferences, whereas Russia is a society where redistributive preferences are stronger among all social classes.
-As was expected, in most societies, the working class holds stronger redistributive preferences in contrast to the intermediate and services classes, with four exceptions where the differences are close to zero between both classes.
-However, it is also notable that there are some differences between the two extreme cases.
-For example, in the U.S., the working class held lower redistributive preferences (49.1) than the intermediate class (50.6), but still above the service class (46.8).
-In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated decrease in the working (85.5), intermediate (83.5), and service class (83.0).
-
-Another interesting fact is related to class differences in redistributive preferences.
-For example, the differences between the service and the working class are close to 2.3 points in the United States.
-At the same time, Finland represents the average case in the distribution but is also one of the most polarized societies in terms of class-based differences in redistributive preferences, showing a gap of 14.1 points between the upper and the lower classes.
-Interestingly, Russian society depicts class differences similar to the U.S., with an average difference of 2.4 points.
-
-```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country comparison of Network homogeneity and Social Class ',warning=FALSE}
-df_plot3 %>%
-ggplot()+
-  geom_point(aes(x = reorder(country3, diff_working_upper),
-                 y = homclass,
-                 shape=dclass3res_V,
-                 color=dclass3res_V),
-             size=3, alpha=2) +
-  geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
-  scale_shape_manual(values = c(4,17, 15, 16)) +
-  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Network homogeneity") +
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text.x=element_text(angle=45,hjust = 1,size=8),
-        legend.title = element_blank()) 
-```
-
-Regarding network segregation, Figure \@ref(fig:fig2) depicts the distribution of network homogeneity and social class across countries.
-In contrast to redistributive preferences, the distribution of network homogeneity is more scattered between countries and social classes.
-However, it is worth to mention at least two interesting findings.
-First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), with Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
-Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
-As noticed, in most cases observed, the general pattern is that the working class is highly homogeneous in their networks, except in the Philipines, where the intermediate class shows a slightly higher average homogeneity.
-In addition, the general pattern is that the service class is less segregated than the intermediate and working class.
-Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the middle and service classes are similar in their network homogeneity.
-Overall, one of the most substantial findings is that, without any exception, the working class is more segregated than the services class.
-
-```{r fig3, fig.dim=c(10,5),fig.cap='Bivariate relationships between Income Inequality, Network homogeneity and Redistributive preferences',warning=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp),
-         )
-homo_ineq <- dfreg %>%
-  # filter(country3 != "HUN") %>%
-  group_by(country2,country3) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp","d10d1"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-
-# Plot Homogeneity and redistributive preferences
-homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
-
-fig_egal_homo <- 
-homo_ineq %>%  
-ggplot(aes(y=egal, x=homclass3_V_res)) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
-  geom_text_repel(label=as.character(homo_ineq$country)) +
-  xlab("Network homogeneity")+
-  ylab("Redistributive preferences") +
-  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
-                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "A")
-fig_homo_gini<- 
-homo_ineq %>%  
-ggplot(aes(y=homclass3_V_res, x=gini_disp)) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
-  # geom_text() +
-  geom_text_repel(label=as.character(homo_ineq$country)) +
-  xlab("Income Inequality") +
-  ylab("Network homogeneity") +
-  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
-                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "B")
-grid.arrange(fig_egal_homo,fig_homo_gini, nrow = 1)
-```
-
-Moving to the bivariate macro relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, our main societal characteristic of interest.
-First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.45, _p_ <.001).
-In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social isolation among the working classes and consequently drive higher redistributive preferences.
-Second, Panel B depicts a positive but relatively weak and nonsignificant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
-In other words, average homogeneity also tends to increase in societies with greater income gaps.
-However, the macro association only shows the general pattern between countries but does not allow us to look deeper into class differences according to the levels of inequality.
-
-Interestingly, certain countries with higher levels of inequality and network homogeneity are societies that present class differences between the working class and the services class (e.g., Thailand or Mexico).
-By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
-As an additional exploratory analysis (see Fig.
-\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.29, _p_<.01).
-In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
-
-## Multivariate results
-
-```{r table1, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
-digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
-                    digclas1_VW_3,
-                    # digclas1_VW_4,
-                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
-
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
-              know_total="Network size",
-              socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
-
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
-      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-       use.packages = F)
-```
-
-The multilevel analysis results are shown in Table \@ref(tab:table1).
-Regarding our first hypothesis ($H_1$), our central argument is that class segregation has differential consequences on redistributive preferences.
-In other words, the association between network homogeneity and redistributive preferences is conditional on class position.
-
-Model 1 integrates our measure of network homogeneity.
-Initially, as previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
-This association persists in Model 2, where we control for network size and social trust—two pivotal factors in establishing and consolidating interpersonal networks.
-However, after including social class in the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
-
-Subsequently, Model 4 incorporates socioeconomic status, employment status, and union membership characteristics.
-As expected, socioeconomic status is negatively associated with redistributive preferences regarding household economic resources and educational credentials.
-In addition, we find that people outside the labor market do not differ significantly from those who are economically active in their preferences.
-In contrast, as expected, being unionized increases redistributive preferences compared to those who have never been union members.
-Then, Model 5 incorporates the social class of the respondent's partner if such information is available.
-Thus, it is observed that the social class of the partner follows a similar pattern to that of the respondent, where belonging to the working or intermediate class presents higher redistributive preferences.
-
-Finally, in Model 6, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
-Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
-For the service class, the relationship is reversed, where more homogeneous networks for this social class decrease redistributive preferences.
-Altogether, these results provide evidence of our hypothesis, where a higher level of network segregation is related to a greater polarization of social class interests.
-
-```{r fig4, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
-int_homo <- digclas1_VW_7
-df_pred1 <- 
-  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.1),
-                                 dclass3res_V = levels(dfreg$dclass3res_V)))
-# names(df_pred1)
-df_pred1 %>% 
-ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=2,color="black") +
-  facet_grid(~factor(dclass3res_V, levels=
-                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
-                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
-  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(50,80))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Network homogeneity",y="Redistributive preferences") +
-  theme(legend.position = "none", legend.title = element_blank())
-```
-
 \newpage
 
-```{r tab2, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.7,
-       caption = paste("(\\#tab:table2)","Multilevel models for Income Inequality, Network segregation and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Country (Intercept)",
-                           "Var: Country Homogeneity",
-                           "Var: Country Intermediate Class ",
-                           "Var: Country Working Class",
-                           "Cov: Country (Intercept), Homogeneity",
-                           "Cov: Country (Intercept), Intermediate Class ",
-                           "Cov: Country (Intercept), Working Class",
-                           "Cov: Country Homogeneity, Intermediate Class",
-                           "Cov: Country Homogeneity, Working Class",
-                           "Cov: Country Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-Table \@ref(tab:table2) presents the results of the multilevel models for income inequality.
-In Model 1, income inequality demonstrates a positive association, as expected, yet it fails to reach significance.
-Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (*p* > .05).
-Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05) while GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
-In other words, in Model 3, economic prosperity appears to depress redistributive preferences; however, when contextualized within a larger welfare state, greater redistributive preferences are observed.
-
-Finally, Model 4 incorporates the three-way interaction to determine whether the relationship established in $H_1$ is moderated by income inequality.
-The relationship observed at the micro level retains its original meaning, indicating that segregation in terms of network homogeneity polarizes the economic interests of the classes.
-Additionally, when observing how this relationship is moderated by the level of inequality in the country, it appears to mitigate, with its intensity decreasing as inequality increases.
-Figure \@ref(fig:fig5) illustrates how the relationship between network homogeneity and social class is more pronounced when inequality is low and gradually diminishes until it becomes almost absent when inequality is high.
-
-Overall, while Hypothesis 2a posited that greater income differences would amplify social segregation and, consequently, polarize redistributive preferences to a greater extent, the results provide evidence in favor of Hypothesis 2b.
-This suggests that inequality plays a mitigating role in class segregation regarding redistributive preferences.
-
-```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion Income Inequality, Network segregation and  Redistributive Preferences'}
-### Predicted values homo*class*GiniD ---------------------------------------
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-# Discussion and conclusion
-
-<!-- _Dicussion_  Luego de la presentación de los resultados, acá se comienza a volver a los argumentos del trabajo y se relaciona cada hipótesis con los resultados.
-Se sugiere ir por orden, y un párrafo para cada hipótesis.
--->
-In this research, we ask how class-based network segregation is related to preferences for redistribution and to what extent economic inequality conditions this relationship.
-In this context, the literature on interpersonal networks has shed light on how network structure harbors not only social resources [@lin_access_1986;@otero_open_2021] but also carries the capacity to establish niches that contribute to the formation of political opinions through social influence, as well as the degree of network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
-In this case, the micro-level relationship under scrutiny was that class-based network segregation does play a role in redistributive preferences.
-In contrast to evidence on the undermining role of network homogeneity on social cohesion [@otero_lives_2022], redistributive preferences are not the case.
-Indeed, we found that greater homogeneity in terms of social class has a polarizing effect on redistributive preferences because it has differentiated attitudinal consequences according to class position.
-In other words, for working-class members, homogeneity strengthens their redistributive preferences, while in the service class, homogeneity translates into even lower redistributive preferences.
-
-Our theoretical approach has established that social classes should be understood beyond labor market relationships but as relational networks that can provide an explanatory framework for attitude formation.
-Theoretically, what the literature has established as processes of social influence [@lindh_missing_2021] or political socialization [@lee_consider_2023] has echoed in how social closure in interpersonal networks generates distance between different social classes in terms of their redistributive preferences.
-Here, the extent to which social classes distance themselves in terms of network segregation indeed creates an "empathy gulf" [@sachweh_moral_2012] that can be observed in how the service class is less willing to take action to strive with inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments [@otero_power_2023], in contrast to the increasing redistributive pressures of the marginalized working class.
-Besides, as network homogeneity represents low cross-class ties, it can be argued that lower social integration [@blau_inequality_1977] can undermine social solidarity as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
-
-While the results are substantially consistent at the micro level, our theoretical framework established alternative scenarios regarding the role of economic inequality.
-In short, our competing hypothesis suggested that income inequality, which represents greater gaps in economic and social resources, should be related to class relations and redistributive preferences.
-In line with the social cohesion argument, it is suggested that social relations are undermined by economic inequality as it represents the distribution of available resources and, consequently, might _amplify_ the relationship between segregation and redistributive preferences given the increase in social distance between social classes.
-However, the evidence indicates the opposite as it shows that inequality _mitigates_ the micro-level relationship, which translates into a narrower class gap, mainly through changes in redistributive preferences in the service class.
-These results resonate with two key pieces of evidence on the role of inequality on (i) class relations and (ii) redistributive preferences.
-It has been argued that in unequal societies, the better-off class position tends to become more egalitarian in their stances on economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
-Additionally, recent cross-national studies suggest that upper classes can consolidate their distinctive position while their advantages allow them to navigate diverse networks at the expense of the marginalization of the poor in contexts of greater inequality [@otero_differences_2023].
-
-<!-- _conclusion_-->
-This research is a contribution to the field of study on social class and redistributive preferences, but it also contributes to previous studies that have emphasized the role of social ties in redistributive preferences [@newman_my_2014;@edlund_influence_2003;@langsaether_more_2020].
-In addition to the micro-level contribution, the cross-national component of this research dialogue with previous studies on the role of income inequality on social networks [@pichler_social_2009;@letki_getting_2015;@otero_differences_2023] and class-based research on redistributive preferences [@edlund_democratic_2015;@curtis_how_2015].
-Besides, this research broadly contributes to the ongoing research on social cohesion beyond Western industrialized countries, as our analyses include a heterogeneous group of societies.
-
-In the end, our research has been reached with limitations.
-On the side of our dependent variable, a two-item index is a rough proxy of what we conceptually claim as redistributive preferences.
-It is well established in the literature that the popular responses to economic inequality are diverse regarding how the government strives with economic inequality [@mccall_americans_2009;@garcia-sanchez_two_2022].
-In addition, the position generator included in the ISSP is limited in terms of the capability to reflect the class structure more precisely, mainly regarding the self-employed and the intermediate-class occupations.
-In this regard, we are aware of the limitations of the instrument, and therefore, we present these results with prudence.
-Finally, it has been established that network formation is structured by contact opportunities [@feld_focused_1981], but values-based interaction also play a role in consolidating networks [@visser_attitudes_2004].
-Thus, the cross-sectional nature of our data does not allow us to make causal claims because there could be problems of endogeneity between class position, the composition of social ties, and attitudes.
-
-To summarize, future survey research should consider better measurement strategies for attitudes in the economic domain, such as market-based social services, willingness to pay taxes as redistributive measures, or direct focalized transfers.
-In addition, the network dimension can be better approached with a more detailed measurement strategy incorporating other aspects of the occupational structure, such as authority or autonomy in the labor market.
-Finally, the causality-related issues can be addressed by employing longitudinal designs.
-
-\newpage
-
-# References
-
-```{=tex}
-\scriptsize
-\singlespacing
-```
-
-<div id="refs"> </div>  <!-- Although <div> is an HTML tag, this method also works for other output formats such as PDF. -->
-
-\newpage
-
 `r if (knitr::is_latex_output()){ '\\appendix'}`
@@
 `r if (knitr::is_latex_output()){ '\\section{Appendix}'}`
-
-```{r descriptive, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  "gini_disp"=wid_gini_disp,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-dfreg <- dfreg %>% dplyr::select(
-  egal,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  dclass3res_V,
-  Q03pcm,
-  edyears,
-  dclass3spo_V,  
-  workst,
-  union,
-  female,
-  agenum,
-  religion,
-  partner,
-  "gini_disp",,
-  loggdppercapita,
-  wstate2
-  )
-
-varlab <- 
-c("Redistributive preferences","Class-based network homogeneity",
-  "Network size","Social trust","Social class",
-  "Household Income","Education in years",
-  "Partner's Social Class","Labor status","Union membership",
-  "Gender","Age in years","Religion","Has partner",
-  "Income Inequality - Gini Index (z-score)",
-  "GDP/capita (z-score)",
-  "Size of the welfare state(z-score)")
-
-sjlabelled::set_label(dfreg) <- varlab
-# names(dfreg) <- varlab
-
-st(dfreg,labels=T,
-   title="Descriptive Statistics for Study Variables",
-   out = "latex",
-   digits = 2, 
-   factor.counts = F,
-   factor.numeric = F,
-   summ = list(
-     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
-     c('notNA(x)','mean(x)')
-   ),
-   summ.names = list(
-     c('N','Mean','SD','Min','Max'),
-     c('Count','Percent')   
-   ))
-```
-
-```{r figapp1, fig.dim=c(5,5),out.width='50%',fig.cap='Bivariate relationships between Income Inequality and Class differences in network homogeneity',warning=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp),
-         )
-
-homo_ineq <- dfreg %>%
-  group_by(country2,country3) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-
-homo_class_diff <- dfreg %>%   
-  group_by(country2,country3,dclass3res_V) %>%
-  summarise_at(c("egal","homclass3_V_res"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  dplyr::select(country3,homclass3_V_res,dclass3res_V) %>% 
-  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass3_V_res") %>% 
-  mutate(diff_working_upper_homo = `Working Class (V+VI+VII)` - `Service Class (I+II)`) %>% 
-  as.data.frame()
-
-# Dataset with class differences in network homogeneity
-homo_ineq <- homo_ineq %>% left_join(homo_class_diff)
-
-# Plot Homogeneity and redistributive preferences
-homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
-
-fig_homodiff_gini<- 
-homo_ineq %>%  
-ggplot(aes(y=diff_working_upper_homo, x=gini_disp)) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
-  # geom_text() +
-  geom_text_repel(label=as.character(homo_ineq$country)) +
-  xlab("Income Inequality") +
-  ylab("Class Differences in Network homogeneity \n (Working Class - Service Class)") +
-  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
-                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = NULL)
-
-grid.arrange(fig_homodiff_gini, nrow = 1)
-```
 
@@
 
-## Income Inequality Ratios
-
-```{r tab2-ratio9010, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(d10d1))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/10)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r tab2-ratio9050, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(wid_p90p50))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/50)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-\pagebreak
 ## OECD Countries
@@
 rm(list=ls())
-
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
@@
 
+## Income Inequality Ratios (OECD)
+
+```{r tab2-ratio9010, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(d10d1))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/10)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r tab2-ratio9050, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(wid_p90p50))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------
+         to_dummy(Q03pcm),
+         to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         socialtrust_gc+
+         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         union_gc+workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/50)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
 \pagebreak
 
-## Social distance
-
-First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_three_2003] for each occupation of the position generator are calculated.
-Second, the ISEI score of the respondent (R's) is subtracted from the average ISEI points of the personal network.
+## Social distance (OECD)
+
+**Social distance**: First, the average ISEI points for each occupation of the position generator are calculated.
+Second, the ISEI of the respondent (R's) is subtracted from the average ISEI points of the personal network.
 For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
@@
 In addition, When the distance is 0, the network is entirely homogeneous.
-
-To facilitate the interpretation of the indicator, we have calculated a homogeneity indicator based on social distance:
-
-1. The absolute values are calculated to represent the total distance to occupations respect to R's ISEI score.
-2. Since we have 0 values representing absolute homogeneity, we rescale the variable by adding 1.
-4. We have inverted the values to make higher values represent higher homogeneity.
-
-Thus, higher values represent greater homogeneity regarding R's ISEI score in contrast to the average network ISEI score.
 
@@
          homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN")
@@
          homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN")
+
 dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values)
-
-dfreg$homclass3_V_res <- reversed_values
 
@@
   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(50,80))+
+  scale_y_continuous(limits = c(50,100))+
   # scale_x_continuous(limits = c(-9,9))+
@@
 ) %>%
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN") %>%
@@
 dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
 # Step 1: Calculate absolute values
@@
   filter(country2 != "SVN") %>% 
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   na.omit() %>% 
@@
          homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN")  %>% 
@@
 dfreg <- na.omit(dfreg)
-
 # Step 1: Calculate absolute values
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values) 
-dfreg$homclass3_V_res <- reversed_values
 
@@
 
-\newpage
-
 ```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE}
@@
 ) %>%
-  # filter(oecd == "OECD") %>%
+  filter(oecd == "OECD") %>%
   filter(country2 != "SVN") %>% 
@@
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Social Distance and Redistributive Preferences",
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",

### 2024-04-03 paper1_jiturra_supp-material.Rmd
supplementary material

@@
 if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
-pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
 knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
@@
 options(knitr.kable.NA = '') # NA en kable = ''
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
 ```
@@
 \fancyhead[R]{\thepage}
-\fancyhead[L]{Research Article Draft}
-
-\newpage
-
-`r if (knitr::is_latex_output()){ '\\appendix'}`
-
-`r if (knitr::is_latex_output()){ '\\section{Appendix}'}`
+\fancyhead[L]{Supplementary material}
 
@@
 
-**Social distance**: First, the average ISEI points for each occupation of the position generator are calculated.
-Second, the ISEI of the respondent (R's) is subtracted from the average ISEI points of the personal network.
-For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
-Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance.
-In addition, When the distance is 0, the network is entirely homogeneous.
-
 ```{r eval=FALSE, include=FALSE}
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
+dfreg$homclass3_V_res <- reversed_values
 
@@
 
-```{r fig5-socdistclass, echo=FALSE, fig.cap='hree-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
+```{r fig5-socdistclass, echo=FALSE, fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
 ### Predicted values homo*class*GiniD ---------------------------------------
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
+
+dfreg$homclass3_V_res <- reversed_values
 

### 2024-04-04 paper1_jiturra.Rmd
slides

@@
         legend.title = element_blank())
+
+# ggsave(plot = last_plot(),filename = "slides-macro-redist.png",device = "png",
+#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
         legend.title = element_blank())
+
+# ggsave(plot = last_plot(),filename = "slides-macro-homogen.png",device = "png",
+#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
 grid.arrange(fig_egal_homo,fig_homo_gini, nrow = 1)
+
+# ggsave(plot = arrangeGrob(fig_egal_homo,fig_homo_gini, nrow = 1),filename = "slides-bivar.png",device = "png",
+#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
 
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
        caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
@@
        float.pos = "h!",
+      # file = "table1.html"
        use.packages = F)
@@
   theme(legend.position = "none", legend.title = element_blank())
+
+# ggsave(plot = last_plot(),filename = "slides-predictions.png",device = "png",
+#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+
+# int_homo <- digclas1_VW_7
+# plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
+# labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+#   geom_hline(yintercept = 0,color="red",linetype=2)+
+#        x="Social Class",y="Redistributive preferences",title = "Conditional Marginal Effects for Network Homogeneity")
+
+# ggsave(plot = last_plot(),filename = "slides-marginal.png",device = "png",
+#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 10)
 ```
@@
                            "Var: Residual"),
+        # file = "table2.html",
        use.packages = F)
@@
         legend.box.background = element_rect(colour = "black"))
+
+ggsave(plot = last_plot(),filename = "slides-predict-macro.png",device = "png",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
 ```
@@
   dclass3spo_V,
-  homclass3_V_res,
+  # homclass3_V_res,
   know_total,
@@
 grid.arrange(fig_homodiff_gini, nrow = 1)
+
+# ggsave(plot = arrangeGrob(fig_homodiff_gini, nrow = 1),filename = "slides-bivar-homodiff.png",device = "png",
+#        path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
 ```
@@
 plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
+  geom_hline(yintercept = 0,color="red",linetype=2)+
 labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),

### 2024-04-14 procesamiento/01-prod_prep-micro.Rmd
up

@@
 
+df1 <- df1 %>% group_by(country) %>% mutate(prop_high_mean=mean(pct_high,na.rm = T))
+df1 <- df1 %>% group_by(country) %>% mutate(prop_midd_mean=mean(pct_middle,na.rm = T))
+df1 <- df1 %>% group_by(country) %>% mutate(prop_low_mean=mean(pct_low,na.rm = T))
+
+summary(df1$prop_high_mean);hist.default(df1$prop_high_mean,breaks = 30)
+summary(df1$prop_midd_mean);hist.default(df1$prop_midd_mean,breaks =30)
+summary(df1$prop_low_mean);hist.default(df1$prop_low_mean,breaks =30)
+
+df1$pct_high_wt <-df1$n_high*df1$prop_high_mean 
+summary(df1$pct_high_wt);hist.default(df1$pct_high_wt,breaks = 30)
+df1[,c("n_high","prop_high_mean","pct_high_wt")]
+
+df1$pct_midd_wt <- df1$n_middle*df1$prop_midd_mean
+summary(df1$pct_midd_wt);hist.default(df1$pct_midd_wt,breaks = 30)
+df1[,c("n_middle","prop_midd_mean","pct_midd_wt")]
+
+df1$pct_low_wt  <- df1$n_low*df1$prop_low_mean
+summary(df1$pct_low_wt);hist.default(df1$pct_low_wt,breaks = 30)
+df1[,c("n_middle","prop_midd_mean","pct_midd_wt")]
+
 ```
@@
 sjlabelled::set_label(df1$homclass3_V_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res)
+
+## Using RESPONDENT Class for homogeneity (WEIGHTED) ---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res_V,pct_high_wt,pct_midd_wt,pct_low_wt,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",df1$pct_high_wt,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",df1$pct_midd_wt,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",df1$pct_low_wt,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res_V,pct_high_wt,pct_midd_wt,pct_low_wt,ingroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",rowSums(df1[,c("pct_low_wt","pct_midd_wt")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("pct_low_wt","pct_high_wt")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("pct_midd_wt","pct_high_wt")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$know_total_wt <- rowSums(df1[,c("pct_low_wt","pct_midd_wt","pct_high_wt")],na.rm = T)
+df1$homclass3_V_res_wt <- as.numeric(df1$ingroup_res/df1$know_total_wt)
+sjlabelled::set_label(df1$homclass3_V_res_wt) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate - Weighted)";frq(df1$homclass3_V_res_wt)
+
 ```

### 2024-04-15 paper1_jiturra.Rmd
up
Update paper1_jiturra.Rmd

@@
 ```
-
-### Social Distance by Social Class
-
-```{r table1-socdistclass, echo=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values)
-
-dfreg$homclass3_V_res <- reversed_values
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
-digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
-                    digclas1_VW_3,
-                    # digclas1_VW_4,
-                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
-
-ccoef <- list(homclass3_V_res="Social distance",
-              know_total="Network size",
-              socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",
-              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class")
-
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table2)","Multilevel models for Social distance and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Social distance x Social Class"=15:16),
-      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-       use.packages = F)
-```
-
-```{r fig1-marg-socdistclass, echo=FALSE, fig.cap='Average Marginal Effects of Social Distance conditionated by Social Class on Redistributive Preferences', fig.dim=c(10,5), warning=FALSE}
-int_homo <- digclas1_VW_7
-plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
-  geom_hline(yintercept = 0,color="red",linetype=2)+
-labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social Distance",y="Redistributive preferences")
-```
-
-```{r fig1-pred-socdistclass, echo=FALSE, fig.cap='Linear Predictions for Social distance on Redistributive Preferences by Social Class', fig.dim=c(10,5), warning=FALSE}
-int_homo <- digclas1_VW_7
-df_pred1 <-
-  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 1),
-                                 dclass3res_V = levels(dfreg$dclass3res_V)))
-# names(df_pred1)
-df_pred1 %>%
-ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=2,color="black") +
-  facet_grid(~factor(dclass3res_V, levels=
-                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
-                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
-  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(50,80))+
-  # scale_x_continuous(limits = c(-9,9))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social Distance",y="Redistributive preferences") +
-  theme(legend.position = "none", legend.title = element_blank())
-```
-
-\pagebreak
-
-```{r tab2-socdistclass, echo=FALSE, cache=TRUE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>%
-  na.omit() %>%
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         gini_disp=scale(gini_disp),
-         homclass3_V_res=homclass3_V_res/10)
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values)
-
-dfreg$homclass3_V_res <- reversed_values
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <-
-  dfreg %>%
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Social distance (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class",
-              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Distance*Working Class*Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance x Social Class"=7:8, "Distance * Social Class x Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-socdistclass, echo=FALSE, fig.cap='hree-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
-### Predicted values homo*class*GiniD ---------------------------------------
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>%
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Social Distance (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-\pagebreak
 

### 2024-04-15 paper1_jiturra.Rmd
Update paper1_jiturra.Rmd

@@
         legend.box.background = element_rect(colour = "black"))
+```
+
+\pagebreak
+
+## Income inequalty groups
+
+```{r table1-ineq-groups, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  religion,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+tab_countries<- 
+  dfreg %>% 
+  group_by(country3) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_q05=ntile(gini_disp,5),
+         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
+  arrange(gini_d10) %>% 
+  dplyr::select(-gini_disp)
+
+dfreg <- dfreg %>% left_join(tab_countries,by="country3")
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+
+library(estimatr)
+
+# Quintile 1 (low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 2 (mid-low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 3 (middle)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 4 (middle-high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 5 (high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_Q05 <- 
+list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
+     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
+     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+
+header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
+texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
+       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.60,
+      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      custom.gof.rows = list("Country FE"=rep("Yes",10)),
+      # include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+      # file = "table1.html"
+       use.packages = F)
+```
+
+```{r fig1-marg-ineqgrup, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+marginal <- bind_rows(
+plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
+plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
+plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
+plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
+plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
+marginal$quintile <- factor(marginal$quintile,labels = c("Q1","Q2","Q3","Q4","Q5"))
+
+ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
+  geom_point(size=2) + 
+  geom_errorbar(width=.2)+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0,color="red") +
+  facet_grid(~quintile) +
+  labs(x=NULL,y="Redistributive preferences")  
 ```

### 2024-04-15 paper1_jiturra.Rmd
bugs en data WID

@@
 plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
-marginal$quintile <- factor(marginal$quintile,labels = c("Q1","Q2","Q3","Q4","Q5"))
+marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
 
@@
   labs(x=NULL,y="Redistributive preferences")
+
 ```

### 2024-04-15 procesamiento/02-prod_prep-macro.Rmd
ajuste data
bugs en data WID

@@
 wid_shares <- haven::read_dta(here::here("input/data/original/wid_shares.dta"))
-
 # wid_gini_2018 <- wid_gini %>% filter(year==2018)
@@
 
+save(macro_data,file = here::here("input/data/proc/study1_macro_data.RData"))
+
 df1$ccode <- as.numeric(df1$country)

### 2024-04-15 paper1_jiturra.Rmd

--- 2024-04-15 paper1_jiturra.Rmd
@@
 plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
-marginal$quintile <- factor(marginal$quintile,labels = c("Q1","Q2","Q3","Q4","Q5"))
+marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
+marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
 
@@
   facet_grid(~quintile) +
-  labs(x=NULL,y="Redistributive preferences")  
+  labs(x=NULL,y="Redistributive preferences",
+       title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
+       )
+
 ```

### 2024-04-15 paper1_jiturra_supp-material.Rmd

@@
 # abstract: | 
-#   # | The escalating economic inequality and the current sanitary crisis have threatened social solidarity among citizens.
-However, these consequences have been unevenly experienced across the social structure where the upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
-Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalization and increasing the demand for welfare support.
-Particularly, social resources through network ties have been suggested to have a direct link with an individual's welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
-Consequently, it has been argued that social isolation not only plays a role in terms of social resources, but higher levels of segregation can bolster opinions, suggesting that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
-In this regard, based on the ISSP 2017 -  Social Networks (N=31,191),  multilevel estimations suggest that the influence of network homogeneity is conditional to social class, where the working and intermediate classes with high homogeneous networks hold higher redistributive preferences than the upper classes.
-Additionally, income inequality has been shown to decrease the polarizing effect of network segregation, mainly among the upper classes, when overall inequality is high.
-In sum, this study highlights the role of both social class and network segregation together to understand redistributive preferences, as well as their implications for policies and cohesion.
-#   # | 
 #   # | **Keywords**: network segregation, redistributive preferences, economic inequality
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r desc-socdist,eval=FALSE, include=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")

### 2024-04-15 paper1_jiturra.Rmd
udpate

--- 2024-04-15 paper1_jiturra.Rmd
@@
   dclass3spo_V,
-  # homclass3_V_res,
+  homclass3_V_res,
   know_total,
@@
        custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
+       symbol = "+",scalebox = 0.55,
       groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
@@
 
-```{r fig1-marg-ineqgrup, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
 marginal <- bind_rows(
@@
   facet_grid(~quintile) +
-  labs(x=NULL,y="Redistributive preferences")  
+  labs(x=NULL,y="Redistributive preferences"
+       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
+       )
+
 ```

### 2024-04-16 paper1_jiturra.Rmd
update

@@
 
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
 digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
@@
        use.packages = F)
+# performance::check_collinearity(digclas1_VW_6)
+# performance::check_model(digclas1_VW_6,check="vif")
 ```
@@
 
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
+dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
 dfreg <- 
@@
          to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
+         # dummy for categorical variables-------------------------------------$
          to_dummy(Q03pcm),
@@
 
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
 homo_V_gini <- 
@@
 ```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion Income Inequality, Network segregation and  Redistributive Preferences'}
-### Predicted values homo*class*GiniD ---------------------------------------
+### Predicted values homo*class*GiniD ---------------------------------------$
 # ginid_max<- round(max(dfreg$gini_disp) ,2)
@@
   gdppercapita,
-  country2,
+  country2,country3,
 ) %>%
@@
   na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
+    mutate(loggdppercapita=gdppercapita/1000,
          edyears2 = edyears ^ 2,
          age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-dfreg <- dfreg %>% dplyr::select(
+         # gini_disp=scale(gini_disp)
+         )
+
+# dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+dfreg$wstate<- rowMeans(dfreg[,c("abs_red","ilo_taxrev","ilo_govspe")],na.rm = T)
+dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
+
+dfreg1 <- dfreg %>% dplyr::select(
   egal,
@@
   partner,
-  "gini_disp",,
+  "gini_disp",
   loggdppercapita,
@@
   "Gender","Age in years","Religion","Has partner",
-  "Income Inequality - Gini Index (z-score)",
-  "GDP/capita (z-score)",
-  "Size of the welfare state(z-score)")
-
-sjlabelled::set_label(dfreg) <- varlab
+  "Income Inequality - Gini Index (post taxes and transfers)",
+  "GDP/capita (in 1000 US dollars)",
+  "Size of the welfare state (0 to 100 scores)")
+
+sjlabelled::set_label(dfreg1) <- varlab
 # names(dfreg) <- varlab
 
-st(dfreg,labels=T,
+st(dfreg1,labels=T,
    title="Descriptive Statistics for Study Variables",
@@
    ))
+```
+
+\newpage
+
+```{r desc-country, echo=FALSE, results='asis'}
+dfreg %>% 
+  group_by(country3) %>% 
+  summarise(n=n(),
+            homclass=mean(homclass3_V_res),
+            gini_disp=mean(gini_disp),
+            loggdppercapita=mean(loggdppercapita),
+            wstate=mean(wstate2),) %>% 
+  arrange(homclass) %>% 
+  kable(digits = 2,booktabs = TRUE,format = "latex", linesep = "",
+        caption = "Contextual variables by country",
+        col.names = c("Country","N","Network Homogeneity","Gini Index","GDP/capita in $1000","Size of the Welfare State")) %>% 
+  kable_styling(full_width = F,latex_options = "scale_down") %>% 
+  column_spec(1, width = "3.2cm") %>% 
+  column_spec(2:6, width = "3cm") %>% 
+  footnote(general = "Data sources are from the ISSP 2017 - Social Networks, WID and ILO. Contextual variables in original scale")
 ```
@@
 
-# Variable Group-Centering ------------------------------------------------
+# Variable Group-Centering ------------------------------------------------$
 dfreg <- 
@@
 \pagebreak
+## Income inequalty groups
+
+```{r table1-ineq-groups, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  religion,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+tab_countries<- 
+  dfreg %>% 
+  group_by(country3) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_q05=ntile(gini_disp,5),
+         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
+  arrange(gini_d10) %>% 
+  dplyr::select(-gini_disp)
+
+dfreg <- dfreg %>% left_join(tab_countries,by="country3")
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+
+library(estimatr)
+
+# Quintile 1 (low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 2 (mid-low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 3 (middle)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 4 (middle-high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 5 (high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_Q05 <- 
+list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
+     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
+     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+
+header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
+texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
+       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.55,
+      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      custom.gof.rows = list("Country FE"=rep("Yes",10)),
+      # include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+      # file = "table1.html"
+       use.packages = F)
+```
+
+```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+marginal <- bind_rows(
+plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
+plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
+plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
+plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
+plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
+marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
+marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
+
+ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
+  geom_point(size=2) + 
+  geom_errorbar(width=.2)+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0,color="red") +
+  facet_grid(~quintile) +
+  labs(x=NULL,y="Redistributive preferences"
+       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
+       )
+
+```
+
+\pagebreak
+
 ## OECD Countries
@@
 ```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------
+### Predicted values homo*class*GiniD ---------------------------------------$
 # ginid_max<- round(max(dfreg$gini_disp) ,2)
@@
 
-## Income inequalty groups
-
-```{r table1-ineq-groups, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-tab_countries<- 
-  dfreg %>% 
-  group_by(country3) %>% 
-  summarise(gini_disp=mean(gini_disp)) %>% 
-  mutate(gini_q05=ntile(gini_disp,5),
-         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
-  arrange(gini_d10) %>% 
-  dplyr::select(-gini_disp)
-
-dfreg <- dfreg %>% left_join(tab_countries,by="country3")
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-
-library(estimatr)
-
-# Quintile 1 (low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
-digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 2 (mid-low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
-digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 3 (middle)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
-digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 4 (middle-high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
-digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 5 (high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
-digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-digclas1_Q05 <- 
-list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
-     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
-     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
-
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
-              know_total="Network size",
-              socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
-
-header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
-texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
-       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.55,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
-      custom.gof.rows = list("Country FE"=rep("Yes",10)),
-      # include.loglik = FALSE,include.aic = FALSE,
-      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-      # file = "table1.html"
-       use.packages = F)
-```
-
-```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
-marginal <- bind_rows(
-plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
-plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
-plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
-plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
-plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
-marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
-marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
-
-ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
-  geom_point(size=2) + 
-  geom_errorbar(width=.2)+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_hline(yintercept = 0,color="red") +
-  facet_grid(~quintile) +
-  labs(x=NULL,y="Redistributive preferences"
-       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
-       )
-
-```
-
-\pagebreak
-
 ## Social distance
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r desc-social, eval=FALSE, include=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 ```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------
+### Predicted values homo*class*GiniD ---------------------------------------$
 # ginid_max<- round(max(dfreg$gini_disp) ,2)

### 2024-04-26 paper1_jiturra.Rmd
update analysis

@@
   dclass3res_V,
-  dclass3spo_V,
+  # dclass3spo_V,
   homclass3_V_res,
   know_total,
-  socialtrust,
+  # socialtrust,
   Q03pcm,
@@
   partner,
-  religion,
-  union,
+  # religion,
+  # union,
   workst,
@@
 
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
 # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
 dfreg <- na.omit(dfreg)
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
 digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
+digclas1_VW_7 <- update(digclas1_VW_5, . ~ . +dclass3res_V*homclass3_V_res)
 digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
@@
                     # digclas1_VW_4,
-                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
+                    digclas1_VW_5,
+                    # digclas1_VW_6,
+                    digclas1_VW_7)
 
@@
               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
               "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
@@
 
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,
        caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       custom.note = "Note: Models include sampling weights. Gender, age, and marital status are included as controls. Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,
@@
        symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
-      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
+      groups = list("Social Class (Ref.= Service Class)" = 3:5, "Household Income (Ref.= Tertile I)"= 6:8,
+                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
+      "Homogeneity x Social Class"=10:11),
+      custom.gof.rows = list("Controls"=rep("Yes",5)),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
@@
   agenum,
-  religion,
+  # religion,
   partner,
-  union,
+  # union,
   workst,
@@
   mutate(to_dummy(female),
-         to_dummy(union),
+         # to_dummy(union),
          to_dummy(workst),
@@
          to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
+         # to_dummy(dclass3spo_V)
   )
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
 dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
@@
 dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
 dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
 dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
 dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
@@
 # Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
 
 # drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,workst_1,
                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
 
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+
          gini_disp +
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+
          gini_disp +loggdppercapita +
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+
          gini_disp +loggdppercapita + wstate2+
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+
          gini_disp +loggdppercapita + wstate2 +
@@
   know_total,
-  socialtrust,
+  # socialtrust,
   dclass3res_V,
@@
   edyears,
-  dclass3spo_V,  
+  # dclass3spo_V,  
   workst,
-  union,
+  # union,
   female,
   agenum,
-  religion,
+  # religion,
   partner,
@@
 c("Redistributive preferences","Class-based network homogeneity",
-  "Network size","Social trust","Social class",
+  "Network size",
+  # "Social trust",
+  "Social class",
   "Household Income","Education in years",
-  "Partner's Social Class","Labor status","Union membership",
-  "Gender","Age in years","Religion","Has partner",
+  # "Partner's Social Class",
+  "Labor status",
+  # "Union membership",
+  "Gender","Age in years",
+  # "Religion",
+  "Has partner",
   "Income Inequality - Gini Index (post taxes and transfers)",
@@
 
-# ggsave(plot = arrangeGrob(fig_homodiff_gini, nrow = 1),filename = "slides-bivar-homodiff.png",device = "png",
-#        path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
+ggsave(plot = arrangeGrob(fig_homodiff_gini, nrow = 1),filename = "slides-bivar-homodiff.png",device = "png",
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
 ```
@@
 # Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
 
 # drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
 
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+         
          gini_disp +loggdppercapita + wstate2+
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita +
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita + wstate2+
@@
          know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita + wstate2 +
@@
 
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
 
@@
 # Quintile 1 (low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
-digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
 digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
@@
 # Quintile 2 (mid-low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
-digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
 digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
@@
 # Quintile 3 (middle)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
-digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
 digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
@@
 # Quintile 4 (middle-high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
-digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum + partner +  factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
 digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
@@
 # Quintile 5 (high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
-digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
 digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
@@
 header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
-texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+screenreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
        caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       custom.note = "Note: Models include sampling weights. Gender, age and marital status are included as controls. Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,
@@
        symbol = "+",scalebox = 0.55,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
+      groups = list("Social Class (Ref.= Service Class)" = 3:4, "Household Income (Ref.= Tertile I)"= 6:8,  
+                    # "Partner's Social Class (Ref.= Service Class)" = 12:14, 
+                    "Homogeneity x Social Class"=10:11),
       custom.gof.rows = list("Country FE"=rep("Yes",10)),
@@
 # Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
 
 # drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
 
@@
 dummy_df <- df1 %>% dplyr::select(id,
-  egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust,
-  Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region,
+  egal = egal2,dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,edyears,female,agenum,
+  # religion,
+  partner,
+  # union,
+  workst,WEIGHT,region,
   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
@@
   dclass3res_V=isei08,
-  dclass3spo_V=isei08sp,
+  # dclass3spo_V=isei08sp,
   homclass3_V_res=socdist,
   know_total,
-  socialtrust,
+  # socialtrust,
   Q03pcm,
@@
          dclass3res_V=dclass3res_V/10,
-         dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10) %>%
+         # dclass3spo_V=dclass3spo_V/10,
+         homclass3_V_res=homclass3_V_res/10
+         ) %>%
   # filter(oecd == "OECD") %>%
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
 digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
 
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
 digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
@@
               know_total="Network size",
-              socialtrust="Social Trust",
+              # socialtrust="Social Trust",
               # "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
@@
               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_V" = "ISEI/10 (Partner)",
+              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              # "dclass3spo_V" = "ISEI/10 (Partner)",
               "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI")
@@
 dummy_df <- df1 %>% dplyr::select(id,
-  egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust,
-  Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region,
+  egal = egal2,dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,know_total,
+  # socialtrust,
+  Q03pcm,edyears,female,agenum,
+  # religion,
+  partner,
+  # union,
+  workst,WEIGHT,region,
   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
@@
          dclass3res_V=dclass3res_V/10,
-         dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10) %>% 
+         # dclass3spo_V=dclass3spo_V/10,
+         homclass3_V_res=homclass3_V_res/10
+         ) %>% 
   filter(id %in% dummy_df$id)
@@
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
 dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
@@
 # dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2)
+# dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2)
 
 # drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
@@
          know_total_gc+
-         socialtrust_gc+
+         # socialtrust_gc+
          dclass3res_V+
          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         dclass3spo_V_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +
@@
          know_total_gc+
-         socialtrust_gc+
+         # socialtrust_gc+
          dclass3res_V+
          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         dclass3spo_V_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita +
@@
          know_total_gc+
-         socialtrust_gc+
+         # socialtrust_gc+
          dclass3res_V+
          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         dclass3spo_V_gc+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita + wstate2+
@@
          know_total_gc+
-         socialtrust_gc+
+         # socialtrust_gc+
          dclass3res_V+
          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         dclass3spo_V_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita + wstate2 +
@@
          know_total_gc+
-         socialtrust_gc+
+         # socialtrust_gc+
          dclass3res_V+
          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         dclass3spo_V_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
+         # union_gc+
+         workst_gc+ 
          gini_disp +loggdppercapita + wstate2+
@@
 ```
+
+```{r table1-alternative, eval=FALSE, include=FALSE, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V=dclass6res,
+  # homclass3_V_res=homclass3_V_res_part,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  # religion,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_3<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_4<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  know_total + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_6<- lmer(egal~1 + homclass3_V_res + female+agenum+ 
+                       partner +  know_total +   
+                       dclass3res_V + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_7<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +   know_total +  
+                       dclass3res_V +  edyears + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_8<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm +(1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_9<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total +  
+                       dclass3res_V +  edyears +  Q03pcm + workst +(1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_10<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm + workst + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_10a<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm + workst + (homclass3_V_res|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_11 <- update(digclas1_VW_10, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,digclas1_VW_3,digclas1_VW_4,
+                    digclas1_VW_6,digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,digclas1_VW_10a,
+                    digclas1_VW_11)
+
+screenreg(digclas1_VW)
+plot_slopes(digclas1_VW_11, variables = "homclass3_V_res", by = "dclass3res_V",draw = T)
+```

### 2024-04-26 procesamiento/01-prod_prep-micro.Rmd
update analysis

--- 2024-03-22 procesamiento/01-prod_prep-micro.Rmd
@@
 sjlabelled::set_label(df1$dclass3res_III_V) <- "Social Class 3 (R's) - (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3res_III_V)
+
+# Class scheme 6 classes 
+df1$dclass6res <- car::recode(df1$egp11,as.factor = T,
+                                 levels =c('Upper Service class',
+                                           'Lower Service class',
+                                           'Routine nonmanual class',
+                                           'Self-employed',
+                                           'Skilled working class',
+                                           'Unskilled working class'), 
+                                 "1='Upper Service class';2='Lower Service class';c(3,4)='Routine nonmanual class';c(5,6,7)='Self-employed';
+                              c(8,9)='Skilled working class';c(10,11)='Unskilled working class'")
+
+sjlabelled::set_label(df1$dclass6res) <- "Social Class 6 (R's) - (DIGCLASS)";frq(df1$dclass6res)
 ```
@@
                  "pct_high","pct_middle","pct_low")],use = "complete.obs")
-
 ```
@@
 sjlabelled::set_label(df1$homclass3_V_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res)
+
+# Partner class as part of the position generator
+frq(df1$dclass3spo_V)
+df1$partner_hig <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "1=1;2:3=0;4=NA");frq(df1$partner_hig)
+df1$partner_mid <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "2=1;c(1,3)=0;4=NA");frq(df1$partner_mid)
+df1$partner_low <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "3=1;c(1,2)=0;4=NA");frq(df1$partner_low)
+
+df1$n_low_partner<- rowSums(df1[,c("n_low","partner_low")],na.rm = T); sjlabelled::set_label(df1$n_low_partner) <- "Number of low status contacts + partner"
+df1$n_mid_partner<- rowSums(df1[,c("n_middle","partner_mid")],na.rm = T); sjlabelled::set_label(df1$n_mid_partner) <- "Number of middle status contacts + partner"
+df1$n_high_partner<- rowSums(df1[,c("n_high","partner_hig")],na.rm = T); sjlabelled::set_label(df1$n_high_partner) <- "Number of high status contacts + partner"
+```
+
+```{r homogeneity-R-digclass-plus-partner}
+## Using RESPONDENT Class for homogeneity---------------------------------------
+df1$ingroup_res <- NA 
+df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",df1$n_high_partner,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",df1$n_mid_partner,df1$ingroup_res)
+df1$ingroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",df1$n_low_partner,df1$ingroup_res);frq(df1$ingroup_res)
+
+df1$outgroup_res <- NA 
+df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low_partner","n_mid_partner")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_partner","n_high_partner")],na.rm = T),df1$outgroup_res)
+df1$outgroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_mid_partner","n_high_partner")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
+
+df1$know_total_partner <- rowSums(df1[,c("n_high_partner","n_mid_partner","n_low_partner")],na.rm = T);sjlabelled::set_label(df1$know_total_partner) <- "Number of contacts + partner"
+
+df1$homclass3_V_res_part <- as.numeric(df1$ingroup_res/df1$know_total_partner)
+sjlabelled::set_label(df1$homclass3_V_res_part) <- "Class homogeneity (R's) + partner tie (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res_part)
+cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
+summary(df1$homclass3_V_res_part)
+summary(df1$homclass3_V_res)
+cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
+df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res,outgroup_res,know_total_partner)
 ```

### 2024-05-06 paper1_jiturra.Rmd
update Alejo

@@
 Particularly, social resources through network ties have been suggested to have a direct link with an individual's welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
-Consequently, it has been argued that social isolation not only plays a role in terms of social resources, but higher levels of segregation can bolster opinions, suggesting that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
+Consequently, it has been argued that being socialy excluded not only plays a role in terms of social resources, but higher levels of segregation can bolster opinions, suggesting that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
 In this regard, based on the ISSP 2017 -  Social Networks (N=31,191),  multilevel estimations suggest that the influence of network homogeneity is conditional to social class, where the working and intermediate classes with high homogeneous networks hold higher redistributive preferences than the upper classes.
@@
 
-Rising economic inequality over the past decades [@piketty_capital_2014] and the recent sanitary crisis have raised citizens' concerns about economic inequality, pushing governments to enact redistributive policies, which has tested the capacity of welfare systems to provide sufficient risk protection for their citizens [@breznau_welfare_2021].
-However, the privileged access to resources held by the upper and intermediate classes has consolidated their resilience capacity in times of greater economic hardship, allowing them to maintain a relatively stable standard of living, in contrast to the decline in the material conditions of working-class families [@moawad_myth_2023].
-In this regard, it has been claimed that economic gaps in economic resources also have a greater effect on social relations.
-Studies on the role of economic inequality have argued that social bonding can be threatened when economic inequality increases, undermines how people perceive each other, their opportunities to participate in social life, and the capacity to knit networks that contribute to social integration [@lancee_income_2012;@letki_getting_2015].
-Therefore, experiencing segregated networks is one of the consequences of greater economic gaps as it represents greater distance between the different social classes  [@pichler_patterns_2007;@otero_space_2022].
-In this regard, it has been argued that segregation can threaten social cohesion and solidarity [@joye_measuring_2019], which in turn can undermine public support for welfare schemes and redistribution [@baldassarri_diversity_2020].
-
-The sociological tradition has understood social classes through the labor market situation of occupations in terms of employment relations, skill level, and authority within the workplace [@Erikson1992;@Erikson1979].
-Likewise, classes represent relations in the labor market and trace lines in terms of status relations as the foundations for opportunities for action and the consolidation of lifestyles [@weber_economy_1978].
-In this matter, the class situation of individuals and households also trace distinctions in various domains of social life, such as cultural consumption behavior [@Chan2007;@torche_social_2007], ideological preferences [@evans_decline_1993], and popular opinions about the welfare state and redistribution [@Svallfors2006].
-Regarding the latter, despite the claims of a displacement of the distributive struggle between classes by other group identities [@clark_declining_1993;@inglehart_culture_1990], past decade research has persistently demonstrated that class positions indeed still explain economic attitudes towards the welfare state and redistribution [@lindh_class_2020, p.
-421].
-Thus, the claimed blurring of the class cleavage has not been strongly supported while the class differences have been evidenced in perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes on market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-
-However, the study of redistributive preferences has been mainly focused on the individual and household situation.
-In contrast, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
-In this regard, how people form their friendship and partnership ties tends to be homogeneous because of the tendency towards homophily in forming interpersonal networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-Hereby, we argue that the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes.
-In this regard, recent research has argued that the degree of segregation in the composition of social ties is a window for learning about others' lifestyles, economic conditions, and worldviews [@mijs_inequality_2018;@otero_power_2023].
-However, there has been no systematic dialogue regarding the role of social ties on preferences for redistribution from a social network perspective.
-Therefore, this research aims to contribute to the ongoing literature on class-based network segregation on attitudes toward redistribution [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-
+The study of redistributive preferences and social class has been mainly focused on the individual and household situation.
+However, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
+Moreover, friendship and partnership ties tend to be homogeneous due to the homophilous tendency in interpersonal network formation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+Thus, the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes [@Svallfors2006].
+In this respect, recent research has argued that the degree of segregation in the composition of social ties can influence opinions about economic inequality as they function as a window for learning about the lifestyles, economic conditions, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
+However, a knowledge gap in the literature still needs to be understood regarding the network mechanisms in forming individual opinions about governmental actions that aspire to achieve egalitarian economic distribution of resources and opportunities in society [@mccall_americans_2009].
+
+The study of redistributive preferences and social class has been mainly focused on the individual and household situation.
+However, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
+Moreover, friendship and partnership ties tend to be homogeneous due to the homophilous tendency in interpersonal network formation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+Thus, the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes [@Svallfors2006].
+In this respect, recent research has argued that the degree of segregation in the composition of social ties can influence opinions about economic inequality as they function as a window for learning about the lifestyles, economic conditions, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
+However, a knowledge gap in the literature still needs to be understood regarding the network mechanisms in forming individual opinions about governmental actions that aspire to achieve egalitarian economic distribution of resources and opportunities in society [@mccall_americans_2009].
+
+Recent studies have argued that understanding class relations requires focusing on network composition as it represents cross-class embeddedness as a property of the social structure [@blau_macrosociological_1977].
+In this regard, it has been argued that the class position of network ties can influence opinions on redistributive policies, but also the degree of segregation from other social classes in more homogeneous social networks can strengthen the class divide in redistributive preferences  [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
 While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention must be devoted to understanding the role of social environments in class relations.
@@
 In addition, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-This research aims to contribute to the literature on preferences toward redistribution from a relational perspective, focusing on how the structural properties of networks can influence people's preferences toward economic redistribution.
-
-Our research seeks to provide answers to two key questions.
-Firstly, at the micro-level, what is the role of class-based network segregation on redistributive preferences?
-Secondly, at the macro-level, does economic inequality play a role in the relationship between class-based network segregation and redistributive preferences?
-To achieve this, we have analyzed data from the International Social Survey Program (ISSP) 2017, which comprises a sample of 31,191 individuals across 31 countries globally.
-In this regard, the ISSP has a unique opportunity to date since it includes information on interpersonal networks through the position generator, the core questions for class position allocation, and attitudes toward economic inequality and redistribution.
+
+Comparative evidence about the contextual factors that affect the relationship between class-based network segregation and redistributive preferences is scarce.
+Previous research on the class-attitude link has suggested that the distribution of economic resources is one of the main societal characteristics that can affect the link between class relations and redistributive demands, as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
+These studies have indicated that the affluent are more sensitive to changes in income inequality and support redistribution to a greater extent when inequality rises, while the working class remains relatively stable.
+In this discussion, the sociological moral economy perspective has suggested that the upper classes are more concerned about the erosion of the opportunity structure as a matter of distributive justice [@sachweh_why_2019].
+In contrast, the political economy approach has suggested that the negative consequences of inequality (e.g., criminality) can motivate greater support for redistribution among the upper classes [@dimick_altruistic_2017].
+
+It has been previously established that wider economic gaps lead to segregated forms of social participation and status composition of social networks [@pichler_patterns_2007;@otero_space_2022].
+Indeed, people with lower economic backgrounds have fewer chances to participate in social activities and form diverse social networks.
+Therefore, it has been suggested that material inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of people with lower resources and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
+
+Only a few studies have examined the role of network structure from a comparative perspective, employing a well-established instrument as the position generator [@hadler_issp_2020;@sapin_issp_2020].
+Despite previous evidence, to our knowledge, no research has stressed the role of economic inequality in the relationship between network segregation and redistributive preferences from a cross-national perspective.
+
+Therefore, our study is guided by two key research questions.
+First, at the micro-level, we explore the role of class-based network segregation in shaping redistributive preferences.
+Secondly, at the macro level, we investigate whether economic inequality conditions the relationship between class-based network segregation and redistributive preferences.
+To address these questions, we have conducted an analysis of data from the International Social Survey Program (ISSP) 2017, which includes a sample of 32,529 individuals across 31 societies.
+The ISSP dataset is particularly valuable for our study as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
 
 # Theoretical views on class, social networks, and redistributive preferences
+
+The class cleavage has not been strongly supported while the class differences have been evidenced in perceived class conflicts (Edlund & Lindh, 2015; Pérez, 2023), attitudes on market-based inequality (Andersen &Yaish, 2018; Lindh, 2015), and redistributive preferences (Brooks & Svallfors, 2010; Curtis & Andersen, 2015; Langsæther & Evans, 2020).
 
@@
 header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
-screenreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
        caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),

### 2024-05-08 paper1_jiturra.Rmd
update abstract y class inequality

@@
 abstract: | 
-  | The escalating economic inequality and the current sanitary crisis have threatened social solidarity among citizens.
-However, these consequences have been unevenly experienced across the social structure where the upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience.
-Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalization and increasing the demand for welfare support.
-Particularly, social resources through network ties have been suggested to have a direct link with an individual's welfare through instrumental and expressive outcomes, such as providing information or help in moments of need.
-Consequently, it has been argued that being socialy excluded not only plays a role in terms of social resources, but higher levels of segregation can bolster opinions, suggesting that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes.
-In this regard, based on the ISSP 2017 -  Social Networks (N=31,191),  multilevel estimations suggest that the influence of network homogeneity is conditional to social class, where the working and intermediate classes with high homogeneous networks hold higher redistributive preferences than the upper classes.
-Additionally, income inequality has been shown to decrease the polarizing effect of network segregation, mainly among the upper classes, when overall inequality is high.
-In sum, this study highlights the role of both social class and network segregation together to understand redistributive preferences, as well as their implications for policies and cohesion.
+  | Escalating economic inequality has increased attention to the link between class-based social ties and redistributive preferences in contemporary societies.
+However, social classes are not equally affected by inequality regarding their chances of establishing cross-class social relations.
+While those in the upper and middle classes have greater access to economic and diverse social ties, the working class has been disproportionately affected by social exclusion.
+Consequently, this leads to a growing divide between their lives and the lives of others, consolidating segregated lifeworlds.
+Previous research has shown that the link between class relations and redistributive preferences can be enriched from a network perspective.
+Meeting people from diverse class positions can help individuals become more aware of the lifestyles and worldviews of others.
+On the one hand, when upper-class networks become more homogeneous, it can lead to lower empathy toward those in need and less support for redistributive policies.
+On the other hand, when there is segregation in lower-class social networks, it can lead to greater marginalization and a higher demand for welfare support.
+This study explores how class-based network segregation influences redistributive preferences from a cross-national perspective, employing data from the International Social Survey 2017, which comprised 32,529 individuals in 31 societies.
+The regression analyses indicate that network homogeneity has a conditional influence on redistributive preferences based on social class.
+Homogeneous social networks in the working and intermediate classes increase redistributive preferences, while greater homogeneity in the upper classes reduces support for redistribution.
+In addition, in contexts of greater income inequality, the conditional influence of network segregation weakens, especially for the upper classes.
+Implications for the study of class relations and policy preferences are discussed.
   | 
-  | **Keywords**: network segregation, redistributive preferences, economic inequality
+  | **Keywords**: social networks, social class, redistributive preferences, income inequality
 output:
@@
 
-The study of redistributive preferences and social class has been mainly focused on the individual and household situation.
-However, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
-Moreover, friendship and partnership ties tend to be homogeneous due to the homophilous tendency in interpersonal network formation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-Thus, the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes [@Svallfors2006].
-In this respect, recent research has argued that the degree of segregation in the composition of social ties can influence opinions about economic inequality as they function as a window for learning about the lifestyles, economic conditions, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
-However, a knowledge gap in the literature still needs to be understood regarding the network mechanisms in forming individual opinions about governmental actions that aspire to achieve egalitarian economic distribution of resources and opportunities in society [@mccall_americans_2009].
-
 Recent studies have argued that understanding class relations requires focusing on network composition as it represents cross-class embeddedness as a property of the social structure [@blau_macrosociological_1977].
@@
 It has been previously established that wider economic gaps lead to segregated forms of social participation and status composition of social networks [@pichler_patterns_2007;@otero_space_2022].
-Indeed, people with lower economic backgrounds have fewer chances to participate in social activities and form diverse social networks.
-Therefore, it has been suggested that material inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of people with lower resources and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
+Indeed, it has been suggested that material inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of people with lower resources and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
 
@@
 As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
-In principle, social stratification scholars have traditionally considered differentiation as observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_inequality_1977].
+In principle, social stratification scholars have traditionally considered differentiation as observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_macrosociological_1977].
 Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] that trace friendship and family ties, such as age and gender, as well as segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
@@
 Here, the extent to which social classes distance themselves in terms of network segregation indeed creates an "empathy gulf" [@sachweh_moral_2012] that can be observed in how the service class is less willing to take action to strive with inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments [@otero_power_2023], in contrast to the increasing redistributive pressures of the marginalized working class.
-Besides, as network homogeneity represents low cross-class ties, it can be argued that lower social integration [@blau_inequality_1977] can undermine social solidarity as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
+Besides, as network homogeneity represents low cross-class ties, it can be argued that lower social integration [@blau_macrosociological_1977] can undermine social solidarity as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
 

### 2024-05-08 procesamiento/02-prod_prep-macro.Rmd
update abstract y class inequality

@@
 
-# centering micro level
+# Class inequality
 
-```{r eval=FALSE, include=FALSE}
-df2 <- 
+```{r}
+summary(df1$incomepcap)
+
+df_class3_ineq <- 
 df2 %>%   
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(class3),to_dummy(class3spo),to_dummy(class3res),to_dummy(Q03pcm))
-df2$female_gc = group_center(df2$female_2, grp = df2$country2)
-df2$union_gc = group_center(df2$union_2, grp = df2$country2)
-df2$workst_gc = group_center(df2$workst_2, grp = df2$country2)
-df2$edyears_gc = group_center(df2$edyears, grp = df2$country2)
-df2$agenum_gc = group_center(df2$agenum, grp = df2$country2)
+  group_by(country2,dclass3res_V) %>%
+  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame() %>%
+  na.omit() %>% 
+  dplyr::select(country2,dclass3res_V,incomepcap,ednum,wid_gini_disp) %>% 
+  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = c("incomepcap","ednum")) %>% 
+  mutate(ratio_class_inc = `incomepcap_Service Class (I+II)`/`incomepcap_Working Class (V+VI+VII)`,
+         ratio_class_educ  = `ednum_Service Class (I+II)`/`ednum_Working Class (V+VI+VII)`) %>% 
+  as.data.frame()
 
-# EGP: dominance
-df2$class3_ser_gc = group_center(df2$class3_1, grp = df2$country2)
-df2$class3_mid_gc = group_center(df2$class3_2, grp = df2$country2)
-df2$class3_wor_gc = group_center(df2$class3_3, grp = df2$country2)
-# EGP: Respondent
-df2$class3res_ser_gc = group_center(df2$class3res_1, grp = df2$country2)
-df2$class3res_mid_gc = group_center(df2$class3res_2, grp = df2$country2)
-df2$class3res_wor_gc = group_center(df2$class3res_3, grp = df2$country2)
-# EGP: Respondent
-df2$class3spo_ser_gc = group_center(df2$class3spo_1, grp = df2$country2)
-df2$class3spo_mid_gc = group_center(df2$class3spo_2, grp = df2$country2)
-df2$class3spo_wor_gc = group_center(df2$class3spo_3, grp = df2$country2)
-# Household Income Tercile
-df2$Q03pcm_1_gc = group_center(df2$Q03pcm_1, grp = df2$country2)
-df2$Q03pcm_2_gc = group_center(df2$Q03pcm_2, grp = df2$country2)
-df2$Q03pcm_3_gc = group_center(df2$Q03pcm_3, grp = df2$country2)
-df2$Q03pcm_NA_gc = group_center(df2$Q03pcm_4, grp = df2$country2)
+df_class3_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
 
-names(df2)
-# drop dummies
-df2 <- 
+df_class6_ineq <- 
 df2 %>%   
-  select(-c(female_1,female_2,union_1,union_2,workst_1,workst_2,
-            class3_1,class3_2,class3_3,class3res_1,class3res_2,class3res_3,
-            class3spo_1,class3spo_2,class3spo_3,
-            Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4))
-names(df2)
+  group_by(country2,dclass6res) %>%
+  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame() %>%
+  na.omit() %>% 
+  dplyr::select(country2,dclass6res,incomepcap,ednum,wid_gini_disp) %>% 
+  tidyr::pivot_wider(names_from = "dclass6res", values_from = c("incomepcap","ednum")) %>% 
+  mutate(ratio_class_inc = `incomepcap_Upper Service class`/`incomepcap_Unskilled working class`,
+         ratio_class_educ  = `ednum_Upper Service class`/`ednum_Unskilled working class`) %>% 
+  as.data.frame() 
+df_class_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
 ```
 
-# centering macro level
+```{r}
 
-```{r eval=FALSE, include=FALSE}
-df2$gini_disp_c <- center(df2$gini_disp)
-df2$gini_mkt_c <- center(df2$gini_mkt)
-df2$palmaratio_c <- center(df2$palmaratio)
-df2$top10_c <- center(df2$top10)
-df2$middle50_c <- center(df2$middle50)
-df2$d10d1_c <- center(df2$d10d1)
-df2$giniindex_c <- center(df2$giniindex)
-df2$ttheilge1_c <- center(df2$ttheilge1)
-df2$rgdpna_c <- center(df2$rgdpna)
+income_data
 
-df2$gini_disp_z <- center(df2$gini_disp)
-df2$gini_mkt_z <- center(df2$gini_mkt)
-df2$palmaratio_z <- center(df2$palmaratio)
-df2$top10_z <- center(df2$top10)
-df2$middle50_z <- center(df2$middle50)
-df2$d10d1_z <- center(df2$d10d1)
-df2$giniindex_z <- center(df2$giniindex)
-df2$ttheilge1_z <- center(df2$ttheilge1)
-df2$rgdpna_z <- center(log(df2$rgdpna))
+# Example data
+# Assuming you have a data frame called 'income_data' with columns: country, social_class, and average_income
 
-df2 %>% 
-  select(country3,ends_with("_c")) %>% group_by(country3) %>% summarise_all(.funs = mean) %>% View()
-table(df2$country2)
+# Calculate all pairs of income ratios within each country
+income_ratios <- income_data %>%
+  group_by(country) %>%
+  mutate(income_ratio = combn(average_income, 2, FUN = function(x) x[1] / x[2])) %>%
+  ungroup()
+
+# Print the result
+print(income_ratios)
+
 ```

### 2024-05-10 paper1_jiturra.Rmd
actualizacion intro y seccion1

@@
 \pagebreak
+
 # Introduction
@@
 The study of redistributive preferences and social class has been mainly focused on the individual and household situation.
-However, less attention has been paid to the sociability structures embedded in class relations regarding social tie formation.
-Moreover, friendship and partnership ties tend to be homogeneous due to the homophilous tendency in interpersonal network formation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+Despite this, less attention has been paid to the role of social networks as socialization agents of attitudes toward redistribution.
+It has been stated that friendship and partnership ties tend to be homogeneous in their characteristics, expressing the tendency to form and consolidate homophilous social networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
 Thus, the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes [@Svallfors2006].
 In this respect, recent research has argued that the degree of segregation in the composition of social ties can influence opinions about economic inequality as they function as a window for learning about the lifestyles, economic conditions, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
-However, a knowledge gap in the literature still needs to be understood regarding the network mechanisms in forming individual opinions about governmental actions that aspire to achieve egalitarian economic distribution of resources and opportunities in society [@mccall_americans_2009].
-
-Recent studies have argued that understanding class relations requires focusing on network composition as it represents cross-class embeddedness as a property of the social structure [@blau_macrosociological_1977].
-In this regard, it has been argued that the class position of network ties can influence opinions on redistributive policies, but also the degree of segregation from other social classes in more homogeneous social networks can strengthen the class divide in redistributive preferences  [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention must be devoted to understanding the role of social environments in class relations.
+However, there is still a knowledge gap to disentangle the network mechanisms involved in political attitude formation about the role of government in enacting redistributive policies to strive against economic inequality [@mccall_americans_2009].
+
+The class composition of network ties can influence opinions on redistributive policies, but also the degree of segregation from other social classes in more homogeneous social networks can strengthen the class divide in redistributive preferences  [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention should be devoted to understanding the role of social environments in class relations.
 This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
@@
 
-Comparative evidence about the contextual factors that affect the relationship between class-based network segregation and redistributive preferences is scarce.
-Previous research on the class-attitude link has suggested that the distribution of economic resources is one of the main societal characteristics that can affect the link between class relations and redistributive demands, as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-These studies have indicated that the affluent are more sensitive to changes in income inequality and support redistribution to a greater extent when inequality rises, while the working class remains relatively stable.
-In this discussion, the sociological moral economy perspective has suggested that the upper classes are more concerned about the erosion of the opportunity structure as a matter of distributive justice [@sachweh_why_2019].
-In contrast, the political economy approach has suggested that the negative consequences of inequality (e.g., criminality) can motivate greater support for redistribution among the upper classes [@dimick_altruistic_2017].
-
-It has been previously established that wider economic gaps lead to segregated forms of social participation and status composition of social networks [@pichler_patterns_2007;@otero_space_2022].
-Indeed, it has been suggested that material inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of people with lower resources and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
-
-Only a few studies have examined the role of network structure from a comparative perspective, employing a well-established instrument as the position generator [@hadler_issp_2020;@sapin_issp_2020].
-Despite previous evidence, to our knowledge, no research has stressed the role of economic inequality in the relationship between network segregation and redistributive preferences from a cross-national perspective.
-
-Therefore, our study is guided by two key research questions.
-First, at the micro-level, we explore the role of class-based network segregation in shaping redistributive preferences.
-Secondly, at the macro level, we investigate whether economic inequality conditions the relationship between class-based network segregation and redistributive preferences.
-To address these questions, we have conducted an analysis of data from the International Social Survey Program (ISSP) 2017, which includes a sample of 32,529 individuals across 31 societies.
-The ISSP dataset is particularly valuable for our study as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
+Besides the individual dynamics, little is known about how contextual factors affect the relationship between networks and redistributive preferences.
+Previous studies have shown that wider economic gaps lead to segregated forms of social participation and status composition of social networks [@pichler_patterns_2007;@otero_space_2022].
+Indeed, economic inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of the lower classes and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
+Studies on the class-attitude link posit that economic inequality is crucial for understanding how class relations are reflected in redistributive demands as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
+The main finding drawn from these studies is that the upper classes tend to hold more egalitarian attitudes in contexts of high inequality, while the attitudes of the working class remain stable regardless of inequality levels.
+In this discussion, the moral economy explanation argues that the upper classes are more concerned about the integrity of resource allocation procedures as a matter of distributive justice [@sachweh_why_2019].
+Conversely, political economy research suggests that the upper classes are more likely to support redistribution policies due to the negative consequences of inequality [@dimick_altruistic_2017].
+
+In this context, to our knowledge, no research has comparatively stressed the role of economic inequality in the relationship between network segregation and redistributive preferences.
+Therefore, the present study aims to answer two research questions.
+First, at the micro-level, what is the role of class-based network segregation on redistributive preferences?
+Secondly, at the macro level, to what extent does economic inequality condition the relationship between class-based network segregation and redistributive preferences?
+To address these questions, we have analyzed data from the International Social Survey Program (ISSP) 2017, which includes a sample of 32,529 individuals across 31 societies.
+In this regard, the ISSP presents a nonprecedence opportunity as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
 
@@
 
-The class cleavage has not been strongly supported while the class differences have been evidenced in perceived class conflicts (Edlund & Lindh, 2015; Pérez, 2023), attitudes on market-based inequality (Andersen &Yaish, 2018; Lindh, 2015), and redistributive preferences (Brooks & Svallfors, 2010; Curtis & Andersen, 2015; Langsæther & Evans, 2020).
+## Class divide in redistributive preferences
+
+Over the past decades, the study of redistributive preferences in industrialized societies has consistently demonstrated the importance of social class as a key explanatory factor  [@lindh_class_2020, p.
+421].
+Specifically, class positions have been shown to significantly influence individual opinions on the government's role in various aspects of the economic sphere, such as reducing income disparities or enhancing opportunities for those in economic distress [@mccall_americans_2009].
+
+However, class-based explanations of redistributive preferences have mainly been, but not exclusively, focused on the individual or household situation.
+For instance, it has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
+Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019]. Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006]. It is argued that continuous interaction with diverse people that characterize interpersonal services can reinforce egalitarian values [@kitschelt_occupations_2014].
+In contrast, the vertical monitoring in managerial occupations and the relevance of autonomy in the case of self-employed can contribute to self-interested and conservative political views [@langsaether_more_2020;@oesch_electoral_2018].
+
+While our understanding of how social class influences public opinion on market-based resource distribution [@andersen_preferences_2018;@lindh_public_2015] and government income redistribution [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010;@Svallfors2006] is substantial, there remains a significant gap in our knowledge about the impact of class-based social relations from a network perspective on redistributive preferences.
 
@@
 
-As social relations within the occupational structure serve as the foundation for class analysis, widening our examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relevance in political attitudes formation.
-In principle, social stratification scholars have traditionally considered differentiation as observable patterns of association given by the intersection of status and group membership, which can be understood as relational networks between positions [@blau_macrosociological_1977].
-Empirically, homophily is one of the most significant findings in network research, understood as the higher likelihood of tie formation between people of similar characteristics [@mcpherson_birds_2001, p.416] that trace friendship and family ties, such as age and gender, as well as segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
-In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of worldviews, reinforcing in-group selectivity and value similarity [@visser_attitudes_2004;@homans_human_1951].
-Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through social differentiation in social activities as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019].
-From this perspective, we argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
-
-How classes are formed also provides insight into social relations and sociability practices.
-In sociology, classes are understood as the basis for action given their labor market situation, which ultimately shapes their access to opportunities and resources [@weber_economy_1978].
-According to the habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984].
-From this approach, classes seek to improve their positions through the intergenerational transmission of resources, where similarities in friendship and family choices play a crucial role in reproducing privileged social positions.
-Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding lower classes [@bourdieu_reproduccion_1981].
-Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring the intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992].
-Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes, where access to resources embedded in social networks follows a pattern of accumulation that ultimately leads to social segregation in both the upper and lower bounds of the social structure.
-
-Previous research on social class and tie formation has suggested that class permeability in social networks, understood as the formation of cross-class social ties, can be traced differently across property and authority boundaries.
-Empirically, evidence from Western industrialized societies has shown that the formation of friendship ties between owners and the working class is significantly less likely, in contrast to the tendency of higher tie formation between supervisors and manual workers.
-This suggests that the property dimension is much less permeable than authority-based boundaries, given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992].
-Similarly, evidence from Chile has shown that the higher permeability of the intermediate classes contrasts with the more homogeneous networks of the working class, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social isolation, whereas the upper class is less permeable and homogenous because of its tendency to self-select as a practice that ultimately seeks to reproduce their privileged status positions [@otero_open_2021].
-
-By contrast, cross-class embeddedness can be described in terms of social activities, generational changes, and the life course.
-In this regard, @pichler_social_2009 suggest that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the working class, which tends to be more homogeneous in civic engagement behavior.
-Similarly, other studies in Europe and South America have shown that the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes, where being socially mobile helps to improve both dimensions in tie formation [@cepic_how_2020;@carrascosa_class_2023].
-Nevertheless, it does not equalize the weight of the class background compared with those that are intergenerationally stable in the upper class.
-Additionally, the little longitudinal evidence suggests that networks change following a dynamic of cumulative advantages regarding its composition in terms of prestige and diversity, where upper classes improve in both dimensions, while the lower class shows more stability across the life course [@volker_social_2020].
-
-Altogether, these studies account for class-based network segregation, as the degree of connectedness of an individual to different occupations is meant to represent social resources embedded in social networks vertically in the social structure [@lin_social_2007].
-Drawing on this approach, stratification scholars have focused on how social connections are distributed across class structure as a matter of social integration [@blau_macrosociological_1977].
-In addition, homogeneity is described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions.
-Simultaneously, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
-Hence, both approaches provide alternatives for studying social class from a network perspective, which has been increasingly discussed in the stratification literature and scholarly discussion about social class and political attitudes.
+It is possible to argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
+Class relations can also be understood as the degree of cross-class relationship as a structural characteristic of a society, representing a network of social ties between different class positions [@blau_macrosociological_1977].
+Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001, p.416].
+Here, friendship and family tend to be homogeneous in terms of their demographic characteristics that simultaneously intersect with socioeconomic status and class [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
+Acknowledging that socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951], we argue that attitudinal similarity is the result of segregated social relations, which in turn are strongly linked to structural processes of differentiation that ultimately demarcate the opportunities in the formation of diverse social ties [@feld_focused_1981].
+
+In the discussion on the class composition of social networks, it is possible to find two approaches.
+On the one hand, one approach has emphasized the role of diversity as the degree of connectedness to dissimilar occupations as social positions that vertically represent access to resources embedded in social networks [@lin_social_2007].
+However, diversity is defined as the rate of dissimilar ties or the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
+On the other hand, a second approach has underscored the role of network segregation, which has been described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions [@otero_open_2021].
+
+Empirically, studies on network diversity have shown that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the more homogeneous participation of the working class [@pichler_social_2009].
+Similar patterns have been found in terms of the composition of social ties, where the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes [@cepic_how_2020;@carrascosa_class_2023].
+Also, this segregation pattern holds during the life course, where the upper classes hold increasingly diverse social contacts in contrast to the stable networks of the working classes [@volker_social_2020].
+In contrast, studies that have focused on segregation suggest that the property dimension is much less permeable than authority-based boundaries, given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992] Similar studies have shown that the intermediate classes' higher permeability contrasts with the working class's more homogeneous networks, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social segregation.
+In contrast, the upper class is less permeable and homogeneous because it tends to self-select as a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
 
@@
 Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more isolated discussion networks [@summers_deliberating_2022].
-Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [e.g.
-@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [e.g.
-@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
+Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
 
@@
 They suggest that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
-Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and isolation because of the choices of others [@otero_open_2021, p.24].
+Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
 In this regard, if we assume that economic inequality sets the conditions for sociability, a possible consequence may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality is also affected by the extent of income differences.
@@
 First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.45, _p_ <.001).
-In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social isolation among the working classes and consequently drive higher redistributive preferences.
+In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social segregation among the working classes and consequently drive higher redistributive preferences.
 Second, Panel B depicts a positive but relatively weak and nonsignificant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).

### 2024-05-21 paper1_jiturra.Rmd
data and variables

@@
 For instance, it has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
-Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019]. Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006]. It is argued that continuous interaction with diverse people that characterize interpersonal services can reinforce egalitarian values [@kitschelt_occupations_2014].
+Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019]. Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
+It is argued that continuous interaction with diverse people that characterize interpersonal services can reinforce egalitarian values [@kitschelt_occupations_2014].
 In contrast, the vertical monitoring in managerial occupations and the relevance of autonomy in the case of self-employed can contribute to self-interested and conservative political views [@langsaether_more_2020;@oesch_electoral_2018].
@@
 
-Besides from the individual approach to attitude formation, we argue that people also form opinions in the economic domain based on their social relations.
-Despite limited research on the link between social ties and attitudes in the economic domain, we identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
+In addition to individual-based explanations, it is argued that people form opinions in the economic domain based on their social relations.
+Despite limited research on the link between social networks and redistributive preferences, I identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
 
@@
 This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@kelley_class_1995].
-Here, the initial argument is that people form their beliefs through the individual, family, friends, and coworkers’ experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
+Here, the initial argument posits that people form their beliefs through the individual, family, friends, and coworkers’ experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
 467].
 From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information that ultimately shapes their perceptions of inequality [@mijs_is_2021].
-Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more isolated discussion networks [@summers_deliberating_2022].
+Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more segregated networks [@summers_deliberating_2022].
 Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
@@
 758].
-Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties, where social influence processes can either align or polarize attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
+Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties, where social influence processes can either allineate or divide attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
 
@@
 A study in the United States showed that those tied to the upper class through parental relations support redistribution and progressive taxation less than those with working-class family backgrounds [@lee_consider_2023].
-In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties polarizes preferences between lower and upper classes.
+In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties divides preferences between lower and upper classes.
 In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
 
-In summary, we argue that class-embedded social relations play a substantial role in shaping support for redistribution.
-In this sense, the tendency to form homophilous social ties in terms of social class reinforces attitudes and consolidates opinion similarity.
-Thus, we hypothesize that segregation in similar class environments polarizes individual class interests so that segregated lower (upper) classes hold more (less) redistributive preferences ($H_1$).
-
-##  Consequences of Economic Inequality on Social Networks and Redistributive Preferences
-
-### Consequences of Economic Inequality on Social Networks
-
-The consequences of inequality in social relationships are diverse.
-Theoretically, it has been stated that economic inequality deepens material and symbolic differences between members of a society, where those in the most favored positions generally become more distant from those with access to fewer resources.
-Consequently, lower resources can constrain or discourage people from actively participating in social life, ultimately affecting the chances of meeting others with different economic conditions and lifestyles [@neckerman_inequality_2007, p.
-344].
-In this discussion, one approach has stressed the role of subjective experiences of inequality in social relations, arguing that a broader gap in economic resources has consequences on perceived competition and status anxiety [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024].
-Therefore, driving stronger experiences of relative deprivation undermines trust in others, given the difficulties of setting shared goals and perceiving others as part of a collectivity that pursues the common good [@salgado_expectations_2021].
-In contrast, the neo-materialist approach sets the attention on resource availability and attributes much less importance to subjective experiences, arguing that more economically equal societies are also characterized by extended welfare institutions that seek to diminish the consequences of unequal access to resources that provide better conditions for people to be socially engaged by improving social trust and individual well-being [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
-In sum, living in more unequal societies goes hand in hand with more extraordinary experiences of uncertainty, which at the same time may be hindered by a lack of trust in the broader social context, affecting the motives to participate in social activities that play a fundamental role in establishing ties between dissimilar groups, either by status or social class [@lancee_diversity_2017].
-
-Empirically, the few studies on this subject share the assumption that economic inequality translates into social distance in terms of class and status positions, which is the basis for consolidating network segregation.
-Cross-national comparisons in Europe show that the patterns of participation and association in formal organizations, as well as those of informal networks in providing social support, are manifested in the form of complementarity or substitution according to the cultural relevance of family or friendship networks and the character of the welfare regime [@pichler_patterns_2007].
-By contrast, @pichler_social_2009 accounts for the role of income inequality on participation in formal and informal networks, showing that more unequal societies depress the extensiveness of formal participation but not the frequency.
-In addition, it is one of the few studies that show how, in more unequal societies, class differences in participation are deepened in the diversity of formal participation networks.
-Similarly, @lancee_income_2012 shows that economic inequality reduces participation.
-However, in formal networks, the inhibiting effect of inequality is better evidenced, being less relevant to participation in informal networks.
-In addition, they show that in more unequal societies, the stratification of participation by income level is strengthened, favoring those with greater resources and marginalizing the poorest.
-
-In contrast to studies on participation in formal and informal networks, recent research has emphasized economic inequality in the structure of interpersonal networks.
-For instance, @letki_getting_2015 argued that economic inequality may constrain access to more extensive networks and the chances of receiving support through them.
-First, they found that individuals in lower-income groups have smaller networks than those in wealthier groups and are less likely to access resources through them.
-However, as inequality increases, low-income individuals hold much more extensive family networks but are less inclined towards utilizing their social ties to access resources than middle- and higher-income groups.
-They suggest that "the poor see maintaining ties with a large extended family as crucial for accessing needed help, which they are unlikely to reach through non-kinship ties" [@letki_getting_2015, p.
-244].
-By contrast, @otero_differences_2023 found that income inequality is not directly associated with the network structure.
-However, they found that income inequality can enhance the relationship between educational level, occupational status, and the diversity of social ties.
-They suggest that income inequality can exacerbate social stratification, creating greater interdependence between cultural, economic, and social capital.
-Hence, they argue that the unique positions held by the upper classes enable them to navigate different social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
-In this regard, if we assume that economic inequality sets the conditions for sociability, a possible consequence may be that the degree of segregation in interpersonal networks and its influence on popular views about economic inequality is also affected by the extent of income differences.
-
-### Consequences of Economic Inequality on Redistributive Preferences
-
-As mentioned, economic inequality influences social relations overall or strengthens inequalities throughout the social structure.
-However, studies on redistributive preferences have provided mixed evidence of the direct impact of income inequality on support for redistribution [@evans_strong_2018;@trump_income_2023].
-In turn, an open discussion has been raised regarding why those in the upper social strata are more sensitive to changes in economic inequality than those in the lower strata.
-
-Theoretically, two approaches were considered in this discussion.
-On the one hand, some studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that, although the rational interest model maintains its general implications, there are nuances within the upper-income strata regarding their greater concerns about the negative externalities of economic inequality (e.g., crime), which ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Additionally, another body of literature has suggested that the differences among the affluent can be understood from a distributive justice framework that focuses on the justice evaluation under which economic resources are allocated [@liebig_sociology_2016].
-The central argument suggests that affluent groups are more sensitive to economic inequality changes as they perceive that the overall opportunity structure is affected.
-In contrast, low-income individuals tend to perceive that the ascribed characteristics are stronger in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
+In summary,  the tendency to form homophilous social ties regarding social class is expected to reinforce attitudes and consolidate opinion similarity.
+Empirically, a weak direct association between homogeneity and redistributive preferences is expected because class segregation does not distinguish between classes as it provides only the _overall_ degree of segregation.
+In contrast, the focus will be on how class-based network homogeneity is conditional to social class.
+In simpler terms, this is possible by examining the interaction between network homogeneity and social class.
+Precisely, this will indicate if being segregated into lower (upper) classes leads to stronger (weaker) redistributive preferences ($H_1$).
+
+## Economic Inequality as context for Class relations and Redistributive Preferences
+
+Studies that have stressed the role of economic inequality on the relationship between social class and redistributive preferences indicate that the lower and the upper classes react differently to rising economic inequality.
+Theoretically, political economy studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
+Conversely, the moral economy literature has suggested that the differences among the affluent can be explained as a matter of justice distributive evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016;@atria_economic_2020].
+Hence, affluent groups are more sensitive because they perceive that increasing inequality undermines opportunities for social mobility [@sachweh_criticizing_2017].
+Likewise, lower perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
+In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality.
+[@sachweh_why_2019, p.
 656].
-Likewise, it has been argued that perceived inequality of opportunity can motivate support for redistribution as a matter of justice in the conditions for getting ahead, showing that this is particularly present in individuals in higher socioeconomic positions [@kim_socioeconomic_2018].
-Therefore, if the degree of segregation in social networks is related to polarization in redistributive attitudes, we believe that income inequality might also play a role in the relationship between class relations and redistributive attitudes.
-
-Empirically, while an important part of the studies addressing the role of economic inequality and redistribution preferences has focused on income, it is also possible to find efforts that emphasize the role of social class.
-In the first case, comparative studies in various societies have demonstrated (1) the relevance of income position and (2) the sensitivity of high-income groups to material inequality [@Schmidt-Catran2016; @franetovic_preferences_2022; @finseraas_income_2009].
-However, class-based studies have contributed equally to the elucidation of this relationship.
-For example, @edlund_democratic_2015 established that the demand for state-organized redistribution reflects the level of political class conflict in a modern industrialized society.
-Thus, their argument suggests that inequality plays a key role in moderating these conflicts because there is evidence of greater political consensus supporting redistribution in societies with greater material inequality.
-They emphasize that social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
+
+Regarding social networks, prior studies have argued that social relations are directly linked to resource access and how these are distributed in society.
+For instance,  Neckerman & Torche [-@neckerman_inequality_2007, p.
+344] suggest that experiencing marginalization is deeply associated with the life chances to participate openly in social life, which can be exacerbated in contexts of greater material inequality.
+Also, economic inequality can lead to greater perceived status competition [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024], which in turn hampers the establishment of trustworthy social ties among those facing economic distress [@salgado_expectations_2021].
+In contrast, it has also been argued that societies with robust welfare institutions and lower economic inequality foster social engagement in civic and social activities, thereby enhancing social trust between citizens and bolstering social solidarity [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
+
+Empirically, comparative evidence shows that already-stratified access to social activities and diverse networks is strengthened in unequal societies
+[@lancee_diversity_2017].
+In this regard, @pichler_social_2009 show that class differences in participation in civic (formal) and family (informal) networks are deepened in more unequal societies.
+Similarly, @lancee_income_2012 have found that the stratified civic participation by income level is strengthened as inequality rises.
+Other studies have shown that low-income individuals hold more extensive close networks and rely on family ties to seek support in unequal societies but rely more on external ties to pursue resources [@letki_getting_2015].
+Likewise, economic inequality enhances stratified access to contact network diversity due to greater interdependence between cultural, economic, and social capital [@otero_differences_2023].
+Thus, the upper classes can navigate diverse social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
+
+It has been argued that state-organized redistribution reflects political class conflict in a modern industrialized capitalist society, and social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
 323].
-
-Similarly, @curtis_how_2015 suggest two possible implications for the class cleavage in redistributive preferences in contexts of rising economic inequality.
-One argument suggests that the decline in social cohesion expressed in trust, civic participation, and prosocial attitudes might undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
+In this line, economic inequality is crucial in moderating conflicts as it can impact the political consensus for supporting redistribution between classes.
+One potential implication is that the decline in social trust, civic participation, and prosocial attitudes could undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
 As a result, less cohesive societies can nurture stronger class polarization that undermines egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
-In contrast, the other argument posits that in the context of greater economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
+However, in contexts of rising economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
 66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
-Additionally, it has been suggested that the degree of perceived social conflict decreases in societies with lower material inequality and a predominant middle-class imaginery [@hertel_conflict_2022].
-Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class.
-
-To summarize, the current state of research has led us to establish two competing scenarios based on the reviewed evidence and theoretical assumptions regarding the role of economic inequality in the relationship between class-based segregation and redistributive preferences.
-On the one hand, if we assume that social relations are eroded in more unequal societies, social classes might be more distant due to lower social trust and participation in formal and informal networks.
-Therefore, one possible expectation is that in unequal societies, the influence of class segregation on redistribution preferences will be stronger ($H_{2a}$).
-In contrast, if we assume that economic inequality has unequal consequences for those in the bottom and top rungs of the class structure in terms of cross-class embeddedness.
-In that case, it might be possible that the working classes are equally segregated regardless of income inequality compared to the more diverse contact and activity networks of the upper classes.
-Likewise, in line with evidence that suggests that the upper classes tend to be more concerned about the causes and consequences of economic inequality, our alternative expectation is that inequality will mitigate the role of network segregation on redistribution preferences, particularly among the upper classes ($H_{2b}$).
+Additionally, it has been suggested that perceived social conflict decreases in societies with lower material inequality and a predominant middle-class imaginery [@hertel_conflict_2022].
+Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class [@curtis_how_2015].
+
+To summarise, it has been shown that economic inequality increases the dependency of network segregation with class positions, leading the working classes to be equally segregated regardless of income inequality compared to the increasingly diverse networks of the upper classes [@pichler_social_2009;@otero_differences_2023].
+Therefore, class-based network segregation in unequal societies might have a weaker association with redistributive preferences.
+Thus, economic inequality is expected to _mitigate_ the association of class-based network segregation with redistributive preferences ($H_{2}$).
 
@@
 However, Slovenia (SVN) was excluded from the analysis because the key dependent variable was not present in the questionnaire.
-Consequently, the present study comprises complete information on 31,191 individuals from 31 countries, representing a group of diverse societies in terms of socio-economic and institutional arrangements.
+Consequently, the present study comprises complete information on 32,529 individuals from 31 countries, representing a group of diverse societies in terms of socio-economic and institutional arrangements.
 
@@
 
-**Redistributive preferences**: Two indicators available in the questionnaire were used to measure redistributive preferences.
+Two indicators available in the questionnaire were used to measure redistributive preferences.
 First, support for government redistribution (1) is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and the egalitarian preferences represented by the item (2) 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
-Thus, based on previous research and the high degree of correlation between the indicators (_r_ = 0.7), we proceed to reverse-code and create a standardized average index ranging from 1 to 100, where higher values represent greater redistributive preferences [@svallfors_government_2013].
-
-**Social class**:  The Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme is employed [@Erikson1992;@Erikson1979], one of the most consistent and validated measure for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
-Thus, based on the recently developed DIGCLASS algorithm, we draw on the available information regarding (i) occupations, (ii) self-employment status and (iii) the number of workers [@cimentada_digclass_2023].
-As a result, following previous research on political attitudes, a collapsed version of three big classes is employed, including the Service Class (I+II),  Intermediate Class (III+IV), and Working Class (V+VI+VII) [@sosnaud_class_2013;@edlund_influence_2003].
-
-**Class-based network segregation**: To create our measure of network homogeneity based on social class, we employed the position generator available in the questionnaire.
+Second, due to the correlation between the indicators (r = 0.7) and following previous research, the indicators were reverse-coded to compute the average values.
+They were then rescaled to create an indicator that ranges from 0 to 100, where higher values reflect stronger redistributive preferences [@svallfors_government_2013].
+
+The Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme is employed [@Erikson1992;@Erikson1979] for measuring social class.
+The EGP is one of the most consistent and validated measures for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
+Therefore, using the recently developed DIGCLASS algorithm [@cimentada_digclass_2023],  information regarding (i) occupational codes, (ii) self-employment status, and (iii) the number of workers was used to classify respondents into class positions.
+In line with previous research on political attitudes, this study utilizes a collapsed version of three classes [@sosnaud_class_2013;@edlund_influence_2003].
+Therefore, the class scheme contemplates the (i) Service Class (Higher and Lower managerial and professionals), (ii) Intermediate Class (Routine nonmanual and Self-employed), and (iii) Working Class (Manual supervisors, skilled manual and unskilled manual).
+
+The position generator is employed to create our measure of network homogeneity based on social class.
 This instrument has been widely employed in social capital studies, relying on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
-In this case, the position generator shows a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
+In this case, the position generator displays a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
 In the case of the indicator used here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
 Based on this, it is possible to obtain the total number of a person's social ties.
-Subsequently, the occupations were classified into three groups resembling social class positions [@otero_open_2021].
-First, the Lawyer, Executive of a large firm, and Human resource manager are classified as high-status.
-Then, a School teacher, Police officer, and Nurse are considered as intermediate-status.
-Finally, a car mechanic, bus driver, hairdresser, and home or office cleaner are considered low-status occupations.
-
-After this, we calculated the number of social ties for each status group.
-Consequently, the group closer to their class position obtains a proxy of the number of ingroup social ties.
-Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
-Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are similar (homogeneity).
-In substantial terms, higher values represent greater social distance from other social classes in society.
-
-As suggested recently, we have selected a set of control variables based on substantive reasoning informed by the current state of research on social networks and redistributive preferences [@kohler_control_2024].
+Subsequently, the occupations are classified into three groups resembling social class positions [@otero_open_2021;@sapin_issp_2020].
+First, the (i) lawyer, (ii) executive of a large firm, and (iii) human resource manager are classified as high-status.
+Second, the (iv) school teacher,  (v) police officer, and (vi) nurse are considered intermediate-status.
+Third, (vii) car mechanic, (viii) bus driver,  (iv) hairdresser, and (v) home or office cleaner are low-status occupations.
+
+As the network status groups are employed as proxies of social class positions, the number of similar or ingroup social ties is calculated according to the respondents' class position and provides the absolute number of similar ties.
+Subsequently, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
+Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are *similar* (homogeneity).
+In substantial terms, higher values represent higher social distance from other social classes in society.
+
+Regarding control variables, the number of social ties is included to guarantee that the observed influence of network homogeneity is independent of network size.
+Second,  socioeconomic characteristics are sequentially incorporated in the models as they represent the current social status in terms of income, educational skills, and labor market risk [@meltzer_rational_1981;@kitschelt_occupations_2014;@hausermann_highskilled_2015].
+In addition, gender, age, and marital status are included in all models as a sociodemographic characteristic to control for the potential influence of gender norms and life course events on attitudes [@alesina_preferences_2005;@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
+
+<!-- As suggested recently, we have selected a set of control variables based on substantive reasoning informed by the current state of research on social networks and redistributive preferences [@kohler_control_2024].
 Our estimations incorporate studies on social capital, network size, and social trust.
@@
 Finally, besides serving the self-interest of unionized working-class members, unions also function as political socialization agents, nurturing egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
-
-Sociodemographic characteristics play a significant role in shaping prosocial attitudes.
+-->
+
+<!-- Sociodemographic characteristics play a significant role in shaping prosocial attitudes.
 Women, for instance, often demonstrate a greater capacity for empathy, motivating them to engage in more communal and relational behavior compared to men [@eagly_his_2009].
@@
 This suggests that marital ties serve as a support network through which individuals can mobilize resources and social support [@alesina_preferences_2005].
+-->
 
@@
 In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
-Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].
+Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].`
 

### 2024-05-22 paper1_jiturra.Rmd
save commit

@@
 For instance, it has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
-Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019]. Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
+Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019].Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
 It is argued that continuous interaction with diverse people that characterize interpersonal services can reinforce egalitarian values [@kitschelt_occupations_2014].
@@
 To summarise, it has been shown that economic inequality increases the dependency of network segregation with class positions, leading the working classes to be equally segregated regardless of income inequality compared to the increasingly diverse networks of the upper classes [@pichler_social_2009;@otero_differences_2023].
-Therefore, class-based network segregation in unequal societies might have a weaker association with redistributive preferences.
+Consequently, it is expected that  class-based network segregation in unequal societies might have a weaker association with redistributive preferences.
 Thus, economic inequality is expected to _mitigate_ the association of class-based network segregation with redistributive preferences ($H_{2}$).
+
+<!-- A simplified framework of the hypotheses is shown in Figure X. -->
 
@@
 The primary societal characteristic under examination is the current levels of economic inequality, for which we have utilized the Gini Index (post-taxes and transfers) sourced from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
-Additionally, two contextual variables have been incorporated as controls in the multilevel models.
-Firstly, economic prosperity has been considered to ensure consistency in the estimates for economic inequality, drawing from the World Income Inequality Dataset (WID) [@Schmidt-Catran2016; @finseraas_income_2009].
-Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state has been included [see @edlund_democratic_2015].
-This measure, as an index, considers three dimensions: (i) tax revenue as a percentage of gross domestic product (GDP) [@ilo_world_2022]; (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022]; and (iii) the current level of redistribution [@solt_measuring_2020].
+Additionally, two contextual variables are incorporated as controls in the multilevel models.
+Firstly, employing the Gross Domestic Product (GDP) available in the WID ensures consistency in the economic inequality estimates independently of economic property [@Schmidt-Catran2016; @finseraas_income_2009].
+Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state is included [see @edlund_democratic_2015].
+The measure is a standardized and rescaled indicator from 0 to 100 that combines (i) tax revenue as a percentage of GDP [@ilo_world_2022], (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022], and (iii) the current level of redistribution [@solt_measuring_2020].
 
@@
 Multilevel linear models account for the hierarchical structure of the data, where individuals are nested within countries.
-Therefore, our first analysis begins with estimating the null model by declaring the nested structure using random intercept.
-This initial model allows us to assess the intraclass correlation, revealing that 13.7% of the variance in redistributive preferences can be attributed to belonging to higher-level units (countries).
-Subsequently, the micro-level models are estimated to determine the association between network homogeneity as well as the interaction with social class for testing our _segregation_ hypothesis ($H_1$).
+Therefore, the analysis begins with estimating the null model by declaring the nested structure using random intercept.
+This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to belonging to higher-level units (countries).
+Subsequently, the micro-level models are estimated to determine the association between network homogeneity and the interaction with social class to test the _segregation_ hypothesis ($H_1$).
 Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class to determine whether economic inequality moderates the effect of the micro-level interaction ($H_2$).
-Therefore, we estimate a three-way cross-level interaction to determine if the current levels of income inequality affect the interactions between network homogeneity and social class.
-In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible problems of collinearity [@hox_multilevel_2010].
-Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].`
+Therefore, a three-way cross-level interaction is estimated to determine if income inequality moderates the interaction between network homogeneity and social class [^1].
+In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible collinearity problems [@hox_multilevel_2010].
+Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations  [@hox_multilevel_2010].
+
+[^1]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
+Additionally, countries were classified into low, middle-low, middle, middle-high, and high-income inequality groups based on quintiles according to the Gini index.
+Hence, country-fixed effects regressions are used to control for the cross-country differences and observed and unobserved societal characteristics.
+The results are consistent with the multilevel estimations.
 
@@
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+set.seed(1234)
 options(ggplot2.discrete.fill = set1)
@@
        caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, and marital status are included as controls. Standard errors in parentheses. %stars",
+       custom.note = "\\item Note: Models include sampling weights. Gender, age, and marital status are included as controls. Standard errors in parentheses. %stars",threeparttable = T,
        caption.above = T,leading.zero = T,
@@
        use.packages = F)
-# performance::check_collinearity(digclas1_VW_6)
-# performance::check_model(digclas1_VW_6,check="vif")
+# performance::check_collinearity(digclas1_VW_5)
+# performance::check_model(digclas1_VW_5,check="vif")
+# performance::icc(digclas1_VW_5)
+sjPlot::tab_model(digclas1_VW_5, show.se = F, show.std = TRUE, show.stat = F)
 ```
@@
        caption = paste("(\\#tab:table2)","Multilevel models for Income Inequality, Network segregation and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
+       custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
        custom.coef.map = ccoef,
@@
 
-First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_three_2003] for each occupation of the position generator are calculated.
+First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010] for each occupation of the position generator are calculated.
 Second, the ISEI score of the respondent (R's) is subtracted from the average ISEI points of the personal network.

### 2024-06-03 paper1_jiturra.Rmd
ediciones v2

@@
 # date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-date: "`r format(Sys.Date(), '%d %B %Y')`"
+date: "`r format(Sys.Date(), '%d %b %Y')`"
 author:
@@
 abstract: | 
-  | Escalating economic inequality has increased attention to the link between class-based social ties and redistributive preferences in contemporary societies.
-However, social classes are not equally affected by inequality regarding their chances of establishing cross-class social relations.
-While those in the upper and middle classes have greater access to economic and diverse social ties, the working class has been disproportionately affected by social exclusion.
-Consequently, this leads to a growing divide between their lives and the lives of others, consolidating segregated lifeworlds.
-Previous research has shown that the link between class relations and redistributive preferences can be enriched from a network perspective.
-Meeting people from diverse class positions can help individuals become more aware of the lifestyles and worldviews of others.
-On the one hand, when upper-class networks become more homogeneous, it can lead to lower empathy toward those in need and less support for redistributive policies.
-On the other hand, when there is segregation in lower-class social networks, it can lead to greater marginalization and a higher demand for welfare support.
-This study explores how class-based network segregation influences redistributive preferences from a cross-national perspective, employing data from the International Social Survey 2017, which comprised 32,529 individuals in 31 societies.
-The regression analyses indicate that network homogeneity has a conditional influence on redistributive preferences based on social class.
-Homogeneous social networks in the working and intermediate classes increase redistributive preferences, while greater homogeneity in the upper classes reduces support for redistribution.
-In addition, in contexts of greater income inequality, the conditional influence of network segregation weakens, especially for the upper classes.
-Implications for the study of class relations and policy preferences are discussed.
+  | Escalating economic inequality has increased attention to the link between class relations and redistributive preferences in contemporary societies.
+Hoewever, economic inequality unevenly affects class relations and their influence on support for redistribution across societies.
+While those in the upper and middle classes reinforce their privileged access to resources and diverse networks, the working class has been disproportionately affected by social exclusion as inequality rises.
+Consequently, inequality consolidates segregated lifeworlds as it increases the divide between the lives and experiences of the different social classes.
+In this context, class relations represent the market situation of individuals and households as well as a network of social relations within and between classes.
+Meeting people from diverse class positions can help individuals become more aware of other people's lifestyles and worldviews.
+Homogeneous upper-class networks may lead to reduced empathy and solidarity towards those in need, resulting in decreased support for redistribution.
+Conversely, segregated lower-class social networks can lead to increased marginalization and reinforce support for redistribution.
+This study explores the relation of class-based network segregation and redistributive preferences employing cross-national data of 32,529 individuals in 31 societies.
+The main findings suggest that social class conditions the association of network homogeneity on redistributive preferences, where working class homogeneity drive stronger redistributive preferences, while greater upper-class homogeneity decreases support for redistribution.
+In addition, the conditional influence of network segregation weakens in unequal societies, especially for the upper classes.
+Implications for the study of class relations and political atttiudes are dicussed.
   | 
-  | **Keywords**: social networks, social class, redistributive preferences, income inequality
+  | **Keywords**: social networks, segregation, social class, income inequality, redistributive preferences 
 output:
@@
 header-includes:
-  - \usepackage{times}           # Times New Roman
+  # - \usepackage{times}           # Times New Roman
+  - \usepackage{helvet}
+  - \renewcommand{\familydefault}{\sfdefault} 
   - \usepackage{caption}
@@
                       message = FALSE,  # mensajes/avisos de librerias  
-                      cache = F,    # cache de los chunks,usar analisis pesados
+                      cache = T,    # cache de los chunks,usar analisis pesados
                       out.width = '100%',
@@
 
+```{r include=FALSE}
+wordcount<- rmdwc::rmdcount(files = "paper1_jiturra.Rmd")
+wordcount$words
+```
+
+**Word count**:  `r wordcount$words`
+
 \pagebreak
@@
 
-The study of redistributive preferences and social class has been mainly focused on the individual and household situation.
-Despite this, less attention has been paid to the role of social networks as socialization agents of attitudes toward redistribution.
-It has been stated that friendship and partnership ties tend to be homogeneous in their characteristics, expressing the tendency to form and consolidate homophilous social networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-Thus, the scope of class analysis in attitude formation urges to be extended to stress the role of social ties and segregation as they involve social processes, such as class identity formation, internalization of shared norms, conflict, and cooperation between classes [@Svallfors2006].
-In this respect, recent research has argued that the degree of segregation in the composition of social ties can influence opinions about economic inequality as they function as a window for learning about the lifestyles, economic conditions, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
-However, there is still a knowledge gap to disentangle the network mechanisms involved in political attitude formation about the role of government in enacting redistributive policies to strive against economic inequality [@mccall_americans_2009].
-
-The class composition of network ties can influence opinions on redistributive policies, but also the degree of segregation from other social classes in more homogeneous social networks can strengthen the class divide in redistributive preferences  [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+During the past decades, the few cross-national studies on redistributive preferences and social class have predominantly focused on the situation of individuals and households [@lindh_class_2020].
+Nonetheless, little attention has been paid to the network mechanisms involved in how individuals form their opinions regarding economic inequality and redistributive policies.
+On the one hand, sociologists have formerly demonstrated that homophily profoundly drives individuals to form similar social ties that consequently nurture social network segregation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+In contrast, it is also known that opinions about economic inequality can be affected by class segregation as it provides a window for learning about the economic conditions, lifestyles, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
+Despite this, it can be argued that the scrutiny of redistributive preferences can be enhanced by broadening the comprehension of class relations from a network perspective, providing a comprehensive manner to understand processes of shared norm internalization, class identity formation, and collective solidarity [@Svallfors2006;@goldthorpe_sobre_1992].
+In this regard, the present study examines the relationship between class-based network segregation and redistributive preferences in cross-national comparison, focusing on the role of economic inequality as a moderator of the claimed influence of class relations on support for redistribution.
+
 While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention should be devoted to understanding the role of social environments in class relations.
@@
 In addition, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-
-Besides the individual dynamics, little is known about how contextual factors affect the relationship between networks and redistributive preferences.
-Previous studies have shown that wider economic gaps lead to segregated forms of social participation and status composition of social networks [@pichler_patterns_2007;@otero_space_2022].
-Indeed, economic inequality reinforces the stratified access to social activities and the social distance between social classes, resulting in an increasing marginalization of the lower classes and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
-Studies on the class-attitude link posit that economic inequality is crucial for understanding how class relations are reflected in redistributive demands as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-The main finding drawn from these studies is that the upper classes tend to hold more egalitarian attitudes in contexts of high inequality, while the attitudes of the working class remain stable regardless of inequality levels.
-In this discussion, the moral economy explanation argues that the upper classes are more concerned about the integrity of resource allocation procedures as a matter of distributive justice [@sachweh_why_2019].
-Conversely, political economy research suggests that the upper classes are more likely to support redistribution policies due to the negative consequences of inequality [@dimick_altruistic_2017].
-
-In this context, to our knowledge, no research has comparatively stressed the role of economic inequality in the relationship between network segregation and redistributive preferences.
-Therefore, the present study aims to answer two research questions.
-First, at the micro-level, what is the role of class-based network segregation on redistributive preferences?
-Secondly, at the macro level, to what extent does economic inequality condition the relationship between class-based network segregation and redistributive preferences?
-To address these questions, we have analyzed data from the International Social Survey Program (ISSP) 2017, which includes a sample of 32,529 individuals across 31 societies.
-In this regard, the ISSP presents a nonprecedence opportunity as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
+In this regard, besides the leverage of individual class position, recent efforts have pointed out that whereas the class positions of network ties do affect redistributive preferences, the degree of segregation in a homogeneous class environment can drive attitudes to become even stronger [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+
+While network segregation intensifies the already established class divide in redistributive preferences, little is known about how contextual factors affect the association of class-based network segregation and support for redistribution.
+On the one hand, studies on the class-attitude link posit that economic inequality is crucial for understanding how class relations are mirrored in redistributive demands as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
+A consistent finding on this matter is that the upper classes tend to hold more egalitarian attitudes in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
+On the other hand, income inequality leads to more segregated forms of social participation and network composition [@pichler_patterns_2007;@otero_space_2022].
+Indeed, inequality reinforces the stratified access to social activities and widens the distance between classes, resulting in an increasing marginalization of the lower classes and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
+Nevertheless, current efforts to examine the impact of income inequality have primarily concentrated on either social networks or support for redistribution.
+A key question that remains unanswered is the extent to which broader economic disparities can influence the relationship between class-based network segregation and support for redistribution within a comprehensive framework.
+
+Thus, as no research has comparatively stressed the role of economic inequality in the relationship between class-based network segregation and redistributive preferences, the present study aims to answer two questions:
+
+(1) How does class-based network segregation affect redistributive preferences? 
+(2) To what extent does economic inequality moderate the relationship between class-based network segregation and redistributive preferences?
+
+For the present investigation, a data sample of 32,529 individuals across 31 societies from the International Social Survey Program (ISSP) 2017 is utilized.
+The ISSP presents a nonprecedence opportunity as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
 
@@
 
-Over the past decades, the study of redistributive preferences in industrialized societies has consistently demonstrated the importance of social class as a key explanatory factor  [@lindh_class_2020, p.
+Over the past decades, the study of political attitudes in industrialized societies has consistently demonstrated the relevance of social class as a driver of public opinion [@lindh_class_2020, p.
 421].
-Specifically, class positions have been shown to significantly influence individual opinions on the government's role in various aspects of the economic sphere, such as reducing income disparities or enhancing opportunities for those in economic distress [@mccall_americans_2009].
+In this view, the role of class goes beyond the market situation of individuals but drives collective economic interests and moral views about the role of the market and the state [@Svallfors2006].
+Here, what has been understood as redistributive preferences entail the public responses to economic inequality regarding the sphere of the role of government actions in aspects such as the reduction of income differences or enhancing opportunities for those in economic despair  [@mccall_americans_2009].
 
 However, class-based explanations of redistributive preferences have mainly been, but not exclusively, focused on the individual or household situation.
-For instance, it has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
-Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019].Another group of studies has suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can also imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
-It is argued that continuous interaction with diverse people that characterize interpersonal services can reinforce egalitarian values [@kitschelt_occupations_2014].
-In contrast, the vertical monitoring in managerial occupations and the relevance of autonomy in the case of self-employed can contribute to self-interested and conservative political views [@langsaether_more_2020;@oesch_electoral_2018].
-
-While our understanding of how social class influences public opinion on market-based resource distribution [@andersen_preferences_2018;@lindh_public_2015] and government income redistribution [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010;@Svallfors2006] is substantial, there remains a significant gap in our knowledge about the impact of class-based social relations from a network perspective on redistributive preferences.
+It has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
+Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019].
+Other approaches have suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
+For instance, continuous and diverse social interactions that characterize interpersonal services can drive empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
+In contrast, the vertical monitoring in managerial occupations and the relevance of autonomy in the case of self-employed fortify self-interested and conservative political views [@langsaether_more_2020;@oesch_electoral_2018].
+
+Empirically, the current understanding of the class divides on redistributive preferences is extensive [@andersen_preferences_2018;@lindh_public_2015; @curtis_how_2015;@langsaether_more_2020;@brooks_why_2010;@Svallfors2006].
+Nevertheless, besides the market situation of individuals and their households, including class-based social ties raises the relevance of the _class situation_ as it comprises both economic interests and life chances that motivate communal action beyond the individualistic lens [@weber_class_2011, pp.
+57-59].
+Therefore, the role of social relations on redistributive preferences from a network perspective needs to be developed beyond mere resource interchanges, but as part of the sociability practices that structure class relations.
 
@@
 
-It is possible to argue that class relations represent not only resource-based distinctions but also patterns of sociability and exchange observed in the differentiation of social ties.
+It can be argued that class relations not only represent resource-based distinctions but also patterns of sociability observed in the differentiation of social ties.
 Class relations can also be understood as the degree of cross-class relationship as a structural characteristic of a society, representing a network of social ties between different class positions [@blau_macrosociological_1977].
 Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001, p.416].
-Here, friendship and family tend to be homogeneous in terms of their demographic characteristics that simultaneously intersect with socioeconomic status and class [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
-Acknowledging that socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951], we argue that attitudinal similarity is the result of segregated social relations, which in turn are strongly linked to structural processes of differentiation that ultimately demarcate the opportunities in the formation of diverse social ties [@feld_focused_1981].
-
-In the discussion on the class composition of social networks, it is possible to find two approaches.
-On the one hand, one approach has emphasized the role of diversity as the degree of connectedness to dissimilar occupations as social positions that vertically represent access to resources embedded in social networks [@lin_social_2007].
-However, diversity is defined as the rate of dissimilar ties or the total ties to certain groups that do not necessarily count with a reference position to describe the network composition.
-On the other hand, a second approach has underscored the role of network segregation, which has been described as lacking cross-class network ties and is conceptually more proximate to the homophily principle because it is anchored in individual class positions [@otero_open_2021].
+Hereby, friendship and family ties are prone to be homogeneous in terms of class and demographic characteristics, but distant ties play the role of bridging individuals to other different social groups and contribute to network diversity [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
+In this sense, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951].
+Nonetheless, it can be argued that attitudinal similarity is the result of segregated social relations, which in turn are linked to structural processes of differentiation that also demarcate the boundaries to form ties with other social positions [@feld_focused_1981].
+
+It is possible to find two approaches in the study of class relations from a network approach.
+On the one hand, it has emphasized the role of _diversity_ as the degree of connectedness to dissimilar occupations that vertically represent access to resources embedded in social networks [@lin_social_2007].
+However, diversity is defined as the rate of dissimilar ties within the network that do not necessarily count with a reference position to describe the network composition.
+A second approach has underscored the role of _segregation_ as the lack of cross-class network ties.
+This perspective is conceptually closer to homophily as it is anchored in individual class positions and has empirically been addressed through the concept of network homogeneity [@otero_open_2021].
 
@@
 Similar patterns have been found in terms of the composition of social ties, where the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes [@cepic_how_2020;@carrascosa_class_2023].
-Also, this segregation pattern holds during the life course, where the upper classes hold increasingly diverse social contacts in contrast to the stable networks of the working classes [@volker_social_2020].
-In contrast, studies that have focused on segregation suggest that the property dimension is much less permeable than authority-based boundaries, given that class interests increase the social distance between proprietors and workers, while the intermediate class position of supervisors and contact frequency with workers make friendship tie formation more likely [@wright_relative_1992] Similar studies have shown that the intermediate classes' higher permeability contrasts with the working class's more homogeneous networks, suggesting that their limited resources and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social segregation.
+Also, this stratified network structure holds during the life course, where the upper classes hold increasingly diverse social contacts in contrast to the stable networks of the working classes [@volker_social_2020].
+In contrast, studies that have focused on segregation suggest that the property dimension is much less permeable than authority-based boundaries, arguing that class interests increase the social distance between proprietors and manual workers, while the intermediate class position of supervisors jointly to their higher contact frequency with manual workers make friendship tie formation more likely [@wright_relative_1992].
+Similar studies have shown that the intermediate class holds higher permeability in contrast to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social segregation.
 In contrast, the upper class is less permeable and homogeneous because it tends to self-select as a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
@@
 
-In addition to individual-based explanations, it is argued that people form opinions in the economic domain based on their social relations.
-Despite limited research on the link between social networks and redistributive preferences, I identify two broad theoretical approaches that have discussed the role of the social environment in attitude formation.
-
-On the one hand, one approach accentuates the role of beliefs about economic inequality rooted in social comparison processes as an explanation through which people form opinions about redistributive policies [@condon_economic_2020].
+Besides individual class-based mechanisms, it can be argued that their social relations represent a relevant factor in attitude formation.
+Particularly, despite limited research on the link between social networks and redistributive preferences, two theoretical approaches have discussed the role of social relations in attitude formation: reference groups and class-based networks.
+
+It has been stated that perceptions about economic inequality rooted in social comparison processes with reference groups can explain the formation of redistributive preferences [@condon_economic_2020].
 This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@kelley_class_1995].
-Here, the initial argument posits that people form their beliefs through the individual, family, friends, and coworkers’ experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of reference groups [@Evans1992, p.
+The argument posits that people form their beliefs through family, friends, and coworkers' experiences instead of the whole society, which is described as an availability heuristic that systematically biases inferences about inequality based on the homophily of these reference groups [@Evans1992, p.
 467].
-From this perspective, how people infer the social world is linked to the degree of segregation in their immediate social environment, which influences the intensity and character of the information that ultimately shapes their perceptions of inequality [@mijs_is_2021].
-Thus, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more segregated networks [@summers_deliberating_2022].
-Despite this, we argue that this research field has been more focused on the cognitive dimension of preference formation through inequality perceptions, either relying on surveys [@cansunar_who_2021;@garcia-castro_perceived_2022] or experimental manipulations [@Cruces2011;@becker_significant_2021] rather than empirically addressing the role of class segregation in social networks and its claimed influence on attitudes in the economic domain.
-
-In contrast, it has been suggested that the lens of a network approach provides a better picture of class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
+Therefore, inferences about the social world are linked to the degree of segregation in the immediate social environment of a person, which influences the intensity and character of the information that ultimately shapes inequality perceptions [@mijs_is_2021].
+Accordingly, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more segregated networks [@summers_deliberating_2022].
+Nevertheless, I argue that this body of research has been mainly focused on the cognitive dimension of preference formation through inequality perceptions or beliefs rather than straightforward addressing the claimed influence of network segregation on redistributive preferences [@cansunar_who_2021;@garcia-castro_perceived_2022;@Cruces2011;@becker_significant_2021].
+
+In contrast, a network approach provides a better picture of class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
 550].
-This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to individual or household material well-being, cultural perspectives, and political preferences that structure broader social experiences [@morris_attenuation_1996, p.
+More precisely, it has been argued that redistributive preferences are influenced by the class situation of both the individual and network ties, where social influence processes can either allineate or divide opinions according to the contacts' class position and how segregated contact opportunities are [@vargassalfate_contact_2023].
+This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to individual and household material well-being, cultural perspectives, and political preferences that structure broader social experiences [@morris_attenuation_1996, p.
 48].
-Furthermore, social integration can be affected in societies with lower contact opportunities between different social classes, where social distance among them widened by extreme inequality can create an “empathy gulf” that comprises barriers to imagining others’ lifestyles [@sachweh_moral_2012].
-In this matter, spatially segregated interactions may nurture doubts about worthiness when the lower classes contrast themselves with the lifestyles of the upper classes, which might undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
-Consequently, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
+Furthermore, social integration can be affected in societies with lower contact opportunities between different social classes, creating an "empathy gulf" that comprises barriers to imagining others' lifestyles in contexts of rising inequality [@sachweh_moral_2012].
+Thus, spatially segregated interactions may nurture doubts about worthiness when the lower classes contrast themselves with the lifestyles of the upper classes, which in turn can undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
+As a result, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
 758].
-Thus, we suggest that attitudes towards redistribution may be influenced by the class situation of both the individual and network ties, where social influence processes can either allineate or divide attitudes according to the characteristics of groups and the level of segregation that allows factual contact opportunities.
-
-In recent years, we have seen an increase in this network turn of class analysis, contributing to unraveling the relationship between the composition of social ties and attitudes toward inequality.
-In this regard, it has been shown that the degree of contact between different classes has shown that individuals of the lower class interacting with those of the upper classes may consider economic inequality as justifiable, whereas interactions with those of the lower class may prompt individuals from different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
+
+<!-- The attention has increased in recent years to how social ties are connected to attitudes toward inequality, and it has been shown that frequent interactions between classes can lead to different attitudinal changes depending on the individuals' social class.
+For instance, contact with the upper classes drives higher justification of economic inequality among the lower classes, whereas interactions with lower classes may prompt the different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
 Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images of the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
-
-In addition, studies that directly addressed the relationship between networks and social classes have been consistent with previous findings.
-For instance, evidence from Sweden suggests that people tend to assimilate their opinions according to their surrounding friends and acquaintances, which is reinforced by class homophily, where higher contacts in the managerial class negatively influence support for redistribution, while ties to the working class increase it regardless of the individual class position suggesting that “individuals take an impression from others and modify their attitudes accordingly” [@lindh_missing_2021, p.
+-->
+
+The class position of surrounding family members, friends, and acquaintances influences redistributive preferences as they function as socialization agents that can be bolstered in segregated social networks.
+In principle, political attitudes are connected to class interests and norms as they are nurtured in the family of origin during childhood and early adulthood.
+For instance, it has been shown that individuals with network ties to the upper class through parental connections support redistribution and progressive taxation less than those from working-class family backgrounds [@lee_consider_2023].
+Also, as households share risk according to the class position of their members, redistributive preferences are not only affected by their family background but also by partners' class positions.
+For example, @paskov_crossclass_2022 found that working-class ties bolster redistributive preferences but decrease with upper-class ties, becoming much more intense when the class positions of individuals, partners, and parents form a more homogeneous network.
+Besides, @lindh_missing_2021 found that including friends and acquaintances in the network structure leads individuals with higher ties to the managerial class to decrease their redistributive preferences compared to those with higher sociocultural and working-class ties, suggesting that people tend to consider and adjust their attitudes according to the class position of their contacts [@lindh_missing_2021, p.
 698].
-Similarly, additional socialization sources are cross-class ties through family members.
-In this sense, the family of origin is crucial for political socialization, where class interests and norms are nurtured in childhood and early adulthood.
-A study in the United States showed that those tied to the upper class through parental relations support redistribution and progressive taxation less than those with working-class family backgrounds [@lee_consider_2023].
-In addition, @paskov_crossclass_2022 argues that the class position of family and partners shapes preferences, while households share risk according to the class position of their members, where class homogeneity in ties divides preferences between lower and upper classes.
-In contrast, this gradient is blurred as heterogeneity increases according to the class position of the partner and family of origin.
-
-In summary,  the tendency to form homophilous social ties regarding social class is expected to reinforce attitudes and consolidate opinion similarity.
+
+In summary, the tendency to form homogenous social ties regarding social class is expected to reinforce attitudes and consolidate opinion similarity.
 Empirically, a weak direct association between homogeneity and redistributive preferences is expected because class segregation does not distinguish between classes as it provides only the _overall_ degree of segregation.
-In contrast, the focus will be on how class-based network homogeneity is conditional to social class.
-In simpler terms, this is possible by examining the interaction between network homogeneity and social class.
+In contrast, the focus is on how class-based network homogeneity is conditional to social class.
+Empirically, this can be observed through the interaction between network homogeneity and social class.
 Precisely, this will indicate if being segregated into lower (upper) classes leads to stronger (weaker) redistributive preferences ($H_1$).
 
-## Economic Inequality as context for Class relations and Redistributive Preferences
+## Economic inequality as context for class relations and redistributive preferences
 
 Studies that have stressed the role of economic inequality on the relationship between social class and redistributive preferences indicate that the lower and the upper classes react differently to rising economic inequality.
-Theoretically, political economy studies have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution  [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Conversely, the moral economy literature has suggested that the differences among the affluent can be explained as a matter of justice distributive evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016;@atria_economic_2020].
-Hence, affluent groups are more sensitive because they perceive that increasing inequality undermines opportunities for social mobility [@sachweh_criticizing_2017].
+Theoretically, political economists have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
+Conversely, the moral economy literature in sociology has argued that the differences among the affluent can be explained as a matter of distributive justice evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016;@atria_economic_2020].
+Hence, affluent groups are more responsive because they perceive that increasing inequality harms the overall opportunity structure and social mobility chances [@sachweh_criticizing_2017].
 Likewise, lower perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
-In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality.
-[@sachweh_why_2019, p.
+In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
 656].
@@
 Regarding social networks, prior studies have argued that social relations are directly linked to resource access and how these are distributed in society.
-For instance,  Neckerman & Torche [-@neckerman_inequality_2007, p.
+Here,  Neckerman & Torche [-@neckerman_inequality_2007, p.
 344] suggest that experiencing marginalization is deeply associated with the life chances to participate openly in social life, which can be exacerbated in contexts of greater material inequality.
-Also, economic inequality can lead to greater perceived status competition [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024], which in turn hampers the establishment of trustworthy social ties among those facing economic distress [@salgado_expectations_2021].
-In contrast, it has also been argued that societies with robust welfare institutions and lower economic inequality foster social engagement in civic and social activities, thereby enhancing social trust between citizens and bolstering social solidarity [@lynch_income_2004;@uslaner_inequality_2005;@kragten_income_2017].
+Also, economic inequality can lead to greater perceived status competition [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024], which in turn hampers trustworthy social ties among the low-status individuals [@salgado_expectations_2021].
+In contrast, societies with robust welfare institutions and lower economic inequality foster social engagement in civic and social activities, thereby enhancing social trust between citizens and bolstering social solidarity [@uslaner_inequality_2005;@kragten_income_2017].
 
@@
 Likewise, economic inequality enhances stratified access to contact network diversity due to greater interdependence between cultural, economic, and social capital [@otero_differences_2023].
-Thus, the upper classes can navigate diverse social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
-
-It has been argued that state-organized redistribution reflects political class conflict in a modern industrialized capitalist society, and social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
+Thus, the upper classes are capable of navigating diverse social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
+
+Theoretically, previous research has stated that state-organized redistribution reflects political class conflict in a modern industrialized capitalist society, and social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
 323].
@@
 One potential implication is that the decline in social trust, civic participation, and prosocial attitudes could undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
-As a result, less cohesive societies can nurture stronger class polarization that undermines egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
-However, in contexts of rising economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
+As a result, less cohesive societies can nurture a stronger class divide in egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
+Nevertheless, in contexts of rising economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
 66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
-Additionally, it has been suggested that perceived social conflict decreases in societies with lower material inequality and a predominant middle-class imaginery [@hertel_conflict_2022].
+Additionally, in societies with lower material inequality and a predominant middle-class imaginery perceived social conflict decreases [@hertel_conflict_2022].
 Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class [@curtis_how_2015].
 
-To summarise, it has been shown that economic inequality increases the dependency of network segregation with class positions, leading the working classes to be equally segregated regardless of income inequality compared to the increasingly diverse networks of the upper classes [@pichler_social_2009;@otero_differences_2023].
+To summarise, here it is argued that economic inequality increases the dependency of network segregation with class positions, leading the working classes to be equally segregated regardless of income inequality compared to the increasingly diverse networks of the upper classes [@pichler_social_2009;@otero_differences_2023].
 Consequently, it is expected that class-based network segregation in unequal societies might have a weaker association with redistributive preferences.
@@
 
-Individual data from the International Social Survey Programme (ISSP) 2017, titled "Social Networks and Social Resources," is utilized [@issp_networks_2017].
-Established in 1984, the ISSP is a collaborative research project that conducts cross-national surveys on various topics related to social issues, attitudes, and values.
-Specifically, the ISSP 2017 survey includes questions on social ties and activities, evaluated through a position generator, as well as inquiries on social resources derived from network members.
-Additionally, respondents express their views on topics such as social trust and attitudes toward economic inequality.
-Initially, the dataset comprised 47,027 individual observations across 32 countries.
-However, Slovenia (SVN) was excluded from the analysis because the key dependent variable was not present in the questionnaire.
-Consequently, the present study comprises complete information on 32,529 individuals from 31 countries, representing a group of diverse societies in terms of socio-economic and institutional arrangements.
+Individual data from the "Social Networks and Social Resources"  module of the International Social Survey Programme (ISSP) from 2017 is employed [@issp_networks_2017].
+This module includes information on a broader range of topics linked to social networks, attitudes toward economic inequality as well as demographic and socioeconomic background characteristics.
+The initial dataset includes 47,027 individual observations from 32 countries.
+However, one country (Slovenia) is excluded from the study because the main dependent variables are not available.
+Subsequently, after applying listwise case deletion, the analytical sample is composed of 32,529 individuals in 31 countries.
 
@@
 Two indicators available in the questionnaire were used to measure redistributive preferences.
-First, support for government redistribution (1) is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and the egalitarian preferences represented by the item (2) 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
+First, (1) support for government redistribution is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and (2) egalitarian preferences represented by the item 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
 Second, due to the correlation between the indicators (r = 0.7) and following previous research, the indicators were reverse-coded to compute the average values.
@@
 
-The Erikson-Goldthorpe-Portocarrero (EGP) Class Scheme is employed [@Erikson1992;@Erikson1979] for measuring social class.
-The EGP is one of the most consistent and validated measures for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in regions of the industrialized world, as well as in countries of late industrialization [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
-Therefore, using the recently developed DIGCLASS algorithm [@cimentada_digclass_2023],  information regarding (i) occupational codes, (ii) self-employment status, and (iii) the number of workers was used to classify respondents into class positions.
-In line with previous research on political attitudes, this study utilizes a collapsed version of three classes [@sosnaud_class_2013;@edlund_influence_2003].
-Therefore, the class scheme contemplates the (i) Service Class (Higher and Lower managerial and professionals), (ii) Intermediate Class (Routine nonmanual and Self-employed), and (iii) Working Class (Manual supervisors, skilled manual and unskilled manual).
-
-The position generator is employed to create our measure of network homogeneity based on social class.
-This instrument has been widely employed in social capital studies, relying on the assumption that access to social resources is based on ties to different positions in the social structure following an ego-centered network approach [@lin_access_1986;@vandergaag_position_2008].
-In this case, the position generator displays a list of ten occupations where the respondent declares four possible options through which this tie is classified: "Family or relative", "Close friend", "Someone else I know", and "No one".
-In the case of the indicator used here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
-Based on this, it is possible to obtain the total number of a person's social ties.
-Subsequently, the occupations are classified into three groups resembling social class positions [@otero_open_2021;@sapin_issp_2020].
+For measuring social class, the Erikson-Goldthorpe-Portocarrero (EGP) class Scheme is employed [@Erikson1992;@Erikson1979].
+The EGP is one of the most consistent and validated measures for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in industrialized and late industrialized societies [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
+Therefore, relying on the DIGCLASS algorithm [@cimentada_digclass_2023], information about occupations, self-employment status, and number of employees is used to classify respondents into class positions.
+Following previous research, a collapsed version of three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
+Accordingly, the class scheme contemplates the Service Class (Higher and Lower managerial and professionals), Intermediate Class (Routine nonmanual and Self-employed), and Working Class (Manual supervisors, skilled manual and unskilled manual).
+
+The position generator is employed for measuring class-based network homogeneity.
+This instrument has been widely employed in social capital studies and follows an ego-centered approach where social ties to different hierarchical positions in the social structure provide access to social resources [@lin_access_1986;@vandergaag_position_2008].
+In this case, a list of ten occupations is displayed and the tie can be classified as "Family or relative", "Close friend", "Someone else I know", or "No one".
+Here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
+Consequently, the total number of social ties per respondent is obtained.
+Subsequently, the occupations are classified into three groups that closely resemble social class positions [@otero_open_2021;@sapin_issp_2020].
 First, the (i) lawyer, (ii) executive of a large firm, and (iii) human resource manager are classified as high-status.
-Second, the (iv) school teacher,  (v) police officer, and (vi) nurse are considered intermediate-status.
+Second, the (iv) school teacher, (v) police officer, and (vi) nurse are considered middle-status.
 Third, (vii) car mechanic, (viii) bus driver, (iv) hairdresser, and (v) home or office cleaner are low-status occupations.
 
-As the network status groups are employed as proxies of social class positions, the number of similar or ingroup social ties is calculated according to the respondents' class position and provides the absolute number of similar ties.
+As the network status groups are employed as proxies of social class positions, the number of similar or ingroup social ties is calculated according to the respondent class position and provides the absolute number of similar ties.
 Subsequently, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
@@
 
-Regarding control variables, the number of social ties is included to guarantee that the observed influence of network homogeneity is independent of network size.
-Second,  socioeconomic characteristics are sequentially incorporated in the models as they represent the current social status in terms of income, educational skills, and labor market risk [@meltzer_rational_1981;@kitschelt_occupations_2014;@hausermann_highskilled_2015].
-In addition, gender, age, and marital status are included in all models as a sociodemographic characteristic to control for the potential influence of gender norms and life course events on attitudes [@alesina_preferences_2005;@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
+First, the number of social ties is included to guarantee that the association of network homogeneity is independent of network size.
+Second,  socioeconomic characteristics are sequentially incorporated in the models as they represent the current social status through income, education, and labor market status [@meltzer_rational_1981;@kitschelt_occupations_2014;@hausermann_highskilled_2015].
+Third, gender, age, and marital status are included in all models as a sociodemographic characteristic to control for the potential influence of gender norms and life course events on attitudes [@alesina_preferences_2005;@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
 
@@
 
-The primary societal characteristic under examination is the current levels of economic inequality, for which we have utilized the Gini Index (post-taxes and transfers) sourced from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
+For measuring economic inequality the Gini index (post-taxes and transfers) from the World Income Inequality Dataset (WID) is employed [@alvaredo_world_2022].
 Additionally, two contextual variables are incorporated as controls in the multilevel models.
@@
 
-Multilevel linear models account for the hierarchical structure of the data, where individuals are nested within countries.
+Multilevel linear regression models are employed in all the analyses for accounting by the hierarchical structure of the data given that individuals are nested within countries.
 Therefore, the analysis begins with estimating the null model by declaring the nested structure using random intercept.
-This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to belonging to higher-level units (countries).
-Subsequently, the micro-level models are estimated to determine the association between network homogeneity and the interaction with social class to test the _segregation_ hypothesis ($H_1$).
-Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class to determine whether economic inequality moderates the effect of the micro-level interaction ($H_2$).
-Therefore, a three-way cross-level interaction is estimated to determine if income inequality moderates the interaction between network homogeneity and social class [^1].
-In the macro-level models, all the individual-level factors are group-mean centered (CWC) to mitigate possible collinearity problems [@hox_multilevel_2010].
+This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to belonging to higher-level units.
+Subsequently, the micro-level models are estimated to determine the association between network homogeneity and the interaction with social class to test hypothesis 1.
+Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class.
+In this set, a three-way cross-level interaction is estimated to determine if income inequality moderates the interaction between network homogeneity and social class to test hypothesis 2 [^1].
+In the latter model, all the individual-level variables are group-mean centered (CWC) to mitigate possible collinearity problems [@hox_multilevel_2010].
 Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations [@hox_multilevel_2010].
+For all the analyses, the package `lme4` for in the statistical package `R`  is employed [@bates_fitting_2015].
 
@@
 
+egal_class_diff <- df_plot %>%
+  dplyr::select(country3,egal2,dclass3res_V) %>% 
+  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "egal2") %>% 
+  mutate(diff_working_upper_egal = `Working Class` - `Service Class`) %>% 
+  dplyr::select(-`Working Class`, -`Service Class`,-`Intermediate Class`) %>% 
+  as.data.frame()
+
 df_plot <- 
@@
   left_join(df_region) %>% as.data.frame() %>% 
-  left_join(homo_class_diff)
+  left_join(homo_class_diff) %>% 
+  left_join(egal_class_diff)
 
@@
 For example, the differences between the service and the working class are close to 2.3 points in the United States.
-At the same time, Finland represents the average case in the distribution but is also one of the most polarized societies in terms of class-based differences in redistributive preferences, showing a gap of 14.1 points between the upper and the lower classes.
+At the same time, Finland represents the average case in the distribution but is also one of societies with the greater class divide in redistributive preferences, showing a gap of 14.1 points between the upper and the lower classes.
 Interestingly, Russian society depicts class differences similar to the U.S., with an average difference of 2.4 points.
@@
         legend.title = element_blank())  
-
+# mean(df_plot3$homclass)
+# sd(df_plot3$homclass)
 # ggsave(plot = last_plot(),filename = "slides-macro-homogen.png",device = "png",
@@
 However, it is worth to mention at least two interesting findings.
-First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.03), with Thailand being the society with higher levels of network segregation (M = 0.42), and Iceland the one of the lowest (M = 0.31).
+First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.08), with Thailand being the society with higher levels of network segregation (M = 0.43), and Iceland among lowest (M = 0.31).
 Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
-As noticed, in most cases observed, the general pattern is that the working class is highly homogeneous in their networks, except in the Philipines, where the intermediate class shows a slightly higher average homogeneity.
 In addition, the general pattern is that the service class is less segregated than the intermediate and working class.
-Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the middle and service classes are similar in their network homogeneity.
-Overall, one of the most substantial findings is that, without any exception, the working class is more segregated than the services class.
+Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the intermediate and service classes are similar in their network homogeneity.
+As noticed, in most cases observed, the general pattern is that the working class is highly homogeneous in their networks, except in the Philippines, where the intermediate class shows a slightly higher average homogeneity.
+Overall, one of the most substantial findings is that the working class is more segregated than the services class.
 
@@
 Moving to the bivariate macro relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, our main societal characteristic of interest.
-First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.45, _p_ <.001).
+First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.43, _p_ <.001).
 In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social segregation among the working classes and consequently drive higher redistributive preferences.
-Second, Panel B depicts a positive but relatively weak and nonsignificant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
+Second, Panel B depicts a positive but relatively weak and non significant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
 In other words, average homogeneity also tends to increase in societies with greater income gaps.
@@
 As an additional exploratory analysis (see Fig.
-\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.29, _p_<.01).
+\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.3, _p_<.01).
 In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
@@
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,
-       caption = paste("(\\#tab:table1)","Multilevel models for Class-based network segregation and Redistributive Preferences"),
+       caption = paste("(\\#tab:table1)","Multilevel models for network homogeneity and redistributive preferences"),
        custom.note = "\\item Note: Models include sampling weights. Gender, age, and marital status are included as controls. Standard errors in parentheses. %stars",threeparttable = T,
@@
 # performance::icc(digclas1_VW_5)
-sjPlot::tab_model(digclas1_VW_5, show.se = F, show.std = TRUE, show.stat = F)
 ```
@@
 The multilevel analysis results are shown in Table \@ref(tab:table1).
-Regarding our first hypothesis ($H_1$), our central argument is that class segregation has differential consequences on redistributive preferences.
+Regarding the first hypothesis, the central argument is that class segregation has differential consequences on redistributive preferences.
 In other words, the association between network homogeneity and redistributive preferences is conditional on class position.
@@
 Initially, as previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
-This association persists in Model 2, where we control for network size and social trust—two pivotal factors in establishing and consolidating interpersonal networks.
-However, after including social class in the analysis, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
-
-Subsequently, Model 4 incorporates socioeconomic status, employment status, and union membership characteristics.
+This association persists in Model 2, where we control for network size.
+However, after including social class in Model 3, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
+Subsequently, Model 4 incorporates income, education in years and employment status.
 As expected, socioeconomic status is negatively associated with redistributive preferences regarding household economic resources and educational credentials.
 In addition, we find that people outside the labor market do not differ significantly from those who are economically active in their preferences.
-In contrast, as expected, being unionized increases redistributive preferences compared to those who have never been union members.
-Then, Model 5 incorporates the social class of the respondent's partner if such information is available.
-Thus, it is observed that the social class of the partner follows a similar pattern to that of the respondent, where belonging to the working or intermediate class presents higher redistributive preferences.
-
-Finally, in Model 6, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
-Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
+Finally, in Model 5, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
+Based on Model 5, Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
 For the service class, the relationship is reversed, where more homogeneous networks for this social class decrease redistributive preferences.
-Altogether, these results provide evidence of our hypothesis, where a higher level of network segregation is related to a greater polarization of social class interests.
-
-```{r fig4, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class',warning=FALSE}
+Altogether, these results provide evidence in favor of hypothesis 1, where the class divide in redistributive preferences becomes stronger for individuals with more homogeneous social networks.
+
+<!-- estimate std.error  statistic            p.value  conf.low conf.high -->
+<!--  2.976180 0.8970721  3.3176597 0.0009077501054860  1.217951  4.734409 -->
+<!--  1.029445 1.1996805  0.8580992 0.3908376677138878 -1.321886  3.380775 -->
+<!-- -7.440596 1.1013920 -6.7556289 0.0000000000142217 -9.599284 -5.281907 -->
+
+```{r fig4, fig.dim=c(10,5),fig.cap='Interaction of network homogeneity and social class on redistributive preferences',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
                        c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
-                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
+                     c("Working Class","Intermediate Class","Service Class"))) +
   scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(50,80))+
+  scale_y_continuous(limits = c(55,80))+
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Network homogeneity",y="Redistributive preferences") +
+       x="Network homogeneity",y="Redistributive preferences (0 - 100)") +
   theme(legend.position = "none", legend.title = element_blank())
 
-# ggsave(plot = last_plot(),filename = "slides-predictions.png",device = "png",
-#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+ggsave(plot = last_plot(),filename = "slides-predictions.png",device = "png",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
 
 # int_homo <- digclas1_VW_7
-# plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
+# plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"),draw = F)+
 # labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-#   geom_hline(yintercept = 0,color="red",linetype=2)+
-#        x="Social Class",y="Redistributive preferences",title = "Conditional Marginal Effects for Network Homogeneity")
+#      x="Social Class",y="Redistributive preferences",title = "Conditional Marginal Effects for Network Homogeneity")+
+#   geom_hline(yintercept = 0,color="red",linetype=2)
 
@@
               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality")
 
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.7,
-       caption = paste("(\\#tab:table2)","Multilevel models for Income Inequality, Network segregation and Redistributive Preferences"),
+       caption = paste("(\\#tab:table2)","Multilevel models for income inequality, network homogeneity and redistributive preferences"),
        custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
@@
 Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (*p* > .05).
-Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05) while GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
-In other words, in Model 3, economic prosperity appears to depress redistributive preferences; however, when contextualized within a larger welfare state, greater redistributive preferences are observed.
-
-Finally, Model 4 incorporates the three-way interaction to determine whether the relationship established in $H_1$ is moderated by income inequality.
-The relationship observed at the micro level retains its original meaning, indicating that segregation in terms of network homogeneity polarizes the economic interests of the classes.
-Additionally, when observing how this relationship is moderated by the level of inequality in the country, it appears to mitigate, with its intensity decreasing as inequality increases.
-Figure \@ref(fig:fig5) illustrates how the relationship between network homogeneity and social class is more pronounced when inequality is low and gradually diminishes until it becomes almost absent when inequality is high.
-
-Overall, while Hypothesis 2a posited that greater income differences would amplify social segregation and, consequently, polarize redistributive preferences to a greater extent, the results provide evidence in favor of Hypothesis 2b.
-This suggests that inequality plays a mitigating role in class segregation regarding redistributive preferences.
-
-```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaccion Income Inequality, Network segregation and  Redistributive Preferences'}
+Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05).
+In contrast, GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
+In other words, in Model 3, economic prosperity appears to depress redistributive preferences.
+Nevertheless, higher redistributive preferences are observed in countries with more generous welfare states.
+
+Finally, Model 4 incorporates the three-way interaction to determine whether the interaction of network homogeneity and social class on redistributive preferences is moderated by income inequality.
+First, the relationship observed at the micro level retains its original meaning, indicating that segregation in terms of network homogeneity strengthens the class divide in redistributive preferences.
+Second, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
+To better illustrate this result, Figure \@ref(fig:fig5) depicts how the relationship between network homogeneity and social class is more pronounced in societies of lower income inequality and gradually diminishes as inequality increases.
+In other words, the results provide evidence in favor of Hypothesis 2, suggesting that the greater class divide in redistributive preferences observed in more segregated class-based social networks weakens as income inequality increases.
+
+```{r fig5, fig.dim=c(12,7),fig.cap='Three-way interaction of network homogeneity, social class and income inequality on redistributive preferences'}
 ### Predicted values homo*class*GiniD ---------------------------------------$
@@
   facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
+  labs(y = "Redistributive preferences (0 - 100)",
        x="Network homogeneity (CWC)",
@@
 -->
-In this research, we ask how class-based network segregation is related to preferences for redistribution and to what extent economic inequality conditions this relationship.
-In this context, the literature on interpersonal networks has shed light on how network structure harbors not only social resources [@lin_access_1986;@otero_open_2021] but also carries the capacity to establish niches that contribute to the formation of political opinions through social influence, as well as the degree of network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
-In this case, the micro-level relationship under scrutiny was that class-based network segregation does play a role in redistributive preferences.
-In contrast to evidence on the undermining role of network homogeneity on social cohesion [@otero_lives_2022], redistributive preferences are not the case.
-Indeed, we found that greater homogeneity in terms of social class has a polarizing effect on redistributive preferences because it has differentiated attitudinal consequences according to class position.
-In other words, for working-class members, homogeneity strengthens their redistributive preferences, while in the service class, homogeneity translates into even lower redistributive preferences.
-
-Our theoretical approach has established that social classes should be understood beyond labor market relationships but as relational networks that can provide an explanatory framework for attitude formation.
-Theoretically, what the literature has established as processes of social influence [@lindh_missing_2021] or political socialization [@lee_consider_2023] has echoed in how social closure in interpersonal networks generates distance between different social classes in terms of their redistributive preferences.
-Here, the extent to which social classes distance themselves in terms of network segregation indeed creates an "empathy gulf" [@sachweh_moral_2012] that can be observed in how the service class is less willing to take action to strive with inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments [@otero_power_2023], in contrast to the increasing redistributive pressures of the marginalized working class.
-Besides, as network homogeneity represents low cross-class ties, it can be argued that lower social integration [@blau_macrosociological_1977] can undermine social solidarity as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
-
-While the results are substantially consistent at the micro level, our theoretical framework established alternative scenarios regarding the role of economic inequality.
-In short, our competing hypothesis suggested that income inequality, which represents greater gaps in economic and social resources, should be related to class relations and redistributive preferences.
-In line with the social cohesion argument, it is suggested that social relations are undermined by economic inequality as it represents the distribution of available resources and, consequently, might _amplify_ the relationship between segregation and redistributive preferences given the increase in social distance between social classes.
-However, the evidence indicates the opposite as it shows that inequality _mitigates_ the micro-level relationship, which translates into a narrower class gap, mainly through changes in redistributive preferences in the service class.
-These results resonate with two key pieces of evidence on the role of inequality on (i) class relations and (ii) redistributive preferences.
-It has been argued that in unequal societies, the better-off class position tends to become more egalitarian in their stances on economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
-Additionally, recent cross-national studies suggest that upper classes can consolidate their distinctive position while their advantages allow them to navigate diverse networks at the expense of the marginalization of the poor in contexts of greater inequality [@otero_differences_2023].
+
+This research asked how class-based network segregation is related to redistributive preferences and to what extent economic inequality moderates this relationship.
+The literature on interpersonal networks has shed light on how network structure harbors not only social resources [@lin_access_1986;@otero_open_2021] but also carries the capacity to establish niches that contribute to the formation of political opinions through social influence, as well as the degree of network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
+In contrast to the previous evidence on the direct diminishing influence of network homogeneity on social cohesion [@otero_lives_2022], the evidence presented in this study suggests that class segregation in terms of network homogeneity widens the already established class divide in redistributive preferences.
+Here, the interaction of class-based network homogeneity and social class shows that for working-class members, homogeneity strengthens their redistributive preferences, while in the service class, homogeneity translates into even lower redistributive preferences.
+
+The theoretical framework of this research posits that the study of the class divide in redistributive preferences should not exclusively address social classes regarding relations in the labor market but observe class in terms of the sociability structure in interpersonal networks.
+The literature has established that processes of social influence [@lindh_missing_2021] and political socialization [@lee_consider_2023] represent mechanisms that echo how social closure in interpersonal networks can trace a divide in redistributive preferences between social classes.
+This 'empathy gulf' [@sachweh_moral_2012] can be observed in how the service class is less willing to take action to strive against inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023].
+Additionally, as network homogeneity represents low cross-class ties, it can be argued that lower social integration can undermine social solidarity [@blau_macrosociological_1977], as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
+
+Besides the micro-level findings, this study has shown that economic inequality moderates the relationship between network segregation and redistributive preferences, which has not previously been discussed in an integrative empirical framework.
+On this behalf, the results from the multilevel models indicate that inequality _mitigates_ the micro-level relationship, which translates into a narrower class gap in redistributive preferences, mainly through changes in the service class.
+Empirically,
+these results resonate with evidence related to the role of inequality in class relations and redistributive preferences.
+It has been argued that in unequal societies, the better-off class tends to become more egalitarian in their attitudes toward economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
+Also, the results engage with the fact that upper classes can consolidate their distinctive position while their advantages allow them to navigate diverse networks at the expense of the marginalization of the poor in contexts of greater inequality [@otero_differences_2023].
+
+In the theoretical framework adopted, economic inequality establishes the field for class relations and conflict that are consequently crystallized in political attitudes, where the class divide in redistributive preferences represents one aspect of the economic domain [@lindh_class_2020].
+In addition, class relations can also be understood as networks of social connections between different class positions.
+Thus, social influence as a network mechanism on redistributive preferences can also be framed as the social force that intensifies class-based mechanisms such as self-interests and values in segregated networks [@lindh_missing_2021].
+Here, the observed weaker interaction between class and homogeneity in more unequal countries can be interpreted in two non-exclusive manners.
+First, network diversity becomes more stratified as inequality increases, meaning that networks in the upper classes become less homogeneous as inequality rises.
+Second, given that the upper classes hold more egalitarian stances in more unequal societies, it is plausible to argue that class homogeneity can also reinforce opinion similarity when redistributive preferences are higher in the upper class.
+Therefore, network segregation could influence opinions by either weakening or reinforcing attitudes based on the average opinion about redistributing within a class.
 
 <!-- _conclusion_-->
+
 This research is a contribution to the field of study on social class and redistributive preferences, but it also contributes to previous studies that have emphasized the role of social ties in redistributive preferences [@newman_my_2014;@edlund_influence_2003;@langsaether_more_2020].
-In addition to the micro-level contribution, the cross-national component of this research dialogue with previous studies on the role of income inequality on social networks [@pichler_social_2009;@letki_getting_2015;@otero_differences_2023] and class-based research on redistributive preferences [@edlund_democratic_2015;@curtis_how_2015].
-Besides, this research broadly contributes to the ongoing research on social cohesion beyond Western industrialized countries, as our analyses include a heterogeneous group of societies.
-
-In the end, our research has been reached with limitations.
-On the side of our dependent variable, a two-item index is a rough proxy of what we conceptually claim as redistributive preferences.
-It is well established in the literature that the popular responses to economic inequality are diverse regarding how the government strives with economic inequality [@mccall_americans_2009;@garcia-sanchez_two_2022].
-In addition, the position generator included in the ISSP is limited in terms of the capability to reflect the class structure more precisely, mainly regarding the self-employed and the intermediate-class occupations.
-In this regard, we are aware of the limitations of the instrument, and therefore, we present these results with prudence.
-Finally, it has been established that network formation is structured by contact opportunities [@feld_focused_1981], but values-based interaction also play a role in consolidating networks [@visser_attitudes_2004].
-Thus, the cross-sectional nature of our data does not allow us to make causal claims because there could be problems of endogeneity between class position, the composition of social ties, and attitudes.
-
-To summarize, future survey research should consider better measurement strategies for attitudes in the economic domain, such as market-based social services, willingness to pay taxes as redistributive measures, or direct focalized transfers.
-In addition, the network dimension can be better approached with a more detailed measurement strategy incorporating other aspects of the occupational structure, such as authority or autonomy in the labor market.
-Finally, the causality-related issues can be addressed by employing longitudinal designs.
+In addition, the cross-national component of this research dialogue with previous studies on the role of income inequality on social networks [@pichler_social_2009;@letki_getting_2015;@otero_differences_2023] and class-based research on redistributive preferences [@edlund_democratic_2015;@curtis_how_2015].
+Overall, the diversity of societies analyzed contributes to the literature on redistributive preferences and social networks beyond affluent industrialized countries.
+
+However, the present study entails some limitations.
+On the side of the dependent variable, a two-item index is a rough proxy of what is conceptually claimed as redistributive preferences.
+For example, poverty relief, tax reforms, or market regulations represent concrete actions on how governments strive with popular responses to economic inequality [@mccall_americans_2009;@garcia-sanchez_two_2022].
+Additionally, the position generator included in the questionnaire is limited in its capability to reflect social classes more precisely, particularly the self-employed and intermediate-class positions.
+Hereby, the results should be taken with prudence as the measurement limitations are recognized.
+Finally, as structural contact opportunities and value-based interactions jointly shape social network composition, the cross-sectional data employed prevents causal claims from being made as endogeneity problems between class position, network composition, and attitudes are recognized.
+
+Future research should improve measurement strategies by including already established survey questions on attitudes toward market distribution of social services or willingness to pay taxes as redistributive measures.
+Additionally, class-based social networks can be improved by including other aspects of the market situation of network ties, such as self-employment status or authority in the workplace.
+Finally, longitudinal analyses can contribute to disentangling the causal mechanism involved in the link between social class, networks, and political attitudes.
 
@@
 `r if (knitr::is_latex_output()){ '\\section{Appendix}'}`
+
+```{r status-ocup, echo=FALSE, cache=TRUE, results='asis'}
+pacman::p_load(dplyr,knitr,kableExtra)  
+# Create the data frame
+df <- data.frame(
+  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
+  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
+                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
+                 "Executive of large firm", "Lawyer"),
+  ISEI08 = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
+) %>% 
+  arrange(-ISEI08)
+kable(df,linesep = "",booktabs=TRUE,caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
+  kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
+  column_spec(1,width = "10cm") %>%
+  pack_rows("Higher-status positions", 1, 3) %>%
+  column_spec(2) %>% 
+  pack_rows("Middle-status positions", 4, 6) %>% 
+  pack_rows("Lower-status positions", 7, 10) 
+```
 
@@
 \pagebreak
-# Additional analysis
-
-## Income Inequality Ratios
+
+# Supplementary analysis
+
+## Income inequality ratios
 
@@
 \pagebreak
-## Income inequalty groups
+## Income inequality groups
 
@@
 
-```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditioned by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
 marginal <- bind_rows(
@@
 
-## OECD Countries
-
-```{r tab2-ocde, results='asis', cache=TRUE}
+<!-- ## OECD Countries -->
+
+```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------$
@@
 
-## Social distance
+## Social Distance by ISEI
 
@@
 Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance.
-In addition, When the distance is 0, the network is entirely homogeneous.
+In addition, when the distance is 0, the network is entirely homogeneous.
 
@@
 
-1. The absolute values are calculated to represent the total distance to occupations respect to R's ISEI score.
-2. Since we have 0 values representing absolute homogeneity, we rescale the variable by adding 1.
-4. We have inverted the values to make higher values represent higher homogeneity.
+1. The absolute values are calculated to represent the total distance to occupations concerning R's ISEI score.
+2. Since there are values of 0 representing absolute homogeneity, the variable is rescaled by summing 1.
+3. The values were inverted to make higher values represent higher homogeneity.
 
@@
 ```
-
-### Social Distance by ISEI
 
@@
 
-```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE}
+```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditioned by ISEI on Redistributive Preferences',warning=FALSE}
 int_homo <- digclas1_VW_7

### 2024-06-03 paper1_jiturra.Rmd
typos abstract

@@
   | Escalating economic inequality has increased attention to the link between class relations and redistributive preferences in contemporary societies.
-Hoewever, economic inequality unevenly affects class relations and their influence on support for redistribution across societies.
+However, economic inequality unevenly affects class relations and their influence on support for redistribution across societies.
 While those in the upper and middle classes reinforce their privileged access to resources and diverse networks, the working class has been disproportionately affected by social exclusion as inequality rises.
 Consequently, inequality consolidates segregated lifeworlds as it increases the divide between the lives and experiences of the different social classes.
-In this context, class relations represent the market situation of individuals and households as well as a network of social relations within and between classes.
 Meeting people from diverse class positions can help individuals become more aware of other people's lifestyles and worldviews.
-Homogeneous upper-class networks may lead to reduced empathy and solidarity towards those in need, resulting in decreased support for redistribution.
+Homogeneous upper-class networks may reduce empathy and solidarity towards those in need, resulting in decreased support for redistribution.
 Conversely, segregated lower-class social networks can lead to increased marginalization and reinforce support for redistribution.
-This study explores the relation of class-based network segregation and redistributive preferences employing cross-national data of 32,529 individuals in 31 societies.
-The main findings suggest that social class conditions the association of network homogeneity on redistributive preferences, where working class homogeneity drive stronger redistributive preferences, while greater upper-class homogeneity decreases support for redistribution.
+This study explores the relationship between class-based network segregation and redistributive preferences employing cross-national data from 32,529 individuals in 31 societies.
+The main findings suggest that social class conditions the association of network homogeneity on redistributive preferences, where working-class homogeneity drives stronger redistributive preferences, while greater upper-class homogeneity decreases support for redistribution.
 In addition, the conditional influence of network segregation weakens in unequal societies, especially for the upper classes.
-Implications for the study of class relations and political atttiudes are dicussed.
+Implications for the study of class relations and political attitudes are discussed.
   | 

### 2024-06-11 paper1_jiturra.Rmd
comentarios method

@@
 
-Individual data from the "Social Networks and Social Resources"  module of the International Social Survey Programme (ISSP) from 2017 is employed [@issp_networks_2017].
-This module includes information on a broader range of topics linked to social networks, attitudes toward economic inequality as well as demographic and socioeconomic background characteristics.
-The initial dataset includes 47,027 individual observations from 32 countries.
-However, one country (Slovenia) is excluded from the study because the main dependent variables are not available.
-Subsequently, after applying listwise case deletion, the analytical sample is composed of 32,529 individuals in 31 countries.
+The primary individual data source is the "Social Networks and Social Resources" module of the International Social Survey Programme (ISSP)  [@issp_networks_2017].
+The ISSP consists of a nationally representative probability sample of the adult population without substitution of each country.
+Each country applies a properly adapted questionnaire to guarantee the cross-cultural validity of the data and allow meaningful comparisons between countries.
+The questionnaire includes sections on social networks, attitudes toward economic inequality, and demographic and socioeconomic background characteristics.
+The complete full sample includes 47,027 observations in 32 countries.
+However, after inspecting the required information and applying listwise case deletion, the sample employed in the final analyses consists of 32,529 observations in 31 countries [^1].
+
+[^1]: Slovenia is excluded from the study because the support for government redistribution measured by 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes' was not available in the dataset.
 
@@
 
-For measuring economic inequality the Gini index (post-taxes and transfers) from the World Income Inequality Dataset (WID) is employed [@alvaredo_world_2022].
-Additionally, two contextual variables are incorporated as controls in the multilevel models.
-Firstly, employing the Gross Domestic Product (GDP) available in the WID ensures consistency in the economic inequality estimates independently of economic property [@Schmidt-Catran2016; @finseraas_income_2009].
+To comparatively measure economic inequality, I include the Gini index (post-taxes and transfers) from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
+In addition, two contextual variables are incorporated as controls in the multilevel regression.
+Firstly, employing the Gross Domestic Product (GDP) in constant 2017 USD (PPP) ensures consistency in the economic inequality estimates independently of economic property [@wiid_2023].
 Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state is included [see @edlund_democratic_2015].
@@
 Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class.
-In this set, a three-way cross-level interaction is estimated to determine if income inequality moderates the interaction between network homogeneity and social class to test hypothesis 2 [^1].
-In the latter model, all the individual-level variables are group-mean centered (CWC) to mitigate possible collinearity problems [@hox_multilevel_2010].
+This set estimates a three-way cross-level interaction to determine if income inequality moderates the interaction between network homogeneity and social class to test hypothesis 2 [^2].
+In the latter model, all the individual-level variables are group-mean centered (CWC) to mitigate collinearity problems between the lower and higher-level predictors and spurious cross-level interaction coefficients [@aguinis_bestpractice_2013].
 Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations [@hox_multilevel_2010].
-For all the analyses, the package `lme4` for in the statistical package `R`  is employed [@bates_fitting_2015].
-
-[^1]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
+For this purpose, the package `lme4` [@bates_fitting_2015] for the statistical package `R` is employed in all the analyses.
+
+[^2]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
 Additionally, countries were classified into low, middle-low, middle, middle-high, and high-income inequality groups based on quintiles according to the Gini index.
@@
 However, it is worth to mention at least two interesting findings.
-First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.08), with Thailand being the society with higher levels of network segregation (M = 0.43), and Iceland among lowest (M = 0.31).
+First, looking at the sample average (M = 0.36), it can be noticed that the variation between countries is low (SD = 0.08), with Thailand being the society with higher levels of network segregation (M = 0.43), and Iceland among lowest (M = 0.31).
 Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
@@
 Moving to the bivariate macro relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, our main societal characteristic of interest.
-First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.43, _p_ <.001).
-In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social segregation among the working classes and consequently drive higher redistributive preferences.
+First,  Panel A depicts a medium positive and significant association between network homogeneity and redistributive preferences (_r_ = 0.43, _p_ <.001).
+In concordance with the previously depicted distribution, the higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social segregation among the working classes and consequently drive higher redistributive preferences.
 Second, Panel B depicts a positive but relatively weak and non significant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
@@
 By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
-As an additional exploratory analysis (see Fig.
-\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.3, _p_<.01).
+Besides, a supplementary analysis (see Fig.
+\@ref(fig:figapp1)) demonstrates that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.3, _p_<.01).
 In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
@@
 Initially, as previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
-This association persists in Model 2, where we control for network size.
-However, after including social class in Model 3, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
+This association is robust to network size in Model 2.
+However, after including social class in Model 3, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_> .05).
 Subsequently, Model 4 incorporates income, education in years and employment status.
 As expected, socioeconomic status is negatively associated with redistributive preferences regarding household economic resources and educational credentials.
-In addition, we find that people outside the labor market do not differ significantly from those who are economically active in their preferences.
-Finally, in Model 5, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
+In addition,  people outside the labor market do not differ significantly from those who are economically active in their preferences.
+Finally,  incorporating the interaction term between network homogeneity and social class, Model 5 shows that the working and intermediate class interaction terms are positive and statistically significant.
 Based on Model 5, Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
@@
 
-To facilitate the interpretation of the indicator, we have calculated a homogeneity indicator based on social distance:
+To facilitate the interpretation of the indicator, the homogeneity indicator based on social distance is calculated:
 

### 2024-07-09 paper1_jiturra.Rmd
update

--- 2024-06-03 paper1_jiturra.Rmd
@@
 linestretch: '1.15'          # interlineado  
+#linestretch: '2.0'          # interlineado 
 papersize: a4
@@
   email: jiturra@uni-bremen.de
-#   number: 1
-# - name: Justin d'Ottawa
-#   affiliation: University of Ottawa
-#   number: 2
-# - name: Pedro Torres
-#   number: 1,2 
-# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
 abstract: | 
-  | Escalating economic inequality has increased attention to the link between class relations and redistributive preferences in contemporary societies.
+  | Rising economic inequality has increased attention to the link between class relations and redistributive preferences in contemporary societies.
 However, economic inequality unevenly affects class relations and their influence on support for redistribution across societies.
@@
 bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
-csl: input/bib/apa6.csl
+csl: input/bib/apa-no-doi-no-issue.csl
 editor_options:
@@
   - \usepackage{helvet}
+  - \usepackage{endnotes}
+  - \let\footnote=\endnote 
   - \renewcommand{\familydefault}{\sfdefault} 
@@
  rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::pdf_document2")
- rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
+ # rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
  rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
@@
 
-```{r include=FALSE}
+```{r include=FALSE, cache=FALSE}
 wordcount<- rmdwc::rmdcount(files = "paper1_jiturra.Rmd") 
@@
 
-During the past decades, the few cross-national studies on redistributive preferences and social class have predominantly focused on the situation of individuals and households [@lindh_class_2020].
-Nonetheless, little attention has been paid to the network mechanisms involved in how individuals form their opinions regarding economic inequality and redistributive policies.
-On the one hand, sociologists have formerly demonstrated that homophily profoundly drives individuals to form similar social ties that consequently nurture social network segregation [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-In contrast, it is also known that opinions about economic inequality can be affected by class segregation as it provides a window for learning about the economic conditions, lifestyles, and worldviews of other social classes [@mijs_inequality_2018;@otero_power_2023].
-Despite this, it can be argued that the scrutiny of redistributive preferences can be enhanced by broadening the comprehension of class relations from a network perspective, providing a comprehensive manner to understand processes of shared norm internalization, class identity formation, and collective solidarity [@Svallfors2006;@goldthorpe_sobre_1992].
-In this regard, the present study examines the relationship between class-based network segregation and redistributive preferences in cross-national comparison, focusing on the role of economic inequality as a moderator of the claimed influence of class relations on support for redistribution.
-
-While prior research has predominantly focused on examining the impact of social class through an individualistic lens, it is noteworthy that more attention should be devoted to understanding the role of social environments in class relations.
-This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
-In addition, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-In this regard, besides the leverage of individual class position, recent efforts have pointed out that whereas the class positions of network ties do affect redistributive preferences, the degree of segregation in a homogeneous class environment can drive attitudes to become even stronger [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-
-While network segregation intensifies the already established class divide in redistributive preferences, little is known about how contextual factors affect the association of class-based network segregation and support for redistribution.
-On the one hand, studies on the class-attitude link posit that economic inequality is crucial for understanding how class relations are mirrored in redistributive demands as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-A consistent finding on this matter is that the upper classes tend to hold more egalitarian attitudes in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
+Over the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
+In contrast, less attention has been paid to how social networks influence redistributive preferences.
+Sociologists have demonstrated that individuals tend to segregate social networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
+Additionally, opinions about economic inequality can be affected by class segregation, as it provides insight into the economic conditions, lifestyles, and worldviews of other social classes [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+Despite this, the study of redistributive preferences can be enhanced by broadening the understanding of class relations from a network perspective.
+This approach offers a comprehensive understanding of processes such as shared norm internalization, class identity formation, and collective solidarity [@Svallfors2006;@goldthorpe_sobre_1992].
+Thus, this study examines the relationship between class-based network segregation and redistributive preferences in a cross-national comparison, focusing on the role of economic inequality as a moderator in the influence of class relations on support for redistribution.
+
+While prior research has predominantly examined the impact of social class through an individualistic lens, more attention should be devoted to understanding the role of social environments in class relations.
+This omission is particularly surprising given that class positions are fundamentally rooted in production relations, making them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
+Furthermore, the normative basis of class relations introduces the relevance of solidarity and reciprocity dimensions, which are argued to provide the moral foundation for legitimacy and popular support for welfare schemes [@mau_moral_2003].
+In this regard, beyond the influence of individual class position, recent efforts have highlighted that while the class positions of network ties do affect redistributive preferences, the degree of segregation in a homogeneous class environment can drive attitudes to become even stronger [@otero_lives_2022].
+
+While network segregation widens the class divide in redistributive preferences, little is known about how income inequality can affect the association between class-based network segregation and support for redistribution.
+On the one hand, studies on the class-attitude link suggest that income inequality is crucial for understanding how class relations are reflected in redistributive demands, as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
+A consistent finding in this literature is that the upper classes tend to support redistribution more in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
 On the other hand, income inequality leads to more segregated forms of social participation and network composition [@pichler_patterns_2007;@otero_space_2022].
-Indeed, inequality reinforces the stratified access to social activities and widens the distance between classes, resulting in an increasing marginalization of the lower classes and consolidating the privileged positions of the upper classes that held better opportunities for diversifying their social activities and interpersonal ties [@lancee_income_2012;@letki_getting_2015;@otero_differences_2023].
-Nevertheless, current efforts to examine the impact of income inequality have primarily concentrated on either social networks or support for redistribution.
-A key question that remains unanswered is the extent to which broader economic disparities can influence the relationship between class-based network segregation and support for redistribution within a comprehensive framework.
-
-Thus, as no research has comparatively stressed the role of economic inequality in the relationship between class-based network segregation and redistributive preferences, the present study aims to answer two questions:
+Indeed, inequality reinforces stratified access to social activities and widens the distance between classes, resulting in increased marginalization of the lower classes and consolidating the privileged positions of the upper classes, who have better opportunities to diversify their social activities and interpersonal ties [@lancee_income_2012;@otero_differences_2023].
+Nevertheless, current efforts to examine the impact of income inequality have primarily focused on either social networks or support for redistribution.
+A key question that remains unanswered is the extent to which broader economic disparities moderate the relationship between class-based network segregation and support for redistribution.
+
+Thus, to the best of my knowledge, no research has comparatively investigated the role of economic inequality in the relationship between class-based network segregation and redistributive preferences.
+This study aims to address two key questions:
 
@@
 
-For the present investigation, a data sample of 32,529 individuals across 31 societies from the International Social Survey Program (ISSP) 2017 is utilized.
-The ISSP presents a nonprecedence opportunity as it provides comprehensive information on interpersonal networks, social class, and attitudes toward redistribution.
+For this investigation, I utilized a sample of 32,529 individuals across 31 countries from the International Social Survey Program (ISSP) 2017.
+This dataset provides unprecedented cross-national comparative data on social networks, social class, and attitudes toward redistribution.
 
@@
 421].
-In this view, the role of class goes beyond the market situation of individuals but drives collective economic interests and moral views about the role of the market and the state [@Svallfors2006].
-Here, what has been understood as redistributive preferences entail the public responses to economic inequality regarding the sphere of the role of government actions in aspects such as the reduction of income differences or enhancing opportunities for those in economic despair  [@mccall_americans_2009].
-
-However, class-based explanations of redistributive preferences have mainly been, but not exclusively, focused on the individual or household situation.
-It has been claimed that redistributive preferences can be explained through the labor market situation, which comprises access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
-Moreover, as material interests might prevail in scarcity, value-driven motivations are a relevant explanatory factor of redistributive preferences [@Kulin2013;@feldman_humanitarian_2001], becoming salient under greater certainty and weaker under material precariousness [@Maldonadoetal2019].
-Other approaches have suggested that given the substantial time workers spend performing their jobs, social relations in the workspace can imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
-For instance, continuous and diverse social interactions that characterize interpersonal services can drive empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
-In contrast, the vertical monitoring in managerial occupations and the relevance of autonomy in the case of self-employed fortify self-interested and conservative political views [@langsaether_more_2020;@oesch_electoral_2018].
-
-Empirically, the current understanding of the class divides on redistributive preferences is extensive [@andersen_preferences_2018;@lindh_public_2015; @curtis_how_2015;@langsaether_more_2020;@brooks_why_2010;@Svallfors2006].
-Nevertheless, besides the market situation of individuals and their households, including class-based social ties raises the relevance of the _class situation_ as it comprises both economic interests and life chances that motivate communal action beyond the individualistic lens [@weber_class_2011, pp.
+In this view, social class not only represents individuals’ market situations but also their economic interests and moral perspectives on the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
+Here, redistributive preferences are understood as the support for policies and mechanisms aimed at reducing economic inequality through the redistribution of wealth and resources [@mccall_americans_2009].
+These preferences encompass views on taxation, welfare programs, public services, and other government interventions designed to transfer resources from wealthier to less wealthy individuals or groups in society [@garcia-sanchez_two_2022].
+
+Class-based explanations of redistributive preferences have primarily focused on the individual or household level but are not exclusively limited to these contexts.
+It has been argued that redistributive preferences can be explained through labor market situations, which encompass access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
+Additionally, while material interests may dominate in situations of scarcity, value-driven motivations become a significant explanatory factor for redistributive preferences under conditions of greater certainty and are weaker under material precariousness [@Kulin2013;@Maldonadoetal2019].
+Other approaches suggest that the substantial time workers spend on their jobs allows social relations in the workplace to imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
+For example, the continuous and diverse social interactions inherent in interpersonal services can foster empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
+In contrast, vertical monitoring in managerial occupations and the emphasis on autonomy in self-employed roles tend to strengthen self-interested and conservative political views [@oesch_electoral_2018].
+
+Empirically, the current understanding of class divides in redistributive preferences is extensive [@lindh_public_2015;@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
+Nevertheless, beyond the market situation of individuals and their households, considering class-based network ties highlights the relevance of the class situation, as it encompasses both economic interests and life chances that drive communal action beyond individuals [@weber_class_2011, pp.
 57-59].
-Therefore, the role of social relations on redistributive preferences from a network perspective needs to be developed beyond mere resource interchanges, but as part of the sociability practices that structure class relations.
+Thus, the role of social relations in shaping redistributive preferences from a network perspective considers more straightforwardly the social ties that structure class relations.
 
@@
 
-It can be argued that class relations not only represent resource-based distinctions but also patterns of sociability observed in the differentiation of social ties.
-Class relations can also be understood as the degree of cross-class relationship as a structural characteristic of a society, representing a network of social ties between different class positions [@blau_macrosociological_1977].
+<!-- It can be argued that class relations not only represent resource-based distinctions but also patterns of connectedness observed in the differentiation of social ties.  -->
+
+Class relations can also be understood as the degree of cross-class relationships as a structural characteristic of society, representing a network of social ties between different class positions [@blau_macrosociological_1977].
 Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001, p.416].
-Hereby, friendship and family ties are prone to be homogeneous in terms of class and demographic characteristics, but distant ties play the role of bridging individuals to other different social groups and contribute to network diversity [@bargsted_pautas_2020; @plaza_juntos_2022;@lazarsfeld_friendship_1954].
-In this sense, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951].
-Nonetheless, it can be argued that attitudinal similarity is the result of segregated social relations, which in turn are linked to structural processes of differentiation that also demarcate the boundaries to form ties with other social positions [@feld_focused_1981].
-
-It is possible to find two approaches in the study of class relations from a network approach.
-On the one hand, it has emphasized the role of _diversity_ as the degree of connectedness to dissimilar occupations that vertically represent access to resources embedded in social networks [@lin_social_2007].
-However, diversity is defined as the rate of dissimilar ties within the network that do not necessarily count with a reference position to describe the network composition.
-A second approach has underscored the role of _segregation_ as the lack of cross-class network ties.
-This perspective is conceptually closer to homophily as it is anchored in individual class positions and has empirically been addressed through the concept of network homogeneity [@otero_open_2021].
-
-Empirically, studies on network diversity have shown that higher civic engagement in formal organizations increases the chances of bridging with diverse people among the upper class, in contrast to the more homogeneous participation of the working class [@pichler_social_2009].
-Similar patterns have been found in terms of the composition of social ties, where the upper and intermediate classes hold increasingly diverse and prestigious social environments than the working classes [@cepic_how_2020;@carrascosa_class_2023].
-Also, this stratified network structure holds during the life course, where the upper classes hold increasingly diverse social contacts in contrast to the stable networks of the working classes [@volker_social_2020].
-In contrast, studies that have focused on segregation suggest that the property dimension is much less permeable than authority-based boundaries, arguing that class interests increase the social distance between proprietors and manual workers, while the intermediate class position of supervisors jointly to their higher contact frequency with manual workers make friendship tie formation more likely [@wright_relative_1992].
-Similar studies have shown that the intermediate class holds higher permeability in contrast to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity to be socially engaged ultimately result in a lack of social resources that lead to social segregation.
-In contrast, the upper class is less permeable and homogeneous because it tends to self-select as a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
+In this context, friendship and family ties tend to be homogeneous concerning class and demographic characteristics, while more distant ties serve to bridge individuals to different social groups and contribute to network diversity [@diprete_segregation_2011; @lazarsfeld_friendship_1954].
+Besides, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004; @homans_human_1951].
+Nevertheless, attitude similarity in segregated networks is rather a consequence of the social differentiation that structures the formation of cross-class network ties [@feld_focused_1981].
+
+There are two primary approaches in the study of class relations from a network perspective.
+On the one hand, network diversity is defined as the degree of connectedness to dissimilar occupations, which represents vertical access to resources embedded in social networks [@lin_access_1986].
+However, diversity is defined as the rate of dissimilar ties within the network without necessarily providing a reference position to describe network similarity.
+On the other hand, network segregation is the absence of cross-class connections and represents how similar network ties are in contrast to the individual.
+This perspective is conceptually closer to homophily as it is anchored in individual class positions and has been empirically addressed through network homogeneity [@otero_open_2021].
+
+How does social class stratify social networks?
+Empirically, studies on network diversity reveal that higher civic engagement in formal organizations increases the likelihood of the upper-class forming connections with diverse individuals, in contrast to the more homogeneous participation observed among the working class [@pichler_social_2009].
+Similar patterns are observed in the composition of social ties, where the upper and intermediate classes maintain increasingly diverse and prestigious social environments compared to the working class [@cepic_how_2020;@carrascosa_class_2023].
+In contrast, studies on network segregation suggest that property-based boundaries are less permeable than authority-based ones.
+For example, @wright_relative_1992 suggest since class interests widen the social distance between proprietors and manual workers, the intermediate position of supervisors, along with their higher contact frequency with manual workers, makes the formation of friendship ties more likely.
+Similarly, @otero_open_2021 have shown that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity for social engagement ultimately result in a lack of social resources that leads to segregation.
+Conversely, the upper class is less permeable and homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
 
@@
 
-Besides individual class-based mechanisms, it can be argued that their social relations represent a relevant factor in attitude formation.
-Particularly, despite limited research on the link between social networks and redistributive preferences, two theoretical approaches have discussed the role of social relations in attitude formation: reference groups and class-based networks.
+Besides individualistic class-based mechanisms in redistributive preferences, the argument that network ties have implications for attitude formation is not novel.
+In particular, two approaches have discussed the role of social relations on redistributive preferences: reference groups and class-based networks.
 
@@
 Accordingly, experience sharing in conversations with socioeconomically diverse networks has been proven to contribute to the accuracy of the images of income and wealth inequalities compared with people in more segregated networks [@summers_deliberating_2022].
-Nevertheless, I argue that this body of research has been mainly focused on the cognitive dimension of preference formation through inequality perceptions or beliefs rather than straightforward addressing the claimed influence of network segregation on redistributive preferences [@cansunar_who_2021;@garcia-castro_perceived_2022;@Cruces2011;@becker_significant_2021].
-
-In contrast, a network approach provides a better picture of class relations that nurture social norms and group identity [@kalmijn_social_2007, p.
+Nevertheless, I argue that this body of research has been mainly focused on the cognitive dimension of preference formation through inequality perceptions rather than straightforwardly addressing the claimed influence of network segregation on redistributive preferences [@cansunar_who_2021;@garcia-castro_perceived_2022].
+
+In contrast, social networks provide a comprehensive picture of the class relations that contribute to group identity formation and internalization of social norms [@kalmijn_social_2007, p.
 550].
-More precisely, it has been argued that redistributive preferences are influenced by the class situation of both the individual and network ties, where social influence processes can either allineate or divide opinions according to the contacts' class position and how segregated contact opportunities are [@vargassalfate_contact_2023].
-This claim resembles the fact that classes are characterized as collectivities with differences in their degrees of cohesion and solidarity, encompassing unequal status-based social interactions that are linked to individual and household material well-being, cultural perspectives, and political preferences that structure broader social experiences [@morris_attenuation_1996, p.
+Specifically, it has been argued that redistributive preferences are influenced not only by individuals' class situations but also by the class positions of their network ties [@paskov_crossclass_2022].
+Social influence processes can either align or divide opinions depending on the class positions of contacts and the level of network segregation [@lindh_missing_2021].
+These findings reflect the notion that classes are characterized as collectivities with varying degrees of cohesion and solidarity, comprising asymmetric status-based interactions related to material resources, cultural practices, and political preferences that shape broader social experiences [@morris_attenuation_1996, p.
 48].
-Furthermore, social integration can be affected in societies with lower contact opportunities between different social classes, creating an "empathy gulf" that comprises barriers to imagining others' lifestyles in contexts of rising inequality [@sachweh_moral_2012].
-Thus, spatially segregated interactions may nurture doubts about worthiness when the lower classes contrast themselves with the lifestyles of the upper classes, which in turn can undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
-As a result, segregation drives the lives of others to become more distant and might have consequences for empathy and solidarity toward others, potentially leading to the perception of fellow citizens as strangers [@otero_lives_2022, p.
+Following @sachweh_moral_2012, social integration can be impeded in societies with few opportunities for contact between different social classes, creating an "empathy gulf" that hinders individuals from understanding others' lifestyles amid rising inequality.
+Consequently, spatially segregated interactions may lead individuals to view the lives of different classes as more distant, which can undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
+Thus, segregation can exacerbate perceptions of others as strangers and may impact empathy and solidarity, potentially diminishing social cohesion [@otero_lives_2022, p.
 758].
@@
 
-The class position of surrounding family members, friends, and acquaintances influences redistributive preferences as they function as socialization agents that can be bolstered in segregated social networks.
-In principle, political attitudes are connected to class interests and norms as they are nurtured in the family of origin during childhood and early adulthood.
-For instance, it has been shown that individuals with network ties to the upper class through parental connections support redistribution and progressive taxation less than those from working-class family backgrounds [@lee_consider_2023].
-Also, as households share risk according to the class position of their members, redistributive preferences are not only affected by their family background but also by partners' class positions.
-For example, @paskov_crossclass_2022 found that working-class ties bolster redistributive preferences but decrease with upper-class ties, becoming much more intense when the class positions of individuals, partners, and parents form a more homogeneous network.
-Besides, @lindh_missing_2021 found that including friends and acquaintances in the network structure leads individuals with higher ties to the managerial class to decrease their redistributive preferences compared to those with higher sociocultural and working-class ties, suggesting that people tend to consider and adjust their attitudes according to the class position of their contacts [@lindh_missing_2021, p.
+The class position of surrounding family members, friends, and acquaintances influences redistributive preferences, as these individuals function as socialization agents whose impact can be amplified in segregated social networks.
+In principle, political attitudes are connected to class interests and norms that are nurtured in the family of origin during childhood and early adulthood.
+For instance, @lee_consider_2023 shows that individuals with network ties to the upper class through parental connections tend to support redistribution and progressive taxation less than those from working-class family backgrounds.
+Moreover, since households share risk based on the class position of their members, redistributive preferences are shaped not only by family background but also by the class positions of partners.
+For example, @paskov_crossclass_2022 indicates that working-class ties bolster redistributive preferences, whereas ties with the upper class decrease these preferences, with the effects becoming more pronounced when the class positions of individuals, partners, and parents create a more homogeneous network.
+Additionally, @lindh_missing_2021 found that friendship and acquaintanceship ties to the managerial class are associated with lower redistributive preferences compared to ties with the sociocultural and working classes.
+Hence, they suggest that individuals tend to adjust their attitudes based on the class position of their contacts [@lindh_missing_2021, p.
 698].
 
-In summary, the tendency to form homogenous social ties regarding social class is expected to reinforce attitudes and consolidate opinion similarity.
-Empirically, a weak direct association between homogeneity and redistributive preferences is expected because class segregation does not distinguish between classes as it provides only the _overall_ degree of segregation.
-In contrast, the focus is on how class-based network homogeneity is conditional to social class.
-Empirically, this can be observed through the interaction between network homogeneity and social class.
-Precisely, this will indicate if being segregated into lower (upper) classes leads to stronger (weaker) redistributive preferences ($H_1$).
+In summary, as homogeneity refers to the overall degree of segregation without distinguishing between class positions I anticipate a weak direct association between network homogeneity and redistributive preferences.
+Conversely, I hypothesize that the association of network homogeneity with redistributive preferences is conditional on social class as homogeneous social networks should reinforce attitude similarity (*segregation hypothesis*).
+Specifically, I propose that greater network segregation in the lower classes is associated with higher redistributive preferences, whereas greater segregation in the upper classes is related to lower redistributive preferences.
+Therefore, the first hypothesis is as follows:
+
+> H1: _The greater the network segregation in the lower (upper) classes, the higher (lower) the redistributive preferences. _
 
@@
 
-Studies that have stressed the role of economic inequality on the relationship between social class and redistributive preferences indicate that the lower and the upper classes react differently to rising economic inequality.
-Theoretically, political economists have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution [@rueda_food_2018;@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Conversely, the moral economy literature in sociology has argued that the differences among the affluent can be explained as a matter of distributive justice evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016;@atria_economic_2020].
-Hence, affluent groups are more responsive because they perceive that increasing inequality harms the overall opportunity structure and social mobility chances [@sachweh_criticizing_2017].
-Likewise, lower perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
-In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019, p.
-656].
-
-Regarding social networks, prior studies have argued that social relations are directly linked to resource access and how these are distributed in society.
-Here,  Neckerman & Torche [-@neckerman_inequality_2007, p.
-344] suggest that experiencing marginalization is deeply associated with the life chances to participate openly in social life, which can be exacerbated in contexts of greater material inequality.
-Also, economic inequality can lead to greater perceived status competition [@wilkinson_spirit_2010;@garcia-sanchez_perceived_2024], which in turn hampers trustworthy social ties among the low-status individuals [@salgado_expectations_2021].
-In contrast, societies with robust welfare institutions and lower economic inequality foster social engagement in civic and social activities, thereby enhancing social trust between citizens and bolstering social solidarity [@uslaner_inequality_2005;@kragten_income_2017].
-
-Empirically, comparative evidence shows that already-stratified access to social activities and diverse networks is strengthened in unequal societies
-[@lancee_diversity_2017].
-In this regard, @pichler_social_2009 show that class differences in participation in civic (formal) and family (informal) networks are deepened in more unequal societies.
-Similarly, @lancee_income_2012 have found that the stratified civic participation by income level is strengthened as inequality rises.
-Other studies have shown that low-income individuals hold more extensive close networks and rely on family ties to seek support in unequal societies but rely more on external ties to pursue resources [@letki_getting_2015].
-Likewise, economic inequality enhances stratified access to contact network diversity due to greater interdependence between cultural, economic, and social capital [@otero_differences_2023].
-Thus, the upper classes are capable of navigating diverse social settings while remaining segregated, whereas the lower classes may experience greater marginalization and segregation because of the choices of others [@otero_open_2021, p.24].
-
-Theoretically, previous research has stated that state-organized redistribution reflects political class conflict in a modern industrialized capitalist society, and social classes should not be undervalued as vehicles of antagonism and social tension [@edlund_democratic_2015, p.
-323].
-In this line, economic inequality is crucial in moderating conflicts as it can impact the political consensus for supporting redistribution between classes.
-One potential implication is that the decline in social trust, civic participation, and prosocial attitudes could undermine the normative basis for collective solidarity [@uslaner_inequality_2005].
-As a result, less cohesive societies can nurture a stronger class divide in egalitarian attitudes [@andersen_preferences_2018], making the middle classes less prone to support policies favoring the working classes.
-Nevertheless, in contexts of rising economic inequality, the middle classes tend to have greater political awareness about the causes and incentives of economic inequality [@Svallfors2006, pp.
-66–67], as well as its consequences for class conflict and cohesion [@kelley_class_1995].
-Additionally, in societies with lower material inequality and a predominant middle-class imaginery perceived social conflict decreases [@hertel_conflict_2022].
-Therefore, in more unequal societies, those who are better-off are more likely to support redistribution than their counterparts in more egalitarian contexts, where their attitudes gradually converge with the interests of the working class [@curtis_how_2015].
-
-To summarise, here it is argued that economic inequality increases the dependency of network segregation with class positions, leading the working classes to be equally segregated regardless of income inequality compared to the increasingly diverse networks of the upper classes [@pichler_social_2009;@otero_differences_2023].
-Consequently, it is expected that class-based network segregation in unequal societies might have a weaker association with redistributive preferences.
-Thus, economic inequality is expected to _mitigate_ the association of class-based network segregation with redistributive preferences ($H_{2}$).
+Studies on economic inequality, social class, and redistributive preferences indicate that the social classes react differently to rising economic inequality.
+Theoretically, political economists have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution [@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
+Conversely, the moral economy literature in sociology has argued that the differences among the affluent can be explained as a matter of distributive justice evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016].
+
+Empirically, affluent groups are more responsive because they perceive the overall opportunity structure and social mobility chances are affected by rising inequality [@sachweh_why_2019].
+Likewise, higher perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
+In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019].
+In a similar perspective, @edlund_democratic_2015 argue that in unequal societies with residual welfare states social class has a poor political meaning, making distributive conflicts weakly institutionalized around traditional working-class organizations (e.g., unions).
+Thus, stronger support for state-organized redistribution among the upper classes can also be explained as they are often more aware of the institutional incentives and societal consequences of income inequality [@curtis_how_2015;@Svallfors2006].
+
+How does income inequality affect social networks?
+As income inequality implies stronger barriers to establishing trustworthy social connections, this has also consequences on the structure of class relations.
+Neckerman and Torche [-@neckerman_inequality_2007, p.
+344] suggest that experiencing marginalization is deeply associated with diminished chances for participating openly in social life, which can be exacerbated in contexts of greater inequality.
+Also, societies with higher income inequality can erode social relations as they exhibit reduced social trust that operates as the basis for mutual understanding and feelings of solidarity [@kragten_income_2017].
+Likewise, in contexts of lower income inequality and encompassing welfare states, the higher levels of civic and social participation increase generalized trust and reduce social conflict [@uslaner_inequality_2005].
+Related evicende shows that higher community participation can incentivize support for redistribution in general, being particularly salient among high-income citizens [@yamamura_social_2012].
+
+Empirically, cross-national studies show that already-stratified access to social activities and diverse networks is further reinforced in unequal societies.
+For instance, @letki_getting_2015 show that extensive networks in unequal societies are more common among low-income individuals who rely more on close ties for social support than high-income individuals.
+Additionally, @pichler_social_2009 demonstrated that class differences in participation in civic and family networks are exacerbated in more unequal societies.
+Likewise, @lancee_income_2012 found that income-based stratification in civic participation becomes more pronounced as inequality increases.
+Also, @otero_differences_2023 found that economic inequality enhances stratified access to network diversity, suggesting that it amplifies the interdependence among cultural, economic, and social capital.
+Thus, the upper classes can navigate diverse social settings while preserving their distinctive position, whereas the lower classes often remain marginalized and segregated due to the choices of others [@otero_open_2021, p.24].
+
+To summarize, I expect that income inequality weakens the interaction between network homogeneity and social class.
+Specifically, I hypothesize that the conditional relationship between network homogeneity and social class (*segregation hypothesis*) will be less pronounced in contexts of higher income inequality (*mitigation hypothesis*).
+Given the above considerations, the second hypothesis reads as follows:
+
+> H2: _The greater the income inequality, the weaker the conditional association of network segregation by social class on redistributive preferences._
 
@@
 
-# Data, variables and method
+# Methodology
 
@@
 
-Individual data from the "Social Networks and Social Resources"  module of the International Social Survey Programme (ISSP) from 2017 is employed [@issp_networks_2017].
-This module includes information on a broader range of topics linked to social networks, attitudes toward economic inequality as well as demographic and socioeconomic background characteristics.
-The initial dataset includes 47,027 individual observations from 32 countries.
-However, one country (Slovenia) is excluded from the study because the main dependent variables are not available.
-Subsequently, after applying listwise case deletion, the analytical sample is composed of 32,529 individuals in 31 countries.
+The primary data source for this study is the "Social Networks and Social Resources" module of the International Social Survey Program (ISSP) [@issp_networks_2017].
+The ISSP provides a nationally representative probability sample of the adult population in each participating country without substitution.
+Each country administers a carefully adapted questionnaire to ensure the cross-cultural validity of the data and enable meaningful comparisons between countries.
+The questionnaire includes sections on social networks, attitudes toward economic inequality, and demographic and socioeconomic background characteristics.
+The complete sample comprises 47,027 observations across 32 countries.
+However, after reviewing the required information and applying listwise case deletion, the final sample used in the analyses consists of 32,529 observations from 31 countries [^data].
+
+[^data]: Slovenia is excluded from the study because the measure of support for government redistribution, specifically "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes," was not available in the dataset.
 
@@
 
-### _Individual level_ {-}
-
-Two indicators available in the questionnaire were used to measure redistributive preferences.
-First, (1) support for government redistribution is measured by the item 'It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.' and (2) egalitarian preferences represented by the item 'For a society to be fair, differences in people's standard of living should be small.' indicators are five-point Likert scales with the categories 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree' (3), 'Disagree' (4) and 'Strongly disagree' (5).
-Second, due to the correlation between the indicators (r = 0.7) and following previous research, the indicators were reverse-coded to compute the average values.
-They were then rescaled to create an indicator that ranges from 0 to 100, where higher values reflect stronger redistributive preferences [@svallfors_government_2013].
-
-For measuring social class, the Erikson-Goldthorpe-Portocarrero (EGP) class Scheme is employed [@Erikson1992;@Erikson1979].
-The EGP is one of the most consistent and validated measures for social class positions in comparative research [@evans_political_2013] and has demonstrated its validity in industrialized and late industrialized societies [@solis_class_2019;@torche_unequal_2005;@ishida_trends_2005;@barozet_measurement_2021; @wang_where_2024].
-Therefore, relying on the DIGCLASS algorithm [@cimentada_digclass_2023], information about occupations, self-employment status, and number of employees is used to classify respondents into class positions.
-Following previous research, a collapsed version of three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
-Accordingly, the class scheme contemplates the Service Class (Higher and Lower managerial and professionals), Intermediate Class (Routine nonmanual and Self-employed), and Working Class (Manual supervisors, skilled manual and unskilled manual).
-
-The position generator is employed for measuring class-based network homogeneity.
-This instrument has been widely employed in social capital studies and follows an ego-centered approach where social ties to different hierarchical positions in the social structure provide access to social resources [@lin_access_1986;@vandergaag_position_2008].
-In this case, a list of ten occupations is displayed and the tie can be classified as "Family or relative", "Close friend", "Someone else I know", or "No one".
-Here, the first three categories are classified as "Knows" = 1 and "Does not know" = 0.
-Consequently, the total number of social ties per respondent is obtained.
-Subsequently, the occupations are classified into three groups that closely resemble social class positions [@otero_open_2021;@sapin_issp_2020].
-First, the (i) lawyer, (ii) executive of a large firm, and (iii) human resource manager are classified as high-status.
-Second, the (iv) school teacher, (v) police officer, and (vi) nurse are considered middle-status.
-Third, (vii) car mechanic, (viii) bus driver, (iv) hairdresser, and (v) home or office cleaner are low-status occupations.
-
-As the network status groups are employed as proxies of social class positions, the number of similar or ingroup social ties is calculated according to the respondent class position and provides the absolute number of similar ties.
-Subsequently, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network [@otero_lives_2022; @volker_birds_2022].
-Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are *similar* (homogeneity).
-In substantial terms, higher values represent higher social distance from other social classes in society.
-
-First, the number of social ties is included to guarantee that the association of network homogeneity is independent of network size.
-Second,  socioeconomic characteristics are sequentially incorporated in the models as they represent the current social status through income, education, and labor market status [@meltzer_rational_1981;@kitschelt_occupations_2014;@hausermann_highskilled_2015].
-Third, gender, age, and marital status are included in all models as a sociodemographic characteristic to control for the potential influence of gender norms and life course events on attitudes [@alesina_preferences_2005;@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
-
-<!-- As suggested recently, we have selected a set of control variables based on substantive reasoning informed by the current state of research on social networks and redistributive preferences [@kohler_control_2024].
-Our estimations incorporate studies on social capital, network size, and social trust.
-The volume of social ties within a network can have implications for both instrumental and expressive outcomes, such as job prospects or self-worth evaluations [@contreras_inequality_2019; @kim_social_2021].
-Moreover, social trust facilitates the formation of social ties beyond the ingroup, enabling individuals to rely on others and participate in supportive networks that may even serve as substitutes for welfare provision [@jaime-castillo_social_2016].
-Furthermore, redistributive preferences can be elucidated through economic self-interest.
-Typically, individuals with higher incomes oppose redistribution while acknowledging that reducing inequality would entail an increased tax burden [@meltzer_rational_1981].
-Education also plays a crucial role, providing individuals with greater security to navigate the dynamics of the labor market.
-Higher skills are associated with less support for redistribution, as individuals with higher levels of education are better equipped to handle market uncertainties [@kitschelt_occupations_2014].
-Similarly, job status reflects integration into the labor market.
-Outsiders, who are more vulnerable to labor market fluctuations, tend to be more supportive of redistributive policies [@hausermann_highskilled_2015].
-Finally, besides serving the self-interest of unionized working-class members, unions also function as political socialization agents, nurturing egalitarian values and altruistic motives rooted in class solidarity [@han_labor_2022].
--->
-
-<!-- Sociodemographic characteristics play a significant role in shaping prosocial attitudes.
-Women, for instance, often demonstrate a greater capacity for empathy, motivating them to engage in more communal and relational behavior compared to men [@eagly_his_2009].
-Moreover, women are frequently employed in interpersonal service occupations characterized by lower wages and higher market risk compared to their male counterparts [@waitkus_investigating_2021].
-Age also emerges as a critical factor, with individuals at different life cycle stages exhibiting varying degrees of dependence and exposure to risk.
-Additionally, different age cohorts encompass distinct experiences of economic and political shocks [@vanheuvelen_intercohort_2018].
-Religion further influences attitudes towards redistribution.
-Religious individuals are generally more supportive of redistribution due to the encouragement of altruistic behavior and prosocial values within religious communities.
-However, there is also evidence suggesting that religious behavior may decrease support for redistribution by contributing to individual well-being [@arikan_was_2019].
-Furthermore, individuals without partners tend to exhibit greater support for redistribution.
-This suggests that marital ties serve as a support network through which individuals can mobilize resources and social support [@alesina_preferences_2005].
--->
-
-### _Macro level_ {-}
-
-For measuring economic inequality the Gini index (post-taxes and transfers) from the World Income Inequality Dataset (WID) is employed [@alvaredo_world_2022].
-Additionally, two contextual variables are incorporated as controls in the multilevel models.
-Firstly, employing the Gross Domestic Product (GDP) available in the WID ensures consistency in the economic inequality estimates independently of economic property [@Schmidt-Catran2016; @finseraas_income_2009].
-Secondly, to account for heterogeneity in institutional arrangements stemming from welfare schemes, a measure of the size of the welfare state is included [see @edlund_democratic_2015].
-The measure is a standardized and rescaled indicator from 0 to 100 that combines (i) tax revenue as a percentage of GDP [@ilo_world_2022], (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022], and (iii) the current level of redistribution [@solt_measuring_2020].
-
-## Method
-
-Multilevel linear regression models are employed in all the analyses for accounting by the hierarchical structure of the data given that individuals are nested within countries.
-Therefore, the analysis begins with estimating the null model by declaring the nested structure using random intercept.
-This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to belonging to higher-level units.
-Subsequently, the micro-level models are estimated to determine the association between network homogeneity and the interaction with social class to test hypothesis 1.
-Following this, macro-level models are estimated by incorporating random intercepts alongside random slopes for network homogeneity and social class.
-In this set, a three-way cross-level interaction is estimated to determine if income inequality moderates the interaction between network homogeneity and social class to test hypothesis 2 [^1].
-In the latter model, all the individual-level variables are group-mean centered (CWC) to mitigate possible collinearity problems [@hox_multilevel_2010].
-Additionally, all the country-level factors have been standardized (z-scores) to ease comparability in the estimations [@hox_multilevel_2010].
-For all the analyses, the package `lme4` for in the statistical package `R`  is employed [@bates_fitting_2015].
-
-[^1]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
-Additionally, countries were classified into low, middle-low, middle, middle-high, and high-income inequality groups based on quintiles according to the Gini index.
-Hence, country-fixed effects regressions are used to control for the cross-country differences and observed and unobserved societal characteristics.
+### Dependent variable {-}
+
+I use two indicators to measure redistributive preferences.
+The first indicator, support for government redistribution, is measured by the item: “It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.” The second indicator, egalitarian preferences, is measured by the item: “For a society to be fair, differences in people’s standard of living should be small.” Both indicators use a five-point Likert scale with the following categories: ‘Strongly agree’ (1), ‘Agree’ (2), ‘Neither agree nor disagree’ (3), ‘Disagree’ (4), and ‘Strongly disagree’ (5), and they are shown to be correlated (r = 0.7).
+The indicators were reverse-coded, averaged, and normalized to a range from 0 to 100, where higher values reflect stronger redistributive preferences [@svallfors_government_2013].
+
+### Independent variables - individual level {-}
+
+To measure social class, the Erikson-Goldthorpe-Portocarrero (EGP) class scheme is employed [@Erikson1992].
+The EGP scheme is one of the most consistent and validated measures for social class positions in comparative research and has demonstrated its validity in both industrialized and late-industrialized societies [@evans_political_2013;@barozet_measurement_2021].
+Therefore, information about occupations, self-employment status, and the number of employees is used to classify respondents into different class positions.
+Following previous research, a simplified version of the EGP class scheme that collapses three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
+Specifically, this version distinguishes among the Service Class (Higher and Lower managerial and professionals), Intermediate Class (Routine nonmanual workers and self-employed), and Working Class (Manual supervisors, skilled manual workers, and unskilled manual workers).
+
+I employed the position generator as the basis for measuring class-based network homogeneity.
+This instrument has been widely used in social capital studies and follows an ego-centered approach where social ties to different hierarchical positions in the social structure provide access to social resources [@vandergaag_position_2008].
+In this approach, a list of ten occupations is displayed, and each tie can be classified as "Family or relative," "Close friend," "Someone else I know," or "No one." The first three categories are coded as "Knows" = 1 and "Does not know" = 0, resulting in a total number of social ties per respondent.
+Subsequently, following the procedures outlined by @otero_open_2021, occupations are classified into three groups using the International Socio-Economic Index of Occupational Status (ISEI) from the 2008 version of the International Standard Classification of Occupations (ISCO-08) [@ganzeboom_new_2010] to approximate Goldthorpe's class positions.
+The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *high-status*; school teacher, police officer, and nurse are classified as *middle-status*; and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *low-status* occupations.
+
+Given the above, I adopted established procedures from the literature for measuring homogeneity in ego-centered networks.
+For instance, @volker_birds_2022 computes network homogeneity for gender and education by evaluating the proportion of similar ties based on the characteristics of respondents and their network members.
+Similarly, @otero_lives_2022 employed a comparable method by classifying occupations from the position generator into three class positions to compute the proportion of similar ties based on social class, thereby measuring class-based network homogeneity.
+In this research, I use this latter approach.
+Specifically, I calculate the number of ingroup ties according to the respondents' class position and divide it by the total number of contacts to obtain a measure of network homogeneity.
+This measure represents the proportion of similar social ties within the personal network, where a value of zero indicates complete *heterogeneity* (i.e., all ties are different), and a value of one indicates complete *homogeneity* (i.e., all ties are similar).
+Substantively, higher values reflect a greater social distance from other social classes in society.
+
+First, the number of social ties is included to ensure that the association between network homogeneity and redistributive preferences is independent of network size.
+Second, socioeconomic characteristics are sequentially incorporated into the models, as they represent the current social status through income, education, and labor market status [@kitschelt_occupations_2014;@hausermann_highskilled_2015].
+Third, gender, age, and marital status are included in all models as sociodemographic characteristics to control for the potential influence of gender norms and life course events on attitudes [@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
+
+### Independent variables - country level {-}
+
+To measure economic inequality comparatively, I use the Gini index (post-taxes and transfers) from the World Income Inequality Dataset (WID) [@alvaredo_world_2022].
+Additionally, I incorporate two contextual variables as controls in the multilevel regression.
+First, employing Gross Domestic Product (GDP) in constant 2017 USD (PPP) ensures that economic inequality estimates remain consistent regardless of economic conditions [@wiid_2023].
+Second, following @edlund_democratic_2015, I include a measure of the welfare state that conceptually captures both its overall size and redistributive capacity based on taxation and spending levels.
+This approach provides a more accurate representation of the welfare state's impact by incorporating a broader range of services and reflecting the actual outcomes of welfare policies.
+Empirically, I compute a normalized indicator on a scale from 0 to 100, which combines (i) tax revenue as a percentage of GDP [@ilo_world_2022], (ii) welfare generosity as total governmental spending as a share of GDP [@ilo_world_2022], and (iii) the current level of redistribution [@solt_measuring_2020].
+
+## Methods
+
+I employ multilevel linear regression models in all the analyses for accounting by the hierarchical structure of the data given that individuals are nested within countries.
+The analysis begins by estimating a null model with a random intercept to reflect this nested structure.
+This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to differences between countries.
+Subsequently, micro-level models are estimated to examine the association between network homogeneity and social class to test Hypothesis [^altmodels].
+Following this, macro-level models are estimated by incorporating random intercepts and random slopes for network homogeneity and social class.
+This model tests Hypothesis 2 by estimating a three-way cross-level interaction to determine whether income inequality moderates the interaction between network homogeneity and social class.
+In the latter models, individual-level variables are group-mean centered (CWC) to mitigate collinearity issues between lower- and higher-level predictors and to avoid spurious cross-level interaction coefficients [@aguinis_bestpractice_2013].
+Additionally, all country-level factors are standardized (z-scores) to facilitate comparability in the estimations [@hox_multilevel_2010].
+In all the models, I use the `lme4` package in `R` [@bates_fitting_2015].
+[^lme4]
+
+[^altmodels]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
+Additionally, I classified countries into low, middle-low, middle, middle-high, and high-income inequality groups based on quintiles according to the Gini index.
+Hence, I used country-fixed effects regressions to control for the cross-country differences and observed and unobserved societal characteristics.
 The results are consistent with the multilevel estimations.
 
+[^lme4]: I employed the Restricted Maximum Likelihood (REML) method because it adjusts the estimation of standard errors for small sample sizes and provides better estimates of variance components in the context of cross-national data [@bryan_multilevel_2016].
+
 # Results
 
-## Descriptive
-
-```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country comparison of Redistributive preferences and Social Class ',warning=FALSE}
+## Descriptive cross-country comparison on class, network segregation and redistributive preferences
+
+```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country comparison of redistributive preferences and social class',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
   scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Redistributive Preferences") +
+  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in redistributive preferences by social class") +
   theme(legend.position = "bottom",
@@
 Figure \@ref(fig:fig1) depicts the distribution of redistributive preferences across countries and social classes.
-First, it is possible to notice that the United States has lower redistributive preferences, whereas Russia is a society where redistributive preferences are stronger among all social classes.
-As was expected, in most societies, the working class holds stronger redistributive preferences in contrast to the intermediate and services classes, with four exceptions where the differences are close to zero between both classes.
-However, it is also notable that there are some differences between the two extreme cases.
-For example, in the U.S., the working class held lower redistributive preferences (49.1) than the intermediate class (50.6), but still above the service class (46.8).
-In contrast, in Russia, the general pattern of higher preferences among the working class is maintained, with an escalated decrease in the working (85.5), intermediate (83.5), and service class (83.0).
-
-Another interesting fact is related to class differences in redistributive preferences.
-For example, the differences between the service and the working class are close to 2.3 points in the United States.
-At the same time, Finland represents the average case in the distribution but is also one of societies with the greater class divide in redistributive preferences, showing a gap of 14.1 points between the upper and the lower classes.
-Interestingly, Russian society depicts class differences similar to the U.S., with an average difference of 2.4 points.
+As expected, in most societies, the working class shows stronger redistributive preferences compared to the intermediate and service classes, with four exceptions where the differences between these classes are minimal.
+Notably, there are also some differences between the two extreme cases.
+For instance, in the United States, the working class exhibits lower redistributive preferences (49.1) compared to the intermediate class (50.6), although both classes have higher preferences than the service class (46.8).
+Conversely, in Russia, the general trend of stronger preferences among the working class persists, with a notable decrease in redistributive preferences from the working (85.5) to the intermediate (83.5) and service class (83.0).
+
+<!-- Another interesting observation concerns class differences in redistributive preferences.
+For example, the gap between the service and working classes in the US is approximately 2.3 points.
+In contrast, Finland represents an average case in the distribution but also shows one of the greatest class divides in redistributive preferences, with a 14.1-point gap between the upper and lower classes.
+Interestingly, Russian society exhibits class differences like those in the US, with an average difference of 2.4 points.
+-->
 
@@
   scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Network homogeneity") +
+  scale_y_continuous(limits = c(0,0.7))+
+  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
   theme(legend.position = "bottom",
@@
 
-Regarding network segregation, Figure \@ref(fig:fig2) depicts the distribution of network homogeneity and social class across countries.
-In contrast to redistributive preferences, the distribution of network homogeneity is more scattered between countries and social classes.
-However, it is worth to mention at least two interesting findings.
-First, looking at the sample average (M = 0.36), we can notice that the variation between countries is low (SD = 0.08), with Thailand being the society with higher levels of network segregation (M = 0.43), and Iceland among lowest (M = 0.31).
-Second, it is depicted that the working class network homogeneity drives the pattern of homogeneity.
-In addition, the general pattern is that the service class is less segregated than the intermediate and working class.
-Besides, an interesting fact is that in some cases (e.g., Mexico), although the working class remains highly segregated (above 0.5), the intermediate and service classes are similar in their network homogeneity.
-As noticed, in most cases observed, the general pattern is that the working class is highly homogeneous in their networks, except in the Philippines, where the intermediate class shows a slightly higher average homogeneity.
-Overall, one of the most substantial findings is that the working class is more segregated than the services class.
+Regarding network segregation, Figure \@ref(fig:fig2)  illustrates that, between-country differences in network homogeneity are relatively low, whereas class differences are quite distinguishable.
+Additionally, the general pattern observed is that the working class demonstrates high network homogeneity, except in the Philippines, where the intermediate class shows a slightly higher average homogeneity.
+Moreover, the service class generally exhibits less segregation compared to the intermediate and working classes.
+An interesting observation is that, in cases like Mexico, although the working class remains highly segregated, the intermediate and service classes exhibit similar levels of network segregation.
 
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
 rm(list=ls())
@@
                                      homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "B")
-grid.arrange(fig_egal_homo,fig_homo_gini, nrow = 1)
+grid.arrange(fig_egal_homo,fig_homo_gini, nrow = 1, 
+ bottom =textGrob("Source: International Social Survey 2017; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
+ gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
+  ))
 
@@
 
-Moving to the bivariate macro relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, our main societal characteristic of interest.
-First, according to @cohen_statistical_1988, for effect size criteria, we observe a medium positive and significant association between network homogeneity and redistributive preferences in Panel A (_r_ = 0.43, _p_ <.001).
-In concordance with the previously depicted distribution, we know that higher levels of network homogeneity are driven by the highly segregated networks of the working classes; what makes it logical that in countries where network homogeneity is high, this might also reflect greater social segregation among the working classes and consequently drive higher redistributive preferences.
-Second, Panel B depicts a positive but relatively weak and non significant association between income inequality and network homogeneity (_r_ = 0.28, _p_<.01).
-In other words, average homogeneity also tends to increase in societies with greater income gaps.
-However, the macro association only shows the general pattern between countries but does not allow us to look deeper into class differences according to the levels of inequality.
-
-Interestingly, certain countries with higher levels of inequality and network homogeneity are societies that present class differences between the working class and the services class (e.g., Thailand or Mexico).
-By contrast, more egalitarian countries tend to be less homogeneous and have smaller class differences (e.g., Denmark or Sweden).
-As an additional exploratory analysis (see Fig.
-\@ref(fig:figapp1)), we have found that the association between income inequality and the gap in network homogeneity between the upper and lower classes tends to be moderate and statistically significant (_r_ = 0.3, _p_<.01).
-In other words, income inequality not only increase homogeneity overall but higher social distance between social classes as well.
-
-## Multivariate results
+Regarding the macro-level relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, which is our main societal characteristic of interest.
+Panel A shows a medium positive association between network homogeneity and redistributive preferences (*r* = 0.43).
+Consistent with the previously described distribution, higher levels of network homogeneity are driven by the highly segregated networks of the working classes.
+Thus, in countries where network homogeneity is high, this is likely to reflect greater social segregation among the working classes, which in turn drives higher redistributive preferences.
+Panel B illustrates a positive but relatively weak association between income inequality and network homogeneity (*r* = 0.28), suggesting that in more unequal countries, class-based network homogeneity is also higher.
+Additionally, the differences in network homogeneity between the working class and the service class increase in countries with higher income inequality (*r* = 0.30; see Appendix Fig.
+\@ref(fig:figapp1)).
+Therefore, income inequality not only increases overall network homogeneity but also widens social distance between social classes.
+
+## The segregation hypothesis on redistributive preferences
 
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
-digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
-digclas1_VW_7 <- update(digclas1_VW_5, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
-                    digclas1_VW_3,
+digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
+# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
+digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
+# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
+
+digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
 # digclas1_VW_4,
-                    digclas1_VW_5,
+#digclas1_VW_5,
 # digclas1_VW_6,
@@
               # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+             # "edyears"="Year of Education",
+             # "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+             # "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
               # "unionYes" ="Union Membership (Ref. = Not Unionized)",
@@
 
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
        caption = paste("(\\#tab:table1)","Multilevel models for network homogeneity and redistributive preferences"),
-       custom.note = "\\item Note: Models include sampling weights. Gender, age, and marital status are included as controls. Standard errors in parentheses. %stars",threeparttable = T,
+       custom.note = "\\item Note: Models include sampling weights.
+Gender, age, marital status, education, household income and employment status are included as controls.
+\\item Standard errors in parentheses.
+$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",threeparttable = T,
        caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 3:5, "Household Income (Ref.= Tertile I)"= 6:8,
+       custom.coef.map = ccoef,scalebox = 0.7,
+      groups = list("Social Class (Ref.= Service Class)" = 3:4, 
+                    # "Household Income (Ref.= Tertile I)"= 6:8,
                     # "Partner's Social Class (Ref.= Service Class)" = 12:14,
-      "Homogeneity x Social Class"=10:11),
-      custom.gof.rows = list("Controls"=rep("Yes",5)),include.loglik = FALSE,include.aic = FALSE,
+      "Homogeneity x Social Class"=5:6),
+      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
@@
 The multilevel analysis results are shown in Table \@ref(tab:table1).
-Regarding the first hypothesis, the central argument is that class segregation has differential consequences on redistributive preferences.
-In other words, the association between network homogeneity and redistributive preferences is conditional on class position.
-
-Model 1 integrates our measure of network homogeneity.
-Initially, as previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
-This association persists in Model 2, where we control for network size.
-However, after including social class in Model 3, the relationship between homogeneity and redistributive preferences appears to reverse, with a reduction in statistical significance (_p_<0.10).
-Subsequently, Model 4 incorporates income, education in years and employment status.
-As expected, socioeconomic status is negatively associated with redistributive preferences regarding household economic resources and educational credentials.
-In addition, we find that people outside the labor market do not differ significantly from those who are economically active in their preferences.
-Finally, in Model 5, we see that by incorporating the interaction term between network homogeneity and social class, we observe that the working and intermediate class interaction terms are positive and statistically significant.
-Based on Model 5, Figure \@ref(fig:fig4) shows increased redistributive preferences in homogeneous working-class networks and the intermediate class.
-For the service class, the relationship is reversed, where more homogeneous networks for this social class decrease redistributive preferences.
-Altogether, these results provide evidence in favor of hypothesis 1, where the class divide in redistributive preferences becomes stronger for individuals with more homogeneous social networks.
+On the one hand, I expected that network homogeneity has a weak direct association with redistributive preferences as it reveals only the overall segregation without distinction between classes.
+In this matter, Model 1 integrates network homogeneity and as it is previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
+Then, this association is robust to network size, sociodemographic characteristics, and socioeconomic status in Model 2.
+However, after including individual social class in Model 3, the association between homogeneity and redistributive preferences loses its strength.
+Regarding this, I expected that the inclusion of class suppresses the association of network homogeneity as it is anchored in class position.
+Despite this, the focus of this study is not on the _direct_ association of network homogeneity but I hypothesized the association of homogeneity, and redistributive preferences is conditional to social class.
+
+Thus, the interaction terms of network homogeneity and social class in Model 4 show that compared to the service class, homogeneity increases redistributive preferences in the working and intermediate classes.
+To illustrate this result further, Figure \@ref(fig:fig4) depicts that the increasing redistributive preferences in homogenous working and intermediate class networks are quite mild, where the differences in redistributive preferences go from 69.8 to 72.8 and from 69.4 to 70.47, respectively.
+In contrast, the decreasing redistributive preferences in homogeneous services class networks are more pronounced, changing from 70 when homogeneity is at its lowest point to 62.8 in fully homogeneous networks.
+Altogether, these results provide evidence in favor of the segregation hypothesis (H1), where the class divide in redistributive preferences becomes stronger for individuals with more homogeneous social networks.
 
@@
   scale_y_continuous(limits = c(55,80))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
+  labs(caption = paste0("Source: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". The line is the fitted values with a confident interval at 95%"),
        x="Network homogeneity",y="Redistributive preferences (0 - 100)") +
@@
        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
-
 # int_homo <- digclas1_VW_7
@@
 \newpage
+
+## The mitigation hypothesis on network segregation and redistributive preferences
 
@@
 
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.7,
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,
        caption = paste("(\\#tab:table2)","Multilevel models for income inequality, network homogeneity and redistributive preferences"),
-       custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
+       custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. 
+       $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",
+       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
        custom.coef.map = ccoef,
@@
 Table \@ref(tab:table2) presents the results of the multilevel models for income inequality.
-In Model 1, income inequality demonstrates a positive association, as expected, yet it fails to reach significance.
-Subsequently, Model 2 incorporates economic prosperity through GDP per capita, revealing a negative and significant relationship (*p* > .05).
-Furthermore, Model 3 indicates that including the size of the welfare state establishes a positive and significant relationship (_p_ > .05).
-In contrast, GDP per capita maintains its negative association with redistributive preferences (_p_ > .01).
-In other words, in Model 3, economic prosperity appears to depress redistributive preferences.
-Nevertheless, higher redistributive preferences are observed in countries with more generous welfare states.
-
-Finally, Model 4 incorporates the three-way interaction to determine whether the interaction of network homogeneity and social class on redistributive preferences is moderated by income inequality.
-First, the relationship observed at the micro level retains its original meaning, indicating that segregation in terms of network homogeneity strengthens the class divide in redistributive preferences.
-Second, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
-To better illustrate this result, Figure \@ref(fig:fig5) depicts how the relationship between network homogeneity and social class is more pronounced in societies of lower income inequality and gradually diminishes as inequality increases.
-In other words, the results provide evidence in favor of Hypothesis 2, suggesting that the greater class divide in redistributive preferences observed in more segregated class-based social networks weakens as income inequality increases.
+In the first place, Model 1 shows that there are no substantial differences in redistributive preferences between societies with different levels of income inequality.
+Subsequently, it can be seen in Model 2 that in societies with higher economic prosperity, redistributive preferences are lower regardless of the differences in income inequality between countries.
+At the same time, Model 3 indicates that in countries with more encompassing welfare states, redistributive preferences are higher, independently of income inequality and economic prosperity.
+More simply, higher redistributive preferences are observed in countries with more generous welfare states.
+
+Finally, Model 4 incorporates a three-way interaction to determine whether the conditional association of network homogeneity to social class on redistributive preferences is moderated by income inequality.
+At the micro level, the findings for the segregation hypothesis remain robust.
+At the macro level, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
+To better illustrate this result, Figure \@ref(fig:fig5) depicts how the relationship between network homogeneity and social class is gradually mitigated as income inequality increases.
+In this regard, the left panel in Figure \@ref(fig:fig5) illustrates that under conditions of lower income inequality, the conditional association of network homogeneity and social class on redistributive preferences is more pronounced than in the center and left panels that respectively represent contexts of middle and higher income inequality.
+
+When taking a closer look, the differences in redistributive preferences between the working and service classes are smaller when network homogeneity is low, regardless of income inequality.
+Besides, higher network homogeneity is associated with larger class differences in redistributive preferences when inequality is low but progressively becomes smaller as income inequality increases.
+These results resonate with previous studies that have argued that the upper classes are more sensitive to income inequality, whereas the working class shows relatively stable attitudes regardless of the contextual levels of income inequality.
+Here, the results jointly suggest that network segregation matters in contexts of low and middle economic inequality but loses relevance in contexts of high inequality.
+Overall, the results presented above support the claims of the _mitigation_ hypothesis (H2), where the wider class divide in redistributive preferences produced by homogeneous class-based networks weakens as income inequality increases.
 
@@
   )
-
 df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
@@
        x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
+       caption = paste0("Source: N (Individuals) = ",nobs(homo_V_gini_full2),"; N (Countries) = ",lme4::ngrps(homo_V_gini_full2),
+                        ". The line is the fitted values with a confident interval at 95%")) +
   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
@@
 
-This research asked how class-based network segregation is related to redistributive preferences and to what extent economic inequality moderates this relationship.
-The literature on interpersonal networks has shed light on how network structure harbors not only social resources [@lin_access_1986;@otero_open_2021] but also carries the capacity to establish niches that contribute to the formation of political opinions through social influence, as well as the degree of network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
-In contrast to the previous evidence on the direct diminishing influence of network homogeneity on social cohesion [@otero_lives_2022], the evidence presented in this study suggests that class segregation in terms of network homogeneity widens the already established class divide in redistributive preferences.
-Here, the interaction of class-based network homogeneity and social class shows that for working-class members, homogeneity strengthens their redistributive preferences, while in the service class, homogeneity translates into even lower redistributive preferences.
-
-The theoretical framework of this research posits that the study of the class divide in redistributive preferences should not exclusively address social classes regarding relations in the labor market but observe class in terms of the sociability structure in interpersonal networks.
-The literature has established that processes of social influence [@lindh_missing_2021] and political socialization [@lee_consider_2023] represent mechanisms that echo how social closure in interpersonal networks can trace a divide in redistributive preferences between social classes.
-This 'empathy gulf' [@sachweh_moral_2012] can be observed in how the service class is less willing to take action to strive against inequality as a matter of collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023].
-Additionally, as network homogeneity represents low cross-class ties, it can be argued that lower social integration can undermine social solidarity [@blau_macrosociological_1977], as it consolidates weaker chances of contact between social classes and the lack of knowledge about the lives of others [@vargassalfate_contact_2023].
-
-Besides the micro-level findings, this study has shown that economic inequality moderates the relationship between network segregation and redistributive preferences, which has not previously been discussed in an integrative empirical framework.
-On this behalf, the results from the multilevel models indicate that inequality _mitigates_ the micro-level relationship, which translates into a narrower class gap in redistributive preferences, mainly through changes in the service class.
-Empirically,
-these results resonate with evidence related to the role of inequality in class relations and redistributive preferences.
-It has been argued that in unequal societies, the better-off class tends to become more egalitarian in their attitudes toward economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
-Also, the results engage with the fact that upper classes can consolidate their distinctive position while their advantages allow them to navigate diverse networks at the expense of the marginalization of the poor in contexts of greater inequality [@otero_differences_2023].
-
-In the theoretical framework adopted, economic inequality establishes the field for class relations and conflict that are consequently crystallized in political attitudes, where the class divide in redistributive preferences represents one aspect of the economic domain [@lindh_class_2020].
-In addition, class relations can also be understood as networks of social connections between different class positions.
-Thus, social influence as a network mechanism on redistributive preferences can also be framed as the social force that intensifies class-based mechanisms such as self-interests and values in segregated networks [@lindh_missing_2021].
-Here, the observed weaker interaction between class and homogeneity in more unequal countries can be interpreted in two non-exclusive manners.
+This research examines how class-based network segregation relates to redistributive preferences and the extent to which economic inequality moderates this relationship.
+The literature on interpersonal networks highlights how network structures not only harbor social resources [@lin_access_1986] but also contribute to forming political opinions through social influence and network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
+Contrary to previous evidence suggesting that network homogeneity diminishes social cohesion [@otero_lives_2022], this study indicates that class segregation exacerbates the existing class divide in redistributive preferences.
+Specifically, the interaction of class-based network homogeneity and social class shows that for working-class members, homogeneity strengthens their redistributive preferences, while for the service class, homogeneity results in even lower redistributive preferences.
+
+The theoretical framework of this research posits that studying the class divide in redistributive preferences should not solely address social classes regarding labor market relations but should also observe them through the structure of interpersonal networks.
+The literature has established that processes of social influence and political socialization demonstrate how social closure in interpersonal networks can create a divide in redistributive preferences between social classes [@lee_consider_2023;@lindh_missing_2021].
+This 'empathy gulf' is evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
+Furthermore, since network homogeneity represents low cross-class ties, lower social integration can undermine social solidarity by reducing contact between social classes and limiting knowledge about others' lives [@blau_macrosociological_1977;@otero_lives_2022].
+
+Besides the micro-level findings, this study demonstrates that economic inequality moderates the relationship between network segregation and redistributive preferences, a topic previously unexplored in an integrative empirical framework.
+The results from the multilevel models indicate that inequality *mitigates* the micro-level relationship, resulting in a narrower class gap in redistributive preferences, primarily through changes in the service class.
+These findings align with evidence on the role of inequality in class relations and redistributive preferences.
+Research suggests that in unequal societies, the better-off class tends to adopt more egalitarian attitudes toward economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
+Additionally, the results highlight that upper classes can consolidate their distinctive positions and navigate diverse networks, often at the expense of marginalizing the poor in more unequal contexts [@otero_differences_2023].
+
+In the theoretical framework adopted, economic inequality establishes the field for class relations and conflict, which are consequently crystallized in political attitudes.
+Here, the class divide in redistributive preferences represents one aspect of the economic domain [@lindh_class_2020].
+Class relations can also be understood as networks of social connections between different class positions.
+Thus, social influence as a network mechanism on redistributive preferences can be framed as the social force that intensifies class-based mechanisms, such as self-interests and values, in segregated networks [@lindh_missing_2021].
+The observed weaker interaction between class and homogeneity in more unequal countries can be interpreted in two non-exclusive ways.
 First, network diversity becomes more stratified as inequality increases, meaning that networks in the upper classes become less homogeneous as inequality rises.
 Second, given that the upper classes hold more egalitarian stances in more unequal societies, it is plausible to argue that class homogeneity can also reinforce opinion similarity when redistributive preferences are higher in the upper class.
-Therefore, network segregation could influence opinions by either weakening or reinforcing attitudes based on the average opinion about redistributing within a class.
+Therefore, network segregation could influence opinions by either weakening or reinforcing attitudes based on the average opinion about redistribution within a class.
 
@@
 
-This research is a contribution to the field of study on social class and redistributive preferences, but it also contributes to previous studies that have emphasized the role of social ties in redistributive preferences [@newman_my_2014;@edlund_influence_2003;@langsaether_more_2020].
-In addition, the cross-national component of this research dialogue with previous studies on the role of income inequality on social networks [@pichler_social_2009;@letki_getting_2015;@otero_differences_2023] and class-based research on redistributive preferences [@edlund_democratic_2015;@curtis_how_2015].
-Overall, the diversity of societies analyzed contributes to the literature on redistributive preferences and social networks beyond affluent industrialized countries.
-
-However, the present study entails some limitations.
-On the side of the dependent variable, a two-item index is a rough proxy of what is conceptually claimed as redistributive preferences.
-For example, poverty relief, tax reforms, or market regulations represent concrete actions on how governments strive with popular responses to economic inequality [@mccall_americans_2009;@garcia-sanchez_two_2022].
-Additionally, the position generator included in the questionnaire is limited in its capability to reflect social classes more precisely, particularly the self-employed and intermediate-class positions.
-Hereby, the results should be taken with prudence as the measurement limitations are recognized.
-Finally, as structural contact opportunities and value-based interactions jointly shape social network composition, the cross-sectional data employed prevents causal claims from being made as endogeneity problems between class position, network composition, and attitudes are recognized.
-
-Future research should improve measurement strategies by including already established survey questions on attitudes toward market distribution of social services or willingness to pay taxes as redistributive measures.
-Additionally, class-based social networks can be improved by including other aspects of the market situation of network ties, such as self-employment status or authority in the workplace.
-Finally, longitudinal analyses can contribute to disentangling the causal mechanism involved in the link between social class, networks, and political attitudes.
+This research contributes to the study of social class and redistributive preferences, building on previous work that has emphasized the role of social ties.
+First, the cross-national component of this research complements existing studies on the impact of income inequality on social networks and class-based redistributive preferences.
+Second, the diverse range of societies analyzed extends the literature on redistributive preferences and social networks beyond affluent industrialized countries.
+
+However, this study has certain limitations.
+The dependent variable, represented by a two-item index, is a rough proxy for redistributive preferences compared to more detailed questions on social services, taxes, or poverty policies.
+Additionally, the position generator employed is limited in accurately reflecting social classes, especially the self-employed and intermediate-class positions.
+Thus, the results should be interpreted with caution, recognizing these measurement limitations.
+Finally, because structural contact opportunities and value-based interactions jointly shape social network composition, the cross-sectional data used prevents causal claims due to potential endogeneity issues between class position, network structure, and attitudes.
+
+Future research should improve measurement strategies by including established survey questions on attitudes toward specific welfare policies or willingness to pay taxes as redistributive measures.
+Additionally, class-based social networks can be better assessed by incorporating other aspects of the market situation of network ties, such as self-employment status or workplace authority.
+Finally, longitudinal analyses can help disentangle the causal mechanisms linking social class, networks, and political attitudes.
+
+\newpage
+\begingroup
+\parindent 0pt
+\parskip 2ex
+\def\enotesize{\footnotesize}
+\theendnotes
+\endgroup
 
@@
   egal = egal2,
-  dclass3res_V,
+  dclass3res_V,dclass6res,
   # dclass3spo_V,
@@
   ) 
-
-varlab <- 
-c("Redistributive preferences","Class-based network homogeneity",
-  "Network size",
-  # "Social trust",
-  "Social class",
-  "Household Income","Education in years",
-  # "Partner's Social Class",
-  "Labor status",
-  # "Union membership",
-  "Gender","Age in years",
-  # "Religion",
-  "Has partner",
-  "Income Inequality - Gini Index (post taxes and transfers)",
-  "GDP/capita (in 1000 US dollars)",
-  "Size of the welfare state (0 to 100 scores)")
-
-sjlabelled::set_label(dfreg1) <- varlab
-# names(dfreg) <- varlab
-
-st(dfreg1,labels=T,
-   title="Descriptive Statistics for Study Variables",
-   out = "latex",
-   digits = 2, 
-   factor.counts = F,
-   factor.numeric = F,
-   summ = list(
-     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
-     c('notNA(x)','mean(x)')
-   ),
-   summ.names = list(
-     c('N','Mean','SD','Min','Max'),
-     c('Count','Percent')   
-   ))
-```
-
-\newpage
+```
+
+```{r class-agreg}
+left_join(
+dfreg %>% 
+  group_by(dclass6res,dclass3res_V) %>% summarise(N=n()),
+dfreg %>% 
+  group_by(dclass3res_V) %>% summarise(N=n()),by="dclass3res_V"
+) %>% 
+  kable(booktabs = TRUE,format = "latex", linesep = "",
+        caption = "Level of aggregation of social class",
+        col.names = c("Class (6)","Class (3)","N","N")) %>% 
+  kable_styling(full_width = F,latex_options = "HOLD_position") %>% 
+  collapse_rows(columns = 1:4, valign = "top")
+```
 
@@
   summarise(n=n(),
-            homclass=mean(homclass3_V_res),
+            homclass=mean(x=homclass3_V_res),
             gini_disp=mean(gini_disp),
             loggdppercapita=mean(loggdppercapita),
-            wstate=mean(wstate2),) %>% 
+            wstate=mean(wstate2)) %>% 
   arrange(homclass) %>% 
   kable(digits = 2,booktabs = TRUE,format = "latex", linesep = "",
-        caption = "Contextual variables by country",
+        caption = "Values per country for the macro-social variables",
         col.names = c("Country","N","Network Homogeneity","Gini Index","GDP/capita in $1000","Size of the Welfare State")) %>% 
@@
 
-grid.arrange(fig_homodiff_gini, nrow = 1)
+#cor.test(homo_ineq$diff_working_upper_homo,
+#                                    homo_ineq$gini_disp, use='complete.obs')
+
+grid.arrange(fig_homodiff_gini, nrow = 1, 
+ bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
+ gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
+  ))
 
@@
 
-\pagebreak
-
-# Supplementary analysis
-
-## Income inequality ratios
-
-```{r tab2-ratio9010, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(d10d1))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+         
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/10)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r tab2-ratio9050, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(wid_p90p50))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/50)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-\pagebreak
-## Income inequality groups
-
-```{r table1-ineq-groups, results='asis'}
+```{r table1full, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 # df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
 # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
 dfreg <- na.omit(dfreg)
-tab_countries<- 
-  dfreg %>% 
-  group_by(country3) %>% 
-  summarise(gini_disp=mean(gini_disp)) %>% 
-  mutate(gini_q05=ntile(gini_disp,5),
-         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
-  arrange(gini_d10) %>% 
-  dplyr::select(-gini_disp)
-
-dfreg <- dfreg %>% left_join(tab_countries,by="country3")
 
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
-
-library(estimatr)
-
-# Quintile 1 (low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
-digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 2 (mid-low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
-digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
-digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 3 (middle)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
-digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 4 (middle-high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum + partner +  factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
-digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 5 (high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
-digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
-digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-digclas1_Q05 <- 
-list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
-     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
-     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
+digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
+# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
+digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
+# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
+
+digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
+digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
+# digclas1_VW_4,
+#digclas1_VW_5,
+# digclas1_VW_6,
+digclas1_VW_7)
 
@@
               # socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
+              "femaleFemale"="Female (Ref. = Male)",
+              "agenum"="Age",
               # "age2"="Age2",
@@
              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+             "partnerHas a partner" = "Has partner (Ref.= No partner)",
+                           "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
               # "unionYes" ="Union Membership (Ref. = Not Unionized)",
@@
 
-header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
-texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
-       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
-       custom.note = "Note: Models include sampling weights. Gender, age and marital status are included as controls. Standard errors in parentheses. %stars",
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
+       caption = paste("(\\#tab:table1full)","Multilevel models for network homogeneity and redistributive preferences"),
+       custom.note = "\\item Note: Standard errors in parentheses. $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",threeparttable = T,
        caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.55,
-      groups = list("Social Class (Ref.= Service Class)" = 3:4, "Household Income (Ref.= Tertile I)"= 6:8,  
+       custom.coef.map = ccoef,scalebox = 0.7,
+      groups = list("Household Income (Ref.= Tertile I)"= 6:8,
+                    "Social Class (Ref.= Service Class)" = 11:12, 
                     # "Partner's Social Class (Ref.= Service Class)" = 12:14,
-                    "Homogeneity x Social Class"=10:11),
-      custom.gof.rows = list("Country FE"=rep("Yes",10)),
-      # include.loglik = FALSE,include.aic = FALSE,
-      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+                    "Homogeneity x Social Class"=13:14
+      ),
+      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
        float.pos = "h!",
@@
        use.packages = F)
-```
-
-```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditioned by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
-marginal <- bind_rows(
-plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
-plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
-plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
-plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
-plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
-marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
-marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
-
-ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
-  geom_point(size=2) + 
-  geom_errorbar(width=.2)+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_hline(yintercept = 0,color="red") +
-  facet_grid(~quintile) +
-  labs(x=NULL,y="Redistributive preferences"
-       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
-       )
-
-```
-
-\pagebreak
-
-<!-- ## OECD Countries -->
-
-```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1) 
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------$
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-\pagebreak
-
-## Social Distance by ISEI
-
-First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010] for each occupation of the position generator are calculated.
-Second, the ISEI score of the respondent (R's) is subtracted from the average ISEI points of the personal network.
-For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
-Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance.
-In addition, when the distance is 0, the network is entirely homogeneous.
-
-To facilitate the interpretation of the indicator, we have calculated a homogeneity indicator based on social distance:
-
-1. The absolute values are calculated to represent the total distance to occupations concerning R's ISEI score.
-2. Since there are values of 0 representing absolute homogeneity, the variable is rescaled by summing 1.
-3. The values were inverted to make higher values represent higher homogeneity.
-
-Thus, higher values represent greater homogeneity regarding R's ISEI score in contrast to the average network ISEI score.
-
-```{r desc-social, eval=FALSE, include=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,correlation)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-```
-
-```{r table1-socdist, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dummy_df <- df1 %>% dplyr::select(id,
-  egal = egal2,dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,edyears,female,agenum,
-  # religion,
-  partner,
-  # union,
-  workst,WEIGHT,region,
-  "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
-  ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita,
-  oecd,country2, country, country3) %>%
-  filter(country2 != "SVN") %>% 
-  # filter(oecd == "OECD") %>%
-  na.omit() %>% 
-  dplyr::select(id)
-
-df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
-df1$isei08 <- car::recode(df1$isei08,"NA=0")
-
-dfreg <- df1 %>% dplyr::select(id,
-  egal = egal2,
-  dclass3res_V=isei08,
-  # dclass3spo_V=isei08sp,
-  homclass3_V_res=socdist,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  # religion,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         dclass3res_V=dclass3res_V/10,
-         # dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10
-         ) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")  %>% 
-  filter(id %in% dummy_df$id)
-dfreg <- na.omit(dfreg)
-
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values) 
-dfreg$homclass3_V_res <- reversed_values
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
-digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
-                    digclas1_VW_3,
-                    # digclas1_VW_4,
-                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
-
-ccoef <- list(homclass3_V_res="Social Distance /10",
-              know_total="Network size",
-              # socialtrust="Social Trust",
-              # "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              # "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "dclass3res_V"="ISEI/10",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              # "dclass3spo_V" = "ISEI/10 (Partner)",
-              "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI")
-
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table2)","Multilevel models for Social Distance and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
-      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-       use.packages = F)
-```
-
-\newpage
-
-```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditioned by ISEI on Redistributive Preferences',warning=FALSE}
-int_homo <- digclas1_VW_7
-plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V" = "threenum"))+
-labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="ISEI",y="Redistributive preferences")
-```
-
-```{r fig1-pred-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Social Distance on Redistributive Preferences by ISEI',warning=FALSE}
-int_homo <- digclas1_VW_7
-df_pred1 <- 
-  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.5),
-                                 dclass3res_V = c(min(dfreg$dclass3res_V),mean(dfreg$dclass3res_V),max(dfreg$dclass3res_V))))
-
-df_pred1$dclass3res_V <- factor(df_pred1$dclass3res_V,labels = c("ISEI (min)","ISEI (Mean)", "ISEI (max)"))
-
-# names(df_pred1)
-df_pred1 %>% 
-ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=2,color="black") +
-  # facet_grid(~dclass3res_V) +
-  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(40,100))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social distance",y="Redistributive preferences") +
-  theme(legend.position = "bottom", legend.title = element_blank())
-```
-
-\pagebreak
-
-```{r tab2-socdist, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-dummy_df <- df1 %>% dplyr::select(id,
-  egal = egal2,dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,know_total,
-  # socialtrust,
-  Q03pcm,edyears,female,agenum,
-  # religion,
-  partner,
-  # union,
-  workst,WEIGHT,region,
-  "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev,
-  ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita,
-  oecd,country2, country, country3) %>%
-  filter(country2 != "SVN") %>% 
-  # filter(oecd == "OECD") %>%
-  na.omit() %>% 
-  dplyr::select(id)
-
-df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
-dfreg <- df1 %>% dplyr::select(id,
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V=isei08,
-  # dclass3spo_V=isei08sp,
-  homclass3_V_res=socdist,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp),
-         dclass3res_V=dclass3res_V/10,
-         # dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10
-         ) %>% 
-  filter(id %in% dummy_df$id)
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-# hist(reversed_values);summary(reversed_values)
-
-dfreg$homclass3_V_res <- reversed_values
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-dfreg$dclass3res_V = group_center(as.numeric(dfreg$dclass3res_V), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-# dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Social Distance (CWC)",
-              "dclass3res_V"="ISEI ",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_V" = "Distance*ISEI",
-              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
-              "dclass3res_V:gini_disp" ="ISEI*Inequality",
-              "homclass3_V_gc:dclass3res_V:gini_disp" = "Distance*Working Class*Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Social Distance and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance*Social Class"=7:8, "Distance * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Soc. Distance",
-                           "Var: Group ISEI",
-                           "Cov: Group (Intercept), Soc. Distance",
-                           "Cov: Group (Intercept), ISEI",                           
-                           "Cov: Group Soc. Distance, ISEI",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------$
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5),
-      dclass3res_V=c(min(dfreg$dclass3res_V),max(dfreg$dclass3res_V))
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-
-df_pred_giniD_gc$dclass3res_V <- factor(df_pred_giniD_gc$dclass3res_V,labels = c("ISEI (min)","ISEI (max)"))
-# df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc$dclass3res_V <- as.factor(df_pred_giniD_gc$dclass3res_V)
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Social Distance (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-```{r table1-alternative, eval=FALSE, include=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V=dclass6res,
-  # homclass3_V_res=homclass3_V_res_part,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  # religion,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_3<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_4<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  know_total + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_6<- lmer(egal~1 + homclass3_V_res + female+agenum+ 
-                       partner +  know_total +   
-                       dclass3res_V + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_7<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +   know_total +  
-                       dclass3res_V +  edyears + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_8<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm +(1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_9<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total +  
-                       dclass3res_V +  edyears +  Q03pcm + workst +(1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_10<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm + workst + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_10a<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm + workst + (homclass3_V_res|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_11 <- update(digclas1_VW_10, . ~ . +dclass3res_V*homclass3_V_res)
-
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,digclas1_VW_3,digclas1_VW_4,
-                    digclas1_VW_6,digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,digclas1_VW_10a,
-                    digclas1_VW_11)
-
-screenreg(digclas1_VW)
-plot_slopes(digclas1_VW_11, variables = "homclass3_V_res", by = "dclass3res_V",draw = T)
-```
+# performance::check_collinearity(digclas1_VW_5)
+# performance::check_model(digclas1_VW_5,check="vif")
+# performance::icc(digclas1_VW_5)
+```

### 2024-07-09 paper1_jiturra_supp-material.Rmd
update

@@
 
-```{r eval=FALSE, include=FALSE}
- # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
- # clean #in the yml
- rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::pdf_document2")
- rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::html_document2")
- rmarkdown::render("paper1_jiturra_supp-material.Rmd", output_format = "bookdown::word_document2")
-
- # install.packages("trackdown")
- trackdown::update_file(file = "paper1_jiturra.Rmd", hide_code = TRUE,gpath = '001_PhD/002dissertation/paper1')
-
-```
-
-<!-- - considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad -->
-<!-- - darle una oportunidad al h-index -->
-<!--     - en general es prácticamente lo mismo que el indicador de homogeneidad -->
-<!-- - controlaria por social activities index () -->
-<!-- - social resources  -->
-
 ```{r setup, include=FALSE}
@@
 \pagebreak
-# Additional analysis
-
-## OECD Countries
-
-```{r tab2-ocde, results='asis', cache=TRUE}
+
+# Supplementary material
+
+## Income inequality ratios
+
+```{r tab2-ratio9010, results='asis', cache=TRUE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 rm(list=ls())
+
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
@@
   agenum,
-  religion,
+  # religion,
   partner,
-  union,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(d10d1))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+         
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/10)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r tab2-ratio9050, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(wid_p90p50))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/50)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+\pagebreak
+## Income inequality groups
+
+```{r table1-ineq-groups, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  # religion,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+tab_countries<- 
+  dfreg %>% 
+  group_by(country3) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_q05=ntile(gini_disp,5),
+         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
+  arrange(gini_d10) %>% 
+  dplyr::select(-gini_disp)
+
+dfreg <- dfreg %>% left_join(tab_countries,by="country3")
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+
+library(estimatr)
+
+# Quintile 1 (low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 2 (mid-low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
+digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 3 (middle)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 4 (middle-high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum + partner +  factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 5 (high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
+digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_Q05 <- 
+list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
+     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
+     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              # socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+
+header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
+texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
+       custom.note = "Note: Models include sampling weights. Gender, age and marital status are included as controls. Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.55,
+      groups = list("Social Class (Ref.= Service Class)" = 3:4, "Household Income (Ref.= Tertile I)"= 6:8,  
+                    # "Partner's Social Class (Ref.= Service Class)" = 12:14, 
+                    "Homogeneity x Social Class"=10:11),
+      custom.gof.rows = list("Country FE"=rep("Yes",10)),
+      # include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+      # file = "table1.html"
+       use.packages = F)
+```
+
+```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditioned by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+marginal <- bind_rows(
+plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
+plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
+plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
+plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
+plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
+marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
+marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
+
+ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
+  geom_point(size=2) + 
+  geom_errorbar(width=.2)+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0,color="red") +
+  facet_grid(~quintile) +
+  labs(x=NULL,y="Redistributive preferences"
+       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
+       )
+
+```
+
+\pagebreak
+
+<!-- ## OECD Countries -->
+
+```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1) 
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
   workst,
@@
   mutate(to_dummy(female),
-         to_dummy(union),
+         # to_dummy(union),
          to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
+         # dummy for categorical variables-------------------------------------$
          to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
+         # to_dummy(dclass3spo_V)
   )
 dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
 dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
@@
 
-```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------
+```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------$
 # ginid_max<- round(max(dfreg$gini_disp) ,2)
@@
 
-## Income Inequality Ratios (OECD)
-
-```{r tab2-ratio9010, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(d10d1))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/10)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r tab2-ratio9050, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(wid_p90p50))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/50)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
 \pagebreak
 
-## Social distance (OECD)
-
-```{r desc-socdist,eval=FALSE, include=FALSE}
+## Social Distance by ISEI
+
+First, the average scores of the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010] for each occupation of the position generator are calculated.
+Second, the ISEI score of the respondent (R's) is subtracted from the average ISEI points of the personal network.
+For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance.
+Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance.
+In addition, when the distance is 0, the network is entirely homogeneous.
+
+To facilitate the interpretation of the indicator, the homogeneity indicator based on social distance is calculated:
+
+1. The absolute values are calculated to represent the total distance to occupations concerning R's ISEI score.
+2. Since there are values of 0 representing absolute homogeneity, the variable is rescaled by summing 1.
+3. The values were inverted to make higher values represent higher homogeneity.
+
+Thus, higher values represent greater homogeneity regarding R's ISEI score in contrast to the average network ISEI score.
+
+```{r desc-social, eval=FALSE, include=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
          homclass3_V_res=homclass3_V_res/10) %>%
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN")
@@
 ```
-
-### Social Distance by Social Class
-
-```{r table1-socdistclass, echo=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         homclass3_V_res=homclass3_V_res/10) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-dfreg$homclass3_V_res <- reversed_values
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
-digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
-
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
-digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,
-                    digclas1_VW_3,
-                    # digclas1_VW_4,
-                    digclas1_VW_5,digclas1_VW_6,digclas1_VW_7)
-
-ccoef <- list(homclass3_V_res="Social distance",
-              know_total="Network size",
-              socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",
-              "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class")
-
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table2)","Multilevel models for Social distance and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.60,
-      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Social distance x Social Class"=15:16),
-      custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-       use.packages = F)
-```
-
-```{r fig1-marg-socdistclass, echo=FALSE, fig.cap='Average Marginal Effects of Social Distance conditionated by Social Class on Redistributive Preferences', fig.dim=c(10,5), warning=FALSE}
-int_homo <- digclas1_VW_7
-plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+
-labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social Distance",y="Redistributive preferences")
-```
-
-```{r fig1-pred-socdistclass, echo=FALSE, fig.cap='Linear Predictions for Social distance on Redistributive Preferences by Social Class', fig.dim=c(10,5), warning=FALSE}
-int_homo <- digclas1_VW_7
-df_pred1 <-
-  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 1),
-                                 dclass3res_V = levels(dfreg$dclass3res_V)))
-# names(df_pred1)
-df_pred1 %>%
-ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=2,color="black") +
-  facet_grid(~factor(dclass3res_V, levels=
-                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
-                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
-  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(50,100))+
-  # scale_x_continuous(limits = c(-9,9))+
-  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social Distance",y="Redistributive preferences") +
-  theme(legend.position = "none", legend.title = element_blank())
-```
-
-\pagebreak
-
-```{r tab2-socdistclass, echo=FALSE, cache=TRUE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  religion,
-  partner,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>%
-  na.omit() %>%
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         gini_disp=scale(gini_disp),
-         homclass3_V_res=homclass3_V_res/10)
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-# Step 1: Calculate absolute values
-absolute_values <- abs(dfreg$homclass3_V_res)
-# hist(absolute_values);summary(absolute_values)
-
-# Step 2: Add 1 to all values to eliminate zeros
-modified_values <- absolute_values + 0.1
-# hist(modified_values);summary(modified_values)
-
-# Step 3: Reverse the order of the scale
-reversed_values <- max(modified_values) + 0.1 - modified_values
-dfreg$homclass3_V_res <- reversed_values
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <-
-  dfreg %>%
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm),
-         to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-homo_V_gini <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         socialtrust_gc+
-         dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         union_gc+workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Social distance (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class",
-              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Distance*Working Class*Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance x Social Class"=7:8, "Distance * Social Class x Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-socdistclass, echo=FALSE, fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
-### Predicted values homo*class*GiniD ---------------------------------------
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>%
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Social Distance (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-\pagebreak
-
-### Social Distance by ISEI
 
@@
   filter(country2 != "SVN") %>% 
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   na.omit() %>% 
@@
          dclass3res_V=dclass3res_V/10,
-         dclass3spo_V=dclass3spo_V/10,
-         homclass3_V_res=homclass3_V_res/10) %>%
-  filter(oecd == "OECD") %>%
+         # dclass3spo_V=dclass3spo_V/10,
+         homclass3_V_res=homclass3_V_res/10
+         ) %>%
+  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN")  %>% 
@@
 dfreg <- na.omit(dfreg)
+
 # Step 1: Calculate absolute values
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
-
+# hist(reversed_values);summary(reversed_values) 
 dfreg$homclass3_V_res <- reversed_values
 
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust)
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total)
 digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V)
 
-digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2)
-digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union)
-digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
+digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum)
+digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
 digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res)
@@
 
-```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE}
+\newpage
+
+```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditioned by ISEI on Redistributive Preferences',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
 ) %>%
-  filter(oecd == "OECD") %>%
+  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN") %>% 
@@
 reversed_values <- max(modified_values) + 0.1 - modified_values
+# hist(reversed_values);summary(reversed_values)
+
 dfreg$homclass3_V_res <- reversed_values
 
-# Variable Group-Centering ------------------------------------------------
+# Variable Group-Centering ------------------------------------------------$
 dfreg <- 
@@
   mutate(to_dummy(female),
-         to_dummy(union),
+         # to_dummy(union),
          to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
+         # dummy for categorical variables-------------------------------------$
          to_dummy(Q03pcm),
@@
 ```
+
+```{r table1-alternative, eval=FALSE, include=FALSE, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V=dclass6res,
+  # homclass3_V_res=homclass3_V_res_part,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  # religion,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_2<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_3<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_4<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  know_total + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_6<- lmer(egal~1 + homclass3_V_res + female+agenum+ 
+                       partner +  know_total +   
+                       dclass3res_V + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_7<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +   know_total +  
+                       dclass3res_V +  edyears + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_8<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm +(1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_9<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total +  
+                       dclass3res_V +  edyears +  Q03pcm + workst +(1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_10<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm + workst + (1|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_10a<- lmer(egal~1 + homclass3_V_res + female+agenum+
+                       partner +  know_total + 
+                       dclass3res_V +  edyears +  Q03pcm + workst + (homclass3_V_res|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_VW_11 <- update(digclas1_VW_10, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,digclas1_VW_3,digclas1_VW_4,
+                    digclas1_VW_6,digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,digclas1_VW_10a,
+                    digclas1_VW_11)
+
+screenreg(digclas1_VW)
+plot_slopes(digclas1_VW_11, variables = "homclass3_V_res", by = "dclass3res_V",draw = T)
+```
+
+<!-- # Additional analysis -->
+
+<!-- ## OECD Countries -->
+
+<!-- ```{r tab2-ocde, results='asis', cache=TRUE} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+<!-- options(scipen=999) -->
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
+<!-- rm(list=ls()) -->
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   # starts_with("class3"), -->
+<!--   # starts_with("digclass3"), -->
+<!--   # starts_with("dclass3"), -->
+<!--   # starts_with("homclass"), -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   religion, -->
+<!--   partner, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   abs_red, -->
+<!--   ilo_taxrev, -->
+<!--   ilo_govspe, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   na.omit() %>%  -->
+<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2,  -->
+<!--          gini_disp=scale(gini_disp)) -->
+
+<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
+
+<!-- # Variable Group-Centering ------------------------------------------------ -->
+<!-- dfreg <-  -->
+<!--   dfreg %>%  -->
+<!--   mutate(to_dummy(female), -->
+<!--          to_dummy(union), -->
+<!--          to_dummy(workst), -->
+<!--          # dummy for categorical variables------------------------------------- -->
+<!--          to_dummy(Q03pcm), -->
+<!--          to_dummy(dclass3spo_V) -->
+<!--   ) -->
+<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
+<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
+<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
+<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
+<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
+<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
+<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
+<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
+<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
+<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
+<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
+
+<!-- # Household Income Tercile -->
+<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
+
+<!-- # Partner Social Class -->
+<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
+
+<!-- # drop dummies -->
+<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
+<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
+<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
+
+<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- homo_V_gini <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_wstate2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_controls <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2 + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_full2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          homclass3_V_gc* -->
+<!--          dclass3res_V* -->
+<!--          gini_disp +  -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- digclas1_macro <- list(homo_V_gini, -->
+<!--                        homo_V_gini_gdp, -->
+<!--                        homo_V_gini_gdp_wstate2, -->
+<!--                        homo_V_gini_full2) -->
+
+<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
+<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               "gini_disp" = "Income inequality (Gini index)", -->
+<!--               loggdppercapita = "GDP/capita", -->
+<!--               wstate2="Size of the welfare state", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
+<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
+
+<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
+<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
+<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T,single.row = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
+<!--        float.pos = "h!", -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
+<!--                            "Var: Group (Intercept)", -->
+<!--                            "Var: Group Homogeneity", -->
+<!--                            "Var: Group Intermediate Class ", -->
+<!--                            "Var: Group Working Class", -->
+<!--                            "Cov: Group (Intercept), Homogeneity", -->
+<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
+<!--                            "Cov: Group (Intercept), Working Class", -->
+<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
+<!--                            "Cov: Group Homogeneity, Working Class", -->
+<!--                            "Cov: Group Intermediate Class, Working Class", -->
+<!--                            "Var: Residual"), -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'} -->
+<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
+<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
+<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
+
+<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
+<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
+<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
+
+<!-- df_pred_giniD_gc <- -->
+<!--   predictions( -->
+<!--     homo_V_gini_full2,newdata = datagrid( -->
+<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
+<!--       wstate2=mean(dfreg$wstate2), -->
+<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
+<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1), -->
+<!--       dclass3res_V=levels(dfreg$dclass3res_V) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
+<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
+<!-- df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
+
+<!-- df_pred_giniD_gc %>%  -->
+<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
+<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
+<!--   geom_line(size=1,color="black") + -->
+<!--   geom_point(size=3, shape = 21,color="black") + -->
+<!--   facet_wrap(~gini_disp) + -->
+<!--   labs(y = "Preferences for Redistribution", -->
+<!--        x="Network homogeneity (CWC)", -->
+<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
+<!--        ) + -->
+<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
+<!--                      ) + -->
+
+<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   theme(legend.position = "bottom", -->
+<!--         legend.direction = "horizontal", -->
+<!--         axis.text=element_text(size=15), -->
+<!--         legend.title = element_blank(), -->
+<!--         legend.background = element_blank(), -->
+<!--         legend.box.background = element_rect(colour = "black")) -->
+<!-- ``` -->
+
+<!-- ## Income Inequality Ratios (OECD) -->
+
+<!-- ```{r tab2-ratio9010, results='asis', cache=TRUE} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+<!-- options(scipen=999) -->
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   # starts_with("class3"), -->
+<!--   # starts_with("digclass3"), -->
+<!--   # starts_with("dclass3"), -->
+<!--   # starts_with("homclass"), -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   religion, -->
+<!--   partner, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   abs_red, -->
+<!--   ilo_taxrev, -->
+<!--   ilo_govspe, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   na.omit() %>%  -->
+<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2,  -->
+<!--          gini_disp=scale(d10d1)) -->
+
+<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
+
+<!-- # Variable Group-Centering ------------------------------------------------ -->
+<!-- dfreg <-  -->
+<!--   dfreg %>%  -->
+<!--   mutate(to_dummy(female), -->
+<!--          to_dummy(union), -->
+<!--          to_dummy(workst), -->
+<!--          # dummy for categorical variables------------------------------------- -->
+<!--          to_dummy(Q03pcm), -->
+<!--          to_dummy(dclass3spo_V) -->
+<!--   ) -->
+<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
+<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
+<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
+<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
+<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
+<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
+<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
+<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
+<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
+<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
+<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
+
+<!-- # Household Income Tercile -->
+<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
+
+<!-- # Partner Social Class -->
+<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
+
+<!-- # drop dummies -->
+<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
+<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
+<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
+
+<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- homo_V_gini <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_wstate2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_controls <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2 + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_full2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          homclass3_V_gc* -->
+<!--          dclass3res_V* -->
+<!--          gini_disp +  -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- digclas1_macro <- list(homo_V_gini, -->
+<!--                        homo_V_gini_gdp, -->
+<!--                        homo_V_gini_gdp_wstate2, -->
+<!--                        homo_V_gini_full2) -->
+
+<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
+<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               "gini_disp" = "Income inequality (Ratio 90/10)", -->
+<!--               loggdppercapita = "GDP/capita", -->
+<!--               wstate2="Size of the welfare state", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
+<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
+
+<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50, -->
+<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
+<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T,single.row = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
+<!--        float.pos = "h!", -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
+<!--                            "Var: Group (Intercept)", -->
+<!--                            "Var: Group Homogeneity", -->
+<!--                            "Var: Group Intermediate Class ", -->
+<!--                            "Var: Group Working Class", -->
+<!--                            "Cov: Group (Intercept), Homogeneity", -->
+<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
+<!--                            "Cov: Group (Intercept), Working Class", -->
+<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
+<!--                            "Cov: Group Homogeneity, Working Class", -->
+<!--                            "Cov: Group Intermediate Class, Working Class", -->
+<!--                            "Var: Residual"), -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r tab2-ratio9050, results='asis', cache=TRUE} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+<!-- options(scipen=999) -->
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   # starts_with("class3"), -->
+<!--   # starts_with("digclass3"), -->
+<!--   # starts_with("dclass3"), -->
+<!--   # starts_with("homclass"), -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   religion, -->
+<!--   partner, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   abs_red, -->
+<!--   ilo_taxrev, -->
+<!--   ilo_govspe, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   na.omit() %>%  -->
+<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2,  -->
+<!--          gini_disp=scale(wid_p90p50)) -->
+
+<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
+
+<!-- # Variable Group-Centering ------------------------------------------------ -->
+<!-- dfreg <-  -->
+<!--   dfreg %>%  -->
+<!--   mutate(to_dummy(female), -->
+<!--          to_dummy(union), -->
+<!--          to_dummy(workst), -->
+<!--          # dummy for categorical variables------------------------------------- -->
+<!--          to_dummy(Q03pcm), -->
+<!--          to_dummy(dclass3spo_V) -->
+<!--   ) -->
+<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
+<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
+<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
+<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
+<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
+<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
+<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
+<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
+<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
+<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
+<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
+
+<!-- # Household Income Tercile -->
+<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
+
+<!-- # Partner Social Class -->
+<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
+
+<!-- # drop dummies -->
+<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
+<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
+<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
+
+<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- homo_V_gini <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_wstate2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_controls <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2 + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_full2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          homclass3_V_gc* -->
+<!--          dclass3res_V* -->
+<!--          gini_disp +  -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- digclas1_macro <- list(homo_V_gini, -->
+<!--                        homo_V_gini_gdp, -->
+<!--                        homo_V_gini_gdp_wstate2, -->
+<!--                        homo_V_gini_full2) -->
+
+<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
+<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               "gini_disp" = "Income inequality (Ratio 90/50)", -->
+<!--               loggdppercapita = "GDP/capita", -->
+<!--               wstate2="Size of the welfare state", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
+<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
+
+<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50, -->
+<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
+<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T,single.row = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
+<!--        float.pos = "h!", -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
+<!--                            "Var: Group (Intercept)", -->
+<!--                            "Var: Group Homogeneity", -->
+<!--                            "Var: Group Intermediate Class ", -->
+<!--                            "Var: Group Working Class", -->
+<!--                            "Cov: Group (Intercept), Homogeneity", -->
+<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
+<!--                            "Cov: Group (Intercept), Working Class", -->
+<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
+<!--                            "Cov: Group Homogeneity, Working Class", -->
+<!--                            "Cov: Group Intermediate Class, Working Class", -->
+<!--                            "Var: Residual"), -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ## Social distance (OECD) -->
+
+<!-- ```{r desc-socdist,eval=FALSE, include=FALSE} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,correlation) -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res=socdist, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   partner, -->
+<!--   religion, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   mutate(logrgdpna = log(rgdpna), -->
+<!--          loggdppercapita=log(gdppercapita), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2, -->
+<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") -->
+
+<!-- dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV) -->
+
+<!-- dfreg <- na.omit(dfreg) -->
+<!-- ``` -->
+
+<!-- ### Social Distance by Social Class -->
+
+<!-- ```{r table1-socdistclass, echo=FALSE, results='asis'} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res=socdist, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   partner, -->
+<!--   religion, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   mutate(logrgdpna = log(rgdpna), -->
+<!--          loggdppercapita=log(gdppercapita), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2, -->
+<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") -->
+
+<!-- dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV) -->
+
+<!-- dfreg <- na.omit(dfreg) -->
+
+<!-- # Step 1: Calculate absolute values -->
+<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
+<!-- # hist(absolute_values);summary(absolute_values) -->
+
+<!-- # Step 2: Add 1 to all values to eliminate zeros -->
+<!-- modified_values <- absolute_values + 0.1 -->
+<!-- # hist(modified_values);summary(modified_values) -->
+
+<!-- # Step 3: Reverse the order of the scale -->
+<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
+<!-- dfreg$homclass3_V_res <- reversed_values -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT) -->
+<!-- digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust) -->
+<!-- digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V) -->
+
+<!-- digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2) -->
+<!-- digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union) -->
+<!-- digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V) -->
+<!-- digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res) -->
+<!-- digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2, -->
+<!--                     digclas1_VW_3, -->
+<!--                     # digclas1_VW_4, -->
+<!--                     digclas1_VW_5,digclas1_VW_6,digclas1_VW_7) -->
+
+<!-- ccoef <- list(homclass3_V_res="Social distance", -->
+<!--               know_total="Network size", -->
+<!--               socialtrust="Social Trust", -->
+<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               # "femaleFemale"="Female (Ref. = Male)", -->
+<!--               # "agenum"="Age", -->
+<!--               # "age2"="Age2", -->
+<!--               "edyears"="Year of Education", -->
+<!--               "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)", -->
+<!--               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)", -->
+<!--               "unionYes" ="Union Membership (Ref. = Not Unionized)", -->
+<!--               "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)", -->
+<!--               "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)", -->
+<!--               "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)", -->
+<!--               "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class", -->
+<!--               "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class") -->
+
+<!-- texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1), -->
+<!--        caption = paste("(\\#tab:table2)","Multilevel models for Social distance and Redistributive Preferences"), -->
+<!--        custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--        symbol = "+",scalebox = 0.60, -->
+<!--       groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Social distance x Social Class"=15:16), -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"), -->
+<!--        float.pos = "h!", -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r fig1-marg-socdistclass, echo=FALSE, fig.cap='Average Marginal Effects of Social Distance conditionated by Social Class on Redistributive Preferences', fig.dim=c(10,5), warning=FALSE} -->
+<!-- int_homo <- digclas1_VW_7 -->
+<!-- plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+ -->
+<!-- labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
+<!--        x="Social Distance",y="Redistributive preferences") -->
+<!-- ``` -->
+
+<!-- ```{r fig1-pred-socdistclass, echo=FALSE, fig.cap='Linear Predictions for Social distance on Redistributive Preferences by Social Class', fig.dim=c(10,5), warning=FALSE} -->
+<!-- int_homo <- digclas1_VW_7 -->
+<!-- df_pred1 <- -->
+<!--   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"), -->
+<!--               newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 1), -->
+<!--                                  dclass3res_V = levels(dfreg$dclass3res_V))) -->
+<!-- # names(df_pred1) -->
+<!-- df_pred1 %>% -->
+<!-- ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
+<!--   geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") + -->
+<!--   geom_line(size=1,color="black") + -->
+<!--   geom_point(size=2,color="black") + -->
+<!--   facet_grid(~factor(dclass3res_V, levels= -->
+<!--                        c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"), -->
+<!--                      c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) + -->
+<!--   scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
+<!--   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
+<!--   scale_y_continuous(limits = c(50,100))+ -->
+<!--   # scale_x_continuous(limits = c(-9,9))+ -->
+<!--   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
+<!--        x="Social Distance",y="Redistributive preferences") + -->
+<!--   theme(legend.position = "none", legend.title = element_blank()) -->
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ```{r tab2-socdistclass, echo=FALSE, cache=TRUE, results='asis'} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+<!-- options(scipen=999) -->
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- dfreg <- df1 %>% dplyr::select( -->
+<!--   egal = egal2, -->
+<!--   # starts_with("class3"), -->
+<!--   # starts_with("digclass3"), -->
+<!--   # starts_with("dclass3"), -->
+<!--   # starts_with("homclass"), -->
+<!--   dclass3res_V, -->
+<!--   dclass3spo_V, -->
+<!--   homclass3_V_res=socdist, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   religion, -->
+<!--   partner, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   abs_red, -->
+<!--   ilo_taxrev, -->
+<!--   ilo_govspe, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") %>% -->
+<!--   na.omit() %>% -->
+<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2, -->
+<!--          gini_disp=scale(gini_disp), -->
+<!--          homclass3_V_res=homclass3_V_res/10) -->
+
+<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
+<!-- # Step 1: Calculate absolute values -->
+<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
+<!-- # hist(absolute_values);summary(absolute_values) -->
+
+<!-- # Step 2: Add 1 to all values to eliminate zeros -->
+<!-- modified_values <- absolute_values + 0.1 -->
+<!-- # hist(modified_values);summary(modified_values) -->
+
+<!-- # Step 3: Reverse the order of the scale -->
+<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
+<!-- dfreg$homclass3_V_res <- reversed_values -->
+
+<!-- # Variable Group-Centering ------------------------------------------------ -->
+<!-- dfreg <- -->
+<!--   dfreg %>% -->
+<!--   mutate(to_dummy(female), -->
+<!--          to_dummy(union), -->
+<!--          to_dummy(workst), -->
+<!--          # dummy for categorical variables------------------------------------- -->
+<!--          to_dummy(Q03pcm), -->
+<!--          to_dummy(dclass3spo_V) -->
+<!--   ) -->
+<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
+<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
+<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
+<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
+<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
+<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
+<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
+<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
+<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
+<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
+<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
+
+<!-- # Household Income Tercile -->
+<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
+
+<!-- # Partner Social Class -->
+<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
+
+<!-- # drop dummies -->
+<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
+<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
+<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
+
+<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- homo_V_gini <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_wstate2 <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_controls <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2 + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_full2 <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          homclass3_V_gc* -->
+<!--          dclass3res_V* -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- digclas1_macro <- list(homo_V_gini, -->
+<!--                        homo_V_gini_gdp, -->
+<!--                        homo_V_gini_gdp_wstate2, -->
+<!--                        homo_V_gini_full2) -->
+
+<!-- ccoef <- list(homclass3_V_gc="Social distance (CWC)", -->
+<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               "gini_disp" = "Income inequality (Gini index)", -->
+<!--               loggdppercapita = "GDP/capita", -->
+<!--               wstate2="Size of the welfare state", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class", -->
+<!--               "homclass3_V_gc:gini_disp"= "Distance*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Distance*Working Class*Income Inequality") -->
+
+<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
+<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
+<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T,single.row = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance x Social Class"=7:8, "Distance * Social Class x Income Inequality"=10:11), -->
+<!--        float.pos = "h!", -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
+<!--                            "Var: Group (Intercept)", -->
+<!--                            "Var: Group Homogeneity", -->
+<!--                            "Var: Group Intermediate Class ", -->
+<!--                            "Var: Group Working Class", -->
+<!--                            "Cov: Group (Intercept), Homogeneity", -->
+<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
+<!--                            "Cov: Group (Intercept), Working Class", -->
+<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
+<!--                            "Cov: Group Homogeneity, Working Class", -->
+<!--                            "Cov: Group Intermediate Class, Working Class", -->
+<!--                            "Var: Residual"), -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r fig5-socdistclass, echo=FALSE, fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)} -->
+<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
+<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
+<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
+
+<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
+<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
+<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
+
+<!-- df_pred_giniD_gc <- -->
+<!--   predictions( -->
+<!--     homo_V_gini_full2,newdata = datagrid( -->
+<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
+<!--       wstate2=mean(dfreg$wstate2), -->
+<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
+<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5), -->
+<!--       dclass3res_V=levels(dfreg$dclass3res_V) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
+<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
+<!-- df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
+
+<!-- df_pred_giniD_gc %>% -->
+<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
+<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
+<!--   geom_line(size=1,color="black") + -->
+<!--   geom_point(size=3, shape = 21,color="black") + -->
+<!--   facet_wrap(~gini_disp) + -->
+<!--   labs(y = "Preferences for Redistribution", -->
+<!--        x="Social Distance (CWC)", -->
+<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
+<!--        ) + -->
+<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
+<!--                      ) + -->
+
+<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   theme(legend.position = "bottom", -->
+<!--         legend.direction = "horizontal", -->
+<!--         axis.text=element_text(size=15), -->
+<!--         legend.title = element_blank(), -->
+<!--         legend.background = element_blank(), -->
+<!--         legend.box.background = element_rect(colour = "black")) -->
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ### Social Distance by ISEI  -->
+
+<!-- ```{r table1-socdist, results='asis'} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+
+<!-- dummy_df <- df1 %>% dplyr::select(id, -->
+<!--   egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust, -->
+<!--   Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region, -->
+<!--   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev, -->
+<!--   ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita, -->
+<!--   oecd,country2, country, country3) %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   na.omit() %>%  -->
+<!--   dplyr::select(id) -->
+
+<!-- df1$isei08sp <- car::recode(df1$isei08sp,"NA=0") -->
+<!-- df1$isei08 <- car::recode(df1$isei08,"NA=0") -->
+
+<!-- dfreg <- df1 %>% dplyr::select(id, -->
+<!--   egal = egal2, -->
+<!--   dclass3res_V=isei08, -->
+<!--   dclass3spo_V=isei08sp, -->
+<!--   homclass3_V_res=socdist, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   partner, -->
+<!--   religion, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   mutate(logrgdpna = log(rgdpna), -->
+<!--          loggdppercapita=log(gdppercapita), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2, -->
+<!--          dclass3res_V=dclass3res_V/10, -->
+<!--          dclass3spo_V=dclass3spo_V/10, -->
+<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN")  %>%  -->
+<!--   filter(id %in% dummy_df$id) -->
+<!-- dfreg <- na.omit(dfreg) -->
+<!-- # Step 1: Calculate absolute values -->
+<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
+<!-- # hist(absolute_values);summary(absolute_values) -->
+
+<!-- # Step 2: Add 1 to all values to eliminate zeros -->
+<!-- modified_values <- absolute_values + 0.1 -->
+<!-- # hist(modified_values);summary(modified_values) -->
+
+<!-- # Step 3: Reverse the order of the scale -->
+<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
+
+<!-- dfreg$homclass3_V_res <- reversed_values -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT) -->
+<!-- digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust) -->
+<!-- digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V) -->
+
+<!-- digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2) -->
+<!-- digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union) -->
+<!-- digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V) -->
+<!-- digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res) -->
+<!-- digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2, -->
+<!--                     digclas1_VW_3, -->
+<!--                     # digclas1_VW_4, -->
+<!--                     digclas1_VW_5,digclas1_VW_6,digclas1_VW_7) -->
+
+<!-- ccoef <- list(homclass3_V_res="Social Distance /10", -->
+<!--               know_total="Network size", -->
+<!--               socialtrust="Social Trust", -->
+<!--               # "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
+<!--               # "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
+<!--               # "femaleFemale"="Female (Ref. = Male)", -->
+<!--               # "agenum"="Age", -->
+<!--               # "age2"="Age2", -->
+<!--               "dclass3res_V"="ISEI/10", -->
+<!--               "edyears"="Year of Education", -->
+<!--               "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)", -->
+<!--               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)", -->
+<!--               "unionYes" ="Union Membership (Ref. = Not Unionized)", -->
+<!--               "dclass3spo_V" = "ISEI/10 (Partner)", -->
+<!--               "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI") -->
+
+<!-- texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1), -->
+<!--        caption = paste("(\\#tab:table2)","Multilevel models for Social Distance and Redistributive Preferences"), -->
+<!--        custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--        symbol = "+",scalebox = 0.60, -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"), -->
+<!--        float.pos = "h!", -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE} -->
+<!-- int_homo <- digclas1_VW_7 -->
+<!-- plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V" = "threenum"))+ -->
+<!-- labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
+<!--        x="ISEI",y="Redistributive preferences") -->
+<!-- ``` -->
+
+<!-- ```{r fig1-pred-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Social Distance on Redistributive Preferences by ISEI',warning=FALSE} -->
+<!-- int_homo <- digclas1_VW_7 -->
+<!-- df_pred1 <-  -->
+<!--   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"), -->
+<!--               newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.5), -->
+<!--                                  dclass3res_V = c(min(dfreg$dclass3res_V),mean(dfreg$dclass3res_V),max(dfreg$dclass3res_V)))) -->
+
+<!-- df_pred1$dclass3res_V <- factor(df_pred1$dclass3res_V,labels = c("ISEI (min)","ISEI (Mean)", "ISEI (max)")) -->
+
+<!-- # names(df_pred1) -->
+<!-- df_pred1 %>%  -->
+<!-- ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
+<!--   geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") + -->
+<!--   geom_line(size=1,color="black") + -->
+<!--   geom_point(size=2,color="black") + -->
+<!--   # facet_grid(~dclass3res_V) + -->
+<!--   scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
+<!--   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
+<!--   scale_y_continuous(limits = c(40,100))+ -->
+<!--   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
+<!--        x="Social distance",y="Redistributive preferences") + -->
+<!--   theme(legend.position = "bottom", legend.title = element_blank()) -->
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ```{r tab2-socdist, results='asis', cache=TRUE} -->
+<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
+<!-- options(ggplot2.discrete.fill = set1) -->
+<!-- options(ggplot2.discrete.colour = set1) -->
+<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
+<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
+<!-- options(scipen=999) -->
+<!-- if (!require("pacman")) install.packages("pacman") -->
+<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
+<!-- rm(list=ls()) -->
+
+<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
+
+<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
+<!-- dummy_df <- df1 %>% dplyr::select(id, -->
+<!--   egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust, -->
+<!--   Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region, -->
+<!--   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev, -->
+<!--   ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita, -->
+<!--   oecd,country2, country, country3) %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   na.omit() %>%  -->
+<!--   dplyr::select(id) -->
+
+<!-- df1$isei08sp <- car::recode(df1$isei08sp,"NA=0") -->
+<!-- dfreg <- df1 %>% dplyr::select(id, -->
+<!--   egal = egal2, -->
+<!--   # starts_with("class3"), -->
+<!--   # starts_with("digclass3"), -->
+<!--   # starts_with("dclass3"), -->
+<!--   # starts_with("homclass"), -->
+<!--   dclass3res_V=isei08, -->
+<!--   dclass3spo_V=isei08sp, -->
+<!--   homclass3_V_res=socdist, -->
+<!--   know_total, -->
+<!--   socialtrust, -->
+<!--   Q03pcm, -->
+<!--   edyears, -->
+<!--   female, -->
+<!--   agenum, -->
+<!--   religion, -->
+<!--   partner, -->
+<!--   union, -->
+<!--   workst, -->
+<!--   WEIGHT, -->
+<!--   region, -->
+<!--   "gini_disp"=wid_gini_disp, -->
+<!--   "gini_mkt", -->
+<!--   gv_spen, -->
+<!--   rel_red, -->
+<!--   abs_red, -->
+<!--   ilo_taxrev, -->
+<!--   ilo_govspe, -->
+<!--   d10d1=wid_p90p10, -->
+<!--   wid_p90p50, -->
+<!--   top10=wid_sharetop10, -->
+<!--   rgdpna, -->
+<!--   gdppercapita, -->
+<!--   oecd, -->
+<!--   country2, country, country3, -->
+<!-- ) %>% -->
+<!--   filter(oecd == "OECD") %>% -->
+<!--   filter(country2 != "SVN") %>%  -->
+<!--   na.omit() %>%  -->
+<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
+<!--          edyears2 = edyears ^ 2, -->
+<!--          age2 = agenum ^ 2,  -->
+<!--          gini_disp=scale(gini_disp), -->
+<!--          dclass3res_V=dclass3res_V/10, -->
+<!--          dclass3spo_V=dclass3spo_V/10, -->
+<!--          homclass3_V_res=homclass3_V_res/10) %>%  -->
+<!--   filter(id %in% dummy_df$id) -->
+
+<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
+<!-- # Step 1: Calculate absolute values -->
+<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
+<!-- # hist(absolute_values);summary(absolute_values) -->
+
+<!-- # Step 2: Add 1 to all values to eliminate zeros -->
+<!-- modified_values <- absolute_values + 0.1 -->
+<!-- # hist(modified_values);summary(modified_values) -->
+
+<!-- # Step 3: Reverse the order of the scale -->
+<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
+<!-- dfreg$homclass3_V_res <- reversed_values -->
+
+<!-- # Variable Group-Centering ------------------------------------------------ -->
+<!-- dfreg <-  -->
+<!--   dfreg %>%  -->
+<!--   mutate(to_dummy(female), -->
+<!--          to_dummy(union), -->
+<!--          to_dummy(workst), -->
+<!--          # dummy for categorical variables------------------------------------- -->
+<!--          to_dummy(Q03pcm), -->
+<!--          # to_dummy(dclass3spo_V) -->
+<!--   ) -->
+<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
+<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
+<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
+<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
+<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
+<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
+<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
+<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
+<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
+<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
+<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
+
+<!-- dfreg$dclass3res_V = group_center(as.numeric(dfreg$dclass3res_V), grp = dfreg$country2) -->
+
+<!-- # Household Income Tercile -->
+<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
+<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
+
+<!-- # Partner Social Class -->
+<!-- # dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
+<!-- # dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
+<!-- # dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
+<!-- # dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
+<!-- dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2) -->
+
+<!-- # drop dummies -->
+<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
+<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
+<!--                                 # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4 -->
+<!--                                 )) -->
+
+<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
+
+<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
+<!-- homo_V_gini <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+ -->
+<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          dclass3spo_V_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+ -->
+<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          dclass3spo_V_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_wstate2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+ -->
+<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          dclass3spo_V_gc+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_gdp_controls <- -->
+<!--   lmer(egal~ -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+ -->
+<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          dclass3spo_V_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2 + -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- homo_V_gini_full2 <-  -->
+<!--   lmer(egal~  -->
+<!--          homclass3_V_gc+ -->
+<!--          know_total_gc+ -->
+<!--          socialtrust_gc+ -->
+<!--          dclass3res_V+ -->
+<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
+<!--          dclass3spo_V_gc+ -->
+<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
+<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
+<!--          union_gc+workst_gc+ -->
+<!--          gini_disp +loggdppercapita + wstate2+ -->
+<!--          homclass3_V_gc* -->
+<!--          dclass3res_V* -->
+<!--          gini_disp +  -->
+<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
+
+<!-- digclas1_macro <- list(homo_V_gini, -->
+<!--                        homo_V_gini_gdp, -->
+<!--                        homo_V_gini_gdp_wstate2, -->
+<!--                        homo_V_gini_full2) -->
+
+<!-- ccoef <- list(homclass3_V_gc="Social Distance (CWC)", -->
+<!--               "dclass3res_V"="ISEI ", -->
+<!--               "gini_disp" = "Income inequality (Gini index)", -->
+<!--               loggdppercapita = "GDP/capita", -->
+<!--               wstate2="Size of the welfare state", -->
+<!--               "homclass3_V_gc:dclass3res_V" = "Distance*ISEI", -->
+<!--               "homclass3_V_gc:gini_disp"= "Distance*Income Inequality", -->
+<!--               "dclass3res_V:gini_disp" ="ISEI*Inequality", -->
+<!--               "homclass3_V_gc:dclass3res_V:gini_disp" = "Distance*Working Class*Income Inequality") -->
+
+<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
+<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
+<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
+<!--        caption.above = T,leading.zero = T,single.row = T, -->
+<!--        custom.coef.map = ccoef, -->
+<!--       # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance*Social Class"=7:8, "Distance * Social Class * Income Inequality"=10:11), -->
+<!--        float.pos = "h!", -->
+<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
+<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
+<!--                            "Var: Group (Intercept)", -->
+<!--                            "Var: Group Soc. Distance", -->
+<!--                            "Var: Group ISEI", -->
+<!--                            "Cov: Group (Intercept), Soc. Distance", -->
+<!--                            "Cov: Group (Intercept), ISEI",                            -->
+<!--                            "Cov: Group Soc. Distance, ISEI", -->
+<!--                            "Var: Residual"), -->
+<!--        use.packages = F) -->
+<!-- ``` -->
+
+<!-- ```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'} -->
+<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
+<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
+<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
+
+<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
+<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
+<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
+
+<!-- df_pred_giniD_gc <- -->
+<!--   predictions( -->
+<!--     homo_V_gini_full2,newdata = datagrid( -->
+<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
+<!--       wstate2=mean(dfreg$wstate2), -->
+<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
+<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5), -->
+<!--       dclass3res_V=c(min(dfreg$dclass3res_V),max(dfreg$dclass3res_V)) -->
+<!--     ) -->
+<!--   ) -->
+
+<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
+<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
+
+<!-- df_pred_giniD_gc$dclass3res_V <- factor(df_pred_giniD_gc$dclass3res_V,labels = c("ISEI (min)","ISEI (max)")) -->
+<!-- # df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
+
+<!-- df_pred_giniD_gc$dclass3res_V <- as.factor(df_pred_giniD_gc$dclass3res_V) -->
+
+<!-- df_pred_giniD_gc %>%  -->
+<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
+<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
+<!--   geom_line(size=1,color="black") + -->
+<!--   geom_point(size=3, shape = 21,color="black") + -->
+<!--   facet_wrap(~gini_disp) + -->
+<!--   labs(y = "Preferences for Redistribution", -->
+<!--        x="Social Distance (CWC)", -->
+<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
+<!--        ) + -->
+<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
+<!--                      ) + -->
+
+<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
+<!--   theme(legend.position = "bottom", -->
+<!--         legend.direction = "horizontal", -->
+<!--         axis.text=element_text(size=15), -->
+<!--         legend.title = element_blank(), -->
+<!--         legend.background = element_blank(), -->
+<!--         legend.box.background = element_rect(colour = "black")) -->
+<!-- ``` -->

### 2024-07-16 paper1_jiturra.Rmd
appendix

@@
 Homogeneous upper-class networks may reduce empathy and solidarity towards those in need, resulting in decreased support for redistribution.
-Conversely, segregated lower-class social networks can lead to increased marginalization and reinforce support for redistribution.
-This study explores the relationship between class-based network segregation and redistributive preferences employing cross-national data from 32,529 individuals in 31 societies.
+Conversely, segregated lower-class social networks can increase marginalization and reinforce redistribution support.
+This study explores the relationship between class-based network segregation and redistributive preferences, employing cross-national data from 31,694 individuals in 31 societies.
 The main findings suggest that social class conditions the association of network homogeneity on redistributive preferences, where working-class homogeneity drives stronger redistributive preferences, while greater upper-class homogeneity decreases support for redistribution.
@@
   bookdown::html_document2:
-    toc: yes
+    toc: false
     code_folding: hide
@@
 header-includes:
-  # - \usepackage{times}           # Times New Roman
-  - \usepackage{helvet}
+  - \usepackage{times}   # Times New Roman
+  # - \usepackage{helvet}
   - \usepackage{endnotes}
   - \let\footnote=\endnote 
-  - \renewcommand{\familydefault}{\sfdefault} 
+  # - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{caption}
@@
 
-```{r eval=FALSE, include=FALSE}
- # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
- # clean #in the yml
+```{r render, include=FALSE, eval=FALSE}
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::pdf_document2")
- # rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
+rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
-
- # install.packages("trackdown")
- trackdown::update_file(file = "paper1_jiturra.Rmd", hide_code = TRUE,gpath = '001_PhD/002dissertation/paper1')
-
-```
-
-<!-- - considerar ISEI08 como alternativa de social class por la correlacion con homogeneidad -->
-<!-- - darle una oportunidad al h-index -->
-<!--     - en general es prácticamente lo mismo que el indicador de homogeneidad -->
-<!-- - controlaria por social activities index () -->
-<!-- - social resources  -->
+```
 
@@
 
-Over the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
-In contrast, less attention has been paid to how social networks influence redistributive preferences.
-Sociologists have demonstrated that individuals tend to segregate social networks [@mcpherson_birds_2001;@lazarsfeld_friendship_1954].
-Additionally, opinions about economic inequality can be affected by class segregation, as it provides insight into the economic conditions, lifestyles, and worldviews of other social classes [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-Despite this, the study of redistributive preferences can be enhanced by broadening the understanding of class relations from a network perspective.
-This approach offers a comprehensive understanding of processes such as shared norm internalization, class identity formation, and collective solidarity [@Svallfors2006;@goldthorpe_sobre_1992].
-Thus, this study examines the relationship between class-based network segregation and redistributive preferences in a cross-national comparison, focusing on the role of economic inequality as a moderator in the influence of class relations on support for redistribution.
-
-While prior research has predominantly examined the impact of social class through an individualistic lens, more attention should be devoted to understanding the role of social environments in class relations.
-This omission is particularly surprising given that class positions are fundamentally rooted in production relations, making them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989].
-Furthermore, the normative basis of class relations introduces the relevance of solidarity and reciprocity dimensions, which are argued to provide the moral foundation for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-In this regard, beyond the influence of individual class position, recent efforts have highlighted that while the class positions of network ties do affect redistributive preferences, the degree of segregation in a homogeneous class environment can drive attitudes to become even stronger [@otero_lives_2022].
-
-While network segregation widens the class divide in redistributive preferences, little is known about how income inequality can affect the association between class-based network segregation and support for redistribution.
-On the one hand, studies on the class-attitude link suggest that income inequality is crucial for understanding how class relations are reflected in redistributive demands, as it represents the current state of the distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-A consistent finding in this literature is that the upper classes tend to support redistribution more in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
-On the other hand, income inequality leads to more segregated forms of social participation and network composition [@pichler_patterns_2007;@otero_space_2022].
-Indeed, inequality reinforces stratified access to social activities and widens the distance between classes, resulting in increased marginalization of the lower classes and consolidating the privileged positions of the upper classes, who have better opportunities to diversify their social activities and interpersonal ties [@lancee_income_2012;@otero_differences_2023].
-Nevertheless, current efforts to examine the impact of income inequality have primarily focused on either social networks or support for redistribution.
-A key question that remains unanswered is the extent to which broader economic disparities moderate the relationship between class-based network segregation and support for redistribution.
-
-Thus, to the best of my knowledge, no research has comparatively investigated the role of economic inequality in the relationship between class-based network segregation and redistributive preferences.
-This study aims to address two key questions:
+ the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
+In contrast, less attention has been paid to the role of social networks on redistributive preferences.
+Sociologists have demonstrated that individuals tend to form segregated social networks according to social class [@mcpherson_birds_2001;@otero_lives_2022].
+Additionally, attitudes toward economic inequality can be affected by class segregation, as it implies distance from other social classes'  economic conditions, lifestyles, and worldviews [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+Therefore, focusing on social ties can improve the understanding of the relationship between social class and redistributive preferences, as it broadens the scrutiny of class relations in terms of internalization of shared norms, class identity formation, and collective solidarity.
+[@Svallfors2006;@goldthorpe_service_1982].
+In this discussion, the first part of this study examines the micro-level relationship between class-based network segregation and redistributive preferences.
+Subsequently, I focus on how cross-national differences in income inequality can moderate the relation of network segregation and support for redistribution.
+
+While previous research has predominantly examined the impact of social class through an individualist lens, more attention has recently been paid to the role of social ties in class relations.
+This omission is especially surprising since social classes are rooted in social relations of production, which makes them inherently relational in their economic foundations and the power dynamics involved in distributive struggles [@wright_comparative_1989].
+Moreover, the normative basis of class relations introduces the relevance of dimensions of solidarity and reciprocity, which are argued to provide the moral foundation for legitimacy and popular support for welfare schemes [@mau_moral_2003].
+Thus, beyond the influence of individual class positions, recent efforts have highlighted that, while the class positions of network ties affect redistributive preferences, segregation in homogeneous class-based social settings can make attitudes even more pronounced [@otero_lives_2022].
+
+As network segregation can widen the class divide in redistributive preferences, little is known about how income inequality may affect the association between class-based network segregation and support for redistribution.
+On the one hand, studies on the class-attitude link suggest that income inequality is crucial for understanding how class relations are reflected in redistributive demands, as it represents the current state of distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
+A consistent finding in this literature is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
+On the other hand, income inequality has implications for social participation and network composition.
+Indeed, inequality reinforces stratified access to social activities and widens the distance between classes, resulting in a higher diversity of networks and activities in the upper classes and more marginalization of the lower classes [@lancee_income_2012;@otero_differences_2023;@pichler_patterns_2007].
+However, current efforts to examine the impact of income inequality have focused primarily on social networks or support for redistribution.
+Thus, a key question that remains unanswered is the extent to which higher income inequality moderates the relationship between social class-based network segregation and redistributive preferences.
+
+To the best of my knowledge, no research has comparatively studied the role of economic inequality in the relationship between class-based network segregation and redistributive preferences.
+Therefore, this study aims to answer two key questions:
 
@@
 
-For this investigation, I utilized a sample of 32,529 individuals across 31 countries from the International Social Survey Program (ISSP) 2017.
+In this study, I used a sample of 31,694 individuals from 31 countries from the International Social Survey Program (ISSP) 2017.
 This dataset provides unprecedented cross-national comparative data on social networks, social class, and attitudes toward redistribution.
@@
 421].
-In this view, social class not only represents individuals’ market situations but also their economic interests and moral perspectives on the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
+In this view, social class not only represents individuals' labor market relations but also their economic interests and moral perspectives on the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
 Here, redistributive preferences are understood as the support for policies and mechanisms aimed at reducing economic inequality through the redistribution of wealth and resources [@mccall_americans_2009].
@@
 Empirically, the current understanding of class divides in redistributive preferences is extensive [@lindh_public_2015;@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-Nevertheless, beyond the market situation of individuals and their households, considering class-based network ties highlights the relevance of the class situation, as it encompasses both economic interests and life chances that drive communal action beyond individuals [@weber_class_2011, pp.
+Nevertheless, considering class-based network ties highlights the relevance of the class situation, as it encompasses economic interests and life chances that drive communal action beyond individuals [@weber_class_2011, pp.
 57-59].
-Thus, the role of social relations in shaping redistributive preferences from a network perspective considers more straightforwardly the social ties that structure class relations.
+Hence, considering the structure of social ties allows one to look more comprehensively into how class relations structure redistributive preferences.
 
@@
 
-<!-- It can be argued that class relations not only represent resource-based distinctions but also patterns of connectedness observed in the differentiation of social ties.  -->
-
-Class relations can also be understood as the degree of cross-class relationships as a structural characteristic of society, representing a network of social ties between different class positions [@blau_macrosociological_1977].
-Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001, p.416].
-In this context, friendship and family ties tend to be homogeneous concerning class and demographic characteristics, while more distant ties serve to bridge individuals to different social groups and contribute to network diversity [@diprete_segregation_2011; @lazarsfeld_friendship_1954].
-Besides, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004; @homans_human_1951].
-Nevertheless, attitude similarity in segregated networks is rather a consequence of the social differentiation that structures the formation of cross-class network ties [@feld_focused_1981].
-
-There are two primary approaches in the study of class relations from a network perspective.
-On the one hand, network diversity is defined as the degree of connectedness to dissimilar occupations, which represents vertical access to resources embedded in social networks [@lin_access_1986].
-However, diversity is defined as the rate of dissimilar ties within the network without necessarily providing a reference position to describe network similarity.
-On the other hand, network segregation is the absence of cross-class connections and represents how similar network ties are in contrast to the individual.
+Class relations can also be comprehended as the structure of social ties between classes as a characteristic of the social structure, represented as networks formed by different social classes [@blau_macrosociological_1977].
+Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001].
+This means that friendship and family ties tend to be homogeneous concerning social status and demographic characteristics, while distant ties bridge individuals to different social groups and contribute to network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
+Besides, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951].
+However, the similarity of attitudes in segregated networks results more from the social differentiation that structures class ties than from individual preferences [@feld_focused_1981].
+
+There are two approaches in the study of class relations from a network perspective.
+On the one hand, network diversity is defined as the degree of connectedness to dissimilar occupations, which represents vertical access to resource diversity embedded in social networks [@lin_access_1986].
+However, diversity is defined as the variability of different ties within the network without necessarily providing a reference position to describe network similarity.
+On the other hand, network segregation is the absence of cross-class connections and represents how similar network ties are in reference to the individual.
 This perspective is conceptually closer to homophily as it is anchored in individual class positions and has been empirically addressed through network homogeneity [@otero_open_2021].
@@
 In contrast, studies on network segregation suggest that property-based boundaries are less permeable than authority-based ones.
-For example, @wright_relative_1992 suggest since class interests widen the social distance between proprietors and manual workers, the intermediate position of supervisors, along with their higher contact frequency with manual workers, makes the formation of friendship ties more likely.
-Similarly, @otero_open_2021 have shown that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity for social engagement ultimately result in a lack of social resources that leads to segregation.
-Conversely, the upper class is less permeable and homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
+For example, @wright_relative_1992 suggest that since class interests widen the social distance between proprietors and manual workers, the intermediate position of supervisors and their higher contact frequency with manual workers makes the formation of friendship ties more likely.
+Similarly, @otero_open_2021 found that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity for social engagement ultimately result in segregation.
+Conversely, the upper class is more homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
 
@@
 
-It has been stated that perceptions about economic inequality rooted in social comparison processes with reference groups can explain the formation of redistributive preferences [@condon_economic_2020].
+The first approach states that perceptions about economic inequality rooted in social comparison processes with reference groups could explain the formation of redistributive preferences [@condon_economic_2020].
 This hypothesis can be traced to the studies on class images and perceived class conflicts [@Evans1992;@kelley_class_1995].
@@
 
-In contrast, social networks provide a comprehensive picture of the class relations that contribute to group identity formation and internalization of social norms [@kalmijn_social_2007, p.
-550].
-Specifically, it has been argued that redistributive preferences are influenced not only by individuals' class situations but also by the class positions of their network ties [@paskov_crossclass_2022].
-Social influence processes can either align or divide opinions depending on the class positions of contacts and the level of network segregation [@lindh_missing_2021].
-These findings reflect the notion that classes are characterized as collectivities with varying degrees of cohesion and solidarity, comprising asymmetric status-based interactions related to material resources, cultural practices, and political preferences that shape broader social experiences [@morris_attenuation_1996, p.
-48].
+The second approach suggests that social networks provide a comprehensive picture of the class relations that contribute to group identity formation and internalization of social norms [@kalmijn_social_2007].
+Specifically, it has been argued that redistributive preferences are influenced not only by individuals' social class but also by the class positions of their network ties [@paskov_crossclass_2022].
+Thus, social influence processes can either align or divide opinions depending on the class positions of contacts and the level of network segregation [@lindh_missing_2021].
+These arguments reflect the notion that classes are characterized as collectivities with varying degrees of cohesion and solidarity, comprising asymmetric status-based interactions related to material resources, cultural practices, and political preferences [@morris_attenuation_1996].
 Following @sachweh_moral_2012, social integration can be impeded in societies with few opportunities for contact between different social classes, creating an "empathy gulf" that hinders individuals from understanding others' lifestyles amid rising inequality.
-Consequently, spatially segregated interactions may lead individuals to view the lives of different classes as more distant, which can undermine feelings of social inclusion and cohesion [@sachweh_moral_2012].
-Thus, segregation can exacerbate perceptions of others as strangers and may impact empathy and solidarity, potentially diminishing social cohesion [@otero_lives_2022, p.
-758].
-
-<!-- The attention has increased in recent years to how social ties are connected to attitudes toward inequality, and it has been shown that frequent interactions between classes can lead to different attitudinal changes depending on the individuals' social class.
-For instance, contact with the upper classes drives higher justification of economic inequality among the lower classes, whereas interactions with lower classes may prompt the different social classes to question the fairness of income distribution [@vargassalfate_contact_2023].
-Further evidence suggests that class-based contact diversity shortens the social distance between social classes, providing broader images of the living conditions of others, which can trigger greater concerns about inequality [@otero_power_2023] and undermine support for the market distribution of social services [@beck_explorando_2019].
--->
-
-The class position of surrounding family members, friends, and acquaintances influences redistributive preferences, as these individuals function as socialization agents whose impact can be amplified in segregated social networks.
-In principle, political attitudes are connected to class interests and norms that are nurtured in the family of origin during childhood and early adulthood.
+Consequently, segregated interactions may lead individuals to perceive the lives of different classes as more distant and undermine feelings of social integration [@sachweh_moral_2012].
+Thus, segregation can potentially diminish social cohesion as it exacerbates perceptions of others as strangers which in turn reduces empathy and solidarity [@otero_lives_2022].
+
+How do network ties affect redistributive preferences?
+The class position of surrounding family members, friends, and acquaintances affects support for redistribution, as these ties function as socialization agents whose impact can be amplified in segregated social networks.
+In principle, political attitudes are connected to class interests and norms as they are socialized in the family of origin during childhood and early adulthood.
 For instance, @lee_consider_2023 shows that individuals with network ties to the upper class through parental connections tend to support redistribution and progressive taxation less than those from working-class family backgrounds.
 Moreover, since households share risk based on the class position of their members, redistributive preferences are shaped not only by family background but also by the class positions of partners.
-For example, @paskov_crossclass_2022 indicates that working-class ties bolster redistributive preferences, whereas ties with the upper class decrease these preferences, with the effects becoming more pronounced when the class positions of individuals, partners, and parents create a more homogeneous network.
-Additionally, @lindh_missing_2021 found that friendship and acquaintanceship ties to the managerial class are associated with lower redistributive preferences compared to ties with the sociocultural and working classes.
-Hence, they suggest that individuals tend to adjust their attitudes based on the class position of their contacts [@lindh_missing_2021, p.
-698].
+For example, @paskov_crossclass_2022 indicates that working-class ties bolster redistributive preferences, whereas ties with the upper class decrease them, with the effects becoming more pronounced when the class positions of individuals, partners, and parents form a more homogeneous network.
+Similarly, @lindh_missing_2021 found that friendship and acquaintanceship ties to the managerial class are associated with lower redistributive preferences compared to ties with the sociocultural and working classes.
+Hence, this suggests that individuals tend to adjust their attitudes based on the class position of their contacts [@lindh_missing_2021].
 
@@
 
-Studies on economic inequality, social class, and redistributive preferences indicate that the social classes react differently to rising economic inequality.
+Studies on economic inequality, social class, and redistributive preferences indicate that social classes react differently to rising economic inequality.
 Theoretically, political economists have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution [@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
@@
 
-Empirically, affluent groups are more responsive because they perceive the overall opportunity structure and social mobility chances are affected by rising inequality [@sachweh_why_2019].
+Empirically, it has been shown that affluent groups are more responsive as they perceive the overall opportunity structure and social mobility chances are affected by rising inequality [@sachweh_why_2019].
 Likewise, higher perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
 In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019].
-In a similar perspective, @edlund_democratic_2015 argue that in unequal societies with residual welfare states social class has a poor political meaning, making distributive conflicts weakly institutionalized around traditional working-class organizations (e.g., unions).
-Thus, stronger support for state-organized redistribution among the upper classes can also be explained as they are often more aware of the institutional incentives and societal consequences of income inequality [@curtis_how_2015;@Svallfors2006].
+In a similar perspective, @edlund_democratic_2015 argue that in unequal societies with residual welfare states, social class has a poor political meaning, making distributive conflicts weakly institutionalized around traditional working-class organizations (e.g., unions).
+Thus, stronger support for state-organized redistribution among the upper classes can also be explained as they are often more aware of the incentives and societal consequences of income inequality [@curtis_how_2015;@Svallfors2006].
 
 How does income inequality affect social networks?
-As income inequality implies stronger barriers to establishing trustworthy social connections, this has also consequences on the structure of class relations.
+As income inequality implies stronger barriers to establishing trustworthy social connections, this also has consequences on the structure of class relations.
 Neckerman and Torche [-@neckerman_inequality_2007, p.
@@
 Also, societies with higher income inequality can erode social relations as they exhibit reduced social trust that operates as the basis for mutual understanding and feelings of solidarity [@kragten_income_2017].
-Likewise, in contexts of lower income inequality and encompassing welfare states, the higher levels of civic and social participation increase generalized trust and reduce social conflict [@uslaner_inequality_2005].
-Related evicende shows that higher community participation can incentivize support for redistribution in general, being particularly salient among high-income citizens [@yamamura_social_2012].
+Likewise, in contexts of lower income inequality and encompassing welfare states, higher levels of civic and social participation increase generalized trust and reduce social conflict [@uslaner_inequality_2005].
+In a similar vein, @yamamura_social_2012 showed that redistributive preferences rise as community-level participation in social activities increases.
+Moreover, high-income citizens in these communities are specifically more likely to support collective solidarity through government redistribution.
 
@@
 The complete sample comprises 47,027 observations across 32 countries.
-However, after reviewing the required information and applying listwise case deletion, the final sample used in the analyses consists of 32,529 observations from 31 countries [^data].
+However, after reviewing the required information and applying listwise case deletion, the final sample used in the analyses consists of 31,694 observations from 31 countries [^data].
 
@@
 I use two indicators to measure redistributive preferences.
-The first indicator, support for government redistribution, is measured by the item: “It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes.” The second indicator, egalitarian preferences, is measured by the item: “For a society to be fair, differences in people’s standard of living should be small.” Both indicators use a five-point Likert scale with the following categories: ‘Strongly agree’ (1), ‘Agree’ (2), ‘Neither agree nor disagree’ (3), ‘Disagree’ (4), and ‘Strongly disagree’ (5), and they are shown to be correlated (r = 0.7).
-The indicators were reverse-coded, averaged, and normalized to a range from 0 to 100, where higher values reflect stronger redistributive preferences [@svallfors_government_2013].
+The first indicator corresponds to support for government redistribution and it is measured by the item: "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes." The second indicator is egalitarian preferences and it is measured by the item: "For a society to be fair, differences in people's standard of living should be small." Both indicators use a five-point Likert scale with the following categories: 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree'(3), 'Disagree' (4), and 'Strongly disagree'(5).
+Following @svallfors_government_2013, I reverse-coded, averaged and normalized the indicators in a 0 to 100 index, where higher values reflect stronger redistributive preferences.
 
@@
 
-To measure social class, the Erikson-Goldthorpe-Portocarrero (EGP) class scheme is employed [@Erikson1992].
+To measure social class, I employ the Erikson-Goldthorpe-Portocarrero (EGP) class scheme [@Erikson1992].
 The EGP scheme is one of the most consistent and validated measures for social class positions in comparative research and has demonstrated its validity in both industrialized and late-industrialized societies [@evans_political_2013;@barozet_measurement_2021].
-Therefore, information about occupations, self-employment status, and the number of employees is used to classify respondents into different class positions.
+Therefore, information about occupations, self-employment status, and the number of employees is used to classify respondents into six class positions.
 Following previous research, a simplified version of the EGP class scheme that collapses three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
-Specifically, this version distinguishes among the Service Class (Higher and Lower managerial and professionals), Intermediate Class (Routine nonmanual workers and self-employed), and Working Class (Manual supervisors, skilled manual workers, and unskilled manual workers).
-
-I employed the position generator as the basis for measuring class-based network homogeneity.
-This instrument has been widely used in social capital studies and follows an ego-centered approach where social ties to different hierarchical positions in the social structure provide access to social resources [@vandergaag_position_2008].
-In this approach, a list of ten occupations is displayed, and each tie can be classified as "Family or relative," "Close friend," "Someone else I know," or "No one." The first three categories are coded as "Knows" = 1 and "Does not know" = 0, resulting in a total number of social ties per respondent.
-Subsequently, following the procedures outlined by @otero_open_2021, occupations are classified into three groups using the International Socio-Economic Index of Occupational Status (ISEI) from the 2008 version of the International Standard Classification of Occupations (ISCO-08) [@ganzeboom_new_2010] to approximate Goldthorpe's class positions.
-The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *high-status*; school teacher, police officer, and nurse are classified as *middle-status*; and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *low-status* occupations.
-
-Given the above, I adopted established procedures from the literature for measuring homogeneity in ego-centered networks.
-For instance, @volker_birds_2022 computes network homogeneity for gender and education by evaluating the proportion of similar ties based on the characteristics of respondents and their network members.
+Specifically, this version distinguishes among the Service Class (higher and lower managerial and professionals), Intermediate Class (routine nonmanual workers and self-employed), and Working Class (manual supervisors, skilled and unskilled manual workers).
+
+I employed the position generator as the basis for the class-based network homogeneity measure.
+This instrument has been widely used in social capital studies and follows an ego-centered approach where is assumed that social ties to different hierarchical positions in the social structure provide access to social resources [@vandergaag_position_2008].
+Here, a list of ten occupations is displayed and declared as a "Family or relative," "Close friend", "Someone else I know," or "No one." The first three categories are binary coded as "Knows" (1) and the rest as "Does not know" (0).
+Then, the sum of all occupations known represents the total number of ties per respondent.
+
+Subsequently, following @otero_differences_2023 I classify occupations into three status positions that resemble Goldthorpe's class positions based on the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010].
+The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *higher* (ISEI range: 68-85); school teacher, police officer, and nurse are classified as *medium* (ISEI range: 48-63); and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *lower* (ISEI range: 17-38) positions (see Table \@ref(tab:tab-an-postgen) in the Appendix).
+
+Given the above, I adopted established procedures in the literature for measuring homogeneity in ego-centered networks.
+For example, @volker_birds_2022 computes gender and educational network homogeneity by calculating the proportion of similar ties based on both respondent and network tie characteristics.
 Similarly, @otero_lives_2022 employed a comparable method by classifying occupations from the position generator into three class positions to compute the proportion of similar ties based on social class, thereby measuring class-based network homogeneity.
-In this research, I use this latter approach.
-Specifically, I calculate the number of ingroup ties according to the respondents' class position and divide it by the total number of contacts to obtain a measure of network homogeneity.
+In this research, I adopt the latter approach.
+
+Therefore, I calculate the number of ingroup ties according to the respondents' class position and divide it by the total number of known occupations to obtain a measure of network homogeneity.
 This measure represents the proportion of similar social ties within the personal network, where a value of zero indicates complete *heterogeneity* (i.e., all ties are different), and a value of one indicates complete *homogeneity* (i.e., all ties are similar).
@@
 
+A set of control variables are considered in the estimations.
 First, the number of social ties is included to ensure that the association between network homogeneity and redistributive preferences is independent of network size.
-Second, socioeconomic characteristics are sequentially incorporated into the models, as they represent the current social status through income, education, and labor market status [@kitschelt_occupations_2014;@hausermann_highskilled_2015].
-Third, gender, age, and marital status are included in all models as sociodemographic characteristics to control for the potential influence of gender norms and life course events on attitudes [@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
+Second, socioeconomic characteristics are incorporated into the models, as they represent the current social status through income, education, and labor market status [@kitschelt_occupations_2014;@hausermann_highskilled_2015].
+Third, gender, age, and marital status are included in all models as sociodemographic characteristics to control for the potential influence of life course events and gendered effects  [@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
 
@@
 
-I employ multilevel linear regression models in all the analyses for accounting by the hierarchical structure of the data given that individuals are nested within countries.
+I employ multilevel linear regression models for accounting by the hierarchical structure of the data given that individuals are nested within countries.
 The analysis begins by estimating a null model with a random intercept to reflect this nested structure.
 This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to differences between countries.
-Subsequently, micro-level models are estimated to examine the association between network homogeneity and social class to test Hypothesis [^altmodels].
+Subsequently, micro-level models are estimated to examine the association between network homogeneity and social class to test Hypothesis 1 [^altmodels].
 Following this, macro-level models are estimated by incorporating random intercepts and random slopes for network homogeneity and social class.
@@
 Additionally, all country-level factors are standardized (z-scores) to facilitate comparability in the estimations [@hox_multilevel_2010].
-In all the models, I use the `lme4` package in `R` [@bates_fitting_2015].
+All the models are estimated employing the `lme4` package in `R` [@bates_fitting_2015].
 [^lme4]
@@
 
-## Descriptive cross-country comparison on class, network segregation and redistributive preferences
-
-```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country comparison of redistributive preferences and social class',warning=FALSE}
+## Descriptive cross-country comparison on class, network segregation, and redistributive preferences
+
+```{r fig1, fig.dim=c(10,5),fig.cap='Cross-country differences in redistributive preferences by social class',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
   egal = egal2,
@@
          )
-
 df_mean <- 
@@
   group_by(country3) %>% 
-  summarise(egal2_c=mean(egal),homclass_c=mean(homclass3_V_res),gini_disp=mean(gini_disp))
+  summarise(egal2_c=weighted.mean(egal,WEIGHT),homclass_c=weighted.mean(homclass3_V_res,WEIGHT),gini_disp=mean(gini_disp))
 df_region <- dfreg %>% group_by(region,country3) %>% summarise(n())
-df_full <- dfreg %>% group_by(dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res),homclass_c=mean(dfreg$homclass3_V_res),egal2_c=mean(dfreg$egal), country3="Sample")
-df_plot <- dfreg %>% group_by(country3,dclass3res_V) %>% summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>%left_join(df_mean) %>% left_join(df_region) 
+df_full <- dfreg %>% group_by(dclass3res_V) %>%
+  summarise(egal2=weighted.mean(egal,WEIGHT),
+            homclass=weighted.mean(homclass3_V_res,WEIGHT),
+            homclass_c=weighted.mean(dfreg$homclass3_V_res,dfreg$WEIGHT),
+            egal2_c=weighted.mean(dfreg$egal,dfreg$WEIGHT), 
+            country3="Sample")
+df_plot <- dfreg %>% group_by(country3,dclass3res_V) %>% 
+  summarise(egal2=weighted.mean(egal,WEIGHT),
+            homclass=weighted.mean(homclass3_V_res, WEIGHT)) %>% 
+  left_join(df_mean) %>% left_join(df_region) 
 df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))
@@
   group_by(country3,dclass3res_V) %>% 
-  summarise(egal2=mean(egal),homclass=mean(homclass3_V_res)) %>% 
+  summarise(egal2=weighted.mean(egal,WEIGHT),homclass=weighted.mean(homclass3_V_res,WEIGHT)) %>% 
   left_join(df_mean) %>%
@@
                                 levels = c("Country","Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)"),labels = c("Country","Service Class","Intermediate Class","Working Class"))
+
+# df_plot3 %>% correlation::correlation()
 
@@
   scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in redistributive preferences by social class") +
+  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; weighted descriptive statistics; figure report country averages in redistributive preferences by social class") +
   theme(legend.position = "bottom",
@@
 
-Figure \@ref(fig:fig1) depicts the distribution of redistributive preferences across countries and social classes.
-As expected, in most societies, the working class shows stronger redistributive preferences compared to the intermediate and service classes, with four exceptions where the differences between these classes are minimal.
+Figure \@ref(fig:fig1) depicts the differences in redistributive preferences across countries and social classes.
+As expected, the working class shows higher redistributive preferences compared to the intermediate and service classes in most societies.
 Notably, there are also some differences between the two extreme cases.
-For instance, in the United States, the working class exhibits lower redistributive preferences (49.1) compared to the intermediate class (50.6), although both classes have higher preferences than the service class (46.8).
-Conversely, in Russia, the general trend of stronger preferences among the working class persists, with a notable decrease in redistributive preferences from the working (85.5) to the intermediate (83.5) and service class (83.0).
+For instance, the working class exhibits similar redistributive preferences compared to the intermediate class in the United States, although both classes have higher preferences than the service class.
+Conversely, the general trend of stronger preferences among the working class persists in Russia, but the preferences of the intermediate class are much closer to the service class.
 
@@
 
-```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country comparison of Network homogeneity and Social Class ',warning=FALSE}
+```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country differences in network homogeneity by social class ',warning=FALSE}
 df_plot3 %>%
@@
   scale_y_continuous(limits = c(0,0.7))+
-  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
+  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; weighted descriptive statistics; figure report country averages in network homogeneity by social class") +
   theme(legend.position = "bottom",
@@
 
-Regarding network segregation, Figure \@ref(fig:fig2)  illustrates that, between-country differences in network homogeneity are relatively low, whereas class differences are quite distinguishable.
-Additionally, the general pattern observed is that the working class demonstrates high network homogeneity, except in the Philippines, where the intermediate class shows a slightly higher average homogeneity.
-Moreover, the service class generally exhibits less segregation compared to the intermediate and working classes.
-An interesting observation is that, in cases like Mexico, although the working class remains highly segregated, the intermediate and service classes exhibit similar levels of network segregation.
-
-```{r fig3, fig.dim=c(10,5),fig.cap='Bivariate relationships between Income Inequality, Network homogeneity and Redistributive preferences',warning=FALSE}
+Regarding network segregation, Figure \@ref(fig:fig2) shows that between-country variation in network homogeneity is relatively low, whereas class differences are quite distinguishable.
+On the one hand, a general pattern is that the working class demonstrates high network homogeneity in most countries.
+On the other hand, the service class generally exhibits less segregation compared to the intermediate and working classes.
+In addition, homogeneity in the intermediate class tends to be close to the average of each country between the lower and upper classes.
+Despite that in some societies these differences do not show the same escalated distribution of homogeneity by social class, the general pattern holds true.
+
+```{r fig3, fig.dim=c(10,5),fig.cap='Relationship between income Inequality, network homogeneity and redistributive preferences',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
   group_by(country2,country3) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp","d10d1"), mean, na.rm = TRUE) %>% 
+  # summarise_at(c("homclass3_V_res","egal","gini_disp"), weighted.mean, w="WEIGHT",na.rm = TRUE) %>% 
+  summarise(homclass3_V_res=weighted.mean(homclass3_V_res,WEIGHT),
+            egal=weighted.mean(egal,WEIGHT),
+            gini_disp=mean(gini_disp)) %>% 
   as.data.frame()
+
+# 
+# homo_ineq %>% correlation::correlation()
 
@@
  bottom =textGrob("Source: International Social Survey 2017; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
- gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
+ gp = gpar(fontface = 6, fontsize = 10),hjust = 1,x = 1
   ))
@@
 Regarding the macro-level relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, which is our main societal characteristic of interest.
-Panel A shows a medium positive association between network homogeneity and redistributive preferences (*r* = 0.43).
+Panel A shows a medium positive association between network homogeneity and redistributive preferences (*r* = 0.45).
 Consistent with the previously described distribution, higher levels of network homogeneity are driven by the highly segregated networks of the working classes.
@@
 Panel B illustrates a positive but relatively weak association between income inequality and network homogeneity (*r* = 0.28), suggesting that in more unequal countries, class-based network homogeneity is also higher.
-Additionally, the differences in network homogeneity between the working class and the service class increase in countries with higher income inequality (*r* = 0.30; see Appendix Fig.
-\@ref(fig:figapp1)).
+Additionally, the differences in network homogeneity between the working class and the service class increase in countries with higher income inequality (*r* = 0.30; see Figure \@ref(fig:fig-an1) in the Appendix).
 Therefore, income inequality not only increases overall network homogeneity but also widens social distance between social classes.
@@
 dfreg <- df1 %>% dplyr::select(
+  prefineq,redist,
   egal = egal2,
@@
 
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
        caption = paste("(\\#tab:table1)","Multilevel models for network homogeneity and redistributive preferences"),
-       custom.note = "\\item Note: Models include sampling weights.
-Gender, age, marital status, education, household income and employment status are included as controls.
-\\item Standard errors in parentheses.
-$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",threeparttable = T,
+       custom.note = "\\item Note: Models include sampling weights. \\item Standard errors in parentheses. %stars",threeparttable = T,
        caption.above = T,leading.zero = T,
@@
        float.pos = "h!",
-      # file = "table1.html"
+      # file = "table1.html",
        use.packages = F) 
@@
   scale_y_continuous(limits = c(55,80))+
-  labs(caption = paste0("Source: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". The line is the fitted values with a confident interval at 95%"),
+  labs(caption = paste0("Source: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". Predictive estimates with 95% confidence intervals"),
        x="Network homogeneity",y="Redistributive preferences (0 - 100)") +
@@
 # int_homo <- digclas1_VW_7
-# plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"),draw = F)+
+# plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"),draw = T)+
 # labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
@@
 
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
        caption = paste("(\\#tab:table2)","Multilevel models for income inequality, network homogeneity and redistributive preferences"),
-       custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. 
-       $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",
+       custom.note = "\\item Note: Models include sampling weights and individual level controls centered within cluster (group mean). \\item Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
@@
 Here, the results jointly suggest that network segregation matters in contexts of low and middle economic inequality but loses relevance in contexts of high inequality.
-Overall, the results presented above support the claims of the _mitigation_ hypothesis (H2), where the wider class divide in redistributive preferences produced by homogeneous class-based networks weakens as income inequality increases.
+Overall, the results presented above support the claims of the _mitigation_ hypothesis (H2), where the wider class divide in redistributive preferences in homogeneous class-based networks weakens as income inequality increases.
 
@@
        caption = paste0("Source: N (Individuals) = ",nobs(homo_V_gini_full2),"; N (Countries) = ",lme4::ngrps(homo_V_gini_full2),
-                        ". The line is the fitted values with a confident interval at 95%")) +
+                        ". Predictive estimates with 95% confidence intervals")) +
   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
@@
 
-This research examines how class-based network segregation relates to redistributive preferences and the extent to which economic inequality moderates this relationship.
-The literature on interpersonal networks highlights how network structures not only harbor social resources [@lin_access_1986] but also contribute to forming political opinions through social influence and network segregation [@lindh_missing_2021;@paskov_crossclass_2022].
-Contrary to previous evidence suggesting that network homogeneity diminishes social cohesion [@otero_lives_2022], this study indicates that class segregation exacerbates the existing class divide in redistributive preferences.
-Specifically, the interaction of class-based network homogeneity and social class shows that for working-class members, homogeneity strengthens their redistributive preferences, while for the service class, homogeneity results in even lower redistributive preferences.
-
-The theoretical framework of this research posits that studying the class divide in redistributive preferences should not solely address social classes regarding labor market relations but should also observe them through the structure of interpersonal networks.
-The literature has established that processes of social influence and political socialization demonstrate how social closure in interpersonal networks can create a divide in redistributive preferences between social classes [@lee_consider_2023;@lindh_missing_2021].
-This 'empathy gulf' is evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
-Furthermore, since network homogeneity represents low cross-class ties, lower social integration can undermine social solidarity by reducing contact between social classes and limiting knowledge about others' lives [@blau_macrosociological_1977;@otero_lives_2022].
-
-Besides the micro-level findings, this study demonstrates that economic inequality moderates the relationship between network segregation and redistributive preferences, a topic previously unexplored in an integrative empirical framework.
-The results from the multilevel models indicate that inequality *mitigates* the micro-level relationship, resulting in a narrower class gap in redistributive preferences, primarily through changes in the service class.
-These findings align with evidence on the role of inequality in class relations and redistributive preferences.
-Research suggests that in unequal societies, the better-off class tends to adopt more egalitarian attitudes toward economic inequality [@edlund_democratic_2015;@sachweh_why_2019].
-Additionally, the results highlight that upper classes can consolidate their distinctive positions and navigate diverse networks, often at the expense of marginalizing the poor in more unequal contexts [@otero_differences_2023].
-
-In the theoretical framework adopted, economic inequality establishes the field for class relations and conflict, which are consequently crystallized in political attitudes.
-Here, the class divide in redistributive preferences represents one aspect of the economic domain [@lindh_class_2020].
-Class relations can also be understood as networks of social connections between different class positions.
-Thus, social influence as a network mechanism on redistributive preferences can be framed as the social force that intensifies class-based mechanisms, such as self-interests and values, in segregated networks [@lindh_missing_2021].
-The observed weaker interaction between class and homogeneity in more unequal countries can be interpreted in two non-exclusive ways.
-First, network diversity becomes more stratified as inequality increases, meaning that networks in the upper classes become less homogeneous as inequality rises.
-Second, given that the upper classes hold more egalitarian stances in more unequal societies, it is plausible to argue that class homogeneity can also reinforce opinion similarity when redistributive preferences are higher in the upper class.
-Therefore, network segregation could influence opinions by either weakening or reinforcing attitudes based on the average opinion about redistribution within a class.
+This research examines how class-based network segregation is associated with redistributive preferences and how income inequality mitigates this relationship from a cross-national perspective.
+[@lindh_missing_2021;@paskov_crossclass_2022].
+Despite the claimed detrimental direct association of network segregation on attachment to society [@otero_lives_2022], my first finding suggests that network segregation is rather conditional to social class in the case of redistributive preferences than directly detrimental.
+Here, I evidenced that higher network homogeneity in the working class increases redistributive preferences, while homogeneous networks in the service class reduce support for redistribution.
+
+In theory, my first hypothesis was that the class divide in redistributive preferences should consider individual class positions and the structure of social networks as sources of preference formation.
+Hence, my finding supports the claims that social influence and particularly segregation in interpersonal networks strengthen class differences in redistributive preferences [@lee_consider_2023;@lindh_missing_2021].
+Also, these results support the idea that low cross-class connections can reduce social integration and solidarity as they limit awareness about the lives of other classes [@blau_macrosociological_1977;@otero_lives_2022].
+Furthermore, the 'empathy gulf' is evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
+
+Besides the micro-level findings, my second hypothesis was that economic inequality moderates the conditional association of network homogeneity by social class and redistributive preferences.
+The results from the multilevel models indicate that income inequality _mitigates_ this relationship.
+In other words, the role of network segregation observed in the interaction of homogeneity and class is less pronounced in highly unequal societies.
+Particularly, the most notable differences in redistributive preferences are observed in homogeneous service class networks.
+Comparatively, preferences in working class homogeneous networks are relatively unaffected by inequality.
+
+Theoretically, I understand economic inequality establishes the field for class relations and conflict that are consequently crystallized in attitudes toward redistribution [@edlund_democratic_2015].
+Also, I conceive class relations as networks of social connections between social classes [@blau_macrosociological_1977].
+In this approach, social influence is linked to redistributive preferences as it represents the driving social force that makes class interests and values more salient as segregation increases [@lindh_missing_2021].
+However, I evidenced that this prevails in societies with low and middle levels of income inequality.
+Hence, I interpret the observed weaker interaction between class and homogeneity in unequal countries in two non-exclusive ways.
+First, social networks become more stratified as inequality increases, increasing the cross-class contacts and lowering network homogeneity in the upper class.
+Second, an alternative explanation is that class homogeneity can reinforce the class divide in contexts where social classes have a stronger political meaning reflected in wider class differences in redistributive preferences.
+Thus, as class relations become segregated, so do redistributive preferences.
+However, I evidenced that unequal societies have weaker class differences mainly because of the higher redistributive preferences in the upper classes.
+Therefore, the consequences of segregated class relations on redistributive preferences become mild as the class divide in political attitudes also loses strength in unequal societies.
 
@@
 
-This research contributes to the study of social class and redistributive preferences, building on previous work that has emphasized the role of social ties.
-First, the cross-national component of this research complements existing studies on the impact of income inequality on social networks and class-based redistributive preferences.
-Second, the diverse range of societies analyzed extends the literature on redistributive preferences and social networks beyond affluent industrialized countries.
+The contribution of this study can be summarized as follows.
+First, I demonstrate that class-based network segregation can reinforce the previously documented class divide in redistributive preferences.
+Unlike previous studies focusing on cross-class contacts, the attention to network homogeneity allows us to observe how different social classes react to inequality in more segregated contexts in societies with different levels of income inequality.
+Second, the inclusion of diverse national contexts provided the opportunity to scrutinize the role of income inequality as a relevant contextual factor that mitigates the association between network segregation and redistributive preferences.
+This comparison is relevant because it allows us to observe how resource inequality also provides a context for class relations which, in turn, has an expression in their attitudes towards redistribution.
 
 However, this study has certain limitations.
-The dependent variable, represented by a two-item index, is a rough proxy for redistributive preferences compared to more detailed questions on social services, taxes, or poverty policies.
-Additionally, the position generator employed is limited in accurately reflecting social classes, especially the self-employed and intermediate-class positions.
-Thus, the results should be interpreted with caution, recognizing these measurement limitations.
-Finally, because structural contact opportunities and value-based interactions jointly shape social network composition, the cross-sectional data used prevents causal claims due to potential endogeneity issues between class position, network structure, and attitudes.
-
-Future research should improve measurement strategies by including established survey questions on attitudes toward specific welfare policies or willingness to pay taxes as redistributive measures.
+On the side of the dependent variable, a two-item index comprises a rough proxy for redistributive preferences compared to more detailed questions on tax or welfare policies.
+Additionally, the position generator employed is limited in accurately representing a class scheme, particularly in the self-employment and authority dimensions.
+Thus, recognizing these measurement limitations, the results should be interpreted cautiously.
+Finally, causality is also a limitation when employing cross-sectional data.
+Theoretically, contact opportunities between classes and sociability preferences jointly drive network composition.
+Therefore, I recognize that the endogenous nature of class positions, network structure, and attitudes imply difficulties regarding causal claims.
+
+Future research should include more fined distinctions in measuring attitudes by including established questions on attitudes toward specific welfare policies or willingness to pay taxes as redistributive measures.
 Additionally, class-based social networks can be better assessed by incorporating other aspects of the market situation of network ties, such as self-employment status or workplace authority.
-Finally, longitudinal analyses can help disentangle the causal mechanisms linking social class, networks, and political attitudes.
+Finally, longitudinal analyses can contribute to disentangling the relationship between class, networks, and political attitudes.
 
@@
 `r if (knitr::is_latex_output()){ '\\appendix'}`
-
 `r if (knitr::is_latex_output()){ '\\section{Appendix}'}`
-
-```{r status-ocup, echo=FALSE, cache=TRUE, results='asis'}
-pacman::p_load(dplyr,knitr,kableExtra)  
-# Create the data frame
-df <- data.frame(
-  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
-  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
-                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
-                 "Executive of large firm", "Lawyer"),
-  ISEI08 = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
-) %>% 
-  arrange(-ISEI08)
-kable(df,linesep = "",booktabs=TRUE,caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
-  kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
-  column_spec(1,width = "10cm") %>%
-  pack_rows("Higher-status positions", 1, 3) %>%
-  column_spec(2) %>% 
-  pack_rows("Middle-status positions", 4, 6) %>% 
-  pack_rows("Lower-status positions", 7, 10) 
-```
-
-```{r descriptive, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
+`r if (knitr::is_latex_output()){ '\\renewcommand{\\thefigure}{A\\arabic{figure}}'}`
+`r if (knitr::is_latex_output()){ '\\renewcommand{\\thetable}{A\\arabic{table}}'}`
+`r if (knitr::is_latex_output()){ '\\setcounter{figure}{0}'}`
+`r if (knitr::is_latex_output()){ '\\setcounter{table}{0}'}`
+
+```{r tab-an-postgen, echo=FALSE, cache=TRUE, results='asis'}
 if (!require("pacman")) install.packages("pacman")
@@
 rm(list=ls())
-
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
+df1$id <- 1:dim(df1)[[1]]
+dfreg <- df1 %>% dplyr::select(id,
+  redist,prefineq,
   egal = egal2,
@@
 
+occup_prop <- df1 %>% 
+  filter(id %in% dfreg$id) %>% 
+  dplyr::select(hrmanager,ceo,lawyer,
+         nurse,police,teacher,
+         cleaner,hairbarber,busdriver,mechanic
+         ) %>% summarise_all(mean,na.rm=T)
+p <- t(round(occup_prop*100,1))[,1]
+pacman::p_load(dplyr,knitr,kableExtra)  
+# Create the data frame
+df <- data.frame(
+  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
+  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
+                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
+                 "Executive of large firm", "Lawyer"),
+  "ISEI" = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
+) %>% 
+  arrange(-ISEI) %>% 
+  mutate("%"=p)
+kable(df,linesep = "",booktabs=TRUE,format='latex',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
+  kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
+  column_spec(1,width = "6cm") %>%
+  pack_rows("Higher-status positions", 1, 3) %>%
+  column_spec(2) %>% 
+  pack_rows("Medium-status positions", 4, 6) %>% 
+  pack_rows("Lower-status positions", 7, 10) %>% 
+  footnote(general = "N = 31,694",footnote_as_chunk = T)
+```
+
+```{r tab-an-desc, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,dclass6res,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  "gini_disp"=wid_gini_disp,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2,country3,country,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=gdppercapita/1000,
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp)
+         )
+
 # dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
@@
   loggdppercapita,
-  wstate2
+  wstate2,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
   ) 
@@
 
-```{r class-agreg}
+```{r tab-an-classag,results='asis', cache=TRUE}
+levels(dfreg$dclass6res) <- c("Upper Service","Lower Service","Routine nonmanual",
+                      "Self-employed","Skilled working","Unskilled working")
+levels(dfreg$dclass3res_V) <- c("Service","Intermediate","Working")
+
 left_join(
 dfreg %>% 
-  group_by(dclass6res,dclass3res_V) %>% summarise(N=n()),
+  group_by(dclass6res,dclass3res_V) %>% summarise(N1=n()) %>% mutate(freq1 = (N1/ dim(dfreg)[[1]])*100),
 dfreg %>% 
-  group_by(dclass3res_V) %>% summarise(N=n()),by="dclass3res_V"
+  group_by(dclass3res_V) %>% summarise(N2=n()) %>% mutate(freq2 = (N2 / dim(dfreg)[[1]])*100),by="dclass3res_V"
 ) %>% 
-  kable(booktabs = TRUE,format = "latex", linesep = "",
+  dplyr::select("dclass6res","N1","freq1","dclass3res_V","N2","freq2") %>%
+  kable(booktabs = TRUE, format='latex',linesep = "",digits = 1,format.args = list(big.mark = ","),
         caption = "Level of aggregation of social class",
-        col.names = c("Class (6)","Class (3)","N","N")) %>% 
+        col.names = c("EGP-6","N","%","EGP-3","N","%")) %>% 
   kable_styling(full_width = F,latex_options = "HOLD_position") %>% 
-  collapse_rows(columns = 1:4, valign = "top")
-```
-
-```{r desc-country, echo=FALSE, results='asis'}
+  collapse_rows(columns = c(4,5,6), valign = "middle") %>% 
+  footnote(general = "N = 31,694",footnote_as_chunk = T)
+```
+
+```{r tab-an-countries, echo=FALSE, results='asis'}
+dfreg$country <- countrycode::countrycode(sourcevar = dfreg$country2,origin = "iso3c",destination = "iso2c")
+dfreg$country3b <- paste0(dfreg$country3," (",dfreg$country,")")
 dfreg %>% 
-  group_by(country3) %>% 
+  group_by(country3b) %>% 
   summarise(n=n(),
@@
             wstate=mean(wstate2)) %>% 
-  arrange(homclass) %>% 
-  kable(digits = 2,booktabs = TRUE,format = "latex", linesep = "",
+  arrange(homclass) %>% ungroup() %>% 
+  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = "latex", linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
         caption = "Values per country for the macro-social variables",
-        col.names = c("Country","N","Network Homogeneity","Gini Index","GDP/capita in $1000","Size of the Welfare State")) %>% 
+        col.names = c("Country","N","Network Homogeneity","Income Inequality (Gini Index)","GDP/capita in $1000","Size of the Welfare State")) %>% 
   kable_styling(full_width = F,latex_options = "scale_down") %>% 
-  column_spec(1, width = "3.2cm") %>% 
-  column_spec(2:6, width = "3cm") %>% 
-  footnote(general = "Data sources are from the ISSP 2017 - Social Networks, WID and ILO. Contextual variables in original scale")
-```
-
-```{r figapp1, fig.dim=c(5,5),out.width='50%',fig.cap='Bivariate relationships between Income Inequality and Class differences in network homogeneity',warning=FALSE}
+  column_spec(column = c(1), width = "4cm") %>%
+  column_spec(column = c(2:6), width = "3cm") %>%
+  footnote(general = "N = 31,694; Source: ISSP 2017, WID, WIID and ILO. Variables in original scale",
+           footnote_as_chunk = T)  
+# dfreg %>% 
+#   group_by(country3) %>% 
+#   summarise(gini_disp=mean(gini_disp),
+#             gdp_1000=mean(loggdppercapita),
+#             # wstate=mean(wstate2),
+#             abs_red=mean(abs_red),
+#             ilo_taxrev=mean(ilo_taxrev),
+#             ilo_govspe=mean(ilo_govspe)
+#             ) %>% ungroup() %>% 
+#   correlation::correlation() %>% 
+#   summary() %>% 
+#   correlation::print_md()
+```
+
+```{r fig-an1, fig.dim=c(9,9),out.width='80%',fig.cap='Relationship between income inequality and class differences in network homogeneity',warning=FALSE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-```{r table1full, results='asis'}
+```{r tab-an-full, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,
+texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,symbol = ".",
        caption = paste("(\\#tab:table1full)","Multilevel models for network homogeneity and redistributive preferences"),
-       custom.note = "\\item Note: Standard errors in parentheses. $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$",threeparttable = T,
+       custom.note = "\\item Note: Standard errors in parentheses. %stars",threeparttable = T,
        caption.above = T,leading.zero = T,

### 2024-07-16 paper1_jiturra_supp-material.Rmd
appendix

@@
 dummy_df <- df1 %>% dplyr::select(id,
+                                  redist,prefineq,
   egal = egal2,dclass3res_V,
@@
 
-df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
-df1$isei08 <- car::recode(df1$isei08,"NA=0")
+# df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
+# df1$isei08 <- car::recode(df1$isei08,"NA=0")
 
@@
 df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-dummy_df <- df1 %>% dplyr::select(id,
+dummy_df <- df1 %>% dplyr::select(id,redist,prefineq,
   egal = egal2,dclass3res_V,
@@
 df1$isei08sp <- car::recode(df1$isei08sp,"NA=0")
-dfreg <- df1 %>% dplyr::select(id,
+dfreg <- df1 %>% dplyr::select(id,redist,prefineq,
   egal = egal2,

### 2024-07-16 procesamiento/01-prod_prep-micro.Rmd
appendix

@@
 
-#frq(df1$v1)
+# frq(df1$v1)
 df1$busdriver <- as.numeric(car::recode(df1$v1,"1:3=1;4=0")) 
 sjlabelled::set_label(df1$busdriver) <- "Know: bus/lorry driver" 
-#frq(df1$busdriver)
+# frq(df1$busdriver)
 
@@
 df1$know_total <- rowSums(x = dplyr::select(df1,isei_ocupnames),na.rm = T)
-# summary(df1$know_total)
+summary(df1$know_total)
 sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'

### 2024-07-17 paper1_jiturra.Rmd
ajuste de anexos

@@
 fontsize: 12pt
-linestretch: '1.15'          # interlineado  
+linestretch: '1.5'          # interlineado  
 #linestretch: '2.0'          # interlineado 
@@
 
- the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
+ During the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
 In contrast, less attention has been paid to the role of social networks on redistributive preferences.
@@
 Following previous research, a simplified version of the EGP class scheme that collapses three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
-Specifically, this version distinguishes among the Service Class (higher and lower managerial and professionals), Intermediate Class (routine nonmanual workers and self-employed), and Working Class (manual supervisors, skilled and unskilled manual workers).
+Specifically, this version distinguishes among the Service Class (higher and lower managerial and professionals), Intermediate Class (routine nonmanual workers and self-employed), and Working Class (manual supervisors, skilled and unskilled manual workers) (see Table \@ref(tab:tab-an-classag) in the Appendix).
 
@@
 Subsequently, following @otero_differences_2023 I classify occupations into three status positions that resemble Goldthorpe's class positions based on the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010].
-The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *higher* (ISEI range: 68-85); school teacher, police officer, and nurse are classified as *medium* (ISEI range: 48-63); and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *lower* (ISEI range: 17-38) positions (see Table \@ref(tab:tab-an-postgen) in the Appendix).
+The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *higher* positions (ISEI range: 68-85); school teacher, police officer, and nurse are classified as *medium* positions (ISEI range: 48-63); and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *lower* positions (ISEI range: 17-38).
 
@@
 
-```{r tab-an-postgen, echo=FALSE, cache=TRUE, results='asis'}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$id <- 1:dim(df1)[[1]]
-dfreg <- df1 %>% dplyr::select(id,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,dclass6res,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  "gini_disp"=wid_gini_disp,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2,country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>%
-    mutate(loggdppercapita=gdppercapita/1000,
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp)
-         )
-
-occup_prop <- df1 %>% 
-  filter(id %in% dfreg$id) %>% 
-  dplyr::select(hrmanager,ceo,lawyer,
-         nurse,police,teacher,
-         cleaner,hairbarber,busdriver,mechanic
-         ) %>% summarise_all(mean,na.rm=T)
-p <- t(round(occup_prop*100,1))[,1]
-pacman::p_load(dplyr,knitr,kableExtra)  
-# Create the data frame
-df <- data.frame(
-  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
-  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
-                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
-                 "Executive of large firm", "Lawyer"),
-  "ISEI" = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
-) %>% 
-  arrange(-ISEI) %>% 
-  mutate("%"=p)
-kable(df,linesep = "",booktabs=TRUE,format='latex',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
-  kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
-  column_spec(1,width = "6cm") %>%
-  pack_rows("Higher-status positions", 1, 3) %>%
-  column_spec(2) %>% 
-  pack_rows("Medium-status positions", 4, 6) %>% 
-  pack_rows("Lower-status positions", 7, 10) %>% 
-  footnote(general = "N = 31,694",footnote_as_chunk = T)
-```
-
-```{r tab-an-desc, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,dclass6res,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  "gini_disp"=wid_gini_disp,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2,country3,country,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=gdppercapita/1000,
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp)
-         )
-
-# dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-dfreg$wstate<- rowMeans(dfreg[,c("abs_red","ilo_taxrev","ilo_govspe")],na.rm = T)
-dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
-
-dfreg1 <- dfreg %>% dplyr::select(
-  egal,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  dclass3res_V,
-  Q03pcm,
-  edyears,
-  # dclass3spo_V,  
-  workst,
-  # union,
-  female,
-  agenum,
-  # religion,
-  partner,
-  "gini_disp",
-  loggdppercapita,
-  wstate2,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  ) 
-```
-
-```{r tab-an-classag,results='asis', cache=TRUE}
-levels(dfreg$dclass6res) <- c("Upper Service","Lower Service","Routine nonmanual",
-                      "Self-employed","Skilled working","Unskilled working")
-levels(dfreg$dclass3res_V) <- c("Service","Intermediate","Working")
-
-left_join(
-dfreg %>% 
-  group_by(dclass6res,dclass3res_V) %>% summarise(N1=n()) %>% mutate(freq1 = (N1/ dim(dfreg)[[1]])*100),
-dfreg %>% 
-  group_by(dclass3res_V) %>% summarise(N2=n()) %>% mutate(freq2 = (N2 / dim(dfreg)[[1]])*100),by="dclass3res_V"
-) %>% 
-  dplyr::select("dclass6res","N1","freq1","dclass3res_V","N2","freq2") %>%
-  kable(booktabs = TRUE, format='latex',linesep = "",digits = 1,format.args = list(big.mark = ","),
-        caption = "Level of aggregation of social class",
-        col.names = c("EGP-6","N","%","EGP-3","N","%")) %>% 
-  kable_styling(full_width = F,latex_options = "HOLD_position") %>% 
-  collapse_rows(columns = c(4,5,6), valign = "middle") %>% 
-  footnote(general = "N = 31,694",footnote_as_chunk = T)
-```
-
-```{r tab-an-countries, echo=FALSE, results='asis'}
-dfreg$country <- countrycode::countrycode(sourcevar = dfreg$country2,origin = "iso3c",destination = "iso2c")
-dfreg$country3b <- paste0(dfreg$country3," (",dfreg$country,")")
-dfreg %>% 
-  group_by(country3b) %>% 
-  summarise(n=n(),
-            homclass=mean(x=homclass3_V_res),
-            gini_disp=mean(gini_disp),
-            loggdppercapita=mean(loggdppercapita),
-            wstate=mean(wstate2)) %>% 
-  arrange(homclass) %>% ungroup() %>% 
-  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = "latex", linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
-        caption = "Values per country for the macro-social variables",
-        col.names = c("Country","N","Network Homogeneity","Income Inequality (Gini Index)","GDP/capita in $1000","Size of the Welfare State")) %>% 
-  kable_styling(full_width = F,latex_options = "scale_down") %>% 
-  column_spec(column = c(1), width = "4cm") %>%
-  column_spec(column = c(2:6), width = "3cm") %>%
-  footnote(general = "N = 31,694; Source: ISSP 2017, WID, WIID and ILO. Variables in original scale",
-           footnote_as_chunk = T)  
-# dfreg %>% 
-#   group_by(country3) %>% 
-#   summarise(gini_disp=mean(gini_disp),
-#             gdp_1000=mean(loggdppercapita),
-#             # wstate=mean(wstate2),
-#             abs_red=mean(abs_red),
-#             ilo_taxrev=mean(ilo_taxrev),
-#             ilo_govspe=mean(ilo_govspe)
-#             ) %>% ungroup() %>% 
-#   correlation::correlation() %>% 
-#   summary() %>% 
-#   correlation::print_md()
-```
-
-```{r fig-an1, fig.dim=c(9,9),out.width='80%',fig.cap='Relationship between income inequality and class differences in network homogeneity',warning=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  gdppercapita,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         # gini_disp=scale(gini_disp),
-         )
-
-homo_ineq <- dfreg %>%
-  group_by(country2,country3) %>%
-  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame()
-
-homo_class_diff <- dfreg %>%   
-  group_by(country2,country3,dclass3res_V) %>%
-  summarise_at(c("egal","homclass3_V_res"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  dplyr::select(country3,homclass3_V_res,dclass3res_V) %>% 
-  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass3_V_res") %>% 
-  mutate(diff_working_upper_homo = `Working Class (V+VI+VII)` - `Service Class (I+II)`) %>% 
-  as.data.frame()
-
-# Dataset with class differences in network homogeneity
-homo_ineq <- homo_ineq %>% left_join(homo_class_diff)
-
-# Plot Homogeneity and redistributive preferences
-homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
-
-fig_homodiff_gini<- 
-homo_ineq %>%  
-ggplot(aes(y=diff_working_upper_homo, x=gini_disp)) +
-  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
-  # geom_text() +
-  geom_text_repel(label=as.character(homo_ineq$country)) +
-  xlab("Income Inequality") +
-  ylab("Class Differences in Network homogeneity \n (Working Class - Service Class)") +
-  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
-                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = NULL)
-
-#cor.test(homo_ineq$diff_working_upper_homo,
-#                                    homo_ineq$gini_disp, use='complete.obs')
-
-grid.arrange(fig_homodiff_gini, nrow = 1, 
- bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
- gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
-  ))
-
-ggsave(plot = arrangeGrob(fig_homodiff_gini, nrow = 1),filename = "slides-bivar-homodiff.png",device = "png",
-       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
-```
-
 ```{r tab-an-full, results='asis'}
@@
 ```
+
+```{r fig-an1, fig.dim=c(9,9),out.width='80%',fig.cap='Relationship between income inequality and class differences in network homogeneity',warning=FALSE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp),
+         )
+
+homo_ineq <- dfreg %>%
+  group_by(country2,country3) %>%
+  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
+  as.data.frame()
+
+homo_class_diff <- dfreg %>%   
+  group_by(country2,country3,dclass3res_V) %>%
+  summarise_at(c("egal","homclass3_V_res"), mean, na.rm = TRUE) %>% 
+  as.data.frame() %>%
+  dplyr::select(country3,homclass3_V_res,dclass3res_V) %>% 
+  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass3_V_res") %>% 
+  mutate(diff_working_upper_homo = `Working Class (V+VI+VII)` - `Service Class (I+II)`) %>% 
+  as.data.frame()
+
+# Dataset with class differences in network homogeneity
+homo_ineq <- homo_ineq %>% left_join(homo_class_diff)
+
+# Plot Homogeneity and redistributive preferences
+homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")
+
+fig_homodiff_gini<- 
+homo_ineq %>%  
+ggplot(aes(y=diff_working_upper_homo, x=gini_disp)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  # geom_text() +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Income Inequality") +
+  ylab("Class Differences in Network homogeneity \n (Working Class - Service Class)") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
+                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = NULL)
+
+#cor.test(homo_ineq$diff_working_upper_homo,
+#                                    homo_ineq$gini_disp, use='complete.obs')
+
+grid.arrange(fig_homodiff_gini, nrow = 1, 
+ bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
+ gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
+  ))
+
+ggsave(plot = arrangeGrob(fig_homodiff_gini, nrow = 1),filename = "slides-bivar-homodiff.png",device = "png",
+       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
+```
+
+```{r tab-an-postgen, echo=FALSE, cache=TRUE, results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$id <- 1:dim(df1)[[1]]
+dfreg <- df1 %>% dplyr::select(id,
+  redist,prefineq,
+  pct_low,pct_middle,pct_high,
+  egal = egal2,
+  dclass3res_V,dclass6res,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  "gini_disp"=wid_gini_disp,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2,country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>%
+    mutate(loggdppercapita=gdppercapita/1000,
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp)
+         )
+
+occup_prop <- df1 %>% 
+  filter(id %in% dfreg$id) %>% 
+  dplyr::select(hrmanager,ceo,lawyer,
+         nurse,police,teacher,
+         cleaner,hairbarber,busdriver,mechanic
+         ) %>% summarise_all(mean,na.rm=T)
+
+status_prop <- df1 %>% 
+  filter(id %in% dfreg$id) %>% 
+  dplyr::select(pct_high,pct_middle,pct_low,
+         ) %>% summarise_all(mean,na.rm=T)
+
+p <- t(round(occup_prop*100,1))[,1]
+pacman::p_load(dplyr,knitr,kableExtra)  
+# Create the data frame
+df <- data.frame(
+  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
+  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
+                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
+                 "Executive of large firm", "Lawyer"),
+  "ISEI" = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
+) %>% 
+  arrange(-ISEI) %>% 
+  mutate("%"=p)
+kable(df,linesep = "",booktabs=TRUE,format='html',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
+  kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
+  column_spec(1,width = "6cm") %>%
+  pack_rows("Higher-status positions", 1, 3) %>%
+  column_spec(2) %>% 
+  pack_rows("Medium-status positions", 4, 6) %>% 
+  pack_rows("Lower-status positions", 7, 10) %>% 
+  footnote(general = "N = 31,694",footnote_as_chunk = T)
+```
+
+```{r tab-an-desc, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,dclass6res,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  "gini_disp"=wid_gini_disp,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2,country3,country,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=gdppercapita/1000,
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp)
+         )
+
+# dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+dfreg$wstate<- rowMeans(dfreg[,c("abs_red","ilo_taxrev","ilo_govspe")],na.rm = T)
+dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
+
+dfreg1 <- dfreg %>% dplyr::select(
+  egal,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  dclass3res_V,
+  Q03pcm,
+  edyears,
+  # dclass3spo_V,  
+  workst,
+  # union,
+  female,
+  agenum,
+  # religion,
+  partner,
+  "gini_disp",
+  loggdppercapita,
+  wstate2,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  ) 
+```
+
+```{r tab-an-classag,results='asis', cache=TRUE}
+levels(dfreg$dclass6res) <- c("Upper Service","Lower Service","Routine nonmanual",
+                      "Self-employed","Skilled working","Unskilled working")
+levels(dfreg$dclass3res_V) <- c("Service","Intermediate","Working")
+
+left_join(
+dfreg %>% 
+  group_by(dclass6res,dclass3res_V) %>% summarise(N1=n()) %>% mutate(freq1 = (N1/ dim(dfreg)[[1]])*100),
+dfreg %>% 
+  group_by(dclass3res_V) %>% summarise(N2=n()) %>% mutate(freq2 = (N2 / dim(dfreg)[[1]])*100),by="dclass3res_V"
+) %>% 
+  dplyr::select("dclass6res","N1","freq1","dclass3res_V","N2","freq2") %>%
+  kable(booktabs = TRUE, format='latex',linesep = "",digits = 1,format.args = list(big.mark = ","),
+        caption = "Level of aggregation of social class",
+        col.names = c("EGP-6","N","%","EGP-3","N","%")) %>% 
+  kable_styling(full_width = F,font_size = 10,latex_options = c("HOLD_position")) %>% 
+  collapse_rows(columns = c(4,5,6), valign = "middle") %>% 
+  footnote(general = "N = 31,694",footnote_as_chunk = T)
+```
+
+```{r tab-an-countries, echo=FALSE, results='asis'}
+dfreg$country <- countrycode::countrycode(sourcevar = dfreg$country2,origin = "iso3c",destination = "iso2c")
+dfreg$country3b <- paste0(dfreg$country3," (",dfreg$country,")")
+dfreg %>% 
+  group_by(country3b) %>% 
+  summarise(n=n(),
+            homclass=mean(x=homclass3_V_res),
+            gini_disp=mean(gini_disp),
+            loggdppercapita=mean(loggdppercapita),
+            wstate=mean(wstate2)) %>% 
+  arrange(homclass) %>% ungroup() %>% 
+  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = "latex", linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
+        caption = "Values per country for the macro-social variables",
+        col.names = c("Country","N","Network Homogeneity","Income Inequality (Gini Index)","GDP/capita in $1000","Size of the Welfare State")) %>% 
+  kable_styling(full_width = F,latex_options = "scale_down") %>% 
+  column_spec(column = c(1), width = "4cm") %>%
+  column_spec(column = c(2:6), width = "3cm") %>%
+  footnote(general = "N = 31,694; Source: ISSP 2017, WID, WIID and ILO. Variables in original scale",
+           footnote_as_chunk = T)  
+# dfreg %>% 
+#   group_by(country3) %>% 
+#   summarise(gini_disp=mean(gini_disp),
+#             gdp_1000=mean(loggdppercapita),
+#             # wstate=mean(wstate2),
+#             abs_red=mean(abs_red),
+#             ilo_taxrev=mean(ilo_taxrev),
+#             ilo_govspe=mean(ilo_govspe)
+#             ) %>% ungroup() %>% 
+#   correlation::correlation() %>% 
+#   summary() %>% 
+#   correlation::print_md()
+```

### 2024-07-18 paper1_jiturra.Rmd
review

@@
 
-Class relations can also be comprehended as the structure of social ties between classes as a characteristic of the social structure, represented as networks formed by different social classes [@blau_macrosociological_1977].
-Empirically, homophily in social relations is a consistent finding in the social network literature [@mcpherson_birds_2001].
-This means that friendship and family ties tend to be homogeneous concerning social status and demographic characteristics, while distant ties bridge individuals to different social groups and contribute to network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
-Besides, socialization preferences indeed play a role in the formation of segregated networks [@visser_attitudes_2004;@homans_human_1951].
-However, the similarity of attitudes in segregated networks results more from the social differentiation that structures class ties than from individual preferences [@feld_focused_1981].
-
-There are two approaches in the study of class relations from a network perspective.
-On the one hand, network diversity is defined as the degree of connectedness to dissimilar occupations, which represents vertical access to resource diversity embedded in social networks [@lin_access_1986].
-However, diversity is defined as the variability of different ties within the network without necessarily providing a reference position to describe network similarity.
-On the other hand, network segregation is the absence of cross-class connections and represents how similar network ties are in reference to the individual.
-This perspective is conceptually closer to homophily as it is anchored in individual class positions and has been empirically addressed through network homogeneity [@otero_open_2021].
+Class relations can be understood as the structure of social ties between different classes within the social structure, represented by networks formed by various social classes [@blau_macrosociological_1977].
+Empirical evidence consistently shows homophily in social relations within the social network literature [@mcpherson_birds_2001].
+This indicates that friendships and family ties are often homogeneous regarding social status and demographic characteristics, whereas distant ties connect individuals to different social groups and enhance network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
+Moreover, socialization preferences do play a role in the formation of segregated networks [@visser_attitudes_2004; @homans_human_1951].
+However, the similarity of attitudes within these networks arises more from the social differentiation structuring class ties than from individual preferences [@feld_focused_1981].
+
+The study of class relations from a network perspective can be approached in two ways.
+First, network diversity is defined as the degree of connectedness to dissimilar occupations, representing vertical access to resource diversity within social networks [@lin_access_1986].
+In this context, diversity refers to the variability of different ties within the network without necessarily providing a reference point to describe network similarity.
+Second, network segregation, defined as the absence of cross-class connections, indicates how similar network ties are in reference to the individual.
+This perspective is conceptually closer to homophily, as it is anchored in individual class positions and has been empirically addressed through network homogeneity [@otero_open_2021].
 
 How does social class stratify social networks?
-Empirically, studies on network diversity reveal that higher civic engagement in formal organizations increases the likelihood of the upper-class forming connections with diverse individuals, in contrast to the more homogeneous participation observed among the working class [@pichler_social_2009].
-Similar patterns are observed in the composition of social ties, where the upper and intermediate classes maintain increasingly diverse and prestigious social environments compared to the working class [@cepic_how_2020;@carrascosa_class_2023].
+Empirical studies on network diversity reveal that higher civic engagement in formal organizations increases the likelihood of the upper class forming connections with diverse individuals, contrasting with the more homogeneous participation observed among the working class [@pichler_social_2009].
+Similar patterns are found in the composition of social ties, where the upper and intermediate classes maintain more diverse and prestigious social environments compared to the working class [@cepic_how_2020; @carrascosa_class_2023].
 In contrast, studies on network segregation suggest that property-based boundaries are less permeable than authority-based ones.
-For example, @wright_relative_1992 suggest that since class interests widen the social distance between proprietors and manual workers, the intermediate position of supervisors and their higher contact frequency with manual workers makes the formation of friendship ties more likely.
-Similarly, @otero_open_2021 found that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class, suggesting that their limited life chances and lower capacity for social engagement ultimately result in segregation.
+For example, @wright_relative_1992 suggest that class interests widen the social distance between proprietors and manual workers, while the intermediate position of supervisors and their higher contact frequency with manual workers make the formation of friendship ties more likely.
+Similarly, @otero_open_2021 found that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class.
+This suggests that limited life chances and lower capacity for social engagement ultimately result in segregation.
 Conversely, the upper class is more homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
@@
 
-[^altmodels]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile ratio (D9/D1) and the Top 10/Bottom 50 ratio.
+[^altmodels]: Supplementary analyses employing alternative income inequality measures show that the results are robust when using the Inter-decile (D9/D1) and the Top 10/Bottom 50 ratios.
 Additionally, I classified countries into low, middle-low, middle, middle-high, and high-income inequality groups based on quintiles according to the Gini index.

### 2024-07-18 paper1_jiturra_supp-material.Rmd
review

@@
 # Supplementary material
+
+## Influential case analysis
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  # religion,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+dfreg <- na.omit(dfreg)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
+digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
+# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
+digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
+# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
+
+digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Create an empty list to store results
+results <- list()
+countries<- levels(as.factor(dfreg$country2))
+subset(dfreg,country2!="AUT")
+
+# Iterate over each country
+for (i in countries){
+  # Exclude the i-th country
+  subset_data <-dfreg %>% dplyr::filter(country2 != i)
+  # Refit the model without the i-th country
+  model_i <- lmer(egal~homclass3_V_res+know_total+female+agenum+partner+edyears + Q03pcm + workst + (1 | country2) + dclass3res_V + homclass3_V_res:dclass3res_V, data = subset_data,weights = WEIGHT)
+
+  # Store the results
+  results[[i]] <- model_i
+
+  }
+
+tidyresults <- list()
+for (i in countries) {
+  tidyresults[[i]] <- broom::tidy(results[[i]],conf.int=T)
+}
+
+jk<- bind_rows(tidyresults, .id = "country");jk$country <-paste("Excluding",jk$country) 
+```
+
+```{r byoneone-exclusion,fig.dim=c(10,10),fig.cap='Interaction of network homogeneity and social class on redistributive preferences. Excluding countries one by one.'}
+jk %>% filter(term %in% c("homclass3_V_res",
+                          "dclass3res_VIntermediate class (III+IV)","dclass3res_VWorking Class (V+VI+VII)",
+                          "homclass3_V_res:dclass3res_VIntermediate class (III+IV)",
+                          "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)")) %>% 
+  ggplot(mapping = aes(y=estimate,x=term,ymin = conf.low, ymax = conf.high)) + 
+  geom_point() +
+  geom_errorbar(width = 0.2) +
+  labs(x=NULL,y="Estimates") +
+  scale_x_discrete(limits=rev(c("homclass3_V_res",
+                          "dclass3res_VIntermediate class (III+IV)","dclass3res_VWorking Class (V+VI+VII)",
+                          "homclass3_V_res:dclass3res_VIntermediate class (III+IV)",
+                          "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)")),
+                   labels=c("Hom:Working","Hom:Intermediate","Working Class","Intermediate Class","Homogeneity"))+
+  geom_hline(yintercept = 0,color="red")+
+  coord_flip() +
+  facet_wrap(~country)
+```
+
+Using dfbetas and Cook distance, there are influential cases. Subsequently I see that in some cases the value is altered, but these changes are not significant.
+
+```{r fig.dim=c(5,5),fig.cap='Cook distance'}
+library(influence.ME)
+estex.m31 <- influence(digclas1_VW_7, "country2")
+dfbetas(estex.m31) 
+cutpoint<- 2/sqrt(31) # cut point
+
+plot(estex.m31, which="cook",
+     cutoff=4/31, sort=TRUE,
+     xlab="Cooks Distance",
+     ylab="Country")
+# sigtest(estex.m31, test=-1.96)
+```
 

### 2024-07-18 paper1_jiturra.Rmd
reviews

@@
       groups = list("Social Class (Ref.= Service Class)" = 3:4, 
-                    # "Household Income (Ref.= Tertile I)"= 6:8,
-                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
       "Homogeneity x Social Class"=5:6),
@@
        float.pos = "h!",
-      # file = "table1.html",
        use.packages = F)
+
+htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
+       caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
+       custom.note = "Note: Models include sampling weights. Standard errors in parentheses. %stars",
+       threeparttable = T,
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 3:4,
+      "Homogeneity x Social Class"=5:6),
+      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+      file = "output/tables/table01.doc"
+      )
 # performance::check_collinearity(digclas1_VW_5)
@@
 On the one hand, I expected that network homogeneity has a weak direct association with redistributive preferences as it reveals only the overall segregation without distinction between classes.
-In this matter, Model 1 integrates network homogeneity and as it is previously noted in the macro associations, individuals with more homogeneous networks tend to exhibit stronger redistributive preferences.
-Then, this association is robust to network size, sociodemographic characteristics, and socioeconomic status in Model 2.
+In this matter, Model 1 integrates network homogeneity and as it is previously noted in the macro associations, more homogeneous networks tend to exhibit higher redistributive preferences.
+Then, the association is robust to network size, sociodemographic characteristics, and socioeconomic status in Model 2.
 However, after including individual social class in Model 3, the association between homogeneity and redistributive preferences loses its strength.
@@
 Thus, the interaction terms of network homogeneity and social class in Model 4 show that compared to the service class, homogeneity increases redistributive preferences in the working and intermediate classes.
-To illustrate this result further, Figure \@ref(fig:fig4) depicts that the increasing redistributive preferences in homogenous working and intermediate class networks are quite mild, where the differences in redistributive preferences go from 69.8 to 72.8 and from 69.4 to 70.47, respectively.
-In contrast, the decreasing redistributive preferences in homogeneous services class networks are more pronounced, changing from 70 when homogeneity is at its lowest point to 62.8 in fully homogeneous networks.
-Altogether, these results provide evidence in favor of the segregation hypothesis (H1), where the class divide in redistributive preferences becomes stronger for individuals with more homogeneous social networks.
+To illustrate this result further, Figure \@ref(fig:fig4) depicts that the changes in redistributive preferences from low to high homogenous working and intermediate class networks are quite mild, where the differences in redistributive preferences go from 69.8 to 72.8 and from 69.4 to 70.47, respectively.
+In contrast, the changes in redistributive preferences in homogeneous services class networks are more pronounced, changing from 70 when homogeneity is at its lowest point to 62.8 in fully homogeneous networks.
+Altogether, these results provide evidence in favor of the segregation hypothesis (H1), where the class differences in redistributive preferences become wider as network homogeneity increases.
 
@@
 
-ggsave(plot = last_plot(),filename = "slides-predictions.png",device = "png",
+ggsave(plot = last_plot(),filename = "figure04.png",device = "png",
        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
@@
        use.packages = F)
+
+htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
+       caption = paste("Multilevel models for income inequality, network homogeneity and redistributive preferences"),
+       custom.note = " Note: Models include sampling weights and individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Country (Intercept)",
+                           "Var: Country Homogeneity",
+                           "Var: Country Intermediate Class ",
+                           "Var: Country Working Class",
+                           "Cov: Country (Intercept), Homogeneity",
+                           "Cov: Country (Intercept), Intermediate Class ",
+                           "Cov: Country (Intercept), Working Class",
+                           "Cov: Country Homogeneity, Intermediate Class",
+                           "Cov: Country Homogeneity, Working Class",
+                           "Cov: Country Intermediate Class, Working Class",
+                           "Var: Residual"),
+        file = "output/tables/table02.doc")
 ```
@@
 At the macro level, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
-To better illustrate this result, Figure \@ref(fig:fig5) depicts how the relationship between network homogeneity and social class is gradually mitigated as income inequality increases.
-In this regard, the left panel in Figure \@ref(fig:fig5) illustrates that under conditions of lower income inequality, the conditional association of network homogeneity and social class on redistributive preferences is more pronounced than in the center and left panels that respectively represent contexts of middle and higher income inequality.
+To better illustrate this result, Figure \@ref(fig:fig5) depicts how the interaction of network homogeneity and social class is gradually mitigated as income inequality increases.
+In this regard, the left panel in Figure \@ref(fig:fig5) illustrates that when inequality is low, the conditional association of network homogeneity and social class on redistributive preferences is more pronounced than in the center and left panels that respectively represent contexts of middle and higher income inequality.
 
@@
 
-This research examines how class-based network segregation is associated with redistributive preferences and how income inequality mitigates this relationship from a cross-national perspective.
-[@lindh_missing_2021;@paskov_crossclass_2022].
-Despite the claimed detrimental direct association of network segregation on attachment to society [@otero_lives_2022], my first finding suggests that network segregation is rather conditional to social class in the case of redistributive preferences than directly detrimental.
+This research examines how class-based network segregation is associated with redistributive preferences and how income inequality mitigates this relationship from a cross-national perspective [@lindh_missing_2021;@paskov_crossclass_2022].
+In contrast, to the claimed detrimental direct association of network segregation on attachment to society [@otero_lives_2022], my first finding suggests that network segregation is rather conditional to social class in the case of redistributive preferences than directly prejudicial.
 Here, I evidenced that higher network homogeneity in the working class increases redistributive preferences, while homogeneous networks in the service class reduce support for redistribution.
 
-In theory, my first hypothesis was that the class divide in redistributive preferences should consider individual class positions and the structure of social networks as sources of preference formation.
+In theory, my first hypothesis was that the study of class differences in redistributive preferences should not only consider individual class positions, but the structure of social networks as sources of preference formation.
 Hence, my finding supports the claims that social influence and particularly segregation in interpersonal networks strengthen class differences in redistributive preferences [@lee_consider_2023;@lindh_missing_2021].
 Also, these results support the idea that low cross-class connections can reduce social integration and solidarity as they limit awareness about the lives of other classes [@blau_macrosociological_1977;@otero_lives_2022].
-Furthermore, the 'empathy gulf' is evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive pressures of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
-
-Besides the micro-level findings, my second hypothesis was that economic inequality moderates the conditional association of network homogeneity by social class and redistributive preferences.
-The results from the multilevel models indicate that income inequality _mitigates_ this relationship.
+Furthermore, the claimed 'empathy gulf' is more evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive demands of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
+
+Besides the micro-level findings, my second hypothesis was that economic inequality mitigates the conditional association of network homogeneity by social class and redistributive preferences.
+The results from the multilevel models indicate that income inequality indeed _mitigates_ this relationship.
 In other words, the role of network segregation observed in the interaction of homogeneity and class is less pronounced in highly unequal societies.
 Particularly, the most notable differences in redistributive preferences are observed in homogeneous service class networks.
-Comparatively, preferences in working class homogeneous networks are relatively unaffected by inequality.
+In contrast, preferences in homogeneous working class networks are relatively unaffected by inequality.
 
@@
 Also, I conceive class relations as networks of social connections between social classes [@blau_macrosociological_1977].
-In this approach, social influence is linked to redistributive preferences as it represents the driving social force that makes class interests and values more salient as segregation increases [@lindh_missing_2021].
-However, I evidenced that this prevails in societies with low and middle levels of income inequality.
-Hence, I interpret the observed weaker interaction between class and homogeneity in unequal countries in two non-exclusive ways.
-First, social networks become more stratified as inequality increases, increasing the cross-class contacts and lowering network homogeneity in the upper class.
-Second, an alternative explanation is that class homogeneity can reinforce the class divide in contexts where social classes have a stronger political meaning reflected in wider class differences in redistributive preferences.
-Thus, as class relations become segregated, so do redistributive preferences.
-However, I evidenced that unequal societies have weaker class differences mainly because of the higher redistributive preferences in the upper classes.
-Therefore, the consequences of segregated class relations on redistributive preferences become mild as the class divide in political attitudes also loses strength in unequal societies.
+In this approach, social influence is linked to redistributive preferences as it represents the driving social force that makes class positions more salient as segregation increases [@lindh_missing_2021].
+However, I evidenced that this prevails mostly in societies with low and middle levels of income inequality.
+
+In this regard, I interpret the observed weaker interaction between homogeneity and class in unequal countries in two non-exclusive ways.
+First, social networks become more stratified as inequality increases, increasing the cross-class contacts and lowering network homogeneity mainly in the upper class.
+Here, it could be possible that higher social integration through social ties towards the intermediate and lower class positions can increase empathy and motivate solidarity towards other social classes and express greater support for redistribution.
+Second, an additional possible explanation could be that class homogeneity reinforces the class divide in contexts where social classes have a stronger political meaning reflected in wider class differences in redistributive preferences.
+In this way, as class relations become more segregated, so does the class divide in redistributive preferences.
+Besides, an important related fact is that unequal societies have smaller class differences mainly because of the higher redistributive preferences in the upper classes.
+Thus, the consequences of segregated class relations on redistributive preferences become mild as the class divide in political attitudes also loses strength in unequal societies.
 
@@
 
-```{r tab-an-full, results='asis'}
+```{r tab-an-1, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
   mutate("%"=p)
-kable(df,linesep = "",booktabs=TRUE,format='html',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
+kable(df,linesep = "",booktabs=TRUE,format='latex',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
   kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%

### 2024-07-18 paper1_jiturra_supp-material.Rmd
reviews

@@
 
+Several robustness checks were consistent with our main results.
+First, a (delete-one) jackknife procedure indicated that estimations for the segregation hypothesis are robust to outliers.
+Additonaly, Using dfbetas and Cook distance, there are influential cases.
+Subsequently I see that in some cases the value is altered, but these changes are not significant.
+Second, repeating the procedure with the models, including the cross-level interaction for the mitigation hypothesis, leads to relatively same results.
+
 ```{r}
@@
 
-Using dfbetas and Cook distance, there are influential cases. Subsequently I see that in some cases the value is altered, but these changes are not significant.
-
 ```{r fig.dim=c(5,5),fig.cap='Cook distance'}
@@
 # sigtest(estex.m31, test=-1.96)
+```
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V, 
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+# Create an empty list to store results
+results <- list()
+countries<- levels(as.factor(dfreg$country2))
+
+# Iterate over each country
+for (i in countries){
+  # Exclude the i-th country
+  subset_data <-dfreg %>% dplyr::filter(country2 != i)
+  # Refit the model without the i-th country
+  model_i <- lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         dclass3res_V+
+         female_gc+agenum_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=subset_data,weights = WEIGHT)
+
+  # Store the results
+  results[[i]] <- model_i
+  }
+
+knitreg(results[1:10])
+knitreg(results[11:20])
+knitreg(results[21:31])
+
+tidyresults <- list()
+for (i in countries) {
+  tidyresults[[i]] <- broom::tidy(results[[i]],conf.int=T)
+}
+
+jk<- bind_rows(tidyresults, .id = "country");jk$country <-paste("Excluding",jk$country)
+
 ```

### 2024-07-19 paper1_jiturra.Rmd
up humboldt

@@
 
- During the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
-In contrast, less attention has been paid to the role of social networks on redistributive preferences.
-Sociologists have demonstrated that individuals tend to form segregated social networks according to social class [@mcpherson_birds_2001;@otero_lives_2022].
-Additionally, attitudes toward economic inequality can be affected by class segregation, as it implies distance from other social classes'  economic conditions, lifestyles, and worldviews [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-Therefore, focusing on social ties can improve the understanding of the relationship between social class and redistributive preferences, as it broadens the scrutiny of class relations in terms of internalization of shared norms, class identity formation, and collective solidarity.
-[@Svallfors2006;@goldthorpe_service_1982].
-In this discussion, the first part of this study examines the micro-level relationship between class-based network segregation and redistributive preferences.
-Subsequently, I focus on how cross-national differences in income inequality can moderate the relation of network segregation and support for redistribution.
+During the past decades, cross-national studies on social class and redistributive preferences have predominantly focused on individuals and households [@lindh_class_2020].
+In contrast, less attention has been paid to how the structure of social relations can contribute to explaining class differences in redistributive preferences.
+In this regard, sociologists have pointed out that a structural feature of contemporary societies is the tendency of social classes to form segregated social networks [@mcpherson_birds_2001;@otero_lives_2022].
+Furthermore, recent studies have argued that class segregation can indeed affect redistributive preferences, as it implies lower social integration and detachment from the economic conditions, lifestyles and worldviews of other social classes [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
+Consequently, focusing on the structure of social networks can contribute to a better understanding of the link between class relations and redistributive preferences.
+Concerning this, networks broaden the scope of class analysis through class-specific relational aspects, such as shared norms internalization, identity formation, and collective solidarity [@Svallfors2006;@goldthorpe_service_1982].
+Adding to this debate, this research starts by examining the micro-level relationship between segregated class-based networks and redistributive preferences.
+Then, I scrutinize how cross-national differences in income inequality may moderate the relationship between network segregation and redistributive preferences.
 
@@
 
-As network segregation can widen the class divide in redistributive preferences, little is known about how income inequality may affect the association between class-based network segregation and support for redistribution.
+Since the degree of segregation may amplify already stratified class differences in redistributive preferences, little is known about how income inequality may moderate this relationship.
 On the one hand, studies on the class-attitude link suggest that income inequality is crucial for understanding how class relations are reflected in redistributive demands, as it represents the current state of distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-A consistent finding in this literature is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
-On the other hand, income inequality has implications for social participation and network composition.
-Indeed, inequality reinforces stratified access to social activities and widens the distance between classes, resulting in a higher diversity of networks and activities in the upper classes and more marginalization of the lower classes [@lancee_income_2012;@otero_differences_2023;@pichler_patterns_2007].
-However, current efforts to examine the impact of income inequality have focused primarily on social networks or support for redistribution.
-Thus, a key question that remains unanswered is the extent to which higher income inequality moderates the relationship between social class-based network segregation and redistributive preferences.
+A consistent finding in this literature is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, while the already high redistributive demands of the working class remain relatively stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
+On the other hand, it is well documented that income inequality has consequences on social relations.
+Indeed, it can reinforce stratified access to social activities and widen the distance between classes, which means that the upper classes participate more and hold more diverse networks, while the lower classes tend to be more inactive and segregated as inequality rises [@lancee_income_2012;@otero_differences_2023;@pichler_patterns_2007].
+However, current efforts to examine the impact of income inequality have focused on either social networks or support for redistribution.
+Thus, a key question that remains unanswered is the extent to which income inequality moderates the relationship between social class-based network segregation and redistributive preferences.
 
@@
 
-Over the past decades, the study of political attitudes in industrialized societies has consistently demonstrated the relevance of social class as a driver of public opinion [@lindh_class_2020, p.
-421].
+Over the past decades, the study of political attitudes in industrialized societies has consistently demonstrated the relevance of social class as a driver of public opinion [@lindh_class_2020].
 In this view, social class not only represents individuals' labor market relations but also their economic interests and moral perspectives on the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
@@
 Additionally, while material interests may dominate in situations of scarcity, value-driven motivations become a significant explanatory factor for redistributive preferences under conditions of greater certainty and are weaker under material precariousness [@Kulin2013;@Maldonadoetal2019].
-Other approaches suggest that the substantial time workers spend on their jobs allows social relations in the workplace to imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
+
+Other approaches have emphasized that social relations in the workplace can imprint normative views that ultimately shape political opinions due to the substantial time workers spend on their jobs [@oesch_redrawing_2006].
 For example, the continuous and diverse social interactions inherent in interpersonal services can foster empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
@@
 Empirically, the current understanding of class divides in redistributive preferences is extensive [@lindh_public_2015;@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-Nevertheless, considering class-based network ties highlights the relevance of the class situation, as it encompasses economic interests and life chances that drive communal action beyond individuals [@weber_class_2011, pp.
+Nevertheless, I suggest that focusing on network ties stresses the relevance of the _class situation_ of individuals and social surroundings, as it encompasses economic interests and life chances that drive communal action  [@weber_class_2011, pp.
 57-59].
-Hence, considering the structure of social ties allows one to look more comprehensively into how class relations structure redistributive preferences.
+Hence, studying connections between classes from a network perspective allows one to examine how class relations structure redistributive preferences comprehensively.
 
@@
 Class relations can be understood as the structure of social ties between different classes within the social structure, represented by networks formed by various social classes [@blau_macrosociological_1977].
-Empirical evidence consistently shows homophily in social relations within the social network literature [@mcpherson_birds_2001].
-This indicates that friendships and family ties are often homogeneous regarding social status and demographic characteristics, whereas distant ties connect individuals to different social groups and enhance network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
-Moreover, socialization preferences do play a role in the formation of segregated networks [@visser_attitudes_2004; @homans_human_1951].
-However, the similarity of attitudes within these networks arises more from the social differentiation structuring class ties than from individual preferences [@feld_focused_1981].
+Empirical evidence in the social network literature consistently demonstrates that homophily is a socially structured tendency in social relations [@mcpherson_birds_2001].
+For instance, this implies that friendships and family ties are often homogeneous concerning social status or demographic characteristics, whereas distant ties link individuals to different social groups and raise network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
+At the same time, it is well established that socialization preferences play a role in forming segregated networks [@visser_attitudes_2004; @homans_human_1951].
+However, it has been argued that attitude similarity within these networks arises more due to the contact opportunities that structure the class composition of networks than individual sociability preferences [@feld_focused_1981].
 
@@
 Similarly, @otero_open_2021 found that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class.
-This suggests that limited life chances and lower capacity for social engagement ultimately result in segregation.
+This suggests that limited life chances and a lower capacity for social engagement ultimately result in segregation.
 Conversely, the upper class is more homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].

### 2024-09-26 paper1_jiturra.Rmd
update

--- 2024-07-18 paper1_jiturra.Rmd
@@
 abstract: | 
-  | Rising economic inequality has increased attention to the link between class relations and redistributive preferences in contemporary societies.
-However, economic inequality unevenly affects class relations and their influence on support for redistribution across societies.
-While those in the upper and middle classes reinforce their privileged access to resources and diverse networks, the working class has been disproportionately affected by social exclusion as inequality rises.
-Consequently, inequality consolidates segregated lifeworlds as it increases the divide between the lives and experiences of the different social classes.
-Meeting people from diverse class positions can help individuals become more aware of other people's lifestyles and worldviews.
-Homogeneous upper-class networks may reduce empathy and solidarity towards those in need, resulting in decreased support for redistribution.
-Conversely, segregated lower-class social networks can increase marginalization and reinforce redistribution support.
-This study explores the relationship between class-based network segregation and redistributive preferences, employing cross-national data from 31,694 individuals in 31 societies.
-The main findings suggest that social class conditions the association of network homogeneity on redistributive preferences, where working-class homogeneity drives stronger redistributive preferences, while greater upper-class homogeneity decreases support for redistribution.
-In addition, the conditional influence of network segregation weakens in unequal societies, especially for the upper classes.
-Implications for the study of class relations and political attitudes are discussed.
+  | Rising economic inequality has increased attention on the link between class-based networks and redistributive preferences in contemporary societies.
+Previous research has shown that class differences in redistributive preferences tend to narrow in more unequal societies, primarily due to higher redistributive preferences within the service class.
+However, little is known about how economic inequality affects the relationship between class-based networks and redistributive preferences.
+Moreover, income inequality can reinforce the role of social class in shaping social networks, highlighting how the lower class becomes increasingly segregated from other classes.
+Experiencing homogeneous class-based networks leads to segregated lifeworlds, which widen the gap between social classes and reduce awareness of the living conditions and worldviews of others.
+Empirically, I expect that homogeneous upper-class networks may reduce empathy and solidarity toward those in need, resulting in lower support for redistribution.
+Conversely, homogeneous working-class networks increase marginalization and strengthen the demand for redistribution.
+At the country level, I anticipate that in more unequal societies, the relationship between class-based network segregation and redistributive preferences weakens, due to the narrower differences between the upper and lower classes.
+This study examines the relationship between class-based network segregation and redistributive preferences and how it is moderated by economic inequality, utilizing cross-national data from 31,694 individuals across 31 societies.
+In line with these expectations, the findings suggest that social class shapes the association between network homogeneity and redistributive preferences: working-class homogeneity drives stronger redistributive preferences, while greater upper-class homogeneity reduces support for redistribution.
+Additionally, the conditional relationship between network segregation and social class weakens as inequality increases, particularly in the service class.
+The implications for studying class-based networks and political attitudes are also discussed.
   | 
@@
 
- During the past decades, cross-national studies on redistributive preferences and social class have predominantly focused on individuals and households [@lindh_class_2020].
-In contrast, less attention has been paid to the role of social networks on redistributive preferences.
-Sociologists have demonstrated that individuals tend to form segregated social networks according to social class [@mcpherson_birds_2001;@otero_lives_2022].
-Additionally, attitudes toward economic inequality can be affected by class segregation, as it implies distance from other social classes'  economic conditions, lifestyles, and worldviews [@lindh_missing_2021;@lee_consider_2023;@paskov_crossclass_2022].
-Therefore, focusing on social ties can improve the understanding of the relationship between social class and redistributive preferences, as it broadens the scrutiny of class relations in terms of internalization of shared norms, class identity formation, and collective solidarity.
-[@Svallfors2006;@goldthorpe_service_1982].
-In this discussion, the first part of this study examines the micro-level relationship between class-based network segregation and redistributive preferences.
-Subsequently, I focus on how cross-national differences in income inequality can moderate the relation of network segregation and support for redistribution.
-
-While previous research has predominantly examined the impact of social class through an individualist lens, more attention has recently been paid to the role of social ties in class relations.
-This omission is especially surprising since social classes are rooted in social relations of production, which makes them inherently relational in their economic foundations and the power dynamics involved in distributive struggles [@wright_comparative_1989].
-Moreover, the normative basis of class relations introduces the relevance of dimensions of solidarity and reciprocity, which are argued to provide the moral foundation for legitimacy and popular support for welfare schemes [@mau_moral_2003].
-Thus, beyond the influence of individual class positions, recent efforts have highlighted that, while the class positions of network ties affect redistributive preferences, segregation in homogeneous class-based social settings can make attitudes even more pronounced [@otero_lives_2022].
-
-As network segregation can widen the class divide in redistributive preferences, little is known about how income inequality may affect the association between class-based network segregation and support for redistribution.
-On the one hand, studies on the class-attitude link suggest that income inequality is crucial for understanding how class relations are reflected in redistributive demands, as it represents the current state of distributive class struggle in contemporary capitalist societies [@edlund_democratic_2015;@curtis_how_2015].
-A consistent finding in this literature is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, while the already high redistributive demands of the working class remain stable regardless of inequality levels [@sachweh_why_2019;@dimick_altruistic_2017].
-On the other hand, income inequality has implications for social participation and network composition.
-Indeed, inequality reinforces stratified access to social activities and widens the distance between classes, resulting in a higher diversity of networks and activities in the upper classes and more marginalization of the lower classes [@lancee_income_2012;@otero_differences_2023;@pichler_patterns_2007].
-However, current efforts to examine the impact of income inequality have focused primarily on social networks or support for redistribution.
-Thus, a key question that remains unanswered is the extent to which higher income inequality moderates the relationship between social class-based network segregation and redistributive preferences.
-
-To the best of my knowledge, no research has comparatively studied the role of economic inequality in the relationship between class-based network segregation and redistributive preferences.
-Therefore, this study aims to answer two key questions:
-
-(1) How does class-based network segregation affect redistributive preferences?
+Over the past few decades, cross-national studies on social class and redistributive preferences have predominantly centered on individual class positions [@lindh_class_2020].
+Recently, however, a growing body of research has begun to focus on how the class profile of social networks influences redistributive preferences [@lindh_missing_2021; @lee_consider_2023; @paskov_crossclass_2022].
+Although prior studies have shown that class-based network segregation—defined as the concentration of similar-class network ties—can undermine attachment to society [@otero_lives_2022], there is still limited understanding of how being embedded in a homogeneously class-based network impacts attitudes toward inequality and redistribution [@otero_power_2023].
+Contributing to this debate, this research first aims to investigate the individual-level relationship between class-based network segregation and redistributive preferences.
+In addition, it has been suggested that social classes tend to form segregated networks according to the homophily principle, understood as the higher chances of forming social ties with others with similar characteristics [@mcpherson_birds_2001;@otero_lives_2022].
+Furthermore, cross-national comparisons indicate that class-based network stratification strengthens in societies with high economic inequality, which in turn drives stronger social distance between classes, particularly among the lower classes [@otero_differences_2023; @pichler_social_2009].
+Against this backdrop, the present study seeks to contribute to understanding how cross-national differences in income inequality act as a moderating factor in the relationship between class-based network segregation and redistributive preferences.
+
+While segregation may deepen existing class divisions in redistributive preferences [@paskov_crossclass_2022], little is known about how income inequality shapes this relationship.
+On the one hand, research on the class-attitude link suggests that income inequality is crucial for understanding how class relations—i.e., the social and political distance between classes—translate into redistributive demands, as it reflects the state of class struggle in contemporary capitalist societies [@edlund_democratic_2015; @curtis_how_2015].
+A consistent finding is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, whereas the already high redistributive demands of the lower classes remain relatively stable, regardless of inequality levels [@sachweh_why_2019; @dimick_altruistic_2017].
+On the other hand, it is well-documented that income inequality affects social relations, reinforcing stratified access to social activities and widening the distance between classes.
+In such conditions, the upper classes tend to be more socially active and maintain more diverse networks, while the lower classes become increasingly inactive and segregated as inequality rises [@lancee_income_2012; @otero_differences_2023; @pichler_social_2009].
+However, current research efforts have primarily examined the impact of income inequality moderates the relations of social class on either social networks or redistributive preferences.
+Thus, this study aims to address two key questions:
+
+(1) How does class-based network segregation influence redistributive preferences?
 (2) To what extent does economic inequality moderate the relationship between class-based network segregation and redistributive preferences?
 
-In this study, I used a sample of 31,694 individuals from 31 countries from the International Social Survey Program (ISSP) 2017.
-This dataset provides unprecedented cross-national comparative data on social networks, social class, and attitudes toward redistribution.
+In this research, I use a sample of 31,694 individuals from 31 countries, drawn from the 2017 International Social Survey Program (ISSP).
+This dataset offers unprecedented cross-national comparative data on social networks, social class, and attitudes toward redistribution.
 
@@
 
-Over the past decades, the study of political attitudes in industrialized societies has consistently demonstrated the relevance of social class as a driver of public opinion [@lindh_class_2020, p.
-421].
-In this view, social class not only represents individuals' labor market relations but also their economic interests and moral perspectives on the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
-Here, redistributive preferences are understood as the support for policies and mechanisms aimed at reducing economic inequality through the redistribution of wealth and resources [@mccall_americans_2009].
-These preferences encompass views on taxation, welfare programs, public services, and other government interventions designed to transfer resources from wealthier to less wealthy individuals or groups in society [@garcia-sanchez_two_2022].
-
-Class-based explanations of redistributive preferences have primarily focused on the individual or household level but are not exclusively limited to these contexts.
-It has been argued that redistributive preferences can be explained through labor market situations, which encompass access to economic resources and risk exposure [@meltzer_rational_1981;@rehm_risks_2009].
-Additionally, while material interests may dominate in situations of scarcity, value-driven motivations become a significant explanatory factor for redistributive preferences under conditions of greater certainty and are weaker under material precariousness [@Kulin2013;@Maldonadoetal2019].
-Other approaches suggest that the substantial time workers spend on their jobs allows social relations in the workplace to imprint normative views that ultimately shape political opinions [@oesch_redrawing_2006].
-For example, the continuous and diverse social interactions inherent in interpersonal services can foster empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
-In contrast, vertical monitoring in managerial occupations and the emphasis on autonomy in self-employed roles tend to strengthen self-interested and conservative political views [@oesch_electoral_2018].
-
-Empirically, the current understanding of class divides in redistributive preferences is extensive [@lindh_public_2015;@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010].
-Nevertheless, considering class-based network ties highlights the relevance of the class situation, as it encompasses economic interests and life chances that drive communal action beyond individuals [@weber_class_2011, pp.
+Over the past few decades, research on political attitudes in industrialized societies has consistently highlighted the significance of social class as a key driver of public opinion [@lindh_class_2020].
+Social class, in this context, not only reflects individuals' labor market relations but also their economic interests and moral perspectives regarding the role of the market and the state in the distribution and redistribution of resources [@Svallfors2006].
+Redistributive preferences refer to the support for policies and mechanisms aimed at reducing economic inequality by redistributing wealth and resources [@mccall_americans_2009].
+These preferences encompass views on taxation, welfare programs, public services, and other government interventions designed to transfer resources from wealthier individuals or groups to those with fewer resources [@garcia-sanchez_two_2022].
+
+Empirically, the class divide in redistributive preferences is well documented [@lindh_public_2015; @curtis_how_2015; @langsaether_more_2020; @brooks_why_2010].
+Class-based explanations of redistributive preferences have predominantly focused on individuals.
+According to self-interest-driven theories, economic resources or exposure to risk explain why working classes with fewer resources and greater job insecurity tend to support redistribution more than the upper classes [@meltzer_rational_1981; @rehm_risks_2009].
+Furthermore, while material interests often dominate in conditions of scarcity, value-based motivations, such as egalitarianism, may drive stronger support for redistribution under conditions of greater security and weaken under material hardship [@Kulin2013; @Maldonadoetal2019].
+
+Other approaches emphasize the role of social relations in the workplace, which can imprint normative views that ultimately shape political opinions due to the significant time people spend at work [@oesch_redrawing_2006].
+For instance, continuous and diverse social interactions in interpersonal service roles can foster empathy and reinforce egalitarian values [@kitschelt_occupations_2014].
+Conversely, vertical oversight in managerial positions and the emphasis on autonomy in self-employed roles often bolster self-interested and conservative political views [@oesch_electoral_2018].
+
+Given this context, studying the connections between social classes from a network perspective offers a comprehensive way to understand redistributive preferences beyond the individual level.
+By focusing on network ties, the collective dimension of class relations is brought to the forefront, emphasizing that social ties encompass both social and economic resources [@lin_access_1986], which serve as the foundation for communal action [@weber_class_2011, pp.
 57-59].
-Hence, considering the structure of social ties allows one to look more comprehensively into how class relations structure redistributive preferences.
 
@@
 
-Class relations can be understood as the structure of social ties between different classes within the social structure, represented by networks formed by various social classes [@blau_macrosociological_1977].
-Empirical evidence consistently shows homophily in social relations within the social network literature [@mcpherson_birds_2001].
-This indicates that friendships and family ties are often homogeneous regarding social status and demographic characteristics, whereas distant ties connect individuals to different social groups and enhance network diversity [@diprete_segregation_2011;@lazarsfeld_friendship_1954].
-Moreover, socialization preferences do play a role in the formation of segregated networks [@visser_attitudes_2004; @homans_human_1951].
-However, the similarity of attitudes within these networks arises more from the social differentiation structuring class ties than from individual preferences [@feld_focused_1981].
-
-The study of class relations from a network perspective can be approached in two ways.
-First, network diversity is defined as the degree of connectedness to dissimilar occupations, representing vertical access to resource diversity within social networks [@lin_access_1986].
-In this context, diversity refers to the variability of different ties within the network without necessarily providing a reference point to describe network similarity.
-Second, network segregation, defined as the absence of cross-class connections, indicates how similar network ties are in reference to the individual.
-This perspective is conceptually closer to homophily, as it is anchored in individual class positions and has been empirically addressed through network homogeneity [@otero_open_2021].
-
-How does social class stratify social networks?
-Empirical studies on network diversity reveal that higher civic engagement in formal organizations increases the likelihood of the upper class forming connections with diverse individuals, contrasting with the more homogeneous participation observed among the working class [@pichler_social_2009].
-Similar patterns are found in the composition of social ties, where the upper and intermediate classes maintain more diverse and prestigious social environments compared to the working class [@cepic_how_2020; @carrascosa_class_2023].
-In contrast, studies on network segregation suggest that property-based boundaries are less permeable than authority-based ones.
-For example, @wright_relative_1992 suggest that class interests widen the social distance between proprietors and manual workers, while the intermediate position of supervisors and their higher contact frequency with manual workers make the formation of friendship ties more likely.
-Similarly, @otero_open_2021 found that the intermediate class exhibits greater permeability compared to the more homogeneous networks of the working class.
-This suggests that limited life chances and lower capacity for social engagement ultimately result in segregation.
-Conversely, the upper class is more homogeneous because it tends to self-select, a practice that ultimately seeks to reproduce its privileged positions [@otero_open_2021].
-
-## Network segregation and attitudes toward redistribution
-
-Besides individualistic class-based mechanisms in redistributive preferences, the argument that network ties have implications for attitude formation is not novel.
-In particular, two approaches have discussed the role of social relations on redistributive preferences: reference groups and class-based networks.
+Theoretically, class relations can be understood as the structure of social ties between different classes within the broader social system, represented by networks spanning various social strata [@blau_macrosociological_1977].
+Research in social network literature consistently demonstrates that homophily—the tendency for individuals to associate with others who are similar—is a structured and persistent feature of social relations [@mcpherson_birds_2001].
+For instance, friendships and family ties often display homogeneity in terms of social status or demographic characteristics, while more distant ties tend to connect individuals to different social groups, thereby contributing to network diversity [@diprete_segregation_2011; @lazarsfeld_friendship_1954].
+Moreover, it is well established that socialization preferences play a role in forming segregated networks [@visser_attitudes_2004; @homans_human_1951].
+However, this research aligns with the prevailing view that attitudinal similarity within networks arises primarily from structural contact opportunities shaped by the class composition of social ties, rather than from homophilic preferences for socializing with like-minded individuals [@feld_focused_1981].
+
+To investigate the implications of networks for redistributive preferences, I propose distinguishing between two closely related—but distinct—perspectives on how class-based networks manifest within social structures.
+
+First, the concept of _network diversity_ refers to the degree of connectedness to dissimilar ties (e.g., different occupations or activities), representing vertical access to diverse resources within social networks [@lin_access_1986].
+In this context, diversity reflects the dispersion of different ties (alteri) across the network, independent of the individual’s (ego) characteristics [@otero_power_2023].
+Empirical studies, such as those by @pichler_social_2009 and @lancee_income_2012, argue that higher civic engagement in formal organizations increases the likelihood of the upper classes forming connections with more diverse individuals, whereas the working classes tend to engage in more homogeneous participation.
+Similar patterns emerge in social tie composition, where the upper and intermediate classes maintain more diverse and prestigious social environments than the working class [@cepic_how_2020; @carrascosa_class_2023].
+
+The second and primary perspective adopted in this study is _network segregation,_ defined as having contact primarily with people of the same class.
+This approach measures the similarity between an individual’s (ego) network ties and is conceptually closer to homophily, as it is rooted in an individual’s class position and has been empirically examined through network homogeneity [@otero_open_2021].
+Evidence suggests that property-based boundaries are far less permeable than authority-based ones in the formation of cross-class ties.
+For example, @wright_relative_1992 suggests that class interests tend to widen the social distance between proprietors and manual workers, while the intermediate position of supervisors and their more frequent contact with manual workers make cross-class friendships more likely.
+Similarly, @otero_open_2021 identified a U-shaped pattern of acquaintance network segregation in Chile, where the middle classes (e.g., lower managerial professionals, clerks, and manual supervisors) exhibit lower network homogeneity.
+Likewise, segregation is most prevalent on both ends of the class structure, particularly among the lower classes.
+They argue that segregation in the lower classes is often driven by limited life chances and reduced social participation, while upper-class segregation is largely explained by self-selection—a practice that reinforces privileged positions, which can coexist with a broader range of social connections [@otero_open_2021].
+
+Given this context, one theoretical implication is that experiencing segregated class-based networks may be related to class differences in redistributive preferences.
+However, whether such segregation—empirically understood as network homogeneity—intensifies or mitigates class differences in these preferences remains a question to be empirically addressed.
+
+## Network segregation and redistributive preferences
+
+In addition to rational self-interest or value-based explanations, the argument that social ties have implications for attitude formation is not precisely new.
+More specifically, two approaches have discussed the role of social relations in redistributive preferences: reference groups and class-based networks.
 
@@
 
-The second approach suggests that social networks provide a comprehensive picture of the class relations that contribute to group identity formation and internalization of social norms [@kalmijn_social_2007].
+This research adopts the second approach, which suggests that social networks provide a comprehensive picture of the class relations that contribute to group identity formation and internalization of social norms [@kalmijn_social_2007].
 Specifically, it has been argued that redistributive preferences are influenced not only by individuals' social class but also by the class positions of their network ties [@paskov_crossclass_2022].
-Thus, social influence processes can either align or divide opinions depending on the class positions of contacts and the level of network segregation [@lindh_missing_2021].
+Thus, opinions can either align or divide through social influence processes depending on the class positions of contacts and the level of network segregation [@lindh_missing_2021].
 These arguments reflect the notion that classes are characterized as collectivities with varying degrees of cohesion and solidarity, comprising asymmetric status-based interactions related to material resources, cultural practices, and political preferences [@morris_attenuation_1996].
@@
 
-In summary, as homogeneity refers to the overall degree of segregation without distinguishing between class positions I anticipate a weak direct association between network homogeneity and redistributive preferences.
+In summary, I anticipate a weak direct association between network segregation and redistributive preferences.
+This is mainly because network homogeneity - as the proportion of similar class network ties - does not distinguish between anchor class positions and refers to the overall degree of segregation.
 Conversely, I hypothesize that the association of network homogeneity with redistributive preferences is conditional on social class as homogeneous social networks should reinforce attitude similarity (*segregation hypothesis*).
@@
 
-> H1: _The greater the network segregation in the lower (upper) classes, the higher (lower) the redistributive preferences. _
-
-## Economic inequality as context for class relations and redistributive preferences
-
-Studies on economic inequality, social class, and redistributive preferences indicate that social classes react differently to rising economic inequality.
-Theoretically, political economists have suggested that high-income individuals are far from monolithic in their redistributive preferences, arguing that their concerns about the harmful _consequences_ of economic inequality (e.g., crime) ultimately motivate altruistic support for redistribution [@dimick_models_2018;@dimick_altruistic_2017;@rueda_externalities_2016].
-Conversely, the moral economy literature in sociology has argued that the differences among the affluent can be explained as a matter of distributive justice evaluations about the _procedures_ for resource allocation [@liebig_sociology_2016].
-
-Empirically, it has been shown that affluent groups are more responsive as they perceive the overall opportunity structure and social mobility chances are affected by rising inequality [@sachweh_why_2019].
-Likewise, higher perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of justice in the conditions for getting ahead [@kim_socioeconomic_2018].
-In contrast, low-income individuals perceive ascribed characteristics as more important in constraining the opportunity structure, regardless of current income inequality [@sachweh_why_2019].
-In a similar perspective, @edlund_democratic_2015 argue that in unequal societies with residual welfare states, social class has a poor political meaning, making distributive conflicts weakly institutionalized around traditional working-class organizations (e.g., unions).
-Thus, stronger support for state-organized redistribution among the upper classes can also be explained as they are often more aware of the incentives and societal consequences of income inequality [@curtis_how_2015;@Svallfors2006].
-
-How does income inequality affect social networks?
-As income inequality implies stronger barriers to establishing trustworthy social connections, this also has consequences on the structure of class relations.
+> H1: _The greater the network segregation in the lower (upper) classes, the higher (lower) the redistributive preferences._
+
+## Economic inequality as context for class-based segregation and redistributive preferences
+
+The literature on the role of economic inequality on (1) the class-attitude link and (2) social relations have been independently developed.
+
+Theoretically, studies on economic inequality, social class, and redistributive preferences show varying class reactions to rising inequality.
+Political economists suggest that high-income individuals are far from being monolithic in their redistributive preferences, motivated by concerns about inequality's adverse effects (e.g., crime), leading to altruistic support for redistribution [@dimick_models_2018; @dimick_altruistic_2017; @rueda_externalities_2016].
+Conversely, the moral economy literature in sociology explains affluent differences through evaluations of distributive justice regarding resource allocation procedures [@liebig_sociology_2016].
+At the same time, the literature on the role of income inequality on social cohesion has argued that unequal societies strengthen barriers to trustworthy social connections.
 Neckerman and Torche [-@neckerman_inequality_2007, p.
-344] suggest that experiencing marginalization is deeply associated with diminished chances for participating openly in social life, which can be exacerbated in contexts of greater inequality.
-Also, societies with higher income inequality can erode social relations as they exhibit reduced social trust that operates as the basis for mutual understanding and feelings of solidarity [@kragten_income_2017].
-Likewise, in contexts of lower income inequality and encompassing welfare states, higher levels of civic and social participation increase generalized trust and reduce social conflict [@uslaner_inequality_2005].
-In a similar vein, @yamamura_social_2012 showed that redistributive preferences rise as community-level participation in social activities increases.
-Moreover, high-income citizens in these communities are specifically more likely to support collective solidarity through government redistribution.
-
-Empirically, cross-national studies show that already-stratified access to social activities and diverse networks is further reinforced in unequal societies.
-For instance, @letki_getting_2015 show that extensive networks in unequal societies are more common among low-income individuals who rely more on close ties for social support than high-income individuals.
-Additionally, @pichler_social_2009 demonstrated that class differences in participation in civic and family networks are exacerbated in more unequal societies.
-Likewise, @lancee_income_2012 found that income-based stratification in civic participation becomes more pronounced as inequality increases.
-Also, @otero_differences_2023 found that economic inequality enhances stratified access to network diversity, suggesting that it amplifies the interdependence among cultural, economic, and social capital.
-Thus, the upper classes can navigate diverse social settings while preserving their distinctive position, whereas the lower classes often remain marginalized and segregated due to the choices of others [@otero_open_2021, p.24].
-
-To summarize, I expect that income inequality weakens the interaction between network homogeneity and social class.
-Specifically, I hypothesize that the conditional relationship between network homogeneity and social class (*segregation hypothesis*) will be less pronounced in contexts of higher income inequality (*mitigation hypothesis*).
-Given the above considerations, the second hypothesis reads as follows:
-
-> H2: _The greater the income inequality, the weaker the conditional association of network segregation by social class on redistributive preferences._
-
-<!-- A simplified framework of the hypotheses is shown in Figure X. -->
+344] noted that marginalization is linked to reduced participation in social life, exacerbated by greater inequality.
+Also, rising economic inequality erodes social relations by reducing social trust, which underpins mutual understanding and collective solidarity [@kragten_income_2017].
+Conversely, it is noted that societies with low inequality and comprehensive welfare states enhance civic and social participation, increasing generalized trust and reducing social conflict [@uslaner_inequality_2005].
+Similarly, it has been argued that social participation can nurture higher chances for cross-class interactions and motivate more egalitarian attitudes, being upper-class citizens who support stronger collective solidarity through government redistribution in more cohesive communities [@yamamura_social_2012].
+
+Empirically, it has been shown that affluent groups are more responsive, perceiving that rising inequality affects the overall opportunity structure and social mobility chances [@sachweh_why_2019].
+Also, higher perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of procedural justice [@kim_socioeconomic_2018].
+In contrast, low-income individuals view ascribed characteristics as more crucial in constraining opportunities, irrespective of current income inequality [@sachweh_why_2019].
+Similarly, @edlund_democratic_2015 argue that in unequal societies with residual welfare states, social class lacks significant political meaning, weakening distributive conflicts around traditional working-class organizations (e.g., unions).
+Thus, stronger support for state-organized redistribution among the upper classes can be attributed to their greater awareness of the incentives and societal consequences of income inequality [@curtis_how_2015; @Svallfors2006].
+At the same time, cross-national comparative evidence indicates that stratified access to social activities and networks is reinforced in unequal societies.
+For example, @pichler_social_2009 demonstrated that class differences in civic and family network participation are exacerbated in unequal societies.
+Similarly, @lancee_income_2012 found that income-based stratification in civic participation increases with inequality.
+Also, @otero_differences_2023 found that economic inequality enhances
+interdependence among cultural, economic, and social capital, which results in stronger stratified chances for cross-class interactions.
+Thus, in unequal societies, the upper classes can navigate diverse social settings while maintaining their distinct positions, whereas the lower classes remain marginalized and segregated due to others' choices [@otero_open_2021, p.24].
+
+Against this backdrop, there are at least three emerging theoretical implications on the role of income inequality on class-based networks and redistributive preferences.
+The first implication is that it is plausible to assume that income inequality drives greater segregation, as the result of lower participation and social trust.
+However,  it is worth noticing that resource interdependency seems to exacerbate social exclusion for the lower classes, while the upper classes may hold more cohesive experiences that drive stable or even lower segregation in more unequal societies.
+A second implication is that the relationship between class and attitudes weakens in highly unequal societies, where the upper classes tend to show more support for redistribution, contrasting with the relatively stable preferences of the lower classes.
+In addition, it is also true that in egalitarian societies with more encompassing welfare states class-based distributive struggles tend to be more institutionalized (e.g.
+through unions or political parties).
+As a result, class positions are more closely implied in political conflict as the institutional framework allows them to better articulate their interests.
+A third implication is that as inequality increases and the class divide in redistributive preferences narrows, this may also be extended to the influence of class-based segregation on redistributive preferences.
+As the class-attitude link becomes mild in more unequal contexts, it is also expected that homogeneous class-based networks might not have the same strength where the role of class positions loses significance.
+Therefore, I expect income inequality to weaken the interaction between network homogeneity and social class.
+Specifically, I hypothesize that the conditional relationship between network homogeneity and social class stated at the individual level (*segregation hypothesis*) will be less pronounced in the context of higher income inequality (*mitigation hypothesis*).
+Given these considerations, the second hypothesis is as follows:
+
+> H2: _The greater the income inequality, the weaker the conditional association of network segregation by social class with redistributive preferences._
+
+A simplified framework of the hypotheses is shown in Figure \@ref(fig:scheme).
+
+```{r scheme, echo=FALSE, out.width='80%',fig.cap='Hypotheses at country and respondent levels'}
+knitr::include_graphics('output/images/paper1-scheme.png')
+```
 
@@
 I use two indicators to measure redistributive preferences.
-The first indicator corresponds to support for government redistribution and it is measured by the item: "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes." The second indicator is egalitarian preferences and it is measured by the item: "For a society to be fair, differences in people's standard of living should be small." Both indicators use a five-point Likert scale with the following categories: 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree'(3), 'Disagree' (4), and 'Strongly disagree'(5).
+The first indicator corresponds to support for government redistribution and it is measured by the item: "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes." The second indicator is egalitarian preferences and it is measured by the item: "For a society to be fair, differences in people's standard of living should be small." Both indicators use a five-point Likert scale with the following categories: 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree'(3), 'Disagree' (4), and 'Strongly disagree'(5) (*r* = 0.62).
 Following @svallfors_government_2013, I reverse-coded, averaged and normalized the indicators in a 0 to 100 index, where higher values reflect stronger redistributive preferences.
@@
 Following previous research, a simplified version of the EGP class scheme that collapses three classes is employed [@sosnaud_class_2013;@edlund_influence_2003].
-Specifically, this version distinguishes among the Service Class (higher and lower managerial and professionals), Intermediate Class (routine nonmanual workers and self-employed), and Working Class (manual supervisors, skilled and unskilled manual workers) (see Table \@ref(tab:tab-an-classag) in the Appendix).
+Specifically, this version distinguishes among the Service Class (higher and lower managerial and professionals), Intermediate Class (routine nonmanual workers and self-employed), and Working Class (manual supervisors, skilled and unskilled manual workers) [^egpclass] (see Table \@ref(tab:tab-an-classag) in the Appendix).
+
+[^egpclass]: Self-employed farmers (IVc) are grouped in the self-employed class, while agricultural labor (VIIb) is in the working class.
 
@@
 This instrument has been widely used in social capital studies and follows an ego-centered approach where is assumed that social ties to different hierarchical positions in the social structure provide access to social resources [@vandergaag_position_2008].
-Here, a list of ten occupations is displayed and declared as a "Family or relative," "Close friend", "Someone else I know," or "No one." The first three categories are binary coded as "Knows" (1) and the rest as "Does not know" (0).
-Then, the sum of all occupations known represents the total number of ties per respondent.
+The position generator employed included a list of ten occupations.
+Here, occupations are presented to the respondent in a grid that allows them to declare whether they know (or not) a person who performs that occupation.
+The tie can be clasified in four groups, defining tie to this person is as a "Family or relative," "Close friend,” "Someone else I know," or "No one.”  With this information, the first three categories are coded as 1 to represent the presence of a tie ("Knows") and 0 as the abscence of a conection to a person with that occupation ("Does not know").
+Subsequently, all declared ties were summed to represent the total number of occupations known by the respondent.
 
@@
 
-Given the above, I adopted established procedures in the literature for measuring homogeneity in ego-centered networks.
-For example, @volker_birds_2022 computes gender and educational network homogeneity by calculating the proportion of similar ties based on both respondent and network tie characteristics.
-Similarly, @otero_lives_2022 employed a comparable method by classifying occupations from the position generator into three class positions to compute the proportion of similar ties based on social class, thereby measuring class-based network homogeneity.
-In this research, I adopt the latter approach.
-
-Therefore, I calculate the number of ingroup ties according to the respondents' class position and divide it by the total number of known occupations to obtain a measure of network homogeneity.
+Given the above, I adopt established procedures in the literature for measuring homogeneity in ego-centered networks [@volker_birds_2022].
+Regarding class segregation, @otero_lives_2022 classified occupations from the position generator into three class positions to compute the proportion of similar ties based on social class, thereby measuring class-based network homogeneity.
+
+I calculate the number of ingroup ties according to the respondents' class position and divide it by the total number of known occupations.
 This measure represents the proportion of similar social ties within the personal network, where a value of zero indicates complete *heterogeneity* (i.e., all ties are different), and a value of one indicates complete *homogeneity* (i.e., all ties are similar).
@@
 Second, socioeconomic characteristics are incorporated into the models, as they represent the current social status through income, education, and labor market status [@kitschelt_occupations_2014;@hausermann_highskilled_2015].
-Third, gender, age, and marital status are included in all models as sociodemographic characteristics to control for the potential influence of life course events and gendered effects  [@waitkus_investigating_2021;@vanheuvelen_intercohort_2018].
+Third, given the gender-based class inequality in economic resources [@waitkus_investigating_2021], age differences in terms of values and socioeconomic vulnerability [@vanheuvelen_intercohort_2018], and the role of family support provided by partners [@edlund_influence_2003], gender, age, and marital status were included as control variables in all models.
 
@@
 This initial model assesses the intraclass correlation, revealing that 13.5% of the variance in redistributive preferences can be attributed to differences between countries.
-Subsequently, micro-level models are estimated to examine the association between network homogeneity and social class to test Hypothesis 1 [^altmodels].
-Following this, macro-level models are estimated by incorporating random intercepts and random slopes for network homogeneity and social class.
+Subsequently, models including the individual level factors are estimated to examine the association between network homogeneity and social class to test Hypothesis 1 [^altmodels].
+Following this, country level variables included in the estimations by incorporating random intercepts and random slopes for network homogeneity and social class.
 This model tests Hypothesis 2 by estimating a three-way cross-level interaction to determine whether income inequality moderates the interaction between network homogeneity and social class.
@@
   gdppercapita,
-  country2, country, country3,
+  country2, country, country3
 ) %>%
@@
 
-Regarding the macro-level relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, which is our main societal characteristic of interest.
+Regarding the country-level relationships, Figure \@ref(fig:fig3) depicts the correlation between network homogeneity, redistributive preferences, and income inequality, which is the main societal characteristic of interest.
 Panel A shows a medium positive association between network homogeneity and redistributive preferences (*r* = 0.45).
@@
 digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
+digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
+                    # digclas1_VW_3,
                     # digclas1_VW_4,
@@
       "Homogeneity x Social Class"=5:6),
-      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.rows = list("Controls"=c("No",rep("Yes",2))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
@@
 
-htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
-       caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
-       custom.note = "Note: Models include sampling weights. Standard errors in parentheses. %stars",
-       threeparttable = T,
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 3:4,
-      "Homogeneity x Social Class"=5:6),
-      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-      file = "output/tables/table01.doc"
-      )
+# htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
+#        caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
+#        custom.note = "Note: Models include sampling weights. Standard errors in parentheses. %stars",
+#        threeparttable = T,
+#        caption.above = T,leading.zero = T,
+#        custom.coef.map = ccoef,
+#       groups = list("Social Class (Ref.= Service Class)" = 3:4,
+#       "Homogeneity x Social Class"=5:6),
+#       custom.gof.rows = list("Controls"=c("No",rep("Yes",2))),include.loglik = FALSE,include.aic = FALSE,
+#       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+#       file = "output/tables/table01.doc"
+#       )
 # performance::check_collinearity(digclas1_VW_5)
@@
 On the one hand, I expected that network homogeneity has a weak direct association with redistributive preferences as it reveals only the overall segregation without distinction between classes.
-In this matter, Model 1 integrates network homogeneity and as it is previously noted in the macro associations, more homogeneous networks tend to exhibit higher redistributive preferences.
+In this matter, Model 1 integrates network homogeneity and as it is previously noted in the country-level associations, more homogeneous networks tend to exhibit higher redistributive preferences.
 Then, the association is robust to network size, sociodemographic characteristics, and socioeconomic status in Model 2.
@@
 
-```{r tab2, results='asis', cache=TRUE}
+```{r table2, results='asis', cache=TRUE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
   region,
-  "gini_disp"=wid_gini_disp,
+  # "gini_disp"=wid_gini_disp,
+  "gini_disp"=difclass,
   "gini_mkt",
@@
 
-htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
-       caption = paste("Multilevel models for income inequality, network homogeneity and redistributive preferences"),
-       custom.note = " Note: Models include sampling weights and individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Country (Intercept)",
-                           "Var: Country Homogeneity",
-                           "Var: Country Intermediate Class ",
-                           "Var: Country Working Class",
-                           "Cov: Country (Intercept), Homogeneity",
-                           "Cov: Country (Intercept), Intermediate Class ",
-                           "Cov: Country (Intercept), Working Class",
-                           "Cov: Country Homogeneity, Intermediate Class",
-                           "Cov: Country Homogeneity, Working Class",
-                           "Cov: Country Intermediate Class, Working Class",
-                           "Var: Residual"),
-        file = "output/tables/table02.doc")
+# htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
+#        caption = paste("Multilevel models for income inequality, network homogeneity and redistributive preferences"),
+#        custom.note = " Note: Models include sampling weights and individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
+#        caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
+#        custom.coef.map = ccoef,
+#       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
+#       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+#       custom.gof.names = c(NA,NA,"Num. groups",
+#                            "Var: Country (Intercept)",
+#                            "Var: Country Homogeneity",
+#                            "Var: Country Intermediate Class ",
+#                            "Var: Country Working Class",
+#                            "Cov: Country (Intercept), Homogeneity",
+#                            "Cov: Country (Intercept), Intermediate Class ",
+#                            "Cov: Country (Intercept), Working Class",
+#                            "Cov: Country Homogeneity, Intermediate Class",
+#                            "Cov: Country Homogeneity, Working Class",
+#                            "Cov: Country Intermediate Class, Working Class",
+#                            "Var: Residual"),
+#         file = "output/tables/table02.doc")
 ```
@@
 Finally, Model 4 incorporates a three-way interaction to determine whether the conditional association of network homogeneity to social class on redistributive preferences is moderated by income inequality.
-At the micro level, the findings for the segregation hypothesis remain robust.
+At the individual level, the findings for the segregation hypothesis remain robust.
 At the macro level, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
@@
 
-In theory, my first hypothesis was that the study of class differences in redistributive preferences should not only consider individual class positions, but the structure of social networks as sources of preference formation.
-Hence, my finding supports the claims that social influence and particularly segregation in interpersonal networks strengthen class differences in redistributive preferences [@lee_consider_2023;@lindh_missing_2021].
+Theoretically, my first hypothesis was that the study of class differences in redistributive preferences should not only consider individual class positions, but the structure of social networks as sources of preference formation.
+Hence, my finding supports the claims that social influence and particularly segregation in interpersonal networks strengthen class differences in redistributive preferences [@paskov_crossclass_2022;@lindh_missing_2021].
 Also, these results support the idea that low cross-class connections can reduce social integration and solidarity as they limit awareness about the lives of other classes [@blau_macrosociological_1977;@otero_lives_2022].
@@
 
-Besides the micro-level findings, my second hypothesis was that economic inequality mitigates the conditional association of network homogeneity by social class and redistributive preferences.
+Besides the individual-level findings, my second hypothesis was that economic inequality mitigates the conditional association of network homogeneity by social class and redistributive preferences.
 The results from the multilevel models indicate that income inequality indeed _mitigates_ this relationship.
@@
 The contribution of this study can be summarized as follows.
-First, I demonstrate that class-based network segregation can reinforce the previously documented class divide in redistributive preferences.
+First, I demonstrated that class-based network segregation can reinforce the previously documented class divide in redistributive preferences.
 Unlike previous studies focusing on cross-class contacts, the attention to network homogeneity allows us to observe how different social classes react to inequality in more segregated contexts in societies with different levels of income inequality.
@@
 However, this study has certain limitations.
-On the side of the dependent variable, a two-item index comprises a rough proxy for redistributive preferences compared to more detailed questions on tax or welfare policies.
+On the side of the dependent variable, a two-item index comprises a rough proxy for redistributive preferences compared to more detailed questions on taxes or welfare policies.
 Additionally, the position generator employed is limited in accurately representing a class scheme, particularly in the self-employment and authority dimensions.
@@
 Additionally, class-based social networks can be better assessed by incorporating other aspects of the market situation of network ties, such as self-employment status or workplace authority.
-Finally, longitudinal analyses can contribute to disentangling the relationship between class, networks, and political attitudes.
+Finally, longitudinal analyses can contribute to disentangling the temporal relationship between class, networks, and political attitudes.
 
@@
 # performance::icc(digclas1_VW_5)
+
+# sjPlot::plot_models(digclas1_VW_1,digclas1_VW_3,digclas1_VW_7,rm.terms = c("femaleFemale","agenum","partnerHas a partner",
+#                                                              "edyears","Q03pcmT02","Q03pcmT03","Q03pcmMissing",
+#                                                              "workstNot in paid work","know_total"),
+#                     m.labels = c("1. Base","2. Controls","3. Interaction"),
+#                     axis.labels = c("Hom : Work","Hom : Interm","Working Class","Intermediate Class  (ref. = Service)","Network Homogeneity"),
+#                     wrap.labels = 0) +
+#   geom_hline(yintercept = 0,color = "darkgray",size=1,linetype = 2) +
+#   scale_y_continuous(limits = c(-10,15)) +
+#   labs(color=NULL) +
+#   scale_color_manual(values = c("gray","gray","red")) +
+#   theme(legend.position = "right")
+# 
+# sjPlot::plot_models(digclas1_VW_1,digclas1_VW_3,digclas1_VW_7,rm.terms = c("femaleFemale","agenum","partnerHas a partner",
+#                                                              "edyears","Q03pcmT02","Q03pcmT03","Q03pcmMissing",
+#                                                              "workstNot in paid work","know_total"),
+#                     m.labels = c("1. Base","2. Controls","3. Interaction"),
+#                     axis.labels = c("Hom : Work","Hom : Interm","Working Class","Intermediate Class  (ref. = Service)","Network Homogeneity"),
+#                     wrap.labels = 0) +
+#   geom_hline(yintercept = 0,color = "darkgray",size=1,linetype = 2) +
+#   scale_y_continuous(limits = c(-10,15)) +
+#   labs(color=NULL) +
+#   scale_color_manual(values = c("gray","blue","gray")) +
+#   theme(legend.position = "right")
+# 
+# 
+# sjPlot::plot_models(digclas1_VW_1,digclas1_VW_3,digclas1_VW_7,rm.terms = c("femaleFemale","agenum","partnerHas a partner",
+#                                                              "edyears","Q03pcmT02","Q03pcmT03","Q03pcmMissing",
+#                                                              "workstNot in paid work","know_total"),
+#                     m.labels = c("1. Base","2. Controls","3. Interaction"),
+#                    axis.labels = c("Hom : Work","Hom : Interm","Working Class","Intermediate Class  (ref. = Service)","Network Homogeneity"),
+#                     wrap.labels = 0) +
+#   geom_hline(yintercept = 0,color = "darkgray",size=1,linetype = 2) +
+#   scale_y_continuous(limits = c(-10,15)) +
+#   labs(color=NULL) +
+#   scale_color_manual(values = c("purple","gray","gray")) +
+#   theme(legend.position = "right")
 ```
@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+  pacman::p_load(knitr)
+tabformat = if(is_html_output()) {"html"} else if(is_latex_output()) {"latex"}
 df1$id <- 1:dim(df1)[[1]]
@@
   mutate("%"=p)
-kable(df,linesep = "",booktabs=TRUE,format='latex',caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
+tab_an_posgen <- 
+kable(df,linesep = "",booktabs=TRUE,format=tabformat,caption = "ISEI scores assigned to occupations included in the position generator instrument") %>%
   kable_styling(full_width = F,font_size = 10,latex_options = "HOLD_position") %>%
@@
   pack_rows("Lower-status positions", 7, 10) %>% 
-  footnote(general = "N = 31,694",footnote_as_chunk = T)
+  footnote(general = "N = 31,694",footnote_as_chunk = T);tab_an_posgen
 ```
@@
 rm(list=ls())
-
+tabformat = if(is_html_output()) {"html"} else if(is_latex_output()) {"latex"}
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
@@
 
+tab_an_classag <- 
 left_join(
@@
   dplyr::select("dclass6res","N1","freq1","dclass3res_V","N2","freq2") %>%
-  kable(booktabs = TRUE, format='latex',linesep = "",digits = 1,format.args = list(big.mark = ","),
+  kable(booktabs = TRUE, format=tabformat,linesep = "",digits = 1,format.args = list(big.mark = ","),
         caption = "Level of aggregation of social class",
@@
   collapse_rows(columns = c(4,5,6), valign = "middle") %>% 
-  footnote(general = "N = 31,694",footnote_as_chunk = T)
+  footnote(general = "N = 31,694",footnote_as_chunk = T);tab_an_classag
 ```
@@
 dfreg$country3b <- paste0(dfreg$country3," (",dfreg$country,")")
+
+tab_an_countries <- 
 dfreg %>% 
@@
   arrange(homclass) %>% ungroup() %>% 
-  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = "latex", linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
-        caption = "Values per country for the macro-social variables",
+  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = tabformat, linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
+        caption = "Values per country for the country-level variables",
         col.names = c("Country","N","Network Homogeneity","Income Inequality (Gini Index)","GDP/capita in $1000","Size of the Welfare State")) %>% 
@@
   footnote(general = "N = 31,694; Source: ISSP 2017, WID, WIID and ILO. Variables in original scale",
-           footnote_as_chunk = T)  
+           footnote_as_chunk = T);tab_an_countries
 # dfreg %>% 

### 2024-10-09 paper1_jiturra-UB-149.Rmd
ajustes patrick 3

--- 2024-09-26 paper1_jiturra.Rmd
@@
 Recently, however, a growing body of research has begun to focus on how the class profile of social networks influences redistributive preferences [@lindh_missing_2021; @lee_consider_2023; @paskov_crossclass_2022].
-Although prior studies have shown that class-based network segregation—defined as the concentration of similar-class network ties—can undermine attachment to society [@otero_lives_2022], there is still limited understanding of how being embedded in a homogeneously class-based network impacts attitudes toward inequality and redistribution [@otero_power_2023].
+Although prior studies have shown that class-based network segregation—defined as the concentration of similar-class network ties—can undermine societal cohesion [@otero_lives_2022], there is still limited understanding of how being embedded in a homogeneously class-based network impacts attitudes toward inequality and redistribution [see @otero_power_2023].
 Contributing to this debate, this research first aims to investigate the individual-level relationship between class-based network segregation and redistributive preferences.
-In addition, it has been suggested that social classes tend to form segregated networks according to the homophily principle, understood as the higher chances of forming social ties with others with similar characteristics [@mcpherson_birds_2001;@otero_lives_2022].
-Furthermore, cross-national comparisons indicate that class-based network stratification strengthens in societies with high economic inequality, which in turn drives stronger social distance between classes, particularly among the lower classes [@otero_differences_2023; @pichler_social_2009].
-Against this backdrop, the present study seeks to contribute to understanding how cross-national differences in income inequality act as a moderating factor in the relationship between class-based network segregation and redistributive preferences.
-
+At the same time, it has been suggested that social classes tend to form segregated networks [see @mcpherson_birds_2001; @otero_lives_2022], and cross-national comparisons indicate that in more economically unequal societies, the link between social class and network composition strengthens, leading to greater segregation, particularly among the working class [see @otero_differences_2023; @lancee_income_2012].
+
+Against this backdrop, the present study seeks to explore how cross-national differences in income inequality act as a moderating factor in the relationship between class-based network segregation and redistributive preferences.
 While segregation may deepen existing class divisions in redistributive preferences [@paskov_crossclass_2022], little is known about how income inequality shapes this relationship.
-On the one hand, research on the class-attitude link suggests that income inequality is crucial for understanding how class relations—i.e., the social and political distance between classes—translate into redistributive demands, as it reflects the state of class struggle in contemporary capitalist societies [@edlund_democratic_2015; @curtis_how_2015].
-A consistent finding is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, whereas the already high redistributive demands of the lower classes remain relatively stable, regardless of inequality levels [@sachweh_why_2019; @dimick_altruistic_2017].
+On theone hand, research on the class-attitude link suggests that income inequality is crucial for understanding how class relations—i.e., the social and political distance between classes—translate into redistributive demands, as it reflects the state of class struggle in contemporary capitalist societies [@edlund_democratic_2015; @curtis_how_2015].
+A consistent finding is that the upper classes tend to be more supportive of redistribution in contexts of high inequality, whereas the already high redistributive demands of the working class remain stable, regardless of inequality levels [@sachweh_why_2019; @dimick_altruistic_2017].
 On the other hand, it is well-documented that income inequality affects social relations, reinforcing stratified access to social activities and widening the distance between classes.
 In such conditions, the upper classes tend to be more socially active and maintain more diverse networks, while the lower classes become increasingly inactive and segregated as inequality rises [@lancee_income_2012; @otero_differences_2023; @pichler_social_2009].
-However, current research efforts have primarily examined the impact of income inequality moderates the relations of social class on either social networks or redistributive preferences.
-Thus, this study aims to address two key questions:
+However, current research efforts have primarily examined the impact of income inequality either on social networks or on support for redistribution.
+Thus, a key question remains: to what extent does income inequality moderate the relationship between class-based network segregation and redistributive preferences?
+
+Therefore, this study aims to address two key questions:
 
@@
 
-Theoretically, studies on economic inequality, social class, and redistributive preferences show varying class reactions to rising inequality.
+Studies on economic inequality, social class, and redistributive preferences show varying class reactions to rising inequality.
 Political economists suggest that high-income individuals are far from being monolithic in their redistributive preferences, motivated by concerns about inequality's adverse effects (e.g., crime), leading to altruistic support for redistribution [@dimick_models_2018; @dimick_altruistic_2017; @rueda_externalities_2016].
 Conversely, the moral economy literature in sociology explains affluent differences through evaluations of distributive justice regarding resource allocation procedures [@liebig_sociology_2016].
-At the same time, the literature on the role of income inequality on social cohesion has argued that unequal societies strengthen barriers to trustworthy social connections.
+Furthermore, income inequality strengthens barriers to trustworthy social connections, affecting social relations.
 Neckerman and Torche [-@neckerman_inequality_2007, p.
 344] noted that marginalization is linked to reduced participation in social life, exacerbated by greater inequality.
-Also, rising economic inequality erodes social relations by reducing social trust, which underpins mutual understanding and collective solidarity [@kragten_income_2017].
-Conversely, it is noted that societies with low inequality and comprehensive welfare states enhance civic and social participation, increasing generalized trust and reducing social conflict [@uslaner_inequality_2005].
-Similarly, it has been argued that social participation can nurture higher chances for cross-class interactions and motivate more egalitarian attitudes, being upper-class citizens who support stronger collective solidarity through government redistribution in more cohesive communities [@yamamura_social_2012].
+Higher economic inequality also erodes social relations by reducing social trust, which underpins mutual understanding and solidarity [@kragten_income_2017].
+Conversely, lower-income inequality and comprehensive welfare states enhance civic and social participation, increasing generalized trust and reducing social conflict [@uslaner_inequality_2005].
+Additionally, @yamamura_social_2012 found that redistributive preferences increase with community-level social activity participation, with high-income citizens supporting collective solidarity through government redistribution.
 
@@
 Thus, stronger support for state-organized redistribution among the upper classes can be attributed to their greater awareness of the incentives and societal consequences of income inequality [@curtis_how_2015; @Svallfors2006].
-At the same time, cross-national comparative evidence indicates that stratified access to social activities and networks is reinforced in unequal societies.
+At the same time, comparative studies indicate that stratified access to social activities and networks is reinforced in unequal societies.
 For example, @pichler_social_2009 demonstrated that class differences in civic and family network participation are exacerbated in unequal societies.
 Similarly, @lancee_income_2012 found that income-based stratification in civic participation increases with inequality.
-Also, @otero_differences_2023 found that economic inequality enhances
-interdependence among cultural, economic, and social capital, which results in stronger stratified chances for cross-class interactions.
-Thus, in unequal societies, the upper classes can navigate diverse social settings while maintaining their distinct positions, whereas the lower classes remain marginalized and segregated due to others' choices [@otero_open_2021, p.24].
-
-Against this backdrop, there are at least three emerging theoretical implications on the role of income inequality on class-based networks and redistributive preferences.
-The first implication is that it is plausible to assume that income inequality drives greater segregation, as the result of lower participation and social trust.
-However,  it is worth noticing that resource interdependency seems to exacerbate social exclusion for the lower classes, while the upper classes may hold more cohesive experiences that drive stable or even lower segregation in more unequal societies.
-A second implication is that the relationship between class and attitudes weakens in highly unequal societies, where the upper classes tend to show more support for redistribution, contrasting with the relatively stable preferences of the lower classes.
+Also, @otero_differences_2023 found that economic inequality enhances stratified access to network diversity, amplifying interdependence among cultural, economic, and social capital.
+Thus, the upper classes navigate diverse social settings while maintaining their distinct positions, whereas the lower classes remain marginalized and segregated due to others' choices [@otero_open_2021, p.24].
+
+Against this backdrop, one theoretical implication is that income inequality drives greater segregation.
+However, resource interdependency seems to exacerbate social exclusion for the lower classes, while the upper classes may experience less segregation.
+Another inference is that the relationship between class and attitudes weakens in highly unequal societies, where the upper classes tend to show more support for redistribution, contrasting with the relatively stable preferences of the lower classes.
 In addition, it is also true that in egalitarian societies with more encompassing welfare states class-based distributive struggles tend to be more institutionalized (e.g.
@@
 As a result, class positions are more closely implied in political conflict as the institutional framework allows them to better articulate their interests.
-A third implication is that as inequality increases and the class divide in redistributive preferences narrows, this may also be extended to the influence of class-based segregation on redistributive preferences.
-As the class-attitude link becomes mild in more unequal contexts, it is also expected that homogeneous class-based networks might not have the same strength where the role of class positions loses significance.
+ A derived implication is that as inequality increases and the class divide in redistributive preferences narrows, this may also be extended to the influence of class-based segregation on redistributive preferences.
 Therefore, I expect income inequality to weaken the interaction between network homogeneity and social class.
-Specifically, I hypothesize that the conditional relationship between network homogeneity and social class stated at the individual level (*segregation hypothesis*) will be less pronounced in the context of higher income inequality (*mitigation hypothesis*).
+Specifically, I hypothesize that the conditional relationship between network homogeneity and social class (*segregation hypothesis*) will be less pronounced in the context of higher income inequality (*mitigation hypothesis*).
 Given these considerations, the second hypothesis is as follows:

### 2024-10-09 paper1_jiturra.Rmd
ajustes patrick 3

@@
 ---
-title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
-css: "input/css/custom.css" # custom CSS para html
+# title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
+# css: "input/css/custom.css" # custom CSS para html
 fontsize: 12pt
 linestretch: '1.5'          # interlineado
-#linestretch: '2.0'          # interlineado 
+# #linestretch: '2.0'          # interlineado 
 papersize: a4
@@
 lang: en-US
-# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-date: "`r format(Sys.Date(), '%d %b %Y')`"
-author:
-- name: Julio Iturra-Sanhueza
-  affiliation: Bremen International Graduate School of Social Sciences
-  email: jiturra@uni-bremen.de
-abstract: | 
-  | Rising economic inequality has increased attention on the link between class-based networks and redistributive preferences in contemporary societies.
+# # date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
+# date: "`r format(Sys.Date(), '%d %b %Y')`"
+# author:
+# - name: Julio Iturra-Sanhueza
+#   affiliation: Bremen International Graduate School of Social Sciences
+#   email: jiturra@uni-bremen.de
+# abstract: | 
+#   | Rising economic inequality has increased attention on the link between class-based networks and redistributive preferences in contemporary societies.
 Previous research has shown that class differences in redistributive preferences tend to narrow in more unequal societies, primarily due to higher redistributive preferences within the service class.
@@
 The implications for studying class-based networks and political attitudes are also discussed.
-  | 
-  | **Keywords**: social networks, segregation, social class, income inequality, redistributive preferences 
+#   | 
+#   | **Keywords**: social networks, segregation, social class, income inequality, redistributive preferences 
 output:
@@
   bookdown::html_document2:
+    toc: false
+    code_folding: hide
+    number_sections: false
+    toc_float:
+      collapsed: false
+      smooth_scroll: false
+  bookdown::word_document2:
+    reference_docx: "input/mytemplate.docx"
     toc: false
@@
   - \usepackage{graphicx}
+  - \usepackage{setspace}  
   - \usepackage{float}
@@
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::pdf_document2")
+rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
 rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::html_document2")
-rmarkdown::render("paper1_jiturra.Rmd", output_format = "bookdown::word_document2")
 ```
@@
 
-**Word count**:  `r wordcount$words`
+<!-- **Word count**:  `r wordcount$words` -->
 
@@
 Recently, however, a growing body of research has begun to focus on how the class profile of social networks influences redistributive preferences [@lindh_missing_2021; @lee_consider_2023; @paskov_crossclass_2022].
-Although prior studies have shown that class-based network segregation—defined as the concentration of similar-class network ties—can undermine attachment to society [@otero_lives_2022], there is still limited understanding of how being embedded in a homogeneously class-based network impacts attitudes toward inequality and redistribution [@otero_power_2023].
-Contributing to this debate, this research first aims to investigate the individual-level relationship between class-based network segregation and redistributive preferences.
-In addition, it has been suggested that social classes tend to form segregated networks according to the homophily principle, understood as the higher chances of forming social ties with others with similar characteristics [@mcpherson_birds_2001;@otero_lives_2022].
-Furthermore, cross-national comparisons indicate that class-based network stratification strengthens in societies with high economic inequality, which in turn drives stronger social distance between classes, particularly among the lower classes [@otero_differences_2023; @pichler_social_2009].
+Additionally, social classes tend to form segregated networks according to the homophily principle, understood as the higher chances of forming social ties with others with similar characteristics [@mcpherson_birds_2001;@otero_open_2021].
+Although prior evidence has shown that class-based network segregation —as the proportion of network contacts from the same class relative to an individual's class position— can undermine attachment to society in highly unequal societies like Chile [@otero_lives_2022], there is still limited understanding of how being embedded in a homogeneously class-based network impacts attitudes toward inequality and redistribution in cross-national perspective [@otero_power_2023].
+Contributing to this debate, this research first aims to investigate the extent individual-level relationship between class-based network segregation and redistributive preferences.
+Furthermore, cross-national comparisons indicate that class-based network stratification strengthens in societies with high economic inequality, which in turn drives wider social distance between classes [@otero_differences_2023; @pichler_social_2009].
 Against this backdrop, the present study seeks to contribute to understanding how cross-national differences in income inequality act as a moderating factor in the relationship between class-based network segregation and redistributive preferences.
@@
 Class-based explanations of redistributive preferences have predominantly focused on individuals.
-According to self-interest-driven theories, economic resources or exposure to risk explain why working classes with fewer resources and greater job insecurity tend to support redistribution more than the upper classes [@meltzer_rational_1981; @rehm_risks_2009].
+According to self-interest-driven theories, economic resources or risk exposure explain why working classes with fewer resources and greater job insecurity tend to support redistribution more than the upper classes [@meltzer_rational_1981; @rehm_risks_2009].
 Furthermore, while material interests often dominate in conditions of scarcity, value-based motivations, such as egalitarianism, may drive stronger support for redistribution under conditions of greater security and weaken under material hardship [@Kulin2013; @Maldonadoetal2019].
@@
 Given this context, studying the connections between social classes from a network perspective offers a comprehensive way to understand redistributive preferences beyond the individual level.
-By focusing on network ties, the collective dimension of class relations is brought to the forefront, emphasizing that social ties encompass both social and economic resources [@lin_access_1986], which serve as the foundation for communal action [@weber_class_2011, pp.
+By focusing on network ties, the collective dimension of between-class relations is brought to the forefront, emphasizing that social ties encompass both social and economic resources [@lin_access_1986], which serve as the foundation for communal action [@weber_class_2011, pp.
 57-59].
@@
 However, this research aligns with the prevailing view that attitudinal similarity within networks arises primarily from structural contact opportunities shaped by the class composition of social ties, rather than from homophilic preferences for socializing with like-minded individuals [@feld_focused_1981].
-
-To investigate the implications of networks for redistributive preferences, I propose distinguishing between two closely related—but distinct—perspectives on how class-based networks manifest within social structures.
-
-First, the concept of _network diversity_ refers to the degree of connectedness to dissimilar ties (e.g., different occupations or activities), representing vertical access to diverse resources within social networks [@lin_access_1986].
-In this context, diversity reflects the dispersion of different ties (alteri) across the network, independent of the individual’s (ego) characteristics [@otero_power_2023].
-Empirical studies, such as those by @pichler_social_2009 and @lancee_income_2012, argue that higher civic engagement in formal organizations increases the likelihood of the upper classes forming connections with more diverse individuals, whereas the working classes tend to engage in more homogeneous participation.
-Similar patterns emerge in social tie composition, where the upper and intermediate classes maintain more diverse and prestigious social environments than the working class [@cepic_how_2020; @carrascosa_class_2023].
-
-The second and primary perspective adopted in this study is _network segregation,_ defined as having contact primarily with people of the same class.
-This approach measures the similarity between an individual’s (ego) network ties and is conceptually closer to homophily, as it is rooted in an individual’s class position and has been empirically examined through network homogeneity [@otero_open_2021].
-Evidence suggests that property-based boundaries are far less permeable than authority-based ones in the formation of cross-class ties.
+Thus, to investigate the implications of networks for redistributive preferences, I propose distinguishing between two closely related—but distinct—perspectives on how class-based networks are structured.
+
+First, _network diversity_ refers to the degree of connectedness to dissimilar ties (e.g., different occupations or activities), representing access to diverse resources within social networks [@lin_access_1986].
+Thus, refers to the dispersion of an attribute tie (alteri) within the network, independently of the characteristic that an individual has (ego) [@otero_power_2023].
+Related studies such as @pichler_social_2009 and @lancee_income_2012, have argued that variety participation in formal organizations increases the chances of upper classes forming more diverse social connections.
+In contrast, the working classes show a more homogeneous participation repertoire.
+Similar patterns emerge in network socioeconomic composition, where the upper middle classes maintain more prestigious and diverse networks than the working classes [@cepic_how_2020; @carrascosa_class_2023].
+However, I argue that while diversity accounts for the dispersion of an attribute within the network this approach lacks an anchor position that allows to address segregation more precisely.
+
+By contrast, the perspective adopted in this study is _network segregation,_ defined as the pattern of contact primarily with people of the same characteristics.
+The focus is on the similarity between the class position of individuals (ego) and their network ties (alteri).
+Therefore, it is conceptually closer to homophily and has been empirically examined through network homogeneity [@otero_open_2021].
+Some studies have suggested that property-based boundaries are far less permeable than authority-based ones in the formation of cross-class ties.
 For example, @wright_relative_1992 suggests that class interests tend to widen the social distance between proprietors and manual workers, while the intermediate position of supervisors and their more frequent contact with manual workers make cross-class friendships more likely.
@@
 
-In addition to rational self-interest or value-based explanations, the argument that social ties have implications for attitude formation is not precisely new.
+In addition to individual class-based explanations, the argument that social ties have implications for attitude formation is not precisely new.
 More specifically, two approaches have discussed the role of social relations in redistributive preferences: reference groups and class-based networks.
@@
 Thus, segregation can potentially diminish social cohesion as it exacerbates perceptions of others as strangers which in turn reduces empathy and solidarity [@otero_lives_2022].
+Although both approaches share the theoretical assumption that social networks contribute information (_availability heuristic_) and affect attitudes (_social influence_).
+I argue that an advantage of the network perspective is that it has been more effective in defining the structural position of network ties, and has more directly addressed the relationship with redistributive preferences.
 
 How do network ties affect redistributive preferences?
-The class position of surrounding family members, friends, and acquaintances affects support for redistribution, as these ties function as socialization agents whose impact can be amplified in segregated social networks.
-In principle, political attitudes are connected to class interests and norms as they are socialized in the family of origin during childhood and early adulthood.
+The class position of surrounding family members, friends, and acquaintances affects support for redistribution, as these ties are a source of social influence whose impact can be amplified in segregated social networks.
+In principle, political attitudes are connected to class interests and norms as they are primarily -  but exclusively - socialized in the family of origin during childhood and early adulthood.
 For instance, @lee_consider_2023 shows that individuals with network ties to the upper class through parental connections tend to support redistribution and progressive taxation less than those from working-class family backgrounds.
@@
 For example, @paskov_crossclass_2022 indicates that working-class ties bolster redistributive preferences, whereas ties with the upper class decrease them, with the effects becoming more pronounced when the class positions of individuals, partners, and parents form a more homogeneous network.
-Similarly, @lindh_missing_2021 found that friendship and acquaintanceship ties to the managerial class are associated with lower redistributive preferences compared to ties with the sociocultural and working classes.
+Beyond family ties, @lindh_missing_2021 found that friendship and acquaintanceship ties to the managerial class are associated with lower redistributive preferences compared to ties with the sociocultural and working classes.
 Hence, this suggests that individuals tend to adjust their attitudes based on the class position of their contacts [@lindh_missing_2021].
 
-In summary, I anticipate a weak direct association between network segregation and redistributive preferences.
+In summary, I expect a weak direct association between network segregation and redistributive preferences.
 This is mainly because network homogeneity - as the proportion of similar class network ties - does not distinguish between anchor class positions and refers to the overall degree of segregation.
@@
 
-The literature on the role of economic inequality on (1) the class-attitude link and (2) social relations have been independently developed.
-
-Theoretically, studies on economic inequality, social class, and redistributive preferences show varying class reactions to rising inequality.
-Political economists suggest that high-income individuals are far from being monolithic in their redistributive preferences, motivated by concerns about inequality's adverse effects (e.g., crime), leading to altruistic support for redistribution [@dimick_models_2018; @dimick_altruistic_2017; @rueda_externalities_2016].
-Conversely, the moral economy literature in sociology explains affluent differences through evaluations of distributive justice regarding resource allocation procedures [@liebig_sociology_2016].
-At the same time, the literature on the role of income inequality on social cohesion has argued that unequal societies strengthen barriers to trustworthy social connections.
-Neckerman and Torche [-@neckerman_inequality_2007, p.
-344] noted that marginalization is linked to reduced participation in social life, exacerbated by greater inequality.
-Also, rising economic inequality erodes social relations by reducing social trust, which underpins mutual understanding and collective solidarity [@kragten_income_2017].
-Conversely, it is noted that societies with low inequality and comprehensive welfare states enhance civic and social participation, increasing generalized trust and reducing social conflict [@uslaner_inequality_2005].
-Similarly, it has been argued that social participation can nurture higher chances for cross-class interactions and motivate more egalitarian attitudes, being upper-class citizens who support stronger collective solidarity through government redistribution in more cohesive communities [@yamamura_social_2012].
-
-Empirically, it has been shown that affluent groups are more responsive, perceiving that rising inequality affects the overall opportunity structure and social mobility chances [@sachweh_why_2019].
-Also, higher perceived inequality of opportunity among the upper classes can motivate support for redistribution as a matter of procedural justice [@kim_socioeconomic_2018].
-In contrast, low-income individuals view ascribed characteristics as more crucial in constraining opportunities, irrespective of current income inequality [@sachweh_why_2019].
-Similarly, @edlund_democratic_2015 argue that in unequal societies with residual welfare states, social class lacks significant political meaning, weakening distributive conflicts around traditional working-class organizations (e.g., unions).
-Thus, stronger support for state-organized redistribution among the upper classes can be attributed to their greater awareness of the incentives and societal consequences of income inequality [@curtis_how_2015; @Svallfors2006].
-At the same time, cross-national comparative evidence indicates that stratified access to social activities and networks is reinforced in unequal societies.
-For example, @pichler_social_2009 demonstrated that class differences in civic and family network participation are exacerbated in unequal societies.
-Similarly, @lancee_income_2012 found that income-based stratification in civic participation increases with inequality.
-Also, @otero_differences_2023 found that economic inequality enhances
-interdependence among cultural, economic, and social capital, which results in stronger stratified chances for cross-class interactions.
-Thus, in unequal societies, the upper classes can navigate diverse social settings while maintaining their distinct positions, whereas the lower classes remain marginalized and segregated due to others' choices [@otero_open_2021, p.24].
-
-Against this backdrop, there are at least three emerging theoretical implications on the role of income inequality on class-based networks and redistributive preferences.
-The first implication is that it is plausible to assume that income inequality drives greater segregation, as the result of lower participation and social trust.
-However,  it is worth noticing that resource interdependency seems to exacerbate social exclusion for the lower classes, while the upper classes may hold more cohesive experiences that drive stable or even lower segregation in more unequal societies.
-A second implication is that the relationship between class and attitudes weakens in highly unequal societies, where the upper classes tend to show more support for redistribution, contrasting with the relatively stable preferences of the lower classes.
-In addition, it is also true that in egalitarian societies with more encompassing welfare states class-based distributive struggles tend to be more institutionalized (e.g.
-through unions or political parties).
-As a result, class positions are more closely implied in political conflict as the institutional framework allows them to better articulate their interests.
-A third implication is that as inequality increases and the class divide in redistributive preferences narrows, this may also be extended to the influence of class-based segregation on redistributive preferences.
-As the class-attitude link becomes mild in more unequal contexts, it is also expected that homogeneous class-based networks might not have the same strength where the role of class positions loses significance.
+Theoretically, rising income inequality prompts diverse responses across social classes regarding redistributive preferences and social cohesion.
+Political economy perspectives suggest that affluent individuals are not uniform in their attitudes, with some supporting redistribution out of concern for the broader societal effects of inequality, such as crime and instability [@dimick_models_2018; @dimick_altruistic_2017].
+The moral economy approach in sociology explains this variation through differing views on distributive justice and fairness in resource allocation [@liebig_sociology_2016].
+At the same time, research on social cohesion shows that inequality erodes trust and participation, particularly among marginalized groups, exacerbating social exclusion [@neckerman_inequality_2007; @kragten_income_2017].
+In contrast, egalitarian societies with strong welfare states foster higher levels of civic engagement and cross-class interactions, which strengthen solidarity and promote more egalitarian attitudes [@uslaner_inequality_2005; @yamamura_social_2012].
+
+Empirical evidence further indicates that affluent individuals are more likely to perceive inequality as a threat to social mobility and opportunity structures, motivating support for redistribution as a form of procedural justice [@sachweh_why_2019; @kim_socioeconomic_2018].
+By contrast, low-income individuals tend to focus on structural barriers that limit opportunities, regardless of inequality [@sachweh_why_2019].
+In highly unequal societies with residual welfare states, where traditional class-based political organizations like unions have weakened, upper-class support for redistribution stems from a heightened awareness of inequality’s societal consequences [@curtis_how_2015; @Svallfors2006; @edlund_democratic_2015].
+Moreover, income inequality reinforces stratification in social participation, as the affluent maintain access to diverse networks while the lower classes face growing exclusion [@pichler_social_2009; @lancee_income_2012].
+This stratification limits cross-class interactions and further entrenches social divisions, with the upper classes navigating diverse social environments while the lower classes remain segregated and marginalized [@otero_differences_2023; @otero_open_2021].
+
+Against this backdrop, three key implications emerge regarding the role of income inequality in shaping class-based networks and redistributive preferences.
+First, income inequality likely leads to greater segregation due to reduced participation and lower social trust; however, while resource interdependency exacerbates social exclusion for lower classes, upper classes may experience greater cohesion, potentially stabilizing or even reducing segregation in more unequal societies.
+Second, the relationship between class and attitudes weakens in highly unequal contexts, where upper classes tend to show increased support for redistribution, contrasting with the relatively stable preferences of lower classes.
+In egalitarian societies with comprehensive welfare states, class-based distributive struggles become more institutionalized, allowing class positions to be closely tied to political conflict.
+Lastly, as inequality rises and the class divide in redistributive preferences narrows, the influence of class-based segregation on these preferences may diminish, with homogeneous class networks losing significance as class positions become less relevant in shaping attitudes.
+
 Therefore, I expect income inequality to weaken the interaction between network homogeneity and social class.
-Specifically, I hypothesize that the conditional relationship between network homogeneity and social class stated at the individual level (*segregation hypothesis*) will be less pronounced in the context of higher income inequality (*mitigation hypothesis*).
+Specifically, I hypothesize that the conditional relationship between network homogeneity and social class at the individual level will be less pronounced in the context of higher income inequality (_mitigation hypothesis_).
 Given these considerations, the second hypothesis is as follows:
@@
 I use two indicators to measure redistributive preferences.
-The first indicator corresponds to support for government redistribution and it is measured by the item: "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes." The second indicator is egalitarian preferences and it is measured by the item: "For a society to be fair, differences in people's standard of living should be small." Both indicators use a five-point Likert scale with the following categories: 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree'(3), 'Disagree' (4), and 'Strongly disagree'(5) (*r* = 0.62).
-Following @svallfors_government_2013, I reverse-coded, averaged and normalized the indicators in a 0 to 100 index, where higher values reflect stronger redistributive preferences.
+The first indicator is support for government redistribution measured by the item: "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes." The second indicator is egalitarian preferences measured by the item: "For a society to be fair, differences in people's standard of living should be small." Both indicators use a five-point Likert scale with the following categories: 'Strongly agree' (1), 'Agree' (2), 'Neither agree nor disagree'(3), 'Disagree' (4), and 'Strongly disagree'(5) (*r* = 0.62).
+Following @svallfors_government_2013, I reverse-coded, averaged, and normalized the indicators in a 0 to 100 index, where higher values reflect stronger redistributive preferences.
 
@@
 
-To measure social class, I employ the Erikson-Goldthorpe-Portocarrero (EGP) class scheme [@Erikson1992].
-The EGP scheme is one of the most consistent and validated measures for social class positions in comparative research and has demonstrated its validity in both industrialized and late-industrialized societies [@evans_political_2013;@barozet_measurement_2021].
+I employ the Erikson-Goldthorpe-Portocarrero (EGP) class scheme [@Erikson1992] to measure social class.
+The EGP scheme is the most consistent and validated measure for class positions in comparative research and has demonstrated its validity in both industrialized and late-industrialized societies [@evans_political_2013;@barozet_measurement_2021].
 Therefore, information about occupations, self-employment status, and the number of employees is used to classify respondents into six class positions.
@@
 
-[^egpclass]: Self-employed farmers (IVc) are grouped in the self-employed class, while agricultural labor (VIIb) is in the working class.
+[^egpclass]: Self-employed farmers (IVc) are included in the self-employed class, while agricultural labor (VIIb) is in the working class.
 
@@
 Here, occupations are presented to the respondent in a grid that allows them to declare whether they know (or not) a person who performs that occupation.
-The tie can be clasified in four groups, defining tie to this person is as a "Family or relative," "Close friend,” "Someone else I know," or "No one.”  With this information, the first three categories are coded as 1 to represent the presence of a tie ("Knows") and 0 as the abscence of a conection to a person with that occupation ("Does not know").
+The tie can be classified into four groups, defining tie to this person as a "Family or relative," "Close friend,” "Someone else I know," or "No one.”  With this information, the first three categories are coded as 1 to represent the presence of a tie ("Knows") and 0 as the absence of a connection to a person with that occupation ("Does not know").
 Subsequently, all declared ties were summed to represent the total number of occupations known by the respondent.
@@
 Subsequently, following @otero_differences_2023 I classify occupations into three status positions that resemble Goldthorpe's class positions based on the International Socio-Economic Index of Occupational Status (ISEI) [@ganzeboom_new_2010].
-The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *higher* positions (ISEI range: 68-85); school teacher, police officer, and nurse are classified as *medium* positions (ISEI range: 48-63); and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *lower* positions (ISEI range: 17-38).
+The classification is as follows: lawyer, executive of a large firm, and human resource manager are categorized as *higher* positions (ISEI range: 68-85); schoolteacher, police officer, and nurse are classified as *medium* positions (ISEI range: 48-63); and car mechanic, bus driver, hairdresser, and home or office cleaner are considered *lower* positions (ISEI range: 17-38).
 
@@
 Subsequently, models including the individual level factors are estimated to examine the association between network homogeneity and social class to test Hypothesis 1 [^altmodels].
-Following this, country level variables included in the estimations by incorporating random intercepts and random slopes for network homogeneity and social class.
+Following this, country-level variables are included in the estimations by incorporating random intercepts and random slopes for network homogeneity and social class.
 This model tests Hypothesis 2 by estimating a three-way cross-level interaction to determine whether income inequality moderates the interaction between network homogeneity and social class.
@@
 In addition, homogeneity in the intermediate class tends to be close to the average of each country between the lower and upper classes.
-Despite that in some societies these differences do not show the same escalated distribution of homogeneity by social class, the general pattern holds true.
+Despite that in some societies these differences do not show the same escalated distribution of homogeneity by social class, the general pattern holds.
 
@@
 
-The multilevel analysis results are shown in Table \@ref(tab:table1).
-On the one hand, I expected that network homogeneity has a weak direct association with redistributive preferences as it reveals only the overall segregation without distinction between classes.
-In this matter, Model 1 integrates network homogeneity and as it is previously noted in the country-level associations, more homogeneous networks tend to exhibit higher redistributive preferences.
-Then, the association is robust to network size, sociodemographic characteristics, and socioeconomic status in Model 2.
-However, after including individual social class in Model 3, the association between homogeneity and redistributive preferences loses its strength.
-Regarding this, I expected that the inclusion of class suppresses the association of network homogeneity as it is anchored in class position.
-Despite this, the focus of this study is not on the _direct_ association of network homogeneity but I hypothesized the association of homogeneity, and redistributive preferences is conditional to social class.
-
-Thus, the interaction terms of network homogeneity and social class in Model 4 show that compared to the service class, homogeneity increases redistributive preferences in the working and intermediate classes.
+The results regarding the relationship between class-based network homogeneity and redistributive preferences using multilevel models are shown in Table \@ref(tab:table1).
+Model 1 shows that individuals embedded in homogeneous social networks are more likely to support redistributive policies.
+In Model 2, the introduction of control variables and network size slightly reduces the effect of homogeneity.
+These results differ from previous findings, where being more segregated is associated with less attachment to society [@otero_lives_2022] and stronger support for redistribution in more cohesive communities [@yamamura_social_2012].
+[^homoclass]
+
+[^homoclass]: After including individual social class, the association between homogeneity and redistributive preferences loses strength and significance (see Appendix \@ref(tab:tab-an-classag)).
+
+Moving to hypothesis 1, the interaction terms of network homogeneity and social class in Model 3 show that compared to the service class, homogeneity increases redistributive preferences in the working and intermediate classes.
 To illustrate this result further, Figure \@ref(fig:fig4) depicts that the changes in redistributive preferences from low to high homogenous working and intermediate class networks are quite mild, where the differences in redistributive preferences go from 69.8 to 72.8 and from 69.4 to 70.47, respectively.
 In contrast, the changes in redistributive preferences in homogeneous services class networks are more pronounced, changing from 70 when homogeneity is at its lowest point to 62.8 in fully homogeneous networks.
-Altogether, these results provide evidence in favor of the segregation hypothesis (H1), where the class differences in redistributive preferences become wider as network homogeneity increases.
-
-<!-- estimate std.error  statistic            p.value  conf.low conf.high -->
-<!--  2.976180 0.8970721  3.3176597 0.0009077501054860  1.217951  4.734409 -->
-<!--  1.029445 1.1996805  0.8580992 0.3908376677138878 -1.321886  3.380775 -->
-<!-- -7.440596 1.1013920 -6.7556289 0.0000000000142217 -9.599284 -5.281907 -->
+
+These results confirm previous findings on how social influence processes through class-based network ties affect attitudes in the economic domain [@lindh_missing_2021;@otero_power_2023].
+Additionally, they echo previous arguments on how sharing similar class positions with partner or family ties tends to intensify redistributive preferences depending on individual class positions [@paskov_crossclass_2022;@lee_consider_2023].
+Altogether, these results support the _segregation hypothesis_ (H1), where the class differences in redistributive preferences become wider as network homogeneity increases.
 
@@
 Table \@ref(tab:table2) presents the results of the multilevel models for income inequality.
-In the first place, Model 1 shows that there are no substantial differences in redistributive preferences between societies with different levels of income inequality.
-Subsequently, it can be seen in Model 2 that in societies with higher economic prosperity, redistributive preferences are lower regardless of the differences in income inequality between countries.
-At the same time, Model 3 indicates that in countries with more encompassing welfare states, redistributive preferences are higher, independently of income inequality and economic prosperity.
-More simply, higher redistributive preferences are observed in countries with more generous welfare states.
+First, Model 1 shows that there are no substantial differences in redistributive preferences between societies with different levels of income inequality.
+Subsequently, Model 2 shows that in societies with higher economic prosperity, redistributive preferences are lower regardless of the differences in income inequality between countries.
+Afterward, Model 3 indicates higher redistributive preferences are observed in countries with more generous welfare states, independently of income inequality.
 
 Finally, Model 4 incorporates a three-way interaction to determine whether the conditional association of network homogeneity to social class on redistributive preferences is moderated by income inequality.
-At the individual level, the findings for the segregation hypothesis remain robust.
-At the macro level, the three-way interaction suggests that higher economic inequality weakens the interaction of network homogeneity and social class.
-To better illustrate this result, Figure \@ref(fig:fig5) depicts how the interaction of network homogeneity and social class is gradually mitigated as income inequality increases.
-In this regard, the left panel in Figure \@ref(fig:fig5) illustrates that when inequality is low, the conditional association of network homogeneity and social class on redistributive preferences is more pronounced than in the center and left panels that respectively represent contexts of middle and higher income inequality.
-
-When taking a closer look, the differences in redistributive preferences between the working and service classes are smaller when network homogeneity is low, regardless of income inequality.
-Besides, higher network homogeneity is associated with larger class differences in redistributive preferences when inequality is low but progressively becomes smaller as income inequality increases.
-These results resonate with previous studies that have argued that the upper classes are more sensitive to income inequality, whereas the working class shows relatively stable attitudes regardless of the contextual levels of income inequality.
-Here, the results jointly suggest that network segregation matters in contexts of low and middle economic inequality but loses relevance in contexts of high inequality.
+The results suggest that higher economic inequality weakens the interaction of network homogeneity and social class – especially in the service class.
+To illustrate this result, Figure \@ref(fig:fig5) depicts how the interaction of network homogeneity and social class is gradually mitigated as income inequality increases.
+In this regard, the left panel in Figure \@ref(fig:fig5) illustrates that when inequality is low, the conditional association of network homogeneity and social class on redistributive preferences is more pronounced than in contexts of middle and high inequality.
+
+Taking a closer look, differences in redistributive preferences between the working and service classes are smaller when network homogeneity is low, regardless of income inequality.
+Besides, higher homogeneity is associated with wider class differences in redistributive preferences when inequality is low but progressively becomes smaller as income inequality increases.
+These results resonate with previous studies that have argued that the upper classes are more sensitive to income inequality, whereas the working class shows relatively stable attitudes regardless of the contextual levels of income inequality [@edlund_democratic_2015; @dimick_altruistic_2017; @curtis_how_2015].
+Here, the results jointly suggest that network segregation matters in contexts of low and middle economic inequality but loses relevance when inequality is high.
+
+Nevertheless, income inequality has a role in activating this association which follows a similar pattern to individual class-positions.
 Overall, the results presented above support the claims of the _mitigation_ hypothesis (H2), where the wider class divide in redistributive preferences in homogeneous class-based networks weakens as income inequality increases.
@@
 Hence, my finding supports the claims that social influence and particularly segregation in interpersonal networks strengthen class differences in redistributive preferences [@paskov_crossclass_2022;@lindh_missing_2021].
-Also, these results support the idea that low cross-class connections can reduce social integration and solidarity as they limit awareness about the lives of other classes [@blau_macrosociological_1977;@otero_lives_2022].
+Also, these results support the idea that low cross-class connections can reduce collective solidarity as they limit awareness about the lives of other classes [@blau_macrosociological_1977;@otero_lives_2022].
 Furthermore, the claimed 'empathy gulf' is more evident in how the service class is less willing to act against inequality as a collective commitment when they are highly segregated in homogeneous upper-class environments, in contrast to the increasing redistributive demands of the marginalized working class [@otero_power_2023;@sachweh_moral_2012].
@@
 Particularly, the most notable differences in redistributive preferences are observed in homogeneous service class networks.
-In contrast, preferences in homogeneous working class networks are relatively unaffected by inequality.
-
-Theoretically, I understand economic inequality establishes the field for class relations and conflict that are consequently crystallized in attitudes toward redistribution [@edlund_democratic_2015].
+In contrast, preferences in homogeneous working-class networks are relatively unaffected by inequality.
+
+Theoretically, I understand economic inequality establishes the field for class-based political conflict that is consequently crystallized in attitudes toward redistribution [@edlund_democratic_2015].
 Also, I conceive class relations as networks of social connections between social classes [@blau_macrosociological_1977].
-In this approach, social influence is linked to redistributive preferences as it represents the driving social force that makes class positions more salient as segregation increases [@lindh_missing_2021].
+In this approach, social influence is linked to redistributive preferences as it explains how class positions make attitudes more intense as segregation increases [@lindh_missing_2021].
 However, I evidenced that this prevails mostly in societies with low and middle levels of income inequality.
@@
        use.packages = F)
+
+htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
+       caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
+       custom.note = "Note: Models include sampling weights. Standard errors in parentheses. %stars",
+       threeparttable = T,
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 3:4,
+      "Homogeneity x Social Class"=5:6),
+      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+      file = "output/tables/tableA1.doc"
+      )
+
 # performance::check_collinearity(digclas1_VW_5)
@@
   xlab("Income Inequality") +
-  ylab("Class Differences in Network homogeneity \n (Working Class - Service Class)") +
+  ylab("Class Diff. in homogeneity (Working - Service)") +
   labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
-                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = NULL)
-
-#cor.test(homo_ineq$diff_working_upper_homo,
-#                                    homo_ineq$gini_disp, use='complete.obs')
-
-grid.arrange(fig_homodiff_gini, nrow = 1, 
+                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "C")
+
+fig_homodiff_redist<- 
+homo_ineq %>%  
+ggplot(aes(y=egal , x=diff_working_upper_homo)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  # geom_text() +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  ylab("Redistributive preferences") +
+  xlab("Class Diff. in homogeneity (Working - Service)") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
+                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "D")
+
+cor.test(homo_ineq$`Service Class (I+II)`,
+                                   homo_ineq$`Working Class (V+VI+VII)`,use='complete.obs')
+
+fig_egal_homo <- 
+homo_ineq %>%  
+ggplot(aes(y=egal, x=homclass3_V_res)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Network homogeneity")+
+  ylab("Redistributive preferences") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
+                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "B")
+fig_homo_gini<- 
+homo_ineq %>%  
+ggplot(aes(y=homclass3_V_res, x=gini_disp)) +
+  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
+  # geom_text() +
+  geom_text_repel(label=as.character(homo_ineq$country)) +
+  xlab("Income Inequality") +
+  ylab("Network homogeneity") +
+  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
+                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "A")
+
+ggsave(plot = arrangeGrob(fig_homo_gini,fig_egal_homo,
+                          fig_homodiff_gini,fig_homodiff_redist,
+             nrow = 2, 
  bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
  gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
-  ))
+  )),
+ filename = "figure4-4-plots.png",device = "png",
+ path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26)
 
@@
        path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
+
 ```
@@
                  "Executive of large firm", "Lawyer"),
-  "ISEI" = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85)
+  "ISEI" = c(17, 32, 36, 38, 48, 54, 63, 68, 70, 85),
+  "ISCO08" = rev(c(2611,1100,1212,2300,5412,2220,7231,8331,5140,9111)),
+  "EGP" = rev(c("I","I","I","II","VI","II","VI","VII","VI","VII"))
 ) %>% 
@@
   footnote(general = "N = 31,694",footnote_as_chunk = T);tab_an_posgen
+
+# iscotab<- df1 %>%
+#   select(dclass11,isei08,ISCO08) %>%
+#   arrange(ISCO08)
+
+# 1 1     'I: Higher Controllers'               
+# 2 2     'II: Lower Controllers'               
+# 3 3     'IIIa: Routine Nonmanual'             
+# 4 4     'IIIb: Lower Sales-Service'           
+# 5 5     'IVa: Self-employed with employees'   
+# 6 6     'IVb: Self-employed with no employees'
+# 7 7     'V: Manual Supervisors'               
+# 8 8     'VI: Skilled Worker'                  
+# 9 9     'VIIa: Unskilled Worker'              
+# 10 10    'VIIb: Farm Labor'                    
+# 11 11    'IVc: Self-employed Farmer'
+
+# iscotab %>% filter(ISCO08==2611) #I
+# iscotab %>% filter(ISCO08==1100) #I
+# iscotab %>% filter(ISCO08==1212) #I
+# 
+# iscotab %>% filter(ISCO08==2300) # II
+# iscotab %>% filter(ISCO08==5412) # VI/VI
+# iscotab %>% filter(ISCO08==2220) # II
+# 
+# iscotab %>% filter(ISCO08==7231) # VI
+# iscotab %>% filter(ISCO08==8331) # VII
+# iscotab %>% filter(ISCO08==5140) # VI
+# iscotab %>% filter(ISCO08==9111) # VII
+
 ```

### 2024-10-22 paper1_jiturra.Rmd
updates patrick v3

@@
   loggdppercapita,
-  wstate2,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
+  wstate2
   )
+
+names(dfreg1)
+varlab <- 
+c("Redistributive preferences","Class-based network homogeneity",
+  "Network size","Social class",
+  "Household Income","Education in years","Labor market status",
+  "Gender","Age in years","Has partner",
+  "Income Inequality - Gini Index",
+  "GDP/capita ",
+  "Size of the welfare state")
+
+sjlabelled::set_label(dfreg1) <- varlab
+# names(dfreg) <- varlab
+
+st(dfreg1,labels=T,
+   title="Descriptive Statistics for Study Variables",
+   out = "viewer",
+   digits = 2, 
+   factor.counts = F,
+   factor.numeric = F,
+   summ = list(
+     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
+     c('notNA(x)','mean(x)')
+   ),
+   summ.names = list(
+     c('N','Mean','SD','Min','Max'),
+     c('Count','Percent')   
+   ))
+
 ```

### 2025-05-07 999-oldcode/paper1_jiturra_supp-material.Rmd
simulaciones

--- 2024-07-18 paper1_jiturra_supp-material.Rmd
@@
 author:
-- name: Julio Iturra-Sanhueza
-  affiliation: Bremen International Graduate School of Social Sciences
-  email: jiturra@uni-bremen.de
+# - name: Julio Iturra-Sanhueza
+  # affiliation: Bremen International Graduate School of Social Sciences
+  # email: jiturra@uni-bremen.de
 #   number: 1
@@
 First, a (delete-one) jackknife procedure indicated that estimations for the segregation hypothesis are robust to outliers.
-Additonaly, Using dfbetas and Cook distance, there are influential cases.
+Additonaly, Using DFbetas and Cook distance, there are influential cases.
 Subsequently I see that in some cases the value is altered, but these changes are not significant.
@@
 for (i in countries) {
-  tidyresults[[i]] <- broom::tidy(results[[i]],conf.int=T)
+  tidyresults[[i]] <- broom.mixed::tidy(results[[i]],conf.int=T)
 }
@@
 
-```
-
-\pagebreak
-
-<!-- ## OECD Countries -->
-
-```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1) 
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------$
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
 ```
@@
 
+\pagebreak
+
+<!-- ## OECD Countries -->
+
+```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1) 
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
+       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
+### Predicted values homo*class*GiniD ---------------------------------------$
+# ginid_max<- round(max(dfreg$gini_disp) ,2)
+# ginid_min<- round(min(dfreg$gini_disp),2)
+
+ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
+ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
+ginid_mea<- round(mean(dfreg$gini_disp),2)
+
+df_pred_giniD_gc <-
+  predictions(
+    homo_V_gini_full2,newdata = datagrid(
+      gini_disp = c(ginid_min, ginid_mea, ginid_max),
+      wstate2=mean(dfreg$wstate2),
+      loggdppercapita=mean(dfreg$loggdppercapita),
+      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
+      dclass3res_V=levels(dfreg$dclass3res_V)
+    )
+  )
+
+df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
+df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
+df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
+
+df_pred_giniD_gc %>% 
+  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
+  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
+  geom_line(size=1,color="black") +
+  geom_point(size=3, shape = 21,color="black") +
+  facet_wrap(~gini_disp) +
+  labs(y = "Preferences for Redistribution",
+       x="Network homogeneity (CWC)",
+       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
+       ) +
+  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
+                     ) +
+
+   scale_fill_manual(values=c("#323232","#CCCCCC"))+
+  scale_color_manual(values=c("#323232","#CCCCCC"))+
+  theme(legend.position = "bottom",
+        legend.direction = "horizontal",
+        axis.text=element_text(size=15),
+        legend.title = element_blank(),
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black"))
+```
+
 <!-- # Additional analysis -->

### 2025-05-07 paper1_jiturra.Rmd
simulaciones

@@
 The implications for studying class-based networks and political attitudes are also discussed.
-#   | 
 #   | **Keywords**: social networks, segregation, social class, income inequality, redistributive preferences 
 output:
+  bookdown::html_document2:
+    toc: false
+    code_folding: hide
+    number_sections: false
+    toc_float:
+      collapsed: false
+      smooth_scroll: false
   bookdown::pdf_document2:
@@
       - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
-  bookdown::html_document2:
-    toc: false
-    code_folding: hide
-    number_sections: false
-    toc_float:
-      collapsed: false
-      smooth_scroll: false
   bookdown::word_document2:
@@
   - \usepackage{times}   # Times New Roman
-  # - \usepackage{helvet}
   - \usepackage{endnotes}
   - \let\footnote=\endnote 
-  # - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{caption}
@@
   scale_color_manual(values = c("black","#000000","#666666","#999999")) +
-  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; weighted descriptive statistics; figure report country averages in redistributive preferences by social class") +
+  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in redistributive preferences by social class") +
   theme(legend.position = "bottom",
@@
   scale_y_continuous(limits = c(0,0.7))+
-  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; weighted descriptive statistics; figure report country averages in network homogeneity by social class") +
+  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
   theme(legend.position = "bottom",
@@
   scale_y_continuous(limits = c(55,80))+
-  labs(caption = paste0("Source: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". Predictive estimates with 95% confidence intervals"),
+  labs(caption = paste0("Note: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". Predictive estimates with 95% confidence intervals"),
        x="Network homogeneity",y="Redistributive preferences (0 - 100)") +
@@
        x="Network homogeneity (CWC)",
-       caption = paste0("Source: N (Individuals) = ",nobs(homo_V_gini_full2),"; N (Countries) = ",lme4::ngrps(homo_V_gini_full2),
+       caption = paste0("Note: N (Individuals) = ",nobs(homo_V_gini_full2),"; N (Countries) = ",lme4::ngrps(homo_V_gini_full2),
                         ". Predictive estimates with 95% confidence intervals")) +
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 3:4,
-      "Homogeneity x Social Class"=5:6),
+      groups = list("Household Income (Ref.= Tertile I)"= 6:8,
+                    "Social Class (Ref.= Service Class)" = 11:12, 
+                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
+                    "Homogeneity x Social Class"=13:14),
       custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,

### 2025-05-07 supplementary_material.Rmd
simulaciones

--- 2025-05-07 999-oldcode/paper1_jiturra_supp-material.Rmd
@@
 # date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
-date: "`r format(Sys.Date(), '%d %B %Y')`"
+# date: "`r format(Sys.Date(), '%d %B %Y')`"
 author:
@@
 if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,influence.ME)
 knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
@@
 
+\makeatletter
+\renewcommand \thesection{S\@arabic\c@section}
+\renewcommand\thetable{S\@arabic\c@table}
+\renewcommand \thefigure{S\@arabic\c@figure}
+\makeatother
+
 \pagebreak
 
-# Supplementary material
-
-## Influential case analysis
-
-Several robustness checks were consistent with our main results.
-First, a (delete-one) jackknife procedure indicated that estimations for the segregation hypothesis are robust to outliers.
-Additonaly, Using DFbetas and Cook distance, there are influential cases.
-Subsequently I see that in some cases the value is altered, but these changes are not significant.
-Second, repeating the procedure with the models, including the cross-level interaction for the mitigation hypothesis, leads to relatively same results.
-
-```{r}
+# Income inequality ratios
+
+```{r tab-S1, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(d10d1))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+         
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/10)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income inequality (Ratio 90/10), Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+```{r tab-S2, results='asis', cache=TRUE}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  # starts_with("class3"),
+  # starts_with("digclass3"),
+  # starts_with("dclass3"),
+  # starts_with("homclass"),
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  # religion,
+  partner,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(wid_p90p50))
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+# Variable Group-Centering ------------------------------------------------$
+dfreg <- 
+  dfreg %>% 
+  mutate(to_dummy(female),
+         # to_dummy(union),
+         to_dummy(workst),
+         # dummy for categorical variables-------------------------------------$
+         to_dummy(Q03pcm),
+         # to_dummy(dclass3spo_V)
+  )
+dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
+# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
+dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
+dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
+dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
+dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
+# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
+dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
+dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
+# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
+dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
+
+# Household Income Tercile
+dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
+dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
+dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
+dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
+
+# Partner Social Class
+# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
+# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
+# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
+# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
+
+# drop dummies
+dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
+                                # union_1,union_2,
+                                workst_1,
+                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
+                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
+                                ))
+
+# dfreg$gini_disp <- scale(dfreg$gini_disp)
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+homo_V_gini <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_wstate2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_gdp_controls <-
+  lmer(egal~
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+homo_V_gini_full2 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         # socialtrust_gc+
+         dclass3res_V+
+         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
+         female_gc+agenum_gc+
+         # age2_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         # union_gc+
+         workst_gc+ 
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+digclas1_macro <- list(homo_V_gini,
+                       homo_V_gini_gdp,
+                       homo_V_gini_gdp_wstate2,
+                       homo_V_gini_full2)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Ratio 90/50)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
+
+texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
+       caption = "Multilevel models for Income inequality (Ratio 90/50), Network segregation and Redistributive Preferences",
+       custom.note = "Note: Models include individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,
+       custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
+       float.pos = "h!",
+      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Group (Intercept)",
+                           "Var: Group Homogeneity",
+                           "Var: Group Intermediate Class ",
+                           "Var: Group Working Class",
+                           "Cov: Group (Intercept), Homogeneity",
+                           "Cov: Group (Intercept), Intermediate Class ",
+                           "Cov: Group (Intercept), Working Class",
+                           "Cov: Group Homogeneity, Intermediate Class",
+                           "Cov: Group Homogeneity, Working Class",
+                           "Cov: Group Intermediate Class, Working Class",
+                           "Var: Residual"),
+       use.packages = F)
+```
+
+\pagebreak
+# Income inequality groups
+
+```{r tab-S3, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 # df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
+
+dfreg <- na.omit(dfreg)
+tab_countries<- 
+  dfreg %>% 
+  group_by(country3) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_q05=ntile(gini_disp,5),
+         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
+  arrange(gini_d10) %>% 
+  dplyr::select(-gini_disp)
+
+dfreg <- dfreg %>% left_join(tab_countries,by="country3")
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+
+library(estimatr)
+
+# Quintile 1 (low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 2 (mid-low)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
+digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 3 (middle)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 4 (middle-high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum + partner +  factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
+digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+# Quintile 5 (high)
+digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
+digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
+
+digclas1_Q05 <- 
+list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
+     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
+     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
+
+ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",
+              # socialtrust="Social Trust",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              # "femaleFemale"="Female (Ref. = Male)",
+              # "agenum"="Age",
+              # "age2"="Age2",
+              "edyears"="Year of Education",
+              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
+              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
+              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
+              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
+              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
+              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
+              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
+
+header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
+texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
+       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
+       custom.note = "Note: Gender, age and marital status are included as controls. Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,
+       custom.coef.map = ccoef,
+       symbol = "+",scalebox = 0.55,
+      groups = list("Social Class (Ref.= Service Class)" = 3:4, "Household Income (Ref.= Tertile I)"= 6:8,  
+                    # "Partner's Social Class (Ref.= Service Class)" = 12:14, 
+                    "Homogeneity x Social Class"=10:11),
+      custom.gof.rows = list("Country FE"=rep("Yes",10)),
+      # include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
+       float.pos = "h!",
+      # file = "table1.html"
+       use.packages = F)
+```
+
+```{r fig-S2, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditioned by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
+marginal <- bind_rows(
+plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
+plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
+plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
+plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
+plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
+marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
+marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
+
+ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
+  geom_point(size=2) + 
+  geom_errorbar(width=.2)+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
+  geom_hline(yintercept = 0,color="red") +
+  facet_grid(~quintile) +
+  labs(x=NULL,y="Redistributive preferences"
+       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
+       )
+
+```
+
+\pagebreak
+
+# Influential case analysis
+
+Several robustness checks were consistent with our main results.
+First, a (delete-one) jackknife procedure indicated that estimations for the segregation hypothesis are robust to outliers.
+Additonaly, Using DFbetas and Cook distance, there are influential cases.
+Subsequently I see that in some cases the value is altered, but these changes are not significant.
+Second, repeating the procedure with the models, including the cross-level interaction for the mitigation hypothesis, leads to relatively same results.
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  # dclass3spo_V,
+  homclass3_V_res,
+  know_total,
+  # socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  # religion,
+  # union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN")
+
+# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
 # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
@@
 countries<- levels(as.factor(dfreg$country2))
-subset(dfreg,country2!="AUT")
 
@@
 
-```{r byoneone-exclusion,fig.dim=c(10,10),fig.cap='Interaction of network homogeneity and social class on redistributive preferences. Excluding countries one by one.'}
+```{r fig-S1,fig.dim=c(10,10),fig.cap='Interaction of network homogeneity and social class on redistributive preferences. Excluding countries one by one.'}
 jk %>% filter(term %in% c("homclass3_V_res",
@@
 
-```{r fig.dim=c(5,5),fig.cap='Cook distance'}
+```{r eval=FALSE, fig.dim=c(5,5), include=FALSE}
 library(influence.ME)
@@
 
-knitreg(results[1:10])
-knitreg(results[11:20])
-knitreg(results[21:31])
+# texreg(results[1:10])
+# knitreg(results[11:20])
+# knitreg(results[21:31])
 
@@
 jk<- bind_rows(tidyresults, .id = "country");jk$country <-paste("Excluding",jk$country) 
-
 ```
 
-## Income inequality ratios
-
-```{r tab2-ratio9010, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(d10d1))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+         
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/10)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r tab2-ratio9050, results='asis', cache=TRUE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(wid_p90p50))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,
-                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Ratio 90/50)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-\pagebreak
-## Income inequality groups
-
-```{r table1-ineq-groups, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  # religion,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-tab_countries<- 
-  dfreg %>% 
-  group_by(country3) %>% 
-  summarise(gini_disp=mean(gini_disp)) %>% 
-  mutate(gini_q05=ntile(gini_disp,5),
-         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
-  arrange(gini_d10) %>% 
-  dplyr::select(-gini_disp)
-
-dfreg <- dfreg %>% left_join(tab_countries,by="country3")
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-
-library(estimatr)
-
-# Quintile 1 (low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
-digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 2 (mid-low)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
-digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
-digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 3 (middle)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
-digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 4 (middle-high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum + partner +  factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
-digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+edyears+ Q03pcm+workst)
-digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-# Quintile 5 (high)
-digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+female+agenum+ partner + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
-digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst)
-digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)
-
-digclas1_Q05 <- 
-list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
-     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
-     digclas1_VW_Q05_1,digclas1_VW_Q05_2)
-
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
-              know_total="Network size",
-              # socialtrust="Social Trust",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-              "edyears"="Year of Education",
-              "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-              "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class")
-
-header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
-texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
-       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
-       custom.note = "Note: Models include sampling weights. Gender, age and marital status are included as controls. Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,
-       custom.coef.map = ccoef,
-       symbol = "+",scalebox = 0.55,
-      groups = list("Social Class (Ref.= Service Class)" = 3:4, "Household Income (Ref.= Tertile I)"= 6:8,  
-                    # "Partner's Social Class (Ref.= Service Class)" = 12:14, 
-                    "Homogeneity x Social Class"=10:11),
-      custom.gof.rows = list("Country FE"=rep("Yes",10)),
-      # include.loglik = FALSE,include.aic = FALSE,
-      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
-       float.pos = "h!",
-      # file = "table1.html"
-       use.packages = F)
-```
-
-```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditioned by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
-marginal <- bind_rows(
-plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
-plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
-plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
-plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
-plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
-marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
-marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)
-
-ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
-  geom_point(size=2) + 
-  geom_errorbar(width=.2)+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
-  geom_hline(yintercept = 0,color="red") +
-  facet_grid(~quintile) +
-  labs(x=NULL,y="Redistributive preferences"
-       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
-       )
-
-```
-
-\pagebreak
-
-## Social Distance by ISEI
+# Network homogeneity by ISEI
 
@@
 
-```{r desc-social, eval=FALSE, include=FALSE}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,correlation)
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  dclass3spo_V,
-  homclass3_V_res=socdist,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  religion,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2,
-         homclass3_V_res=homclass3_V_res/10) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-```
-
-```{r table1-socdist, results='asis'}
+```{r tab-S4, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-ccoef <- list(homclass3_V_res="Social Distance /10",
+ccoef <- list(homclass3_V_res="ISEI-based network homogeneity/10",
               know_total="Network size",
@@
               # "dclass3spo_V" = "ISEI/10 (Partner)",
-              "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI")
+              "homclass3_V_res:dclass3res_V" = "Homogeneity*ISEI")
 
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),
-       caption = paste("(\\#tab:table2)","Multilevel models for Social Distance and Redistributive Preferences"),
-       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
+       caption = paste("(\\#tab:table2)","Multilevel models for ISEI-based network homogeneity and Redistributive Preferences"),
+       custom.note = "Note: Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,
@@
 
-```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditioned by ISEI on Redistributive Preferences',warning=FALSE}
+```{r fig-S3, fig.dim=c(10,5),fig.cap='Average Marginal Effects of ISEI-based network homogeneity conditioned by ISEI on Redistributive Preferences',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
 
-```{r fig1-pred-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Social Distance on Redistributive Preferences by ISEI',warning=FALSE}
+```{r fig-S4, fig.dim=c(10,5),fig.cap='Linear Predictions for ISEI-based network homogeneity on Redistributive Preferences by ISEI',warning=FALSE}
 int_homo <- digclas1_VW_7
@@
   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
-       x="Social distance",y="Redistributive preferences") +
+       x="ISEI-based network homogeneity",y="Redistributive preferences") +
   theme(legend.position = "bottom", legend.title = element_blank())
@@
 
-```{r tab2-socdist, results='asis', cache=TRUE}
+```{r tab-S5, results='asis', cache=TRUE}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-ccoef <- list(homclass3_V_gc="Social Distance (CWC)",
+ccoef <- list(homclass3_V_gc="ISEI-based network homogeneity (CWC)",
               "dclass3res_V"="ISEI ",
@@
               wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_V" = "Distance*ISEI",
-              "homclass3_V_gc:gini_disp"= "Distance*Income Inequality",
+              "homclass3_V_gc:dclass3res_V" = "Homogeneity*ISEI",
+              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
               "dclass3res_V:gini_disp" ="ISEI*Inequality",
-              "homclass3_V_gc:dclass3res_V:gini_disp" = "Distance*Working Class*Income Inequality")
+              "homclass3_V_gc:dclass3res_V:gini_disp" = "Homogeneity*Working Class*Income Inequality")
 
 texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Social Distance and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
+       caption = "Multilevel models for Income Inequality, Network homogeneity and Redistributive Preferences",
+       custom.note = "Note: Models include individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
        caption.above = T,leading.zero = T,single.row = T,
@@
                            "Var: Group (Intercept)",
-                           "Var: Group Soc. Distance",
+                           "Var: Group Homogeneity",
                            "Var: Group ISEI",
-                           "Cov: Group (Intercept), Soc. Distance",
+                           "Cov: Group (Intercept), Homogeneity",
                            "Cov: Group (Intercept), ISEI",                           
-                           "Cov: Group Soc. Distance, ISEI",
+                           "Cov: Group Homogeneity, ISEI",
                            "Var: Residual"),
@@
 
-```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'}
+```{r fig-S5, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, ISEI-based network homogeneity, ISEI and Income Inequality'}
 ### Predicted values homo*class*GiniD ---------------------------------------$
@@
   labs(y = "Preferences for Redistribution",
-       x="Social Distance (CWC)",
+       x="ISEI-based network homogeneity (CWC)",
        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
@@
 
-```{r table1-alternative, eval=FALSE, include=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V=dclass6res,
-  # homclass3_V_res=homclass3_V_res_part,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  # religion,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-# dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-# df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-# sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV)
-
-dfreg <- na.omit(dfreg)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_2<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_3<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_4<- lmer(egal~1 + homclass3_V_res + female+agenum+ partner +  know_total + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_6<- lmer(egal~1 + homclass3_V_res + female+agenum+ 
-                       partner +  know_total +   
-                       dclass3res_V + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_7<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +   know_total +  
-                       dclass3res_V +  edyears + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_8<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm +(1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_9<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total +  
-                       dclass3res_V +  edyears +  Q03pcm + workst +(1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_10<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm + workst + (1|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_10a<- lmer(egal~1 + homclass3_V_res + female+agenum+
-                       partner +  know_total + 
-                       dclass3res_V +  edyears +  Q03pcm + workst + (homclass3_V_res|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_VW_11 <- update(digclas1_VW_10, . ~ . +dclass3res_V*homclass3_V_res)
-
-digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2,digclas1_VW_3,digclas1_VW_4,
-                    digclas1_VW_6,digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,digclas1_VW_10a,
-                    digclas1_VW_11)
-
-screenreg(digclas1_VW)
-plot_slopes(digclas1_VW_11, variables = "homclass3_V_res", by = "dclass3res_V",draw = T)
-```
-
-\pagebreak
-
-<!-- ## OECD Countries -->
-
-```{r tab2-ocde, eval=FALSE, cache=TRUE, include=FALSE, results='asis'}
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1) 
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
-dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
-  egal = egal2,
-  # starts_with("class3"),
-  # starts_with("digclass3"),
-  # starts_with("dclass3"),
-  # starts_with("homclass"),
-  dclass3res_V,
-  # dclass3spo_V,
-  homclass3_V_res,
-  know_total,
-  # socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  # religion,
-  partner,
-  # union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  filter(oecd == "OECD") %>%
-  filter(country2 != "SVN") %>% 
-  na.omit() %>% 
-    mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
-
-dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
-
-# Variable Group-Centering ------------------------------------------------$
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         # to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------$
-         to_dummy(Q03pcm),
-         # to_dummy(dclass3spo_V)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-# dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
-dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
-dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
-dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
-dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
-# dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2)
-dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
-dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
-# dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2)
-dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)
-
-# Household Income Tercile
-dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
-dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
-dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
-dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)
-
-# Partner Social Class
-# dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2)
-# dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2)
-# dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2)
-# dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2)
-
-# drop dummies
-dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
-                                # union_1,union_2,
-                                workst_1,workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
-                                # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4
-                                ))
-
-# dfreg$gini_disp <- scale(dfreg$gini_disp)
-
-## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_wstate2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_gdp_controls <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2 +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-homo_V_gini_full2 <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         # socialtrust_gc+
-         dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
-         female_gc+agenum_gc+
-         # age2_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
-         workst_gc+ 
-         gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-digclas1_macro <- list(homo_V_gini,
-                       homo_V_gini_gdp,
-                       homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
-
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "gini_disp" = "Income inequality (Gini index)",
-              loggdppercapita = "GDP/capita",
-              wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
-              "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality")
-
-texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
-       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences",
-       custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars",
-       caption.above = T,leading.zero = T,single.row = T,
-       custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11),
-       float.pos = "h!",
-      custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE,
-      custom.gof.names = c(NA,NA,"Num. groups",
-                           "Var: Group (Intercept)",
-                           "Var: Group Homogeneity",
-                           "Var: Group Intermediate Class ",
-                           "Var: Group Working Class",
-                           "Cov: Group (Intercept), Homogeneity",
-                           "Cov: Group (Intercept), Intermediate Class ",
-                           "Cov: Group (Intercept), Working Class",
-                           "Cov: Group Homogeneity, Intermediate Class",
-                           "Cov: Group Homogeneity, Working Class",
-                           "Cov: Group Intermediate Class, Working Class",
-                           "Var: Residual"),
-       use.packages = F)
-```
-
-```{r fig5-ocde, eval = FALSE,include = FALSE,fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'}
-### Predicted values homo*class*GiniD ---------------------------------------$
-# ginid_max<- round(max(dfreg$gini_disp) ,2)
-# ginid_min<- round(min(dfreg$gini_disp),2)
-
-ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
-ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
-ginid_mea<- round(mean(dfreg$gini_disp),2)
-
-df_pred_giniD_gc <-
-  predictions(
-    homo_V_gini_full2,newdata = datagrid(
-      gini_disp = c(ginid_min, ginid_mea, ginid_max),
-      wstate2=mean(dfreg$wstate2),
-      loggdppercapita=mean(dfreg$loggdppercapita),
-      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
-      dclass3res_V=levels(dfreg$dclass3res_V)
-    )
-  )
-
-df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
-df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
-df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")
-
-df_pred_giniD_gc %>% 
-  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
-  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
-  geom_line(size=1,color="black") +
-  geom_point(size=3, shape = 21,color="black") +
-  facet_wrap(~gini_disp) +
-  labs(y = "Preferences for Redistribution",
-       x="Network homogeneity (CWC)",
-       caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2))
-       ) +
-  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
-                     ) +
-
-   scale_fill_manual(values=c("#323232","#CCCCCC"))+
-  scale_color_manual(values=c("#323232","#CCCCCC"))+
-  theme(legend.position = "bottom",
-        legend.direction = "horizontal",
-        axis.text=element_text(size=15),
-        legend.title = element_blank(),
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black"))
-```
-
-<!-- # Additional analysis -->
-
-<!-- ## OECD Countries -->
-
-<!-- ```{r tab2-ocde, results='asis', cache=TRUE} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-<!-- options(scipen=999) -->
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
-<!-- rm(list=ls()) -->
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   # starts_with("class3"), -->
-<!--   # starts_with("digclass3"), -->
-<!--   # starts_with("dclass3"), -->
-<!--   # starts_with("homclass"), -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   religion, -->
-<!--   partner, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   abs_red, -->
-<!--   ilo_taxrev, -->
-<!--   ilo_govspe, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   na.omit() %>%  -->
-<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2,  -->
-<!--          gini_disp=scale(gini_disp)) -->
-
-<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
-
-<!-- # Variable Group-Centering ------------------------------------------------ -->
-<!-- dfreg <-  -->
-<!--   dfreg %>%  -->
-<!--   mutate(to_dummy(female), -->
-<!--          to_dummy(union), -->
-<!--          to_dummy(workst), -->
-<!--          # dummy for categorical variables------------------------------------- -->
-<!--          to_dummy(Q03pcm), -->
-<!--          to_dummy(dclass3spo_V) -->
-<!--   ) -->
-<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
-<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
-<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
-<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
-<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
-<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
-<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
-<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
-<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
-<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
-<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
-
-<!-- # Household Income Tercile -->
-<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
-
-<!-- # Partner Social Class -->
-<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
-
-<!-- # drop dummies -->
-<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
-<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
-<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
-
-<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- homo_V_gini <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_wstate2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_controls <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2 + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_full2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          homclass3_V_gc* -->
-<!--          dclass3res_V* -->
-<!--          gini_disp +  -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- digclas1_macro <- list(homo_V_gini, -->
-<!--                        homo_V_gini_gdp, -->
-<!--                        homo_V_gini_gdp_wstate2, -->
-<!--                        homo_V_gini_full2) -->
-
-<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
-<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               "gini_disp" = "Income inequality (Gini index)", -->
-<!--               loggdppercapita = "GDP/capita", -->
-<!--               wstate2="Size of the welfare state", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
-<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
-
-<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
-<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
-<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T,single.row = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
-<!--        float.pos = "h!", -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
-<!--                            "Var: Group (Intercept)", -->
-<!--                            "Var: Group Homogeneity", -->
-<!--                            "Var: Group Intermediate Class ", -->
-<!--                            "Var: Group Working Class", -->
-<!--                            "Cov: Group (Intercept), Homogeneity", -->
-<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
-<!--                            "Cov: Group (Intercept), Working Class", -->
-<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
-<!--                            "Cov: Group Homogeneity, Working Class", -->
-<!--                            "Cov: Group Intermediate Class, Working Class", -->
-<!--                            "Var: Residual"), -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r fig5-ocde, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Network segregation, Social class and Income Inequality'} -->
-<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
-<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
-<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
-
-<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
-<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
-<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
-
-<!-- df_pred_giniD_gc <- -->
-<!--   predictions( -->
-<!--     homo_V_gini_full2,newdata = datagrid( -->
-<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
-<!--       wstate2=mean(dfreg$wstate2), -->
-<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
-<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1), -->
-<!--       dclass3res_V=levels(dfreg$dclass3res_V) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
-<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
-<!-- df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
-
-<!-- df_pred_giniD_gc %>%  -->
-<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
-<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
-<!--   geom_line(size=1,color="black") + -->
-<!--   geom_point(size=3, shape = 21,color="black") + -->
-<!--   facet_wrap(~gini_disp) + -->
-<!--   labs(y = "Preferences for Redistribution", -->
-<!--        x="Network homogeneity (CWC)", -->
-<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
-<!--        ) + -->
-<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
-<!--                      ) + -->
-
-<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   theme(legend.position = "bottom", -->
-<!--         legend.direction = "horizontal", -->
-<!--         axis.text=element_text(size=15), -->
-<!--         legend.title = element_blank(), -->
-<!--         legend.background = element_blank(), -->
-<!--         legend.box.background = element_rect(colour = "black")) -->
-<!-- ``` -->
-
-<!-- ## Income Inequality Ratios (OECD) -->
-
-<!-- ```{r tab2-ratio9010, results='asis', cache=TRUE} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-<!-- options(scipen=999) -->
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   # starts_with("class3"), -->
-<!--   # starts_with("digclass3"), -->
-<!--   # starts_with("dclass3"), -->
-<!--   # starts_with("homclass"), -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   religion, -->
-<!--   partner, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   abs_red, -->
-<!--   ilo_taxrev, -->
-<!--   ilo_govspe, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   na.omit() %>%  -->
-<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2,  -->
-<!--          gini_disp=scale(d10d1)) -->
-
-<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
-
-<!-- # Variable Group-Centering ------------------------------------------------ -->
-<!-- dfreg <-  -->
-<!--   dfreg %>%  -->
-<!--   mutate(to_dummy(female), -->
-<!--          to_dummy(union), -->
-<!--          to_dummy(workst), -->
-<!--          # dummy for categorical variables------------------------------------- -->
-<!--          to_dummy(Q03pcm), -->
-<!--          to_dummy(dclass3spo_V) -->
-<!--   ) -->
-<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
-<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
-<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
-<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
-<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
-<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
-<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
-<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
-<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
-<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
-<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
-
-<!-- # Household Income Tercile -->
-<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
-
-<!-- # Partner Social Class -->
-<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
-
-<!-- # drop dummies -->
-<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
-<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
-<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
-
-<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- homo_V_gini <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_wstate2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_controls <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2 + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_full2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          homclass3_V_gc* -->
-<!--          dclass3res_V* -->
-<!--          gini_disp +  -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- digclas1_macro <- list(homo_V_gini, -->
-<!--                        homo_V_gini_gdp, -->
-<!--                        homo_V_gini_gdp_wstate2, -->
-<!--                        homo_V_gini_full2) -->
-
-<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
-<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               "gini_disp" = "Income inequality (Ratio 90/10)", -->
-<!--               loggdppercapita = "GDP/capita", -->
-<!--               wstate2="Size of the welfare state", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
-<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
-
-<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50, -->
-<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
-<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T,single.row = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
-<!--        float.pos = "h!", -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
-<!--                            "Var: Group (Intercept)", -->
-<!--                            "Var: Group Homogeneity", -->
-<!--                            "Var: Group Intermediate Class ", -->
-<!--                            "Var: Group Working Class", -->
-<!--                            "Cov: Group (Intercept), Homogeneity", -->
-<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
-<!--                            "Cov: Group (Intercept), Working Class", -->
-<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
-<!--                            "Cov: Group Homogeneity, Working Class", -->
-<!--                            "Cov: Group Intermediate Class, Working Class", -->
-<!--                            "Var: Residual"), -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r tab2-ratio9050, results='asis', cache=TRUE} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-<!-- options(scipen=999) -->
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   # starts_with("class3"), -->
-<!--   # starts_with("digclass3"), -->
-<!--   # starts_with("dclass3"), -->
-<!--   # starts_with("homclass"), -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   religion, -->
-<!--   partner, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   abs_red, -->
-<!--   ilo_taxrev, -->
-<!--   ilo_govspe, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   na.omit() %>%  -->
-<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2,  -->
-<!--          gini_disp=scale(wid_p90p50)) -->
-
-<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
-
-<!-- # Variable Group-Centering ------------------------------------------------ -->
-<!-- dfreg <-  -->
-<!--   dfreg %>%  -->
-<!--   mutate(to_dummy(female), -->
-<!--          to_dummy(union), -->
-<!--          to_dummy(workst), -->
-<!--          # dummy for categorical variables------------------------------------- -->
-<!--          to_dummy(Q03pcm), -->
-<!--          to_dummy(dclass3spo_V) -->
-<!--   ) -->
-<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
-<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
-<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
-<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
-<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
-<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
-<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
-<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
-<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
-<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
-<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
-
-<!-- # Household Income Tercile -->
-<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
-
-<!-- # Partner Social Class -->
-<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
-
-<!-- # drop dummies -->
-<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
-<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
-<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
-
-<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- homo_V_gini <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_wstate2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_controls <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2 + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_full2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          homclass3_V_gc* -->
-<!--          dclass3res_V* -->
-<!--          gini_disp +  -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- digclas1_macro <- list(homo_V_gini, -->
-<!--                        homo_V_gini_gdp, -->
-<!--                        homo_V_gini_gdp_wstate2, -->
-<!--                        homo_V_gini_full2) -->
-
-<!-- ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)", -->
-<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               "gini_disp" = "Income inequality (Ratio 90/50)", -->
-<!--               loggdppercapita = "GDP/capita", -->
-<!--               wstate2="Size of the welfare state", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class", -->
-<!--               "homclass3_V_gc:gini_disp"= "Homogeneity*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class *Income Inequality") -->
-
-<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.50, -->
-<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
-<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T,single.row = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity*Social Class"=7:8, "Homogeneity * Social Class * Income Inequality"=10:11), -->
-<!--        float.pos = "h!", -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
-<!--                            "Var: Group (Intercept)", -->
-<!--                            "Var: Group Homogeneity", -->
-<!--                            "Var: Group Intermediate Class ", -->
-<!--                            "Var: Group Working Class", -->
-<!--                            "Cov: Group (Intercept), Homogeneity", -->
-<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
-<!--                            "Cov: Group (Intercept), Working Class", -->
-<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
-<!--                            "Cov: Group Homogeneity, Working Class", -->
-<!--                            "Cov: Group Intermediate Class, Working Class", -->
-<!--                            "Var: Residual"), -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- \pagebreak -->
-
-<!-- ## Social distance (OECD) -->
-
-<!-- ```{r desc-socdist,eval=FALSE, include=FALSE} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,correlation) -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res=socdist, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   partner, -->
-<!--   religion, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   mutate(logrgdpna = log(rgdpna), -->
-<!--          loggdppercapita=log(gdppercapita), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2, -->
-<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") -->
-
-<!-- dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV) -->
-
-<!-- dfreg <- na.omit(dfreg) -->
-<!-- ``` -->
-
-<!-- ### Social Distance by Social Class -->
-
-<!-- ```{r table1-socdistclass, echo=FALSE, results='asis'} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res=socdist, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   partner, -->
-<!--   religion, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   mutate(logrgdpna = log(rgdpna), -->
-<!--          loggdppercapita=log(gdppercapita), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2, -->
-<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") -->
-
-<!-- dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- # sjPlot::tab_xtab(df1$dclass3spo_V,df1$PARTLIV) -->
-
-<!-- dfreg <- na.omit(dfreg) -->
-
-<!-- # Step 1: Calculate absolute values -->
-<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
-<!-- # hist(absolute_values);summary(absolute_values) -->
-
-<!-- # Step 2: Add 1 to all values to eliminate zeros -->
-<!-- modified_values <- absolute_values + 0.1 -->
-<!-- # hist(modified_values);summary(modified_values) -->
-
-<!-- # Step 3: Reverse the order of the scale -->
-<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
-<!-- dfreg$homclass3_V_res <- reversed_values -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT) -->
-<!-- digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust) -->
-<!-- digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V) -->
-
-<!-- digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2) -->
-<!-- digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union) -->
-<!-- digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V) -->
-<!-- digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res) -->
-<!-- digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2, -->
-<!--                     digclas1_VW_3, -->
-<!--                     # digclas1_VW_4, -->
-<!--                     digclas1_VW_5,digclas1_VW_6,digclas1_VW_7) -->
-
-<!-- ccoef <- list(homclass3_V_res="Social distance", -->
-<!--               know_total="Network size", -->
-<!--               socialtrust="Social Trust", -->
-<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               # "femaleFemale"="Female (Ref. = Male)", -->
-<!--               # "agenum"="Age", -->
-<!--               # "age2"="Age2", -->
-<!--               "edyears"="Year of Education", -->
-<!--               "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)", -->
-<!--               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)", -->
-<!--               "unionYes" ="Union Membership (Ref. = Not Unionized)", -->
-<!--               "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)", -->
-<!--               "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)", -->
-<!--               "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)", -->
-<!--               "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class", -->
-<!--               "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class") -->
-
-<!-- texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1), -->
-<!--        caption = paste("(\\#tab:table2)","Multilevel models for Social distance and Redistributive Preferences"), -->
-<!--        custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--        symbol = "+",scalebox = 0.60, -->
-<!--       groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Social distance x Social Class"=15:16), -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"), -->
-<!--        float.pos = "h!", -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r fig1-marg-socdistclass, echo=FALSE, fig.cap='Average Marginal Effects of Social Distance conditionated by Social Class on Redistributive Preferences', fig.dim=c(10,5), warning=FALSE} -->
-<!-- int_homo <- digclas1_VW_7 -->
-<!-- plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V"))+ -->
-<!-- labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
-<!--        x="Social Distance",y="Redistributive preferences") -->
-<!-- ``` -->
-
-<!-- ```{r fig1-pred-socdistclass, echo=FALSE, fig.cap='Linear Predictions for Social distance on Redistributive Preferences by Social Class', fig.dim=c(10,5), warning=FALSE} -->
-<!-- int_homo <- digclas1_VW_7 -->
-<!-- df_pred1 <- -->
-<!--   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"), -->
-<!--               newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 1), -->
-<!--                                  dclass3res_V = levels(dfreg$dclass3res_V))) -->
-<!-- # names(df_pred1) -->
-<!-- df_pred1 %>% -->
-<!-- ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
-<!--   geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") + -->
-<!--   geom_line(size=1,color="black") + -->
-<!--   geom_point(size=2,color="black") + -->
-<!--   facet_grid(~factor(dclass3res_V, levels= -->
-<!--                        c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"), -->
-<!--                      c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) + -->
-<!--   scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
-<!--   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
-<!--   scale_y_continuous(limits = c(50,100))+ -->
-<!--   # scale_x_continuous(limits = c(-9,9))+ -->
-<!--   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
-<!--        x="Social Distance",y="Redistributive preferences") + -->
-<!--   theme(legend.position = "none", legend.title = element_blank()) -->
-<!-- ``` -->
-
-<!-- \pagebreak -->
-
-<!-- ```{r tab2-socdistclass, echo=FALSE, cache=TRUE, results='asis'} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-<!-- options(scipen=999) -->
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4) -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- dfreg <- df1 %>% dplyr::select( -->
-<!--   egal = egal2, -->
-<!--   # starts_with("class3"), -->
-<!--   # starts_with("digclass3"), -->
-<!--   # starts_with("dclass3"), -->
-<!--   # starts_with("homclass"), -->
-<!--   dclass3res_V, -->
-<!--   dclass3spo_V, -->
-<!--   homclass3_V_res=socdist, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   religion, -->
-<!--   partner, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   abs_red, -->
-<!--   ilo_taxrev, -->
-<!--   ilo_govspe, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") %>% -->
-<!--   na.omit() %>% -->
-<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2, -->
-<!--          gini_disp=scale(gini_disp), -->
-<!--          homclass3_V_res=homclass3_V_res/10) -->
-
-<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
-<!-- # Step 1: Calculate absolute values -->
-<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
-<!-- # hist(absolute_values);summary(absolute_values) -->
-
-<!-- # Step 2: Add 1 to all values to eliminate zeros -->
-<!-- modified_values <- absolute_values + 0.1 -->
-<!-- # hist(modified_values);summary(modified_values) -->
-
-<!-- # Step 3: Reverse the order of the scale -->
-<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
-<!-- dfreg$homclass3_V_res <- reversed_values -->
-
-<!-- # Variable Group-Centering ------------------------------------------------ -->
-<!-- dfreg <- -->
-<!--   dfreg %>% -->
-<!--   mutate(to_dummy(female), -->
-<!--          to_dummy(union), -->
-<!--          to_dummy(workst), -->
-<!--          # dummy for categorical variables------------------------------------- -->
-<!--          to_dummy(Q03pcm), -->
-<!--          to_dummy(dclass3spo_V) -->
-<!--   ) -->
-<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
-<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
-<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
-<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
-<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
-<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
-<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
-<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
-<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
-<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
-<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
-
-<!-- # Household Income Tercile -->
-<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
-
-<!-- # Partner Social Class -->
-<!-- dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
-
-<!-- # drop dummies -->
-<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
-<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
-<!--                                 dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4)) -->
-
-<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- homo_V_gini <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_wstate2 <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_controls <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2 + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_full2 <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          homclass3_V_gc* -->
-<!--          dclass3res_V* -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- digclas1_macro <- list(homo_V_gini, -->
-<!--                        homo_V_gini_gdp, -->
-<!--                        homo_V_gini_gdp_wstate2, -->
-<!--                        homo_V_gini_full2) -->
-
-<!-- ccoef <- list(homclass3_V_gc="Social distance (CWC)", -->
-<!--               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               "gini_disp" = "Income inequality (Gini index)", -->
-<!--               loggdppercapita = "GDP/capita", -->
-<!--               wstate2="Size of the welfare state", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Distance*Intermediate Class", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Distance*Working Class", -->
-<!--               "homclass3_V_gc:gini_disp"= "Distance*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Distance*Intermediate Class*Income Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Distance*Working Class*Income Inequality") -->
-
-<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
-<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
-<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T,single.row = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--       groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance x Social Class"=7:8, "Distance * Social Class x Income Inequality"=10:11), -->
-<!--        float.pos = "h!", -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
-<!--                            "Var: Group (Intercept)", -->
-<!--                            "Var: Group Homogeneity", -->
-<!--                            "Var: Group Intermediate Class ", -->
-<!--                            "Var: Group Working Class", -->
-<!--                            "Cov: Group (Intercept), Homogeneity", -->
-<!--                            "Cov: Group (Intercept), Intermediate Class ", -->
-<!--                            "Cov: Group (Intercept), Working Class", -->
-<!--                            "Cov: Group Homogeneity, Intermediate Class", -->
-<!--                            "Cov: Group Homogeneity, Working Class", -->
-<!--                            "Cov: Group Intermediate Class, Working Class", -->
-<!--                            "Var: Residual"), -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r fig5-socdistclass, echo=FALSE, fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)} -->
-<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
-<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
-<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
-
-<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
-<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
-<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
-
-<!-- df_pred_giniD_gc <- -->
-<!--   predictions( -->
-<!--     homo_V_gini_full2,newdata = datagrid( -->
-<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
-<!--       wstate2=mean(dfreg$wstate2), -->
-<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
-<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5), -->
-<!--       dclass3res_V=levels(dfreg$dclass3res_V) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
-<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
-<!-- df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
-
-<!-- df_pred_giniD_gc %>% -->
-<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
-<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
-<!--   geom_line(size=1,color="black") + -->
-<!--   geom_point(size=3, shape = 21,color="black") + -->
-<!--   facet_wrap(~gini_disp) + -->
-<!--   labs(y = "Preferences for Redistribution", -->
-<!--        x="Social Distance (CWC)", -->
-<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
-<!--        ) + -->
-<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
-<!--                      ) + -->
-
-<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   theme(legend.position = "bottom", -->
-<!--         legend.direction = "horizontal", -->
-<!--         axis.text=element_text(size=15), -->
-<!--         legend.title = element_blank(), -->
-<!--         legend.background = element_blank(), -->
-<!--         legend.box.background = element_rect(colour = "black")) -->
-<!-- ``` -->
-
-<!-- \pagebreak -->
-
-<!-- ### Social Distance by ISEI  -->
-
-<!-- ```{r table1-socdist, results='asis'} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-
-<!-- dummy_df <- df1 %>% dplyr::select(id, -->
-<!--   egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust, -->
-<!--   Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region, -->
-<!--   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev, -->
-<!--   ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita, -->
-<!--   oecd,country2, country, country3) %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   na.omit() %>%  -->
-<!--   dplyr::select(id) -->
-
-<!-- df1$isei08sp <- car::recode(df1$isei08sp,"NA=0") -->
-<!-- df1$isei08 <- car::recode(df1$isei08,"NA=0") -->
-
-<!-- dfreg <- df1 %>% dplyr::select(id, -->
-<!--   egal = egal2, -->
-<!--   dclass3res_V=isei08, -->
-<!--   dclass3spo_V=isei08sp, -->
-<!--   homclass3_V_res=socdist, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   partner, -->
-<!--   religion, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   mutate(logrgdpna = log(rgdpna), -->
-<!--          loggdppercapita=log(gdppercapita), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2, -->
-<!--          dclass3res_V=dclass3res_V/10, -->
-<!--          dclass3spo_V=dclass3spo_V/10, -->
-<!--          homclass3_V_res=homclass3_V_res/10) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN")  %>%  -->
-<!--   filter(id %in% dummy_df$id) -->
-<!-- dfreg <- na.omit(dfreg) -->
-<!-- # Step 1: Calculate absolute values -->
-<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
-<!-- # hist(absolute_values);summary(absolute_values) -->
-
-<!-- # Step 2: Add 1 to all values to eliminate zeros -->
-<!-- modified_values <- absolute_values + 0.1 -->
-<!-- # hist(modified_values);summary(modified_values) -->
-
-<!-- # Step 3: Reverse the order of the scale -->
-<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
-
-<!-- dfreg$homclass3_V_res <- reversed_values -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- digclas1_VW_1<- lmer(egal~1 + homclass3_V_res + female+agenum+age2 + partner + religion + (1|country2),data=dfreg,weights = WEIGHT) -->
-<!-- digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total+socialtrust) -->
-<!-- digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V) -->
-
-<!-- digclas1_VW_4 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2) -->
-<!-- digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union) -->
-<!-- digclas1_VW_6 <- update(digclas1_VW_3, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V) -->
-<!-- digclas1_VW_7 <- update(digclas1_VW_6, . ~ . +dclass3res_V*homclass3_V_res) -->
-<!-- digclas1_VW <- list(digclas1_VW_1,digclas1_VW_2, -->
-<!--                     digclas1_VW_3, -->
-<!--                     # digclas1_VW_4, -->
-<!--                     digclas1_VW_5,digclas1_VW_6,digclas1_VW_7) -->
-
-<!-- ccoef <- list(homclass3_V_res="Social Distance /10", -->
-<!--               know_total="Network size", -->
-<!--               socialtrust="Social Trust", -->
-<!--               # "dclass3res_VIntermediate class (III+IV)"="Intermediate Class", -->
-<!--               # "dclass3res_VWorking Class (V+VI+VII)"="Working Class", -->
-<!--               # "femaleFemale"="Female (Ref. = Male)", -->
-<!--               # "agenum"="Age", -->
-<!--               # "age2"="Age2", -->
-<!--               "dclass3res_V"="ISEI/10", -->
-<!--               "edyears"="Year of Education", -->
-<!--               "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)", -->
-<!--               "workstNot in paid work" = "Not in paid work (Ref. = In paid work)", -->
-<!--               "unionYes" ="Union Membership (Ref. = Not Unionized)", -->
-<!--               "dclass3spo_V" = "ISEI/10 (Partner)", -->
-<!--               "homclass3_V_res:dclass3res_V" = "Social Distance*ISEI") -->
-
-<!-- texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1), -->
-<!--        caption = paste("(\\#tab:table2)","Multilevel models for Social Distance and Redistributive Preferences"), -->
-<!--        custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--        symbol = "+",scalebox = 0.60, -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",6)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"), -->
-<!--        float.pos = "h!", -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r fig1-marg-socdist, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Social Distance conditionated by ISEI on Redistributive Preferences',warning=FALSE} -->
-<!-- int_homo <- digclas1_VW_7 -->
-<!-- plot_slopes(digclas1_VW_7, variables = "homclass3_V_res", condition = list("dclass3res_V" = "threenum"))+ -->
-<!-- labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
-<!--        x="ISEI",y="Redistributive preferences") -->
-<!-- ``` -->
-
-<!-- ```{r fig1-pred-socdist, fig.dim=c(10,5),fig.cap='Linear Predictions for Social Distance on Redistributive Preferences by ISEI',warning=FALSE} -->
-<!-- int_homo <- digclas1_VW_7 -->
-<!-- df_pred1 <-  -->
-<!--   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"), -->
-<!--               newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.5), -->
-<!--                                  dclass3res_V = c(min(dfreg$dclass3res_V),mean(dfreg$dclass3res_V),max(dfreg$dclass3res_V)))) -->
-
-<!-- df_pred1$dclass3res_V <- factor(df_pred1$dclass3res_V,labels = c("ISEI (min)","ISEI (Mean)", "ISEI (max)")) -->
-
-<!-- # names(df_pred1) -->
-<!-- df_pred1 %>%  -->
-<!-- ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
-<!--   geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") + -->
-<!--   geom_line(size=1,color="black") + -->
-<!--   geom_point(size=2,color="black") + -->
-<!--   # facet_grid(~dclass3res_V) + -->
-<!--   scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
-<!--   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+ -->
-<!--   scale_y_continuous(limits = c(40,100))+ -->
-<!--   labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)), -->
-<!--        x="Social distance",y="Redistributive preferences") + -->
-<!--   theme(legend.position = "bottom", legend.title = element_blank()) -->
-<!-- ``` -->
-
-<!-- \pagebreak -->
-
-<!-- ```{r tab2-socdist, results='asis', cache=TRUE} -->
-<!-- set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1") -->
-<!-- options(ggplot2.discrete.fill = set1) -->
-<!-- options(ggplot2.discrete.colour = set1) -->
-<!-- ggplot2::theme_set(ggplot2::theme_bw()) -->
-<!-- ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif")) -->
-<!-- options(scipen=999) -->
-<!-- if (!require("pacman")) install.packages("pacman") -->
-<!-- pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)   -->
-<!-- rm(list=ls()) -->
-
-<!-- load(here::here("input/data/proc/study1_country.RData"));df1 <- df2 -->
-
-<!-- df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)")) -->
-<!-- dummy_df <- df1 %>% dplyr::select(id, -->
-<!--   egal = egal2,dclass3res_V,dclass3spo_V,homclass3_V_res,know_total,socialtrust, -->
-<!--   Q03pcm,edyears,female,agenum,religion,partner,union,workst,WEIGHT,region, -->
-<!--   "gini_disp"=wid_gini_disp,"gini_mkt",gv_spen,rel_red,abs_red,ilo_taxrev, -->
-<!--   ilo_govspe,d10d1=wid_p90p10,wid_p90p50,top10=wid_sharetop10,rgdpna,gdppercapita, -->
-<!--   oecd,country2, country, country3) %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   na.omit() %>%  -->
-<!--   dplyr::select(id) -->
-
-<!-- df1$isei08sp <- car::recode(df1$isei08sp,"NA=0") -->
-<!-- dfreg <- df1 %>% dplyr::select(id, -->
-<!--   egal = egal2, -->
-<!--   # starts_with("class3"), -->
-<!--   # starts_with("digclass3"), -->
-<!--   # starts_with("dclass3"), -->
-<!--   # starts_with("homclass"), -->
-<!--   dclass3res_V=isei08, -->
-<!--   dclass3spo_V=isei08sp, -->
-<!--   homclass3_V_res=socdist, -->
-<!--   know_total, -->
-<!--   socialtrust, -->
-<!--   Q03pcm, -->
-<!--   edyears, -->
-<!--   female, -->
-<!--   agenum, -->
-<!--   religion, -->
-<!--   partner, -->
-<!--   union, -->
-<!--   workst, -->
-<!--   WEIGHT, -->
-<!--   region, -->
-<!--   "gini_disp"=wid_gini_disp, -->
-<!--   "gini_mkt", -->
-<!--   gv_spen, -->
-<!--   rel_red, -->
-<!--   abs_red, -->
-<!--   ilo_taxrev, -->
-<!--   ilo_govspe, -->
-<!--   d10d1=wid_p90p10, -->
-<!--   wid_p90p50, -->
-<!--   top10=wid_sharetop10, -->
-<!--   rgdpna, -->
-<!--   gdppercapita, -->
-<!--   oecd, -->
-<!--   country2, country, country3, -->
-<!-- ) %>% -->
-<!--   filter(oecd == "OECD") %>% -->
-<!--   filter(country2 != "SVN") %>%  -->
-<!--   na.omit() %>%  -->
-<!--     mutate(loggdppercapita=scale(gdppercapita/1000), -->
-<!--          edyears2 = edyears ^ 2, -->
-<!--          age2 = agenum ^ 2,  -->
-<!--          gini_disp=scale(gini_disp), -->
-<!--          dclass3res_V=dclass3res_V/10, -->
-<!--          dclass3spo_V=dclass3spo_V/10, -->
-<!--          homclass3_V_res=homclass3_V_res/10) %>%  -->
-<!--   filter(id %in% dummy_df$id) -->
-
-<!-- dfreg$wstate2 <- scale(scale(dfreg$abs_red*100) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe)) -->
-<!-- # Step 1: Calculate absolute values -->
-<!-- absolute_values <- abs(dfreg$homclass3_V_res) -->
-<!-- # hist(absolute_values);summary(absolute_values) -->
-
-<!-- # Step 2: Add 1 to all values to eliminate zeros -->
-<!-- modified_values <- absolute_values + 0.1 -->
-<!-- # hist(modified_values);summary(modified_values) -->
-
-<!-- # Step 3: Reverse the order of the scale -->
-<!-- reversed_values <- max(modified_values) + 0.1 - modified_values -->
-<!-- dfreg$homclass3_V_res <- reversed_values -->
-
-<!-- # Variable Group-Centering ------------------------------------------------ -->
-<!-- dfreg <-  -->
-<!--   dfreg %>%  -->
-<!--   mutate(to_dummy(female), -->
-<!--          to_dummy(union), -->
-<!--          to_dummy(workst), -->
-<!--          # dummy for categorical variables------------------------------------- -->
-<!--          to_dummy(Q03pcm), -->
-<!--          # to_dummy(dclass3spo_V) -->
-<!--   ) -->
-<!-- dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2) -->
-<!-- dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2) -->
-<!-- dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2) -->
-<!-- dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2) -->
-<!-- dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2) -->
-<!-- dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2) -->
-<!-- dfreg$socialtrust_gc = group_center(dfreg$socialtrust, grp = dfreg$country2) -->
-<!-- dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2) -->
-<!-- dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2) -->
-<!-- dfreg$religion_gc = group_center(as.numeric(dfreg$religion), grp = dfreg$country2) -->
-<!-- dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2) -->
-
-<!-- dfreg$dclass3res_V = group_center(as.numeric(dfreg$dclass3res_V), grp = dfreg$country2) -->
-
-<!-- # Household Income Tercile -->
-<!-- dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2) -->
-<!-- dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2) -->
-
-<!-- # Partner Social Class -->
-<!-- # dfreg$dclass3spo_V_1_gc = group_center(dfreg$dclass3spo_V_1, grp = dfreg$country2) -->
-<!-- # dfreg$dclass3spo_V_2_gc = group_center(dfreg$dclass3spo_V_2, grp = dfreg$country2) -->
-<!-- # dfreg$dclass3spo_V_3_gc = group_center(dfreg$dclass3spo_V_3, grp = dfreg$country2) -->
-<!-- # dfreg$dclass3spo_V_NA_gc = group_center(dfreg$dclass3spo_V_4, grp = dfreg$country2) -->
-<!-- dfreg$dclass3spo_V_gc = group_center(dfreg$dclass3spo_V, grp = dfreg$country2) -->
-
-<!-- # drop dummies -->
-<!-- dfreg <- dplyr::select(dfreg,-c(female_1,female_2,union_1,union_2,workst_1, -->
-<!--                                 workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4, -->
-<!--                                 # dclass3spo_V_1,dclass3spo_V_2,dclass3spo_V_3,dclass3spo_V_4 -->
-<!--                                 )) -->
-
-<!-- # dfreg$gini_disp <- scale(dfreg$gini_disp) -->
-
-<!-- ## Model -  EGP3 - DIGCLASS - V to Working ----------------------------- -->
-<!-- homo_V_gini <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+ -->
-<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          dclass3spo_V_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+ -->
-<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          dclass3spo_V_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_wstate2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+ -->
-<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          dclass3spo_V_gc+         female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_gdp_controls <- -->
-<!--   lmer(egal~ -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+ -->
-<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          dclass3spo_V_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2 + -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- homo_V_gini_full2 <-  -->
-<!--   lmer(egal~  -->
-<!--          homclass3_V_gc+ -->
-<!--          know_total_gc+ -->
-<!--          socialtrust_gc+ -->
-<!--          dclass3res_V+ -->
-<!--          # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+ -->
-<!--          dclass3spo_V_gc+ -->
-<!--          female_gc+agenum_gc+age2_gc+partner_gc+religion_gc+ -->
-<!--          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+ -->
-<!--          union_gc+workst_gc+ -->
-<!--          gini_disp +loggdppercapita + wstate2+ -->
-<!--          homclass3_V_gc* -->
-<!--          dclass3res_V* -->
-<!--          gini_disp +  -->
-<!--          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT) -->
-
-<!-- digclas1_macro <- list(homo_V_gini, -->
-<!--                        homo_V_gini_gdp, -->
-<!--                        homo_V_gini_gdp_wstate2, -->
-<!--                        homo_V_gini_full2) -->
-
-<!-- ccoef <- list(homclass3_V_gc="Social Distance (CWC)", -->
-<!--               "dclass3res_V"="ISEI ", -->
-<!--               "gini_disp" = "Income inequality (Gini index)", -->
-<!--               loggdppercapita = "GDP/capita", -->
-<!--               wstate2="Size of the welfare state", -->
-<!--               "homclass3_V_gc:dclass3res_V" = "Distance*ISEI", -->
-<!--               "homclass3_V_gc:gini_disp"= "Distance*Income Inequality", -->
-<!--               "dclass3res_V:gini_disp" ="ISEI*Inequality", -->
-<!--               "homclass3_V_gc:dclass3res_V:gini_disp" = "Distance*Working Class*Income Inequality") -->
-
-<!-- texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60, -->
-<!--        caption = "Multilevel models for Income Inequality, Network segregation and Redistributive Preferences", -->
-<!--        custom.note = "Note: Models include sampling weights and individual level controls centered within cluster (group mean). Standard errors in parentheses. %stars", -->
-<!--        caption.above = T,leading.zero = T,single.row = T, -->
-<!--        custom.coef.map = ccoef, -->
-<!--       # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Distance*Social Class"=7:8, "Distance * Social Class * Income Inequality"=10:11), -->
-<!--        float.pos = "h!", -->
-<!--       custom.gof.rows = list("Controls"=rep("Yes",4)),include.loglik = FALSE,include.aic = FALSE, -->
-<!--       custom.gof.names = c(NA,NA,"Num. groups", -->
-<!--                            "Var: Group (Intercept)", -->
-<!--                            "Var: Group Soc. Distance", -->
-<!--                            "Var: Group ISEI", -->
-<!--                            "Cov: Group (Intercept), Soc. Distance", -->
-<!--                            "Cov: Group (Intercept), ISEI",                            -->
-<!--                            "Cov: Group Soc. Distance, ISEI", -->
-<!--                            "Var: Residual"), -->
-<!--        use.packages = F) -->
-<!-- ``` -->
-
-<!-- ```{r fig2-socdist, fig.dim=c(12,7),fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, ISEI and Income Inequality'} -->
-<!-- ### Predicted values homo*class*GiniD --------------------------------------- -->
-<!-- # ginid_max<- round(max(dfreg$gini_disp) ,2) -->
-<!-- # ginid_min<- round(min(dfreg$gini_disp),2) -->
-
-<!-- ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2) -->
-<!-- ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2) -->
-<!-- ginid_mea<- round(mean(dfreg$gini_disp),2) -->
-
-<!-- df_pred_giniD_gc <- -->
-<!--   predictions( -->
-<!--     homo_V_gini_full2,newdata = datagrid( -->
-<!--       gini_disp = c(ginid_min, ginid_mea, ginid_max), -->
-<!--       wstate2=mean(dfreg$wstate2), -->
-<!--       loggdppercapita=mean(dfreg$loggdppercapita), -->
-<!--       homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.5), -->
-<!--       dclass3res_V=c(min(dfreg$dclass3res_V),max(dfreg$dclass3res_V)) -->
-<!--     ) -->
-<!--   ) -->
-
-<!-- df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc) -->
-<!-- df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)")) -->
-
-<!-- df_pred_giniD_gc$dclass3res_V <- factor(df_pred_giniD_gc$dclass3res_V,labels = c("ISEI (min)","ISEI (max)")) -->
-<!-- # df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)") -->
-
-<!-- df_pred_giniD_gc$dclass3res_V <- as.factor(df_pred_giniD_gc$dclass3res_V) -->
-
-<!-- df_pred_giniD_gc %>%  -->
-<!--   ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) + -->
-<!--   geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") + -->
-<!--   geom_line(size=1,color="black") + -->
-<!--   geom_point(size=3, shape = 21,color="black") + -->
-<!--   facet_wrap(~gini_disp) + -->
-<!--   labs(y = "Preferences for Redistribution", -->
-<!--        x="Social Distance (CWC)", -->
-<!--        caption = paste0("N=",nobs(homo_V_gini_full2),", Countries=",lme4::ngrps(homo_V_gini_full2)) -->
-<!--        ) + -->
-<!--   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL), -->
-<!--                      ) + -->
-
-<!--    scale_fill_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   scale_color_manual(values=c("#323232","#CCCCCC"))+ -->
-<!--   theme(legend.position = "bottom", -->
-<!--         legend.direction = "horizontal", -->
-<!--         axis.text=element_text(size=15), -->
-<!--         legend.title = element_blank(), -->
-<!--         legend.background = element_blank(), -->
-<!--         legend.box.background = element_rect(colour = "black")) -->
-<!-- ``` -->
+# References

### 2025-05-07 procesamiento/prod_analysis_reviews.R

@@ -1,0 +1,265 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+  prefineq,redist,
+  egal = egal2,
+  dclass3res_V,
+  dclass6res,
+  homclass3_V_res,
+  know_total,
+  n_low,
+  n_middle,
+  n_high,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst, 
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  oecd,
+  country2, country, country3,
+) %>%
+  mutate(logrgdpna = log(rgdpna),
+         loggdppercapita=log(gdppercapita),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2) %>%
+  filter(country2 != "SVN") 
+
+
+dfreg <- na.omit(dfreg)
+
+
+
+dfreg$n_low <- (dfreg$n_low - min(dfreg$n_low)) / (max(dfreg$n_low) - min(dfreg$n_low))*100
+dfreg$n_middle <- (dfreg$n_middle - min(dfreg$n_middle)) / (max(dfreg$n_middle) - min(dfreg$n_middle))*100
+dfreg$n_high <- (dfreg$n_high - min(dfreg$n_high)) / (max(dfreg$n_high) - min(dfreg$n_high))*100
+
+
+# Single class-profile analysis -------------------------------------------
+digclas1_VW_0<- lmer(egal~1 + (1|country2),data=dfreg)
[…]

### 2025-05-07 procesamiento/prod_otero_iturra.R

@@ -1,0 +1,482 @@
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+
+
+
+
+df1$isolation_v1<- 
+  sjmisc::rec(set_na(car::recode(df1$v31,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v1)
+df1$isolation_v2<- 
+  sjmisc::rec(set_na(car::recode(df1$v32,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v2)
+df1$isolation_v3<- 
+  sjmisc::rec(set_na(car::recode(df1$v33,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v3)
+
+
+df1$part_v1<- 
+  sjmisc::rec(set_na(car::recode(df1$v17,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v1)
+df1$part_v2<- 
+  sjmisc::rec(set_na(car::recode(df1$v18,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v2)
+df1$part_v3<- 
+  sjmisc::rec(set_na(car::recode(df1$v19,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v3)
+
+
+sjmisc::frq(df1$VOTE_LE)
+df1$vote <- factor(car::recode(df1$VOTE_LE,recodes = "1=1;2=0;else=NA"))
+table(df1$country3,df1$vote)
+
+df1$politrust <- set_na(car::recode(df1$v36,"c(98,99)=NA"),na = c(98,99));frq(df1$politrust)
+
+dfreg <- df1 %>% dplyr::select(
+  socialtrust,
+  politrust,
[…]

### 2025-05-13 paper1_jiturra.Rmd
avance review

@@
   region,
-  # "gini_disp"=wid_gini_disp,
-  "gini_disp"=difclass,
+  "gini_disp"=wid_gini_disp,
+  # "gini_disp"=difclass,
   "gini_mkt",
@@
          know_total_gc+
-         # socialtrust_gc+
          dclass3res_V+
-         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
          female_gc+agenum_gc+
-         # age2_gc+
          partner_gc+
          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         # union_gc+
          workst_gc+
@@
 
+homo_V_gini_full3 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         dclass3res_V+
+         female_gc+agenum_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         workst_gc+
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         wstate2 +
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
 digclas1_macro <- list(homo_V_gini,
@@
                        homo_V_gini_gdp_wstate2,
-                       homo_V_gini_full2)
+                       homo_V_gini_full2,homo_V_gini_full3)
+screenreg(digclas1_macro)
 

### 2025-05-13 procesamiento/05-prod_prep-complementary-analysis.Rmd
avance review

---
title: "Complementary analysis"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse,haven,MLMusingR)
```

# Individual-level

```{r, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,
  n_middle,n_low,n_high,
  homclass3_V_res,
  know_total,
  Q03pcm,
  edyears,
  female,
  agenum,
  partner,
  workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN")

dfreg <- na.omit(dfreg)

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$

digclas1_VW_7 <- lmer(egal~1 + dclass3res_V+n_low+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_8 <- lmer(egal~1 + dclass3res_V+n_low+n_middle+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_10 <- lmer(egal~1 + dclass3res_V+n_low+n_middle+n_high+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_10.1 <- lmer(egal~1 + dclass3res_V*n_low+n_middle+n_high+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_10.2 <- lmer(egal~1 + dclass3res_V*n_middle+n_high+n_low+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_10.3 <- lmer(egal~1 + dclass3res_V*n_high+n_low+n_middle+female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW_11 <- lmer(egal~1 + dclass3res_V*n_low + dclass3res_V*n_middle + dclass3res_V*n_high +female+agenum+partner+workst+ (1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW <- list(digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,
                    digclas1_VW_10.1,digclas1_VW_10.2,digclas1_VW_10.3,
                    digclas1_VW_11)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "n_low" = "Tie to working class",
              "n_middle" = "Tie to Intermediate class",
              "n_high" = "Tie to Service class",
              "dclass3res_VIntermediate class (III+IV):n_low" = "Intermediate x Tie to Working class",
              "dclass3res_VWorking Class (V+VI+VII):n_low"    = "Working x Tie to Working class",
              "dclass3res_VIntermediate class (III+IV):n_middle" = "Intermediate x Tie to Intermediate class",
              "dclass3res_VWorking Class (V+VI+VII):n_middle" = "Working x Tie to Intermediate class",
              "dclass3res_VIntermediate class (III+IV):n_high" = "Intermediate x Tie to Service class",
              "dclass3res_VWorking Class (V+VI+VII):n_high"= "Working x Tie to Service class"
              )

screenreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,symbol = ".",
       caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 1:2,
                    "Network class-profile" = 3:5,
                    "Interactions Class x Class-profile" = 6:11),
      # custom.gof.rows = list("Controls"=c("Yes",rep("Yes",1))),
      include.loglik = FALSE,
      include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual")
      )
```

# Country-level

```{r}
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
data_corruption <- xlsx::read.xlsx("input/data/original/coruption-data/CPI2017_Full_DataSet-1801.xlsx",sheetIndex = 1)
data_corruption$year <- 2017

data_unionden <- haven::read_dta("input/data/original/union-density/union-density.dta") 
data_migration <- data.table::fread("input/data/original/migration/migrant-stock-share.csv")
data_unemployment <- data.table::fread("input/data/original/unemployment-world-bank/unemployment-rate.csv")
data_qog <- haven::read_dta("input/data/original/QOG/qog_std_ts_jan25.dta") 
data_vdem <- haven::read_dta("input/data/original/QOG/V-Dem-CY-Full+Others-v15.dta")

union_den <- 
data_unionden %>% 
  dplyr::select(country=ref_area_label,year=time,union_den=obs_value) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

migration<- 
data_migration %>% dplyr::select(country=Entity,year=Year,mig_share=`Share of the population that was born in another country`) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

corruption <- 
data_corruption %>% 
  dplyr::select(country=Country,year,iso3=ISO3,cpi=CPI.Score.2017) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

unemployment <- 
data_unemployment %>% 
  dplyr::select(country=Entity,year=Year,unemployment_rate=`Unemployment, total (% of total labor force) (modeled ILO estimate)`) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

democracy <- 
data_qog %>% 
  dplyr::select(country=cname,year=year,van_index,p_polity2) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

vdem <- 
data_vdem %>% 
  dplyr::select(country=country_name,year=year,v2x_delibdem,v2x_polyarchy,v2x_egal) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

additional_macro <- 
union_den %>% 
  full_join(migration,by=c("ccode","country","year")) %>% 
  full_join(corruption,by=c("ccode","country","year")) %>% 
  full_join(unemployment,by=c("ccode","country","year")) %>%   
  full_join(democracy,by=c("ccode","country","year")) %>%
  full_join(vdem,by=c("ccode","country","year")) %>%  
  arrange(year)

summary(additional_macro)

country_code<- as.numeric(levels(as.factor(as.character(df1$ccode))))

additional_macro_2000to2018 <- 
  additional_macro %>% 
  filter(year %in% c(2015:2017)) %>% 
  filter(ccode %in% country_code)

additional_macro_avg <- 
additional_macro_2000to2018 %>% 
  group_by(ccode) %>% 
  summarise(union_den=mean(union_den,na.rm=T),
            mig_share=mean(mig_share,na.rm=T),
            cpi=mean(cpi,na.rm=T),
            unemployment_rate=mean(unemployment_rate,na.rm=T),
            van_index=mean(van_index,na.rm=T),
            p_polity2=mean(p_polity2,na.rm=T),            
            v2x_delibdem=mean(v2x_delibdem ,na.rm=T),
            v2x_polyarchy=mean(v2x_polyarchy ,na.rm=T),
            v2x_egal = mean(v2x_egal,na.rm=T)
            )
summary(additional_macro_avg)
save(additional_macro_avg,file ="input/data/proc/additional_macro_avg.RData")
```

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
# rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
load(file ="input/data/proc/additional_macro_avg.RData")

# Merge new macro-data
df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  Q03pcm,
  edyears,
  female,
  agenum,
  partner,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  cpi,
  mig_share,union_den,van_index,v2x_delibdem,v2x_polyarchy,v2x_egal,p_polity2,
  country2, country, country3,
) %>%
  filter(country2 != "SVN") %>% 
  # na.omit() %>%
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         gini_disp=scale(gini_disp))

dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))

# Variable Group-Centering ------------------------------------------------$
dfreg <- 
  dfreg %>% 
  mutate(to_dummy(female),
         to_dummy(workst),
         to_dummy(Q03pcm)
         )
dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
dfreg$workst_gc = group_center(dfreg$workst_2, grp = dfreg$country2)
dfreg$edyears_gc = group_center(dfreg$edyears, grp = dfreg$country2)
dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
dfreg$age2_gc = group_center(dfreg$age2, grp = dfreg$country2)
dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
dfreg$partner_gc = group_center(as.numeric(dfreg$partner), grp = dfreg$country2)

# Household Income Tercile
dfreg$Q03pcm_1_gc = group_center(dfreg$Q03pcm_1, grp = dfreg$country2)
dfreg$Q03pcm_2_gc = group_center(dfreg$Q03pcm_2, grp = dfreg$country2)
dfreg$Q03pcm_3_gc = group_center(dfreg$Q03pcm_3, grp = dfreg$country2)
dfreg$Q03pcm_NA_gc = group_center(dfreg$Q03pcm_4, grp = dfreg$country2)

# drop dummies
dfreg <- dplyr::select(dfreg,-c(female_1,female_2,
                                workst_2,Q03pcm_1,Q03pcm_2,Q03pcm_2,Q03pcm_4,
                                ))

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini)
homo_V_gini_gdp <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp)

homo_V_gini_gdp_wstate2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_wstate2)

homo_V_gini_gdp_cpi <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + cpi +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_cpi)

homo_V_gini_gdp_mig <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + mig_share +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_mig)

homo_V_gini_gdp_union <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 +union_den + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_union)

homo_V_gini_gdp_van_index <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + van_index +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
screenreg(homo_V_gini_gdp_van_index)

homo_V_gini_gdp_v2x_delibdem <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + v2x_delibdem +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
screenreg(homo_V_gini_gdp_v2x_delibdem)
homo_V_gini_gdp_v2x_polyarchy <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + v2x_polyarchy +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_v2x_egal <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + v2x_egal +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_v2x_egal)

homo_V_gini_gdp_p_polity2 <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 + p_polity2 +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_gdp_p_polity2)

homo_V_gini_full2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_full2)

homo_V_gini_full2.1 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         homclass3_V_gc*
         dclass3res_V*
         wstate2 +          
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

screenreg(homo_V_gini_full2.1)

homo_V_gini_full3 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + mig_share + union_den + p_polity2 + cpi+ 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
screenreg(homo_V_gini_full3)
```

### 2025-05-16 procesamiento/05-prod_prep-complementary-analysis.Rmd
data for sims

@@
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
+# rm(list=ls())
 
@@
 
-screenreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,symbol = ".",
-       caption = paste("Multilevel models for network homogeneity and redistributive preferences"),
+htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,symbol = ".",
+       file = "output/tables/tableSX.html",
+       caption = paste("Table SX: Multilevel models for class-based profiles, social classs and redistributive preferences"),
        custom.note = "Note: Standard errors in parentheses. %stars",
@@
 
-```{r}
+```{r data-prep}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+# rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
@@
 data_corruption$year <- 2017
-
 data_unionden <- haven::read_dta("input/data/original/union-density/union-density.dta") 
@@
 data_qog %>% 
-  dplyr::select(country=cname,year=year,van_index,p_polity2) %>% 
+  dplyr::select(country=cname,year=year,van_index,p_polity2,fe_etfra) %>% 
   mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
@@
 data_vdem %>% 
-  dplyr::select(country=country_name,year=year,v2x_delibdem,v2x_polyarchy,v2x_egal) %>% 
+  dplyr::select(country=country_name,year=year,v2x_delibdem,v2x_polyarchy,v2x_egal,v2catrauni) %>% 
   mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
@@
             v2x_polyarchy=mean(v2x_polyarchy ,na.rm=T),
-            v2x_egal = mean(v2x_egal,na.rm=T)
+            v2x_egal = mean(v2x_egal,na.rm=T),
+            fe_etfra = mean(fe_etfra,na.rm=T),
+            v2catrauni = mean(v2catrauni,na.rm=T)
             )
@@
 
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
 # Merge new macro-data
@@
 dfreg <- df1 %>% dplyr::select(
+  idnum,
   redist,prefineq,
@@
   cpi,
-  mig_share,union_den,van_index,v2x_delibdem,v2x_polyarchy,v2x_egal,p_polity2,
+  mig_share,
+  union_den,
+  v2x_polyarchy,
+  unemployment_rate,
+  v2catrauni,
   country2, country, country3,
@@
          age2 = agenum ^ 2, 
-         gini_disp=scale(gini_disp))
+         gini_disp=scale(gini_disp)) %>% 
+  filter(idnum %in%  dfid$idnum)
 
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
-homo_V_gini <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         dclass3res_V+
-         female_gc+agenum_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         workst_gc+
-         gini_disp +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-screenreg(homo_V_gini)
-homo_V_gini_gdp <- 
-  lmer(egal~ 
-         homclass3_V_gc+
-         know_total_gc+
-         dclass3res_V+
-         female_gc+agenum_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         workst_gc+
-         gini_disp +loggdppercapita +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-screenreg(homo_V_gini_gdp)
-
 homo_V_gini_gdp_wstate2 <- 
@@
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-screenreg(homo_V_gini_gdp_wstate2)
 
@@
 
-screenreg(homo_V_gini_gdp_cpi)
-
 homo_V_gini_gdp_mig <-
@@
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-
-screenreg(homo_V_gini_gdp_mig)
 
@@
 
-screenreg(homo_V_gini_gdp_union)
-
-homo_V_gini_gdp_van_index <-
+homo_V_gini_gdp_unempl <-
   lmer(egal~
@@
          workst_gc+
-         gini_disp +loggdppercapita + wstate2 + van_index +
+         gini_disp +loggdppercapita + wstate2 +unemployment_rate + 
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-screenreg(homo_V_gini_gdp_van_index)
 
-homo_V_gini_gdp_v2x_delibdem <-
-  lmer(egal~
-         homclass3_V_gc+
-         know_total_gc+
-         dclass3res_V+
-         female_gc+agenum_gc+
-         partner_gc+
-         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
-         workst_gc+
-         gini_disp +loggdppercapita + wstate2 + v2x_delibdem +
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-screenreg(homo_V_gini_gdp_v2x_delibdem)
 homo_V_gini_gdp_v2x_polyarchy <-
@@
 
-homo_V_gini_gdp_v2x_egal <-
+homo_V_gini_full2 <- 
   lmer(egal~ 
@@
          workst_gc+
-         gini_disp +loggdppercapita + wstate2 + v2x_egal +
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + 
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
 
-screenreg(homo_V_gini_gdp_v2x_egal)
-
-homo_V_gini_gdp_p_polity2 <-
+homo_V_gini_full3 <- 
   lmer(egal~ 
@@
          workst_gc+
-         gini_disp +loggdppercapita + wstate2 + p_polity2 +
+         gini_disp +loggdppercapita + wstate2+
+         homclass3_V_gc*
+         dclass3res_V*
+         gini_disp + mig_share + union_den +unemployment_rate + v2x_polyarchy + cpi+ 
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
 
-screenreg(homo_V_gini_gdp_p_polity2)
+models_macro <- list(homo_V_gini_gdp_wstate2,
+                     homo_V_gini_gdp_cpi,
+                     homo_V_gini_gdp_mig,
+                     homo_V_gini_gdp_union,
+                     homo_V_gini_gdp_unempl,
+                     homo_V_gini_gdp_v2x_polyarchy,
+                     homo_V_gini_full2,
+                     homo_V_gini_full3
+                     )
 
-homo_V_gini_full2 <- 
+screenreg(models_macro)
+
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              cpi = "Corruption Index",
+              mig_share = "Migration (pop %)",
+              union_den = "Union density",
+              unemployment_rate = "Unemployment rate",
+              v2x_polyarchy = "Democracy (polyarchy index)",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality")
+
+htmlreg(models_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
+       file = "output/tables/tableSXX.html",
+       caption = paste("Table SX: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
+       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
+       custom.coef.map = ccoef,
+      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
+      # custom.gof.rows = list("Controls"=rep("Yes",4)),
+      include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Country (Intercept)",
+                           "Var: Country Homogeneity",
+                           "Var: Country Intermediate Class ",
+                           "Var: Country Working Class",
+                           "Cov: Country (Intercept), Homogeneity",
+                           "Cov: Country (Intercept), Intermediate Class ",
+                           "Cov: Country (Intercept), Working Class",
+                           "Cov: Country Homogeneity, Intermediate Class",
+                           "Cov: Country Homogeneity, Working Class",
+                           "Cov: Country Intermediate Class, Working Class",
+                           "Var: Residual")
+      )
+
+```
+
+```{r}
+homo_V_wstate_full2 <- 
   lmer(egal~ 
@@
          partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
          workst_gc+
@@
          dclass3res_V*
-         gini_disp + 
+         wstate2 + 
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
 
-screenreg(homo_V_gini_full2)
-
-homo_V_gini_full2.1 <- 
+homo_V_gini_wstate <- 
   lmer(egal~ 
@@
          partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
          workst_gc+
          gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + 
-         homclass3_V_gc*
-         dclass3res_V*
-         wstate2 +          
+         homclass3_V_gc*dclass3res_V*gini_disp + 
+         homclass3_V_gc*dclass3res_V*wstate2 + 
          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
 
-screenreg(homo_V_gini_full2.1)
+models_interactions<- list(homo_V_gini_full2,
+               homo_V_wstate_full2,
+               homo_V_gini_wstate)
 
-homo_V_gini_full3 <- 
+ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              "gini_disp" = "Income inequality (Gini index)",
+              loggdppercapita = "GDP/capita",
+              wstate2="Size of the welfare state",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:wstate2"= "Homogeneity x Welfare State",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Homogeneity*Intermediate Class*Welfare State",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Homogeneity*Working Class*Welfare State")
+
+htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
+       file = "output/tables/tableSXXX.html",
+       caption = paste("Table SX: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
+       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
+       custom.coef.map = ccoef,
+      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
+      # custom.gof.rows = list("Controls"=rep("Yes",4)),
+      include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Country (Intercept)",
+                           "Var: Country Homogeneity",
+                           "Var: Country Intermediate Class ",
+                           "Var: Country Working Class",
+                           "Cov: Country (Intercept), Homogeneity",
+                           "Cov: Country (Intercept), Intermediate Class ",
+                           "Cov: Country (Intercept), Working Class",
+                           "Cov: Country Homogeneity, Intermediate Class",
+                           "Cov: Country Homogeneity, Working Class",
+                           "Cov: Country Intermediate Class, Working Class",
+                           "Var: Residual")
+      )
+```
+
+# Power analysis
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+# rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+load(file ="input/data/proc/additional_macro_avg.RData")
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  cpi,
+  mig_share,
+  union_den,
+  v2x_polyarchy,
+  unemployment_rate,
+  v2catrauni,
+  country2, country, country3,
+) %>%
+  filter(country2 != "SVN") %>% 
+  # na.omit() %>%
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         gini_disp=scale(gini_disp)) %>% 
+  filter(idnum %in%  dfid$idnum)
+
+dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+
+library(simr)
+
+homo_V_gini_gdp_wstate2 <- 
   lmer(egal~ 
+         gini_disp +
          homclass3_V_gc+
@@
          partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
          workst_gc+
          gini_disp +loggdppercapita + wstate2+
-         homclass3_V_gc*
-         dclass3res_V*
-         gini_disp + mig_share + union_den + p_polity2 + cpi+ 
-         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
-screenreg(homo_V_gini_full3)
+         (1|country2),data=dfreg,weights = WEIGHT)
+
+coef<- summary(homo_V_gini_gdp_wstate2)$coef[,"Estimate"]
+fixed<- as.numeric(coef)
+varcomp<- as.data.frame(lme4::VarCorr(homo_V_gini_gdp_wstate2))
+varcomp$vcov[1] # var country
+varcomp$sdcor[2] # var individual
+
+# fixed intercept and slope
+fixed <- fixed
+# random intercept and slope variance-covariance matrix
+# For class
+rand <- varcomp$vcov[1]
+
+# Exrtact the residual sd
+s <- varcomp$sdcor[2]
+
+model <- makeLmer(egal~
+         gini_disp +            
+         homclass3_V_gc+
+         know_total_gc+
+         dclass3res_V+
+         female_gc+agenum_gc+
+         partner_gc+
+         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
+         workst_gc+
+         loggdppercapita + wstate2+ (1|country2), fixef=fixed, VarCorr=rand, sigma=s, data=dfreg)
+model
+
+# For a range of effects sizes 2.2, + 1SD, +2SD, -1SD, -2 SD
+
+model_ext_country <- extend(model, along = "country2", n =200)
+
+p_sim_gini_disp <- 
+powerSim(model_ext_country, 
+         test=fixed("gini_disp",method = c("t")),
+         # along="country2",
+         # breaks = c(10,20,30,40,50,60,70,90,100),
+         nsim=1,
+         alpha=.05,
+         progress=TRUE);p_sim_gini_disp
+
+p_curve_gini_disp <- powerCurve(model_ext_country, 
+                            test=fixed("gini_disp",method = c("t")), 
+                            along="country2",
+                            breaks = c(10,20,30,40,50,60,70,90,100),
+                            nsim=5*60,
+                            alpha=.05,
+                            progress=TRUE)
 ```
+
+- determine effect sizes (small, medium, high)
+- determine number of clusters
+- Simulate with 1000, 5000 and 10.000 reps

### 2025-05-16 procesamiento/prod_power-analysis.R

@@ -1,0 +1,165 @@
+# Power analysis 
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+# rm(list=ls()) 
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+load(file ="input/data/proc/additional_macro_avg.RData")
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
[…]

### 2025-07-18 paper1_jiturra.Rmd
RR Patrick

@@
   filter(country2 != "SVN") 
+dfreg$egal <- as.numeric(scale(dfreg$egal))
 
@@
 digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
-                    # digclas1_VW_3,
+                    digclas1_VW_3,
                     # digclas1_VW_4,
@@
 
+screenreg(digclas1_VW)
 texreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
@@
   predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
-              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.1),
-                                 dclass3res_V = levels(dfreg$dclass3res_V)))
+              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res),
+                                                       max(dfreg$homclass3_V_res), by= 0.2),
+                                 dclass3res_V = levels(dfreg$dclass3res_V),
+                                 know_total = mean(dfreg$know_total)))
 # names(df_pred1) 
@@
   scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
-  scale_y_continuous(limits = c(55,80))+
+  # scale_y_continuous(limits = c(55,80))+
   labs(caption = paste0("Note: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". Predictive estimates with 95% confidence intervals"),
-       x="Network homogeneity",y="Redistributive preferences (0 - 100)") +
+       x="Network homogeneity (z-score)",y="Redistributive preferences (z-score)") +
   theme(legend.position = "none", legend.title = element_blank())
@@
   dclass3res_V,
-  # dclass3spo_V, 
   homclass3_V_res,
   know_total,
-  # socialtrust,
   Q03pcm,
@@
   agenum,
-  # religion,
   partner,
-  # union,
   workst,
@@
   "gini_disp"=wid_gini_disp,
-  # "gini_disp"=difclass,
   "gini_mkt",
@@
 ) %>%
-  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN") %>% 
@@
     mutate(loggdppercapita=scale(gdppercapita/1000),
-         edyears2 = edyears ^ 2,
          age2 = agenum ^ 2, 
@@
 dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
+dfreg$egal <- as.numeric(scale(dfreg$egal))
+# dfreg$homclass3_V_res <- as.numeric(scale(dfreg$homclass3_V_res))
+# dfreg$know_total <- as.numeric(scale(dfreg$know_total))
+# dfreg$agenum <- as.numeric(scale(dfreg$agenum))
+# dfreg$edyears <- as.numeric(scale(dfreg$edyears))
 
@@
                        homo_V_gini_full2,homo_V_gini_full3)
+
 screenreg(digclas1_macro)
@@
        path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 17)
-
 ```

### 2025-07-18 procesamiento/05-prod_prep-supplementary-material.Rmd
RR Patrick

---
title: "Complementary analysis"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,sjPlot,sjlabelled,tidyverse,haven,MLMusingR)
```

# Individual-level

```{r tableS1, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4,gridExtra,grid)  
# rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,class6res,
  n_middle,n_low,n_high,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)) %>%
  filter(country2 != "SVN")
dfreg <- na.omit(dfreg)
dfreg$egal <- scale(dfreg$egal)

dfreg$n_low <- dfreg$n_low/4 
dfreg$n_middle <- dfreg$n_middle/3
dfreg$n_high <- dfreg$n_high/3

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
digclas1_VW_7 <- lmer(egal~1 + dclass3res_V+n_low+female+agenum+ (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_8 <- lmer(egal~1 + dclass3res_V+n_low+n_middle+female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_10 <- lmer(egal~1 + dclass3res_V+n_low+n_middle+n_high+female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_10.1 <- lmer(egal~1 + dclass3res_V*n_low+n_middle+n_high+female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_10.2 <- lmer(egal~1 + dclass3res_V*n_middle+n_high+n_low+female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_10.3 <- lmer(egal~1 + dclass3res_V*n_high+n_low+n_middle+female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_11 <- lmer(egal~1 + dclass3res_V*n_low + dclass3res_V*n_middle + dclass3res_V*n_high +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)

digclas1_VW <- list(digclas1_VW_7,digclas1_VW_8,digclas1_VW_10,
                    digclas1_VW_10.1,digclas1_VW_10.2,digclas1_VW_10.3,digclas1_VW_11)

fit_low<- plot_predictions(digclas1_VW_11, condition = list("dclass3res_V", n_low = seq(0, 1, by = 0.1)),draw=F)
fit_mid<-plot_predictions(digclas1_VW_11, condition = list("dclass3res_V", n_middle = seq(0, 1, by = 0.1)),draw = F)
fit_hig<-plot_predictions(digclas1_VW_11, condition = list("dclass3res_V", n_high = seq(0, 1, by = 0.1)),draw = F)

fit_low$n_low <- as.numeric(as.character(fit_low$n_low))
fit_mid$n_middle <- as.numeric(as.character(fit_mid$n_middle))
fit_hig$n_high <- as.numeric(as.character(fit_hig$n_high))

plot_low <- 
fit_low %>% 
ggplot(aes(y =estimate,x=n_low, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high,group=dclass3res_V)) +
  # geom_errorbar(alpha=0.8,size=0.5,linetype="solid",color="black") +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
       x="Class-profile low",y="Redistributive preferences",,tag = "A") +
  theme(legend.position = "none", legend.title = element_blank())

plot_mid<- 
fit_mid %>% 
ggplot(aes(y =estimate,x=n_middle, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
    scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
      x="Class-profile Middle",y="Redistributive preferences",tag = "B") +
  theme(legend.position = "none", legend.title = element_blank())

plot_hig <- 
fit_hig %>% 
ggplot(aes(y =estimate,x=n_high, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals",),
       x="Class-profile High",y="Redistributive preferences",tag = "C") +
  theme(legend.position = "none", legend.title = element_blank())

set.seed(123)

grid.arrange(plot_low,plot_mid,plot_hig, ncol=1)
ggsave(plot = arrangeGrob(plot_low,plot_mid,plot_hig,
             nrow = 3, 
 bottom =textGrob("Source: International Social Survey 2017; the line is the fitted values; CI at 95%",
 gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
  )),
 filename = "figureS1.png",device = "png",
 path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "n_low" = "Tie to working class",
              "n_middle" = "Tie to Intermediate class",
              "n_high" = "Tie to Service class",
              "dclass3res_VIntermediate class (III+IV):n_low" = "Intermediate × Tie to Working class",
              "dclass3res_VWorking Class (V+VI+VII):n_low"    = "Working × Tie to Working class",
              "dclass3res_VIntermediate class (III+IV):n_middle" = "Intermediate × Tie to Intermediate class",
              "dclass3res_VWorking Class (V+VI+VII):n_middle" = "Working × Tie to Intermediate class",
              "dclass3res_VIntermediate class (III+IV):n_high" = "Intermediate × Tie to Service class",
              "dclass3res_VWorking Class (V+VI+VII):n_high"= "Working × Tie to Service class"
              )

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,symbol = ".",
       file = here::here("output/tables/tableS01.html"),
       caption = paste("Table S1: Multilevel models for class-based profiles, social classs and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars.",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 1:2,
                    "Network class-profile" = 3:5,
                    "Interactions Class × Class-profile" = 6:11),
      # custom.gof.rows = list("Controls"=c("Yes",rep("Yes",1))),
      include.loglik = FALSE,
      include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual")
      )
```

# Country-level controls

```{r data-prep}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
# rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
data_corruption <- xlsx::read.xlsx("input/data/original/coruption-data/CPI2017_Full_DataSet-1801.xlsx",sheetIndex = 1)
data_corruption$year <- 2017
data_unionden <- haven::read_dta("input/data/original/union-density/union-density.dta") 
data_migration <- data.table::fread("input/data/original/migration/migrant-stock-share.csv")
data_unemployment <- data.table::fread("input/data/original/unemployment-world-bank/unemployment-rate.csv")
data_qog <- haven::read_dta("input/data/original/QOG/qog_std_ts_jan25.dta") 
data_vdem <- haven::read_dta("input/data/original/QOG/V-Dem-CY-Full+Others-v15.dta")

# data_socx <- data.table::fread("input/data/original/ocde-socx/ocde-socx.csv")
data_socx <- data.table::fread("input/data/original/ocde-socx/ocde-socspen.csv")

socx <- 
data_socx %>% 
  filter(SUBJECT =="PUB") %>% 
  dplyr::select(country=LOCATION,year=TIME_PERIOD,socx=OBS_VALUE) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "iso3c",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

union_den <- 
data_unionden %>% 
  dplyr::select(country=ref_area_label,year=time,union_den=obs_value) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

migration<- 
data_migration %>% dplyr::select(country=Entity,year=Year,mig_share=`Share of the population that was born in another country`) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

corruption <- 
data_corruption %>% 
  dplyr::select(country=Country,year,iso3=ISO3,cpi=CPI.Score.2017) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

unemployment <- 
data_unemployment %>% 
  dplyr::select(country=Entity,year=Year,unemployment_rate=`Unemployment, total (% of total labor force) (modeled ILO estimate)`) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

democracy <- 
data_qog %>% 
  dplyr::select(country=cname,year=year,van_index,p_polity2,fe_etfra) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

vdem <- 
data_vdem %>% 
  dplyr::select(country=country_name,year=year,v2x_delibdem,v2x_polyarchy,v2x_egal,v2catrauni) %>% 
  mutate(ccode=countrycode::countrycode(country,origin = "country.name",destination = "iso3n"),
         country=countrycode::countrycode(ccode,origin = "iso3n",destination = "country.name"),
         year=as.numeric(year))

additional_macro <- 
union_den %>% 
  full_join(migration,by=c("ccode","country","year")) %>% 
  full_join(corruption,by=c("ccode","country","year")) %>% 
  full_join(unemployment,by=c("ccode","country","year")) %>%   
  full_join(democracy,by=c("ccode","country","year")) %>%
  full_join(vdem,by=c("ccode","country","year")) %>%  
  full_join(socx,by=c("ccode","country","year")) %>% 
  arrange(year)

summary(additional_macro)

country_code<- as.numeric(levels(as.factor(as.character(df1$ccode))))

additional_macro_2000to2018 <- 
  additional_macro %>% 
  filter(year %in% c(2015:2017)) %>% 
  filter(ccode %in% country_code)

additional_macro_avg <- 
additional_macro_2000to2018 %>% 
  group_by(ccode) %>% 
  summarise(union_den=mean(union_den,na.rm=T),
            mig_share=mean(mig_share,na.rm=T),
            cpi=mean(cpi,na.rm=T),
            unemployment_rate=mean(unemployment_rate,na.rm=T),
            van_index=mean(van_index,na.rm=T),
            p_polity2=mean(p_polity2,na.rm=T),            
            v2x_delibdem=mean(v2x_delibdem ,na.rm=T),
            v2x_polyarchy=mean(v2x_polyarchy ,na.rm=T),
            v2x_egal = mean(v2x_egal,na.rm=T),
            fe_etfra = mean(fe_etfra,na.rm=T),
            v2catrauni = mean(v2catrauni,na.rm=T),
            socx = mean(socx,na.rm=T)
            )
summary(additional_macro_avg)
save(additional_macro_avg,file ="input/data/proc/additional_macro_avg.RData")
```

```{r tableS2}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
# rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
load(here::here("input/data/proc/additional_macro_avg.RData"))
df1$idnum <- rownames(df1)
dfid <- df1 %>% dplyr::select(
  idnum,
  redist,prefineq,
  egal = egal2,
  dclass3res_V,dclass6res,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  country2, country, country3,
) %>% na.omit()

# Merge new macro-data
df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
dfreg <- df1 %>% dplyr::select(
  idnum,
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,dclass6res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  cpi,
  mig_share,
  union_den,
  v2x_polyarchy,
  unemployment_rate,
  v2catrauni,socx,
  country2, country, country3,
) %>%
  filter(country2 != "SVN") %>% 
  # na.omit() %>%
    mutate(loggdppercapita=scale(gdppercapita/1000),
         age2 = agenum ^ 2) %>% 
  filter(idnum %in%  dfid$idnum)

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
dfreg$wstate2 <- as.numeric(scale(dfreg$wstate2))

dfreg$socx<- as.numeric(scale(dfreg$socx))

dfreg$gini_disp <- as.numeric(scale(dfreg$gini_disp))

dfreg$ilo_taxrev <- as.numeric(scale(dfreg$ilo_taxrev))
dfreg$ilo_govspe <- as.numeric(scale(dfreg$ilo_govspe))

dfreg$cpi <- as.numeric(scale(dfreg$cpi))
dfreg$mig_share <- as.numeric(scale(dfreg$mig_share))
dfreg$union_den <- as.numeric(scale(dfreg$union_den))
dfreg$v2x_polyarchy <- as.numeric(scale(dfreg$v2x_polyarchy))
dfreg$unemployment_rate <- as.numeric(scale(dfreg$unemployment_rate))
dfreg$egal <- scale(dfreg$egal)

# Variable Group-Centering ------------------------------------------------$
dfreg <- 
  dfreg %>% 
  mutate(to_dummy(female)
         )
dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
homo_V_gini_gdp_wstate2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_cpi <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2 + cpi +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_mig <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2 + mig_share +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_union <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2 +union_den + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_unempl <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2 +unemployment_rate + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_v2x_polyarchy <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2 + v2x_polyarchy +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full3 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + mig_share + union_den +unemployment_rate + v2x_polyarchy + cpi+ 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

models_macro <- list(homo_V_gini_gdp_wstate2,
                     homo_V_gini_gdp_cpi,
                     homo_V_gini_gdp_v2x_polyarchy,                     
                     homo_V_gini_gdp_mig,
                     homo_V_gini_gdp_union,
                     homo_V_gini_gdp_unempl,
                     homo_V_gini_full2,
                     homo_V_gini_full3
                     )

screenreg(models_macro)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              cpi = "Corruption Index",
              v2x_polyarchy = "Democracy (polyarchy index)",
              mig_share = "Migration (pop %)",
              union_den = "Union density",
              unemployment_rate = "Unemployment rate",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality")

htmlreg(models_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS02.html"),
       caption = paste("Table S2: Multilevel models for country-level factors,
                       income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars. The depedent variable and country-level variables are in standardized (z-score)",
       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

# Cross-level interaction

```{r tableS3}
# Main cross-level interaction for Income Inequality---------------------------
int_xlvl_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# Main cross-level interaction with Welfare State Size--------------------------
int_xlvl_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         gini_disp +
         homclass3_V_gc*
         dclass3res_V*
         wstate2 + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Tax Reveneu)-------
int_xlvl_gini_taxrev <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*ilo_taxrev + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Goverment Spending)------
int_xlvl_gini_govspe <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*ilo_govspe + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# Double cross-level interaction Gini and Welfare State Size (Redistribution)----
int_xlvl_gini_redist <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*abs_red + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         loggdppercapita+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*wstate2 + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and GDP ----------------------------------
int_xlvl_gini_gdp<- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*loggdppercapita +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

models_interactions<- list(int_xlvl_gini,int_xlvl_gini_taxrev,int_xlvl_gini_govspe,int_xlvl_gini_redist,int_xlvl_gini_wstate,int_xlvl_gini_gdp)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",

              gini_disp = "Income inequality (Gini index)",
              ilo_taxrev="(i) Tax revenue",
              ilo_govspe="(ii) Gov. Spending",
              abs_red="(iii) Redistribution",              
              wstate2="(i,ii,iii) Size of the welfare state",
              loggdppercapita = "GDP/capita",

              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality",

              "homclass3_V_gc:ilo_taxrev"= "Homogeneity × (Tax revenue)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Homogeneity × Intermediate Class × (Tax revenue)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Homogeneity × Working Class × (Tax revenue) ",

              "homclass3_V_gc:ilo_govspe"= "Homogeneity × Welfare State (Gov. Spending)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Homogeneity × Intermediate Class × (Gov. Spending)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Homogeneity × Working Class × (Gov. Spending)",

              "homclass3_V_gc:abs_red"= "Homogeneity × Welfare State (Redistribution)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):abs_red" = "Homogeneity × Intermediate Class × (Redistribution)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):abs_red" = "Homogeneity × Working Class × (Redistribution)",

              "homclass3_V_gc:wstate2"= "Homogeneity × Welfare State",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Homogeneity × Intermediate Class × Welfare State",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Homogeneity × Working Class × Welfare State",

              "homclass3_V_gc:loggdppercapita"= "Homogeneity × GDP",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Homogeneity × Intermediate Class × GDP",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Homogeneity × Working Class × GDP"              
              )

htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS03.html"),
       caption = paste("Table S3: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

```{r tableS4, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,
  # dclass3spo_V,
  homclass3_V_res,dclass6res,
  know_total,
  # socialtrust,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # religion,
  # union,
  # workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  ilo_taxrev,ilo_govspe,abs_red,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)
         ) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") 
dfreg$egal <- as.numeric(scale(dfreg$egal))
dfreg <- na.omit(dfreg)

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)

digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)

digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
                    digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              "dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              "homclass3_V_res:dclass6resLower Service class" = "Homogeneity × Lower Service",
              "homclass3_V_res:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
              "homclass3_V_res:dclass6resSelf-employed"= "Homogeneity × Self-employed",
              "homclass3_V_res:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
              "homclass3_V_res:dclass6resUnskilled working class" = "Homogeneity × Skilled working class" 
              )

screenreg(digclas1_VW)

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table S4: Multilevel models for network homogeneity and redistributive preferences (6-class version)"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups =
         list("Social Class (Ref.= Upper Service)" = 3:7,
              "Homogeneity × Social Class"=8:11),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableS04.html")
      )
```

```{r tableS5}
# Main cross-level interaction for Income Inequality---------------------------
int_xlvl_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*
         dclass6res*
         gini_disp + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Main cross-level interaction with Welfare State Size--------------------------
int_xlvl_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         gini_disp +
         homclass3_V_gc*
         dclass6res*
         wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Tax Reveneu)-------
int_xlvl_gini_taxrev <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_taxrev + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Goverment Spending)------
int_xlvl_gini_govspe <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_govspe + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Double cross-level interaction Gini and Welfare State Size (Redistribution)----
int_xlvl_gini_redist <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*abs_red + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and GDP ----------------------------------
int_xlvl_gini_gdp<- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*loggdppercapita +
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

models_interactions<- list(int_xlvl_gini,int_xlvl_gini_taxrev,int_xlvl_gini_govspe,int_xlvl_gini_redist,int_xlvl_gini_wstate,int_xlvl_gini_gdp)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
              know_total="Network size",
              "dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              "homclass3_V_gc:dclass6resLower Service class" = "Homogeneity × Lower Service",
              "homclass3_V_gc:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
              "homclass3_V_gc:dclass6resSelf-employed"= "Homogeneity × Self-employed",
              "homclass3_V_gc:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
              "homclass3_V_gc:dclass6resUnskilled working class" = "Homogeneity × Skilled working class",

              gini_disp = "Income inequality (Gini index)",
              ilo_taxrev="(i) Tax revenue",
              ilo_govspe="(ii) Gov. Spending",
              abs_red="(iii) Redistribution",              
              wstate2="(i,ii,iii) Size of the welfare state",            
              loggdppercapita = "GDP/capita",

              # 3-way interactions: × Gini
              "homclass3_V_gc:dclass6resLower Service class:gini_disp"         = "Homogeneity × Lower Service × Gini",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:gini_disp"     = "Homogeneity × Routine Nonmanual × Gini",
              "homclass3_V_gc:dclass6resSelf-employed:gini_disp"               = "Homogeneity × Self-employed × Gini",
              "homclass3_V_gc:dclass6resSkilled working class:gini_disp"       = "Homogeneity × Skilled Working Class × Gini",
              "homclass3_V_gc:dclass6resUnskilled working class:gini_disp"     = "Homogeneity × Unskilled Working Class × Gini",

              # 3-way interactions: × Tax Revenue
              "homclass3_V_gc:dclass6resLower Service class:ilo_taxrev"         = "Homogeneity × Lower Service × Tax Revenue",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_taxrev"     = "Homogeneity × Routine Nonmanual × Tax Revenue",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_taxrev"               = "Homogeneity × Self-employed × Tax Revenue",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_taxrev"       = "Homogeneity × Skilled Working Class × Tax Revenue",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_taxrev"     = "Homogeneity × Unskilled Working Class × Tax Revenue",

              # 3-way interactions: × Government Spending
              "homclass3_V_gc:dclass6resLower Service class:ilo_govspe"         = "Homogeneity × Lower Service × Gov. Spending",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_govspe"     = "Homogeneity × Routine Nonmanual × Gov. Spending",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_govspe"               = "Homogeneity × Self-employed × Gov. Spending",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_govspe"       = "Homogeneity × Skilled Working Class × Gov. Spending",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_govspe"     = "Homogeneity × Unskilled Working Class × Gov. Spending",

              # 3-way interactions: × Redistribution
              "homclass3_V_gc:dclass6resLower Service class:abs_red"         = "Homogeneity × Lower Service × Redistribution",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:abs_red"     = "Homogeneity × Routine Nonmanual × Redistribution",
              "homclass3_V_gc:dclass6resSelf-employed:abs_red"               = "Homogeneity × Self-employed × Redistribution",
              "homclass3_V_gc:dclass6resSkilled working class:abs_red"       = "Homogeneity × Skilled Working Class × Redistribution",
              "homclass3_V_gc:dclass6resUnskilled working class:abs_red"     = "Homogeneity × Unskilled Working Class × Redistribution",

              # 3-way interactions: × Welfare State
              "homclass3_V_gc:dclass6resLower Service class:wstate2"         = "Homogeneity × Lower Service × Welfare State",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:wstate2"     = "Homogeneity × Routine Nonmanual × Welfare State",
              "homclass3_V_gc:dclass6resSelf-employed:wstate2"               = "Homogeneity × Self-employed × Welfare State",
              "homclass3_V_gc:dclass6resSkilled working class:wstate2"       = "Homogeneity × Skilled Working Class × Welfare State",
              "homclass3_V_gc:dclass6resUnskilled working class:wstate2"     = "Homogeneity × Unskilled Working Class × Welfare State",
              # 3-way interactions: × GDP
              "homclass3_V_gc:dclass6resLower Service class:loggdppercapita"         = "Homogeneity × Lower Service × GDP",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:loggdppercapita"     = "Homogeneity × Routine Nonmanual × GDP",
              "homclass3_V_gc:dclass6resSelf-employed:loggdppercapita"               = "Homogeneity × Self-employed × GDP",
              "homclass3_V_gc:dclass6resSkilled working class:loggdppercapita"       = "Homogeneity × Skilled Working Class × GDP",
              "homclass3_V_gc:dclass6resUnskilled working class:loggdppercapita"     = "Homogeneity × Unskilled Working Class × GDP"              
              )

htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS05.html"),
       caption = paste("Table S5: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,
  "Num. groups: country2" = "Number of countries",
  # Variances
  "Var: country2 (Intercept)" = "Var: country Intercept",
  "Var: country2 homclass3_V_gc" = "Var: country Homogeneity",
  "Var: country2 dclass6resLower Service class" = "Var: country Lower Service",
  "Var: country2 dclass6resRoutine nonmanual class" = "Var: country Routine Nonmanual",
  "Var: country2 dclass6resSelf-employed" = "Var: country Self-employed",
  "Var: country2 dclass6resSkilled working class" = "Var: country Skilled Working Class",
  "Var: country2 dclass6resUnskilled working class" = "Var: country Unskilled Working Class",

  # Covariances with intercept
  "Cov: country2 (Intercept) homclass3_V_gc" = "Cov: Intercept × Homogeneity",
  "Cov: country2 (Intercept) dclass6resLower Service class" = "Cov: Intercept × Lower Service",
  "Cov: country2 (Intercept) dclass6resRoutine nonmanual class" = "Cov: Intercept × Routine Nonmanual",
  "Cov: country2 (Intercept) dclass6resSelf-employed" = "Cov: Intercept × Self-employed",
  "Cov: country2 (Intercept) dclass6resSkilled working class" = "Cov: Intercept × Skilled Working Class",
  "Cov: country2 (Intercept) dclass6resUnskilled working class" = "Cov: Intercept × Unskilled Working Class",

  # Covariances with Homogeneity
  "Cov: country2 homclass3_V_gc dclass6resLower Service class" = "Cov: Homogeneity × Lower Service",
  "Cov: country2 homclass3_V_gc dclass6resRoutine nonmanual class" = "Cov: Homogeneity × Routine Nonmanual",
  "Cov: country2 homclass3_V_gc dclass6resSelf-employed" = "Cov: Homogeneity × Self-employed",
  "Cov: country2 homclass3_V_gc dclass6resSkilled working class" = "Cov: Homogeneity × Skilled Working Class",
  "Cov: country2 homclass3_V_gc dclass6resUnskilled working class" = "Cov: Homogeneity × Unskilled Working Class",

  # Covariances between classes
  "Cov: country2 dclass6resLower Service class dclass6resRoutine nonmanual class" = "Cov: Lower Service × Routine Nonmanual",
  "Cov: country2 dclass6resLower Service class dclass6resSelf-employed" = "Cov: Lower Service × Self-employed",
  "Cov: country2 dclass6resLower Service class dclass6resSkilled working class" = "Cov: Lower Service × Skilled Working Class",
  "Cov: country2 dclass6resLower Service class dclass6resUnskilled working class" = "Cov: Lower Service × Unskilled Working Class",
  "Cov: country2 dclass6resRoutine nonmanual class dclass6resSelf-employed" = "Cov: Routine Nonmanual × Self-employed",
  "Cov: country2 dclass6resRoutine nonmanual class dclass6resSkilled working class" = "Cov: Routine Nonmanual × Skilled Working Class",
  "Cov: country2 dclass6resRoutine nonmanual class dclass6resUnskilled working class" = "Cov: Routine Nonmanual × Unskilled Working Class",
  "Cov: country2 dclass6resSelf-employed dclass6resSkilled working class" = "Cov: Self-employed × Skilled Working Class",
  "Cov: country2 dclass6resSelf-employed dclass6resUnskilled working class" = "Cov: Self-employed × Unskilled Working Class",
  "Cov: country2 dclass6resSkilled working class dclass6resUnskilled working class" = "Cov: Skilled Working Class × Unskilled Working Class",
  "Var: Residual" = "Residual variance"
)
      )
```

### 2025-07-18 procesamiento/06_prod_psim-gini.R

@@ -1,0 +1,609 @@
+# Power analysis 
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+# load("study1_country.RData");df1 <- df2
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# load("additional_macro_avg.RData")
+load(here::here("input/data/proc/additional_macro_avg.RData"))
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  female,
+  agenum,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  # Q03pcm,
+  # edyears,
+  female,
+  agenum,
+  # partner,
+  # workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
[…]

### 2025-07-18 procesamiento/07_prod_psim-cross-level.R

@@ -1,0 +1,280 @@
+# Power analysis 
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+
+# setwd("~/paper1")
+# load("study1_country.RData");df1 <- df2
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# load("additional_macro_avg.RData")
+load(here::here("input/data/proc/additional_macro_avg.RData"))
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  partner,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
[…]

### 2025-07-18 procesamiento/prod_power-analysis.R

@@ -1,165 +1,0 @@
-# Power analysis 
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-# rm(list=ls()) 
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-load(file ="input/data/proc/additional_macro_avg.RData")
-
-df1$idnum <- rownames(df1)
-
-dfid <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  country2, country, country3,
-) %>% na.omit()
-
-# Merge new macro-data
-df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
-dfreg <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
[…]

### 2025-07-29 procesamiento/01-prod_prep-microdata.Rmd
ajustes data micro

--- 2024-07-16 procesamiento/01-prod_prep-micro.Rmd
@@
 
-```{r eval=FALSE, include=FALSE}
-knitr::knit(input = here::here("procesamiento/01-prod_prep-micro.Rmd"));file.remove("01-prod_prep-micro.md")
-knitr::knit(input = here::here("procesamiento/02-prod_prep-macro.Rmd"));file.remove("02-prod_prep-macro.md")
-```
-
 # Setup
@@
 ```{r setup}
-knitr::opts_chunk$set(warning = FALSE, 
-                      message = FALSE, 
-                      echo = TRUE,
-                      cache = T
-                      )
-options(scipen=9999) # desactivar notacion cientifica
+options(scipen=9999) 
 ```
@@
 dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))
-dfTR$weight <- 1
 df1 <- df1 %>% rename(topbot=TOPBOT)
@@
                         RELIGGRP=religgrp,
-                        MARITAL=marital)
+                        MARITAL=marital,
+                        WRKHRS=wrkhrs)
 
@@
 
-# Welfare attitudes
+# Inequality perceptions
 
 ```{r}
-#frq(df1$v13)
-df1$redist <- car::recode(df1$v13,recodes = "c(0,8,9)=NA")
-df1$redist <- set_na(df1$redist,na = c(0,8,9))
-df1$redist <- sjmisc::rec(x = df1$redist,rec = "rev")
-sjlabelled::set_label(df1$redist) <- "Preferences goverment redistribution"
-#frq(df1$redist)
-
-#frq(df1$v15)
-df1$whealth <- car::recode(df1$v15,recodes = "c(0,8,9)=NA")
-df1$whealth <- set_na(df1$whealth,na = c(0,8,9))
-df1$whealth <- sjmisc::rec(x = df1$whealth,rec = "rev")
-sjlabelled::set_label(df1$whealth) <- "Welfare provision: health"
-#frq(df1$whealth)
-
-#frq(df1$v16)
-df1$wcarelder <- car::recode(df1$v16,recodes = "c(0,8,9)=NA")
-df1$wcarelder <- set_na(df1$wcarelder,na = c(0,8,9))
-df1$wcarelder <- sjmisc::rec(x = df1$wcarelder,rec = "rev")
-sjlabelled::set_label(df1$wcarelder) <- "Welfare provision: elderly care"
-#frq(df1$wcarelder)
-# cor(df1[,c("redist","whealth","wcarelder")],use = "complete.obs")
-```
-
-# Inequality perceptions
-
-```{r}
-#frq(df1$v59)
-df1$hhdepriv <- car::recode(df1$v59,recodes = "c(0,8,9)=NA")
-df1$hhdepriv <- set_na(df1$hhdepriv,na = c(0,8,9))
-# df1$hhdepriv <- sjmisc::rec(x = df1$hhdepriv,rec = "rev")
-sjlabelled::set_label(df1$hhdepriv) <- "Household economic deprivation (household difficulties)"
-#frq(df1$hhdepriv)
-
-#frq(df1$v11)
-df1$perineq <- car::recode(df1$v11,recodes = "c(0,8,9)=NA")
-df1$perineq <- set_na(df1$perineq,na = c(0,8,9))
-df1$perineq <- sjmisc::rec(x = df1$perineq,rec = "rev")
-sjlabelled::set_label(df1$perineq) <- "Perceived economic inequality (Inc. diff. too large)"
-#frq(df1$perineq)
-
-#frq(df1$v12)
 df1$prefineq <- car::recode(df1$v12,recodes = "c(0,8,9)=NA")
@@
 sjlabelled::set_label(df1$prefineq) <- "Preference inequality (society has to be fair)"
-#frq(df1$prefineq)
-
-#frq(df1$v14)
+
 df1$pertransfer <- car::recode(df1$v14,recodes = "c(0,8,9)=NA")
@@
 sjlabelled::set_label(df1$pertransfer) <- "Perception about welfare (people become lazy)"
-#frq(df1$pertransfer)
 ```
@@
 ```{r}
-df1$egal3<- rowMeans(df1[,c("redist","prefineq","perineq")],na.rm = T)
-df1$egal3 <- ((df1$egal3-min(df1$egal3,na.rm = T))/(max(df1$egal3,na.rm = T)-min(df1$egal3,na.rm = T)))*100
-
-sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
-# #hist.default(df1$egal3)
-
 df1$egal2<- rowMeans(df1[,c("redist","prefineq")],na.rm = T)
@@
 sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
-# #hist.default(df1$egal2)
-```
-
-# Trust
-
-```{r}
-# sjmisc::frq(df1$v35)
-df1$socialtrust <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
-df1$socialtrust <- set_na(df1$socialtrust,na = c(0,8,9))
-df1$socialtrust <- sjmisc::rec(x = df1$socialtrust,rec = "rev")
-# sjmisc::frq(df1$socialtrust)
-# hist.default(df1$socialtrust)
 ```
@@
 
-```{r}
+```{r education}
 #frq(df1$EDUCYRS)
@@
 
-```{r subjstatus}
-df1$sstatus <- car::recode(df1$topbot, "c(0,98,99)=NA") 
-#frq(df1$sstatus)
-```
-
 # Occupational variables
@@
 
-```{r union}
-frq(df1$UNION)
-df1$union <- car::recode(as.numeric(df1$UNION),
-                         recodes= "1:2='Yes';c(0,3,7)='No';8:9=NA",
-                         levels = c("No","Yes"),as.factor = T)
-frq(df1$union)
-```
-
 ```{r isei}
@@
 frq(df1$n_employees_spo)
-
-haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
-                              "is_supervisor","self_employed","n_employees",
-                              "isco88spo","sempspo","supvisspo",
-                              "is_supervisor_spo","self_employed_spo","n_employees_spo")],
-                 path = here::here("input/data/proc/ocup_respondent-spouse.dta"))
-```
-
-```{r class-from-stata1}
-# Load the data created in stata------------------------------------------------
-df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
-df1 <- left_join(df1,df_class,by='id')
-
-# Class R´s and Spouse----------------------------------------------------------
-frq(df1$class10)
-
-# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$class10f <- as_factor(df1$class10)
-frq(df1$class10f)
-
-df1$class10f <- factor(df1$class10f,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$class10f <- as_labelled(df1$class10f)
-sjlabelled::set_label(df1$class10f) <- "Social Class - respondent"
-frq(df1$class10f)
-
-df1$class10spof <- as_factor(df1$class10spo)
-frq(df1$class10spof)
-
-df1$class10spof <-factor(df1$class10spof,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$class10spof <- as_labelled(df1$class10spof)
-sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse";frq(df1$class10spof)
-#if NA in class of respondent, replace with spouse
-
-frq(df1$class10f)
-frq(df1$class10spof)
-
-df1$class11 <- ifelse(is.na(df1$class10f),df1$class10spof,df1$class10f)
-frq(df1$class11)
-
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one, just for those
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$class11d <- pmax(df1$class11, #social class respondent + spouse vs:
-                     df1$class10spof,#social class spouse
-                     na.rm = T) # if NA, do nothing
-frq(df1$class11d)
-df1$class11d <- 
-  sjlabelled::set_labels(df1$class11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
-                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$class11d) <- "Social Class"
-frq(df1$class11d)
-
-# Class Scheme 3 classes
-df1$class3 <- car::recode(df1$class11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3) <- "Social Class Dominance (isko - v1 - V to Intermediate)";frq(df1$class3)
-
-df1$class3_V <- car::recode(df1$class11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3_V) <- "Social Class Dominance (isko - v1 - V to Working Class)";frq(df1$class3_V)
-
-# Class Scheme 6 classes
-df1$class6 <- car::recode(
-  df1$class11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-# Class only R's --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$class3res <- car::recode(as.numeric(df1$class10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3res) <- "Social Class 3 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class3res)
-
-df1$class3res_V <- car::recode(as.numeric(df1$class10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3res_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3res_V)
-
-# Class Scheme 6 classes
-df1$class6res <- car::recode(
-  as.numeric(df1$class10f),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$class6res) <- "Social Class 6 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class6res)
-# Class only Spouse --------------------------------------------------------------
-
-# Class Scheme 3 classes
-df1$class3spo <- car::recode(as.numeric(df1$class10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:10='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3spo) <- "Social Class 3 (Spouse) - (isko - v1 -  V to Intermediate)";frq(df1$class3spo)
-
-df1$class3spo_V <- car::recode(as.numeric(df1$class10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:10='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3spo_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3spo_V)
-
-# Class Scheme 6 classes
-df1$class6spo <- car::recode(
-  as.numeric(df1$class10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-sjlabelled::set_label(df1$class6spo) <- "Social Class 6 (Spouse) - (isko - v1)";frq(df1$class6spo) 
-```
-
-```{r class-from-stata2}
-# Class R´s and Spouse----------------------------------------------------------
-frq(df1$digclass10)
-
-# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$digclass10f <- as_factor(df1$digclass10)
-frq(df1$digclass10f)
-
-df1$digclass10f <- factor(df1$digclass10f,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-df1$digclass10f <- as_labelled(df1$digclass10f)
-sjlabelled::set_label(df1$digclass10f) <- "Social Class - respondent"
-frq(df1$digclass10f)
-df1$digclass10spof <- as_factor(df1$digclass10spo)
-frq(df1$digclass10spof)
-
-df1$digclass10spof <-factor(df1$digclass10spof,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$digclass10spof <- as_labelled(df1$digclass10spof)
-sjlabelled::set_label(df1$digclass10spof) <- "Social Class - spouse"
-
-frq(df1$digclass10spof)
-#if NA in class of respondent, replace with spouse
-
-frq(df1$digclass10f)
-frq(df1$digclass10spof)
-
-df1$digclass11 <- ifelse(is.na(df1$digclass10f),df1$digclass10spof,df1$digclass10f)
-frq(df1$class11)
-
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one, just for those
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
-                     df1$digclass10spof,#social class spouse
-                     na.rm = T) # if NA, do nothing
-frq(df1$digclass11d)
-df1$digclass11d <- 
-  sjlabelled::set_labels(df1$digclass11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
-                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$digclass11d) <- "Social Class 11 (isko - v2)"
-frq(df1$digclass11d)
-
-# Class Scheme 3 classes
-df1$digclass3 <- car::recode(df1$digclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3) <- "Social Class 3 (isko - v2 - V to Intermediate) ";frq(df1$digclass3)
-
-df1$digclass3_V <- car::recode(df1$digclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3_V)
-
-# Class only R's --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$digclass3res <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3res) <- "Social Class 3 (R's) - (V to Intermediate - isko - v2)";frq(df1$digclass3res)
-
-df1$digclass3res_V <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3res_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3res_V)
-
-# Class Scheme 6 classes
-df1$digclass6res <- car::recode(
-  as.numeric(df1$digclass10),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$digclass6res) <- "Social Class 6 (R's) - (isko - v2)"
-
-# Class only Spouse --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$digclass3spo <- car::recode(as.numeric(df1$digclass10spo),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate - isko - v2)";frq(df1$digclass3spo)
-
-df1$digclass3spo_V <- car::recode(as.numeric(df1$digclass10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3spo_V) <- "Social Class 3 (Spouse) (V to Working Class - isko - v2)";frq(df1$digclass3spo_V)
-
-# Class Scheme 6 classes
-df1$digclass6spo <- car::recode(
-  as.numeric(df1$digclass10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-sjlabelled::set_label(df1$digclass6spo) <- "Social Class  6 (Spouse) - (isko - v2)"
-```
-
-# Class using R
-
-```{r digclass-egp}
-# install.packages("devtools") 
-# devtools::install_git("https://code.europa.eu/digclass/digclass.git")
-
-library("DIGCLASS")
-library(dplyr)
-
-df1 <- 
-df1 %>% 
-mutate(egp11 = isco88_to_egp(isco88r, self_employed, n_employees, label = F,to_factor = T),
-       egp11spo = isco88_to_egp(isco88spo, self_employed_spo, n_employees_spo, label = F,to_factor = T))
-
-frq(df1$egp11)
-df1$egp11 <- as_numeric(df1$egp11)
-frq(df1$egp11)
-
-frq(df1$egp11spo)
-df1$egp11spo <- as_numeric(df1$egp11spo)
-frq(df1$egp11spo)
-
-#if NA in class of respondent, replace with spouse
-df1$dclass11 <- ifelse(is.na(df1$egp11),df1$egp11spo,df1$egp11)
-
-frq(df1$dclass11)
-#0.1 label respondent egp11 classes
-df1$egp11 <- 
-  sjlabelled::set_labels(df1$egp11,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
-                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb"))
-
-#0.2 label spouse egp11 classes
-df1$egp11spo <- 
-  sjlabelled::set_labels(df1$egp11spo,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
-                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb"))
-
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one, just for those
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$dclass11d <- pmax(df1$egp11, #social class respondent + spouse vs:
-                     df1$egp11spo,#social class spouse
-                     na.rm = T) # if NA, do nothing
-frq(df1$dclass11d)
-df1$dclass11d <- as_numeric(df1$dclass11d)
-frq(df1$dclass11d)
-
-df1$dclass11d <- 
-  sjlabelled::set_labels(df1$dclass11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
-                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb"))
-
-sjlabelled::set_label(df1$dclass11d) <- "Social Class 11 Dominance (EGP11 -  DIGICLASS)";frq(df1$dclass11d)
-
-# Class scheme using dominance-------------------------------------------------
-# # Class Scheme 3 classes -  V to intermediate class
-df1$dclass3 <- car::recode(df1$dclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:8='Intermediate class (III+IV+V)';
-                             9:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3) <- "Social Class 3 Dominance (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3)
-
-# Class Scheme 3 classes -  V to working class
-df1$dclass3_V <- car::recode(df1$dclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV)';
-                             8:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3_V) <- "Social Class 3 Dominance (V to Working Class - DIGCLASS)";frq(df1$dclass3_V)
-
-# Class Scheme 3 classes -  IIIb to working class
-df1$dclass3_III <- car::recode(df1$dclass11d,as.factor = T,
-                            levels =c('Service Class',
-                                      'Intermediate class',
-                                      'Working Class'), 
-                            "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
-
-sjlabelled::set_label(df1$dclass3_III) <- "Social Class 3 Dominance (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3_III)
-
-# Class Scheme 3 classes -  IIIb and V to working class
-df1$dclass3_III_V <- car::recode(df1$dclass11d,as.factor = T,
-                            levels =c('Service Class',
-                                      'Intermediate class',
-                                      'Working Class'), 
-                            "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
-
-sjlabelled::set_label(df1$dclass3_III_V) <- "Social Class 3 Dominance (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3_III)
-
-# Class Scheme 6 classes
-df1$dclass6 <- car::recode(
-  df1$dclass11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$dclass6) <- "Social Class 6 Dominance (DIGCLASS)"
-```
+```
+
+# Social Class
 
@@
 
-```{r digclass-egp-spouse}
-# Class scheme using Spouse-------------------------------------------------
-# # Class Scheme 3 classes -  V to intermediate class
-
-df1$dclass3spo <- car::recode(df1$egp11spo,as.factor = T,
-                              levels =c('Service Class (I+II)',
-                                        'Intermediate class (III+IV+V)',
-                                        'Working Class (VI+VII)'), 
-                              "1:2='Service Class (I+II)';
-                             3:8='Intermediate class (III+IV+V)';
-                             9:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3spo)
-
-# Class Scheme 3 classes -  V to working class
-df1$dclass3spo_V <- car::recode(df1$egp11spo,as.factor = T,
-                                levels =c('Service Class (I+II)',
-                                          'Intermediate class (III+IV)',
-                                          'Working Class (V+VI+VII)'), 
-                                "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV)';
-                             8:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$dclass3spo_V) <- "Social Class 3 (Spouse) - (V to Working Class - DIGCLASS)";frq(df1$dclass3spo_V)
-
-# Class Scheme 3 classes -  IIIb to working class
-df1$dclass3spo_III <- car::recode(df1$egp11spo,as.factor = T,
-                                  levels =c('Service Class',
-                                            'Intermediate class',
-                                            'Working Class'), 
-                                  "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")
-
-sjlabelled::set_label(df1$dclass3spo_III) <- "Social Class 3 (Spouse) - (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3spo_III)
-
-# Class Scheme 3 classes -  IIIb and V to working class
-df1$dclass3spo_III_V <- car::recode(df1$egp11spo,as.factor = T,
-                                    levels =c('Service Class',
-                                              'Intermediate class',
-                                              'Working Class'), 
-                                    "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")
-
-sjlabelled::set_label(df1$dclass3spo_III_V) <- "Social Class 3 (Spouse) - (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3spo_III_V)
-```
-
-# Networks
-
-```{r generador}
+# Social Networks
+
+```{r generator}
 ocupations <- names(dplyr::select(df1,v1:v10))
@@
 
-```{r strenght-ties}
-ocupations <- names(dplyr::select(df1,v1:v10))
-vl<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Tie strenght:")
-vl2<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Strong tie:")
-vl3<- dplyr::select(df1,busdriver:teacher) %>% get_label() %>% stringr::str_replace_all(pattern = "Know:",replacement = "Weak tie:")
-
-for (i in 1:length(ocupations)) {
-  df1[[i]] <- car::recode(df1[[i]],"c(8,9)=NA")
-  df1[[i]] <- sjlabelled::set_na(df1[[i]],na = c(8,9))
-}
-lb <- c("Absent"=0,"Weak"=1,"Strong"=2)
-lb2 <- c("Strong"=1,"Weak"=0)
-lb3 <- c("Strong"=0,"Weak"=1)
-r <- "4=0;3=1;1:2=2"
-r2 <- "1:2=1;3=0;4=NA"
-r3 <- "1:2=0;3=1;4=NA"
-
-df1 <- df1 %>%
-  # Tie strenght
-  mutate("busdriver_ts" = set_labels(car::recode(df1$v1,r),labels = lb),
-         "ceo_ts" =  set_labels(car::recode(df1$v2,r),labels = lb),
-         "cleaner_ts" = set_labels(car::recode(df1$v3,r),labels = lb),
-         "hairbarber_ts"  = set_labels(car::recode(df1$v4,r),labels = lb),
-         "hrmanager_ts" = set_labels(car::recode(df1$v5,r),labels = lb),
-         "lawyer_ts"  = set_labels(car::recode(df1$v6,r),labels = lb),
-         "mechanic_ts" = set_labels(car::recode(df1$v7,r),labels = lb),
-         "nurse_ts" = set_labels(car::recode(df1$v8,r),labels = lb),
-         "police_ts"  = set_labels(car::recode(df1$v9,r),labels = lb),
-         "teacher_ts" = set_labels(car::recode(df1$v10, r, as.factor = T), labels = lb)) %>%
-  # strong ties  
-  mutate("busdriver_s" = set_labels(car::recode(df1$v1,r2),labels = lb2),
-         "ceo_s" =  set_labels(car::recode(df1$v2,r2),labels = lb2),
-         "cleaner_s" = set_labels(car::recode(df1$v3,r2),labels = lb2),
-         "hairbarber_s"  = set_labels(car::recode(df1$v4,r2),labels = lb2),
-         "hrmanager_s" = set_labels(car::recode(df1$v5,r2),labels = lb2),
-         "lawyer_s"  = set_labels(car::recode(df1$v6,r2),labels = lb2),
-         "mechanic_s" = set_labels(car::recode(df1$v7,r2),labels = lb2),
-         "nurse_s" = set_labels(car::recode(df1$v8,r2),labels = lb2),
-         "police_s"  = set_labels(car::recode(df1$v9,r2),labels = lb2),
-         "teacher_s" = set_labels(car::recode(df1$v10, r2), labels = lb2)) %>% 
-  # weak ties
-  mutate("busdriver_w" = set_labels(car::recode(df1$v1,r3),labels = lb3),
-         "ceo_w" =  set_labels(car::recode(df1$v2,r3),labels = lb3),
-         "cleaner_w" = set_labels(car::recode(df1$v3,r3),labels = lb3),
-         "hairbarber_w"  = set_labels(car::recode(df1$v4,r3),labels = lb3),
-         "hrmanager_w" = set_labels(car::recode(df1$v5,r3),labels = lb3),
-         "lawyer_w"  = set_labels(car::recode(df1$v6,r3),labels = lb3),
-         "mechanic_w" = set_labels(car::recode(df1$v7,r3),labels = lb3),
-         "nurse_w" = set_labels(car::recode(df1$v8,r3),labels = lb3),
-         "police_w"  = set_labels(car::recode(df1$v9,r3),labels = lb3),
-         "teacher_w" = set_labels(car::recode(df1$v10, r3), labels = lb3))
-
-v = names(dplyr::select(df1,ends_with("_ts")))
-df1[,v]<- set_label(x = df1[,v],label = vl) #label Tie strenght
-
-s = names(dplyr::select(df1,ends_with("_s")))
-df1[,s]<- set_label(x = df1[,s],label = vl2) #label strong tie
-
-w = names(dplyr::select(df1,ends_with("_w")))
-df1[,w]<- set_label(x = df1[,w],label = vl3) #label weak tie
-
-df1$know_total_s <- rowSums(x = select(df1,ends_with("_s")),na.rm = T)
-sjlabelled::set_label(df1$know_total_s) <- 'Total of known occupations (strong ties)'
-
-df1$know_total_w <- rowSums(x = select(df1,ends_with("_w")),na.rm = T)
-sjlabelled::set_label(df1$know_total_s) <- 'Total of known occupations (weak ties)'
-
-```
-
-```{r strenght-num}
-# strong ties
-df1$n_high_s<-rowSums(x = df1[c("lawyer_s","hrmanager_s","ceo_s")],na.rm = T)
-set_label(df1$n_high_s) <- 'Number of high status contacts (strong ties)'
-
-df1$n_middle_s<-rowSums(x = df1[c("teacher_s","police_s","nurse_s")],na.rm = T)
-set_label(df1$n_middle_s) <- 'Number of middle status contacts (strong ties)'
-
-df1$n_low_s <- rowSums(x = df1[c("mechanic_s","busdriver_s","hairbarber_s","cleaner_s")],na.rm = T)
-set_label(df1$n_low_s) <- 'Number of low status contacts (strong ties)'
-
-# weak ties
-df1$n_high_w<-rowSums(x = df1[c("lawyer_w","hrmanager_w","ceo_w")],na.rm = T)
-set_label(df1$n_high_w) <- 'Number of high status contacts (weak ties)'
-
-df1$n_middle_w<-rowSums(x = df1[c("teacher_w","police_w","nurse_w")],na.rm = T)
-set_label(df1$n_middle_w) <- 'Number of middle status contacts (weak ties)'
-
-df1$n_low_w <- rowSums(x = df1[c("mechanic_w","busdriver_w","hairbarber_w","cleaner_w")],na.rm = T)
-set_label(df1$n_low_w) <- 'Number of low status contacts (weak ties)'
-```
-
 ```{r isei-generador}
@@
 sjlabelled::set_label(df1$n_high) <- 'Number of high status contacts'
-# sjPlot::plot_#frq(df1$n_high,type = 'density')
-
-# percentage of high status contacts
-
-df1$pct_high <- (df1$n_high/df1$know_total)*100
-sjlabelled::set_label(df1$df1$pct_high ) <- 'Percentage of high status contacts'
-# sjPlot::plot_#frq(df1$pct_high,type = 'density')
 
@@
 sjlabelled::set_label(df1$n_middle) <- 'Number of middle status contacts'
-# sjPlot::plot_#frq(df1$n_middle,type = 'density')
-
-# percentage of middle status contacts
-df1$pct_middle <- (df1$n_middle/df1$know_total)*100
-sjlabelled::set_label(df1$pct_middle) <- 'Percentage of middle status contacts'
-# sjPlot::plot_#frq(df1$pct_middle,type = 'density')
 
 # number of low status contacts
-# df1$n_low <- 
-#   rowSums(x = select(df1,c("n_waiter","n_carmech","n_taxi","n_stvend","n_cleaner")),na.rm = T)
 df1$n_low <- 
@@
 sjlabelled::set_label(df1$n_low) <- 'Number of low status contacts'
-# sjPlot::plot_#frq(df1$n_low,type = 'density')
-
-# percentage of low status contacts
-df1$pct_low <- (df1$n_low/df1$know_total)*100
-sjlabelled::set_label(df1$pct_low) <- 'Percentage of low status contacts'
-# sjPlot::plot_#frq(df1$pct_low,type = 'density')
 
 # Average ISEI 
-df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) #REVISAR NO DEBERIA CONTENER 0
+#REVIEW SHOULD NOT CONTAIN 0
+df1$isei_avg <- rowMeans(x = select(df1,isei_ocupnames),na.rm = T) 
 sjlabelled::set_label(df1$isei_avg) <- 'Average contact prestige'
 summary(df1$isei_avg)
-
-# sjPlot::plot_#frq(df1$isei_avg,type = 'density')
-
-# Total ISEI 
-df1$isei_tot <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
-sjlabelled::set_label(df1$isei_tot) <- 'Total contact prestige'
-summary(df1$isei_tot)
-# sjPlot::plot_#frq(df1$isei_tot,type = 'density')
-
-# skimr::skim(df1$isei_tot/df1$n_total)
-# skimr::skim(df1$isei_tot/df1$know_total)
-# skimr::skim(df1$isei_avg)
-
-# max ISEI 
-df1 <- df1 %>% 
-mutate(isei_max = do.call(pmax, c(select(., isei_ocupnames), na.rm = TRUE)))
-sjlabelled::set_label(df1$isei_max) <- 'Maximum contact prestige'
-# sjmisc::frq(df1$isei_max)
-# sjPlot::plot_#frq(df1$isei_max)
-
-# min ISEI
-df1 <- df1 %>% 
-mutate(isei_min = do.call(pmin, c(select(., isei_ocupnames), na.rm = TRUE)))
-sjlabelled::set_label(df1$isei_min) <- 'Minimum contact prestige'
-# sjmisc::frq(df1$isei_min)
-# sjPlot::plot_#frq(df1$isei_min)
-
-# range ISEI
-table(df1$know_total>=2)
-df1$isei_range <- ifelse(df1$know_total>=2,(df1$isei_max - df1$isei_min),no = NA)
-
-sjlabelled::set_label(df1$isei_range) <- 'Range contact prestige'
-# sjmisc::frq(df1$isei_range)
-# sjPlot::plot_#frq(df1$isei_range)
-# df1 %>% select(starts_with("isei_")) %>%View
-
-cor(df1[,c("isei_avg","isei_max","isei_range",
-                 "know_total","n_high","n_middle","n_low",
-                 "pct_high","pct_middle","pct_low")],use = "complete.obs")
-```
-
-```{r heterogeneity, eval=FALSE, include=FALSE}
-isei_ocupnames<- names(select(df1,busdriver:teacher))
-
-df1$hindex_sta<- 
-as.numeric(
-  1 - (
-    #p1^2
-    (df1$n_high / df1$know_total)^2 +
-    #p2^2
-    (df1$n_middle / df1$know_total)^2 +
-    #p3^2
-    (df1$n_low / df1$know_total)^2
-    )
-  )
-
-sjlabelled::set_label(df1$hindex_sta) <- "D-index: status groups"
-
-df1$hindex_10<- 
-as.numeric(
-  1 - (
-    #p1^2
-    (df1$busdriver/df1$know_total)^2 +
-    #p2^2
-    (df1$ceo / df1$know_total)^2 +
-    #p3^2
-    (df1$cleaner / df1$know_total)^2 +
-    #p3^2
-    (df1$hairbarber / df1$know_total)^2 +
-     #p3^2
-    (df1$hrmanager / df1$know_total)^2 +
-    #p3^2
-    (df1$lawyer / df1$know_total)^2+
-    #p3^2
-    (df1$mechanic / df1$know_total)^2+
-    #p3^2
-    (df1$nurse / df1$know_total)^2+
-    #p3^2
-    (df1$police / df1$know_total)^2+    
-    #p3^2
-    (df1$teacher / df1$know_total)^2        
-    )
-  )
-
-sjlabelled::set_label(df1$hindex_10) <- "D-index: 10 ocupations"
 ```
@@
 - using my original coding
-
-```{r homogeneity-v01-V-to-intermediate}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(class3,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
-#frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(class3,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-#frq(df1$outgroup)
-
-df1$homclass <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass) <- "Class homogeneity (isko v1 - V to Intermediate)"
-df1$homclass_gc <- group_center(x = df1$homclass,grp = df1$country)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-# EI homophily index
-df1$ingroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res)
-# frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
-# frq(df1$outgroup_res)
-
-df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's) (isko v1 - V to Intermediate)"
-```
-
-```{r homogeneity-v01-V-to-working}
-df1$ingroup <- NA 
-df1 %>% select(class3_V,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$class3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
-#frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1$outgroup <- ifelse(df1$class3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$class3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-#frq(df1$outgroup)
-
-df1$homclass_V <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass_V) <- "Class homogeneity (isko v1 - V to Working)"
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res_V=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$class3res_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
-# frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(class3res,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$class3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
-# frq(df1$outgroup_res)
-
-df1$homclass_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass_V_res) <- "Class homogeneity (R's) (isko v1 - V to Working)"
-```
-
-- Using my edited original coding. I recoded the variables from n_employees y self_employed. The class scheme changed a bit, where the Service class was overestimated. This should be better:
-
-```{r homogeneity-v02-V-intermediate}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(digclass3,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$digclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
-#frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(digclass3,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$digclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-#frq(df1$outgroup)
-
-df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass2) <- "Class homogeneity Dominance (isko - v2 - V to intermediate)"
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(digclass3res,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res)
-# frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res)
-# frq(df1$outgroup_res)
-
-df1$homclass2_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_res) <- "Class homogeneity (R's) (isko - v2 - V to intermediate)";frq(df1$homclass_res)
-```
-
-```{r homogeneity-v02-V-working}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(digclass3_V,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup)
-#frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(digclass3,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$digclass3_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$digclass3_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-# frq(df1$outgroup)
-
-df1$homclass2_V <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass2_V) <- "Class homogeneity Dominance (isko - v2- V to Working)";frq(df1$homclass2_V)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(digclass3res_V,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res_V=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res_V=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$digclass3res_V=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(digclass3res_V,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$digclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass2_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass2_V_res) <- "Class homogeneity (R's) (isko - v2 - V to working)";frq(df1$homclass2_V_res)
-```
-
-```{r homogeneity-R-digclass-V-intermediate}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(class3,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$dclass3=="Service Class (I+II)",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",df1$n_low,df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(class3,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$dclass3=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-
-df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3) <- "Class homogeneity Dominance (DIGCLASS - V to intermediate)";frq(df1$homclass3)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res=="Intermediate class (III+IV+V)",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res=="Working Class (VI+VII)",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res=="Service Class (I+II)",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res=="Working Class (VI+VII)",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass3_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_res)
-```
 
@@
 
-```{r homogeneity-R-digclass-plus-partner}
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",df1$n_high_partner,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",df1$n_mid_partner,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",df1$n_low_partner,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low_partner","n_mid_partner")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_partner","n_high_partner")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_mid_partner","n_high_partner")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$know_total_partner <- rowSums(df1[,c("n_high_partner","n_mid_partner","n_low_partner")],na.rm = T);sjlabelled::set_label(df1$know_total_partner) <- "Number of contacts + partner"
-
-df1$homclass3_V_res_part <- as.numeric(df1$ingroup_res/df1$know_total_partner)
-sjlabelled::set_label(df1$homclass3_V_res_part) <- "Class homogeneity (R's) + partner tie (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res_part)
-cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
-summary(df1$homclass3_V_res_part)
-summary(df1$homclass3_V_res)
-cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res,outgroup_res,know_total_partner)
-```
-
-```{r homogeneity-R-digclass-IIIb-working}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(dclass3_III,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Service Class",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Intermediate class",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Working Class",df1$n_low,df1$ingroup);frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(dclass3_III,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup);frq(df1$outgroup)
-
-df1$homclass3_III <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III) <- "Class homogeneity Dominance (DIGCLASS version - IIIb to Working)";frq(df1$homclass3_III)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_III,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Service Class",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass3_III_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_res)
-```
-
-```{r homogeneity-R-digclass-IIIb-V-working}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Service Class",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Intermediate class",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Working Class",df1$n_low,df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-
-df1$homclass3_III_V <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_V) <- "Class homogeneity Dominance (DIGCLASS version - IIIb+V to Working)";frq(df1$homclass3_III_V)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass3_III_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_V_res)
-```
-
-```{r social distance, include=FALSE}
+```{r homogeneity-isei, include=FALSE}
 df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
@@
 
-```{r}
-
-sjmisc::frq(df1$v46)
-
-table(df1$country,df1$v46)
-
-# (1+4)/2
-# (5+9)/2
-# (10+19)/2
-# (20+49)/2
-# (50+99)/2
-# 100
-
-df1$week_cont <- as.numeric(car::recode(df1$v46,"c(8,9)=NA;1=2.5;2=7;3=14.5;4=34.5;5=74.5;6=100"))
-
-sjmisc::frq(df1$week_cont)
-sjPlot::tab_corr(df1[,c("know_total","week_cont","homclass","homclass_V","homclass2","homclass2_V")])
-
-df1$homclass
-
-a <- df1 %>% dplyr::select("know_total","week_cont","homclass") 
-a$country <- NULL
-a$week_cont <- as.factor(a$week_cont)
-polycor::hetcor(data = as.data.frame(a))
-
-sjPlot::plot_grpfrq(var.grp = df1$class6,var.cnt = df1$know_total,type = "box",ylim = c(0,10))
-sjPlot::plot_grpfrq(var.grp = df1$class6,var.cnt = df1$week_cont,type = "box",ylim = c(2.5,100))
-```
-
 # Demographics
@@
 sjlabelled::set_label(df1$agenum) <- "Age in years"
-#frq(df1$agenum)
-
-#frq(df1$SEX)
+
 df1$female <- car::recode(as.numeric(df1$SEX),"2='Female';1='Male';9=NA",
                           levels = c('Male','Female'),as.factor = T)
-#frq(df1$female)
-
-frq(df1$ATTEND)
-df1$relig <- car::recode(df1$ATTEND,recodes = "c(97,98,99)=NA",as.numeric = T)
-df1$relig <- set_na(df1$relig,na = c(97,98,99))
-df1$relig <- sjmisc::rec(x = df1$relig,rec = "rev")
-frq(df1$relig)
-
-df1$religcat <- car::recode(df1$ATTEND,recodes = "0=0;1:7=1;c(97,98,99)=NA",as.factor = T)
-df1$religcat <- set_na(df1$religcat,na = c(97,98,99))
-sjlabelled::set_label(df1$religcat) <- "Attendance of religious services"
-frq(df1$religcat)
-
-frq(df1$RELIGGRP)
-df1$religion <- car::recode(df1$RELIGGRP,recodes = "0=0;1:10=1;c(97,98,99)=NA",as.factor = T)
-df1$religion <- set_na(df1$religion,na = c(97,98,99))
-sjlabelled::set_label(df1$religion) <- "Religion"
-df1$religion <- factor(df1$religion,labels = c("No Religion","Has Religion"))
-frq(df1$religion)
 
@@
 ```
-
-# Backup code
-
-```{r homogeneity-strong-v01, eval=FALSE, include=FALSE}
-# EI homophily index
-df1$ingroup_s<- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_s,df1$ingroup_s)
-#frq(df1$ingroup_s)
-
-df1$outgroup_s <- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
-#frq(df1$outgroup_s)
-
-df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
-sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
-#frq(df1$eindex_s)
-#hist.default(df1$eindex_s)
-
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
-df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
-sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
-#hist.default(df1$homclass_s)
-```
-
-```{r homogeneity-weak-v01, eval=FALSE, include=FALSE}
-# EI homophily index
-df1$ingroup_w<- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_w,df1$ingroup_w)
-# frq(df1$ingroup_w)
-
-df1$outgroup_w <- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
-# frq(df1$outgroup_w)
-
-df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
-sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
-frq(df1$eindex_w)
-#hist.default(df1$eindex_w)
-
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
-df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
-sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
-#hist.default(df1$homclass_s)
-```
-
-(i)  the highest status job accessed (upper reachability),
-(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
-(iii) the total number of occupations accessed (network extensity),
-(iv) the total accessed prestige (resource volume),
-(v) the average status of jobs accessed (network prestige),
-(vi) the total number of higher-status positions accessed,
-(vii) the total number of medium-status positions accessed,
-(viii) the total number of lower-status positions accessed.
-
-```{r pca, eval=FALSE, include=FALSE}
-library(psych)
-library(dplyr)
-isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
-
-# Calculate the standard deviation for each column
-df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
-
-# Print the standard deviation for each column
-# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
-
-# reduce dimensions in 2: diversity and prestige
-df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
-summary(df_cs)
-dim(df_cs)
-
-# df_cs <- na.omit(df_cs)
-cor<- corr.test(df_cs)
-psych::KMO(r = cor$r)
-cortest.bartlett(cor$r,n = dim(df_cs)[1])
-plot(scree(df_cs,factors = 2))
-
-# Porcentaje de varianza explicada
-fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
-fit1$loadings
-plot(fit1,labels = c(names(df_cs)))
-cor(fit1$scores)
-
-fit2<- psych::fa(df_cs,nfactors = 2)
-plot(fit2,labels = c(names(df_cs)))
-fit2$scores
-cor(fit2$scores)
-fs<- as.data.frame(fit2$scores)
-names(fs) <- c("diversity","prestige")
-
-df1 <- bind_cols(df1,fs)
-sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
-sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
-```

### 2025-07-29 procesamiento/02-prod_prep-country.Rmd
ajustes data micro

--- 2024-05-08 procesamiento/02-prod_prep-macro.Rmd
@@
 
+# Class inequality
+
+<!-- We calculated this statistic through a simple earnings regression controlling for age, age squared, and occupation (ISCO 2-digits) in large samples (EU-SILC), or directly for each class in smaller samples (ISSP, EU-EQ), based on the weighted individual data from the IDS; we made these calculations separately for men and women.
+Based on predicted wage rates, we calculated average hourly wages for each class and took the ratio thereof for different OD class pairs in order to obtain the between-class wage inequality measure.
+In order to minimize the role of yearly fluctuations (or the 2007-2008 financial crisis), we took the average of yearly ratios available over the first decade of the 21st century.
+-->
+
+<!-- First, determine the total number of hours worked by multiplying the hours per week by the number of weeks in a year (52).
+Next, divide this number from the annual salary.
+For example, if an employee has a salary of $50,000 and works 40 hours per week, the hourly rate is $50,000/2,080 (40 x 52) = $24.04.
+-->
+
+```{r classineq-data}
+summary(df1$incomer)
+summary(df1$egp11)
+library(DIGCLASS)
+frq(df1$WRKHRS)
+df1$weekhour <- car::recode(df1$WRKHRS,"c(0,95,96,98,99)=NA")
+summary(df1$weekhour); hist(df1$weekhour)
+# weekhour * 4 =  monthly worked hours
+df1$monthhour <- df1$weekhour*4
+countries <- unique(countrycode::countrycode(df1$country,"iso3n","iso3c"))
+df1$hhincome <- as.numeric(df1$income/sqrt(df1$hhpop)) # Ingreso per capita del hogar
+summary(df1$hhincome)
+# Wages for Males
+males<- df1%>% 
+  filter(female=="Male" & agenum %in% c(18:55)) %>% 
+  mutate(country3=countrycode::countrycode(country,"iso3n","iso3c")) %>% 
+  select(id,incomer=hhincome,agenum,isco88r,WEIGHT,country3) %>% 
+  mutate(isco88_2=factor(isco88_swap(isco88r,from = 4,to = 2)),
+         age2=agenum*agenum) %>% na.omit()
+
+# Step 1: Model wages: income regressed age, age squared and occupation
+wages_male <- list() 
+for (i in countries) {
+wages_male[[i]] <-  lm(incomer~agenum+age2+isco88_2,data = males,subset = (country3==i),weights = WEIGHT)
+}
+
+# Step 2: predicted wages
+
+predicted_male <- list()
+for (i in countries) {
+  predicted_male[[i]] <- data.frame(wages=predict.lm(wages_male[[i]]),country=i)
+  }
+# Step 3: save predicted values
+wages_male_df<- bind_rows(predicted_male);dim(wages_male_df)
+males$wages_male<- wages_male_df$wages
+summary(males$wages_male);hist(males$wages_male)
+table(males$wages_male>=0)
+
+# Wages for Females
+females<- df1 %>% 
+  filter(female=="Female" & agenum %in% c(18:55)) %>%
+  mutate(country3=countrycode::countrycode(country,"iso3n","iso3c")) %>%   
+  select(id,incomer,agenum,isco88r,WEIGHT,country3) %>% 
+  mutate(isco88_2=factor(isco88_swap(isco88r,from = 4,to = 2)),
+         age2=agenum*agenum) %>% na.omit() 
+# Step 1: Model wages: income regressed on education, age age squared and occupation
+wages_female <- list() 
+for (i in countries) {
+wages_female[[i]] <-  lm(incomer~agenum+age2+isco88_2,data = females,subset = (country3==i),weights = WEIGHT)
+}
+
+# Step 2: predicted wages 
+predicted_female <- list()
+for (i in countries) {
+  predicted_female[[i]] <- data.frame(wages=predict(wages_female[[i]]),country=i)
+  }
+# Step 3: save predicted values
+wages_female_df<- bind_rows(predicted_female)
+females$wages_female<- wages_female_df$wages
+summary(females$wages_female);hist(females$wages_female)
+table(females$wages_female>=0)
+
+# Step 4 create the wage, male female dataset to merge to the main data
+wages_df<- 
+bind_rows(
+females %>% select(id,wages=wages_female),
+males %>% select(id,wages=wages_male)
+)
+#Step 5 merge predicted wages to currentdataset
+df1 <- left_join(df1,wages_df,"id")
+
+#Step 6: calculate the weekly per hour wage
+df1$wageratio <- df1$wages/df1$monthhour
+summary(df1$wageratio);hist(df1$wageratio)
+table(df1$wageratio>=0)
+df1$wageratio[df1$wageratio<0] <- NA # wage ratio per hour lower than 0 is NA
+summary(df1$wageratio);hist(df1$wageratio)
+
+# Final: create the dataset for the 6 classes and respective income, education and wage averages
+
+df_hhincome <- 
+df1 %>%   
+  group_by(country,dclass6res) %>%
+  summarise(
+    n=n(),
+    "incomer"=mean(hhincome,na.rm = TRUE)) %>% 
+  as.data.frame() %>% 
+  na.omit()
+
+df_education <- 
+df1 %>%   
+  filter(agenum %in% c(18:64)) %>% 
+  group_by(country,dclass6res) %>%
+  summarise("ednum"=mean(edyears,na.rm = TRUE)) %>%
+  ungroup() %>% 
+  # select(-country,-dclass6res) %>%
+  as.data.frame() %>% 
+  na.omit()
+
+df_wages <- 
+df1 %>%   
+  group_by(country,dclass6res) %>%
+  summarise("wageratio"=mean(wageratio,na.rm = TRUE)) %>%
+  ungroup() %>% 
+  # select(-country,-dclass6res) %>%
+  as.data.frame() %>% 
+  na.omit()
+
+table(df_hhincome$country)
+table(df_education$country)
+table(df_wages$country)
+
+df_class3_ineq<- bind_cols(df_hhincome,df_education %>% select(ednum),df_wages %>% select(wageratio))
+df_class3_ineq$country <- countrycode::countrycode(df_class3_ineq$country,"iso3n","iso3c") 
+summary(df_class3_ineq)
+```
+
+```{r template, eval=FALSE, include=FALSE}
+# Step 1: Create the vector of average incomes
+average_incomes <- c(upper = 1000, routine = 700, self_employed = 900, working = 500)
+
+# Step 2: Create the matrix of ratios
+income_diff_matrix <- outer(average_incomes, average_incomes, FUN = function(x, y) y/x)
+
+# Step 3: Set the diagonal to 0
+diag(income_diff_matrix) <- 0
+
+# Step 4: Flatten the matrix, excluding the diagonal
+income_diff_vector <- income_diff_matrix[lower.tri(income_diff_matrix, diag = FALSE)] # Extract lower triangular matrix
+# income_diff_vector <- c(income_diff_vector, income_diff_matrix[upper.tri(income_diff_matrix, diag = FALSE)]) # Add upper triangular matrix
+
+# Step 5: Calculate the mean of the differences
+average_value <- mean(income_diff_vector)
+
+# Display the average value
+print(average_value)
+```
+
+```{r class-inq-income}
+# Step 0: prepare the data
+countries<- unique(df_class3_ineq$country)
+
+# Step 1: Create the vector of average incomes
+average_incomes <- df_class3_ineq %>% select(country,dclass6res,incomer)
+
+# Step 2: Create the matrix of ratios
+matrix_incomer <- list()
+for (i in countries) {
+  matrix_incomer[[i]] <- outer(subset(average_incomes,country==i)$incomer,subset(average_incomes,country==i)$incomer, FUN = function(x, y) y/x)
+}
+# Step 3: Set the diagonal to 0
+for (i in countries) {
+  diag(matrix_incomer[[i]]) <- 0
+}
+# Step 4: Flatten the matrix, excluding the diagonal
+for (i in countries) {
+  matrix_incomer[[i]] <- matrix_incomer[[i]][lower.tri(matrix_incomer[[i]], diag = FALSE)] # Extract lower triangular matrix
+}
+# Step 5: Calculate the mean of the differences
+average_incomeratio <- list()
+for (i in countries) {
+  average_incomeratio[[i]] <- mean(matrix_incomer[[i]])
+}
+
+# Display the average value
+print(average_incomeratio)
+```
+
+```{r class-inq-education}
+# Step 0: prepare the data
+countries<- unique(df_class3_ineq$country)
+
+# Step 1: Create the vector of average incomes
+average_education <- df_class3_ineq %>% select(country,dclass6res,ednum)
+
+# Step 2: Create the matrix of ratios
+matrix_education <- list()
+for (i in countries) {
+  matrix_education[[i]] <- outer(subset(average_education,country==i)$ednum,subset(average_education,country==i)$ednum, FUN = function(x, y) y/x)
+}
+# Step 3: Set the diagonal to 0
+for (i in countries) {
+  diag(matrix_education[[i]]) <- 0
+}
+# Step 4: Flatten the matrix, excluding the diagonal
+for (i in countries) {
+  matrix_education[[i]] <- matrix_education[[i]][lower.tri(matrix_education[[i]], diag = FALSE)] # Extract lower triangular matrix
+}
+# Step 5: Calculate the mean of the differences
+average_educratio <- list()
+for (i in countries) {
+  average_educratio[[i]] <- mean(matrix_education[[i]])
+}
+
+# Display the average value
+print(average_educratio)
+```
+
+```{r class-inq-wages}
+# Step 0: prepare the data
+countries<- unique(df_class3_ineq$country)
+
+# Step 1: Create the vector of average incomes
+average_wages <- df_class3_ineq %>% select(country,dclass6res,wageratio)
+
+# Step 2: Create the matrix of ratios
+matrix_wages <- list()
+for (i in countries) {
+  matrix_wages[[i]] <- outer(subset(average_wages,country==i)$wageratio,subset(average_wages,country==i)$wageratio, FUN = function(x, y) y/x)
+}
+# Step 3: Set the diagonal to 0
+for (i in countries) {
+  diag(matrix_wages[[i]]) <- 0
+}
+# Step 4: Flatten the matrix, excluding the diagonal
+for (i in countries) {
+  matrix_wages[[i]] <- matrix_wages[[i]][lower.tri(matrix_wages[[i]], diag = FALSE)] # Extract lower triangular matrix
+}
+# Step 5: Calculate the mean of the differences
+average_wageratio <- list()
+for (i in countries) {
+  average_wageratio[[i]] <- mean(matrix_wages[[i]])
+}
+
+# Display the average value
+print(average_wageratio)
+```
+
+```{r}
+df_classdiff<- data.frame(t(bind_rows(average_wageratio,average_incomeratio,average_educratio)))
+df_classdiff <- 
+df_classdiff %>% 
+  mutate(country= row.names(df_classdiff),
+         ccode= countrycode::countrycode(country, origin = "iso3c",destination = "iso3n")) %>% 
+  select(ccode,difclass_wage=X1,difclass_income=X2,difclass_educ=X3)
+
+psych::alpha(x = df_classdiff[,c("difclass_wage","difclass_income","difclass_educ")])
+psych::fa(df_classdiff[,c("difclass_wage","difclass_income","difclass_educ")])
+model1 <- 'classineq=~difclass_wage+difclass_income+difclass_educ'
+fit1<- lavaan::cfa(model = model1,data = df_classdiff)
+lavaan::summary(fit1,standardized=T,fit.measures=T)
+
+df_classdiff$difclass <- df_classdiff$difclass_wage + df_classdiff$difclass_income + df_classdiff$difclass_educ
+skimr::skim(df_classdiff)
+```
+
 ```{r merge}
@@
   left_join(wid_df1) %>% 
-  left_join(ilo_df)
+  left_join(ilo_df) %>% 
+  left_join(df_classdiff)
 
+correlation::correlation(macro_data)
 save(macro_data,file = here::here("input/data/proc/study1_macro_data.RData"))
@@
 
-# Class inequality
-
-```{r}
-summary(df1$incomepcap)
-
-df_class3_ineq <- 
-df2 %>%   
-  group_by(country2,dclass3res_V) %>%
-  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  na.omit() %>% 
-  dplyr::select(country2,dclass3res_V,incomepcap,ednum,wid_gini_disp) %>% 
-  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = c("incomepcap","ednum")) %>% 
-  mutate(ratio_class_inc = `incomepcap_Service Class (I+II)`/`incomepcap_Working Class (V+VI+VII)`,
-         ratio_class_educ  = `ednum_Service Class (I+II)`/`ednum_Working Class (V+VI+VII)`) %>% 
-  as.data.frame()
-
-df_class3_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
-
-df_class6_ineq <- 
-df2 %>%   
-  group_by(country2,dclass6res) %>%
-  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  na.omit() %>% 
-  dplyr::select(country2,dclass6res,incomepcap,ednum,wid_gini_disp) %>% 
-  tidyr::pivot_wider(names_from = "dclass6res", values_from = c("incomepcap","ednum")) %>% 
-  mutate(ratio_class_inc = `incomepcap_Upper Service class`/`incomepcap_Unskilled working class`,
-         ratio_class_educ  = `ednum_Upper Service class`/`ednum_Unskilled working class`) %>% 
-  as.data.frame() 
-df_class_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
-```
-
-```{r}
-
-income_data
-
-# Example data
-# Assuming you have a data frame called 'income_data' with columns: country, social_class, and average_income
-
-# Calculate all pairs of income ratios within each country
-income_ratios <- income_data %>%
-  group_by(country) %>%
-  mutate(income_ratio = combn(average_income, 2, FUN = function(x) x[1] / x[2])) %>%
-  ungroup()
-
-# Print the result
-print(income_ratios)
-
-```
-
 ```{r save}

### 2025-07-29 procesamiento/01-prod_prep-individual.Rmd
data for reproducibility

--- 2024-07-16 procesamiento/01-prod_prep-micro.Rmd
@@
 ---
-title: "Data preparation"
+title: "Data preparation - individual"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
 
-# Welfare attitudes
+# Inequality perceptions
 
 ```{r}
-#frq(df1$v13)
 df1$redist <- car::recode(df1$v13,recodes = "c(0,8,9)=NA")
@@
 sjlabelled::set_label(df1$redist) <- "Preferences goverment redistribution"
-#frq(df1$redist)
-
-#frq(df1$v15)
-df1$whealth <- car::recode(df1$v15,recodes = "c(0,8,9)=NA")
-df1$whealth <- set_na(df1$whealth,na = c(0,8,9))
-df1$whealth <- sjmisc::rec(x = df1$whealth,rec = "rev")
-sjlabelled::set_label(df1$whealth) <- "Welfare provision: health"
-#frq(df1$whealth)
-
-#frq(df1$v16)
-df1$wcarelder <- car::recode(df1$v16,recodes = "c(0,8,9)=NA")
-df1$wcarelder <- set_na(df1$wcarelder,na = c(0,8,9))
-df1$wcarelder <- sjmisc::rec(x = df1$wcarelder,rec = "rev")
-sjlabelled::set_label(df1$wcarelder) <- "Welfare provision: elderly care"
-#frq(df1$wcarelder)
-# cor(df1[,c("redist","whealth","wcarelder")],use = "complete.obs")
-```
-
-# Inequality perceptions
-
-```{r}
-#frq(df1$v59)
-df1$hhdepriv <- car::recode(df1$v59,recodes = "c(0,8,9)=NA")
-df1$hhdepriv <- set_na(df1$hhdepriv,na = c(0,8,9))
-# df1$hhdepriv <- sjmisc::rec(x = df1$hhdepriv,rec = "rev")
-sjlabelled::set_label(df1$hhdepriv) <- "Household economic deprivation (household difficulties)"
-#frq(df1$hhdepriv)
-
-#frq(df1$v11)
-df1$perineq <- car::recode(df1$v11,recodes = "c(0,8,9)=NA")
-df1$perineq <- set_na(df1$perineq,na = c(0,8,9))
-df1$perineq <- sjmisc::rec(x = df1$perineq,rec = "rev")
-sjlabelled::set_label(df1$perineq) <- "Perceived economic inequality (Inc. diff. too large)"
-#frq(df1$perineq)
-
-#frq(df1$v12)
+
 df1$prefineq <- car::recode(df1$v12,recodes = "c(0,8,9)=NA")
@@
 frq(df1$n_employees_spo)
-
-haven::write_dta(data = df1[c("id","isco88r","semp","supvis",
-                              "is_supervisor","self_employed","n_employees",
-                              "isco88spo","sempspo","supvisspo",
-                              "is_supervisor_spo","self_employed_spo","n_employees_spo")],
-                 path = here::here("input/data/proc/ocup_respondent-spouse.dta"))
-```
-
-```{r class-from-stata1}
-# Load the data created in stata------------------------------------------------
-df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
-df1 <- left_join(df1,df_class,by='id')
-
-# Class R´s and Spouse----------------------------------------------------------
-frq(df1$class10)
-
-# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$class10f <- as_factor(df1$class10)
-frq(df1$class10f)
-
-df1$class10f <- factor(df1$class10f,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$class10f <- as_labelled(df1$class10f)
-sjlabelled::set_label(df1$class10f) <- "Social Class - respondent"
-frq(df1$class10f)
-
-df1$class10spof <- as_factor(df1$class10spo)
-frq(df1$class10spof)
-
-df1$class10spof <-factor(df1$class10spof,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$class10spof <- as_labelled(df1$class10spof)
-sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse";frq(df1$class10spof)
-#if NA in class of respondent, replace with spouse
-
-frq(df1$class10f)
-frq(df1$class10spof)
-
-df1$class11 <- ifelse(is.na(df1$class10f),df1$class10spof,df1$class10f)
-frq(df1$class11)
-
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one, just for those
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$class11d <- pmax(df1$class11, #social class respondent + spouse vs:
-                     df1$class10spof,#social class spouse
-                     na.rm = T) # if NA, do nothing
-frq(df1$class11d)
-df1$class11d <- 
-  sjlabelled::set_labels(df1$class11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
-                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$class11d) <- "Social Class"
-frq(df1$class11d)
-
-# Class Scheme 3 classes
-df1$class3 <- car::recode(df1$class11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3) <- "Social Class Dominance (isko - v1 - V to Intermediate)";frq(df1$class3)
-
-df1$class3_V <- car::recode(df1$class11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3_V) <- "Social Class Dominance (isko - v1 - V to Working Class)";frq(df1$class3_V)
-
-# Class Scheme 6 classes
-df1$class6 <- car::recode(
-  df1$class11d,
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-# Class only R's --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$class3res <- car::recode(as.numeric(df1$class10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3res) <- "Social Class 3 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class3res)
-
-df1$class3res_V <- car::recode(as.numeric(df1$class10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3res_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3res_V)
-
-# Class Scheme 6 classes
-df1$class6res <- car::recode(
-  as.numeric(df1$class10f),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$class6res) <- "Social Class 6 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class6res)
-# Class only Spouse --------------------------------------------------------------
-
-# Class Scheme 3 classes
-df1$class3spo <- car::recode(as.numeric(df1$class10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:10='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$class3spo) <- "Social Class 3 (Spouse) - (isko - v1 -  V to Intermediate)";frq(df1$class3spo)
-
-df1$class3spo_V <- car::recode(as.numeric(df1$class10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:10='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$class3spo_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3spo_V)
-
-# Class Scheme 6 classes
-df1$class6spo <- car::recode(
-  as.numeric(df1$class10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-sjlabelled::set_label(df1$class6spo) <- "Social Class 6 (Spouse) - (isko - v1)";frq(df1$class6spo) 
-```
-
-```{r class-from-stata2}
-# Class R´s and Spouse----------------------------------------------------------
-frq(df1$digclass10)
-
-# df1$class10 <- car::recode(df1$class10, "7=8; 8=9; 9=10; 10=11; 11=7")
-df1$digclass10f <- as_factor(df1$digclass10)
-frq(df1$digclass10f)
-
-df1$digclass10f <- factor(df1$digclass10f,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-df1$digclass10f <- as_labelled(df1$digclass10f)
-sjlabelled::set_label(df1$digclass10f) <- "Social Class - respondent"
-frq(df1$digclass10f)
-df1$digclass10spof <- as_factor(df1$digclass10spo)
-frq(df1$digclass10spof)
-
-df1$digclass10spof <-factor(df1$digclass10spof,
-                       levels = c("higher controllers","lo controllers",
-                                 "routine nonmanual",
-                                 "sempl with emp","sempl without empl","selfempl farm",
-                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
-                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
-
-df1$digclass10spof <- as_labelled(df1$digclass10spof)
-sjlabelled::set_label(df1$digclass10spof) <- "Social Class - spouse"
-
-frq(df1$digclass10spof)
-#if NA in class of respondent, replace with spouse
-
-frq(df1$digclass10f)
-frq(df1$digclass10spof)
-
-df1$digclass11 <- ifelse(is.na(df1$digclass10f),df1$digclass10spof,df1$digclass10f)
-frq(df1$class11)
-
-# if NA in respondents it is assumed to be lower than spouse
-# now, with the cases in we have information for respondent and spouse
-# we replace the value by the highest one, just for those
-
-# Replace the highest class by dominance criteria 
-# Keep the highest of two values:
-df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
-                     df1$digclass10spof,#social class spouse
-                     na.rm = T) # if NA, do nothing
-frq(df1$digclass11d)
-df1$digclass11d <- 
-  sjlabelled::set_labels(df1$digclass11d,
-                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
-                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
-                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
-sjlabelled::set_label(df1$digclass11d) <- "Social Class 11 (isko - v2)"
-frq(df1$digclass11d)
-
-# Class Scheme 3 classes
-df1$digclass3 <- car::recode(df1$digclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3) <- "Social Class 3 (isko - v2 - V to Intermediate) ";frq(df1$digclass3)
-
-df1$digclass3_V <- car::recode(df1$digclass11d,as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3_V)
-
-# Class only R's --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$digclass3res <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3res) <- "Social Class 3 (R's) - (V to Intermediate - isko - v2)";frq(df1$digclass3res)
-
-df1$digclass3res_V <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3res_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3res_V)
-
-# Class Scheme 6 classes
-df1$digclass6res <- car::recode(
-  as.numeric(df1$digclass10),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-
-sjlabelled::set_label(df1$digclass6res) <- "Social Class 6 (R's) - (isko - v2)"
-
-# Class only Spouse --------------------------------------------------------------
-# Class Scheme 3 classes
-df1$digclass3spo <- car::recode(as.numeric(df1$digclass10spo),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV+V)',
-                                      'Working Class (VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:7='Intermediate class (III+IV+V)';
-                             8:11='Working Class (VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate - isko - v2)";frq(df1$digclass3spo)
-
-df1$digclass3spo_V <- car::recode(as.numeric(df1$digclass10spof),as.factor = T,
-                            levels =c('Service Class (I+II)',
-                                      'Intermediate class (III+IV)',
-                                      'Working Class (V+VI+VII)'), 
-                            "1:2='Service Class (I+II)';
-                             3:6='Intermediate class (III+IV)';
-                             7:11='Working Class (V+VI+VII)'")
-
-sjlabelled::set_label(df1$digclass3spo_V) <- "Social Class 3 (Spouse) (V to Working Class - isko - v2)";frq(df1$digclass3spo_V)
-
-# Class Scheme 6 classes
-df1$digclass6spo <- car::recode(
-  as.numeric(df1$digclass10spo),
-  as.factor = T,
-  levels = c(
-    'Service class (I - higher grade)',
-    'Service class (II - lower grade)',
-    'Routine non-manual (IIIa+b)',
-    'Petty-bourgeoise (IVa+b+c)',
-    'Skilled manual workers and supv. (V+VI)',
-    'Non-skilled manual workers (VIIa+b)'
-  ),
-  "1='Service class (I - higher grade)';
-   2='Service class (II - lower grade)';
-   3:4='Routine non-manual (IIIa+b)';
-   5:7='Petty-bourgeoise (IVa+b+c)';
-   8:9='Skilled manual workers and supv. (V+VI)';
-   10:11='Non-skilled manual workers (VIIa+b)'"
-)
-sjlabelled::set_label(df1$digclass6spo) <- "Social Class  6 (Spouse) - (isko - v2)"
-```
-
-# Class using R
+```
+
+# Social Class
 
@@
 # devtools::install_git("https://code.europa.eu/digclass/digclass.git")
-
 library("DIGCLASS")
-library(dplyr)
-
 df1 <- 
@@
 sjlabelled::set_label(df1$homclass3_V_res) <- "Class homogeneity (R's) (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res)
-
-# Partner class as part of the position generator
-frq(df1$dclass3spo_V)
-df1$partner_hig <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "1=1;2:3=0;4=NA");frq(df1$partner_hig)
-df1$partner_mid <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "2=1;c(1,3)=0;4=NA");frq(df1$partner_mid)
-df1$partner_low <- car::recode(as.numeric(df1$dclass3spo_V),recodes = "3=1;c(1,2)=0;4=NA");frq(df1$partner_low)
-
-df1$n_low_partner<- rowSums(df1[,c("n_low","partner_low")],na.rm = T); sjlabelled::set_label(df1$n_low_partner) <- "Number of low status contacts + partner"
-df1$n_mid_partner<- rowSums(df1[,c("n_middle","partner_mid")],na.rm = T); sjlabelled::set_label(df1$n_mid_partner) <- "Number of middle status contacts + partner"
-df1$n_high_partner<- rowSums(df1[,c("n_high","partner_hig")],na.rm = T); sjlabelled::set_label(df1$n_high_partner) <- "Number of high status contacts + partner"
-```
-
-```{r homogeneity-R-digclass-plus-partner}
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",df1$n_high_partner,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",df1$n_mid_partner,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",df1$n_low_partner,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Service Class (I+II)",rowSums(df1[,c("n_low_partner","n_mid_partner")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Intermediate class (III+IV)",rowSums(df1[,c("n_low_partner","n_high_partner")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_V=="Working Class (V+VI+VII)",rowSums(df1[,c("n_mid_partner","n_high_partner")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$know_total_partner <- rowSums(df1[,c("n_high_partner","n_mid_partner","n_low_partner")],na.rm = T);sjlabelled::set_label(df1$know_total_partner) <- "Number of contacts + partner"
-
-df1$homclass3_V_res_part <- as.numeric(df1$ingroup_res/df1$know_total_partner)
-sjlabelled::set_label(df1$homclass3_V_res_part) <- "Class homogeneity (R's) + partner tie (DIGCLASS - V to intermediate)";frq(df1$homclass3_V_res_part)
-cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
-summary(df1$homclass3_V_res_part)
-summary(df1$homclass3_V_res)
-cor(df1$homclass3_V_res_part,df1$homclass3_V_res,use = "complete.obs")
-df1 %>% select(dclass3res_V,n_high_partner,n_mid_partner,n_low_partner,ingroup_res,outgroup_res,know_total_partner)
-```
-
-```{r homogeneity-R-digclass-IIIb-working}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(dclass3_III,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Service Class",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Intermediate class",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III=="Working Class",df1$n_low,df1$ingroup);frq(df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(dclass3_III,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup);frq(df1$outgroup)
-
-df1$homclass3_III <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III) <- "Class homogeneity Dominance (DIGCLASS version - IIIb to Working)";frq(df1$homclass3_III)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_III,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Service Class",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_V,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass3_III_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_res)
-```
-
-```{r homogeneity-R-digclass-IIIb-V-working}
-# EI homophily index
-df1$ingroup <- NA 
-df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Service Class",df1$n_high,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Intermediate class",df1$n_middle,df1$ingroup)
-df1$ingroup <- ifelse(df1$dclass3_III_V=="Working Class",df1$n_low,df1$ingroup)
-
-df1$outgroup <- NA 
-df1 %>% select(dclass3_III_V,n_high,n_middle,n_low,outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup)
-df1$outgroup <- ifelse(df1$dclass3_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup)
-
-df1$homclass3_III_V <- as.numeric(df1$ingroup/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_V) <- "Class homogeneity Dominance (DIGCLASS version - IIIb+V to Working)";frq(df1$homclass3_III_V)
-
-## Using RESPONDENT Class for homogeneity---------------------------------------
-df1$ingroup_res <- NA 
-df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",df1$n_high,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",df1$n_middle,df1$ingroup_res)
-df1$ingroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",df1$n_low,df1$ingroup_res);frq(df1$ingroup_res)
-
-df1$outgroup_res <- NA 
-df1 %>% select(dclass3res_III_V,n_high,n_middle,n_low,outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Service Class",rowSums(df1[,c("n_low","n_middle")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Intermediate class",rowSums(df1[,c("n_low","n_high")],na.rm = T),df1$outgroup_res)
-df1$outgroup_res <- ifelse(df1$dclass3res_III_V=="Working Class",rowSums(df1[,c("n_middle","n_high")],na.rm=T),df1$outgroup_res);frq(df1$outgroup_res)
-
-df1$homclass3_III_V_res <- as.numeric(df1$ingroup_res/df1$know_total)
-sjlabelled::set_label(df1$homclass3_III_res) <- "Class homogeneity (R's) (DIGCLASS - IIIb to working)";frq(df1$homclass3_III_V_res)
-```
-
-```{r social distance, include=FALSE}
+```
+
+```{r homogeneity-isei, include=FALSE}
 df1$dis_busdriver <- df1$isei08 - df1$isei_busdriver
@@
 
-```{r}
+```{r svae}
 save(df1,file = here::here("input/data/proc/study1.RData"))
 ```
-
-# Backup code
-
-```{r homogeneity-strong-v01, eval=FALSE, include=FALSE}
-# EI homophily index
-df1$ingroup_s<- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_s,df1$ingroup_s)
-df1$ingroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_s,df1$ingroup_s)
-#frq(df1$ingroup_s)
-
-df1$outgroup_s <- NA 
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_s","n_middle_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_s","n_high_s")],na.rm = T),df1$outgroup_s)
-df1$outgroup_s <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_s","n_high_s")],na.rm=T),df1$outgroup_s)
-#frq(df1$outgroup_s)
-
-df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
-sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
-#frq(df1$eindex_s)
-#hist.default(df1$eindex_s)
-
-df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
-df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
-sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
-#hist.default(df1$homclass_s)
-```
-
-```{r homogeneity-weak-v01, eval=FALSE, include=FALSE}
-# EI homophily index
-df1$ingroup_w<- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Service Class (I+II)",df1$n_high_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",df1$n_middle_w,df1$ingroup_w)
-df1$ingroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",df1$n_low_w,df1$ingroup_w)
-# frq(df1$ingroup_w)
-
-df1$outgroup_w <- NA 
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Service Class (I+II)",rowSums(df1[,c("n_low_w","n_middle_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Intermediate class (III+IV+V)",rowSums(df1[,c("n_low_w","n_high_w")],na.rm = T),df1$outgroup_w)
-df1$outgroup_w <- ifelse(df1$class3=="Working Class (VI+VII)",rowSums(df1[,c("n_middle_w","n_high_w")],na.rm=T),df1$outgroup_w)
-# frq(df1$outgroup_w)
-
-df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
-sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
-frq(df1$eindex_w)
-#hist.default(df1$eindex_w)
-
-df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
-df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
-sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
-#hist.default(df1$homclass_s)
-```
-
-(i)  the highest status job accessed (upper reachability),
-(ii) the range between highest and lowest occupations accessed (resource heterogeneity)
-(iii) the total number of occupations accessed (network extensity),
-(iv) the total accessed prestige (resource volume),
-(v) the average status of jobs accessed (network prestige),
-(vi) the total number of higher-status positions accessed,
-(vii) the total number of medium-status positions accessed,
-(viii) the total number of lower-status positions accessed.
-
-```{r pca, eval=FALSE, include=FALSE}
-library(psych)
-library(dplyr)
-isei_ocupnames<- names(dplyr::select(df1,starts_with("isei_")))
-
-# Calculate the standard deviation for each column
-df1$isei_sd <- apply(df1[isei_ocupnames], 1, sd, na.rm = TRUE)
-
-# Print the standard deviation for each column
-# df1 %>% dplyr::select(isei_ocupnames,isei_sd) %>% View()
-
-# reduce dimensions in 2: diversity and prestige
-df_cs<- df1[,c("isei_max","isei_avg","isei_range","know_total","isei_sd")]
-summary(df_cs)
-dim(df_cs)
-
-# df_cs <- na.omit(df_cs)
-cor<- corr.test(df_cs)
-psych::KMO(r = cor$r)
-cortest.bartlett(cor$r,n = dim(df_cs)[1])
-plot(scree(df_cs,factors = 2))
-
-# Porcentaje de varianza explicada
-fit1<- psych::pca(df_cs,nfactors = 2,rotate = "varimax")
-fit1$loadings
-plot(fit1,labels = c(names(df_cs)))
-cor(fit1$scores)
-
-fit2<- psych::fa(df_cs,nfactors = 2)
-plot(fit2,labels = c(names(df_cs)))
-fit2$scores
-cor(fit2$scores)
-fs<- as.data.frame(fit2$scores)
-names(fs) <- c("diversity","prestige")
-
-df1 <- bind_cols(df1,fs)
-sjlabelled::set_label(df1$prestige) <- "Network Contacts Prestige"
-sjlabelled::set_label(df1$diversity) <- "Network Contacts Diversity"
-```

### 2025-07-29 procesamiento/02-prod_prep-country.Rmd
data for reproducibility

--- 2024-05-08 procesamiento/02-prod_prep-macro.Rmd
@@
 ---
-title: "Data preparation"
+title: "Data preparation - country"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
                       )
-options(scipen=9999) # desactivar notacion cientifica
-if (!require("pacman")) install.packages("pacman") # instalar pacman
+options(scipen=9999)
+if (!require("pacman")) install.packages("pacman") 
 load(here::here("input/data/proc/study1.RData"))
@@
 ```
-
-Revisar:
-
-https://wid.world/codes-dictionary#post-tax-income
 
@@
 
-**Otero et.al (2023)**
-
-```{r otero23}
-otero <- 
-  read.csv(file = here::here("input/data/original/otero23.csv"),sep = ";")
-otero$ccode <- countrycode::countrycode(sourcevar = otero$iso3n,origin = "iso2c",destination = "iso3n")
-otero$gdp <- gsub('\\,', '',otero$gdp) 
-otero<- otero %>% select(ccode,gv_spen,individualism)
-```
-
 **ILO Data**
@@
 ilo_df <- left_join(long_ilo_tax,long_ilo_spe) %>% filter(year==2016)
-
-# long_ilo_spe$country <- countrycode::countrycode(sourcevar = long_ilo_spe$ccode,origin = "iso3n",destination = "iso3c")
-
-# Plot points connected by a line representing time
-# ggplot(long_ilo_spe, aes(x = factor(year), y = govspe, group = factor(country), color = factor(country))) +
-#   geom_line() +
-#   geom_point(size = 3) +
-#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
-#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
-#   theme_minimal()
-# 
-# 
-# # Plot points connected by a line representing time
-# ggplot(long_ilo_tax, aes(x = factor(year), y = taxrev, group = factor(country), color = factor(country))) +
-#   geom_line() +
-#   geom_point(size = 3) +
-#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
-#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
-#   theme_minimal()
-
 ```
@@
   left_join(pen_2017) %>% 
-  left_join(otero) %>%
   left_join(ocde) %>% 
@@
 save(macro_data,file = here::here("input/data/proc/study1_macro_data.RData"))
-
 df1$ccode <- as.numeric(df1$country)
@@
 
-# Class inequality
-
-```{r}
-summary(df1$incomepcap)
-
-df_class3_ineq <- 
-df2 %>%   
-  group_by(country2,dclass3res_V) %>%
-  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  na.omit() %>% 
-  dplyr::select(country2,dclass3res_V,incomepcap,ednum,wid_gini_disp) %>% 
-  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = c("incomepcap","ednum")) %>% 
-  mutate(ratio_class_inc = `incomepcap_Service Class (I+II)`/`incomepcap_Working Class (V+VI+VII)`,
-         ratio_class_educ  = `ednum_Service Class (I+II)`/`ednum_Working Class (V+VI+VII)`) %>% 
-  as.data.frame()
-
-df_class3_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
-
-df_class6_ineq <- 
-df2 %>%   
-  group_by(country2,dclass6res) %>%
-  summarise_at(c("incomepcap","ednum","wid_gini_disp"), mean, na.rm = TRUE) %>% 
-  as.data.frame() %>%
-  na.omit() %>% 
-  dplyr::select(country2,dclass6res,incomepcap,ednum,wid_gini_disp) %>% 
-  tidyr::pivot_wider(names_from = "dclass6res", values_from = c("incomepcap","ednum")) %>% 
-  mutate(ratio_class_inc = `incomepcap_Upper Service class`/`incomepcap_Unskilled working class`,
-         ratio_class_educ  = `ednum_Upper Service class`/`ednum_Unskilled working class`) %>% 
-  as.data.frame() 
-df_class_ineq %>% select(wid_gini_disp,ratio_class_inc,ratio_class_educ) %>% tab_corr()
-```
-
-```{r}
-
-income_data
-
-# Example data
-# Assuming you have a data frame called 'income_data' with columns: country, social_class, and average_income
-
-# Calculate all pairs of income ratios within each country
-income_ratios <- income_data %>%
-  group_by(country) %>%
-  mutate(income_ratio = combn(average_income, 2, FUN = function(x) x[1] / x[2])) %>%
-  ungroup()
-
-# Print the result
-print(income_ratios)
-
-```
-
 ```{r save}
 save(df2,file = here::here("input/data/proc/study1_country.RData"))
-# haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
 sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )

### 2025-07-29 procesamiento/03_prod_main_analysis.Rmd
data for reproducibility

---
# title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
fontsize: 12pt
linestretch: '1.5'          # interlineado
# #linestretch: '2.0'          # interlineado 
papersize: a4
link-citations: yes         # citas linkeadas
lang: en-US
  bookdown::html_document2:
    toc: false
    code_folding: hide
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    number_sections: true
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::word_document2:
    reference_docx: "input/mytemplate.docx"
    toc: false
    code_folding: hide
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false

always_allow_html: true      
linkcolor: gray                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa-no-doi-no-issue.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm" # márgenes de página
header-includes:
  - \usepackage{times}   # Times New Roman
  - \usepackage{endnotes}
  - \let\footnote=\endnote 
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{setspace}  
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \setlength\parindent{24pt} 
  - \usepackage{fancyhdr}
  - \fancyhead{} 
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = T,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''  
```

# Results

## Descriptive cross-country comparison on class, network segregation, and redistributive preferences

```{r fig2, fig.dim=c(10,5),fig.cap='Cross-country differences in redistributive preferences by social class',warning=FALSE}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1) 
options(ggplot2.discrete.colour = set1) 
ggplot2::theme_set(ggplot2::theme_bw()) 
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  Q03pcm,
  edyears,
  female,
  agenum,
  partner,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2, country, country3,
) %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000))

df_mean <- 
dfreg %>% 
  group_by(country3) %>% 
  summarise(egal2_c=weighted.mean(egal,WEIGHT),homclass_c=weighted.mean(homclass3_V_res,WEIGHT),gini_disp=mean(gini_disp))
df_region <- dfreg %>% group_by(region,country3) %>% summarise(n())
df_full <- dfreg %>% group_by(dclass3res_V) %>%
  summarise(egal2=weighted.mean(egal,WEIGHT),
            homclass=weighted.mean(homclass3_V_res,WEIGHT),
            homclass_c=weighted.mean(dfreg$homclass3_V_res,dfreg$WEIGHT),
            egal2_c=weighted.mean(dfreg$egal,dfreg$WEIGHT), 
            country3="Sample")
df_plot <- dfreg %>% group_by(country3,dclass3res_V) %>% 
  summarise(egal2=weighted.mean(egal,WEIGHT),
            homclass=weighted.mean(homclass3_V_res, WEIGHT)) %>% 
  left_join(df_mean) %>% left_join(df_region) 
df_plot$dclass3res_V <- factor(df_plot$dclass3res_V,levels = levels(df_plot$dclass3res_V),labels = c("Service Class","Intermediate Class","Working Class"))

# Calculate the difference between the mean value of working class and upper class within each country
homo_class_diff <- df_plot %>%
  dplyr::select(country3,homclass,dclass3res_V) %>% 
  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass") %>% 
  mutate(diff_working_upper = `Working Class` - `Service Class`) %>% 
  dplyr::select(-`Working Class`, -`Service Class`,-`Intermediate Class`) %>% 
  as.data.frame()

egal_class_diff <- df_plot %>%
  dplyr::select(country3,egal2,dclass3res_V) %>% 
  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "egal2") %>% 
  mutate(diff_working_upper_egal = `Working Class` - `Service Class`) %>% 
  dplyr::select(-`Working Class`, -`Service Class`,-`Intermediate Class`) %>% 
  as.data.frame()

df_plot <- 
dfreg %>% 
  group_by(country3,dclass3res_V) %>% 
  summarise(egal2=weighted.mean(egal,WEIGHT),homclass=weighted.mean(homclass3_V_res,WEIGHT)) %>% 
  left_join(df_mean) %>%
  left_join(df_region) %>% as.data.frame() %>% 
  left_join(homo_class_diff) %>% 
  left_join(egal_class_diff)

df_plot2 <- df_plot
df_plot2$dclass3res_V <- "Country"
df_plot2$homclass <- df_plot2$homclass_c
df_plot2$egal2 <- df_plot2$egal2_c 
df_plot3 <- bind_rows(df_plot,df_plot2)
df_plot3$dclass3res_V <- factor(df_plot3$dclass3res_V,
                                levels = c("Country","Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)"),labels = c("Country","Service Class","Intermediate Class","Working Class"))

df_plot3 %>% 
ggplot()+
  geom_hline(yintercept = mean(dfreg$egal),linetype=2)+
  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,
                 shape=dclass3res_V,
                 color=dclass3res_V
                 ),size=3, alpha=2) +
  scale_shape_manual(values = c(4,17, 15, 16)) +
  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
  labs(x=NULL,y="Redistributive Preferences",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in redistributive preferences by social class") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x=element_text(angle=45,hjust = 1,size=8),
        legend.title = element_blank())

ggsave(plot = last_plot(),filename = "figure002.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r fig3, fig.dim=c(10,5),fig.cap='Cross-country differences in network homogeneity by social class ',warning=FALSE}
df_plot3 %>%
ggplot()+
  geom_point(aes(x = reorder(country3, diff_working_upper),
                 y = homclass,
                 shape=dclass3res_V,
                 color=dclass3res_V),
             size=3, alpha=2) +
  geom_hline(yintercept = mean(dfreg$homclass3_V_res),linetype=2)+
  scale_shape_manual(values = c(4,17, 15, 16)) +
  scale_color_manual(values = c("black","#000000","#666666","#999999")) +
  scale_y_continuous(limits = c(0,0.7))+
  labs(x=NULL,y="Network homogeneity",caption="Source: International Social Survey 2017; descriptive statistics; figure report country averages in network homogeneity by social class") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x=element_text(angle=45,hjust = 1,size=8),
        legend.title = element_blank())  
ggsave(plot = last_plot(),filename = "figure003.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r fig4, fig.dim=c(10,5),fig.cap='Relationship between income Inequality, network homogeneity and redistributive preferences',warning=FALSE}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  # dclass3spo_V,
  homclass3_V_res,
  know_total,
  # socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  # religion,
  partner,
  # union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2, country, country3,
) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         # gini_disp=scale(gini_disp),
         )

homo_ineq <- dfreg %>%
  group_by(country2,country3) %>%
  summarise_at(c("homclass3_V_res","egal","gini_disp"), mean, na.rm = TRUE) %>% 
  as.data.frame()

homo_class_diff <- dfreg %>%   
  group_by(country2,country3,dclass3res_V) %>%
  summarise_at(c("egal","homclass3_V_res"), mean, na.rm = TRUE) %>% 
  as.data.frame() %>%
  dplyr::select(country3,homclass3_V_res,dclass3res_V) %>% 
  tidyr::pivot_wider(names_from = "dclass3res_V", values_from = "homclass3_V_res") %>% 
  mutate(diff_working_upper_homo = `Working Class (V+VI+VII)` - `Service Class (I+II)`) %>% 
  as.data.frame()

# Dataset with class differences in network homogeneity
homo_ineq <- homo_ineq %>% left_join(homo_class_diff)

# Plot Homogeneity and redistributive preferences
homo_ineq$country <- countrycode::countrycode(sourcevar = homo_ineq$country2,origin = "iso3c",destination = "iso2c")

fig_homodiff_gini<- 
homo_ineq %>%  
ggplot(aes(y=diff_working_upper_homo, x=gini_disp)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
  # geom_text() +
  geom_text_repel(label=as.character(homo_ineq$country)) +
  xlab("Income Inequality") +
  ylab("Class Diff. in homogeneity (Working - Service)") +
  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "C")

fig_homodiff_redist<- 
homo_ineq %>%  
ggplot(aes(y=egal , x=diff_working_upper_homo)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
  # geom_text() +
  geom_text_repel(label=as.character(homo_ineq$country)) +
  ylab("Redistributive preferences") +
  xlab("Class Diff. in homogeneity (Working - Service)") +
  labs(caption =paste("r = ",round(cor(homo_ineq$diff_working_upper_homo,
                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "D")

fig_egal_homo <- 
homo_ineq %>%  
ggplot(aes(y=egal, x=homclass3_V_res)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
  geom_text_repel(label=as.character(homo_ineq$country)) +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
                                     homo_ineq$egal, use='complete.obs'),digits = 2)),tag = "B")
fig_homo_gini<- 
homo_ineq %>%  
ggplot(aes(y=homclass3_V_res, x=gini_disp)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black",linetype = 2,size=1,se = T) +
  # geom_text() +
  geom_text_repel(label=as.character(homo_ineq$country)) +
  xlab("Income Inequality") +
  ylab("Network homogeneity") +
  labs(caption =paste("r = ",round(cor(homo_ineq$homclass3_V_res,
                                     homo_ineq$gini_disp, use='complete.obs'),digits = 2)),tag = "A")

setseed(1234)
ggsave(plot = arrangeGrob(fig_homo_gini,fig_egal_homo,
                          fig_homodiff_gini,fig_homodiff_redist,
             nrow = 2, 
 bottom =textGrob("Source: International Social Survey 2017; descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
 gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
  )),
 filename = "figure004.png",device = "png",
 path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26)
```

## The segregation hypothesis on redistributive preferences

```{r table1, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,
  # dclass3spo_V,
  homclass3_V_res,
  know_total,
  # socialtrust,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # religion,
  # union,
  # workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)
         ) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") 
dfreg$egal <- as.numeric(scale(dfreg$egal))
dfreg <- na.omit(dfreg)

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
                    digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              # socialtrust="Social Trust",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              # "femaleFemale"="Female (Ref. = Male)",
              # "agenum"="Age",
              # "age2"="Age2",
             # "edyears"="Year of Education",
             # "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
             # "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")

screenreg(digclas1_VW)

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table 1: Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups = 
         list("Social Class (Ref.= Service Class)" = 3:4,
              "Homogeneity × Social Class"=5:6),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/table001.html")
      )
```

```{r fig5, fig.dim=c(10,5),fig.cap='Interaction of network homogeneity and social class on redistributive preferences',warning=FALSE}
int_homo <- digclas1_VW_7
df_pred1 <- 
  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res),
                                                       max(dfreg$homclass3_V_res), by= 0.1),
                                 dclass3res_V = levels(dfreg$dclass3res_V),
                                 know_total = mean(dfreg$know_total)))
# names(df_pred1) 
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(caption = paste0("Note: N (individuals) = ",nobs(int_homo),"; N (countries) = ",lme4::ngrps(int_homo),". Predictive estimates with 95% confidence intervals"),
       x="Network homogeneity",y="Redistributive preferences (z-score)") +
  theme(legend.position = "none", legend.title = element_blank())

ggsave(plot = last_plot(),filename = "figure005.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

## The mitigation hypothesis on network segregation and redistributive preferences

```{r table2, results='asis', cache=TRUE}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         age2 = agenum ^ 2, 
         gini_disp=scale(gini_disp),
         d10d1=scale(d10d1),
         wid_p90p50=scale(wid_p90p50)
         )

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
dfreg$wstate2 <- as.numeric(scale(dfreg$wstate2))

dfreg$egal <- as.numeric(scale(dfreg$egal))

# Variable Group-Centering -----------------------------------------------------
dfreg <- 
  dfreg %>% 
  mutate(to_dummy(female)
  )
dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
# drop dummies
dfreg <- dplyr::select(dfreg,-c(female_1,female_2))

## Cross-level interactions-----------------------------------------------------
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         homclass3_V_gc*dclass3res_V+
         female_gc+agenum_gc+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = NULL)

homo_V_gini_int <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         gini_disp +
         homclass3_V_gc*
         dclass3res_V*
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = NULL)

digclas1_macro <- list(homo_V_gini,homo_V_gini_int)
screenreg(digclas1_macro)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",

              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",

              "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
              "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",

              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality")

htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       caption = paste("Table 2: Multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: Individual level variables are centered within cluster (group mean).Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 2:3,
                    "Homogeneity × Social Class"=5:6, 
                    "Class × Income Inequality" = 8:9 ,
                    "Homogeneity × Social Class × Income Inequality"=10:11),
      custom.gof.rows = list("Controls"=rep("Yes",2)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual"),
        file = here::here("output/tables/table002.html"))
```

```{r fig6, fig.dim=c(12,7),fig.cap='Three-way interaction of network homogeneity, social class and income inequality on redistributive preferences'}
### Predicted values homo*class*GiniD ---------------------------------------$
ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
ginid_mea<- round(mean(dfreg$gini_disp),2)

df_pred_giniD_gc <-
  predictions(
    homo_V_gini_int,newdata = datagrid(
      gini_disp = c(ginid_min, ginid_mea, ginid_max),
      wstate2=mean(dfreg$wstate2),
      loggdppercapita=mean(dfreg$loggdppercapita),
      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc)+0.01, max(dfreg$homclass3_V_gc)+0.01, by=0.1),
      dclass3res_V=levels(dfreg$dclass3res_V)
    )
  )
df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))
df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")

df_pred_giniD_gc %>% 
  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=3, shape = 21,color="black") +
  facet_wrap(~gini_disp) +
  labs(y = "Redistributive preferences (z-score)",
       x="Network homogeneity",
       caption = paste0("Note: N (Individuals) = ",nobs(homo_V_gini_int),"; N (Countries) = ",lme4::ngrps(homo_V_gini_int),
                        ". Predictive estimates with 95% confidence intervals")) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax) \n ", breaks = NULL, labels = NULL),
                     ) +

   scale_fill_manual(values=c("#323232","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#CCCCCC"))+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text=element_text(size=15),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))

ggsave(plot = last_plot(),filename = "figure006.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r tableA1, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  Q03pcm,
  edyears,
  female,
  agenum,
  partner,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") 
dfreg <- na.omit(dfreg)
dfreg$egal <- as.numeric(scale(dfreg$egal))
## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              # socialtrust="Social Trust",
              "femaleFemale"="Female (Ref. = Male)",
              "agenum"="Age",
              # "age2"="Age2",
             "edyears"="Year of Education",
             "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
             "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
             "partnerHas a partner" = "Has partner (Ref.= No partner)",
                           "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table A1: Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
      groups = list("Household Income (Ref.= Tertile I)"= 6:8,
                    "Social Class (Ref.= Service Class)" = 11:12, 
                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
                    "Homogeneity x Social Class"=13:14),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableA1.html")
      )
```

```{r tableA2, echo=FALSE, cache=TRUE, results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
  pacman::p_load(knitr)
tabformat = if(is_html_output()) {"html"} else if(is_latex_output()) {"latex"}
df1$id <- 1:dim(df1)[[1]]
dfreg <- df1 %>% dplyr::select(id,
  redist,prefineq,
  pct_low,pct_middle,pct_high,
  egal = egal2,
  dclass3res_V,dclass6res,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  "gini_disp"=wid_gini_disp,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2,country3,
) %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>%
    mutate(loggdppercapita=gdppercapita/1000,
         age2 = agenum ^ 2, 
         )

occup_prop <- df1 %>% 
  filter(id %in% dfreg$id) %>% 
  dplyr::select(hrmanager,ceo,lawyer,
         nurse,police,teacher,
         cleaner,hairbarber,busdriver,mechanic
         ) %>% summarise_all(mean,na.rm=T)

status_prop <- df1 %>% 
  filter(id %in% dfreg$id) %>% 
  dplyr::select(pct_high,pct_middle,pct_low,
         ) %>% summarise_all(mean,na.rm=T)

p <- t(round(occup_prop*100,1))[,1]
pacman::p_load(dplyr,knitr,kableExtra)  
# Create the data frame
df <- data.frame(
  # Item = c("c", "d", "a", "g", "h", "i", "j", "e", "b", "f"),
  Occupation = c("Home or office cleaner", "Hairdresser/barber", "Bus/lory driver", "Car mechanic", 
                 "Nurse", "Police officer", "School teacher", "Human resource manager", 
                 "Executive of large firm", "Lawyer"),
  "ISCO08" = rev(c(2611,1100,1212,2300,5412,2220,7231,8331,5140,9111))
) %>% 
  mutate("%"=p)
tab_an_posgen <- 
kable(df,linesep = "",booktabs=TRUE,format=tabformat,caption = "Table A2: Occupations included in the position generator instrument") %>%
  kable_classic(full_width = F,font_size = 15,latex_options = "HOLD_position",,html_font = "sans") %>%
  column_spec(1,width = "6cm") %>%
  pack_rows("Higher-status positions", 1, 3) %>%
  column_spec(2) %>% 
  pack_rows("Medium-status positions", 4, 6) %>% 
  pack_rows("Lower-status positions", 7, 10) 
tab_an_posgen

kableExtra::save_kable(tab_an_posgen, here::here("output/tables/tableA02.html"))
```

```{r tableA3,results='asis', cache=TRUE}
levels(dfreg$dclass6res) <- c("Upper Service","Lower Service","Routine nonmanual",
                      "Self-employed","Skilled working","Unskilled working")
levels(dfreg$dclass3res_V) <- c("Service","Intermediate","Working")

tab_an_classag <- 
left_join(
dfreg %>% 
  group_by(dclass6res,dclass3res_V) %>% summarise(N1=n()) %>% mutate(freq1 = (N1/ dim(dfreg)[[1]])*100),
dfreg %>% 
  group_by(dclass3res_V) %>% summarise(N2=n()) %>% mutate(freq2 = (N2 / dim(dfreg)[[1]])*100),by="dclass3res_V"
) %>% 
  dplyr::select("dclass6res","N1","freq1","dclass3res_V","N2","freq2") %>%
  kable(booktabs = TRUE, format=tabformat,linesep = "",digits = 1,format.args = list(big.mark = ","),
        caption = "Table A3: Level of aggregation of social class",
        col.names = c("EGP-6","N","%","EGP-3","N","%")) %>% 
  kable_classic(full_width = F,font_size = 15,latex_options = c("HOLD_position"),html_font = "sans") %>% 
  collapse_rows(columns = c(4,5,6), valign = "middle");tab_an_classag

kableExtra::save_kable(tab_an_classag, here::here("output/tables/tableA03.html"))

```

```{r tableA4, echo=FALSE, results='asis'}
dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,dclass6res,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  "gini_disp"=wid_gini_disp,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2,country3,country,
) %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=gdppercapita/1000)

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100

dfreg$country <- countrycode::countrycode(sourcevar = dfreg$country2,origin = "iso3c",destination = "iso2c")
dfreg$country3b <- paste0(dfreg$country3," (",dfreg$country,")")

tab_an_countries <- 
dfreg %>% 
  group_by(country3b) %>% 
  summarise(n=n(),
            homclass=mean(x=homclass3_V_res),
            gini_disp=mean(gini_disp),
            loggdppercapita=mean(loggdppercapita),
            wstate=mean(wstate2)) %>% 
  arrange(homclass) %>% ungroup() %>% 
  kable(digits = c(1,1,3,2,2,2),booktabs = TRUE,format = tabformat, linesep = "",format.args = list(big.mark = ","),align = "lrccccc",
        caption = "Table A4: Values per country for the country-level variables",
        col.names = c("Country","N","Network Homogeneity","Income Inequality (Gini Index)","GDP/capita in $1000","Size of the Welfare State")) %>% 
  kable_classic(full_width = F,latex_options = "scale_down",html_font = "sans") %>% 
  column_spec(column = c(1), width = "4cm") %>%
  column_spec(column = c(2:6), width = "3cm") %>%
  footnote(general = "Source: ISSP 2017, WID, WIID and ILO. Variables in original scale",
           footnote_as_chunk = T);tab_an_countries

kableExtra::save_kable(tab_an_countries, here::here("output/tables/tableA04.html"))
```

```{r tableA5, results='asis', cache=TRUE}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
rm(list=ls())
tabformat = if(is_html_output()) {"html"} else if(is_latex_output()) {"latex"}
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,dclass6res,
  homclass3_V_res,
  know_total,
  # Q03pcm,edyears,
  female,
  agenum,
  # partner,
  # workst,
  "gini_disp"=wid_gini_disp,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2,country3,country,
) %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=gdppercapita/1000
         )

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100

dfreg1 <- dfreg %>% dplyr::select(
  egal,
  homclass3_V_res,
  know_total,
  dclass3res_V,
  # Q03pcm,
  # edyears,
  # workst,
  female,
  agenum,
  # partner,
  "gini_disp",
  loggdppercapita,
  wstate2
  )

names(dfreg1)
varlab <- 
c("Redistributive preferences","Class-based network homogeneity",
  "Network size","Social class",
  # "Household Income","Education in years","Labor market status",
  "Gender","Age in years",
  # "Has partner",
  "Income Inequality - Gini Index",
  "GDP/capita ",
  "Size of the welfare state")

sjlabelled::set_label(dfreg1) <- varlab

tab05 <- 
st(dfreg1,labels=T,
   title="Table A5: Descriptive statistics for study variables",
   out = "kable",
   numformat = formatfunc(digits = 2),
   digits = 2, 
   factor.counts = F,
   factor.numeric = F,
   summ = list(
     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
     c('notNA(x)','mean(x)')
   ),
   summ.names = list(
     c('N','Mean','SD','Min','Max'),
     c('Count','Percent')   
     )) %>% 
    kable_classic(html_font = "sans",full_width = F)

kableExtra::save_kable(tab05, here::here("output/tables/tableA05.html"))
```

### 2025-07-29 procesamiento/04-prod_prep-supplementary-material.Rmd
data for reproducibility

--- 2025-07-18 procesamiento/05-prod_prep-supplementary-material.Rmd
@@
 pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-# rm(list=ls())
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
@@
 data_vdem <- haven::read_dta("input/data/original/QOG/V-Dem-CY-Full+Others-v15.dta") 
-
-# data_socx <- data.table::fread("input/data/original/ocde-socx/ocde-socx.csv")
 data_socx <- data.table::fread("input/data/original/ocde-socx/ocde-socspen.csv")

### 2025-07-29 procesamiento/99-prod_analysis-descriptives.Rmd
data for reproducibility

--- 2024-02-09 procesamiento/03-prod_analysis-descriptives.Rmd
@@
 macro_data %>% 
-  dplyr::select(egal2,gini_disp,starts_with("homclass"),"class3_1","class3_2","class3_3") %>% 
+  # dplyr::filter(country3!="ZAF") %>% 
+  dplyr::select(egal2,gini_disp,starts_with("homclass")) %>% 
   correlation::correlation() %>% 
@@
 
+ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
+       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 20)
+
 homo_ineq %>%
@@
 
-ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
-       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 20)
-
+31*31*3
 ```
@@
 ```
+
+```{r}
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra)  
+rm(list=ls())
+
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
+
+df1$employed <- ifelse(df1$MAINSTAT==1,yes = 1,no = 0)
+df1$unemployed <- ifelse(df1$MAINSTAT==2,yes = 1,no = 0)
+
+# The unemployment rate for an occupation j was computed as [(number of people unemployed in j)/
+# (number of people unemployed in j + number of people employed in j)]*100
+
+df_employment_country <- df1 %>% 
+  group_by(country,country3,isco88r) %>% 
+  summarise(unemployed=mean(unemployed),employed=mean(employed),isei08=mean(isei08)) %>% 
+  mutate(unemrate=(unemployed/(unemployed+employed))*100)
+
+df_employment_country %>% ungroup() %>% 
+  select(unemployed,employed,isei08,unemrate) %>% 
+  sjPlot::tab_corr()
+
+dfreg <- df1 %>% dplyr::select(
+  egal = egal2,
+  dclass3res_V,
+  dclass3spo_V,
+  # homclass3_V_res,
+  know_total,
+  socialtrust,
+  Q03pcm,
+  edyears,
+  female,
+  agenum,
+  religion,
+  partner,
+  union,
+  workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  gdppercapita,
+  country2, country, country3,
+) %>%
+  # filter(oecd == "OECD") %>%
+  filter(country2 != "SVN") %>% 
+  na.omit() %>% 
+    mutate(loggdppercapita=scale(gdppercapita/1000),
+         edyears2 = edyears ^ 2,
+         age2 = agenum ^ 2, 
+         # gini_disp=scale(gini_disp),
+         )
+
+```

### 2025-07-29 procesamiento/06_prod_power-analysis.R

@@ -248,7 +248,9 @@ save(p_sim_gini_disp_600,file ="p_sim_gini_disp_600.RData")
 # Visualization Power analysis for main effect of Gini--------------------------
 
 pacman::p_load(simr,dplyr,ggplot2)  
-load(here::here("output/tables/p_sim_gini_disp_60.RData"))
+
+
+load(here::here("output/tables/p_sim_gini_disp_50.RData"))
 load(here::here("output/tables/p_sim_gini_disp_100.RData"))
 load(here::here("output/tables/p_sim_gini_disp_150.RData"))
 load(here::here("output/tables/p_sim_gini_disp_200.RData"))
@@ -282,7 +284,7 @@ all_pwcurve_s = p_sim_gini_disp_100_small
 all_pwcurve_l = p_sim_gini_disp_100_large
 
 # Combine results
-all_pwcurve$ps = c(p_sim_gini_disp_60$ps[1],
+all_pwcurve$ps = c(p_sim_gini_disp_50$ps[1],
                    p_sim_gini_disp_100$ps[1],
                    p_sim_gini_disp_150$ps[1],
                    p_sim_gini_disp_200$ps[1],                   
@@ -292,7 +294,7 @@ all_pwcurve$ps = c(p_sim_gini_disp_60$ps[1],
                    p_sim_gini_disp_500$ps[1],
                    p_sim_gini_disp_600$ps[1])
 # Combine the different numbers of levels.
-all_pwcurve$xval = c(p_sim_gini_disp_60$nlevels,
+all_pwcurve$xval = c(p_sim_gini_disp_50$nlevels,
                      p_sim_gini_disp_100$nlevels,
                      p_sim_gini_disp_150$nlevels,
                      p_sim_gini_disp_200$nlevels,                     
@@ -403,7 +405,7 @@ df_psim_s %>%
   labs(title = "Power for predictor Gini (post-tax and transfers) on redistributive preferences",
        x = 'Number of clusters (countries)', 
        # subtitle = "β = 0.09 (observed effect)",
-       caption = "Note: Based on 500 Monte Carlo replications of a multilevel model including the cross-level interaction. The simulations correspond to the\nobserved effect: 0.09. Each point represents the proportion of statistically significant p-values (< .05). Confidence intervals are at 95%..") + 
[…]

### 2025-07-29 procesamiento/02-prod_prep-country.Rmd
main code for reproducibility, simulations are missing

@@
 wid_shares <- haven::read_dta(here::here("input/data/original/wid_shares.dta"))
-# wid_gini_2018 <- wid_gini %>% filter(year==2018)
-# wid_gini_2018$year[wid_gini_2018$year==2018] <- 2016
-# wid_gini_2018$country_yr <- stringi::stri_replace_all(str = wid_gini_2018$country_yr,replacement = "2016",regex = "2018")
-
 wid_df <-wid_ratios  %>% 

### 2025-07-29 procesamiento/03_prod_main_analysis.Rmd
main code for reproducibility, simulations are missing

@@
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
 
@@
 
-setseed(1234)
+set.seed(1234)
 ggsave(plot = arrangeGrob(fig_homo_gini,fig_egal_homo,
@@
   "gini_mkt",
-  gv_spen,
   rel_red,
@@
 
-df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))
-
 dfreg <- df1 %>% dplyr::select(
@@
 dfreg$wstate2 <- as.numeric(scale(dfreg$wstate2))
-
 dfreg$egal <- as.numeric(scale(dfreg$egal))
@@
   redist,prefineq,
-  pct_low,pct_middle,pct_high,
   egal = egal2,
@@
 
-status_prop <- df1 %>% 
-  filter(id %in% dfreg$id) %>% 
-  dplyr::select(pct_high,pct_middle,pct_low,
-         ) %>% summarise_all(mean,na.rm=T)
-
 p <- t(round(occup_prop*100,1))[,1]
@@
 kable(df,linesep = "",booktabs=TRUE,format=tabformat,caption = "Table A2: Occupations included in the position generator instrument") %>%
-  kable_classic(full_width = F,font_size = 15,latex_options = "HOLD_position",,html_font = "sans") %>%
+  kable_classic(full_width = F,font_size = 15,latex_options = "HOLD_position",html_font = "sans") %>%
   column_spec(1,width = "6cm") %>%

### 2025-07-29 procesamiento/04-prod_prep-supplementary-material.Rmd
main code for reproducibility, simulations are missing

@@
     # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
-       x="Class-profile low",y="Redistributive preferences",,tag = "A") +
+       x="Ties to Working Class",y="Redistributive preferences",,tag = "A") +
   theme(legend.position = "none", legend.title = element_blank())
-
 plot_mid<- 
@@
     # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
-      x="Class-profile Middle",y="Redistributive preferences",tag = "B") +
+      x="Ties to Intermediate Class",y="Redistributive preferences",tag = "B") +
   theme(legend.position = "none", legend.title = element_blank())
@@
     # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals",),
-       x="Class-profile High",y="Redistributive preferences",tag = "C") +
+       x="Ties to Service Class",y="Redistributive preferences",tag = "C") +
   theme(legend.position = "none", legend.title = element_blank())
@@
 dfreg$socx<- as.numeric(scale(dfreg$socx))
-
 dfreg$gini_disp <- as.numeric(scale(dfreg$gini_disp))
-
 dfreg$ilo_taxrev <- as.numeric(scale(dfreg$ilo_taxrev))
 dfreg$ilo_govspe <- as.numeric(scale(dfreg$ilo_govspe))
-
 dfreg$cpi <- as.numeric(scale(dfreg$cpi))
@@
 ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
 if (!require("pacman")) install.packages("pacman")
@@
          ) %>%
-  # filter(oecd == "OECD") %>%
   filter(country2 != "SVN") 
@@
 digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
-# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
 digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
-# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
-
 digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)
-
 digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)
@@
          female_gc+agenum_gc+
-         # partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
-         # workst_gc+
          homclass3_V_gc*
@@
          female_gc+agenum_gc+
-         # partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
-         # workst_gc+
          gini_disp +
@@
          female_gc+agenum_gc+
-         # partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
-         # workst_gc+
          homclass3_V_gc*dclass6res*gini_disp + 

### 2025-07-29 procesamiento/04-prod_prep-supplementary-material.Rmd
power analisis 01

@@
 ---
-title: "Complementary analysis"
+title: "Supplementary Analyses"
 date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
@@
   know_total,
-  # Q03pcm,
-  # edyears,
   female,
   agenum,
-  # partner,
-  # workst, 
   WEIGHT,
@@
 ggplot(aes(y =estimate,x=n_low, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high,group=dclass3res_V)) +
-  # geom_errorbar(alpha=0.8,size=0.5,linetype="solid",color="black") +
   geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
@@
   labs(
-    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
-       x="Ties to Working Class",y="Redistributive preferences",,tag = "A") +
+       x="Ties to Working Class",y="Redistributive preferences",tag = "A") +
   theme(legend.position = "none", legend.title = element_blank())
@@
   labs(
-    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
       x="Ties to Intermediate Class",y="Redistributive preferences",tag = "B") +
@@
   labs(
-    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals",),
        x="Ties to Service Class",y="Redistributive preferences",tag = "C") +
@@
          female_gc+agenum_gc+
-         # partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
-         # workst_gc+
          homclass3_V_gc*dclass3res_V*gini_disp + 
@@
          loggdppercapita+
-         # partner_gc+
-         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
-         # workst_gc+
          homclass3_V_gc*dclass3res_V*gini_disp + 
@@
   dclass3res_V,
-  # dclass3spo_V,
   homclass3_V_res,dclass6res,
   know_total,
-  # socialtrust,
-  # Q03pcm,
-  # edyears,
   female,
   agenum,
-  # partner,
-  # religion,
-  # union,
-  # workst, 
   WEIGHT,

### 2025-07-29 procesamiento/06_prod_power-analysis.R

@@ -136,20 +136,36 @@ model <- makeLmer(egal_sd~
                     (1|country2), 
                   fixef=fixed, VarCorr=rand, sigma=s, data=dfreg)
 summary(model)
+# Save the baseline model with the (i) coefficients and (ii) variance structure (between-within countries)
 save(model,file = here::here("output/tables/model_psim_gini.RData"))
+################################################################################.
+# Simulation section ------------------------------------------------------
+################################################################################.
 
-
-
-# Simulation seccion ------------------------------------------------------
 # Load the model object previously created:
-load(here::here("output/tables/model_psim_gini.RData"))
+load(here::here("output/tables/model_psim_gini.RData")) # load the baseline model
 pacman::p_load(simr,dplyr)  
-# Create the simulated data for a maximum of 600 clusters 
+# Using the baseline model, create the simulated data for a maximum of 600 clusters 
 set.seed(12345)
-model_ext_country <- extend(model, along = "country2", n =600)
+model_ext_country <- extend(model, along = "country2", n =600) 
+# Save the simulated data (extended - 'ext') based on the model - this is the data used in  the power analysis
 save(model_ext_country,file = here::here("output/tables/model_ext_country.RData"))
-n_sim <- 500
-# fixef(model)['treatintervention:time1'] <- 0.091169 # Original effect size
+
+# Repeat for a Large effect size (0.2 SD)
+model_large <- model
+fixef(model_large)['gini_disp'] <- 0.2
+model_ext_country <- extend(model_large, along = "country2", n =600)
+save(model_ext_country,file =  here::here("output/tables/model_ext_country_large.RData"))
+
+# Repeat for a Small effect size (0.05 SD)
+model_small <- model
+fixef(model_small)['gini_disp'] <- 0.05
+model_ext_country <- extend(model_small, along = "country2", n =600)
+save(model_ext_country,file =  here::here("output/tables/model_ext_country_small.RData"))
+
+n_sim <- 500 # set the number of repetitions
+
+# Simulation MAIN effect size --------------------------------------------------
 ## Model with 60 clusters --------------------------------------------------
 p_sim_gini_disp_50 <- 
   powerCurve(model_ext_country, 
@@ -245,10 +261,17 @@ p_sim_gini_disp_600 <-
 save(p_sim_gini_disp_600,file ="p_sim_gini_disp_600.RData")
 
 
[…]

### 2025-07-30 procesamiento/05_prod_psim_main-effect.R
interactions backup

@@ -1,0 +1,668 @@
+# Power analysis 
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+
+# load("study1_country.RData");df1 <- df2
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+# load("additional_macro_avg.RData")
+load(here::here("input/data/proc/additional_macro_avg.RData"))
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  female,
+  agenum,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  # Q03pcm,
+  # edyears,
+  female,
+  agenum,
+  # partner,
+  # workst,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
[…]

### 2025-07-30 procesamiento/06_prod_power-analysis.R

@@ -1,634 +1,0 @@
-# Power analysis 
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-# load("study1_country.RData");df1 <- df2
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-# load("additional_macro_avg.RData")
-load(here::here("input/data/proc/additional_macro_avg.RData"))
-
-df1$idnum <- rownames(df1)
-
-dfid <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  female,
-  agenum,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  country2, country, country3,
-) %>% na.omit()
-
-# Merge new macro-data
-df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
-dfreg <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  # Q03pcm,
-  # edyears,
-  female,
-  agenum,
-  # partner,
-  # workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
[…]

### 2025-07-30 procesamiento/06_prod_psim-cross-level-interactions.R

@@ -1,0 +1,355 @@
+# Power analysis 
+set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
+options(ggplot2.discrete.fill = set1)
+options(ggplot2.discrete.colour = set1)
+ggplot2::theme_set(ggplot2::theme_bw())
+ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
+options(scipen=999)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+load(here::here("input/data/proc/additional_macro_avg.RData"))
+
+df1$idnum <- rownames(df1)
+
+dfid <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  female,
+  agenum,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  country2, country, country3,
+) %>% na.omit()
+
+# Merge new macro-data
+df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
+dfreg <- df1 %>% dplyr::select(
+  idnum,
+  redist,prefineq,
+  egal = egal2,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  female,
+  agenum,
+  WEIGHT,
+  region,
+  "gini_disp"=wid_gini_disp,
+  "gini_mkt",
+  gv_spen,
+  rel_red,
+  abs_red,
+  ilo_taxrev,
+  ilo_govspe,
+  d10d1=wid_p90p10,
+  wid_p90p50,
+  top10=wid_sharetop10,
+  rgdpna,
+  gdppercapita,
+  cpi,
+  mig_share,
+  union_den,
+  v2x_polyarchy,
[…]

### 2025-07-30 procesamiento/07_prod_psim-cross-level.R

@@ -1,280 +1,0 @@
-# Power analysis 
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-
-# setwd("~/paper1")
-# load("study1_country.RData");df1 <- df2
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-# load("additional_macro_avg.RData")
-load(here::here("input/data/proc/additional_macro_avg.RData"))
-
-df1$idnum <- rownames(df1)
-
-dfid <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
-  ilo_govspe,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  country2, country, country3,
-) %>% na.omit()
-
-# Merge new macro-data
-df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
-dfreg <- df1 %>% dplyr::select(
-  idnum,
-  redist,prefineq,
-  egal = egal2,
-  dclass3res_V,
-  homclass3_V_res,
-  know_total,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  abs_red,
-  ilo_taxrev,
[…]

### 2025-09-08 procesamiento/04-prod_prep-supplementary-material.Rmd
update for RR

@@
 
-```{r tableS1, results='asis'}
+```{r tableS2, results='asis'}
 set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
@@
 
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
+ccoef <- list(
               "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
               "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              homclass3_V_gc="Class-based network homogeneity (CWC)",
               "gini_disp" = "Income inequality (Gini index)",
@@
               unemployment_rate = "Unemployment rate",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
               "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality")
+              "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
+              "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality")
 
@@
 The depedent variable and country-level variables are in standardized (z-score)",
-       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
+       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
        custom.coef.map = ccoef,
@@
          female_gc+agenum_gc+
-         loggdppercapita+
          homclass3_V_gc*dclass3res_V*gini_disp + 
@@
 
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",
-
-              gini_disp = "Income inequality (Gini index)",
-              ilo_taxrev="(i) Tax revenue",
-              ilo_govspe="(ii) Gov. Spending",
-              abs_red="(iii) Redistribution",              
-              wstate2="(i,ii,iii) Size of the welfare state",
-              loggdppercapita = "GDP/capita",
-
-              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality",
-
-              "homclass3_V_gc:ilo_taxrev"= "Homogeneity × (Tax revenue)",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Homogeneity × Intermediate Class × (Tax revenue)",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Homogeneity × Working Class × (Tax revenue) ",
-
-              "homclass3_V_gc:ilo_govspe"= "Homogeneity × Welfare State (Gov. Spending)",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Homogeneity × Intermediate Class × (Gov. Spending)",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Homogeneity × Working Class × (Gov. Spending)",
-
-              "homclass3_V_gc:abs_red"= "Homogeneity × Welfare State (Redistribution)",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):abs_red" = "Homogeneity × Intermediate Class × (Redistribution)",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):abs_red" = "Homogeneity × Working Class × (Redistribution)",
-
-              "homclass3_V_gc:wstate2"= "Homogeneity × Welfare State",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Homogeneity × Intermediate Class × Welfare State",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Homogeneity × Working Class × Welfare State",
-
-              "homclass3_V_gc:loggdppercapita"= "Homogeneity × GDP",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Homogeneity × Intermediate Class × GDP",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Homogeneity × Working Class × GDP"              
-              )
-
+ccoef <- list(
+  # Class
+  "dclass3res_VIntermediate class (III+IV)" = "Intermediate Class",
+  "dclass3res_VWorking Class (V+VI+VII)" = "Working Class",
+
+  # Homogeneity
+  homclass3_V_gc = "Class-Based Network Homogeneity (CWC)",
+
+  # Class × Homogeneity
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
+
+  # Macro variables
+  gini_disp = "Income Inequality (Gini Index)",
+  ilo_taxrev = "Tax Revenue (% of GDP)",
+  ilo_govspe = "Government Spending (% of GDP)",
+  abs_red = "Redistribution",
+  wstate2 = "Welfare State Size",
+  loggdppercapita = "GDP per Capita (Log)",
+
+  # Homogeneity × Macro
+  "homclass3_V_gc:gini_disp" = "Homogeneity × Income Inequality",
+  "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
+  "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality",
+
+  "homclass3_V_gc:ilo_taxrev" = "Homogeneity × Tax Revenue",
+  "dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Intermediate Class × Tax Revenue",
+  "dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Working Class × Tax Revenue",  
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Intermediate Class × Homogeneity × Tax Revenue",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Working Class × Homogeneity × Tax Revenue",
+
+  "homclass3_V_gc:ilo_govspe" = "Homogeneity × Government Spending",
+  "dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Intermediate Class × Government Spending",
+  "dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Working Class × Government Spending",  
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Intermediate Class × Homogeneity × Government Spending",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Working Class × Homogeneity × Government Spending",
+
+  "homclass3_V_gc:abs_red" = "Homogeneity × Redistribution",
+  "dclass3res_VIntermediate class (III+IV):abs_red" = "Intermediate Class × Redistribution",
+  "dclass3res_VWorking Class (V+VI+VII):abs_red" = "Working Class × Redistribution",    
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):abs_red" = "Intermediate Class × Homogeneity × Redistribution",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):abs_red" = "Working Class × Homogeneity × Redistribution",
+
+  "homclass3_V_gc:wstate2" = "Homogeneity × Welfare State Size",
+  "dclass3res_VIntermediate class (III+IV):wstate2" = "Intermediate Class × Welfare State Size",
+  "dclass3res_VWorking Class (V+VI+VII):wstate2" = "Working Class × Welfare State Size",    
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Intermediate Class × Homogeneity × Welfare State Size",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Working Class × Homogeneity × Welfare State Size",
+
+  "homclass3_V_gc:loggdppercapita" = "Homogeneity × GDP per Capita",
+  "dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Intermediate Class × GDP per Capita",
+  "dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Working Class × GDP per Capita",      
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Intermediate Class × Homogeneity × GDP per Capita",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Working Class × Homogeneity × GDP per Capita"
+)
+
+screenreg(models_interactions)
 htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
-digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_0<- lmer(egal~1 + dclass6res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total+(1|country2),data=dfreg,weights = WEIGHT)
 digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
@@
 digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)
-
 digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
@@
 
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
-              know_total="Network size",
-              "dclass6resLower Service class"="Lower Service",
+ccoef <- list("dclass6resLower Service class"="Lower Service",
               "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
@@
               "dclass6resUnskilled working class" = "Unskilled working",
-              "homclass3_V_res:dclass6resLower Service class" = "Homogeneity × Lower Service",
-              "homclass3_V_res:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
-              "homclass3_V_res:dclass6resSelf-employed"= "Homogeneity × Self-employed",
-              "homclass3_V_res:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
-              "homclass3_V_res:dclass6resUnskilled working class" = "Homogeneity × Skilled working class" 
+              homclass3_V_res="Class-based network homogeneity",
+              know_total="Network size",              
+              "homclass3_V_res:dclass6resLower Service class" = "Lower Service × Homogeneity",
+              "homclass3_V_res:dclass6resRoutine nonmanual class" = "Routine nonmanual × Homogeneity",
+              "homclass3_V_res:dclass6resSelf-employed"= "Self-employed × Homogeneity",
+              "homclass3_V_res:dclass6resSkilled working class" = "Skilled working class × Homogeneity",
+              "homclass3_V_res:dclass6resUnskilled working class" = "Unskilled working class × Homogeneity" 
               )
@@
        groups =
-         list("Social Class (Ref.= Upper Service)" = 3:7,
-              "Homogeneity × Social Class"=8:11),
-      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+         list("Social Class (Ref.= Upper Service)" = 1:5,
+              "Social Class × Homogeneity"=8:12),
+      custom.gof.rows = list("Controls"=c("Yes",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
@@
               "homclass3_V_gc:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
-              "homclass3_V_gc:dclass6resUnskilled working class" = "Homogeneity × Skilled working class",
+              "homclass3_V_gc:dclass6resUnskilled working class" = "Homogeneity × Unskilled working class",
 
@@
               # 3-way interactions: × Gini
+              "homclass3_V_gc:gini_disp" = "Homogeneity × Gini",
+              "dclass6resLower Service class:gini_disp"     = "Lower Service × Gini",
+              "dclass6resRoutine nonmanual class:gini_disp" = "Routine Nonmanual × Gini",
+              "dclass6resSelf-employed:gini_disp"           = "Self-employed × Gini",
+              "dclass6resSkilled working class:gini_disp"   = "Skilled Working Class × Gini",
+              "dclass6resUnskilled working class:gini_disp" = "Unskilled Working Class × Gini",
               "homclass3_V_gc:dclass6resLower Service class:gini_disp"         = "Homogeneity × Lower Service × Gini",
@@
               # 3-way interactions: × Tax Revenue
+              "homclass3_V_gc:ilo_taxrev" = "Homogeneity × Tax Revenue",
+              "dclass6resLower Service class:ilo_taxrev"     = "Lower Service × Tax Revenue",
+              "dclass6resRoutine nonmanual class:ilo_taxrev" = "Routine Nonmanual × Tax Revenue",
+              "dclass6resSelf-employed:ilo_taxrev"           = "Self-employed × Tax Revenue",
+              "dclass6resSkilled working class:ilo_taxrev"   = "Skilled Working Class × Tax Revenue",
+              "dclass6resUnskilled working class:ilo_taxrev" = "Unskilled Working Class × Tax Revenue",              
               "homclass3_V_gc:dclass6resLower Service class:ilo_taxrev"         = "Homogeneity × Lower Service × Tax Revenue",
@@
               # 3-way interactions: × Government Spending
+              "homclass3_V_gc:ilo_govspe" = "Homogeneity × Gov. Spending",
+              "dclass6resLower Service class:ilo_govspe"     = "Lower Service × Gov. Spending",
+              "dclass6resRoutine nonmanual class:ilo_govspe" = "Routine Nonmanual × Gov. Spending",
+              "dclass6resSelf-employed:ilo_govspe"           = "Self-employed × Gov. Spending",
+              "dclass6resSkilled working class:ilo_govspe"   = "Skilled Working Class × Gov. Spending",
+              "dclass6resUnskilled working class:ilo_govspe" = "Unskilled Working Class × Gov. Spending",                
               "homclass3_V_gc:dclass6resLower Service class:ilo_govspe"         = "Homogeneity × Lower Service × Gov. Spending",
@@
               # 3-way interactions: × Redistribution
+              "homclass3_V_gc:abs_red" = "Homogeneity × Redistribution",
+              "dclass6resLower Service class:abs_red"     = "Lower Service × Redistribution",
+              "dclass6resRoutine nonmanual class:abs_red" = "Routine Nonmanual × Redistribution",
+              "dclass6resSelf-employed:abs_red"           = "Self-employed × Redistribution",
+              "dclass6resSkilled working class:abs_red"   = "Skilled Working Class × Redistribution",
+              "dclass6resUnskilled working class:abs_red" = "Unskilled Working Class × Redistribution",                
               "homclass3_V_gc:dclass6resLower Service class:abs_red"         = "Homogeneity × Lower Service × Redistribution",
@@
               # 3-way interactions: × Welfare State
+              "homclass3_V_gc:wstate2" = "Homogeneity × Welfare State",
+              "dclass6resLower Service class:wstate2"     = "Lower Service × Welfare State",
+              "dclass6resRoutine nonmanual class:wstate2" = "Routine Nonmanual × Welfare State",
+              "dclass6resSelf-employed:wstate2"           = "Self-employed × Welfare State",
+              "dclass6resSkilled working class:wstate2"   = "Skilled Working Class × Welfare State",
+              "dclass6resUnskilled working class:wstate2" = "Unskilled Working Class × Welfare State",                   
               "homclass3_V_gc:dclass6resLower Service class:wstate2"         = "Homogeneity × Lower Service × Welfare State",
@@
               # 3-way interactions: × GDP
+              "homclass3_V_gc:loggdppercapita" = "Homogeneity × GDP",
+              "dclass6resLower Service class:loggdppercapita"     = "Lower Service × GDP",
+              "dclass6resRoutine nonmanual class:loggdppercapita" = "Routine Nonmanual × GDP",
+              "dclass6resSelf-employed:loggdppercapita"           = "Self-employed × GDP",
+              "dclass6resSkilled working class:loggdppercapita"   = "Skilled Working Class × GDP",
+              "dclass6resUnskilled working class:loggdppercapita" = "Unskilled Working Class × GDP",               
               "homclass3_V_gc:dclass6resLower Service class:loggdppercapita"         = "Homogeneity × Lower Service × GDP",
@@
 ```
+
+```{r tableS6}
+dfreg$d10d1 <- as.numeric(scale(dfreg$d10d1))
+dfreg$wid_p90p50 <- as.numeric(scale(dfreg$wid_p90p50))
+int_xlvl_r9010 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         dclass3res_V+
+         female_gc+agenum_gc+
+         homclass3_V_gc*
+         dclass3res_V*
+         d10d1 + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+int_xlvl_wid_p90p50 <- 
+  lmer(egal~ 
+         homclass3_V_gc+
+         know_total_gc+
+         dclass3res_V+
+         female_gc+agenum_gc+
+         homclass3_V_gc*
+         dclass3res_V*
+         wid_p90p50 + 
+         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
+
+screenreg(list(int_xlvl_r9010,int_xlvl_wid_p90p50))
+
+ccoef <- list(
+  "dclass3res_VIntermediate class (III+IV)" = "Intermediate Class",
+  "dclass3res_VWorking Class (V+VI+VII)" = "Working Class",
+
+  homclass3_V_gc = "Class-Based Network Homogeneity (CWC)",
+
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
+
+  d10d1 = "Inequality (Ratio 90/10)",
+  "homclass3_V_gc:d10d1" = "Homogeneity × Inequality (R90/10)",
+  "dclass3res_VIntermediate class (III+IV):d10d1" = "Intermediate Class × Inequality (R90/10)",
+  "dclass3res_VWorking Class (V+VI+VII):d10d1" = "Working Class × Inequality (R90/10)",  
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):d10d1" = "Intermediate Class × Homogeneity × Inequality (R90/10)",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):d10d1" = "Working Class × Homogeneity × Inequality (R90/10)",
+
+  wid_p90p50 = "Inequality (Ratio 90/50)",
+  "homclass3_V_gc:wid_p90p50" = "Homogeneity × Inequality (R90/50)",
+  "dclass3res_VIntermediate class (III+IV):wid_p90p50" = "Intermediate Class × Inequality (R90/50)",
+  "dclass3res_VWorking Class (V+VI+VII):wid_p90p50" = "Working Class × Inequality (R90/50)",   
+  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wid_p90p50" = "Intermediate Class × Homogeneity × Inequality (R90/50)",
+  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wid_p90p50" = "Working Class × Homogeneity × Inequality (R90/50)"
+)
+
+htmlreg(list(int_xlvl_r9010,int_xlvl_wid_p90p50),stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
+       file = here::here("output/tables/tableS06.html"),
+       caption = paste("Table S6: Robustness analysis of the multilevel models for income inequality ratios, network homogeneity and redistributive preferences"),
+       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
+       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
+       custom.coef.map = ccoef,
+      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
+      custom.gof.rows = list("Controls"=rep("Yes",2)),
+      include.loglik = FALSE,include.aic = FALSE,
+      custom.gof.names = c(NA,NA,"Num. groups",
+                           "Var: Country (Intercept)",
+                           "Var: Country Homogeneity",
+                           "Var: Country Intermediate Class ",
+                           "Var: Country Working Class",
+                           "Cov: Country (Intercept), Homogeneity",
+                           "Cov: Country (Intercept), Intermediate Class ",
+                           "Cov: Country (Intercept), Working Class",
+                           "Cov: Country Homogeneity, Intermediate Class",
+                           "Cov: Country Homogeneity, Working Class",
+                           "Cov: Country Intermediate Class, Working Class",
+                           "Var: Residual")
+      )
+
+```
+
+```{r tableS7}
+tab_countries<- 
+  dfreg %>% 
+  group_by(country3) %>% 
+  summarise(gini_disp=mean(gini_disp)) %>% 
+  mutate(gini_q05=ntile(gini_disp,5),
+         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
+  arrange(gini_d10) %>% 
+  dplyr::select(-gini_disp)
+
+dfreg <- dfreg %>% left_join(tab_countries,by="country3")
+
+## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
+
+library(estimatr)
+
+# Quintile 1 (low)
+digclas1_VW_Q1<- lm(egal~1 + dclass3res_V*homclass3_V_res +know_total+female+agenum+factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
+
+# Quintile 2 (mid-low)
+digclas1_VW_Q2<- lm(egal~1 + dclass3res_V*homclass3_V_res +know_total+female+agenum+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
+
+# Quintile 3 (middle)
+digclas1_VW_Q3<- lm(egal~1 + dclass3res_V*homclass3_V_res +know_total+female+agenum+ factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
+
+# Quintile 4 (middle-high)
+digclas1_VW_Q4<- lm(egal~1 + dclass3res_V*homclass3_V_res +know_total+female+agenum +factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
+
+# Quintile 5 (high)
+digclas1_VW_Q5<- lm(egal~1 + dclass3res_V*homclass3_V_res +know_total+female+agenum+ factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
+
+digclas1_Q05 <- list("Q1"=digclas1_VW_Q1,"Q2"=digclas1_VW_Q2,"Q3"=digclas1_VW_Q3,"Q4"=digclas1_VW_Q4,"Q5"=digclas1_VW_Q5)
+
+ccoef <- list("(Intercept)" = "(Intercept)",
+              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              homclass3_V_res="Class-based network homogeneity",
+              "dclass3res_VIntermediate class (III+IV):homclass3_V_res" = "Intermediate Class × Homogeneity",
+              "dclass3res_VWorking Class (V+VI+VII):homclass3_V_res" = "Working Class × Homogeneity")
+# header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
+htmlreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,include.ci = FALSE,
+        file = here::here("output/tables/tableS07.html"),
+        caption = "Table S7: Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles",
+        custom.note = "Note: Standard errors in parentheses. %stars",
+        caption.above = T,leading.zero = T,
+        custom.coef.map = ccoef,
+      groups = list("Social Class (Ref.= Service Class)" = 2:3,
+                    "Social Class × Homogeneity"=5:6),
+      custom.gof.rows = list("Country FE"=rep("Yes",5)),
+      # include.loglik = FALSE,include.aic = FALSE,
+      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual")
+      )
+```

### 2025-09-08 procesamiento/05_prod_psim_main-effect.R

@@ -9,9 +9,7 @@ if (!require("pacman")) install.packages("pacman")
 pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
 rm(list=ls())
 
-# load("study1_country.RData");df1 <- df2
 load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-# load("additional_macro_avg.RData")
 load(here::here("input/data/proc/additional_macro_avg.RData"))
 
 df1$idnum <- rownames(df1)
@@ -647,7 +645,8 @@ bind_rows(df_psim_s,df_psim,df_psim_l) %>%
   scale_y_continuous(name = 'Share of significant', limits = c(0, 1), 
                      breaks = c(0, .2, .4, .6, .8, 1),
                      labels = c('0%', '20%', '40%', '60%', '80%', '100%')) +
-  labs(title = "Statistical Power for the coefficient of Gini (post-tax and transfers) on redistributive preferences",
+  labs(
+    # title = "Statistical Power for the coefficient of Gini (post-tax and transfers) on redistributive preferences",
        x = 'Number of clusters (countries)', 
        caption = "Note: Based on 500 Monte Carlo replications of a multilevel model. Each point represents the proportion of statistically significant p-values (< .05).\nConfidence intervals are at 95%.") + 
   theme(axis.title.x = element_text(size = 12, margin = margin(t = 8)), 

### 2025-09-08 procesamiento/06_prod_psim-cross-level-interactions.R

@@ -330,8 +330,8 @@ bind_rows(df_psim,df_psim_int) %>%
                      labels = c('0%', '20%', '40%', '60%', '80%', '100%')) +
   guides(color = guide_legend(title = NULL)) +
   labs(
-    title = "Statistical Power for Cross-Level Interaction",
-    subtitle = "Observed effect of Class × Homogeneity × Gini on redistributive preferences",
+    # title = "Statistical Power for Cross-Level Interaction",
+    # subtitle = "Observed effect of Class × Homogeneity × Gini on redistributive preferences",
     x = "Number of clusters (countries)",
     y = "Share significant",
     caption = "Note: Based on 500 Monte Carlo replications of the multilevel model including the cross-level interactions. The simulations correspond to the observed\neffects: −0.109 (Working Class × Homogeneity × Gini) and −0.248 (Intermediate Class × Homogeneity × Gini). Each point represents the proportion of statistically\nsignificant p-values (< .05). Confidence intervals are at 95%."

### 2025-09-30 processing/03_prod_main_analysis.Rmd
to-ignore2

--- 2025-07-29 procesamiento/03_prod_main_analysis.Rmd
@@
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
-digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
+digclas1_VW_0<- lmer(egal~1 + dclass3res_V + female+agenum+know_total+(1|country2),data=dfreg,weights = WEIGHT)
+# digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
 # digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
@@
 
-digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
-                    digclas1_VW_3,
+digclas1_VW_7 <- update(digclas1_VW_0, . ~ . +dclass3res_V*homclass3_V_res+know_total)
+digclas1_VW <- list(digclas1_VW_0,
+                    # digclas1_VW_1,
+                    # digclas1_VW_3,
                     # digclas1_VW_4,
@@
 
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
-              know_total="Network size",
-              # socialtrust="Social Trust",
+ccoef <- list("(Intercept)"= "(Intercept)",
   "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
               "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "femaleFemale"="Female (Ref. = Male)",
-              # "agenum"="Age",
-              # "age2"="Age2",
-             # "edyears"="Year of Education",
-             # "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
-             # "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
-              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")
+              homclass3_V_res="Class-based network homogeneity",
+              "dclass3res_VIntermediate class (III+IV):homclass3_V_res" = "Intermediate Class × Homogeneity",
+              "dclass3res_VWorking Class (V+VI+VII):homclass3_V_res" = "Working Class × Homogeneity"
+)
 
@@
 htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
-       caption = paste("Table 1: Multilevel models for network homogeneity and redistributive preferences"),
+       caption = paste("Table 1: Multilevel models for social class, network homogeneity and redistributive preferences"),
        custom.note = "Note: Standard errors in parentheses. %stars",
@@
        groups =
-         list("Social Class (Ref.= Service Class)" = 3:4,
-              "Homogeneity × Social Class"=5:6),
-      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+         list("Social Class (Ref.= Service Class)" = 2:3,
+              "Social Class × Homogeneity"=5:6),
+      custom.gof.rows = list("Controls"=c(rep("Yes",2))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
@@
 
-ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
-              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+ccoef <- list("dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
               "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              homclass3_V_gc="Class-based network homogeneity",
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
               "gini_disp" = "Income inequality (Gini index)",
@@
               wstate2="Size of the welfare state",
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",
-
               "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",
-
               "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
               "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
-
-              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
-              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality")
+              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
+              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality")
 
 htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
-       caption = paste("Table 2: Multilevel models for income inequality, network homogeneity and redistributive preferences"),
+       caption = paste("Table 2: Multilevel models for income inequality, social class, network homogeneity and redistributive preferences"),
        custom.note = " Note: Individual level variables are centered within cluster (group mean).Standard errors in parentheses. %stars",
@@
        custom.coef.map = ccoef,
-      groups = list("Social Class (Ref.= Service Class)" = 2:3,
-                    "Homogeneity × Social Class"=5:6, 
+      groups = list("Social Class (Ref.= Service Class)" = 1:2,
+                    "Social Class × Homogeneity"=4:5,
                     "Class × Income Inequality" = 8:9 ,
-                    "Homogeneity × Social Class × Income Inequality"=10:11),
+                    "Social Class × Homogeneity × Income Inequality"=10:11),
       custom.gof.rows = list("Controls"=rep("Yes",2)),
@@
 dfreg <- df1 %>% dplyr::select(
-  redist,prefineq,
+   prefineq,redist,
   egal = egal2,
@@
   know_total,
+  female,
+  agenum,
   Q03pcm,
   edyears,
-  female,
-  agenum,
   partner,
@@
   mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
+         loggdppercapita=log(gdppercapita)
+         ) %>%
   filter(country2 != "SVN") 
-dfreg <- na.omit(dfreg)
 dfreg$egal <- as.numeric(scale(dfreg$egal))
+dfreg_1 <- na.omit(dfreg %>% dplyr::select(prefineq,redist,
+  egal,
+  dclass3res_V,
+  homclass3_V_res,
+  know_total,
+  female,
+  agenum,
+  WEIGHT,
+  region,country2)
+  )
+
 ## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
-digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
-digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
+digclas1_VW_0<- lmer(egal~1 + (1|country2),data=dfreg_1,weights = WEIGHT)
+digclas1_VW_2 <- update(digclas1_VW_0, . ~ . + dclass3res_V)
+digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V+homclass3_V_res+female+agenum+know_total)
 digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
-digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
-digclas1_VW_7)
+#Include additional controls
+digclas1_VW_8 <- update(digclas1_VW_7, . ~ . + edyears+Q03pcm+partner+workst,data=na.omit(dfreg))
+digclas1_VW <- list(digclas1_VW_2,digclas1_VW_3,digclas1_VW_7,digclas1_VW_8)
 
-ccoef <- list(homclass3_V_res="Class-based network homogeneity",
+ccoef <- list("dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
+             "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
+              homclass3_V_res="Class-based network homogeneity",
               know_total="Network size",
-              # socialtrust="Social Trust",
-              "femaleFemale"="Female (Ref. = Male)",
-              "agenum"="Age",
-              # "age2"="Age2",
+              "dclass3res_VIntermediate class (III+IV):homclass3_V_res" = "Intermediate Class × Homogeneity",
+              "dclass3res_VWorking Class (V+VI+VII):homclass3_V_res" = "Working Class × Homogeneity",
              "edyears"="Year of Education",
@@
              "partnerHas a partner" = "Has partner (Ref.= No partner)",
-                           "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
-              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
-              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
-              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
-              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
-              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
-              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
-              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")
+             "femaleFemale"="Female (Ref. = Male)",
+             "agenum"="Age"
+             )
 
@@
        custom.coef.map = ccoef,
-      groups = list("Household Income (Ref.= Tertile I)"= 6:8,
-                    "Social Class (Ref.= Service Class)" = 11:12, 
-                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
-                    "Homogeneity x Social Class"=13:14),
-      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
+      groups = list("Social Class (Ref.= Service Class)" = 1:2,
+                    "Social Class × Homogeneity"=5:6,
+                    "Household Income (Ref.= Tertile I)"= 8:10
+                    ),
+      custom.gof.rows = list("Controls"=c(rep("Yes",4))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),

### 2025-09-30 processing/99-prod_power-analysis.Rmd
to-ignore2

---
title: "Power analysis"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Power analysis

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(simr,dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())
# setwd("~/paper1")
# load("study1_country.RData");df1 <- df2
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
# load("additional_macro_avg.RData")
load(here::here("input/data/proc/additional_macro_avg.RData"))

df1$idnum <- rownames(df1)

dfid <- df1 %>% dplyr::select(
  idnum,
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  country2, country, country3,
) %>% na.omit()

# Merge new macro-data
df1 <- df1 %>% left_join(.,additional_macro_avg,by ="ccode")
dfreg <- df1 %>% dplyr::select(
  idnum,
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  cpi,
  mig_share,
  union_den,
  v2x_polyarchy,
  unemployment_rate,
  v2catrauni,
  country2, country, country3,
) %>%
  filter(country2 != "SVN") %>% 
  # na.omit() %>%
  filter(idnum %in%  dfid$idnum) %>% 
  mutate(loggdppercapita=scale(gdppercapita/1000),
         gini_disp=scale(gini_disp))

fit_gov<- psych::pca(dfreg[,c("ilo_taxrev","ilo_govspe","abs_red")])
dfreg$wstate<- as.numeric(fit_gov$scores)
dfreg$wstate2 <- ((dfreg$wstate-min(dfreg$wstate,na.rm = T))/(max(dfreg$wstate,na.rm = T)-min(dfreg$wstate,na.rm = T)))*100
dfreg$wstate2 <- as.numeric(scale(dfreg$wstate2))
dfreg$gini_disp <- as.numeric(scale(dfreg$gini_disp))

# Variable Group-Centering ------------------------------------------------$
dfreg <- 
  dfreg %>% 
  mutate(to_dummy(female)
         )
dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
dfreg$agenum_gc = group_center(dfreg$agenum, grp = dfreg$country2)
dfreg$homclass3_V_gc <-group_center(dfreg$homclass3_V_res, grp = dfreg$country2)
dfreg$know_total_gc = group_center(dfreg$know_total, grp = dfreg$country2)
dfreg$egal_sd <- scale(dfreg$egal) #standardized DV

# Create Model with the double cross-level interactions: Gini + Welfare State Size------
model_re <- 
  lmer(egal_sd~homclass3_V_gc+know_total_gc+dclass3res_V+female_gc+agenum_gc+
         homclass3_V_gc*dclass3res_V*gini_disp+homclass3_V_gc*dclass3res_V*wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

model <- 
  makeLmer(egal_sd~homclass3_V_gc+know_total_gc+dclass3res_V+female_gc+agenum_gc+
             homclass3_V_gc*dclass3res_V*gini_disp +homclass3_V_gc*dclass3res_V*wstate2+
             (homclass3_V_gc+dclass3res_V|country2), 
         fixef=as.numeric(summary(model_re)$coef[,"Estimate"]), 
         VarCorr=lme4::VarCorr(model_re), 
         sigma=as.data.frame(lme4::VarCorr(model_re))$sdcor[11], 
         data=dfreg)

## Simulation for N clusters ----------------------------------------------
n_clusters <- c(50,200) # set the number of clusters
n_sim <- 500 # set the number of simulations

# Simulation: Homogeneity*Working*Gini ------------------------------------
psim_work <- list(NA,NA) # set empty list 
model_psim <- extend(model, along = "country2", n =200)

psim_work_50 <-
    powerCurve(model_psim,
             test=simr::fixed("homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp",method = c("t")),
             breaks = 50,along = "country2",
             nsim=100,
             alpha=.05,
             progress=TRUE,
             seed = 123)

psim_work_200 <-
    powerCurve(model_psim,
             test=simr::fixed("homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp",method = c("t")),
             breaks = 200,along = "country2",
             nsim=20,
             alpha=.05,
             progress=TRUE,
             seed = 123)

model_psim <- extend(model, along = "country2", n =200)
  psim_work[[2]] <-
    powerSim(model_psim,
             test=simr::fixed("homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp",method = c("t")),
             nsim=n_sim,
             alpha=.05,
             progress=TRUE)

psim_work
save(psim_work,file = "psim_xlvl_working.RData")

# Simulation: Homogeneity*Intermediate*Gini -------------------------------
psim_inte <- list() # set empty list 
for (i in n_clusters) {
  model_psim <- extend(model, along = "country2", n =i)
  psim_inte[[i]] <-powerSim(model_psim, 
                            test=simr::fixed("homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp",method = c("t")),
                            nsim=n_sim,
                            alpha=.05,
                            progress=TRUE)
}
psim_inte
save(psim_inte,file = "psim_xlvl_middle.RData")

```

### 2025-09-30 processing/prod_analysis-ocde-sample.Rmd
to-ignore2

--- 2023-10-29 procesamiento/prod_analysis-ocde-sample.Rmd
@@
 ```
+
+# Numeric -  Egalitarian Attitudes Index
+
+Cronbach's alpha is 0.7 for:
+
+1. It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes. 
+2. For a society to be fair, differences in people's standard of living should be small.
+
+Note: the item "Differences in income in [COUNTRY] are too large" is not included because of two reasons.
+First, the item is fuzzy in terms of what is it measuring, "are" refers to a perception about inequality and "too large" as a normative judgement.
+Second, the literature has addressed this indicator as perceived or concerns about inequality.
+
+<!----------------------------------------------------------------------------->
+
+## Full network
+
+```{r mod-homclass-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(
+                        egal=egal3,
+                        class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+ filter(oecd=="OECD" & country2 != "SVN") %>% 
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/ocde-egalitarian-homclass-full-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                               class3,
+                        homclass,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(oecd=="OECD" & country2 != "SVN") %>% 
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+# summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+# summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/ocde-egalitarian-homclass-full-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/ocde-egalitarian-homclass-full-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/ocde-egalitarian-homclass-full-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Strong ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(oecd=="OECD" & country2 != "SVN") %>%   
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/ocde-egalitarian-homclass-strong-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_s,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(oecd=="OECD" & country2 != "SVN") %>% 
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/ocde-egalitarian-homclass-strong-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/ocde-egalitarian-homclass-strong-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/ocde-egalitarian-homclass-strong-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+
+## Weak ties
+
+```{r mod-homclass-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+filter(oecd=="OECD" & country2 != "SVN") %>% 
+  na.omit()
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/ocde-egalitarian-homclass-weak-individual.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-strong-ties,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3,
+                        homclass=homclass_w,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(oecd=="OECD" & country2 != "SVN") %>% 
+  na.omit()
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/ocde-egalitarian-homclass-weak-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/ocde-egalitarian-homclass-weak-individual.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/ocde-egalitarian-homclass-weak-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+```
+## R's class
+
+```{r mod-homclass-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        homclass=homclass_res,
+                        class3spo,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(oecd=="OECD" & country2 != "SVN")
+
+# Models 
+base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
+homclass<- update(base, . ~ . +homclass)
+full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
+rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
+rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
+# anova(rob1,rob2)
+# Interactions segregation x class
+int_homo <- update(rob1, . ~ . +class3*homclass)
+
+models <- list(homclass,full1,rob1,int_homo)
+save(models,file = here::here("output/ocde-egalitarian-homclass-respondent.RData"),compress = "gzip")
+```
+
+```{r mod-intermacro-numeric-respondent,results='asis'}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
+rm(list=ls())
+load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
+dfreg <- df1 %>% dplyr::select(egal=egal2,
+                        class3=class3res,
+                        class3spo,
+                        homclass=homclass_res,
+                        Q03pcm,
+                        edyears,
+                        female,
+                        agenum,
+                        union,
+                        workst,
+                        WEIGHT,
+                        region,
+                        "gini_disp",
+                        "gini_mkt",
+                        rgdpna,
+                        oecd,
+                        country2,country,
+                        palmaratio,
+                        top10,
+                        middle50,
+                        d10d1,
+                        giniindex,
+                        ttheilge1
+                        ) %>% 
+  mutate(logrgdpna=log(rgdpna),
+         edyears2=edyears^2,
+         age2=agenum^2) %>%
+  filter(oecd=="OECD" & country2 != "SVN")
+
+# Homoclass x Gini--------------------------------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
+giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniD_gdp,giniD_rs)
+giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
+summary(giniD_int)
+
+giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
+giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
+# anova(giniM_gdp,giniM_rs)
+giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
+summary(giniM_int)
+models <- list(giniD_gdp,giniD_rs,giniD_int,
+               giniM_gdp,giniM_rs,giniM_int)
+
+# Homoclass x Other Economic Inequality-----------------------------------------
+main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+ class3spo +(homclass|country2)"
+base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
+int_palma <- update(base, . ~ . +homclass*palmaratio)
+int_pc10  <- update(base, . ~ . +homclass*top10)
+int_pc50  <- update(base, . ~ . +homclass*middle50)
+int_d10d1 <- update(base, . ~ . +homclass*d10d1)
+int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
+int_theil  <- update(base, . ~ . +homclass*ttheilge1)
+
+models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil
+                 )
+save(giniD_gdp,giniD_rs,giniD_int,
+                 giniM_gdp,giniM_rs,giniM_int,
+                 int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil,
+     file = here::here("output/ocde-egalitarian-homclass-respondent-macro.RData"),compress = "gzip")
+```
+
+```{r}
+load(here::here("output/ocde-egalitarian-homclass-respondent.RData"))
+texreg::knitreg(models)
+
+load(here::here("output/ocde-egalitarian-homclass-respondent-macro.RData"))
+texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
+                 int_gini_wiid,int_theil))
+
+marginaleffects::plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F)
+marginaleffects::plot_predictions(int_gini_wiid, condition = list("homclass",giniindex=range),gray = F)
+marginaleffects::plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)
+```

### 2025-09-30 processing/prod_analysis-alternatives.R
to-ignore3

@@ -1,713 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  # egal = perineq,
-  # egal = redist,
-  # egal = prefineq,
-  class3,
-  homclass,
-  class6,
-  know_total,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_rd10d01,
-  wid_rp90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         know_total=log(know_total),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  filter(country2 != "SVN") %>% 
-  # filter(oecd == "OECD") %>%
-  na.omit()
-
-dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric")) %>% 
-  rename(prop_serv=class3_1,prop_inte=class3_2,prop_work=class3_3)
-dfreg <- 
-dfreg %>% 
-  group_by(country2) %>% 
-  mutate(prop_serv=mean(prop_serv),prop_inte=mean(prop_inte),prop_work=mean(prop_work))
-
-dfreg <- as.data.frame(dfreg)
-
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
[…]

### 2025-09-30 processing/prod_analysis-test-oper_dominance.R

@@ -1,654 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  class3,
-  class3_V,
-  class6,
-  homclass,
-  homclass_V,
-  digclass3,
-  digclass3_V,
-  digclass6,
-  homclass2,
-  homclass2_V,
-  dclass3,
-  dclass3_V,
-  dclass3_III,
-  dclass3_III_V,
-  dclass6,
-  homclass3,
-  homclass3_V,
-  homclass3_III,
-  homclass3_III_V,
-  class3res,
-  class3spo,
-  homclass_res,
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         # know_total=log(know_total),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")  
-
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
[…]

### 2025-09-30 processing/prod_analysis-test-oper_resp-spouse.R

@@ -1,648 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  egal = egal2,
-  starts_with("class3"),
-  starts_with("digclass3"),
-  starts_with("dclass3"),
-  starts_with("homclass"),
-  know_total,
-  socialtrust,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  union,
-  workst,
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  # filter(oecd == "OECD") %>%
-  filter(country2 != "SVN")
-
-# Variable Group-Centering ------------------------------------------------
-dfreg <- 
-  dfreg %>% 
-  mutate(to_dummy(female),
-         to_dummy(union),
-         to_dummy(workst),
-         # dummy for categorical variables-------------------------------------
-         to_dummy(Q03pcm)
-  )
-dfreg$female_gc = group_center(dfreg$female_2, grp = dfreg$country2)
-dfreg$union_gc = group_center(dfreg$union_2, grp = dfreg$country2)
[…]

### 2025-09-30 processing/prod_analysis_reviews.R

@@ -1,265 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
-rm(list=ls())
-
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-dfreg <- df1 %>% dplyr::select(
-  prefineq,redist,
-  egal = egal2,
-  dclass3res_V,
-  dclass6res,
-  homclass3_V_res,
-  know_total,
-  n_low,
-  n_middle,
-  n_high,
-  Q03pcm,
-  edyears,
-  female,
-  agenum,
-  partner,
-  workst, 
-  WEIGHT,
-  region,
-  "gini_disp"=wid_gini_disp,
-  "gini_mkt",
-  gv_spen,
-  rel_red,
-  d10d1=wid_p90p10,
-  wid_p90p50,
-  top10=wid_sharetop10,
-  rgdpna,
-  gdppercapita,
-  oecd,
-  country2, country, country3,
-) %>%
-  mutate(logrgdpna = log(rgdpna),
-         loggdppercapita=log(gdppercapita),
-         edyears2 = edyears ^ 2,
-         age2 = agenum ^ 2) %>%
-  filter(country2 != "SVN") 
-
-
-dfreg <- na.omit(dfreg)
-
-
-
-dfreg$n_low <- (dfreg$n_low - min(dfreg$n_low)) / (max(dfreg$n_low) - min(dfreg$n_low))*100
-dfreg$n_middle <- (dfreg$n_middle - min(dfreg$n_middle)) / (max(dfreg$n_middle) - min(dfreg$n_middle))*100
-dfreg$n_high <- (dfreg$n_high - min(dfreg$n_high)) / (max(dfreg$n_high) - min(dfreg$n_high))*100
-
-
-# Single class-profile analysis -------------------------------------------
-digclas1_VW_0<- lmer(egal~1 + (1|country2),data=dfreg)
[…]

### 2025-09-30 processing/prod_egp-household.R

@@ -1,695 +1,0 @@
-## Ocupación
-# Ocupación u oficio actual ISCO 08
-frq(df1$SPISCO08) # isco08 
-# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
-df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
-sjmisc::frq(df1$isco88spo)
-
-#Relación de Empleo encuestado
-sjmisc::frq(df1$SPEMPREL)
-
-df1$sempspo <- df1$SPEMPREL
-df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
-sjmisc::frq(df1$sempspo)
-
-df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
-sjmisc::frq(df1$sempspo)
-
-# superivison
-sjmisc::frq(df1$SPWRKSUP) #supervision spouse
-df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
-sjmisc::frq(df1$supvisspo)
-
-# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
-df1$tmpisco88 <- df1$isco88
-
-# Replace values in `tmpdf1$isco88` based on specified conditions
-df1$tempisco <- ifelse((df1$isco88spo >= 6100 & df1$isco88spo <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88spo)
-df1$tempisco <- ifelse((df1$isco88spo >= 9200 & df1$isco88spo <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88spo)
-df1$tempisco <- ifelse(df1$isco88spo == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88spo)
-df1$tempisco <- ifelse(df1$isco88spo == 1312 & df1$supvis > 10 & !is.na(df1$supvis), 1222, df1$isco88spo)
-df1$tempisco <- ifelse(df1$isco88spo == 1313 & df1$supvis > 10 & !is.na(df1$supvis), 1223, df1$isco88spo)
[…]

### 2025-09-30 processing/prod_egp-respondent.R

@@ -1,706 +1,0 @@
-## Ocupación
-# Ocupación u oficio actual ISCO 08
-frq(df1$ISCO08) # isco08 
-# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
-df1$isco88r <- occupar::isco08to88(df1$ISCO08)
-sjmisc::frq(df1$isco88r)
-
-#Note: the package generate identical recodes as my own manual recoding
-
-#Employment relation encuestado
-sjmisc::frq(df1$EMPREL)
-sjmisc::frq(df1$WORK)
-df1$semp <- df1$EMPREL
-df1$semp <- as.numeric(car::recode(df1$semp, "c(2,3,4)=1;c(1)=2;c(0,8,9)=NA"))
-sjmisc::frq(df1$semp)
-df1$semp <- sjlabelled::set_labels(x = df1$semp,labels=c('Self-employed','Employee'))
-sjmisc::frq(df1$semp)
-
-# superivison
-sjmisc::frq(df1$NEMPLOY) #supervision respondent
-df1$supvis <- as.numeric(car::recode(df1$NEMPLOY,"c(9998,9999)=NA"))
-sjmisc::frq(df1$supvis)
-
-# head(df1[,c('ISCO08','cod_m22',"isco88",'m06','m25',"supvis")],50)
-# View(df1[,c('ISCO08','cod_m22',"isco88",'m06','m25',"supvis")])
-
-# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
-df1$tmpisco88 <- df1$isco88r
-summary(df1$tmpisco88)
-# Replace values in `tmpdf1$isco88` based on specified conditions
-df1$tempisco <- ifelse((df1$isco88r >= 6100 & df1$isco88r <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88r)
-df1$tempisco <- ifelse((df1$isco88r >= 9200 & df1$isco88r <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88r)
-df1$tempisco <- ifelse(df1$isco88r == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88r)
[…]

### 2025-09-30 processing/prod_egp-spouse.R

@@ -1,701 +1,0 @@
-## Ocupación
-# Ocupación u oficio actual ISCO 08
-frq(df1$SPISCO08) # isco08 
-# Recode CIUO_encuestado desde ISCO 2008 a ISCO 1988
-df1$isco88spo <- occupar::isco08to88(df1$SPISCO08)
-sjmisc::frq(df1$isco88spo)
-
-#Relación de Empleo encuestado
-sjmisc::frq(df1$SPEMPREL)
-
-df1$sempspo <- df1$SPEMPREL
-df1$sempspo <- as.numeric(car::recode(df1$sempspo, "c(2,3,4,5)=1;c(1)=2;c(0,8,9)=NA"))
-sjmisc::frq(df1$sempspo)
-
-df1$sempspo <- sjlabelled::set_labels(x = df1$sempspo,labels=c('Self-employed','Employee'))
-sjmisc::frq(df1$sempspo)
-
-# superivison
-sjmisc::frq(df1$SPWRKSUP) #supervision spouse
-df1$supvisspo <- as.numeric(car::recode(df1$SPWRKSUP,"c(0,2)=0;1=9;c(8,9)=NA"))
-sjmisc::frq(df1$supvisspo)
-
-df1$id <- NULL
-df1 <- tibble::rowid_to_column(df1, "id")
-haven::write_dta(data = df1[c("id","isco88spo","sempspo","supvisspo")],
-                 path = "input/data/proc/ocup_spouse.dta")
-df1$id <- NULL
-
-# Create a temporary variable `tmpisco88` and assign it the value of `isco88`
-df1$tmpisco88 <- df1$isco88
-
-# Replace values in `tmpdf1$isco88` based on specified conditions
-df1$tempisco <- ifelse((df1$isco88spo >= 6100 & df1$isco88spo <= 6133) & df1$supvis >= 1 & !is.na(df1$supvis), 1311, df1$isco88spo)
-df1$tempisco <- ifelse((df1$isco88spo >= 9200 & df1$isco88spo <= 9213) & df1$supvis > 1 & !is.na(df1$supvis), 6132, df1$isco88spo)
-df1$tempisco <- ifelse(df1$isco88spo == 1311 & df1$supvis > 10 & !is.na(df1$supvis), 1221, df1$isco88spo)
[…]

### 2025-09-30 processing/prod_otero_iturra.R

@@ -1,482 +1,0 @@
-set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
-options(ggplot2.discrete.fill = set1)
-options(ggplot2.discrete.colour = set1)
-ggplot2::theme_set(ggplot2::theme_bw())
-ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
-options(scipen=999)
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(dplyr,sjmisc,sjlabelled,haven,vtable)  
-rm(list=ls())
-load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
-
-
-
-
-df1$isolation_v1<- 
-  sjmisc::rec(set_na(car::recode(df1$v31,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v1)
-df1$isolation_v2<- 
-  sjmisc::rec(set_na(car::recode(df1$v32,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v2)
-df1$isolation_v3<- 
-  sjmisc::rec(set_na(car::recode(df1$v33,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$isolation_v3)
-
-
-df1$part_v1<- 
-  sjmisc::rec(set_na(car::recode(df1$v17,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v1)
-df1$part_v2<- 
-  sjmisc::rec(set_na(car::recode(df1$v18,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v2)
-df1$part_v3<- 
-  sjmisc::rec(set_na(car::recode(df1$v19,"c(8,9)=NA"),na = c(0,8,9)),rec="rev");sjmisc::frq(df1$part_v3)
-
-
-sjmisc::frq(df1$VOTE_LE)
-df1$vote <- factor(car::recode(df1$VOTE_LE,recodes = "1=1;2=0;else=NA"))
-table(df1$country3,df1$vote)
-
-df1$politrust <- set_na(car::recode(df1$v36,"c(98,99)=NA"),na = c(98,99));frq(df1$politrust)
-
-dfreg <- df1 %>% dplyr::select(
-  socialtrust,
-  politrust,
[…]

### 2025-10-06 processing/03_prod_main_analysis.Rmd
images
better image quality

@@
 
-ggsave(plot = last_plot(),filename = "figure002.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+ggsave(plot = last_plot(),filename = "figure002.png",device = "tiff",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
 ```
@@
         legend.title = element_blank())  
-ggsave(plot = last_plot(),filename = "figure003.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+ggsave(plot = last_plot(),filename = "figure003.png",device = "tiff",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
 ```
@@
   )),
- filename = "figure004.png",device = "png",
- path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26)
+ filename = "figure004.png",device = "tiff",
+ path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 26,dpi = 500)
 ```
@@
 # digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
-digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
+digclas1_VW_3 <- update(digclas1_VW_0, . ~ . + dclass3res_V)
 # digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)
@@
 
-ggsave(plot = last_plot(),filename = "figure005.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+ggsave(plot = last_plot(),filename = "figure005.png",device = "tiff",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
 ```
@@
 
-ggsave(plot = last_plot(),filename = "figure006.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
+ggsave(plot = last_plot(),filename = "figure006.png",device = "tiff",
+       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15,dpi = 500)
 ```

### 2025-10-06 processing/05_prod_psim_main-effect.R

@@ -661,7 +661,7 @@ bind_rows(df_psim_s,df_psim,df_psim_l) %>%
         plot.caption = element_text(size = rel(0.8), hjust = 0, vjust = 1, margin = margin(t = 10)))
 
 ggsave(plot = last_plot(),filename = "figureS02.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1.5,units = "cm",scale = 15)
+       path = here::here("output/images"),width = 2,height = 1.5,units = "cm",scale = 15,dpi = 500)
 
 
 

### 2025-10-06 processing/06_prod_psim-cross-level-interactions.R

@@ -350,6 +350,6 @@ bind_rows(df_psim,df_psim_int) %>%
         )
 
 ggsave(plot = last_plot(),filename = "figureS01.png",device = "png",
-       path = here::here("output/images"),width = 2,height = 1.5,units = "cm",scale = 15)
+       path = here::here("output/images"),width = 2,height = 1.5,units = "cm",scale = 15,dpi = 500)
 
 
